### 2023-02-01 paper/FPF-WG1.tex
Added paper draft

\documentclass[11pt,a4paper]{article}
\pdfoutput=1

\usepackage[colorlinks=true, linkcolor=black!50!blue, urlcolor=blue, citecolor=blue, anchorcolor=blue]{hyperref}
\usepackage[font=small,labelfont=bf,margin=0mm,labelsep=period,tableposition=top]{caption}
\usepackage[a4paper,top=1.5cm,bottom=2cm,left=1.5cm,right=1.5cm,bindingoffset=0mm]{geometry}

\usepackage{placeins,cite}
\usepackage{graphicx}
\usepackage{float}
\usepackage{afterpage}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{multirow}
\usepackage{url}
\usepackage{xcolor}
\usepackage{ulem}
\usepackage{url}
\usepackage{booktabs,multirow}
\usepackage{textcomp}
\graphicspath{{../}{./figures/}}

\makeatletter
\def\thickhline{%
             \noalign{\ifnum0 =`}\fi\hrule \@height \thickarrayrulewidth \futurelet
             \reserved@a\@xthickhline}
\def\@xthickhline{\ifx\reserved@a\thickhline
                \vskip\doublerulesep
                \vskip -\thickarrayrulewidth
                \fi
                \ifnum0 =`{\fi}}
\makeatother
\newlength{\thickarrayrulewidth}
\setlength{\thickarrayrulewidth}{3\arrayrulewidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{shapes.geometric, arrows}
\usetikzlibrary{arrows.meta}
\usepackage{varwidth}
\usepackage{xcolor}
%['#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', '#8c564b', '#e377c2', '#7f7f7f', '#bcbd22', '#17becf']
\definecolor{mtplotlib1}{HTML}{1f77b4}
\definecolor{mtplotlib2}{HTML}{ff7f0e}
\definecolor{mtplotlib3}{HTML}{2ca02c}
\definecolor{mtplotlib4}{HTML}{d62728}

\tikzset{%
  >={Latex[width=2mm,length=2mm]},
  % Specifications for style of nodes:
            base/.style = {rectangle, rounded corners, draw=black,
                           minimum width=4cm, minimum height=1cm,
                           text centered}, %, font=\sffamily},
            mystyle/.style={rectangle, rounded corners, draw=black,
            minimum width=12cm, minimum height=1cm,
            text centered}, %, font=\sffamily},
    col0/.style = {base, fill=white!30},
    col1/.style = {base, fill=mtplotlib1!30},
    col11/.style = {mystyle, fill=mtplotlib1!30},
    col2/.style = {base, fill=mtplotlib2!30},
    col3/.style = {base, fill=mtplotlib3!30},
    col4/.style = {base, minimum width=2.5cm, fill=mtplotlib4!15,}%font=\ttfamily},
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\smallfrac#1#2{\hbox{$\frac{#1}{#2}$}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\ben}{\begin{enumerate}}
\newcommand{\een}{\end{enumerate}}
\newcommand{\la}{\left\langle}
\newcommand{\ra}{\right\rangle}
\newcommand{\lc}{\left[}
\newcommand{\rc}{\right]}
\newcommand{\lp}{\left(}
\newcommand{\rp}{\right)}
\newcommand{\as}{\alpha_s}
\newcommand{\aq}{\alpha_s\left( Q^2 \right)}
\newcommand{\amz}{\alpha_s\left( M_Z^2 \right)}
\newcommand{\aqq}{\alpha_s \left( Q^2_0 \right)}
\newcommand{\aqz}{\alpha_s \left( Q^2_0 \right)}
\def\toinf#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
{#1\rightarrow\infty }}}}
\def\tozero#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
{#1\rightarrow0 }}}}
\def\toone#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
{#1\rightarrow1 }}}}
\def\frac#1#2{{{#1}\over {#2}}}
\def\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
    \raise1pt\hbox{$>$}}}       
\def\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
    \raise1pt\hbox{$<$}}}       
\newcommand{\mrexp}{\mathrm{exp}}
\newcommand{\dat}{\mathrm{dat}}
\newcommand{\one}{\mathrm{(1)}}
\newcommand{\two}{\mathrm{(2)}}
\newcommand{\art}{\mathrm{art}}
\newcommand{\rep}{\mathrm{rep}}
\newcommand{\net}{\mathrm{net}}
\newcommand{\stopp}{\mathrm{stop}}
\newcommand{\sys}{\mathrm{sys}}
\newcommand{\stat}{\mathrm{stat}}
\newcommand{\pdf}{\mathrm{pdf}}
\newcommand{\tot}{\mathrm{tot}}
\newcommand{\minn}{\mathrm{min}}
\newcommand{\mut}{\mathrm{mut}}
\newcommand{\partt}{\mathrm{part}}
\newcommand{\dof}{\mathrm{dof}}
\newcommand{\NS}{\mathrm{NS}}
\newcommand{\cov}{\mathrm{cov}}
\newcommand{\gen}{\mathrm{gen}}
\newcommand{\parr}{\mathrm{par}}
\newcommand{\val}{\mathrm{val}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\checkk}{\mathrm{check}}
\newcommand{\reff}{\mathrm{ref}}
\newcommand{\Mll}{M_{ll}}
\newcommand{\extra}{\mathrm{extra}}
\newcommand{\draft}[1]{}
\newcommand{\comment}[1]{{\bf \it  #1}}
\newcommand{\todo}[1]{\footnote{{\bfseries{\color{red} TODO} #1}}} % For todo's
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}

\numberwithin{equation}{section}
\numberwithin{figure}{section}
\numberwithin{table}{section}

\newcommand{\tmop}[1]{\ensuremath{\operatorname{#1}}}
\newcommand{\tmtextit}[1]{{\itshape{#1}}}
\newcommand{\tmtextrm}[1]{{\rmfamily{#1}}}
\newcommand{\tmtexttt}[1]{{\ttfamily{#1}}}

\usepackage{tabularx}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\DeclareRobustCommand{\RG}[1]{{\color{magenta}\textbf{[RG: #1]}}\xspace}

\definecolor{darkblue}{rgb}{0.0,0,0.5}
\definecolor{darkgreen}{rgb}{0.0,0.3,0.0}
\definecolor{redish}{rgb}{0.675,0,0.2}
\definecolor{red}{rgb}{0.8,0,0}
\definecolor{green}{rgb}{0,0.6,0}
\definecolor{bluish}{rgb}{0.2,0.2,0.675}
\definecolor{mygrey}{rgb}{0.6,0.6,0.6}

\usepackage{tikz} 
\usetikzlibrary{shapes,arrows,positioning,automata,backgrounds,calc,er,patterns,arrows.meta}
\usepackage{tikz-feynman}
\tikzfeynmanset{compat=1.0.0}
\usepackage{varwidth}
\usepackage{xcolor}
%['#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', '#8c564b', '#e377c2', '#7f7f7f', '#bcbd22', '#17becf']
\definecolor{mtplotlib1}{HTML}{1f77b4}
\definecolor{mtplotlib2}{HTML}{ff7f0e}
\definecolor{mtplotlib3}{HTML}{2ca02c}
\definecolor{mtplotlib4}{HTML}{d62728}

\tikzset{%
  >={Latex[width=2mm,length=2mm]},
  % Specifications for style of nodes:
            base/.style = {rectangle, rounded corners, draw=black,
                           minimum width=4cm, minimum height=1cm,
                           text centered}, %, font=\sffamily},
            mystyle/.style={rectangle, rounded corners, draw=black,
            minimum width=12cm, minimum height=1cm,
            text centered}, %, font=\sffamily},
    col0/.style = {base, fill=white!30},
    col1/.style = {base, fill=mtplotlib1!30},
    col11/.style = {mystyle, fill=mtplotlib1!30},
    col2/.style = {base, fill=mtplotlib2!30},
    col3/.style = {base, fill=mtplotlib3!30},
    col4/.style = {base, minimum width=2.5cm, fill=mtplotlib4!15,}%font=\ttfamily},
}

\usepackage{tabularx}
\usepackage{subcaption}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\DeclareRobustCommand{\RG}[1]{{\color{magenta}\textbf{[RG: #1]}}\xspace}

%%%%% raquel: color marks %%%%%
%\usepackage{color} 
\newcommand{\raq}[1]{{\bf\color{orange} #1}}  
%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%% jaco: wider spacing in tables %%%%%
\renewcommand{\arraystretch}{1.7}
\def\lra#1{\overset{\text{\scriptsize$\leftrightarrow$}}{#1}}

\begin{document}
\newgeometry{top=1.5cm,bottom=1.5cm,left=1.5cm,right=1.5cm,bindingoffset=0mm}

\vspace{0.7cm}

\begin{center}
  {\Large \bf FPF WG1: Neutrino Interactions and Hadronic Structure}
\vspace{1.1cm}

\vspace{1.0cm}

{\bf \large Abstract}

\end{center}
Notes to collect the studies
carried out in WG1 of the Forward
Physics Facility study: {\bf  Neutrino Interactions and Hadronic Structure}

\tableofcontents

\section{Recap of DIS kinematics}

The double-differential cross-section for neutrino-nucleus scattering
can be decomposed
in terms of three independent structure functions $F_i^{\nu A}(x,Q^2)$ with $i=1,2,3$.
%
Focusing on the charged-current (CC) scattering case, mediated
by the exchange of a $W^+$ weak boson, the differential
 cross section reads
\be
\label{eq:neutrino_DIS_xsec}
\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/2\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc (1-y)F^{\nu A}_2(x,Q^2) + y^2xF^{\nu A}_1(x,Q^2) + y\lp 1-\frac{y}{2}\rp xF^{\nu A}_3(x,Q^2)\rc  \, ,
\ee
where $s=2m_N E_\nu$ is the neutrino-nucleon center of mass energy squared, $m_N$ is the nucleon mass,
$E_\nu$ is the incoming neutrino energy,
and the inelasticity $y$ is defined as $y=Q^2/(2x m_n E_{\nu})$.
%
For the time being we are neglecting target mass 
corrections.
%
An analogous expression holds for  antineutrino 
scattering, mediated
by the exchange of a $W^-$ weak boson, with the only difference being a sign change
in front of the parity-violating structure function $xF_3$,
\be
\label{eq:antineutrino_DIS_xsec}
\frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/2\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc (1-y)F^{\bar{\nu} A}_2(x,Q^2) + y^2xF^{\bar{\nu} A}_1(x,Q^2) - y\lp 1-\frac{y}{2}\rp xF^{\bar{\nu} A}_3(x,Q^2)\rc  \, .
\ee
While the differential cross-section depends on three kinematic variables, $(x,Q^2,y)$,
the structure functions themselves depend only on $x$ and $Q^2$.
%
Furthermore, both the cross-section and the structure functions depend
on the atomic mass number $A$ of the target nucleus via nuclear modifications of the free-nucleon
structure functions.

Alternatively, Eq.~(\ref{eq:neutrino_DIS_xsec}) can be expressed in terms
of the longitudinal structure function  $F_L^{\nu A}(x,Q^2)$ defined
by $F_L = F_2-2xF_1$, leading to
\be
\label{eq:neutrino_DIS_xsec_FL}
\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\nu A}_2(x,Q^2) - y^2F^{\nu A}_L(x,Q^2) +Y_- xF^{\nu A}_3(x,Q^2)\rc  \, ,
\ee
where $Y_\pm = 1 \pm (1-y)^2$ and with a counterpart expression for anti-neutrino scattering,
\be
\label{eq:antineutrino_DIS_xsec_FL}
\frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\bar{\nu} A}_2(x,Q^2) - y^2F^{\bar{\nu} A}_L(x,Q^2) -Y_- xF^{\bar{\nu} A}_3(x,Q^2)\rc  \, ,
\ee
%
Expressing the differential cross-section as in Eq.~(\ref{eq:neutrino_DIS_xsec_FL}) is advantageous
because in the parton model (and in perturbative QCD at leading order) the longitudinal
structure function vanishes, $F_L^{\nu A}(x,Q^2)=0$.
%
The combination of neutrino and antineutrino measurements makes possible disentangling
the different structure functions, for example the cross-section difference
\be
\label{eq:neutrino_DIS_xsec_FL_diff}
\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} - \frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy}=  \frac{G_F^2s Y_-}
{4\pi \lp 1+Q^2/m_W^2\rp^2}\lc    xF^{\nu A}_3(x,Q^2)+  xF^{\bar{\nu} A}_3(x,Q^2)\rc \, ,
\ee
is proportional to the parity-violating structure function $xF_3$ averaged over neutrinos
and antineutrinos.

When both the momentum transfer squared $Q^2$
and the  hadronic final-state
invariant mass $W$ given by
\be
W^2 = m_N^2 + Q^2 \frac{(1-x)}{x} \, ,
\ee
are large enough, $Q^2 \gsim {\rm few~GeV}^2$ and $W \gsim 2$ GeV
respectively, we find ourselves in the
deep-inelastic scattering region where
structure functions can be evaluated in perturbative QCD in terms of a factorised
convolution of process-dependent partonic scattering cross-sections and
of process-independent parton distribution functions,
\be
\label{eq:sfs_pqcd}
 F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g}\int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \quad i = 2,3,L \, ,
 \ee
 where $j$ is an index that runs over all possible partonic initial states
 and $C_{i,j}^{\nu N}$ is the process-dependent (but target-independent) coefficient function.
 %
 The latter can be expressed  as a series expansion in powers of the strong
 coupling $\alpha_s(Q^2)$,
 \be
 \label{eq:coeff_fun_expansion}
 C_{i,j}^{\nu N}(z,\alpha_s(Q^2)) = \sum_{k=0}^m \lp \alpha_s(Q^2) \rp^{k} C_{i,j}^{\nu N(k)}(z) \, .
 \ee
 The leading-order ($k=0$)  term is independent of $\alpha_s$ since the Born scattering
 is mediated by the weak interaction.
 %
 At leading order and considering a proton target, $n_f=4$ active quark flavours,
 neglecting charm mass effects and assuming a diagonal CKM matrix,
 we can express the $F_2^{\nu p}$ and $xF_3^{\nu p}$ structure functions as
 follows
 \bea
 F_2^{\nu p}(x,Q^2) &=& 2x\lp f_{\bar{u}} + f_{d} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
 F_2^{\bar{\nu} p}(x,Q^2) &=& 2x\lp f_u + f_{\bar{d}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:neutrinoSFs} \\
 xF_3^{\nu p}(x,Q^2) &=& 2x\lp -f_{\bar{u}} + f_d +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
 xF_3^{\bar{\nu} p}(x,Q^2) &=& 2x\lp f_u - f_{\bar{d}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, . \nonumber
 \eea
 The corresponding expressions for a neutron target and or isoscalar target can be obtained
 from isospin symmetry, for instance the LO structure functions for
 neutrino-neutron scattering are
 \bea
 F_2^{\nu n}(x,Q^2) &=& 2x\lp f_{\bar{d}} + f_{u} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
 F_2^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d + f_{\bar{u}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:antineutrinoSFs} \\
 xF_3^{\nu n}(x,Q^2) &=& 2x\lp -f_{\bar{d}} + f_u +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
 xF_3^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d - f_{\bar{u}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, . \nonumber
 \eea

\section{DIS pseudo-data generation}

The first goal is to produce projections
for DIS pseudo-data at the FPF based on
some idealised detector concepts and
some initial choice of neutrino fluxes
e.g.~\cite{Kling:2021gos}.
%
This requires a knowledge of the detector geometry
and material, as well as of the double-differential
neutrino interaction cross-section. 
%
Since we aim to produce pseudo-data binned in $(x,Q^2)$,
for each simulated event we need to determine the 
final-state kinematics.

Specifically, we would like to evaluate the
number of charged-current neutrino interaction events
within the detector volume in different bins
of the incoming neutrino energy $E_\nu$, the Bjorken
variable $x$ and the momentum transfer square $Q^2$,
\begin{equation}
    N_{\rm ev}(E_\nu, x, Q^2) \, ,
\end{equation}
for some binning in these three kinematic variables.
%
This can be evaluated as
\begin{equation}
\label{eq:nev_v1}
    N_{\rm ev}(E_\nu, x, Q^2) =  \frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} \mathcal{L}(E_{\nu}) \, ,
\end{equation}
where $\mathcal{L}(E_{\nu}) $ is the incoming neutrino
luminosity which accounts for the detector geometry
and material density. 
%
Eq.~(\ref{eq:nev_v1}) can be integrated to
determine the actual number of events within
the bin boundaries.

\section{Experimental acceptance performance}

\paragraph{AdvSND} 
\begin{itemize}
    \item The detectors will be able to track muons that have energy greater
    than $20~\rm{GeV}$ (the values for the other charged leptons remain to be
    determined) with an acceptance angle of 100 mrad for the muons and 
    500 mrad for the both electrons and tau.
    \item In addition, the information on the charge of the outgoing leptons
    can also be accessed.
    \item It should also be possible to reconstruct the hadronic final states
    by measuring the total energy.
\end{itemize}

\paragraph{FLArE}
\begin{itemize}
    \item The detectors will be able to detect electrons with energy up to
    $1~\rm{TeV}$ and an acceptance angel as high as 0.5 rad. For the muons,
    the detectors will only be able to track them up to $1.5~\rm{GeV}$ with
    a scattering angle reaching up to 0.4 mrad. The reconstruction of the
    tau's angle and energy instead will be very difficult. However, it might
    be possible to find the vertex of a particular tau decay if fine position
    resolution is achieved.
    \item With the current baseline design of the detector, it will not be
    possible to access the information on the sign of the charged leptons.
    \item It should also be possible to reconstruct the hadronic final
    states but the reconstruction efficiency and particles will depend on
    the type of particles. It is expected that the final states hadrons will
    be dominated by pions, protons, and neutrons.
    \item Regarding the systematic errors on the charged lepton energy and
    scattering angle, it is expected to get $5\%$ energy resolution for
    electrons and about 15 mrad in angular resolution. Due to the large
    missing energy in the detector, $30\%$ energy resolution is probably
    achievable for muons with about 5 mrad angular resolution.
\end{itemize}

\section{Impact in proton PDF fits}

Once we have generated pseudo-data for the 
neutrino DIS charged-current structure functions
in bins of $(x,Q^2,y)$, and assuming that uncertainties
are purely of statistical origin, we can assess their
impact on proton PDFs.
%
At a first step we neglect nuclear effects
and treat data as corresponding to a free isoscalar
nucleon with $A=1$.

\section{Impact in nuclear PDF fits}

Next we account for the nuclear dependence of
the measured neutrino structure functions.

\section{Description of the $\nu$FPF codes}

The part that computes the differential cross sections is taken care by the python
package $\nu$FPF. By default, it computes the HERA cross section defined as
\begin{equation}
    \frac{d^2\tilde{\sigma}^{A}}{dxdy} \lp x,Q^2,y \rp =  \frac{1}{2}\lc (1-y)F^{\nu A}_2(x,Q^2) + y^2xF^{\nu A}_1(x,Q^2)
    + (-1)^\ell  y\lp 1-\frac{y}{2}\rp xF^{\nu A}_3(x,Q^2)\rc ,
\end{equation}
where $\ell = 0$ for leptons and $\ell = 1$ for anti-leptons. Thus, in order to compare with 
Eq.~\ref{eq:neutrino_DIS_xsec} one needs to multiply the above equation with $G_F^2s/2 \pi (1 + Q^2/m^2_W)^2$.

\bibliographystyle{utphys}
\bibliography{FPF-WG1}

\end{document}

### 2023-02-01 paper/FPF-WG1.tex
title
Update FPF-WG1.tex
Updated notes on pseudo-data event generation

@@
 \begin{center}
-  {\Large \bf FPF WG1: Neutrino Interactions and Hadronic Structure}
+  {\Large \bf Deep-Inelastic Scattering with TeV Neutrinos at the LHC}
 \vspace{1.1cm}
@@
 
+\newline
+\newline
+We start with a perfect detector.
+\newline
+\newline
+For bins in $x,Q^2,E_{\nu}$, we start with the \href{https://github.com/juanrojochacon/FPF-WG1/blob/main/results/diff_xsecs_a1.txt}{differential cross section},$\frac{d^2\sigma(x,Q^2,E_{\nu}}{dxdQ^2})$ [pb GeV$^{-2}$] as output from {\tt YADISM} and convovle with the \href{https://github.com/KlingFelix/FastNeutrinoFluxSimulation/tree/main/Fluxes}{neutrino flux}, $\frac{dN_{\nu}}{dE_{\nu}}$.
+So for a detector with $n_T$ nuclear target density and $L_T$ length, we calculate the event rate per bin as
+
+\begin{equation}
+    N_{\rm ev}/{\rm bin} = n_T L_T\int_{Q^2_{min}}^{Q^2_{max}}\int_{x_{min}}^{x_{max}}\int_{E_{\nu,min}}^{E_{\nu , max}} \frac{dN_{\nu}}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) dQ^2 dx dE_{\nu}.
+\end{equation}
+
+Using a MC integration, we can calculate $N_{\rm ev}/{\rm bin}$ by sampling $N$ points in $x,Q^2,E_{\nu}$ space such that $0< y = \frac{Q^2}{2m_N E_{\nu }x} < 1$ and integrating over the bin.
+
+\begin{equation}
+    N_{\rm ev}/{\rm bin} \approx n_T L_T \frac{(Q^2_{max}-Q^2_{min})(x_{max}-x_{min})(E_{\nu ,max}-E_{\nu ,min})}{N}\times \sum_i^N f(x_i,Q^2_i,E_{\nu ,i})
+\end{equation}
+
+where $f(x_i,Q^2_i,E_{\nu ,i}) = \frac{dN_{\nu}}{dE_{\nu,i}}\left(\frac{d^2\sigma(x_i,Q^2_i,E_{\nu,i})}{dxdQ^2}\right)$.
+
+The statistical uncertainty for each bin is then defined by a gaussian distribution with fractional uncertainty $1/\sqrt{N{\rm ev}/{\rm bin}}$, i.e.
+$\delta N_{\rm ev}/{\rm bin} = \sqrt{N_{\rm ev} /{\rm bin}$
+\newline
+Following this prescription, we can produce plots which characterize the event rate for a particular neutrino species at a particular experiment.
+
+Results for FASER$\nu$2 can be found \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results}{here}.
+The .txt files will display which neutrino species was considered, and also compile experimental geometries and target details in the header.
+In the subfolder \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results/Summaries}{summaries}, plots can be found which show the event rate in $x,Q^2$ space, integrating over the entire neutrino spectrum.
+The event rate for muon neutrinos at FASER$\nu$2 is shown in Fig~\ref{fig:fasernu2_muon}.
+
+\begin{figure}[h]
+    \centering
+\includegraphics[width=1\textwidth]{Nevent_FASERv2_14.pdf}
+    \caption{Event rate per bin for muon neutrinos at FASER$\nu$2.
+Bins are denoted by dashed grid, and the red dot indicates the weighted average of $x,Q^2$ points in each bin.
+The total number of muon neutrino events calculated is $\approx2.6\times 10^5$.
+Note that bins were chosen somewhat arbitrarily, and can be iterated to improve PDF fits }
+    \label{fig:fasernu2_muon}
+\end{figure}
+
 \section{Experimental acceptance performance}

### 2023-02-09 paper/FPF-WG1.tex
Added proton PDF profiling

@@
 \section{DIS pseudo-data generation}
+\label{sec:pseudo-data_generation}
 
@@
 
+The expected impact of the FPF data on global PDF fits is assessed by a profiling procedure~\cite{Paukkunen:2014zia, Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre}, based on minimizing the function
+%TODO correlations are also included here, as we hopefully get there in the end -- if not, remove terms involving correlations+pseudodata
+\begin{equation}
+\chi^2 = 
+\sum_{i=1}^{N_{\textrm{bins}}} 
+\frac{\left(  \sigma_i^{\textrm{pd}}
+            + \Gamma_i^{\alpha,\textrm{pd}}
+              b_\alpha^{\textrm{pd}}
+            - \sigma_i^{\textrm{th}}
+            - \Gamma_i^{\beta,\textrm{th}}
+              b_\beta^{\textrm{th}}
+     \right)^2
+     }{\Delta_i^2}
++ \sum_\alpha (b_\alpha^{\textrm{pd}})^2
++ \sum_\beta  (b_\beta^{\textrm{th}})^2 \, .
+\label{eq:profilingchi2}
+\end{equation}
+Here the pseudodata 
+$\sigma_i^{\textrm{pd}}$ 
+is obtained from the central theoretical prediction 
+$\sigma_i^{\textrm{th}}$ 
+for each bin $i$ out of $N_{\textrm{bins}}$ by varying it with the statistical uncertainties 
+$\delta_i^{\textrm{stat}}$, 
+obtained in the procedure desribed in Section~\ref{sec:pseudo-data_generation}, 
+as 
+%TODO once more complete uncertainty estimates are there, add them to the variation
+$\sigma_i^{\textrm{pd}} = \sigma_i^{\textrm{th}}(1 + r_i \delta_i^{\textrm{stat}})$, 
+with $r_i$ a univariate Gaussian random number.
+%
+The correlated uncertainties for the pseudodata and the theoretical prediction 
+are contained in the nuisance parameter vectors $b^{\textrm{pd}}$ and $b^{\textrm{th}}$, respectively, and the uncorrelated uncertainties in $\Delta_i$.
+%
+Their effect on $\sigma^{\textrm{th}}$ and $\sigma^{\textrm{pd}}$
+is described by the matrices $\Gamma_i^{\textrm{pd}}$ and $\Gamma_i^{\textrm{th}}$.
+The indices $\alpha$ and $\beta$ then run over the uncertainty nuisance parameters for the pseudodata and the theoretical prediction, respectively.
+%
+The nuisance parameter values $b^{\textrm{th(min)}}$ that minimize Eq.~\eqref{eq:profilingchi2} give the central PDFs $f'_0$ optimized to the profiled dataset in the form
+\begin{equation}
+f_0' = f_0
+      + \sum_\beta b_\beta^{\textrm{th(min)}} 
+        \left(  \frac{f_\beta^+   -  f_\beta^- }{2}
+              -    b_\beta^{\textrm{th(min)}}
+                \frac{f_\beta^+ + f_\beta^- - 2f_0}{2}
+        \right),
+\end{equation}
+where $f_0$ is the original central PDF and the up and down variation eigenvectors are given by $f^+, f^-$.
+The decrease in the uncertainties of the shifted PDFs indicates the enhancement that including the FPF data in the global PDF fit could bring.
+Here, the profiling studies are performed using version 2.2.1 of the \textsc{xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}, extended to support the use of \textsc{PineAPPL} grids~\cite{christopher_schwan_2023_7499507, Carrazza:2020gss}.
+%
+Using the PDF4LHC21~\cite{PDF4LHCWorkingGroup:2022cjn} PDF set, the results are illustrated by comparing the fractional uncertainties of the original PDF set to those obtained after profiling. 
+This is shown for the valence quark, gluon and the singlet distributions in Fig.~\ref{FASERv2_profiling} for FASER$\nu$2 pseudodata, while Fig.~\ref{FASERv_profiling} indicates the impact of FASER$\nu$.
+FASER$\nu$2 is observed to provide tighter constraints on the PDFs, with the effects being the most prominent for the valence and sea quark distributions.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
+\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\caption{The fractional uncertainties in the valence quark, gluon and singlet PDFs as a function of the momentum fraction $x$ at the scale $Q^2 = 10000 \, \textrm{GeV}^2$.
+The profiling is performed using the
+PDF4LHC21 set and the pseudodata for FASER$\nu$2. The original uncertainty of PDF4LHC21 is
+indicated by the red band, while the blue band demonstrates the profiled result.}
+\label{FASERv2_profiling}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_dv_ratio.pdf}\\
+\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_Sea_ratio.pdf}
+\caption{The fractional uncertainties in the valence quark, gluon and singlet PDFs as a function of the momentum fraction $x$ at the scale $Q^2 = 10000 \, \textrm{GeV}^2$.
+The profiling is performed using the
+PDF4LHC21 set and the pseudodata for FASER$\nu$. The original uncertainty of PDF4LHC21 is
+indicated by the red band, while the blue band demonstrates the profiled result.}
+\label{FASERv_profiling}
+\end{figure}
+
 \section{Impact in nuclear PDF fits}

### 2023-02-17 paper/FPF-WG1.tex

@@
     N_{\rm ev}/{\rm bin} \approx n_T L_T \frac{(Q^2_{max}-Q^2_{min})(x_{max}-x_{min})(E_{\nu ,max}-E_{\nu ,min})}{N}\times \sum_i^N f(x_i,Q^2_i,E_{\nu ,i})
+    \label{MCintegration}
 \end{equation}
@@
     \label{fig:fasernu2_muon}
+\end{figure}
+
+\subsection{Systematic Effects on Pseudodata}
+We now wish to understand the impact of systematic uncertainties on the event rate in $(x,Q^2,E_{\nu})$ space.
+For each experiment, the observables $E_{l},E_{h},\theta$ are related to $(x,Q^2,E_{\nu})$ by
+
+\begin{align}
+E_{\nu} = E_l + E_h \nonumber \\
+Q^2 = 4E_lE_{\nu}\sin^2{\theta/2} \nonumber \\
+x = \frac{Q^2}{2m_N(E_{\nu} - E_l)}.
+\end{align}
+
+We wish to sample over the space of observables, $(E_{l},E_{h},\theta)$, perform  cuts based on detector performance, calculate the event rates, and then smear this sampling according to experimental uncertainties to estimate the uncertainty on the event rate.
+
+Taking FASER${\nu}$2 as an example, we can write the experimental cuts and uncertainties as
+
+\begin{align}
+100 < E_l < E_{\nu,{\rm max}} , \delta E_l = 30\% \nonumber \\
+100 < E_h < E_{\nu,{\rm max}} , \delta E_h = 50\% \nonumber \\
+0 < \theta < \tan^{-1}(0.5) , \delta\theta = 1~{\rm mrad}
+\label{fasernu2systematic_errors}
+\end{align}
+
+We first generate a MC dataset, $D_0$, over this space with $N = 10^7$ samples and calculate $x,Q^2,E_{\nu}$ for each event, removing samples with $y > 1$.
+We then integrate according to Eq.
+\ref{MCintegration} to produce a distribution of events with bins in $x,Q^2,E_{\nu}$.
+We then smear each sample according to a gaussian distribution with widths given by Eq.~\ref{fasernu2systematic_errors} to produce a new data set $D_i$ and repeat to produce $M = 10$ event distributions($M>10$ can later be used, but $M = 10$ appears to be stable).
+For each bin we take the standard deviation to produce the systematic errors per bin (denoted as "N\textunderscore sys\textunderscore errs" in files named "binned\textunderscore sysevents...
+.txt" \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results}{here}).
+
+For FASER${\nu}$2, the systematic erros typically dominate over statsitcal errors, at about $10\%$.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width = 1\textwidth]{error_plot_FASERv2_14.pdf}
+    \caption{Event rates with errorbars at FASER$\nu$2 for $\nu_{\mu} N \rightarrow \mu^- X$} summed over $Q^2$.
+The errobars along the x-axis showing the width of the $x$-bins, and are not showing any type of error.
+    \label{fig:my_label}
 \end{figure}

### 2023-03-13 paper/FPF-WG1.tex
added abstract

@@
 \begin{center}
-  {\Large \bf Deep-Inelastic Scattering with TeV Neutrinos at the LHC}
+  {\Large \bf The LHC as a Neutrino-Ion Collider }\\
   \vspace{1.1cm}
+  {\small
+Max Fieg$^{1}$, Tommaso Giani$^{2,3}$, Peter Krack$^{2,3}$  Giacomo Magni$^{2,3}$, \\[0.1cm] Toni Makela$^{4}$,
+    Tanjona Rabemananjara$^{2,3}$, and Juan Rojo$^{2,3}$, 
+  }\\
+
+\vspace{0.7cm}
+
+{\it \small
+	~$^1$ UC Irvine  \\[0.1cm]
+ 	~$^2$Department of Physics and Astronomy, Vrije Universiteit, NL-1081 HV Amsterdam\\[0.1cm]
+  	~$^3$Nikhef Theory Group, Science Park 105, 1098 XG Amsterdam, The Netherlands\\[0.1cm]
+        ~$^4$ IPJ \\[0.1cm]
+ }
 
@@
 \end{center}
-Notes to collect the studies
-carried out in WG1 of the Forward
-Physics Facility study: {\bf  Neutrino Interactions and Hadronic Structure}
+
+Proton-proton collisions at the LHC produce a collimated beam large flux of high-energy neutrinos,
+which until recently escaped detection and hence we not used for physics.
+%
+Detection and analysis of these far-forward LHC neutrinos is taking now place at the
+FASER$\nu$ and SND@LHC experiments, and would be uniquely scrutinized
+at the proposed Forward Physics Facility (FPF).
+%
+In this work we demonstrate that exploiting this high-energy far-forward neutrino beam
+provides new constraints on the quark and gluon substructure of nucleons and nuclei.
+%
+We generate projections for inclusive and charm (dimuon)
+deep-inelastic scattering (DIS) structure functions
+at cross-sections for all ongoing and planned far-forward LHC neutrinos experiments,
+including the expected systematic uncertainties.
+%
+By means of both the xFitter and NNPDF frameworks we quantify the impact of the FPF
+measurements on proton and nuclear structure, showing stringent constraints specially
+in quark flavour separation.
+%
+Our analysis demonstrates that instrumenting the far-forward region to exploit the HL-LHC
+neutrino fluxes effectively realises a  Neutrino-Ion Collider with
+center of mass  energy around 100 GeV at CERN, fully complementary
+and operating concurrently to the
+Electron-Ion Collider in the US.
 
@@
 
-\newline
-\newline
 We start with a perfect detector.
-\newline
-\newline
-For bins in $x,Q^2,E_{\nu}$, we start with the \href{https://github.com/juanrojochacon/FPF-WG1/blob/main/results/diff_xsecs_a1.txt}{differential cross section},$\frac{d^2\sigma(x,Q^2,E_{\nu}}{dxdQ^2})$ [pb GeV$^{-2}$] as output from {\tt YADISM} and convovle with the \href{https://github.com/KlingFelix/FastNeutrinoFluxSimulation/tree/main/Fluxes}{neutrino flux}, $\frac{dN_{\nu}}{dE_{\nu}}$.
+
+For bins in $x,Q^2,E_{\nu}$, we start with the \href{https://github.com/juanrojochacon/FPF-WG1/blob/main/results/diff_xsecs_a1.txt}{differential cross section},$\frac{d^2\sigma(x,Q^2,E_{\nu}}{dxdQ^2})$ [pb GeV$^{-2}$] as output from {\tt YADISM} and convolve with the \href{https://github.com/KlingFelix/FastNeutrinoFluxSimulation/tree/main/Fluxes}{neutrino flux}, $\frac{dN_{\nu}}{dE_{\nu}}$.
 So for a detector with $n_T$ nuclear target density and $L_T$ length, we calculate the event rate per bin as
@@
 
-The statistical uncertainty for each bin is then defined by a gaussian distribution with fractional uncertainty $1/\sqrt{N{\rm ev}/{\rm bin}}$, i.e.
-$\delta N_{\rm ev}/{\rm bin} = \sqrt{N_{\rm ev} /{\rm bin}$
-\newline
+The statistical uncertainty for each bin is then defined by a Gaussian distribution with fractional uncertainty $1/\sqrt{N{\rm ev}/{\rm bin}}$, i.e.
+$\delta N_{\rm ev}/{\rm bin} = \sqrt{N_{\rm ev}} /{\rm bin}$
+
   Following this prescription, we can produce plots which characterize the event rate for a particular neutrino species at a particular experiment.
@@
 The .txt files will display which neutrino species was considered, and also compile experimental geometries and target details in the header.
-In the subfolder \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results/Summaries}{summaries}, plots can be found which show the event rate in $x,Q^2$ space, integrating over the entire neutrino spectrum.
+In the sub-folder \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results/Summaries}{summaries}, plots can be found which show the event rate in $x,Q^2$ space, integrating over the entire neutrino spectrum.
 The event rate for muon neutrinos at FASER$\nu$2 is shown in Fig~\ref{fig:fasernu2_muon}.
@@
 \ref{MCintegration} to produce a distribution of events with bins in $x,Q^2,E_{\nu}$.
-We then smear each sample according to a gaussian distribution with widths given by Eq.~\ref{fasernu2systematic_errors} to produce a new data set $D_i$ and repeat to produce $M = 10$ event distributions($M>10$ can later be used, but $M = 10$ appears to be stable).
-For each bin we take the standard deviation to produce the systematic errors per bin (denoted as "N\textunderscore sys\textunderscore errs" in files named "binned\textunderscore sysevents...
+We then smear each sample according to a Gaussian distribution with widths given by Eq.~\ref{fasernu2systematic_errors} to produce a new data set $D_i$ and repeat to produce $M = 10$ event distributions($M>10$ can later be used, but $M = 10$ appears to be stable).
+For each bin we take the standard deviation to produce the systematic errors per bin (denoted as "N\textunderscore sys\textunderscore errs" in files named "binned\textunderscore sys-events...
 .txt" \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results}{here}).
 
-For FASER${\nu}$2, the systematic erros typically dominate over statsitcal errors, at about $10\%$.
+For FASER${\nu}$2, the systematic errors typically dominate over statistical errors, at about $10\%$.
 
@@
     \includegraphics[width = 1\textwidth]{error_plot_FASERv2_14.pdf}
-    \caption{Event rates with errorbars at FASER$\nu$2 for $\nu_{\mu} N \rightarrow \mu^- X$} summed over $Q^2$.
-The errobars along the x-axis showing the width of the $x$-bins, and are not showing any type of error.
+    \caption{Event rates with error bars at FASER$\nu$2 for $\nu_{\mu} N \rightarrow \mu^- X$} summed over $Q^2$.
+The error bars along the x-axis showing the width of the $x$-bins, and are not showing any type of error.
     \label{fig:my_label}
@@
 $\delta_i^{\textrm{stat}}$, 
-obtained in the procedure desribed in Section~\ref{sec:pseudo-data_generation}, 
+obtained in the procedure described in Section~\ref{sec:pseudo-data_generation}, 
 as 

### 2023-03-13 paper/FPF-WG1.tex
Toni: added institute and last name umlauts

@@
   {\small
-Max Fieg$^{1}$, Tommaso Giani$^{2,3}$, Peter Krack$^{2,3}$  Giacomo Magni$^{2,3}$, \\[0.1cm] Toni Makela$^{4}$,
+Max Fieg$^{1}$, Tommaso Giani$^{2,3}$, Peter Krack$^{2,3}$  Giacomo Magni$^{2,3}$, \\[0.1cm] Toni M\"akel\"a$^{4}$,
     Tanjona Rabemananjara$^{2,3}$, and Juan Rojo$^{2,3}$, 
@@
     ~$^3$Nikhef Theory Group, Science Park 105, 1098 XG Amsterdam, The Netherlands\\[0.1cm]
-        ~$^4$ IPJ \\[0.1cm]
+    ~$^4$National Centre for Nuclear Research, Pasteura 7, Warsaw, PL-02-093, Poland \\[0.1cm]
  }

### 2023-05-09 paper/sec-dis-pseudodata.tex
added structure to paper

--- 2023-03-13 paper/FPF-WG1.tex
@@
-\documentclass[11pt,a4paper]{article}
-\pdfoutput=1
+\clearpage
+\section{Projections for LHC neutrino structure functions}
+\label{sec:dis_pseudodata}
 
-\usepackage[colorlinks=true, linkcolor=black!50!blue, urlcolor=blue, citecolor=blue, anchorcolor=blue]{hyperref}
-\usepackage[font=small,labelfont=bf,margin=0mm,labelsep=period,tableposition=top]{caption}
-\usepackage[a4paper,top=1.5cm,bottom=2cm,left=1.5cm,right=1.5cm,bindingoffset=0mm]{geometry}
+We begin by describing the procedure adopted to generate
+projections for LHC neutrino DIS structure functions, including
+the models for the expected systematic uncertainties associated
+to the various experiments.
 
-\usepackage{placeins,cite}
-\usepackage{graphicx}
-\usepackage{float}
-\usepackage{afterpage}
-\usepackage{epsfig}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{bm}
-\usepackage{multirow}
-\usepackage{url}
-\usepackage{xcolor}
-\usepackage{ulem}
-\usepackage{url}
-\usepackage{booktabs,multirow}
-\usepackage{textcomp}
-\graphicspath{{../}{./figures/}}
-
-\makeatletter
-\def\thickhline{%
-             \noalign{\ifnum0 =`}\fi\hrule \@height \thickarrayrulewidth \futurelet
-             \reserved@a\@xthickhline}
-\def\@xthickhline{\ifx\reserved@a\thickhline
-                \vskip\doublerulesep
-                \vskip -\thickarrayrulewidth
-                \fi
-                \ifnum0 =`{\fi}}
-\makeatother
-\newlength{\thickarrayrulewidth}
-\setlength{\thickarrayrulewidth}{3\arrayrulewidth}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{tikz}
-\usetikzlibrary{positioning}
-\usetikzlibrary{shapes.geometric, arrows}
-\usetikzlibrary{arrows.meta}
-\usepackage{varwidth}
-\usepackage{xcolor}
-%['#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', '#8c564b', '#e377c2', '#7f7f7f', '#bcbd22', '#17becf']
-\definecolor{mtplotlib1}{HTML}{1f77b4}
-\definecolor{mtplotlib2}{HTML}{ff7f0e}
-\definecolor{mtplotlib3}{HTML}{2ca02c}
-\definecolor{mtplotlib4}{HTML}{d62728}
-
-\tikzset{%
-  >={Latex[width=2mm,length=2mm]},
-  % Specifications for style of nodes:
-            base/.style = {rectangle, rounded corners, draw=black,
-                           minimum width=4cm, minimum height=1cm,
-                           text centered}, %, font=\sffamily},
-            mystyle/.style={rectangle, rounded corners, draw=black,
-            minimum width=12cm, minimum height=1cm,
-            text centered}, %, font=\sffamily},
-    col0/.style = {base, fill=white!30},
-    col1/.style = {base, fill=mtplotlib1!30},
-    col11/.style = {mystyle, fill=mtplotlib1!30},
-    col2/.style = {base, fill=mtplotlib2!30},
-    col3/.style = {base, fill=mtplotlib3!30},
-    col4/.style = {base, minimum width=2.5cm, fill=mtplotlib4!15,}%font=\ttfamily},
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\def\smallfrac#1#2{\hbox{$\frac{#1}{#2}$}}
-\newcommand{\be}{\begin{equation}}
-\newcommand{\ee}{\end{equation}}
-\newcommand{\bea}{\begin{eqnarray}}
-\newcommand{\eea}{\end{eqnarray}}
-\newcommand{\bi}{\begin{itemize}}
-\newcommand{\ei}{\end{itemize}}
-\newcommand{\ben}{\begin{enumerate}}
-\newcommand{\een}{\end{enumerate}}
-\newcommand{\la}{\left\langle}
-\newcommand{\ra}{\right\rangle}
-\newcommand{\lc}{\left[}
-\newcommand{\rc}{\right]}
-\newcommand{\lp}{\left(}
-\newcommand{\rp}{\right)}
-\newcommand{\as}{\alpha_s}
-\newcommand{\aq}{\alpha_s\left( Q^2 \right)}
-\newcommand{\amz}{\alpha_s\left( M_Z^2 \right)}
-\newcommand{\aqq}{\alpha_s \left( Q^2_0 \right)}
-\newcommand{\aqz}{\alpha_s \left( Q^2_0 \right)}
-\def\toinf#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
-{#1\rightarrow\infty }}}}
-\def\tozero#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
-{#1\rightarrow0 }}}}
-\def\toone#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
-{#1\rightarrow1 }}}}
-\def\frac#1#2{{{#1}\over {#2}}}
-\def\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
-    \raise1pt\hbox{$>$}}}       
-\def\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
-    \raise1pt\hbox{$<$}}}       
-\newcommand{\mrexp}{\mathrm{exp}}
-\newcommand{\dat}{\mathrm{dat}}
-\newcommand{\one}{\mathrm{(1)}}
-\newcommand{\two}{\mathrm{(2)}}
-\newcommand{\art}{\mathrm{art}}
-\newcommand{\rep}{\mathrm{rep}}
-\newcommand{\net}{\mathrm{net}}
-\newcommand{\stopp}{\mathrm{stop}}
-\newcommand{\sys}{\mathrm{sys}}
-\newcommand{\stat}{\mathrm{stat}}
-\newcommand{\pdf}{\mathrm{pdf}}
-\newcommand{\tot}{\mathrm{tot}}
-\newcommand{\minn}{\mathrm{min}}
-\newcommand{\mut}{\mathrm{mut}}
-\newcommand{\partt}{\mathrm{part}}
-\newcommand{\dof}{\mathrm{dof}}
-\newcommand{\NS}{\mathrm{NS}}
-\newcommand{\cov}{\mathrm{cov}}
-\newcommand{\gen}{\mathrm{gen}}
-\newcommand{\parr}{\mathrm{par}}
-\newcommand{\val}{\mathrm{val}}
-\newcommand{\tr}{\mathrm{tr}}
-\newcommand{\checkk}{\mathrm{check}}
-\newcommand{\reff}{\mathrm{ref}}
-\newcommand{\Mll}{M_{ll}}
-\newcommand{\extra}{\mathrm{extra}}
-\newcommand{\draft}[1]{}
-\newcommand{\comment}[1]{{\bf \it  #1}}
-\newcommand{\todo}[1]{\footnote{{\bfseries{\color{red} TODO} #1}}} % For todo's
-\def\beq{\begin{equation}}
-\def\eeq{\end{equation}}
-
-\numberwithin{equation}{section}
-\numberwithin{figure}{section}
-\numberwithin{table}{section}
-
-\newcommand{\tmop}[1]{\ensuremath{\operatorname{#1}}}
-\newcommand{\tmtextit}[1]{{\itshape{#1}}}
-\newcommand{\tmtextrm}[1]{{\rmfamily{#1}}}
-\newcommand{\tmtexttt}[1]{{\ttfamily{#1}}}
-
-\usepackage{tabularx}
-\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
-\DeclareRobustCommand{\RG}[1]{{\color{magenta}\textbf{[RG: #1]}}\xspace}
-
-\definecolor{darkblue}{rgb}{0.0,0,0.5}
-\definecolor{darkgreen}{rgb}{0.0,0.3,0.0}
-\definecolor{redish}{rgb}{0.675,0,0.2}
-\definecolor{red}{rgb}{0.8,0,0}
-\definecolor{green}{rgb}{0,0.6,0}
-\definecolor{bluish}{rgb}{0.2,0.2,0.675}
-\definecolor{mygrey}{rgb}{0.6,0.6,0.6}
-
-\usepackage{tikz} 
-\usetikzlibrary{shapes,arrows,positioning,automata,backgrounds,calc,er,patterns,arrows.meta}
-\usepackage{tikz-feynman}
-\tikzfeynmanset{compat=1.0.0}
-\usepackage{varwidth}
-\usepackage{xcolor}
-%['#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', '#8c564b', '#e377c2', '#7f7f7f', '#bcbd22', '#17becf']
-\definecolor{mtplotlib1}{HTML}{1f77b4}
-\definecolor{mtplotlib2}{HTML}{ff7f0e}
-\definecolor{mtplotlib3}{HTML}{2ca02c}
-\definecolor{mtplotlib4}{HTML}{d62728}
-
-\tikzset{%
-  >={Latex[width=2mm,length=2mm]},
-  % Specifications for style of nodes:
-            base/.style = {rectangle, rounded corners, draw=black,
-                           minimum width=4cm, minimum height=1cm,
-                           text centered}, %, font=\sffamily},
-            mystyle/.style={rectangle, rounded corners, draw=black,
-            minimum width=12cm, minimum height=1cm,
-            text centered}, %, font=\sffamily},
-    col0/.style = {base, fill=white!30},
-    col1/.style = {base, fill=mtplotlib1!30},
-    col11/.style = {mystyle, fill=mtplotlib1!30},
-    col2/.style = {base, fill=mtplotlib2!30},
-    col3/.style = {base, fill=mtplotlib3!30},
-    col4/.style = {base, minimum width=2.5cm, fill=mtplotlib4!15,}%font=\ttfamily},
-}
-
-\usepackage{tabularx}
-\usepackage{subcaption}
-\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
-\DeclareRobustCommand{\RG}[1]{{\color{magenta}\textbf{[RG: #1]}}\xspace}
-
-%%%%% raquel: color marks %%%%%
-%\usepackage{color} 
-\newcommand{\raq}[1]{{\bf\color{orange} #1}}  
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%% jaco: wider spacing in tables %%%%%
-\renewcommand{\arraystretch}{1.7}
-\def\lra#1{\overset{\text{\scriptsize$\leftrightarrow$}}{#1}}
-
-\begin{document}
-\newgeometry{top=1.5cm,bottom=1.5cm,left=1.5cm,right=1.5cm,bindingoffset=0mm}
-
-\vspace{0.7cm}
-
-\begin{center}
-  {\Large \bf The LHC as a Neutrino-Ion Collider }\\
-  \vspace{1.1cm}
-  {\small
-Max Fieg$^{1}$, Tommaso Giani$^{2,3}$, Peter Krack$^{2,3}$  Giacomo Magni$^{2,3}$, \\[0.1cm] Toni Makela$^{4}$,
-    Tanjona Rabemananjara$^{2,3}$, and Juan Rojo$^{2,3}$, 
-  }\\
-
-\vspace{0.7cm}
-
-{\it \small
-	~$^1$ UC Irvine  \\[0.1cm]
- 	~$^2$Department of Physics and Astronomy, Vrije Universiteit, NL-1081 HV Amsterdam\\[0.1cm]
-  	~$^3$Nikhef Theory Group, Science Park 105, 1098 XG Amsterdam, The Netherlands\\[0.1cm]
-        ~$^4$ IPJ \\[0.1cm]
- }
-
-\vspace{1.0cm}
-
-{\bf \large Abstract}
-
-\end{center}
-
-Proton-proton collisions at the LHC produce a collimated beam large flux of high-energy neutrinos,
-which until recently escaped detection and hence we not used for physics.
-%
-Detection and analysis of these far-forward LHC neutrinos is taking now place at the
-FASER$\nu$ and SND@LHC experiments, and would be uniquely scrutinized
-at the proposed Forward Physics Facility (FPF).
-%
-In this work we demonstrate that exploiting this high-energy far-forward neutrino beam
-provides new constraints on the quark and gluon substructure of nucleons and nuclei.
-%
-We generate projections for inclusive and charm (dimuon)
-deep-inelastic scattering (DIS) structure functions
-at cross-sections for all ongoing and planned far-forward LHC neutrinos experiments,
-including the expected systematic uncertainties.
-%
-By means of both the xFitter and NNPDF frameworks we quantify the impact of the FPF
-measurements on proton and nuclear structure, showing stringent constraints specially
-in quark flavour separation.
-%
-Our analysis demonstrates that instrumenting the far-forward region to exploit the HL-LHC
-neutrino fluxes effectively realises a  Neutrino-Ion Collider with
-center of mass  energy around 100 GeV at CERN, fully complementary
-and operating concurrently to the
-Electron-Ion Collider in the US.
-
-\tableofcontents
-
-\section{Recap of DIS kinematics}
+\subsection{Recap of DIS kinematics}
 
@@
 
-\section{DIS pseudo-data generation}
+\subsection{DIS pseudo-data generation}
 \label{sec:pseudo-data_generation}
@@
 \label{eq:nev_v1}
-    N_{\rm ev}(E_\nu, x, Q^2) =  \frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} \mathcal{L}(E_{\nu}) \, ,
+    N_{\rm ev}(E_\nu, x, Q^2) \propto \int_{\rm bin}\int_{\rm det}  \frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} \mathcal{L}_{\nu}(E_{\nu}) \, ,
 \end{equation}
@@
     \centering
-\includegraphics[width=1\textwidth]{Nevent_FASERv2_14.pdf}
+\includegraphics[width=1\textwidth]{plots/Nevent_FASERv2_14.pdf}
     \caption{Event rate per bin for muon neutrinos at FASER$\nu$2.
@@
     \centering
-    \includegraphics[width = 1\textwidth]{error_plot_FASERv2_14.pdf}
+    \includegraphics[width = 1\textwidth]{plots/error_plot_FASERv2_14.pdf}
     \caption{Event rates with error bars at FASER$\nu$2 for $\nu_{\mu} N \rightarrow \mu^- X$} summed over $Q^2$.
@@
 
-\section{Experimental acceptance performance}
+\subsection{Experimental acceptance performance}
 
@@
 \end{itemize}
-
-\section{Impact in proton PDF fits}
-
-Once we have generated pseudo-data for the 
-neutrino DIS charged-current structure functions
-in bins of $(x,Q^2,y)$, and assuming that uncertainties
-are purely of statistical origin, we can assess their
-impact on proton PDFs.
-%
-At a first step we neglect nuclear effects
-and treat data as corresponding to a free isoscalar
-nucleon with $A=1$.
-
-The expected impact of the FPF data on global PDF fits is assessed by a profiling procedure~\cite{Paukkunen:2014zia, Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre}, based on minimizing the function
-%TODO correlations are also included here, as we hopefully get there in the end -- if not, remove terms involving correlations+pseudodata
-\begin{equation}
-\chi^2 = 
-\sum_{i=1}^{N_{\textrm{bins}}} 
-\frac{\left(  \sigma_i^{\textrm{pd}}
-            + \Gamma_i^{\alpha,\textrm{pd}}
-              b_\alpha^{\textrm{pd}}
-            - \sigma_i^{\textrm{th}}
-            - \Gamma_i^{\beta,\textrm{th}}
-              b_\beta^{\textrm{th}}
-     \right)^2
-     }{\Delta_i^2}
-+ \sum_\alpha (b_\alpha^{\textrm{pd}})^2
-+ \sum_\beta  (b_\beta^{\textrm{th}})^2 \, .
-\label{eq:profilingchi2}
-\end{equation}
-Here the pseudodata 
-$\sigma_i^{\textrm{pd}}$ 
-is obtained from the central theoretical prediction 
-$\sigma_i^{\textrm{th}}$ 
-for each bin $i$ out of $N_{\textrm{bins}}$ by varying it with the statistical uncertainties 
-$\delta_i^{\textrm{stat}}$, 
-obtained in the procedure described in Section~\ref{sec:pseudo-data_generation}, 
-as 
-%TODO once more complete uncertainty estimates are there, add them to the variation
-$\sigma_i^{\textrm{pd}} = \sigma_i^{\textrm{th}}(1 + r_i \delta_i^{\textrm{stat}})$, 
-with $r_i$ a univariate Gaussian random number.
-%
-The correlated uncertainties for the pseudodata and the theoretical prediction 
-are contained in the nuisance parameter vectors $b^{\textrm{pd}}$ and $b^{\textrm{th}}$, respectively, and the uncorrelated uncertainties in $\Delta_i$.
-%
-Their effect on $\sigma^{\textrm{th}}$ and $\sigma^{\textrm{pd}}$
-is described by the matrices $\Gamma_i^{\textrm{pd}}$ and $\Gamma_i^{\textrm{th}}$.
-The indices $\alpha$ and $\beta$ then run over the uncertainty nuisance parameters for the pseudodata and the theoretical prediction, respectively.
-%
-The nuisance parameter values $b^{\textrm{th(min)}}$ that minimize Eq.~\eqref{eq:profilingchi2} give the central PDFs $f'_0$ optimized to the profiled dataset in the form
-\begin{equation}
-f_0' = f_0
-      + \sum_\beta b_\beta^{\textrm{th(min)}} 
-        \left(  \frac{f_\beta^+   -  f_\beta^- }{2}
-              -    b_\beta^{\textrm{th(min)}}
-                \frac{f_\beta^+ + f_\beta^- - 2f_0}{2}
-        \right),
-\end{equation}
-where $f_0$ is the original central PDF and the up and down variation eigenvectors are given by $f^+, f^-$.
-The decrease in the uncertainties of the shifted PDFs indicates the enhancement that including the FPF data in the global PDF fit could bring.
-Here, the profiling studies are performed using version 2.2.1 of the \textsc{xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}, extended to support the use of \textsc{PineAPPL} grids~\cite{christopher_schwan_2023_7499507, Carrazza:2020gss}.
-%
-Using the PDF4LHC21~\cite{PDF4LHCWorkingGroup:2022cjn} PDF set, the results are illustrated by comparing the fractional uncertainties of the original PDF set to those obtained after profiling. 
-This is shown for the valence quark, gluon and the singlet distributions in Fig.~\ref{FASERv2_profiling} for FASER$\nu$2 pseudodata, while Fig.~\ref{FASERv_profiling} indicates the impact of FASER$\nu$.
-FASER$\nu$2 is observed to provide tighter constraints on the PDFs, with the effects being the most prominent for the valence and sea quark distributions.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_g_ratio.pdf}
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\caption{The fractional uncertainties in the valence quark, gluon and singlet PDFs as a function of the momentum fraction $x$ at the scale $Q^2 = 10000 \, \textrm{GeV}^2$.
-The profiling is performed using the
-PDF4LHC21 set and the pseudodata for FASER$\nu$2. The original uncertainty of PDF4LHC21 is
-indicated by the red band, while the blue band demonstrates the profiled result.}
-\label{FASERv2_profiling}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_dv_ratio.pdf}\\
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_g_ratio.pdf}
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_Sea_ratio.pdf}
-\caption{The fractional uncertainties in the valence quark, gluon and singlet PDFs as a function of the momentum fraction $x$ at the scale $Q^2 = 10000 \, \textrm{GeV}^2$.
-The profiling is performed using the
-PDF4LHC21 set and the pseudodata for FASER$\nu$. The original uncertainty of PDF4LHC21 is
-indicated by the red band, while the blue band demonstrates the profiled result.}
-\label{FASERv_profiling}
-\end{figure}
-
-\section{Impact in nuclear PDF fits}
-
-Next we account for the nuclear dependence of
-the measured neutrino structure functions.
-
-\section{Description of the $\nu$FPF codes}
-
-The part that computes the differential cross sections is taken care by the python
-package $\nu$FPF. By default, it computes the HERA cross section defined as
-\begin{equation}
-    \frac{d^2\tilde{\sigma}^{A}}{dxdy} \lp x,Q^2,y \rp =  \frac{1}{2}\lc (1-y)F^{\nu A}_2(x,Q^2) + y^2xF^{\nu A}_1(x,Q^2)
-    + (-1)^\ell  y\lp 1-\frac{y}{2}\rp xF^{\nu A}_3(x,Q^2)\rc ,
-\end{equation}
-where $\ell = 0$ for leptons and $\ell = 1$ for anti-leptons. Thus, in order to compare with 
-Eq.~\ref{eq:neutrino_DIS_xsec} one needs to multiply the above equation with $G_F^2s/2 \pi (1 + Q^2/m^2_W)^2$.
-
-\bibliographystyle{utphys}
-\bibliography{FPF-WG1}
-
-\end{document}

### 2023-05-09 paper/sec-introduction.tex
added structure to paper

\section{Introduction and motivation}
\label{sec:introduction}

The outline of this paper is as follows.
%

### 2023-05-09 paper/sec-protonPDFs.tex
added structure to paper

--- 2023-02-17 paper/FPF-WG1.tex
@@
-\documentclass[11pt,a4paper]{article}
-\pdfoutput=1
+\clearpage
+\section{Impact on the proton PDFs}
+\label{sec:protonPDFs}
 
-\usepackage[colorlinks=true, linkcolor=black!50!blue, urlcolor=blue, citecolor=blue, anchorcolor=blue]{hyperref}
-\usepackage[font=small,labelfont=bf,margin=0mm,labelsep=period,tableposition=top]{caption}
-\usepackage[a4paper,top=1.5cm,bottom=2cm,left=1.5cm,right=1.5cm,bindingoffset=0mm]{geometry}
-
-\usepackage{placeins,cite}
-\usepackage{graphicx}
-\usepackage{float}
-\usepackage{afterpage}
-\usepackage{epsfig}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{bm}
-\usepackage{multirow}
-\usepackage{url}
-\usepackage{xcolor}
-\usepackage{ulem}
-\usepackage{url}
-\usepackage{booktabs,multirow}
-\usepackage{textcomp}
-\graphicspath{{../}{./figures/}}
-
-\makeatletter
-\def\thickhline{%
-             \noalign{\ifnum0 =`}\fi\hrule \@height \thickarrayrulewidth \futurelet
-             \reserved@a\@xthickhline}
-\def\@xthickhline{\ifx\reserved@a\thickhline
-                \vskip\doublerulesep
-                \vskip -\thickarrayrulewidth
-                \fi
-                \ifnum0 =`{\fi}}
-\makeatother
-\newlength{\thickarrayrulewidth}
-\setlength{\thickarrayrulewidth}{3\arrayrulewidth}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{tikz}
-\usetikzlibrary{positioning}
-\usetikzlibrary{shapes.geometric, arrows}
-\usetikzlibrary{arrows.meta}
-\usepackage{varwidth}
-\usepackage{xcolor}
-%['#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', '#8c564b', '#e377c2', '#7f7f7f', '#bcbd22', '#17becf']
-\definecolor{mtplotlib1}{HTML}{1f77b4}
-\definecolor{mtplotlib2}{HTML}{ff7f0e}
-\definecolor{mtplotlib3}{HTML}{2ca02c}
-\definecolor{mtplotlib4}{HTML}{d62728}
-
-\tikzset{%
-  >={Latex[width=2mm,length=2mm]},
-  % Specifications for style of nodes:
-            base/.style = {rectangle, rounded corners, draw=black,
-                           minimum width=4cm, minimum height=1cm,
-                           text centered}, %, font=\sffamily},
-            mystyle/.style={rectangle, rounded corners, draw=black,
-            minimum width=12cm, minimum height=1cm,
-            text centered}, %, font=\sffamily},
-    col0/.style = {base, fill=white!30},
-    col1/.style = {base, fill=mtplotlib1!30},
-    col11/.style = {mystyle, fill=mtplotlib1!30},
-    col2/.style = {base, fill=mtplotlib2!30},
-    col3/.style = {base, fill=mtplotlib3!30},
-    col4/.style = {base, minimum width=2.5cm, fill=mtplotlib4!15,}%font=\ttfamily},
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\def\smallfrac#1#2{\hbox{$\frac{#1}{#2}$}}
-\newcommand{\be}{\begin{equation}}
-\newcommand{\ee}{\end{equation}}
-\newcommand{\bea}{\begin{eqnarray}}
-\newcommand{\eea}{\end{eqnarray}}
-\newcommand{\bi}{\begin{itemize}}
-\newcommand{\ei}{\end{itemize}}
-\newcommand{\ben}{\begin{enumerate}}
-\newcommand{\een}{\end{enumerate}}
-\newcommand{\la}{\left\langle}
-\newcommand{\ra}{\right\rangle}
-\newcommand{\lc}{\left[}
-\newcommand{\rc}{\right]}
-\newcommand{\lp}{\left(}
-\newcommand{\rp}{\right)}
-\newcommand{\as}{\alpha_s}
-\newcommand{\aq}{\alpha_s\left( Q^2 \right)}
-\newcommand{\amz}{\alpha_s\left( M_Z^2 \right)}
-\newcommand{\aqq}{\alpha_s \left( Q^2_0 \right)}
-\newcommand{\aqz}{\alpha_s \left( Q^2_0 \right)}
-\def\toinf#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
-{#1\rightarrow\infty }}}}
-\def\tozero#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
-{#1\rightarrow0 }}}}
-\def\toone#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
-{#1\rightarrow1 }}}}
-\def\frac#1#2{{{#1}\over {#2}}}
-\def\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
-    \raise1pt\hbox{$>$}}}       
-\def\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
-    \raise1pt\hbox{$<$}}}       
-\newcommand{\mrexp}{\mathrm{exp}}
-\newcommand{\dat}{\mathrm{dat}}
-\newcommand{\one}{\mathrm{(1)}}
-\newcommand{\two}{\mathrm{(2)}}
-\newcommand{\art}{\mathrm{art}}
-\newcommand{\rep}{\mathrm{rep}}
-\newcommand{\net}{\mathrm{net}}
-\newcommand{\stopp}{\mathrm{stop}}
-\newcommand{\sys}{\mathrm{sys}}
-\newcommand{\stat}{\mathrm{stat}}
-\newcommand{\pdf}{\mathrm{pdf}}
-\newcommand{\tot}{\mathrm{tot}}
-\newcommand{\minn}{\mathrm{min}}
-\newcommand{\mut}{\mathrm{mut}}
-\newcommand{\partt}{\mathrm{part}}
-\newcommand{\dof}{\mathrm{dof}}
-\newcommand{\NS}{\mathrm{NS}}
-\newcommand{\cov}{\mathrm{cov}}
-\newcommand{\gen}{\mathrm{gen}}
-\newcommand{\parr}{\mathrm{par}}
-\newcommand{\val}{\mathrm{val}}
-\newcommand{\tr}{\mathrm{tr}}
-\newcommand{\checkk}{\mathrm{check}}
-\newcommand{\reff}{\mathrm{ref}}
-\newcommand{\Mll}{M_{ll}}
-\newcommand{\extra}{\mathrm{extra}}
-\newcommand{\draft}[1]{}
-\newcommand{\comment}[1]{{\bf \it  #1}}
-\newcommand{\todo}[1]{\footnote{{\bfseries{\color{red} TODO} #1}}} % For todo's
-\def\beq{\begin{equation}}
-\def\eeq{\end{equation}}
-
-\numberwithin{equation}{section}
-\numberwithin{figure}{section}
-\numberwithin{table}{section}
-
-\newcommand{\tmop}[1]{\ensuremath{\operatorname{#1}}}
-\newcommand{\tmtextit}[1]{{\itshape{#1}}}
-\newcommand{\tmtextrm}[1]{{\rmfamily{#1}}}
-\newcommand{\tmtexttt}[1]{{\ttfamily{#1}}}
-
-\usepackage{tabularx}
-\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
-\DeclareRobustCommand{\RG}[1]{{\color{magenta}\textbf{[RG: #1]}}\xspace}
-
-\definecolor{darkblue}{rgb}{0.0,0,0.5}
-\definecolor{darkgreen}{rgb}{0.0,0.3,0.0}
-\definecolor{redish}{rgb}{0.675,0,0.2}
-\definecolor{red}{rgb}{0.8,0,0}
-\definecolor{green}{rgb}{0,0.6,0}
-\definecolor{bluish}{rgb}{0.2,0.2,0.675}
-\definecolor{mygrey}{rgb}{0.6,0.6,0.6}
-
-\usepackage{tikz} 
-\usetikzlibrary{shapes,arrows,positioning,automata,backgrounds,calc,er,patterns,arrows.meta}
-\usepackage{tikz-feynman}
-\tikzfeynmanset{compat=1.0.0}
-\usepackage{varwidth}
-\usepackage{xcolor}
-%['#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', '#8c564b', '#e377c2', '#7f7f7f', '#bcbd22', '#17becf']
-\definecolor{mtplotlib1}{HTML}{1f77b4}
-\definecolor{mtplotlib2}{HTML}{ff7f0e}
-\definecolor{mtplotlib3}{HTML}{2ca02c}
-\definecolor{mtplotlib4}{HTML}{d62728}
-
-\tikzset{%
-  >={Latex[width=2mm,length=2mm]},
-  % Specifications for style of nodes:
-            base/.style = {rectangle, rounded corners, draw=black,
-                           minimum width=4cm, minimum height=1cm,
-                           text centered}, %, font=\sffamily},
-            mystyle/.style={rectangle, rounded corners, draw=black,
-            minimum width=12cm, minimum height=1cm,
-            text centered}, %, font=\sffamily},
-    col0/.style = {base, fill=white!30},
-    col1/.style = {base, fill=mtplotlib1!30},
-    col11/.style = {mystyle, fill=mtplotlib1!30},
-    col2/.style = {base, fill=mtplotlib2!30},
-    col3/.style = {base, fill=mtplotlib3!30},
-    col4/.style = {base, minimum width=2.5cm, fill=mtplotlib4!15,}%font=\ttfamily},
-}
-
-\usepackage{tabularx}
-\usepackage{subcaption}
-\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
-\DeclareRobustCommand{\RG}[1]{{\color{magenta}\textbf{[RG: #1]}}\xspace}
-
-%%%%% raquel: color marks %%%%%
-%\usepackage{color} 
-\newcommand{\raq}[1]{{\bf\color{orange} #1}}  
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%% jaco: wider spacing in tables %%%%%
-\renewcommand{\arraystretch}{1.7}
-\def\lra#1{\overset{\text{\scriptsize$\leftrightarrow$}}{#1}}
-
-\begin{document}
-\newgeometry{top=1.5cm,bottom=1.5cm,left=1.5cm,right=1.5cm,bindingoffset=0mm}
-
-\vspace{0.7cm}
-
-\begin{center}
-  {\Large \bf Deep-Inelastic Scattering with TeV Neutrinos at the LHC}
-\vspace{1.1cm}
-
-\vspace{1.0cm}
-
-{\bf \large Abstract}
-
-\end{center}
-Notes to collect the studies
-carried out in WG1 of the Forward
-Physics Facility study: {\bf  Neutrino Interactions and Hadronic Structure}
-
-\tableofcontents
-
-\section{Recap of DIS kinematics}
-
-The double-differential cross-section for neutrino-nucleus scattering
-can be decomposed
-in terms of three independent structure functions $F_i^{\nu A}(x,Q^2)$ with $i=1,2,3$.
-%
-Focusing on the charged-current (CC) scattering case, mediated
-by the exchange of a $W^+$ weak boson, the differential
- cross section reads
-\be
-\label{eq:neutrino_DIS_xsec}
-\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/2\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc (1-y)F^{\nu A}_2(x,Q^2) + y^2xF^{\nu A}_1(x,Q^2) + y\lp 1-\frac{y}{2}\rp xF^{\nu A}_3(x,Q^2)\rc  \, ,
-\ee
-where $s=2m_N E_\nu$ is the neutrino-nucleon center of mass energy squared, $m_N$ is the nucleon mass,
-$E_\nu$ is the incoming neutrino energy,
-and the inelasticity $y$ is defined as $y=Q^2/(2x m_n E_{\nu})$.
-%
-For the time being we are neglecting target mass 
-corrections.
-%
-An analogous expression holds for  antineutrino 
-scattering, mediated
-by the exchange of a $W^-$ weak boson, with the only difference being a sign change
-in front of the parity-violating structure function $xF_3$,
-\be
-\label{eq:antineutrino_DIS_xsec}
-\frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/2\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc (1-y)F^{\bar{\nu} A}_2(x,Q^2) + y^2xF^{\bar{\nu} A}_1(x,Q^2) - y\lp 1-\frac{y}{2}\rp xF^{\bar{\nu} A}_3(x,Q^2)\rc  \, .
-\ee
-While the differential cross-section depends on three kinematic variables, $(x,Q^2,y)$,
-the structure functions themselves depend only on $x$ and $Q^2$.
-%
-Furthermore, both the cross-section and the structure functions depend
-on the atomic mass number $A$ of the target nucleus via nuclear modifications of the free-nucleon
-structure functions.
-
-Alternatively, Eq.~(\ref{eq:neutrino_DIS_xsec}) can be expressed in terms
-of the longitudinal structure function  $F_L^{\nu A}(x,Q^2)$ defined
-by $F_L = F_2-2xF_1$, leading to
-\be
-\label{eq:neutrino_DIS_xsec_FL}
-\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\nu A}_2(x,Q^2) - y^2F^{\nu A}_L(x,Q^2) +Y_- xF^{\nu A}_3(x,Q^2)\rc  \, ,
-\ee
-where $Y_\pm = 1 \pm (1-y)^2$ and with a counterpart expression for anti-neutrino scattering,
-\be
-\label{eq:antineutrino_DIS_xsec_FL}
-\frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\bar{\nu} A}_2(x,Q^2) - y^2F^{\bar{\nu} A}_L(x,Q^2) -Y_- xF^{\bar{\nu} A}_3(x,Q^2)\rc  \, ,
-\ee
-%
-Expressing the differential cross-section as in Eq.~(\ref{eq:neutrino_DIS_xsec_FL}) is advantageous
-because in the parton model (and in perturbative QCD at leading order) the longitudinal
-structure function vanishes, $F_L^{\nu A}(x,Q^2)=0$.
-%
-The combination of neutrino and antineutrino measurements makes possible disentangling
-the different structure functions, for example the cross-section difference
-\be
-\label{eq:neutrino_DIS_xsec_FL_diff}
-\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} - \frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy}=  \frac{G_F^2s Y_-}
-{4\pi \lp 1+Q^2/m_W^2\rp^2}\lc    xF^{\nu A}_3(x,Q^2)+  xF^{\bar{\nu} A}_3(x,Q^2)\rc \, ,
-\ee
-is proportional to the parity-violating structure function $xF_3$ averaged over neutrinos
-and antineutrinos.
-
-When both the momentum transfer squared $Q^2$
-and the  hadronic final-state
-invariant mass $W$ given by
-\be
-W^2 = m_N^2 + Q^2 \frac{(1-x)}{x} \, ,
-\ee
-are large enough, $Q^2 \gsim {\rm few~GeV}^2$ and $W \gsim 2$ GeV
-respectively, we find ourselves in the
-deep-inelastic scattering region where
-structure functions can be evaluated in perturbative QCD in terms of a factorised
-convolution of process-dependent partonic scattering cross-sections and
-of process-independent parton distribution functions,
-\be
-\label{eq:sfs_pqcd}
- F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g}\int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \quad i = 2,3,L \, ,
- \ee
- where $j$ is an index that runs over all possible partonic initial states
- and $C_{i,j}^{\nu N}$ is the process-dependent (but target-independent) coefficient function.
- %
- The latter can be expressed  as a series expansion in powers of the strong
- coupling $\alpha_s(Q^2)$,
- \be
- \label{eq:coeff_fun_expansion}
- C_{i,j}^{\nu N}(z,\alpha_s(Q^2)) = \sum_{k=0}^m \lp \alpha_s(Q^2) \rp^{k} C_{i,j}^{\nu N(k)}(z) \, .
- \ee
- The leading-order ($k=0$)  term is independent of $\alpha_s$ since the Born scattering
- is mediated by the weak interaction.
- %
- At leading order and considering a proton target, $n_f=4$ active quark flavours,
- neglecting charm mass effects and assuming a diagonal CKM matrix,
- we can express the $F_2^{\nu p}$ and $xF_3^{\nu p}$ structure functions as
- follows
- \bea
- F_2^{\nu p}(x,Q^2) &=& 2x\lp f_{\bar{u}} + f_{d} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
- F_2^{\bar{\nu} p}(x,Q^2) &=& 2x\lp f_u + f_{\bar{d}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:neutrinoSFs} \\
- xF_3^{\nu p}(x,Q^2) &=& 2x\lp -f_{\bar{u}} + f_d +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
- xF_3^{\bar{\nu} p}(x,Q^2) &=& 2x\lp f_u - f_{\bar{d}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, . \nonumber
- \eea
- The corresponding expressions for a neutron target and or isoscalar target can be obtained
- from isospin symmetry, for instance the LO structure functions for
- neutrino-neutron scattering are
- \bea
- F_2^{\nu n}(x,Q^2) &=& 2x\lp f_{\bar{d}} + f_{u} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
- F_2^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d + f_{\bar{u}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:antineutrinoSFs} \\
- xF_3^{\nu n}(x,Q^2) &=& 2x\lp -f_{\bar{d}} + f_u +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
- xF_3^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d - f_{\bar{u}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, . \nonumber
- \eea
-
-\section{DIS pseudo-data generation}
-\label{sec:pseudo-data_generation}
-
-The first goal is to produce projections
-for DIS pseudo-data at the FPF based on
-some idealised detector concepts and
-some initial choice of neutrino fluxes
-e.g.~\cite{Kling:2021gos}.
-%
-This requires a knowledge of the detector geometry
-and material, as well as of the double-differential
-neutrino interaction cross-section. 
-%
-Since we aim to produce pseudo-data binned in $(x,Q^2)$,
-for each simulated event we need to determine the 
-final-state kinematics.
-
-Specifically, we would like to evaluate the
-number of charged-current neutrino interaction events
-within the detector volume in different bins
-of the incoming neutrino energy $E_\nu$, the Bjorken
-variable $x$ and the momentum transfer square $Q^2$,
-\begin{equation}
-    N_{\rm ev}(E_\nu, x, Q^2) \, ,
-\end{equation}
-for some binning in these three kinematic variables.
-%
-This can be evaluated as
-\begin{equation}
-\label{eq:nev_v1}
-    N_{\rm ev}(E_\nu, x, Q^2) =  \frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} \mathcal{L}(E_{\nu}) \, ,
-\end{equation}
-where $\mathcal{L}(E_{\nu}) $ is the incoming neutrino
-luminosity which accounts for the detector geometry
-and material density. 
-%
-Eq.~(\ref{eq:nev_v1}) can be integrated to
-determine the actual number of events within
-the bin boundaries.
-
-\newline
-\newline
-We start with a perfect detector.
-\newline
-\newline
-For bins in $x,Q^2,E_{\nu}$, we start with the \href{https://github.com/juanrojochacon/FPF-WG1/blob/main/results/diff_xsecs_a1.txt}{differential cross section},$\frac{d^2\sigma(x,Q^2,E_{\nu}}{dxdQ^2})$ [pb GeV$^{-2}$] as output from {\tt YADISM} and convovle with the \href{https://github.com/KlingFelix/FastNeutrinoFluxSimulation/tree/main/Fluxes}{neutrino flux}, $\frac{dN_{\nu}}{dE_{\nu}}$.
-So for a detector with $n_T$ nuclear target density and $L_T$ length, we calculate the event rate per bin as
-
-\begin{equation}
-    N_{\rm ev}/{\rm bin} = n_T L_T\int_{Q^2_{min}}^{Q^2_{max}}\int_{x_{min}}^{x_{max}}\int_{E_{\nu,min}}^{E_{\nu , max}} \frac{dN_{\nu}}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) dQ^2 dx dE_{\nu}.
-\end{equation}
-
-Using a MC integration, we can calculate $N_{\rm ev}/{\rm bin}$ by sampling $N$ points in $x,Q^2,E_{\nu}$ space such that $0< y = \frac{Q^2}{2m_N E_{\nu }x} < 1$ and integrating over the bin.
-
-\begin{equation}
-    N_{\rm ev}/{\rm bin} \approx n_T L_T \frac{(Q^2_{max}-Q^2_{min})(x_{max}-x_{min})(E_{\nu ,max}-E_{\nu ,min})}{N}\times \sum_i^N f(x_i,Q^2_i,E_{\nu ,i})
-    \label{MCintegration}
-\end{equation}
-
-where $f(x_i,Q^2_i,E_{\nu ,i}) = \frac{dN_{\nu}}{dE_{\nu,i}}\left(\frac{d^2\sigma(x_i,Q^2_i,E_{\nu,i})}{dxdQ^2}\right)$.
-
-The statistical uncertainty for each bin is then defined by a gaussian distribution with fractional uncertainty $1/\sqrt{N{\rm ev}/{\rm bin}}$, i.e.
-$\delta N_{\rm ev}/{\rm bin} = \sqrt{N_{\rm ev} /{\rm bin}$
-\newline
-Following this prescription, we can produce plots which characterize the event rate for a particular neutrino species at a particular experiment.
-
-Results for FASER$\nu$2 can be found \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results}{here}.
-The .txt files will display which neutrino species was considered, and also compile experimental geometries and target details in the header.
-In the subfolder \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results/Summaries}{summaries}, plots can be found which show the event rate in $x,Q^2$ space, integrating over the entire neutrino spectrum.
-The event rate for muon neutrinos at FASER$\nu$2 is shown in Fig~\ref{fig:fasernu2_muon}.
-
-\begin{figure}[h]
-    \centering
-\includegraphics[width=1\textwidth]{Nevent_FASERv2_14.pdf}
-    \caption{Event rate per bin for muon neutrinos at FASER$\nu$2.
-Bins are denoted by dashed grid, and the red dot indicates the weighted average of $x,Q^2$ points in each bin.
-The total number of muon neutrino events calculated is $\approx2.6\times 10^5$.
-Note that bins were chosen somewhat arbitrarily, and can be iterated to improve PDF fits }
-    \label{fig:fasernu2_muon}
-\end{figure}
-
-\subsection{Systematic Effects on Pseudodata}
-We now wish to understand the impact of systematic uncertainties on the event rate in $(x,Q^2,E_{\nu})$ space.
-For each experiment, the observables $E_{l},E_{h},\theta$ are related to $(x,Q^2,E_{\nu})$ by
-
-\begin{align}
-E_{\nu} = E_l + E_h \nonumber \\
-Q^2 = 4E_lE_{\nu}\sin^2{\theta/2} \nonumber \\
-x = \frac{Q^2}{2m_N(E_{\nu} - E_l)}.
-\end{align}
-
-We wish to sample over the space of observables, $(E_{l},E_{h},\theta)$, perform  cuts based on detector performance, calculate the event rates, and then smear this sampling according to experimental uncertainties to estimate the uncertainty on the event rate.
-
-Taking FASER${\nu}$2 as an example, we can write the experimental cuts and uncertainties as
-
-\begin{align}
-100 < E_l < E_{\nu,{\rm max}} , \delta E_l = 30\% \nonumber \\
-100 < E_h < E_{\nu,{\rm max}} , \delta E_h = 50\% \nonumber \\
-0 < \theta < \tan^{-1}(0.5) , \delta\theta = 1~{\rm mrad}
-\label{fasernu2systematic_errors}
-\end{align}
-
-We first generate a MC dataset, $D_0$, over this space with $N = 10^7$ samples and calculate $x,Q^2,E_{\nu}$ for each event, removing samples with $y > 1$.
-We then integrate according to Eq.
-\ref{MCintegration} to produce a distribution of events with bins in $x,Q^2,E_{\nu}$.
-We then smear each sample according to a gaussian distribution with widths given by Eq.~\ref{fasernu2systematic_errors} to produce a new data set $D_i$ and repeat to produce $M = 10$ event distributions($M>10$ can later be used, but $M = 10$ appears to be stable).
-For each bin we take the standard deviation to produce the systematic errors per bin (denoted as "N\textunderscore sys\textunderscore errs" in files named "binned\textunderscore sysevents...
-.txt" \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results}{here}).
-
-For FASER${\nu}$2, the systematic erros typically dominate over statsitcal errors, at about $10\%$.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width = 1\textwidth]{error_plot_FASERv2_14.pdf}
-    \caption{Event rates with errorbars at FASER$\nu$2 for $\nu_{\mu} N \rightarrow \mu^- X$} summed over $Q^2$.
-The errobars along the x-axis showing the width of the $x$-bins, and are not showing any type of error.
-    \label{fig:my_label}
-\end{figure}
-
-\section{Experimental acceptance performance}
-
-\paragraph{AdvSND} 
-\begin{itemize}
-    \item The detectors will be able to track muons that have energy greater
-    than $20~\rm{GeV}$ (the values for the other charged leptons remain to be
-    determined) with an acceptance angle of 100 mrad for the muons and 
-    500 mrad for the both electrons and tau.
-    \item In addition, the information on the charge of the outgoing leptons
-    can also be accessed.
-    \item It should also be possible to reconstruct the hadronic final states
-    by measuring the total energy.
-\end{itemize}
-
-\paragraph{FLArE}
-\begin{itemize}
-    \item The detectors will be able to detect electrons with energy up to
-    $1~\rm{TeV}$ and an acceptance angel as high as 0.5 rad. For the muons,
-    the detectors will only be able to track them up to $1.5~\rm{GeV}$ with
-    a scattering angle reaching up to 0.4 mrad. The reconstruction of the
-    tau's angle and energy instead will be very difficult. However, it might
-    be possible to find the vertex of a particular tau decay if fine position
-    resolution is achieved.
-    \item With the current baseline design of the detector, it will not be
-    possible to access the information on the sign of the charged leptons.
-    \item It should also be possible to reconstruct the hadronic final
-    states but the reconstruction efficiency and particles will depend on
-    the type of particles. It is expected that the final states hadrons will
-    be dominated by pions, protons, and neutrons.
-    \item Regarding the systematic errors on the charged lepton energy and
-    scattering angle, it is expected to get $5\%$ energy resolution for
-    electrons and about 15 mrad in angular resolution. Due to the large
-    missing energy in the detector, $30\%$ energy resolution is probably
-    achievable for muons with about 5 mrad angular resolution.
-\end{itemize}
-
-\section{Impact in proton PDF fits}
-
-Once we have generated pseudo-data for the 
-neutrino DIS charged-current structure functions
-in bins of $(x,Q^2,y)$, and assuming that uncertainties
-are purely of statistical origin, we can assess their
-impact on proton PDFs.
-%
-At a first step we neglect nuclear effects
-and treat data as corresponding to a free isoscalar
-nucleon with $A=1$.
-
-The expected impact of the FPF data on global PDF fits is assessed by a profiling procedure~\cite{Paukkunen:2014zia, Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre}, based on minimizing the function
-%TODO correlations are also included here, as we hopefully get there in the end -- if not, remove terms involving correlations+pseudodata
-\begin{equation}
-\chi^2 = 
-\sum_{i=1}^{N_{\textrm{bins}}} 
-\frac{\left(  \sigma_i^{\textrm{pd}}
-            + \Gamma_i^{\alpha,\textrm{pd}}
-              b_\alpha^{\textrm{pd}}
-            - \sigma_i^{\textrm{th}}
-            - \Gamma_i^{\beta,\textrm{th}}
-              b_\beta^{\textrm{th}}
-     \right)^2
-     }{\Delta_i^2}
-+ \sum_\alpha (b_\alpha^{\textrm{pd}})^2
-+ \sum_\beta  (b_\beta^{\textrm{th}})^2 \, .
-\label{eq:profilingchi2}
-\end{equation}
-Here the pseudodata 
-$\sigma_i^{\textrm{pd}}$ 
-is obtained from the central theoretical prediction 
-$\sigma_i^{\textrm{th}}$ 
-for each bin $i$ out of $N_{\textrm{bins}}$ by varying it with the statistical uncertainties 
-$\delta_i^{\textrm{stat}}$, 
-obtained in the procedure desribed in Section~\ref{sec:pseudo-data_generation}, 
-as 
-%TODO once more complete uncertainty estimates are there, add them to the variation
-$\sigma_i^{\textrm{pd}} = \sigma_i^{\textrm{th}}(1 + r_i \delta_i^{\textrm{stat}})$, 
-with $r_i$ a univariate Gaussian random number.
-%
-The correlated uncertainties for the pseudodata and the theoretical prediction 
-are contained in the nuisance parameter vectors $b^{\textrm{pd}}$ and $b^{\textrm{th}}$, respectively, and the uncorrelated uncertainties in $\Delta_i$.
-%
-Their effect on $\sigma^{\textrm{th}}$ and $\sigma^{\textrm{pd}}$
-is described by the matrices $\Gamma_i^{\textrm{pd}}$ and $\Gamma_i^{\textrm{th}}$.
-The indices $\alpha$ and $\beta$ then run over the uncertainty nuisance parameters for the pseudodata and the theoretical prediction, respectively.
-%
-The nuisance parameter values $b^{\textrm{th(min)}}$ that minimize Eq.~\eqref{eq:profilingchi2} give the central PDFs $f'_0$ optimized to the profiled dataset in the form
-\begin{equation}
-f_0' = f_0
-      + \sum_\beta b_\beta^{\textrm{th(min)}} 
-        \left(  \frac{f_\beta^+   -  f_\beta^- }{2}
-              -    b_\beta^{\textrm{th(min)}}
-                \frac{f_\beta^+ + f_\beta^- - 2f_0}{2}
-        \right),
-\end{equation}
-where $f_0$ is the original central PDF and the up and down variation eigenvectors are given by $f^+, f^-$.
-The decrease in the uncertainties of the shifted PDFs indicates the enhancement that including the FPF data in the global PDF fit could bring.
-Here, the profiling studies are performed using version 2.2.1 of the \textsc{xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}, extended to support the use of \textsc{PineAPPL} grids~\cite{christopher_schwan_2023_7499507, Carrazza:2020gss}.
-%
 Using the PDF4LHC21~\cite{PDF4LHCWorkingGroup:2022cjn} PDF set, the results are illustrated by comparing the fractional uncertainties of the original PDF set to those obtained after profiling. 
@@
 \end{figure}
-
-\section{Impact in nuclear PDF fits}
-
-Next we account for the nuclear dependence of
-the measured neutrino structure functions.
-
-\section{Description of the $\nu$FPF codes}
-
-The part that computes the differential cross sections is taken care by the python
-package $\nu$FPF. By default, it computes the HERA cross section defined as
-\begin{equation}
-    \frac{d^2\tilde{\sigma}^{A}}{dxdy} \lp x,Q^2,y \rp =  \frac{1}{2}\lc (1-y)F^{\nu A}_2(x,Q^2) + y^2xF^{\nu A}_1(x,Q^2)
-    + (-1)^\ell  y\lp 1-\frac{y}{2}\rp xF^{\nu A}_3(x,Q^2)\rc ,
-\end{equation}
-where $\ell = 0$ for leptons and $\ell = 1$ for anti-leptons. Thus, in order to compare with 
-Eq.~\ref{eq:neutrino_DIS_xsec} one needs to multiply the above equation with $G_F^2s/2 \pi (1 + Q^2/m^2_W)^2$.
-
-\bibliographystyle{utphys}
-\bibliography{FPF-WG1}
-
-\end{document}

### 2023-05-09 paper/sec-summary.tex
added structure to paper

\clearpage
\section{Summary and outlook}
\label{sec:summary}

In this work ....

### 2023-05-09 paper/scripts/PDFs.py

@@ -1,0 +1,299 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+import os,sys
+import lhapdf
+import numpy as np
+import matplotlib.pyplot as py
+from matplotlib import gridspec
+from  matplotlib import rc
+rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+rc('text',usetex=True)
+from pylab import *
+import scipy
+from scipy.integrate import dblquad
+
+print("\n *********************************************************")
+print("      Charm asymmetry                               ")
+print(" ***********************************************************\n")
+
+q = 100 # GeV
+stringQ=r'$Q=100~{\rm GeV}$'
+filelabel='q100gev-ratios'
+nx = 1000
+xmin = 1e-3
+xmax= 0.95
+# Reduce verbosity of LHAPDF
+lhapdf.setVerbosity(0)
+# max number of replicas
+nrepmax=1000
+# number of flavours to be plotted
+nfl=6
+# Set x grid
+X = np.logspace(log(xmin),log(xmax),nx)
+# number of pdf sets
+nset=2
+
+nrep=np.zeros(nset, dtype='int')
+nrep_max = 1000
+
+pdfset=["210713-n3fit-001","NNPDF_FASERV2"]
+
+for iset in range(nset):
+
+    p=lhapdf.getPDFSet(pdfset[iset])
+    nrep[iset]=int(p.get_entry("NumMembers"))-1
+    
+    if(iset==0):
+        fit1 = np.zeros((nrep[iset],nfl,nx))
+    if(iset==1):
+        fit2 = np.zeros((nrep[iset],nfl,nx))
+    if(iset==2):
+        fit3 = np.zeros((nrep[iset],nfl,nx))
+
+    print(pdfset[iset])
+    print("nrep = ",nrep[iset])
+
+    # Run over replicas
+    for i in range(1,nrep[iset]+1):
+        p=lhapdf.mkPDF(pdfset[iset],i)
+        lhapdf.setVerbosity(0)
+
+        #print("irep = ",i)
+        
+        # Run over x arrat
+        for k in range(nx):
+            
+            x = X[k]
+            q2 = pow(q,2.0)
+
+            # run over flavours
[…]

### 2023-05-24 paper/FPF-WG1.tex

--- 2023-02-17 paper/FPF-WG1.tex
@@
 \begin{center}
-  {\Large \bf Deep-Inelastic Scattering with TeV Neutrinos at the LHC}
+  {\Large \bf The LHC as a Neutrino-Ion Collider }\\
   \vspace{1.1cm}
+  {\small
+Max Fieg$^{1}$, Tommaso Giani$^{2,3}$, Peter Krack$^{2,3}$  Giacomo Magni$^{2,3}$, Toni M\"akel\"a$^{4}$, \\[0.1cm]
+    Tanjona Rabemananjara$^{2,3}$, and Juan Rojo$^{2,3}$.
+  }\\
+
+\vspace{0.7cm}
+
+{\it \small
+    ~$^1$ UC Irvine  \\[0.1cm]
+    ~$^2$Department of Physics and Astronomy, Vrije Universiteit, NL-1081 HV Amsterdam\\[0.1cm]
+    ~$^3$Nikhef Theory Group, Science Park 105, 1098 XG Amsterdam, The Netherlands\\[0.1cm]
+    ~$^4$National Centre for Nuclear Research, Pasteura 7, Warsaw, PL-02-093, Poland \\[0.1cm]
+ }
 
@@
 \end{center}
-Notes to collect the studies
-carried out in WG1 of the Forward
-Physics Facility study: {\bf  Neutrino Interactions and Hadronic Structure}
+
+Proton-proton collisions at the LHC produce an intense collimated flux of neutrinos
+characterised by the largest energies (up to several TeV) achieved in laboratory experiments.
+%
+Until recently, these neutrinos escaped detection and hence were lost for physics.
+%
+The observation in March 2023 of LHC neutrinos by the FASER$\nu$ and SND@LHC experiments
+heralds the beginning of a ``LHC neutrino era'' offering unprecedented scientific opportunities
+for particle and astroparticle physics both within the Standard Model and beyond it.
+%
+Here we assess the expected impact of LHC neutrino deep-inelastic scattering (DIS) structure functions
+on the quark and gluon substructure of nucleons and heavy nuclei.
+%
+In addition to projections for FASER$\nu$ and SND@LHC based on the full Run III luminosity,
+we also consider the experiments entering the proposed
+ Forward Physics Facility (FPF) to operate concurrently with the HL-LHC.
+%
+ We generate pseudo-data for inclusive and charm DIS structure functions for these various experiments,
+model their  systematic uncertainties, and quantify their impact
+on proton and nuclear PDFs by means of both  Hessian profiling within {\sc\small xFitter}
+and using the NNPDF framework.
+%
+We find the LHC neutrino scattering, specially
+for the high-statistics  experiments at the FPF, provides  stringent constraints
+concerning the separation between quark and antiquark PDFs of different flavours.
+%
+Our analysis demonstrates that detection and analysis of LHC far-forward neutrinos  effectively
+extends the LHC with a charged-current counterpart of the Electron-Ion Collider (EIC)
+with comparable kinematic reach and hence realises a ``Neutrino-Ion Collider'' at CERN.
+
+\clearpage
 
@@
 
-\section{Recap of DIS kinematics}
+% Introduction and motivation
+\input{sec-introduction}
 
-The double-differential cross-section for neutrino-nucleus scattering
-can be decomposed
-in terms of three independent structure functions $F_i^{\nu A}(x,Q^2)$ with $i=1,2,3$.
-%
-Focusing on the charged-current (CC) scattering case, mediated
-by the exchange of a $W^+$ weak boson, the differential
- cross section reads
-\be
-\label{eq:neutrino_DIS_xsec}
-\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/2\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc (1-y)F^{\nu A}_2(x,Q^2) + y^2xF^{\nu A}_1(x,Q^2) + y\lp 1-\frac{y}{2}\rp xF^{\nu A}_3(x,Q^2)\rc  \, ,
-\ee
-where $s=2m_N E_\nu$ is the neutrino-nucleon center of mass energy squared, $m_N$ is the nucleon mass,
-$E_\nu$ is the incoming neutrino energy,
-and the inelasticity $y$ is defined as $y=Q^2/(2x m_n E_{\nu})$.
-%
-For the time being we are neglecting target mass 
-corrections.
-%
-An analogous expression holds for  antineutrino 
-scattering, mediated
-by the exchange of a $W^-$ weak boson, with the only difference being a sign change
-in front of the parity-violating structure function $xF_3$,
-\be
-\label{eq:antineutrino_DIS_xsec}
-\frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/2\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc (1-y)F^{\bar{\nu} A}_2(x,Q^2) + y^2xF^{\bar{\nu} A}_1(x,Q^2) - y\lp 1-\frac{y}{2}\rp xF^{\bar{\nu} A}_3(x,Q^2)\rc  \, .
-\ee
-While the differential cross-section depends on three kinematic variables, $(x,Q^2,y)$,
-the structure functions themselves depend only on $x$ and $Q^2$.
-%
-Furthermore, both the cross-section and the structure functions depend
-on the atomic mass number $A$ of the target nucleus via nuclear modifications of the free-nucleon
-structure functions.
+% Generation of FPF DIS structure functions pseudo-data
+\input{sec-dis-pseudodata}
 
-Alternatively, Eq.~(\ref{eq:neutrino_DIS_xsec}) can be expressed in terms
-of the longitudinal structure function  $F_L^{\nu A}(x,Q^2)$ defined
-by $F_L = F_2-2xF_1$, leading to
-\be
-\label{eq:neutrino_DIS_xsec_FL}
-\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\nu A}_2(x,Q^2) - y^2F^{\nu A}_L(x,Q^2) +Y_- xF^{\nu A}_3(x,Q^2)\rc  \, ,
-\ee
-where $Y_\pm = 1 \pm (1-y)^2$ and with a counterpart expression for anti-neutrino scattering,
-\be
-\label{eq:antineutrino_DIS_xsec_FL}
-\frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\bar{\nu} A}_2(x,Q^2) - y^2F^{\bar{\nu} A}_L(x,Q^2) -Y_- xF^{\bar{\nu} A}_3(x,Q^2)\rc  \, ,
-\ee
-%
-Expressing the differential cross-section as in Eq.~(\ref{eq:neutrino_DIS_xsec_FL}) is advantageous
-because in the parton model (and in perturbative QCD at leading order) the longitudinal
-structure function vanishes, $F_L^{\nu A}(x,Q^2)=0$.
-%
-The combination of neutrino and antineutrino measurements makes possible disentangling
-the different structure functions, for example the cross-section difference
-\be
-\label{eq:neutrino_DIS_xsec_FL_diff}
-\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} - \frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy}=  \frac{G_F^2s Y_-}
-{4\pi \lp 1+Q^2/m_W^2\rp^2}\lc    xF^{\nu A}_3(x,Q^2)+  xF^{\bar{\nu} A}_3(x,Q^2)\rc \, ,
-\ee
-is proportional to the parity-violating structure function $xF_3$ averaged over neutrinos
-and antineutrinos.
+% Analysis settings, theory calculations, xfitter vs NNPDFs, yadism/eko/pineappl
+% Fitting vs profiling
+\input{sec-analysis}
 
-When both the momentum transfer squared $Q^2$
-and the  hadronic final-state
-invariant mass $W$ given by
-\be
-W^2 = m_N^2 + Q^2 \frac{(1-x)}{x} \, ,
-\ee
-are large enough, $Q^2 \gsim {\rm few~GeV}^2$ and $W \gsim 2$ GeV
-respectively, we find ourselves in the
-deep-inelastic scattering region where
-structure functions can be evaluated in perturbative QCD in terms of a factorised
-convolution of process-dependent partonic scattering cross-sections and
-of process-independent parton distribution functions,
-\be
-\label{eq:sfs_pqcd}
- F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g}\int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \quad i = 2,3,L \, ,
- \ee
- where $j$ is an index that runs over all possible partonic initial states
- and $C_{i,j}^{\nu N}$ is the process-dependent (but target-independent) coefficient function.
- %
- The latter can be expressed  as a series expansion in powers of the strong
- coupling $\alpha_s(Q^2)$,
- \be
- \label{eq:coeff_fun_expansion}
- C_{i,j}^{\nu N}(z,\alpha_s(Q^2)) = \sum_{k=0}^m \lp \alpha_s(Q^2) \rp^{k} C_{i,j}^{\nu N(k)}(z) \, .
- \ee
- The leading-order ($k=0$)  term is independent of $\alpha_s$ since the Born scattering
- is mediated by the weak interaction.
- %
- At leading order and considering a proton target, $n_f=4$ active quark flavours,
- neglecting charm mass effects and assuming a diagonal CKM matrix,
- we can express the $F_2^{\nu p}$ and $xF_3^{\nu p}$ structure functions as
- follows
- \bea
- F_2^{\nu p}(x,Q^2) &=& 2x\lp f_{\bar{u}} + f_{d} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
- F_2^{\bar{\nu} p}(x,Q^2) &=& 2x\lp f_u + f_{\bar{d}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:neutrinoSFs} \\
- xF_3^{\nu p}(x,Q^2) &=& 2x\lp -f_{\bar{u}} + f_d +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
- xF_3^{\bar{\nu} p}(x,Q^2) &=& 2x\lp f_u - f_{\bar{d}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, . \nonumber
- \eea
- The corresponding expressions for a neutron target and or isoscalar target can be obtained
- from isospin symmetry, for instance the LO structure functions for
- neutrino-neutron scattering are
- \bea
- F_2^{\nu n}(x,Q^2) &=& 2x\lp f_{\bar{d}} + f_{u} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
- F_2^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d + f_{\bar{u}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:antineutrinoSFs} \\
- xF_3^{\nu n}(x,Q^2) &=& 2x\lp -f_{\bar{d}} + f_u +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
- xF_3^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d - f_{\bar{u}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, . \nonumber
- \eea
+% REsults for the proton PDFs, using NNPDF and PDF4LHC21/xfitter
+\input{sec-protonPDFs}
 
-\section{DIS pseudo-data generation}
-\label{sec:pseudo-data_generation}
+% REsults for the nuclear PDFs, using NNPDF and EPPS21/xfitter
+\input{sec-nuclearPDFs}
 
-The first goal is to produce projections
-for DIS pseudo-data at the FPF based on
-some idealised detector concepts and
-some initial choice of neutrino fluxes
-e.g.~\cite{Kling:2021gos}.
-%
-This requires a knowledge of the detector geometry
-and material, as well as of the double-differential
-neutrino interaction cross-section. 
-%
-Since we aim to produce pseudo-data binned in $(x,Q^2)$,
-for each simulated event we need to determine the 
-final-state kinematics.
+% Summary and outlook
+\input{sec-summary}
 
-Specifically, we would like to evaluate the
-number of charged-current neutrino interaction events
-within the detector volume in different bins
-of the incoming neutrino energy $E_\nu$, the Bjorken
-variable $x$ and the momentum transfer square $Q^2$,
-\begin{equation}
-    N_{\rm ev}(E_\nu, x, Q^2) \, ,
-\end{equation}
-for some binning in these three kinematic variables.
-%
-This can be evaluated as
-\begin{equation}
-\label{eq:nev_v1}
-    N_{\rm ev}(E_\nu, x, Q^2) =  \frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} \mathcal{L}(E_{\nu}) \, ,
-\end{equation}
-where $\mathcal{L}(E_{\nu}) $ is the incoming neutrino
-luminosity which accounts for the detector geometry
-and material density. 
-%
-Eq.~(\ref{eq:nev_v1}) can be integrated to
-determine the actual number of events within
-the bin boundaries.
+%\section{Description of the $\nu$FPF codes}
 
-\newline
-\newline
-We start with a perfect detector.
-\newline
-\newline
-For bins in $x,Q^2,E_{\nu}$, we start with the \href{https://github.com/juanrojochacon/FPF-WG1/blob/main/results/diff_xsecs_a1.txt}{differential cross section},$\frac{d^2\sigma(x,Q^2,E_{\nu}}{dxdQ^2})$ [pb GeV$^{-2}$] as output from {\tt YADISM} and convovle with the \href{https://github.com/KlingFelix/FastNeutrinoFluxSimulation/tree/main/Fluxes}{neutrino flux}, $\frac{dN_{\nu}}{dE_{\nu}}$.
-So for a detector with $n_T$ nuclear target density and $L_T$ length, we calculate the event rate per bin as
+%The part that computes the differential cross sections is taken care by the python
+%package $\nu$FPF. By default, it computes the HERA cross section defined as
+%\begin{equation}
+%    \frac{d^2\tilde{\sigma}^{A}}{dxdy} \lp x,Q^2,y \rp =  \frac{1}{2}\lc (1-y)F^{\nu A}_2(x,Q^2) + y^2xF^{\nu A}_1(x,Q^2)
+%    + (-1)^\ell  y\lp 1-\frac{y}{2}\rp xF^{\nu A}_3(x,Q^2)\rc ,
+%\end{equation}
+%where $\ell = 0$ for leptons and $\ell = 1$ for anti-leptons. Thus, in order to compare with 
+%Eq.~\ref{eq:neutrino_DIS_xsec} one needs to multiply the above equation with $G_F^2s/2 \pi (1 + Q^2/m^2_W)^2$.
 
-\begin{equation}
-    N_{\rm ev}/{\rm bin} = n_T L_T\int_{Q^2_{min}}^{Q^2_{max}}\int_{x_{min}}^{x_{max}}\int_{E_{\nu,min}}^{E_{\nu , max}} \frac{dN_{\nu}}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) dQ^2 dx dE_{\nu}.
-\end{equation}
-
-Using a MC integration, we can calculate $N_{\rm ev}/{\rm bin}$ by sampling $N$ points in $x,Q^2,E_{\nu}$ space such that $0< y = \frac{Q^2}{2m_N E_{\nu }x} < 1$ and integrating over the bin.
-
-\begin{equation}
-    N_{\rm ev}/{\rm bin} \approx n_T L_T \frac{(Q^2_{max}-Q^2_{min})(x_{max}-x_{min})(E_{\nu ,max}-E_{\nu ,min})}{N}\times \sum_i^N f(x_i,Q^2_i,E_{\nu ,i})
-    \label{MCintegration}
-\end{equation}
-
-where $f(x_i,Q^2_i,E_{\nu ,i}) = \frac{dN_{\nu}}{dE_{\nu,i}}\left(\frac{d^2\sigma(x_i,Q^2_i,E_{\nu,i})}{dxdQ^2}\right)$.
-
-The statistical uncertainty for each bin is then defined by a gaussian distribution with fractional uncertainty $1/\sqrt{N{\rm ev}/{\rm bin}}$, i.e.
-$\delta N_{\rm ev}/{\rm bin} = \sqrt{N_{\rm ev} /{\rm bin}$
-\newline
-Following this prescription, we can produce plots which characterize the event rate for a particular neutrino species at a particular experiment.
-
-Results for FASER$\nu$2 can be found \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results}{here}.
-The .txt files will display which neutrino species was considered, and also compile experimental geometries and target details in the header.
-In the subfolder \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results/Summaries}{summaries}, plots can be found which show the event rate in $x,Q^2$ space, integrating over the entire neutrino spectrum.
-The event rate for muon neutrinos at FASER$\nu$2 is shown in Fig~\ref{fig:fasernu2_muon}.
-
-\begin{figure}[h]
-    \centering
-\includegraphics[width=1\textwidth]{Nevent_FASERv2_14.pdf}
-    \caption{Event rate per bin for muon neutrinos at FASER$\nu$2.
-Bins are denoted by dashed grid, and the red dot indicates the weighted average of $x,Q^2$ points in each bin.
-The total number of muon neutrino events calculated is $\approx2.6\times 10^5$.
-Note that bins were chosen somewhat arbitrarily, and can be iterated to improve PDF fits }
-    \label{fig:fasernu2_muon}
-\end{figure}
-
-\subsection{Systematic Effects on Pseudodata}
-We now wish to understand the impact of systematic uncertainties on the event rate in $(x,Q^2,E_{\nu})$ space.
-For each experiment, the observables $E_{l},E_{h},\theta$ are related to $(x,Q^2,E_{\nu})$ by
-
-\begin{align}
-E_{\nu} = E_l + E_h \nonumber \\
-Q^2 = 4E_lE_{\nu}\sin^2{\theta/2} \nonumber \\
-x = \frac{Q^2}{2m_N(E_{\nu} - E_l)}.
-\end{align}
-
-We wish to sample over the space of observables, $(E_{l},E_{h},\theta)$, perform  cuts based on detector performance, calculate the event rates, and then smear this sampling according to experimental uncertainties to estimate the uncertainty on the event rate.
-
-Taking FASER${\nu}$2 as an example, we can write the experimental cuts and uncertainties as
-
-\begin{align}
-100 < E_l < E_{\nu,{\rm max}} , \delta E_l = 30\% \nonumber \\
-100 < E_h < E_{\nu,{\rm max}} , \delta E_h = 50\% \nonumber \\
-0 < \theta < \tan^{-1}(0.5) , \delta\theta = 1~{\rm mrad}
-\label{fasernu2systematic_errors}
-\end{align}
-
-We first generate a MC dataset, $D_0$, over this space with $N = 10^7$ samples and calculate $x,Q^2,E_{\nu}$ for each event, removing samples with $y > 1$.
-We then integrate according to Eq.
-\ref{MCintegration} to produce a distribution of events with bins in $x,Q^2,E_{\nu}$.
-We then smear each sample according to a gaussian distribution with widths given by Eq.~\ref{fasernu2systematic_errors} to produce a new data set $D_i$ and repeat to produce $M = 10$ event distributions($M>10$ can later be used, but $M = 10$ appears to be stable).
-For each bin we take the standard deviation to produce the systematic errors per bin (denoted as "N\textunderscore sys\textunderscore errs" in files named "binned\textunderscore sysevents...
-.txt" \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results}{here}).
-
-For FASER${\nu}$2, the systematic erros typically dominate over statsitcal errors, at about $10\%$.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width = 1\textwidth]{error_plot_FASERv2_14.pdf}
-    \caption{Event rates with errorbars at FASER$\nu$2 for $\nu_{\mu} N \rightarrow \mu^- X$} summed over $Q^2$.
-The errobars along the x-axis showing the width of the $x$-bins, and are not showing any type of error.
-    \label{fig:my_label}
-\end{figure}
-
-\section{Experimental acceptance performance}
-
-\paragraph{AdvSND} 
-\begin{itemize}
-    \item The detectors will be able to track muons that have energy greater
-    than $20~\rm{GeV}$ (the values for the other charged leptons remain to be
-    determined) with an acceptance angle of 100 mrad for the muons and 
-    500 mrad for the both electrons and tau.
-    \item In addition, the information on the charge of the outgoing leptons
-    can also be accessed.
-    \item It should also be possible to reconstruct the hadronic final states
-    by measuring the total energy.
-\end{itemize}
-
-\paragraph{FLArE}
-\begin{itemize}
-    \item The detectors will be able to detect electrons with energy up to
-    $1~\rm{TeV}$ and an acceptance angel as high as 0.5 rad. For the muons,
-    the detectors will only be able to track them up to $1.5~\rm{GeV}$ with
-    a scattering angle reaching up to 0.4 mrad. The reconstruction of the
-    tau's angle and energy instead will be very difficult. However, it might
-    be possible to find the vertex of a particular tau decay if fine position
-    resolution is achieved.
-    \item With the current baseline design of the detector, it will not be
-    possible to access the information on the sign of the charged leptons.
-    \item It should also be possible to reconstruct the hadronic final
-    states but the reconstruction efficiency and particles will depend on
-    the type of particles. It is expected that the final states hadrons will
-    be dominated by pions, protons, and neutrons.
-    \item Regarding the systematic errors on the charged lepton energy and
-    scattering angle, it is expected to get $5\%$ energy resolution for
-    electrons and about 15 mrad in angular resolution. Due to the large
-    missing energy in the detector, $30\%$ energy resolution is probably
-    achievable for muons with about 5 mrad angular resolution.
-\end{itemize}
-
-\section{Impact in proton PDF fits}
-
-Once we have generated pseudo-data for the 
-neutrino DIS charged-current structure functions
-in bins of $(x,Q^2,y)$, and assuming that uncertainties
-are purely of statistical origin, we can assess their
-impact on proton PDFs.
-%
-At a first step we neglect nuclear effects
-and treat data as corresponding to a free isoscalar
-nucleon with $A=1$.
-
-The expected impact of the FPF data on global PDF fits is assessed by a profiling procedure~\cite{Paukkunen:2014zia, Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre}, based on minimizing the function
-%TODO correlations are also included here, as we hopefully get there in the end -- if not, remove terms involving correlations+pseudodata
-\begin{equation}
-\chi^2 = 
-\sum_{i=1}^{N_{\textrm{bins}}} 
-\frac{\left(  \sigma_i^{\textrm{pd}}
-            + \Gamma_i^{\alpha,\textrm{pd}}
-              b_\alpha^{\textrm{pd}}
-            - \sigma_i^{\textrm{th}}
-            - \Gamma_i^{\beta,\textrm{th}}
-              b_\beta^{\textrm{th}}
-     \right)^2
-     }{\Delta_i^2}
-+ \sum_\alpha (b_\alpha^{\textrm{pd}})^2
-+ \sum_\beta  (b_\beta^{\textrm{th}})^2 \, .
-\label{eq:profilingchi2}
-\end{equation}
-Here the pseudodata 
-$\sigma_i^{\textrm{pd}}$ 
-is obtained from the central theoretical prediction 
-$\sigma_i^{\textrm{th}}$ 
-for each bin $i$ out of $N_{\textrm{bins}}$ by varying it with the statistical uncertainties 
-$\delta_i^{\textrm{stat}}$, 
-obtained in the procedure desribed in Section~\ref{sec:pseudo-data_generation}, 
-as 
-%TODO once more complete uncertainty estimates are there, add them to the variation
-$\sigma_i^{\textrm{pd}} = \sigma_i^{\textrm{th}}(1 + r_i \delta_i^{\textrm{stat}})$, 
-with $r_i$ a univariate Gaussian random number.
-%
-The correlated uncertainties for the pseudodata and the theoretical prediction 
-are contained in the nuisance parameter vectors $b^{\textrm{pd}}$ and $b^{\textrm{th}}$, respectively, and the uncorrelated uncertainties in $\Delta_i$.
-%
-Their effect on $\sigma^{\textrm{th}}$ and $\sigma^{\textrm{pd}}$
-is described by the matrices $\Gamma_i^{\textrm{pd}}$ and $\Gamma_i^{\textrm{th}}$.
-The indices $\alpha$ and $\beta$ then run over the uncertainty nuisance parameters for the pseudodata and the theoretical prediction, respectively.
-%
-The nuisance parameter values $b^{\textrm{th(min)}}$ that minimize Eq.~\eqref{eq:profilingchi2} give the central PDFs $f'_0$ optimized to the profiled dataset in the form
-\begin{equation}
-f_0' = f_0
-      + \sum_\beta b_\beta^{\textrm{th(min)}} 
-        \left(  \frac{f_\beta^+   -  f_\beta^- }{2}
-              -    b_\beta^{\textrm{th(min)}}
-                \frac{f_\beta^+ + f_\beta^- - 2f_0}{2}
-        \right),
-\end{equation}
-where $f_0$ is the original central PDF and the up and down variation eigenvectors are given by $f^+, f^-$.
-The decrease in the uncertainties of the shifted PDFs indicates the enhancement that including the FPF data in the global PDF fit could bring.
-Here, the profiling studies are performed using version 2.2.1 of the \textsc{xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}, extended to support the use of \textsc{PineAPPL} grids~\cite{christopher_schwan_2023_7499507, Carrazza:2020gss}.
-%
-Using the PDF4LHC21~\cite{PDF4LHCWorkingGroup:2022cjn} PDF set, the results are illustrated by comparing the fractional uncertainties of the original PDF set to those obtained after profiling. 
-This is shown for the valence quark, gluon and the singlet distributions in Fig.~\ref{FASERv2_profiling} for FASER$\nu$2 pseudodata, while Fig.~\ref{FASERv_profiling} indicates the impact of FASER$\nu$.
-FASER$\nu$2 is observed to provide tighter constraints on the PDFs, with the effects being the most prominent for the valence and sea quark distributions.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_g_ratio.pdf}
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\caption{The fractional uncertainties in the valence quark, gluon and singlet PDFs as a function of the momentum fraction $x$ at the scale $Q^2 = 10000 \, \textrm{GeV}^2$.
-The profiling is performed using the
-PDF4LHC21 set and the pseudodata for FASER$\nu$2. The original uncertainty of PDF4LHC21 is
-indicated by the red band, while the blue band demonstrates the profiled result.}
-\label{FASERv2_profiling}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_dv_ratio.pdf}\\
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_g_ratio.pdf}
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_Sea_ratio.pdf}
-\caption{The fractional uncertainties in the valence quark, gluon and singlet PDFs as a function of the momentum fraction $x$ at the scale $Q^2 = 10000 \, \textrm{GeV}^2$.
-The profiling is performed using the
-PDF4LHC21 set and the pseudodata for FASER$\nu$. The original uncertainty of PDF4LHC21 is
-indicated by the red band, while the blue band demonstrates the profiled result.}
-\label{FASERv_profiling}
-\end{figure}
-
-\section{Impact in nuclear PDF fits}
-
-Next we account for the nuclear dependence of
-the measured neutrino structure functions.
-
-\section{Description of the $\nu$FPF codes}
-
-The part that computes the differential cross sections is taken care by the python
-package $\nu$FPF. By default, it computes the HERA cross section defined as
-\begin{equation}
-    \frac{d^2\tilde{\sigma}^{A}}{dxdy} \lp x,Q^2,y \rp =  \frac{1}{2}\lc (1-y)F^{\nu A}_2(x,Q^2) + y^2xF^{\nu A}_1(x,Q^2)
-    + (-1)^\ell  y\lp 1-\frac{y}{2}\rp xF^{\nu A}_3(x,Q^2)\rc ,
-\end{equation}
-where $\ell = 0$ for leptons and $\ell = 1$ for anti-leptons. Thus, in order to compare with 
-Eq.~\ref{eq:neutrino_DIS_xsec} one needs to multiply the above equation with $G_F^2s/2 \pi (1 + Q^2/m^2_W)^2$.
-
+% Bibliography
 \bibliographystyle{utphys}

### 2023-05-24 paper/sec-analysis.tex

\section{Analysis settings}
\label{sec:settings}

Once we have generated pseudo-data for the 
neutrino DIS charged-current structure functions
in bins of $(x,Q^2,y)$, and assuming that uncertainties
are purely of statistical origin, we can assess their
impact on proton PDFs.
%
At a first step we neglect nuclear effects
and treat data as corresponding to a free isoscalar
nucleon with $A=1$.

The expected impact of the FPF data on global PDF fits is assessed by a profiling procedure~\cite{Paukkunen:2014zia, Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre}, based on minimizing the function
%TODO correlations are also included here, as we hopefully get there in the end -- if not, remove terms involving correlations+pseudodata
\begin{equation}
\chi^2 = 
\sum_{i=1}^{N_{\textrm{bins}}} 
\frac{\left(  \sigma_i^{\textrm{pd}}
            + \Gamma_i^{\alpha,\textrm{pd}}
              b_\alpha^{\textrm{pd}}
            - \sigma_i^{\textrm{th}}
            - \Gamma_i^{\beta,\textrm{th}}
              b_\beta^{\textrm{th}}
     \right)^2
     }{\Delta_i^2}
+ \sum_\alpha (b_\alpha^{\textrm{pd}})^2
+ \sum_\beta  (b_\beta^{\textrm{th}})^2 \, .
\label{eq:profilingchi2}
\end{equation}
Here the pseudodata 
$\sigma_i^{\textrm{pd}}$ 
is obtained from the central theoretical prediction 
$\sigma_i^{\textrm{th}}$ 
for each bin $i$ out of $N_{\textrm{bins}}$ by varying it with the statistical uncertainties 
$\delta_i^{\textrm{stat}}$, 
obtained in the procedure described in Section~\ref{sec:pseudo-data_generation}, 
as 
%TODO once more complete uncertainty estimates are there, add them to the variation
$\sigma_i^{\textrm{pd}} = \sigma_i^{\textrm{th}}(1 + r_i \delta_i^{\textrm{stat}})$, 
with $r_i$ a univariate Gaussian random number.
%
The correlated uncertainties for the pseudodata and the theoretical prediction 
are contained in the nuisance parameter vectors $b^{\textrm{pd}}$ and $b^{\textrm{th}}$, respectively, and the uncorrelated uncertainties in $\Delta_i$.
%
Their effect on $\sigma^{\textrm{th}}$ and $\sigma^{\textrm{pd}}$
is described by the matrices $\Gamma_i^{\textrm{pd}}$ and $\Gamma_i^{\textrm{th}}$.
The indices $\alpha$ and $\beta$ then run over the uncertainty nuisance parameters for the pseudodata and the theoretical prediction, respectively.
%
The nuisance parameter values $b^{\textrm{th(min)}}$ that minimize Eq.~\eqref{eq:profilingchi2} give the central PDFs $f'_0$ optimized to the profiled dataset in the form
\begin{equation}
f_0' = f_0
      + \sum_\beta b_\beta^{\textrm{th(min)}} 
        \left(  \frac{f_\beta^+   -  f_\beta^- }{2}
              -    b_\beta^{\textrm{th(min)}}
                \frac{f_\beta^+ + f_\beta^- - 2f_0}{2}
        \right),
\end{equation}
where $f_0$ is the original central PDF and the up and down variation eigenvectors are given by $f^+, f^-$. The decrease in the uncertainties of the shifted PDFs indicates the enhancement that including the FPF data in the global PDF fit could bring. Here, the profiling studies are performed using version 2.2.1 of the \textsc{xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}, extended to support the use of \textsc{PineAPPL} grids~\cite{christopher_schwan_2023_7499507, Carrazza:2020gss}.
%

### 2023-05-24 paper/sec-dis-pseudodata.tex
done intro

@@
-\clearpage
 \section{Projections for LHC neutrino structure functions}
@@
 We begin by describing the procedure adopted to generate
-projections for LHC neutrino DIS structure functions, including
-the models for the expected systematic uncertainties associated
-to the various experiments.
+projections for DIS structure functions associated to LHC neutrinos.
+%
+Assembling these projections requires defining the kinematic acceptance
+and expected yields of the various ongoing and proposed experiments,
+assessing the performance of their response in order to estimate
+the corresponding systematic uncertainties,
+and then evaluating pseudo-data based on specific underlying theory assumption which should be consistent
+with the settings of the subsequent (nuclear) PDF analyses.
 
-\subsection{Recap of DIS kinematics}
+In this section, for completeness first of all we provide a recap of the kinematics
+of neutrino DIS structure function measurements.
+%
+Then we present an overview of the LHC far-forward neutrino detectors that
+will be considered in the present study.
+%
+The calculation of event yields in bins of $x,Q^2$, and neutrino energy $E_\nu$ in terms
+of the incoming neutrino fluxes is presented next, resulting in quantitative predictions
+for the kinematic coverage and statistical uncertainties.
+%
+Finally, we discuss how for each of the considered experiments the dominant systematic
+uncertainties are evaluated and which assumptions are taken about their bin-to-bin correlations.
 
-The double-differential cross-section for neutrino-nucleus scattering
-can be decomposed
-in terms of three independent structure functions $F_i^{\nu A}(x,Q^2)$ with $i=1,2,3$.
+\subsection{Neutrino deep-inelastic scattering}
+
+The theoretical framework underlying neutrino DIS is well known, see e.g.~\cite{Candido:2023utz}
+and references therein.
 %
-Focusing on the charged-current (CC) scattering case, mediated
-by the exchange of a $W^+$ weak boson, the differential
- cross section reads
-\be
-\label{eq:neutrino_DIS_xsec}
-\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/2\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc (1-y)F^{\nu A}_2(x,Q^2) + y^2xF^{\nu A}_1(x,Q^2) + y\lp 1-\frac{y}{2}\rp xF^{\nu A}_3(x,Q^2)\rc  \, ,
-\ee
-where $s=2m_N E_\nu$ is the neutrino-nucleon center of mass energy squared, $m_N$ is the nucleon mass,
-$E_\nu$ is the incoming neutrino energy,
-and the inelasticity $y$ is defined as $y=Q^2/(2x m_n E_{\nu})$.
+For completeness, we provide here a short overview of the neutrino DIS formalism.
 %
-For the time being we are neglecting target mass 
-corrections.
-%
-An analogous expression holds for  antineutrino 
-scattering, mediated
-by the exchange of a $W^-$ weak boson, with the only difference being a sign change
-in front of the parity-violating structure function $xF_3$,
-\be
-\label{eq:antineutrino_DIS_xsec}
-\frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/2\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc (1-y)F^{\bar{\nu} A}_2(x,Q^2) + y^2xF^{\bar{\nu} A}_1(x,Q^2) - y\lp 1-\frac{y}{2}\rp xF^{\bar{\nu} A}_3(x,Q^2)\rc  \, .
-\ee
-While the differential cross-section depends on three kinematic variables, $(x,Q^2,y)$,
-the structure functions themselves depend only on $x$ and $Q^2$.
-%
-Furthermore, both the cross-section and the structure functions depend
-on the atomic mass number $A$ of the target nucleus via nuclear modifications of the free-nucleon
-structure functions.
-
-Alternatively, Eq.~(\ref{eq:neutrino_DIS_xsec}) can be expressed in terms
-of the longitudinal structure function  $F_L^{\nu A}(x,Q^2)$ defined
-by $F_L = F_2-2xF_1$, leading to
+The double-differential cross-section for neutrino-nucleus charged-current scattering
+can be expressed in terms of three
+independent structure functions $F_2^{\nu A}(x,Q^2)$, $xF_3^{\nu A}(x,Q^2)$
+and $F_L^{\nu A}(x,Q^2)$ as follows
 \be
@@
 \ee
+where $s=2m_N E_\nu$ is the neutrino-nucleon center of mass energy squared, $m_N$ is the nucleon mass,
+$E_\nu$ is the incoming neutrino energy,
+and the inelasticity is $y=Q^2/(2x m_n E_{\nu})$.
 %
-Expressing the differential cross-section as in Eq.~(\ref{eq:neutrino_DIS_xsec_FL}) is advantageous
-because in the parton model (and in perturbative QCD at leading order) the longitudinal
-structure function vanishes, $F_L^{\nu A}(x,Q^2)=0$.
+While structure functions depend only on $x$ and $Q^2$, the differential
+cross-section depends also on the neutrino energy $E_\nu$ (or alternatively
+on the inelasticity $y$).
 %
-The combination of neutrino and antineutrino measurements makes possible disentangling
-the different structure functions, for example the cross-section difference
+Structure functions $F^{\nu A}_i(x,Q^2)$ and $F^{\bar{\nu} A}_i(x,Q^2)$ depend on the nuclear target $A$ entering
+for the neutrino scattering through the nuclear modifications of the proton PDFs.
+
+Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) are valid in the  inelastic
+scattering regime, defined as the kinematic region for which the 
+hadronic final-state
+invariant mass $W$  satisfies
 \be
-\label{eq:neutrino_DIS_xsec_FL_diff}
-\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} - \frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy}=  \frac{G_F^2s Y_-}
-{4\pi \lp 1+Q^2/m_W^2\rp^2}\lc    xF^{\nu A}_3(x,Q^2)+  xF^{\bar{\nu} A}_3(x,Q^2)\rc \, ,
+W^2 = \lp m_N^2 + Q^2 \frac{(1-x)}{x} \rp \gsim \lp 2\,{\rm GeV} \rp^2\, ,
 \ee
-is proportional to the parity-violating structure function $xF_3$ averaged over neutrinos
-and antineutrinos.
-
-When both the momentum transfer squared $Q^2$
-and the  hadronic final-state
-invariant mass $W$ given by
-\be
-W^2 = m_N^2 + Q^2 \frac{(1-x)}{x} \, ,
-\ee
-are large enough, $Q^2 \gsim {\rm few~GeV}^2$ and $W \gsim 2$ GeV
-respectively, we find ourselves in the
-deep-inelastic scattering region where
-structure functions can be evaluated in perturbative QCD in terms of a factorised
-convolution of process-dependent partonic scattering cross-sections and
-of process-independent parton distribution functions,
+given that for smaller values of $W^2$  neutrino scattering is dominated by either quasi-elastic scattering
+or the resonance production region.
+%
+Provided the momentum transfer becomes large enough, $Q^2 \gsim {\rm few~GeV}^2$,
+the inelastic structure functions Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL})
+can be decomposed in terms of a convolution of partonic scattering cross-sections  $C_{i,j}^{\nu N}(x,\alpha_s)$ and
+of process-independent PDFs $f^{(A)}_j\lp x,Q^2\rp$, 
 \be
 \label{eq:sfs_pqcd}
- F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g}\int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \quad i = 2,3,L \, ,
+ F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g}\int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \quad i = 2,3,L \, .
  \ee
- where $j$ is an index that runs over all possible partonic initial states
- and $C_{i,j}^{\nu N}$ is the process-dependent (but target-independent) coefficient function.
+ Eq.~(\ref{eq:sfs_pqcd}) holds both for inclusive and for heavy quark production structure functions,
+ thought in the latter case one needs to account for mass-dependent effects.
  %
- The latter can be expressed  as a series expansion in powers of the strong
- coupling $\alpha_s(Q^2)$,
- \be
- \label{eq:coeff_fun_expansion}
- C_{i,j}^{\nu N}(z,\alpha_s(Q^2)) = \sum_{k=0}^m \lp \alpha_s(Q^2) \rp^{k} C_{i,j}^{\nu N(k)}(z) \, .
- \ee
- The leading-order ($k=0$)  term is independent of $\alpha_s$ since the Born scattering
- is mediated by the weak interaction.
+ Neutrino structure functions can be computed up to N$^3$LO for the massless case
+ and up to NNLO (with respect to the Born cross-section) for the charm production
+ case~\cite{Gao:2017kkx}.
  %
- At leading order and considering a proton target, $n_f=4$ active quark flavours,
- neglecting charm mass effects and assuming a diagonal CKM matrix,
- we can express the $F_2^{\nu p}$ and $xF_3^{\nu p}$ structure functions as
- follows
+ We discuss in Sect.~\ref{sec:settings} the
+ tools~\cite{Candido:2022tld,yadism,Candido:2023utz,Carrazza:2020gss} used in this work to
+ evaluate neutrino DIS structure functions in order to generate
+ LHC neutrino pseudo-data.
+ %
+ In this work we don't consider structure functions in the shallow inelastic scattering region (SIS)
+ defined by $Q^2 \lsim {\rm few~GeV}^2$, for which a different approach
+ must the  adopted for their evaluation~\cite{Candido:2023utz}.
+
+ Each different structure function provides complementary sensitivity
+ to the partonic flavour decompositions of nucleons.
+ %
+ To illustrate this sensitivity, one can consider a leading order (LO) calculation
+ for a proton target, $n_f=4$ active quark flavours,
+ neglecting charm mass effects and assuming a diagonal CKM matrix.
+ %
+ In this scenario one can express the $F_2^{\nu p}$ and $xF_3^{\nu p}$ structure functions as
+ follows:
  \bea
@@
  \eea
- The corresponding expressions for a neutron target and or isoscalar target can be obtained
- from isospin symmetry, for instance the LO structure functions for
- neutrino-neutron scattering are
+ The corresponding expressions for a neutron target are obtained from isospin symmetry
  \bea
@@
  xF_3^{\nu n}(x,Q^2) &=& 2x\lp -f_{\bar{d}} + f_u +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
- xF_3^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d - f_{\bar{u}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, . \nonumber
+ xF_3^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d - f_{\bar{u}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, , \nonumber
  \eea
+ while for an isoscalar, free-nucleon target denoted by $N$ one has
+ \bea
+ F_2^{\nu N}(x,Q^2) &=& 2x\lp f_{u^+} + f_{d^+} + 2f_s + 2f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
+ F_2^{\bar{\nu} N}(x,Q^2) &=& 2x\lp f_{u^+} + f_{d^+} + 2f_{\bar{s}} + 2f_c \rp(x,Q^2) \, , \label{eq:neutrinoSFs} \\
+ xF_3^{\nu N}(x,Q^2) &=& 2x\lp f_{u^-} + f_{d^-} +2f_s - 2f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
+ xF_3^{\bar{\nu} N}(x,Q^2) &=& 2x\lp   f_{u^-} + f_{d^-}-2f_{\bar{s}} +2 f_{c}\rp(x,Q^2) \, , \nonumber
+ \eea
+ in terms of the valence and sea PDF combinations defined by
+ \be
+ f_{q^+} (x,Q^2)\equiv \lp f_{q}+f_{\bar{q}}\rp(x,Q^2) \, , \qquad
+ f_{q^-} (x,Q^2)\equiv \lp f_{q}- f_{\bar{q}}\rp(x,Q^2) \, .
+ \ee
+ From this partonic decomposition we see that even for isoscalar targets separate measurements
+ for neutrinos and antineutrinos are not equivalent since in general neither $f_{s^-}$ nor
+ $f_{c^-}$ are expected to vanish.
+
+ In the projections presented in this work, when interpreting the LHC neutrino structure
+ functions in terms of proton PDFs we assume isoscalar free-nucleon targets and neglect
+ nuclear PDF modifications.
+ %
+ When evaluating structure functions for a tungsten (W) target, we keep into account
+ that the target is not isoscalar when evaluating the physical observables.
+
+ \subsection{Far-forward neutrino detectors at the LHC}
+ \label{sec:neutrinoDetectors}
 

### 2023-05-24 paper/sec-introduction.tex

@@
 
+Proton-proton collisions at energy-frontier hadron colliders
+such as the LHC produce an intense collimated flux of neutrinos~\cite{Kling:2021gos}.
+%
+These neutrinos are characterised by the largest energies ever achieved in laboratory experiments
+and reaching up to  several TeV, only surpassed by astrophysical neutrinos.
+%
+Due to the lack of dedicated instrumentation in the LHC far-forward region,
+until recently these neutrinos escaped detection and hence could not be used
+for scientific enquiry.
+%
+This situation changed drastically in  March 2023
+with the reports of the first observation of LHC neutrinos~\cite{FASER:2023zcr} by the
+far-forward  FASER$\nu$~\cite{FASER:2019dxq} and SND@LHC~\cite{SHiP:2020sos} experiments.
+%
+The discovery of LHC neutrinos enables
+unprecedented scientific opportunities
+for particle and astroparticle physics both within the Standard Model and beyond it,
+see~\cite{Anchordoqui:2021ghd,Feng:2022inv}
+and references therein for a comprehensive summary.
+%
+Beyond the ongoing Run III, a dedicated suite of upgraded far-forward
+neutrino experiments hosted by a dedicated
+Forward Physics Facility (FPF)~\cite{Anchordoqui:2021ghd,Feng:2022inv} has been
+proposed to operate concurrently with the HL-LHC.
+
+Among its many possible applications, the high-energy neutrino beam produced by the LHC
+can be deployed as a sensitive probe of hadron structure.
+%
+As well known~\cite{Conrad:1997ne,Mangano:2001mj},
+measurements of neutrino structure functions in deep-inelastic scattering
+(DIS)~\cite{Candido:2023utz} provide valuable information on the parton distribution functions (PDFs)
+of nucleons and nuclei~\cite{Ethier:2020way,Gao:2017yyd,Kovarik:2019xvh}, in particular
+concerning the quark and antiquark PDF flavour separation.
+%
+Furthermore, these constraints from charged-current neutrino DIS are complementary to those
+provided by neutral-current charged-lepton DIS, being sensitive to independent
+flavour combinations.
+%
+With this motivation, several  experiments have in the past measured neutrino-nucleus
+DIS structure functions over a wide range of energies, and neutrino data
+from e.g. the CHORUS~\cite{CHORUS:2005cpn}, NuTeV~\cite{NuTeV:2001dfo},
+CCFR~\cite{Yang:2000ju}, and CDHS~\cite{Berge:1989hr} experiments enter 
+some of the most recent global determinations of proton~\cite{Hou:2019efy,Bailey:2020ooq,NNPDF:2021njg} and
+nuclear PDFs~\cite{AbdulKhalek:2022fyi,Eskola:2021nhw,Muzakka:2022wey}.
+
+As compared to previous neutrino DIS measurements,  LHC data benefits
+from higher neutrino energies  increasing the kinematic coverage
+in the $(x,Q^2)$ plane by an order of magnitude both in the small-$x$
+and the large-$Q^2$ directions~\cite{Feng:2022inv}.
+%
+Furthermore, the large number of expected neutrino scattering events enable
+structure function measurements with excellent precision,
+e.g. the  $\mathcal{O}(10^6)$ muon neutrinos expected at the FPF detectors~\cite{Kling:2021gos}
+enable sub-percent statistical uncertainties for most of the bins in the $(x,Q^2)$ plane.
+%
+However,  so far discussions about the impact of far-forward LHC neutrinos on hadronic structure
+have been restricted to the level  of qualitative estimates.
+%
+The main reason for this limitation is the lack
+of dedicated projections for the LHC neutrino structure function data, including the expected
+statistical and systematic uncertainties for the various operating and proposed detectors.
+
+The main goal of this work is to bridge this gap and quantify
+the expected impact of LHC neutrino DIS data on the PDFs of  nucleons and heavy nuclei
+for the various relevant experiments and for different assumptions about their performance
+and the integrated luminosities.
+%
+In addition to projections for FASER$\nu$ and SND@LHC based on the full Run III luminosity,
+we consider also three of the proposed FPF experiments, FLArE, AdvSND, and FASER$\nu$2.
+%
+For each detector, we generate dedicated  pseudo-data for both inclusive and charm (dimuon)
+structure functions and estimate the event yields as a function of the binning
+in $x$ and $Q^2$.
+%
+Emphasis is devoted to assessing the expected systematic uncertainties
+from the intended acceptance and performance of the LHC neutrino experiments.
+
+Following this DIS pseudo-data generation, we study their impact first
+on the proton PDFs and subsequently on the nuclear PDFs.
+%
+In the former case, this is achieved both by means of the Hessian profiling~\cite{Paukkunen:2014zia}
+of the PDF4LHC21 combination~\cite{PDF4LHCWorkingGroup:2022cjn}
+within the  {\sc\small xFitter} framework~\cite{Alekhin:2014irh} and by means
+of their direct inclusion in the open-source NNPDF fitting framework~\cite{NNPDF:2021uiq}.
+%
+In the latter case, the EPPS21 global nuclear PDF determination~\cite{Eskola:2021nhw}
+is profiled again using {\sc\small xFitter}.
+%
+Theoretical predictions for neutrino DIS structure functions are evaluated with the {\sc\small EKO}~\cite{Candido:2022tld}
+and {\sc\small YADISM}~\cite{yadism,Candido:2023utz} programs interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss}, with the latter providing the fast interpolation grids to be used in the fit.
+%
+To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed.
+
+Qualitatively consistent results are obtained from the analyses using both the {\sc\small xFitter}
+and NNPDF frameworks and reveal that  LHC neutrino scattering, specially
+for the high-statistics  experiments of the FPF, provides  stringent constraints
+disentangling the quark and antiquark (nuclear) PDFs of different flavours.
+%
+We find that the inclusion of systematic uncertainties does not significantly modify the
+impact of these structure function measurements on the PDFs as compared
+to an analysis that considers only statistical errors, unless extreme assumptions on the bin-by-bin
+correlation model are adopted.
+%
+We illustrate the impact that the expected improvements on the (nuclear) PDFs provided 
+on LHC neutrinos may have on precision measurements at the HL-LHC.
+%
+Our analysis demonstrates that detection and analysis of LHC far-forward neutrinos  effectively
+extends the LHC with a charged-current counterpart of the
+US-based Electron-Ion Collider (EIC)~\cite{AbdulKhalek:2021gbh}
+with comparable kinematic reach, therefore realising a ``Neutrino-Ion Collider'' at CERN
+without the need of additional accelerator infrastructure.
+
 The outline of this paper is as follows.
 %
+First of all, in Sect.~\ref{sec:dis_pseudodata} we describe the procedure
+adopted to generate projections for DIS structure functions associated to
+LHC neutrino scattering, including the modelling of experimental systematic
+uncertainties.
+%
+Then in Sect.~\ref{sec:settings} we discuss the theoretical settings used
+for the calculation of DIS structure functions and the methodology adopted
+to account for the constraints of LHC neutrino DIS data on proton and nuclear PDFs.
+%
+The projected impact of these structure functions on proton and nuclear
+PDFs is quantified in Sects.~\ref{sec:protonPDFs} and~\ref{sec:nuclearPDFs} respectively.
+%
+Finally we summarise in Sect.~\ref{sec:summary} and consider some possible
+directions for follow-up research.

### 2023-05-24 paper/sec-nuclearPDFs.tex

\clearpage
\section{Impact on nuclear PDFs}
\label{sec:nuclearPDFs}

Here we study

### 2023-06-04 xFitter/PDF_profiling/PDF4LHC21/statOnly/collectPlots.tex
Adding results corresponding to stat-only and all-syst-unc-uncorrelated cases

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{fontenc}
\usepackage{amsmath}
\usepackage{parskip}
\usepackage[pdftex]{graphicx}
\usepackage{verbatim}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{mathtools}
\usepackage{geometry}	%For manipulating page layout
  \geometry{
  paperwidth=210mm,paperheight=150mm,	%Custom page size, for cropping
  left=0mm,
  right=0mm,
  top=0mm,
  bottom=0mm,
}
\usepackage{float}	%Better control of figure placement
\usepackage{subfig}	%For including subfigures within figures
\usepackage{pdfpages}
\usepackage{listings}	%For including program code
\usepackage{color}
\usepackage{tikz}

\newcommand{\figw}{70mm}
\newcommand{\experiment}{FASERv2}
\newcommand{\unctype}{statOnly}

\begin{document}

FASERv2\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}

\newpage

FASERv2 nochargediscrimination\\
\newcommand{\dataset}{_nochargediscrimination}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}

\newpage

FASERv2 inclusive\\
\renewcommand{\dataset}{_inclusive}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}

\newpage

FASERv2 inclusive nochargediscrimination\\
\renewcommand{\dataset}{_inclusive_nochargediscrimination}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}

\newpage

FASERv2 charm\\
\renewcommand{\dataset}{_charm}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}

\newpage

FASERv2 charm nochargediscrimination\\
\renewcommand{\dataset}{_charm_nochargediscrimination}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}

\end{document}

### 2023-06-19 paper/FPF-WG1.tex
abstract

@@
 {\it \small
-    ~$^1$ UC Irvine  \\[0.1cm]
+    ~$^1$ Department of Physics and Astronomy, University of California, Irvine, CA 92697 USA  \\[0.1cm]
     ~$^2$Department of Physics and Astronomy, Vrije Universiteit, NL-1081 HV Amsterdam\\[0.1cm]
@@
 
-Proton-proton collisions at the LHC produce an intense collimated flux of neutrinos
-characterised by the largest energies (up to several TeV) achieved in laboratory experiments.
+Proton-proton collisions at the LHC produce an intense collimated beam of high-energy neutrinos
+in the forward direction.
 %
-Until recently, these neutrinos escaped detection and hence were lost for physics.
+Their recent  observation by the FASER$\nu$ and SND@LHC experiments
+indicates that this hitherto discarded beam becomes now available for scientific studies.
 %
-The observation in March 2023 of LHC neutrinos by the FASER$\nu$ and SND@LHC experiments
-heralds the beginning of a ``LHC neutrino era'' offering unprecedented scientific opportunities
-for particle and astroparticle physics both within the Standard Model and beyond it.
+Neutrino deep-inelastic scattering (DIS) is known
+to provide a sensitive probe of the quark flavour separation in nucleons
+and nuclei, in particular strangeness.
 %
-Here we assess the expected impact of LHC neutrino deep-inelastic scattering (DIS) structure functions
-on the quark and gluon substructure of nucleons and heavy nuclei.
+Here we assess the expected impact of DIS neutrino structure functions at the LHC
+on the parton distribution functions (PDFs) of protons and heavy nuclei.
 %
-In addition to projections for FASER$\nu$ and SND@LHC based on the full Run III luminosity,
-we also consider the experiments entering the proposed
- Forward Physics Facility (FPF) to operate concurrently with the HL-LHC.
+We consider projections for  FASER$\nu$ and SND@LHC based on the Run III luminosity
+and for the  experiments hosted by the
+ Forward Physics Facility (FPF) operating concurrently with the HL-LHC.
  %
- We generate pseudo-data for inclusive and charm DIS structure functions for these various experiments,
-model their  systematic uncertainties, and quantify their impact
-on proton and nuclear PDFs by means of both  Hessian profiling within {\sc\small xFitter}
-and using the NNPDF framework.
+ By means of both Hessian profiling within {\sc\small xFitter} and
+ of the  NNPDF open-source framework,
+ we demonstrate the significant PDF impact of the high-statistics FPF data
+ on the region $10^{-3}\lsim x \lsim 0.7$, comparable to that covered by the
+ Electron-Ion Collider (EIC) with neutral-current scattering.
 %
-We find the LHC neutrino scattering, specially
-for the high-statistics  experiments at the FPF, provides  stringent constraints
-concerning the separation between quark and antiquark PDFs of different flavours.
-%
-Our analysis demonstrates that detection and analysis of LHC far-forward neutrinos  effectively
-extends the LHC with a charged-current counterpart of the Electron-Ion Collider (EIC)
-with comparable kinematic reach and hence realises a ``Neutrino-Ion Collider'' at CERN.
+ Our analysis highlights how exploiting the potential
+ of this unique neutrino beam  effectively
+extends the LHC with a ``Neutrino-Ion Collider''.
 

### 2023-06-19 paper/sec-dis-pseudodata.tex
introduction

@@
  \label{sec:neutrinoDetectors}
+
+ \subsection{Modelling DIS structure functions}
+
+ %
+Theoretical predictions for neutrino DIS structure functions are evaluated with the {\sc\small EKO}~\cite{Candido:2022tld}
+and {\sc\small YADISM}~\cite{yadism,Candido:2023utz} programs interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss}, with the latter providing the fast interpolation grids to be used in the fit.
+%
+To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed.
 

### 2023-06-19 paper/sec-introduction.tex
introduction

--- 2023-05-09 paper/sec-introduction.tex
@@
 
+Proton-proton collisions at energy-frontier hadron colliders
+such as the LHC produce an intense collimated flux of neutrinos~\cite{Kling:2021gos}.
+%
+These neutrinos are characterised by the largest energies ever achieved in laboratory experiments,
+reaching up to several TeV.
+%
+Due to the lack of dedicated instrumentation in the LHC far-forward region,
+until recently these neutrinos escaped detection.
+%
+The reported observation of LHC neutrinos~\cite{FASER:2023zcr,SNDLHC:2023pun} by the
+far-forward  FASER$\nu$~\cite{FASER:2019dxq} and SND@LHC~\cite{SHiP:2020sos,SNDLHC:2022ihg} experiments
+demonstrates that this hitherto discarded beam can now be deployed for physics studies.
+%
+Beyond the ongoing Run III, a dedicated suite of upgraded far-forward
+neutrino experiments hosted by a
+Forward Physics Facility (FPF)~\cite{Anchordoqui:2021ghd,Feng:2022inv} has been
+proposed to operate concurrently with the High-Luminosity LHC~\cite{Azzi:2019yne,Cepeda:2019klc}.
+%
+LHC neutrinos enable
+unprecedented scientific opportunities
+for particle and astroparticle physics both within the Standard Model and beyond it,
+as summarised in~\cite{Anchordoqui:2021ghd,Feng:2022inv}
+and references therein.
+
+As well known~\cite{Conrad:1997ne,Mangano:2001mj},
+measurements of neutrino structure functions~\cite{Candido:2023utz} in deep-inelastic scattering
+(DIS) provide sensitive information on the parton distribution functions (PDFs)
+of nucleons and nuclei~\cite{Ethier:2020way,Gao:2017yyd,Kovarik:2019xvh}, in particular
+they probe the quark/antiquark  flavour separation including
+strangeness~\cite{NuTeV:2007uwm,CCFR:1994ikl,Faura:2020oom,NOMAD:2013hbk}.
+%
+These constraints, arising from charged-current DIS, are fully complementary to those
+provided by neutral-current charged-lepton DIS given that they reveal independent
+flavour combinations.
+%
+Several  experiments have measured neutrino-nucleus
+DIS structure functions over a wide range of energies, and neutrino data
+from the CHORUS~\cite{CHORUS:2005cpn}, NuTeV~\cite{NuTeV:2001dfo},
+CCFR~\cite{Yang:2000ju}, and CDHS~\cite{Berge:1989hr}
+and other experiments is routinely  included in global
+determinations of proton~\cite{NNPDF:2021njg,Hou:2019efy,Bailey:2020ooq} and nuclear
+PDFs~\cite{Eskola:2021nhw,AbdulKhalek:2022fyi,Muzakka:2022wey}.
+
+As compared to these previous experiments,
+the unique benefit of LHC neutrinos is their energy spectrum, reaching
+energies up to a factor 10 higher (several TeV).
+%
+This feature, together with the large statistics (up to $10^6$ muon neutrinos detected at the FPF~\cite{Kling:2021gos}),  strongly suggest that the LHC  neutrino beam should be
+deployed as a precise probe of hadron structure, complementing
+and extending available results by an order of magnitude both at small-$x$
+and large-$Q^2$~\cite{Feng:2022inv}.
+%
+However, we currently lack  dedicated projections for the kinematic coverage
+and accuracy expected for LHC neutrino structure functions,
+including bin-by-bin statistical and systematic uncertainties and their
+correlations, for the various operating and proposed detectors.
+%
+The lack of these projections
+has so far prevented quantitative studies assessing the impact
+of LHC neutrinos in global fits of proton and nuclear PDFs along the lines
+of those performed for the HL-LHC~\cite{AbdulKhalek:2018rok}, the Electron-Ion Collider (EIC)~\cite{AbdulKhalek:2021gbh,Khalek:2021ulf}, and the
+Large Hadron electron Collider (LHeC)~\cite{AbdulKhalek:2019mps,LHeC:2020van}.
+
+The goal of this work is to bridge this gap and quantify
+the expected impact of  DIS structure functions from the LHC
+neutrino beam on the proton and nuclear PDFs.
+%
+To this end, we carry out projections for  FASER$\nu$ and SND@LHC based on the full Run III luminosity
+as well as for  three of the proposed experiments to be hosted
+at the FPF~\cite{Anchordoqui:2021ghd,Feng:2022inv}: FLArE, AdvSND, and FASER$\nu$2.
+%
+For each experiment, we determine the expected event yields in bins in $x$, $Q^2$,
+and neutrino energy $E_\nu$,
+generate pseudo-data for  inclusive and charm 
+structure functions, 
+and estimate the main systematic uncertainties and their correlation pattern.
+%
+Subsequently, we study their impact on the proton PDFs by means of the Hessian profiling~\cite{Paukkunen:2014zia}
+of the PDF4LHC21 combination~\cite{PDF4LHCWorkingGroup:2022cjn}
+within the  {\sc\small xFitter} framework~\cite{Alekhin:2014irh}, cross-checked
+with their direct inclusion in the open-source NNPDF fitting framework~\cite{NNPDF:2021uiq}.
+%
+We also assess their impact on the PDFs of tungsten (target of FASER$\nu$ and SND@LHC)
+using the EPPS21 global nuclear PDF fit~\cite{Eskola:2021nhw}
+profiled with {\sc\small xFitter}.
+
+Our analysis reveals that  neutrino structure function measurements at the LHC, specially
+for the high-statistics  experiments of the FPF, provides  stringent constraints
+on the quark and antiquark (nuclear) PDFs, specially on the up and down
+antiquarks and on strangeness, as compared to state-of-the-art (n)PDF determinations.
+%
+The best-case scenario when only statistical errors are considered is not
+significantly distorted upon the inclusion of realistic systematic errors.
+%
+We make the resulting (n)PDF sets publicly available, as well as the DIS pseudo-data projections
+for the various scenarios for the systematic uncertainties considered.
+%
+Our work demonstrates that detection of LHC far-forward neutrinos  effectively
+extends the LHC with a charged-current counterpart of the EIC,
+with similar kinematic reach and complementary charged-current reactions,
+therefore realising (upon Lorentz-boosting) the analog of a ``Neutrino-Ion Collider'' at CERN
+without the need of additional accelerator infrastructure.
+
 The outline of this paper is as follows.
 %
+First, in Sect.~\ref{sec:dis_pseudodata} we describe the procedure
+adopted to generate projections for DIS structure functions associated to
+LHC neutrino scattering, including the modelling of experimental systematic
+uncertainties.
+%
+Then in Sect.~\ref{sec:settings} we discuss the theoretical settings used
+for the calculation of DIS structure functions and the methodology adopted
+to account for the constraints of LHC neutrino DIS data on proton and nuclear PDFs.
+%
+The projected impact of these structure functions on proton and nuclear
+PDFs is quantified in Sects.~\ref{sec:protonPDFs} and~\ref{sec:nuclearPDFs} respectively.
+%
+Finally we summarise in Sect.~\ref{sec:summary} and consider some possible
+directions for follow-up research.

### 2023-06-19 paper/sec-analysis.tex
working on sect 2

@@
 %
+
+\subsection{Modelling DIS structure functions}
+
+ %
+Theoretical predictions for neutrino DIS structure functions are evaluated with the {\sc\small EKO}~\cite{Candido:2022tld}
+and {\sc\small YADISM}~\cite{yadism,Candido:2023utz} programs interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss}, with the latter providing the fast interpolation grids to be used in the fit.
+%
+To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed

### 2023-06-19 paper/sec-dis-pseudodata.tex
working on sect 2

--- 2023-05-09 paper/sec-dis-pseudodata.tex
@@
-\clearpage
-\section{Projections for LHC neutrino structure functions}
+\section{DIS pseudo-data generation}
 \label{sec:dis_pseudodata}
 
-We begin by describing the procedure adopted to generate
-projections for LHC neutrino DIS structure functions, including
-the models for the expected systematic uncertainties associated
-to the various experiments.
+Here we describe the procedure adopted in order 
+to generate projections for the kinematic coverage
+and experimental uncertainties associated to differential measurements
+of neutrino-nucleus scattering at the LHC far-forward experiments.
+%
+First, we summarise the theoretical description of differential
+neutrino scattering in terms of DIS structure functions and highlight
+their PDF sensitivity.
+%
+Second, we present an  overview of the operative and proposed
+LHC far-forward neutrino detectors that
+will be considered in the present study and indicate their
+key acceptance and performance parameters.
+%
+By convoluting the expected muon neutrino fluxes
+with the acceptance and scattering rates of each
+of these detectors,
+we compute the foreseen event yields in bins of $x$, $Q^2$,
+and $E_\nu$ and therefore the associated statistical uncertainties.
+%
+Finally, we estimate how the dominant systematic
+uncertainties in each experiment translate into uncertainties in the predicted
+event rates and use this information to complete the calculation of the experimental
+covariance matrix.
 
-\subsection{Recap of DIS kinematics}
+\subsection{Neutrino DIS revisited}
 
-The double-differential cross-section for neutrino-nucleus scattering
-can be decomposed
-in terms of three independent structure functions $F_i^{\nu A}(x,Q^2)$ with $i=1,2,3$.
-%
-Focusing on the charged-current (CC) scattering case, mediated
-by the exchange of a $W^+$ weak boson, the differential
- cross section reads
-\be
-\label{eq:neutrino_DIS_xsec}
-\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/2\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc (1-y)F^{\nu A}_2(x,Q^2) + y^2xF^{\nu A}_1(x,Q^2) + y\lp 1-\frac{y}{2}\rp xF^{\nu A}_3(x,Q^2)\rc  \, ,
-\ee
-where $s=2m_N E_\nu$ is the neutrino-nucleon center of mass energy squared, $m_N$ is the nucleon mass,
-$E_\nu$ is the incoming neutrino energy,
-and the inelasticity $y$ is defined as $y=Q^2/(2x m_n E_{\nu})$.
-%
-For the time being we are neglecting target mass 
-corrections.
-%
-An analogous expression holds for  antineutrino 
-scattering, mediated
-by the exchange of a $W^-$ weak boson, with the only difference being a sign change
-in front of the parity-violating structure function $xF_3$,
-\be
-\label{eq:antineutrino_DIS_xsec}
-\frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/2\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc (1-y)F^{\bar{\nu} A}_2(x,Q^2) + y^2xF^{\bar{\nu} A}_1(x,Q^2) - y\lp 1-\frac{y}{2}\rp xF^{\bar{\nu} A}_3(x,Q^2)\rc  \, .
-\ee
-While the differential cross-section depends on three kinematic variables, $(x,Q^2,y)$,
-the structure functions themselves depend only on $x$ and $Q^2$.
-%
-Furthermore, both the cross-section and the structure functions depend
-on the atomic mass number $A$ of the target nucleus via nuclear modifications of the free-nucleon
-structure functions.
-
-Alternatively, Eq.~(\ref{eq:neutrino_DIS_xsec}) can be expressed in terms
-of the longitudinal structure function  $F_L^{\nu A}(x,Q^2)$ defined
-by $F_L = F_2-2xF_1$, leading to
+The double-differential cross-section for neutrino-nucleus charged-current scattering,
+see~\cite{Candido:2023utz} and references therein,
+can be expressed in terms of 
+independent structure functions $F_2^{\nu A}$, $xF_3^{\nu A}$
+and $F_L^{\nu A}$:
 \be
@@
 \ee
+where $s=2m_N E_\nu$ being the neutrino-nucleon center of mass energy squared, $m_N$ is the nucleon mass,
+$E_\nu$ is the incoming neutrino energy,
+and the inelasticity is $y=Q^2/(2x m_n E_{\nu})$.
 %
-Expressing the differential cross-section as in Eq.~(\ref{eq:neutrino_DIS_xsec_FL}) is advantageous
-because in the parton model (and in perturbative QCD at leading order) the longitudinal
-structure function vanishes, $F_L^{\nu A}(x,Q^2)=0$.
+Structure functions depend only on $x$ and $Q^2$ while the differential
+cross-section depends also on the neutrino energy $E_\nu$, or alternatively
+on the inelasticity $y$.
 %
-The combination of neutrino and antineutrino measurements makes possible disentangling
-the different structure functions, for example the cross-section difference
+Further, structure functions $F^{\nu A}_i(x,Q^2)$ and $F^{\bar{\nu} A}_i(x,Q^2)$ depend on the nuclear target $A$ entering
+for the neutrino scattering through the nuclear modifications of the proton PDFs.
+
+Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) are valid provided
+the hadronic 
+invariant mass $W$  is above the resonance threshold,
 \be
-\label{eq:neutrino_DIS_xsec_FL_diff}
-\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} - \frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy}=  \frac{G_F^2s Y_-}
-{4\pi \lp 1+Q^2/m_W^2\rp^2}\lc    xF^{\nu A}_3(x,Q^2)+  xF^{\bar{\nu} A}_3(x,Q^2)\rc \, ,
+W^2 = \lp m_N^2 + Q^2 \frac{(1-x)}{x} \rp \gsim \lp 2\,{\rm GeV} \rp^2\, ,
 \ee
-is proportional to the parity-violating structure function $xF_3$ averaged over neutrinos
-and antineutrinos.
-
-When both the momentum transfer squared $Q^2$
-and the  hadronic final-state
-invariant mass $W$ given by
-\be
-W^2 = m_N^2 + Q^2 \frac{(1-x)}{x} \, ,
-\ee
-are large enough, $Q^2 \gsim {\rm few~GeV}^2$ and $W \gsim 2$ GeV
-respectively, we find ourselves in the
-deep-inelastic scattering region where
-structure functions can be evaluated in perturbative QCD in terms of a factorised
-convolution of process-dependent partonic scattering cross-sections and
-of process-independent parton distribution functions,
+and in addition here we  restrict ourselves to the DIS region with perturbative momentum
+transfers $Q^2$, such that
+ structure functions are decomposed as
 \be
 \label{eq:sfs_pqcd}
- F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g}\int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \quad i = 2,3,L \, ,
+ F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g}\int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \quad i = 2,3,L \, .
  \ee
- where $j$ is an index that runs over all possible partonic initial states
- and $C_{i,j}^{\nu N}$ is the process-dependent (but target-independent) coefficient function.
 %
- The latter can be expressed  as a series expansion in powers of the strong
- coupling $\alpha_s(Q^2)$,
- \be
- \label{eq:coeff_fun_expansion}
- C_{i,j}^{\nu N}(z,\alpha_s(Q^2)) = \sum_{k=0}^m \lp \alpha_s(Q^2) \rp^{k} C_{i,j}^{\nu N(k)}(z) \, .
- \ee
- The leading-order ($k=0$)  term is independent of $\alpha_s$ since the Born scattering
- is mediated by the weak interaction.
+in terms of a convolution of partonic scattering cross-sections  $C_{i,j}^{\nu N}(x,\alpha_s)$ and
+of process-independent PDFs $f^{(A)}_j\lp x,Q^2\rp$.
 %
- At leading order and considering a proton target, $n_f=4$ active quark flavours,
- neglecting charm mass effects and assuming a diagonal CKM matrix,
- we can express the $F_2^{\nu p}$ and $xF_3^{\nu p}$ structure functions as
- follows
+A similar expression holds for charm production~\cite{Faura:2020oom}, which requires
+accounting also for charm mass effects~\cite{Gao:2017kkx}.
+ %
+We discuss in Sect.~\ref{sec:settings} the theoretical
+settings adopted~\cite{Candido:2022tld,yadism,Candido:2023utz,Carrazza:2020gss} to
+evaluate predictions for
+neutrino DIS structure functions, Eq.~(\ref{eq:sfs_pqcd}),
+and for differential cross-sections,
+Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}),
+in the kinematic range of relevance for LHC neutrinos.
+
+ Each neutrino structure function provides complementary sensitivity
+ to the partonic flavour decompositions of nucleons.
+ %
+ To illustrate this sensitivity, consider a leading order  calculation
+ for a proton target with $n_f=4$ active quark flavours,
+a diagonal CKM matrix and no heavy quark mass effects.
+ %
+ The resulting $F_2^{\nu p}$ and $xF_3^{\nu p}$ structure functions read
  \bea
  F_2^{\nu p}(x,Q^2) &=& 2x\lp f_{\bar{u}} + f_{d} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
- F_2^{\bar{\nu} p}(x,Q^2) &=& 2x\lp f_u + f_{\bar{d}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:neutrinoSFs} \\
+ F_2^{\bar{\nu} p}(x,Q^2) &=& 2x\lp f_u + f_{\bar{d}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:neutrinoSFs_proton} \\
  xF_3^{\nu p}(x,Q^2) &=& 2x\lp -f_{\bar{u}} + f_d +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
@@
  \eea
- The corresponding expressions for a neutron target and or isoscalar target can be obtained
- from isospin symmetry, for instance the LO structure functions for
- neutrino-neutron scattering are
+ The corresponding expressions for a neutron target are obtained from isospin symmetry
  \bea
  F_2^{\nu n}(x,Q^2) &=& 2x\lp f_{\bar{d}} + f_{u} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
- F_2^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d + f_{\bar{u}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:antineutrinoSFs} \\
+ F_2^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d + f_{\bar{u}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:antineutrinoSFs_neutron} \\
  xF_3^{\nu n}(x,Q^2) &=& 2x\lp -f_{\bar{d}} + f_u +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
- xF_3^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d - f_{\bar{u}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, . \nonumber
+ xF_3^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d - f_{\bar{u}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, , \nonumber
  \eea
+ while for an isoscalar, free-nucleon target denoted by $N$ one has
+ \bea
+ F_2^{\nu N}(x,Q^2) &=& 2x\lp f_{u^+} + f_{d^+} + 2f_s + 2f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
+ F_2^{\bar{\nu} N}(x,Q^2) &=& 2x\lp f_{u^+} + f_{d^+} + 2f_{\bar{s}} + 2f_c \rp(x,Q^2) \, , \label{eq:neutrinoSFs_isoscalar} \\
+ xF_3^{\nu N}(x,Q^2) &=& 2x\lp f_{u^-} + f_{d^-} +2f_s - 2f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
+ xF_3^{\bar{\nu} N}(x,Q^2) &=& 2x\lp   f_{u^-} + f_{d^-}-2f_{\bar{s}} +2 f_{c}\rp(x,Q^2) \, , \nonumber
+ \eea
+ in terms of the valence and sea PDF combinations defined by
+ \be
+ f_{q^+} (x,Q^2)\equiv \lp f_{q}+f_{\bar{q}}\rp(x,Q^2) \, , \qquad
+ f_{q^-} (x,Q^2)\equiv \lp f_{q}- f_{\bar{q}}\rp(x,Q^2) \, .
+ \ee
+ We note that even for isoscalar targets separate measurements
+ for neutrinos and antineutrinos will not be equivalent, since in general neither $f_{s^-}$ nor
+ $f_{c^-}$ are expected to vanish.
+
+ In the projections presented in this work, when interpreting the LHC neutrino structure
+ functions in terms of proton PDFs we will assume a isoscalar free-nucleon target and neglect
+ nuclear PDF modifications, along the lines of Eq.~(\ref{eq:neutrinoSFs_isoscalar}).
+ %
+ On the other hand, when evaluating structure functions
+ for a tungsten (W) target, we keep into account both
+ nuclear corrections and that
+ the target is not isoscalar when evaluating the physical observables.
+ %
+ We point out that accounting for nuclear target effects in a global proton
+ PDF fit is straightforward by means of the procedure developed
+ in~\cite{Ball:2020xqw,Ball:2018twp}.
+
+ It is illustrative to compare the PDF dependence of neutrino structure functions
+ at LO with that of their counterparts for neutral-current
+ scattering with a charged lepton projectile.
+ %
+ Within the same assumptions, for energies below
+ the $Z$-boson mass, $Q^2 \ll m_Z$, the corresponding
+ partonic decomposition is
+ the 
+ \bea
+ F_2^{\ell p}(x,Q^2) &=& x\lp \frac{4}{9}\lc f_{u^+} + f_{c^+}\rc
+ + \frac{1}{9}\lc f_{d^+} + f_{s^+}\rc\rp(x,Q^2) \, , \nonumber  \\
+ F_2^{\ell n}(x,Q^2) &=& x\lp \frac{4}{9}\lc f_{d^+} + f_{c^+}\rc
+ + \frac{1}{9}\lc f_{u^+} + f_{s^+}\rc\rp(x,Q^2) \, ,\label{eq:NC_chargedlepton}   \\
+ F_2^{\ell N}(x,Q^2) &=& x\lp \frac{5}{18}\lc f_{u^+} + f_{d^+}\rc
+ + \frac{1}{9} f_{s^+} + \frac{4}{9} f_{c^+} \rp(x,Q^2) \, , \nonumber  
+ \eea
+ with $xF_3$ being negligible in this region.
+ %
+ Eq.~(\ref{eq:NC_chargedlepton}) showcases the complementarity between
+ neutrino and charged-lepton DIS in terms of sensitivity
+ to the flavour PDF decomposition.
+
+ \subsection{Far-forward neutrino detectors at the LHC}
+ \label{sec:neutrinoDetectors}
+
+ As we discuss below, the calculation of differential neutrino scattering event rates
+ at the LHC far-forward detectors requires two main ingredients: the energy
+ and flavour dependence of the incoming neutrino flux crossing
+ the detector fiducial volume, on the one hand,
+ and the scattering rates within the same fiducial volume, on the other hand.
+ %
+ In this section, we summarise the main features of each of the ongoing and future
+ far-forward detectors considered in this study, in particular concerning
+ their acceptance, geometry, and neutrino detection method.
+ %
+ We also indicate the expected performance of the three FPF detectors
+ and how this translates into the dominant experimental systematic
+ uncertainties.
 

### 2023-06-19 paper/sec-dis-pseudodata.tex
more work on sect 2

@@
  uncertainties.
+ %
+ Since for the projection studies considered in this work we focus on muon
+ neutrino scattering, we will focus the subsequent discussion on the detection
+ performance of this neutrino flavour.
 
-\subsection{DIS pseudo-data generation}
+ Table~\ref{tab:FPF_experiments} indicates
+ the rapidity coverage, target material,
+ muon neutrino acceptance, and the identification and reconstruction performance
+ for each of the far-forward LHC neutrino experiments considered
+ in this work.
+ %
+ More details of the information listed in this table is provided
+ in the following.
+
+  %-----------------------------------------------------------------
+\begin{table}[h!]
+  \centering
+  \small
+  \renewcommand{\arraystretch}{1.60}
+\begin{tabularx}{\textwidth}{Xcccc}
+\toprule
+Detector &  Rapidity &  Target &  Acceptance  & Performance \\
+\midrule
+FASER$\nu$  &   &     &       &              \\
+SND@LHC  &   &     &       &              \\
+\midrule
+FASER$\nu$2  &   &     &       &              \\
+AdvSND  &   &     &       &              \\
+FLArE  &   &     &       &              \\
+  \bottomrule
+\end{tabularx}
+\vspace{0.2cm}
+\caption{\small For each of the far-forward LHC neutrino experiments considered
+  in this work we indicate their rapidity coverage, target material,
+  muon neutrino acceptance, and the identification and reconstruction performance.
+  \label{tab:FPF_experiments}
+}
+\end{table}
+%-----------------------------------------------------------------
+
+ \paragraph{AdvSND.}
+ %
+ The AdvSND far-detector will be able to track muons with energy $E_\nu \gsim 20$ GeV
+ within an acceptance of 100 mrad with information on the charge
+ of the  outgoing charged leptons.
+ %
+ The total energy of the hadronic final state can also be measured.
+ %
+ A proposed ``near-detector'' companion is being discussed for AdvSND, but
+ it would not be installed in the FPF and hence is not discussed here further.
+
+ \paragraph{FLArE.}
+ %
+ A liquid argon (LAr) detector able to track muon neutrinos
+ with energies  $E\le 1.5~\rm{TeV}$ with
+ a scattering angle reaching up to 0.4 mrad.
+ %
+ No information on the sign of the charged leptons can be extracted.
+ %
+ Reconstruction of the total energy of the hadronic final state should be
+ possible. 
+ %
+ A $\delta E_\nu\sim$30\% of energy resolution is
+ the target performance for muons, with an associated
+ $\delta \sim 5$ mrad of angular  resolution.
+
+ % Table coverage + detector performance
+
+\subsection{Differential event rate calculation}
 \label{sec:pseudo-data_generation}
@@
 
-\subsection{Systematic Effects on Pseudodata}
+\subsection{Estimating systematic uncertainties}
+
 We now wish to understand the impact of systematic uncertainties on the event rate in $(x,Q^2,E_{\nu})$ space.
@@
 \end{figure}
-
-\subsection{Experimental acceptance performance}
-
-\paragraph{AdvSND} 
-\begin{itemize}
-    \item The detectors will be able to track muons that have energy greater
-    than $20~\rm{GeV}$ (the values for the other charged leptons remain to be
-    determined) with an acceptance angle of 100 mrad for the muons and 
-    500 mrad for the both electrons and tau.
-    \item In addition, the information on the charge of the outgoing leptons
-    can also be accessed.
-    \item It should also be possible to reconstruct the hadronic final states
-    by measuring the total energy.
-\end{itemize}
-
-\paragraph{FLArE}
-\begin{itemize}
-    \item The detectors will be able to detect electrons with energy up to
-    $1~\rm{TeV}$ and an acceptance angel as high as 0.5 rad. For the muons,
-    the detectors will only be able to track them up to $1.5~\rm{GeV}$ with
-    a scattering angle reaching up to 0.4 mrad. The reconstruction of the
-    tau's angle and energy instead will be very difficult. However, it might
-    be possible to find the vertex of a particular tau decay if fine position
-    resolution is achieved.
-    \item With the current baseline design of the detector, it will not be
-    possible to access the information on the sign of the charged leptons.
-    \item It should also be possible to reconstruct the hadronic final
-    states but the reconstruction efficiency and particles will depend on
-    the type of particles. It is expected that the final states hadrons will
-    be dominated by pions, protons, and neutrons.
-    \item Regarding the systematic errors on the charged lepton energy and
-    scattering angle, it is expected to get $5\%$ energy resolution for
-    electrons and about 15 mrad in angular resolution. Due to the large
-    missing energy in the detector, $30\%$ energy resolution is probably
-    achievable for muons with about 5 mrad angular resolution.
-\end{itemize}

### 2023-06-20 paper/sec-dis-pseudodata.tex
sect 2

@@
   %-----------------------------------------------------------------
-\begin{table}[h!]
+\begin{table}[t]
   \centering
   \small
-  \renewcommand{\arraystretch}{1.60}
-\begin{tabularx}{\textwidth}{Xcccc}
+  \renewcommand{\arraystretch}{1.50}
+\begin{tabularx}{\textwidth}{Xccccc}
 \toprule
-Detector &  Rapidity &  Target &  Acceptance  & Performance \\
+Detector &  Rapidity &  Target & Lepton sign & Acceptance  & Performance \\
 \midrule
-FASER$\nu$  &   &     &       &              \\
-SND@LHC  &   &     &       &              \\
+\multirow{2}{*}{FASER$\nu$}  &   &   Tungsten  & \multirow{2}{*}{muons}      &     &         \\
+  &   &   (1.1 ton)  &       &     &         \\
 \midrule
-FASER$\nu$2  &   &     &       &              \\
-AdvSND  &   &     &       &              \\
-FLArE  &   &     &       &              \\
+\multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &       &       &       \\
+  &   &  (0.83 ton)   &       &       &       \\
+\midrule
+\midrule
+\multirow{3}{*}{FASER$\nu$2}  &   & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{only muons}     &   $E_\ell \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
+  &   &  \multirow{2}{*}{(20 ton)}   &       &  $\tan \theta_\ell \lsim 0.5$   &   $\delta \theta_\ell \sim 1$ mrad      \\
+  &   &     &       &  reconstructed $E_h$ \& charm ID   &  $\delta E_h \sim 30\%$        \\
+\midrule
+\multirow{3}{*}{AdvSND~(far)}  &   \multirow{3}{*}{ $7.2 \le \eta_\nu \le 8.4$}  &
+\multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{only muons}    &  $E_\mu \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
+  &   &   \multirow{2}{*}{(5 ton)}  &        & $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$     &           \\
+  &   &     &       &  reconstructed $E_h$   &           \\
+\midrule
+\multirow{3}{*}{FLArE}  & \multirow{3}{*}{Liquid Argon}  &  & \multirow{3}{*}{ maybe muons}  &  $E_\mu \lsim 2$ GeV, $E_e \lsim 1$ TeV    &    $\delta E_e \sim 5\% $ \\
+&   &     &   & $\theta_\mu \lsim 0.4$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $ mrad   \\
+ &   &     &  & reconstructed $E_h$  &    $\delta E_h \sim 30\% $   \\
   \bottomrule
@@
 \caption{\small For each of the far-forward LHC neutrino experiments considered
-  in this work we indicate their rapidity coverage, target material,
-  muon neutrino acceptance, and the identification and reconstruction performance.
+  in this work, we indicate their rapidity coverage, target material, whether
+  they can identify the sign of the outgoing charged lepton,
+  the detector acceptance for the charged lepton and hadronic final state,
+  and the expected reconstruction performance.
+  %
+  We consider separately the acceptance and performance for electron and muon
+  neutrinos.
+  %
+  Tau neutrinos have much lower production rates and are not considered in this study.
+  %
+  See the description of each experiment in the text for more details.
   \label{tab:FPF_experiments}
@@
 
+\paragraph{FASER$\nu$.}
+%
+The ForwArd Search ExpeRiment (FASER) detector and its companion FASER$\nu$
+are located at the TI12 tunnel of the CERN accelerator complex.
+%
+Both detectors are aligned
+with the collision axis LOS  and have been taking data since the begin of Run III.
+%
+Neutrino scattering takes place in the FASER$\nu$
+detector, composed by interleaved emulsion and tungsten plates and
+adding up to a mass of 1.1 tons with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 30~{\rm cm}$.
+%
+The FASER/FASER$\nu$ apparatus is immersed in a magnetic field which enables charged lepton
+identification, provided by two 1 m-long dipole magnets with $B=0.57$ T
+and another 1.5 m-long magnet in front of the spectrometer. 
+%
+Neutrino detection and identification can be carried out either using the emulsion
+films of FASER$\nu$2, which have the key benefit of excellent position and angular resolution,
+or instead using the electronic detector components of FASER, which enable the tagging
+of the outgoing downstream energetic muons.
+
+\paragraph{SND@LHC.}
+%
+In the same manner as FASER, the SND@LHC experiment is located in a service tunnel (TI18)
+around 500 meters from the ATLAS interaction point and has been taking data
+since the  beginning of Run 3.
+%
+SND@LHC is installed off the LOS axis in order to cover the neutrino
+pseudo-rapidity range of $7.2 \le \eta_\nu \le 8.4$.
+%
+With a total fiducial volume of 830 kg, it is composed by tungsten plates,
+where neutrino scattering takes place, interleaved with nuclear emulsions and electronic tracker
+components.
+%
+Downstream, the scattering volume is followed by a hadronic calorimeter and a muon tracking system.
+%
+The electromagnetic
+ and hadronic energy deposits can be measured at the electronic detectors, with the emulsion
+ components providing vertex reconstruction.
+ %
+ The lack of magnetic field prevents the charge-sign identification of the outgoing charged leptons.
+
+\paragraph{FASER$\nu$2.}
+%
+A 20-ton neutrino experiment located on the line of sight (LOS)
+of the LHC neutrino beam.
+%
+It is based on an emulsion-based detector optimised to identify heavy flavor particles, including
+tau leptons and charm and beauty particles, arising from neutrino interactions.
+%
+The FASER$\nu$2 detector is composed of 3300 emulsion layers interleaved with 2-mm-thick tungsten plates,
+for a total volume of  tungsten of $40~\rm{cm} \times 40~\rm{cm} \times 6.6~{\rm m}$.
+%
+The combination of FASER$\nu$2  with the nearby FASER2 detector, equipped with a spectrometer, makes measurements of the outgoing muon charge possible.
+
  \paragraph{AdvSND.}
  %
- The AdvSND far-detector will be able to track muons with energy $E_\nu \gsim 20$ GeV
- within an acceptance of 100 mrad with information on the charge
- of the  outgoing charged leptons.
+ This experiment consists on  two detectors, a far-detector to be installed
+ at the FPF with a coverage in neutrino pseudorapidity $\eta_\nu$ of $7.2 \le \eta_\nu \le 8.4$
+ (hence off-LOS) and a near detector installed somewhere else in LHC
+ complex and covering the range $4 \le \eta_\nu \le 5$.
  %
- The total energy of the hadronic final state can also be measured.
+ In the following we focus on the AdvSND far-detector.
  %
- A proposed ``near-detector'' companion is being discussed for AdvSND, but
- it would not be installed in the FPF and hence is not discussed here further.
+ It would be
+ composed (from upstream to downstream) by a target region
+ for  vertex reconstruction and electromagnetic energy measurement, followed  by a hadronic calorimeter, a  muon identification system, and finally  a magnet enabling muon charge and momentum measurements.
+ %
+ The target region of the detector, where the neutrino interactions take place, is made of thin sensitive layers interleaved with tungsten plates, for a total mass of 5 tons.
+ %
+ This detector configuration will be able to track muons with energy $E_\nu \gsim 20$ GeV
+ within an acceptance of 100 mrad and provide information on the charge
+ of the  outgoing muon thanks to its magnet.
+ %
+ The total energy of the hadronic final state will be measured
+ in the hadronic calorimeter.
 
@@
  %
- A liquid argon (LAr) detector able to track muon neutrinos
- with energies  $E\le 1.5~\rm{TeV}$ with
- a scattering angle reaching up to 0.4 mrad.
+ Building upon recent progress in liquid noble gas neutrino detectors over the last decade (ICARUS, MicroBooNE, SBND, ProtoDUNE, DUNE), this experiment relies on a modularized liquid argon (LAr) time projection detector.
  %
- No information on the sign of the charged leptons can be extracted.
+ The use of LAr as target is particularly beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimeter spatial resolution in all three dimensions.
  %
- Reconstruction of the total energy of the hadronic final state should be
+ FLArE is suitable to identify high-energy neutrinos ($E_\nu \gsim 100$ GeV)  from all three generations
+ while  fully containing the events as required for kinematic reconstruction.
+ %
+ The detector will be equipped with a magnetized hadron/muon calorimeter downstream of the liquid argon volume
+ for muon charge and momentum measurements.
+ %
+ With an expected fiducial (active) mass of 10 tons (30 tons), FLArE will
+ detect muon neutrinos with energies  $E_\mu\lsim 1.5~\rm{TeV}$ and
+ scattering angles up to 0.4 mrad.
+ %
+ Reconstruction of the total energy of the hadronic final state will also
  possible. 
  %
- A $\delta E_\nu\sim$30\% of energy resolution is
- the target performance for muons, with an associated
- $\delta \sim 5$ mrad of angular  resolution.
-
- % Table coverage + detector performance
+ In terms of performance, the targets
+ are $\delta E_\mu \sim$30\% of muon energy resolution and
+ $\delta \theta_\mu \sim 5$ mrad of muon angular  resolution.
 
@@
 
-The first goal is to produce projections
-for DIS pseudo-data at the FPF based on
-some idealised detector concepts and
-some initial choice of neutrino fluxes
-e.g.~\cite{Kling:2021gos}.
+For each of the LHC far-forward neutrino detectors
+described in Table~\ref{tab:FPF_experiments}, we generate
+projections for the expected precision of DIS structure function
+measurements as follows.
 %
-This requires a knowledge of the detector geometry
-and material, as well as of the double-differential
-neutrino interaction cross-section. 
+The goal is to quantify the number of reconstructed charged-current neutrino interaction
+events taking place in the fiducial volume of the detector in bins of Bjorken-$x$,
+momentum transfer $Q^2$, and neutrino energy $E_\nu$, that is,
+\be
+\label{eq:event_yields}
+N_{\rm ev}^{(i)}\lp \nu_e ; E_{{\rm min}}^{(i)} \le E_\nu \le E_{{\rm max}}^{(i)} ,\,
+x_{{\rm min}}^{(i)} \le x \le x_{{\rm max}}^{(i)} ;\, Q_{{\rm min}}^{2(i)} \le Q^2 \le Q_{{\rm max}}^{2(i)}\rp
+\, ,\quad i=1,\ldots, N_{\rm bins} \, ,
+\ee
+for electron neutrinos and for each of the bins composing the measurement, and with similar
+expressions applying for muon and tau neutrinos and antineutrinos.
 %
-Since we aim to produce pseudo-data binned in $(x,Q^2)$,
-for each simulated event we need to determine the 
-final-state kinematics.
+These event yields determine the statistical
+precision associated to a measurement of the double-differential cross-sections
+Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
+%
+Subsequently, we account for the expected reconstruction performance of the detector
+in order to estimate the systematic uncertainties associated to these event yields.
+%
+The choice of the binning is in principle arbitrary, and here we define them
+to ensure that Gaussian statistics hold for all the bins of the measurement.
 
-Specifically, we would like to evaluate the
-number of charged-current neutrino interaction events
-within the detector volume in different bins
-of the incoming neutrino energy $E_\nu$, the Bjorken
-variable $x$ and the momentum transfer square $Q^2$,
+In this calculation we assume the neutrino fluxes provided by the calculation
+of~\cite{Kling:2021gos} and neglect the associated uncertainties.
+%
+The bin-by-bin integrated event yields in Eq.~(\ref{eq:event_yields}) are
+obtained by convoluting the incoming neutrino fluxes, for a given geometric acceptance
+of the target detector, with the corresponding neutrino differential cross-sections
+Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
+%
+As we further discuss in Sect.~\ref{sec:settings}, theoretical predictions
+for the latter are computed with {\sc\small YADISM} interfaced to {\sc\small PineAPPL}
+to produce fast precomputed interpolation grids.
+%
+Differential event yields are therefore evaluated using
 \begin{equation}
-    N_{\rm ev}(E_\nu, x, Q^2) \, ,
+   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) dQ^2 dx dE_{\nu} \, ,\quad i=1,\ldots, N_{\rm bins} \, ,
 \end{equation}
-for some binning in these three kinematic variables.
+with $n_T$ is the nuclear density of the target detector material and $L_T$ its lenght.
 %
-This can be evaluated as
-\begin{equation}
-\label{eq:nev_v1}
-    N_{\rm ev}(E_\nu, x, Q^2) \propto \int_{\rm bin}\int_{\rm det}  \frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} \mathcal{L}_{\nu}(E_{\nu}) \, ,
-\end{equation}
-where $\mathcal{L}(E_{\nu}) $ is the incoming neutrino
-luminosity which accounts for the detector geometry
-and material density. 
-%
-Eq.~(\ref{eq:nev_v1}) can be integrated to
-determine the actual number of events within
-the bin boundaries.
-
-We start with a perfect detector.
+The incoming neutrino fluxes, which include the geometric acceptance of the considered detector,
+as encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$.
 
@@
 So for a detector with $n_T$ nuclear target density and $L_T$ length, we calculate the event rate per bin as
-
-\begin{equation}
-    N_{\rm ev}/{\rm bin} = n_T L_T\int_{Q^2_{min}}^{Q^2_{max}}\int_{x_{min}}^{x_{max}}\int_{E_{\nu,min}}^{E_{\nu , max}} \frac{dN_{\nu}}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) dQ^2 dx dE_{\nu}.
-\end{equation}
 

### 2023-06-20 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

@@
 \begin{equation}
+  \label{eq:event_yields}
    N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) dQ^2 dx dE_{\nu} \, ,\quad i=1,\ldots, N_{\rm bins} \, ,
 \end{equation}
-with $n_T$ is the nuclear density of the target detector material and $L_T$ its lenght.
+with $n_T$ is the nuclear density of the target detector material and $L_T$ its length.
 %
 The incoming neutrino fluxes, which include the geometric acceptance of the considered detector,
-as encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$.
-
-For bins in $x,Q^2,E_{\nu}$, we start with the \href{https://github.com/juanrojochacon/FPF-WG1/blob/main/results/diff_xsecs_a1.txt}{differential cross section},$\frac{d^2\sigma(x,Q^2,E_{\nu}}{dxdQ^2})$ [pb GeV$^{-2}$] as output from {\tt YADISM} and convolve with the \href{https://github.com/KlingFelix/FastNeutrinoFluxSimulation/tree/main/Fluxes}{neutrino flux}, $\frac{dN_{\nu}}{dE_{\nu}}$.
-So for a detector with $n_T$ nuclear target density and $L_T$ length, we calculate the event rate per bin as
-
-Using a MC integration, we can calculate $N_{\rm ev}/{\rm bin}$ by sampling $N$ points in $x,Q^2,E_{\nu}$ space such that $0< y = \frac{Q^2}{2m_N E_{\nu }x} < 1$ and integrating over the bin.
-
+are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$.
+%
+We consider the scattering of muon neutrinos, characterised by the highest rates, and in some cases
+we present results also for electron neutrinos.
+%
+We have verified that the differential event yield calculation
+implemented in Eq.~(\ref{eq:event_yields}), when extrapolated to a single bin
+covering the full detector acceptance,
+is consistent with the fiducial interaction rates presented in~\cite{Feng:2022inv}.
+%
+The triple integral in  Eq.~(\ref{eq:event_yields}) is evaluated numerically by means
+of Monte Carlo sampling, by generating sampling $N_{\rm mc}$ points in the $\lp x,Q^2,E_{\nu}\rp$ space
+with the constraint that $0 < y = Q^2/2m_N E_{\nu }x <1 $
+and then  integrating over the bin range:
 \begin{equation}
-    N_{\rm ev}/{\rm bin} \approx n_T L_T \frac{(Q^2_{max}-Q^2_{min})(x_{max}-x_{min})(E_{\nu ,max}-E_{\nu ,min})}{N}\times \sum_i^N f(x_i,Q^2_i,E_{\nu ,i})
+    N_{\rm ev}^{(i)} \approx n_T L_T \frac{(Q^{2(i)}_{\rm max}-Q^{2(i)}_{\rm min})(x^{(i)}_{\rm max}-x^{(i)}_{\rm min})(E_{\rm max}^{(i)}-E_{\rm min}^{(i)})}{N_{\rm mc}}\times \sum_{j=1}^{N_{\rm mc}} \frac{dN_{\nu}(E^{(j)}_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x^{(j)},Q^{2(j)},E^{(j)}_{\nu})}{dxdQ^2}\right) \, ,
     \label{MCintegration}
 \end{equation}
+and where $N_{\rm mc}$ is chosen to be large enough such that residual Monte Carlo integration
+uncertainties are negligible.
 

### 2023-06-20 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

@@
 
+Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the five detectors considered
+  in the present analysis, separated into electron neutrinos and antineutrinos
+  and muon neutrinos and antineutrinos.
+  %
+  These event yields are computed from Eq.~(\ref{eq:event_yields}) with the only
+  restriction that the momentum transfer and the final-state invariant mass should be restricted
+  to the DIS region, $Q^2 \ge 2$ GeV$^2$ and $W^2 \ge 12.5$ GeV$^2$.
+  %
+  As discussed above, for FASER$\nu$ and SND@LHC we assume the integrated luminosity to
+  be that of Run III while for the FPF experiments we assume the full HL-LHC
+  luminosity (3 ab$^{-1}$).
+  %
+   The numbers in parenthesis indicate the event rates corresponding to charm
+  production for those experiments with heavy flavour tagging capabilities.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%-----------------------------------------------------------------
+\begin{table}[t]
+  \centering
+  \small
+  \renewcommand{\arraystretch}{1.60}
+\begin{tabularx}{\textwidth}{X|c|c|c|c|c|c}
+\toprule
+Detector & $\quad$ $N_{\nu_e}$ $\quad$ &$\quad$ $N_{\bar{\nu}_e}$$\quad$   &   $N_{\nu_e} + N_{\bar{\nu}_e}$ &
+$\quad$$N_{\nu_\mu}$ $\quad$ & $\quad$ $N_{\bar{\nu}_\mu}$ $\quad$  &   $N_{\nu_\mu} + N_{\bar{\nu}_\mu}$ \\
+\midrule
+FASER$\nu$  &    &    &   &   &    &    \\
+SND@LHC  &    &    &   &   &    &    \\
+\midrule
+FASER$\nu$2  &    &    &   &   &    &    \\
+AdvSND~(far)  &    &    &   &   &    &    \\
+FLArE &    &    &   &   &    &    \\
+  \bottomrule
+\end{tabularx}
+\vspace{0.2cm}
+\caption{\small The predicted integrated event yields for the five detectors considered
+  in the present analysis, separated into electron neutrinos and antineutrinos
+  and muon neutrinos and antineutrinos.
+  %
+  These event yields are computed from Eq.~(\ref{eq:event_yields}) with the only
+  restriction that the momentum transfer and the final-state invariant mass be restricted
+  to the DIS region, $Q^2 \ge 2$ GeV$^2$ and $W^2 \ge 12.5$ GeV$^2$.
+  %
+  The numbers in parenthesis indicate the event rates corresponding to charm
+  production.
+  \label{tab:integrated_rates}
+}
+\end{table}
+%-----------------------------------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Eq.~(\ref{eq:event_yields}) can be generalised to charm-production events, with
+the only difference beings that now the neutrino scattering cross-section is restricted
+to those processes leading to final-state charm quarks.
+%
+Assuming that charm quarks can be directly tagged by the detector one has
+\be
+\label{eq:event_yields_charm}
+  N_{\rm ev,c}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma^{\nu N \to \ell + c+X}(x,Q^2,E_{\nu})}{dxdQ^2}\right) dQ^2 dx dE_{\nu} \,
+  \ee
+  with the charm production cross-sections being discussed in~\cite{Faura:2020oom}
+  and references therein.
+  %
+  Detectors without charm-tagging capabilities can still be sensitive to charm production via
+  the semileptonic decays of the $D$-mesons, resulting in the characteristic
+  dimuon topology, where
+  \be
+ N_{\rm ev,2\mu}^{(i)} \approx N_{\rm ev,c}^{(i)} \times \mathcal{B}\lp c \to D \to \mu + X\rp \, ,
+ \ee
+ with $\mathcal{B}$ a numerical factor that accounts for charm hadronisation and the
+ resulting semileptonic decay to a muon.
+ %
+ Given that $\mathcal{B}\sim 0.1$, being able to tag directly charm quarks increases the event yields
+ of charm production events by a factor 10 as compared to reconstructing the dimuon final state.
+ %
+ Here we neglect finite acceptance effects, which can only be properly estimated by means
+ of a full detector simulation.
+
+%-----------------------------------------------------------------------
+\begin{figure}[t]
+    \centering
+\includegraphics[width=1\textwidth]{plots/Nevent_FASERv2_14.pdf}
+    \caption{Event rate per bin for muon neutrinos at FASER$\nu$2.
+Bins are denoted by dashed grid, and the red dot indicates the weighted average of $x,Q^2$ points in each bin.
+The total number of muon neutrino events calculated is $\approx2.6\times 10^5$.
+Note that bins were chosen somewhat arbitrarily, and can be iterated to improve PDF fits }
+    \label{fig:fasernu2_muon}
+\end{figure}
+%-----------------------------------------------------------------------
+
 where $f(x_i,Q^2_i,E_{\nu ,i}) = \frac{dN_{\nu}}{dE_{\nu,i}}\left(\frac{d^2\sigma(x_i,Q^2_i,E_{\nu,i})}{dxdQ^2}\right)$.
@@
 
-\begin{figure}[h]
-    \centering
-\includegraphics[width=1\textwidth]{plots/Nevent_FASERv2_14.pdf}
-    \caption{Event rate per bin for muon neutrinos at FASER$\nu$2.
-Bins are denoted by dashed grid, and the red dot indicates the weighted average of $x,Q^2$ points in each bin.
-The total number of muon neutrino events calculated is $\approx2.6\times 10^5$.
-Note that bins were chosen somewhat arbitrarily, and can be iterated to improve PDF fits }
-    \label{fig:fasernu2_muon}
-\end{figure}
+charm production
 

### 2023-06-20 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

@@
   restriction that the momentum transfer and the final-state invariant mass should be restricted
-  to the DIS region, $Q^2 \ge 2$ GeV$^2$ and $W^2 \ge 12.5$ GeV$^2$.
+  to the DIS region,
+  \be
+  \label{eq:DISconditions}
+Q^2 \ge 2~{\rm GeV}^2\quad{\rm and} W^2 \ge 12.5~{\rm GeV}^2 \, .
+\ee
   %
@@
 
+ Fig.~\ref{fig:fasernu2_muon} displays the
+ event yields per bin,  Eq.~(\ref{eq:event_yields}),
+  for muon neutrinos detected at FASER$\nu$2.
+  %
+  We present results binned in $x$ and $Q^2$ and integrated over the neutrino energies.
+  %
+  The red dot indicates the weighted center of each bin.
+  %
+  Adding up all bin entries results into $N_{\rm ev}(\nu_\mu)\sim 3\times 10^5 $ reconstructed muon
+  neutrinos as indicated in Table~\ref{tab:integrated_rates}.
+  %
+  Kinematic cuts are such that the DIS conditions Eq.~(\ref{eq:DISconditions}) are satisfied.
+  %
+  Only bins with at least 30 events are retained.
+  %
+  One can observe the large event rates for most of the region in $\lp x,Q^2\rp$ covered,
+  which result into very competitive statistical uncertainties.
+  %
+  From Fig.~\ref{fig:fasernu2_muon} we see that the kinematic coverage of FASER$\nu$2 is
+  $x_{\rm min}\sim 10^{-3}$ at small-$x$ and $Q^2_{\rm max}\sim 10^4$ at large-$Q^2$, which represent an extension
+  of around one order of magnitude in both directions as compared to available
+  DIS neutrino data.
+
 %-----------------------------------------------------------------------
@@
     \centering
-\includegraphics[width=1\textwidth]{plots/Nevent_FASERv2_14.pdf}
-    \caption{Event rate per bin for muon neutrinos at FASER$\nu$2.
-Bins are denoted by dashed grid, and the red dot indicates the weighted average of $x,Q^2$ points in each bin.
-The total number of muon neutrino events calculated is $\approx2.6\times 10^5$.
-Note that bins were chosen somewhat arbitrarily, and can be iterated to improve PDF fits }
+\includegraphics[width=0.9\textwidth]{plots/Nevent_FASERv2_14.pdf}
+\caption{The event yields per bin $ N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}),
+  for muon neutrinos at FASER$\nu$2.
+  %
+  We present results binned in $x$ and $Q^2$ and integrating over the neutrino energies.
+  %
+  The red dot indicates the weighted center of each bin.
+  %
+  Adding up all bin entries results into $N_{\rm ev}(\nu_\mu)\sim 3\times 10^5 $ reconstructed muon
+  neutrinos. }
     \label{fig:fasernu2_muon}
@@
 
-where $f(x_i,Q^2_i,E_{\nu ,i}) = \frac{dN_{\nu}}{dE_{\nu,i}}\left(\frac{d^2\sigma(x_i,Q^2_i,E_{\nu,i})}{dxdQ^2}\right)$.
+The event yields displayed in Fig.~\ref{fig:fasernu2_muon} determine the associated
+statistical uncertainty in each bin
+\be
+\label{eq:statistical_uncertainties}
+\delta_{\rm stat}  N_{\rm ev}^{(i)} = \sqrt{N_{\rm ev}^{(i)}} \, ,
+\ee
+such that the fractional statistical uncertainty per bin is $1/\sqrt{N_{\rm ev}^{(i)}}$.
+%
+Since here we discard bins with less than 30 events, this statistical uncertainty
+ranges between $\sim 1\%$ and $\sim 18\%$ for muon neutrinos in FASER$\nu$2 depending on the values of
+$x$ and $Q^2$ associated to this bin.
+%
+These statistical uncertainties are displayed in the left panel
+of Fig.~\ref{fig:error_plot_FASERv2_14}, which corresponds
+to the same event yields as in
+Fig.~\ref{fig:fasernu2_muon}
+now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$.
+%
+The error bar in the $y$-direction indicates the statistical uncertainties, while
+that in the $x$ direction corresponds to the width of the $x$-bins.
 
-The statistical uncertainty for each bin is then defined by a Gaussian distribution with fractional uncertainty $1/\sqrt{N{\rm ev}/{\rm bin}}$, i.e.
-$\delta N_{\rm ev}/{\rm bin} = \sqrt{N_{\rm ev}} /{\rm bin}$
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h]
+    \centering
+    \includegraphics[width = 0.95\textwidth]{plots/error_plot_FASERv2_14.pdf}
+    \caption{Same as Fig.~\ref{fig:fasernu2_muon}
+      now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$.
+      %
+      In addition to the event yields we show the error bars corresponding to
+      statistical errors only (left), systematic errors only (middle), and the
+      sum in quadrature of the two (right panel).
+      %
+      The error bars in the $x$ direction indicate the width of the adopted $x$-bins.
+      }
+    \label{fig:error_plot_FASERv2_14}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-  Following this prescription, we can produce plots which characterize the event rate for a particular neutrino species at a particular experiment.
+\subsection{Systematic uncertainties}
 
-Results for FASER$\nu$2 can be found \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results}{here}.
-The .txt files will display which neutrino species was considered, and also compile experimental geometries and target details in the header.
-In the sub-folder \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results/Summaries}{summaries}, plots can be found which show the event rate in $x,Q^2$ space, integrating over the entire neutrino spectrum.
-The event rate for muon neutrinos at FASER$\nu$2 is shown in Fig~\ref{fig:fasernu2_muon}.
+In addition to the statistical uncertainties given by Eq.~(\ref{eq:statistical_uncertainties}),
+one needs to estimate the systematic uncertainties associated to the reconstruction
+of the final state leptonic and hadronic variables as listed in Table~\ref{tab:FPF_experiments}.
+%
+For instance, an event which would be classified in a given bin in the case
+of a perfect detector may end up in a different bin in the presence of systematic
+shifts associated to the lepton energy $E_\ell$, lepton scattering angle $\theta_\ell$, and
+hadronic energy $E_h$.
+%
+Hence, for each source of experimental systematic uncertainty we would like to estimate
+its impact at the level of event yields and eventually stablish also the associated
+correlation matrix.
 
-charm production
-
-\subsection{Estimating systematic uncertainties}
-
-We now wish to understand the impact of systematic uncertainties on the event rate in $(x,Q^2,E_{\nu})$ space.
-For each experiment, the observables $E_{l},E_{h},\theta$ are related to $(x,Q^2,E_{\nu})$ by
-
-\begin{align}
-E_{\nu} = E_l + E_h \nonumber \\
-Q^2 = 4E_lE_{\nu}\sin^2{\theta/2} \nonumber \\
-x = \frac{Q^2}{2m_N(E_{\nu} - E_l)}.
-\end{align}
+By means of tree-level DIS kinematics one can relate the variables describing the neutrino-nucleon
+hard-scattering, $(x,Q^2,E_{\nu})$,
+with those describing the leptonic and hadronic final state, namely $\lp E_{\ell},\theta_\ell, E_{h} \rp$,
+and that correspond to experimentally measured quantities.
+%
+The mapping between the two sets of variables is 
+\bea
+E_{\nu} &=& E_\ell + E_h \, ,\nonumber \\
+Q^2 &=& 4E_\ell E_{\nu}\sin^2\lp {\theta_\ell/2}\rp  =  4E_\ell \lp E_\ell + E_h  \rp\sin^2\lp {\theta_\ell/2}\rp \, , \\
+x &=& \frac{Q^2}{2m_N(E_{\nu} - E_\ell)} = \frac{4E_\ell \lp E_\ell + E_h  \rp\sin^2\lp {\theta_\ell/2}\rp}{2m_NE_{h}} \, , \nonumber
+\eea
+highlighting how the measurement of $E_{\ell}$, $\theta_\ell$, and $E_{h}$ uniquely specify the hard-scattering
+kinematics $(x,Q^2,E_{\nu})$ of the event.
+%
+Therefore, systematic uncertainties in the measurement of these final-state variables will modify
+the assignbment of each event to a given bin of $x$, $Q^$, and $E_\mu$ introducing a systematic
+error in the event yields and hence in the measurement of the double-differemtial
+neutrino scattering cross-section.
 
@@
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width = 1\textwidth]{plots/error_plot_FASERv2_14.pdf}
-    \caption{Event rates with error bars at FASER$\nu$2 for $\nu_{\mu} N \rightarrow \mu^- X$} summed over $Q^2$.
-The error bars along the x-axis showing the width of the $x$-bins, and are not showing any type of error.
-    \label{fig:my_label}
-\end{figure}
+\subsection{Pseudo-data generation}

### 2023-06-20 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

@@
 Therefore, systematic uncertainties in the measurement of these final-state variables will modify
-the assignbment of each event to a given bin of $x$, $Q^$, and $E_\mu$ introducing a systematic
-error in the event yields and hence in the measurement of the double-differemtial
+the assignment of each event to a given bin of $x$, $Q^$, and $E_\mu$ introducing a systematic
+error in the event yields and hence in the measurement of the double-differential
 neutrino scattering cross-section.

### 2023-06-20 paper/sec-dis-pseudodata.tex
sect 2

@@
   \label{eq:DISconditions}
-Q^2 \ge 2~{\rm GeV}^2\quad{\rm and} W^2 \ge 12.5~{\rm GeV}^2 \, .
+Q^2 \ge 2~{\rm GeV}^2\quad{\rm and}\quad  W^2 \ge 12.5~{\rm GeV}^2 \, .
 \ee
@@
 
-By means of tree-level DIS kinematics one can relate the variables describing the neutrino-nucleon
+By means of tree-level DIS kinematics, one can relate the variables describing the neutrino-nucleon
 hard-scattering, $(x,Q^2,E_{\nu})$,
@@
 %
-Therefore, systematic uncertainties in the measurement of these final-state variables will modify
-the assignment of each event to a given bin of $x$, $Q^$, and $E_\mu$ introducing a systematic
+Therefore, systematic shifts in the measurement of these final-state variables will modify
+the assignment of each event to a given bin of $x$, $Q^2$, and $E_\mu$, introducing a systematic
 error in the event yields and hence in the measurement of the double-differential
@@
 
-We wish to sample over the space of observables, $(E_{l},E_{h},\theta)$, perform  cuts based on detector performance, calculate the event rates, and then smear this sampling according to experimental uncertainties to estimate the uncertainty on the event rate.
+In order to determine these bin-by-bin systematic uncertainties,
+we extend the calculation delineated in Eq.~(\ref{sec:pseudo-data_generation}) as follows.
+%
+Let us consider for illustrative purposes the FASER${\nu}$2 case.
+%
+From Table~\ref{tab:FPF_experiments}, one reads that the corresponding acceptances
+and performance parameters for $E_{\ell}$, $\theta_\ell$, and $E_{h}$   are given by
+\bea
+E_\ell \ge 100~{\rm GeV} \, , \quad \delta E_\ell \sim 30\% \, ,\nonumber \\
+E_h \ge 100~{\rm GeV} \, , \quad \delta E_h \sim 30\% \, ,\\
+ \theta_\ell \le \tan^{-1}(0.5) \, , \quad \delta\theta_\ell \sim 1~{\rm mrad} \, . \nonumber 
+\label{fasernu2systematic_errors}
+\eea
+In order to translate the systematic uncertainties $\delta E_\ell$, $\delta E_h $,
+and $\delta\theta_\ell$ into systematic errors associated to the binned event yields, 
+\be
+\label{eq:event_yields_systematic_error}
+\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} \, ,\quad
+\delta_{\rm sys}^{(E_h)} N_{\rm ev}^{(i)}
+\, ,\quad
+\delta_{\rm sys}^{(\theta_\ell)} N_{\rm ev}^{(i)} \, ,\qquad i=1,\ldots,N_{\rm bin} \, ,
+\ee
+we generate first a Monte Carlo set of events, denoted by $\mathcal{D}_0$,
+composed by $N_{\rm mc} = 10^7$ samples and determine the assignment of each event
+to a point in the $\lp x,Q^2,E_{\nu}\rp$ space.
+%
+By integrating over this sample by means of Eq.~(\ref{MCintegration}) we determine
+the binned event yields for this reference $\mathcal{D}_0$ sample.
 
-Taking FASER${\nu}$2 as an example, we can write the experimental cuts and uncertainties as
+We then produce a second Monte Carlo sample $\mathcal{D}_1$ starting from the events
+of $\mathcal{D}_0$ which are then smeared with Gaussian distributions whose variances
+are given by Eq.~(\ref{fasernu2systematic_errors}).
+%
+The bin assignment of the events in the smeared sample $\mathcal{D}_1$ will
+in general be different from those of the baseline sample.
+%
+The procedure is repeated $M$ times, leading to
+$\mathcal{D}_k$ (with $k=1,\ldots,M$) smeared
+samples each one leading to a different binned event yields
+$ N_{\rm ev}^{(i)(k)}$.
+%
+Provided the number of samples $M$ is large enough, the standard deviation over samples in this $ N_{\rm ev}^{(i)(k)}$
+distribution provides the sought-for estimate of the systematic uncertainties.
+%
+Furthermore, 
+since the systematic errors are treated as uncorrelated among them,
+by producing samples where only one source of error is varied at a time
+we can determine the values of Eq.~(\ref{eq:event_yields_systematic_error}) in each bin.
 
-\begin{align}
-100 < E_l < E_{\nu,{\rm max}} , \delta E_l = 30\% \nonumber \\
-100 < E_h < E_{\nu,{\rm max}} , \delta E_h = 50\% \nonumber \\
-0 < \theta < \tan^{-1}(0.5) , \delta\theta = 1~{\rm mrad}
-\label{fasernu2systematic_errors}
-\end{align}
+The end result of the procedure is the estimate of statistical and systematic uncertainties
+for each bin of the measurement, from which a experimental covariance matrix can be constructed as
+\be
+   {\rm cov}_{ij} = \delta_{ij} \lp \delta_{\rm stat}  N_{\rm ev}^{(i)}\rp^2
+   + \lp \delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} \rp \lp \delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(j)} \rp 
+   + \lp \delta_{\rm sys}^{(E_h)} N_{\rm ev}^{(i)} \rp \lp\delta_{\rm sys}^{(E_h)} N_{\rm ev}^{(j)}\rp 
+   + \lp \delta_{\rm sys}^{(\theta_\ell)} N_{\rm ev}^{(i)} \rp
+   \lp \delta_{\rm sys}^{(\theta_\ell)} N_{\rm ev}^{(j)} \rp
+   \, ,\qquad
+ \nonumber
+ \ee
+ for $i,j=1,\ldots,N_{\rm bin}$, and the same for the associated correlation
+ matrix of the measurement
+ \be
+ \rho_{ij} =  \frac{{\rm cov}_{ij}}{\sqrt{ {\rm cov}_{ii} }\sqrt{ {\rm cov}_{jj} } } \, . 
+ \ee
+ The relative covariance matrix, $ {\rm cov}_{ij}/( N_{\rm ev}^{(i)}N_{\rm ev}^{(j)})$, is
+ independent of the considered observable and would also apply
+ for the double-differential cross-sections Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) which are related to the event yields by a constant factor.
 
-We first generate a MC dataset, $D_0$, over this space with $N = 10^7$ samples and calculate $x,Q^2,E_{\nu}$ for each event, removing samples with $y > 1$.
-We then integrate according to Eq.
-\ref{MCintegration} to produce a distribution of events with bins in $x,Q^2,E_{\nu}$.
-We then smear each sample according to a Gaussian distribution with widths given by Eq.~\ref{fasernu2systematic_errors} to produce a new data set $D_i$ and repeat to produce $M = 10$ event distributions($M>10$ can later be used, but $M = 10$ appears to be stable).
-For each bin we take the standard deviation to produce the systematic errors per bin (denoted as "N\textunderscore sys\textunderscore errs" in files named "binned\textunderscore sys-events...
-.txt" \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results}{here}).
+ One should emphasize that in a real experiment the actual covariance matrix will be
+ composed by a much larger number of uncertainty sources, with typical
+  HERA and LHC precision measurements characterised by up to hundreds
+ of different sources of systematic error.
+ %
+ In particular, the assumption that a single source of systematic error, say $\delta E_\ell$,
+ is fully correlated among all the bins in $(x,Q^2)$ is likely not to be realistic.
+ %
+ For this reason, here we present impact results both for the nominal correlation model,
+ for the case where systematic and statistical uncertainties are added in quadrature,
+ and intermediate scenarios.
 
-For FASER${\nu}$2, the systematic errors typically dominate over statistical errors, at about $10\%$.
+ Fig.~\ref{fig:error_plot_FASERv2_14} (central and right panels) display
+ the integrated event yields for FASER$\nu$2 as a function of $x$ for only
+ systematic errors and for the sum in quadrature of statistical and systematic errors.
+ %
+ For most of the bins, for the baseline performance assumptions the total systematic
+ uncertainty is at the $10\%$ and dominates over the statistical uncertainties.
 
  \subsection{Pseudo-data generation}
+
+ In order to generate pseudo-data for double-differential
+ neutrino scattering cross-sections at the LHC, we follow the procedure
+ used for the HL-LHC PDF projections of~\cite{AbdulKhalek:2018rok} which was
+ also adopted in~\cite{Ethier:2021ydt} and~\cite{Greljo:2021kvv} for SMEFT impact projections
+ of vector-boson scattering and high-mass Drell-Yan data at the HL-LHC, respectively.
+ %
+ The starting point are the predictions for the differential neutrino scattering
+ cross-section
+ \be
+ \label{eq:theory_dis_projections}
+ \mathcal{O}_i^{{\rm (th)}} \equiv \frac{d^2\sigma^{\nu N}(x_i,Q^2_i,y_i)}{dxdy} \, ,\quad
+ i=1,\ldots,N_{\rm bin} \, ,
+ \ee
+ with $(x_i,Q^2_i,y_i)$ being the corresponding bin centers.
+ %
+ The observables $\mathcal{O}_i $ are evaluated using {\sc\small YADISM} and {\sc\small PineAPPL}
+ as described in Sect.~\ref{sec:settings}.
+ %
+ An important point here is the choice of PDF set entering the evaluation of
+ the observable in Eq.~(\ref{eq:theory_dis_projections}): it should be consistent
+ with that of the fitting framework used to assess their impact on the (n)PDFs.
+ %
+ For instance, when using the {\sc\small xFitter} profiling of PDF4LHC21, one needs
+ to generate LHC neutrino pseudo-data also using PDF4LHC21 as input.
+ %
+ In order words, the generated pseudo-data should be fully consistent with the prior PDF
+ set used as baseline, else one is introducing artificially inconsistencies which
+ compromise the validity of the projection studies.
+
+ The central values for the LHC neutrino scattering pseudo-data, denoted
+ by $\mathcal{O}_i^{{\rm exp}} $, are obtained
+ by fluctuating this reference theory prediction by the statistical and systematic
+ uncertainties, that is
+ \begin{equation}
+  \label{eq:pseudo_data}
+  \mathcal{O}_i^{{\rm (exp)}}  =   \mathcal{O}_i^{{\rm (th)}}\left( 1+ r^{(i)}_{\rm stat}\delta_{i,{\rm stat}}
+  + \sum_{k=E_\ell, E_h,\theta_\ell} r_{{\rm sys},k} \,\delta_{i,{\rm sys}}^{(k)}\right) \, , \qquad i=1,\ldots,N_{\rm bin} \, ,
+ \end{equation}
+ with $r^{(i)}_{\rm stat}$ and $r_{{\rm sys},k}$ being univariate Gaussian random numbers,
+ and $\delta_{\rm stat}$ ($\delta_{\rm sys}^{(k)}$) indicate the relative statistical (systematic)
+ uncertainties associated to the $i$-th bin.
+ %
+ Note that a given systematic variation is assumed to be fully correlated among all the bins
+ in the measurement.
+
+ Alternatively, we can add all uncertainties in quadrature and account for a possible
+ improvement in the systematic errors with respect to the current estimates,
+ \be
+ \delta_{{\rm tot},i}^{\rm exp} = \left( \left( \delta_i^{\rm stat}\right)^2 + \sum_{k=1}^{n_{\rm sys}}
+\left( f_{{\rm red},j}\delta_{i,j}^{\rm sys} \right)^2\right)^{1/2} \, ,
+ \ee
+ with $f_{{\rm red},j} \le 1$ quantifies the possible reduction of systematic uncertainties, and
+ then the pseudo-data is evaluated by means of
+ \begin{equation}
+  \label{eq:pseudo_data_v2}
+  \mathcal{O}_i^{{\rm (exp)}}  =   \mathcal{O}_i^{{\rm (th)}}\left( 1+ r^{(i)}_{\rm stat}\delta_{i,{\rm tot}}
+  \right) \, , \qquad i=1,\ldots,N_{\rm bin} \, .
+ \end{equation}
+ While the actual correlation model will lie somewhere between no correlation and full correlation,
+ these two approaches to generate the pseudo-data bracket the projected impact
+ on the PDFs and its dependence on the experimental correlation model.

### 2023-06-22 paper/sec-introduction.tex
Additional xFitter ref.s to updated versions, added version number, and the profiling ref.s we would use among xFitter developers

@@
 %
-Subsequently, we study their impact on the proton PDFs by means of the Hessian profiling~\cite{Paukkunen:2014zia}
+Subsequently, we study their impact on the proton PDFs by means of the Hessian profiling~\cite{Paukkunen:2014zia,  Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre}
 of the PDF4LHC21 combination~\cite{PDF4LHCWorkingGroup:2022cjn}
-within the  {\sc\small xFitter} framework~\cite{Alekhin:2014irh}, cross-checked
-with their direct inclusion in the open-source NNPDF fitting framework~\cite{NNPDF:2021uiq}.
+within the  {\sc\small xFitter} framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web} version 2.2.1, 
+cross-checked with their direct inclusion in the open-source NNPDF fitting framework~\cite{NNPDF:2021uiq}.
 %

### 2023-06-22 paper/sec-dis-pseudodata.tex
Added power of 2 to RHS of ^2 \ll m_Z^2$ (dimension mismatch) above Eq. 2.9
Simple typo fixes, comment about the wording of x and y directions

@@
  Within the same assumptions, for energies below
- the $Z$-boson mass, $Q^2 \ll m_Z$, the corresponding
+ the $Z$-boson mass, $Q^2 \ll m_Z^2$, the corresponding
  partonic decomposition is
@@
 Eq.~(\ref{eq:event_yields}) can be generalised to charm-production events, with
-the only difference beings that now the neutrino scattering cross-section is restricted
+the only difference being that now the neutrino scattering cross-section is restricted
 to those processes leading to final-state charm quarks.
@@
  Given that $\mathcal{B}\sim 0.1$, being able to tag directly charm quarks increases the event yields
- of charm production events by a factor 10 as compared to reconstructing the dimuon final state.
+ of charm production events by a factor of 10 as compared to reconstructing the dimuon final state.
  %
@@
   %
-  Kinematic cuts are such that the DIS conditions Eq.~(\ref{eq:DISconditions}) are satisfied.
+  Kinematic cuts are such that the DIS conditions in Eq.~(\ref{eq:DISconditions}) are satisfied.
   %
@@
 that in the $x$ direction corresponds to the width of the $x$-bins.
+{\color{red}[Suggestion (TM): let's refer to horizontal and vertical directions, since $x$ and $y$ are variables as well, not only directions]}
 

### 2023-06-26 paper/sec-analysis.tex
more work on sect 2
Added PineAPPL software ref. (per developers' citation instructions) and included the syst. unc. improvement factor 0.5 when describing pseudodata

--- 2023-05-24 paper/sec-analysis.tex
@@
+\clearpage
 \section{Analysis settings}
@@
 $\sigma_i^{\textrm{th}}$ 
-for each bin $i$ out of $N_{\textrm{bins}}$ by varying it with the statistical uncertainties 
-$\delta_i^{\textrm{stat}}$, 
+for each bin $i$ out of $N_{\textrm{bins}}$ by varying it within bounds obtained from the statistical (systematic) uncertainties 
+$\delta_i^{\textrm{stat}}$ ($\delta_i^{\textrm{syst}}$), 
 obtained in the procedure described in Section~\ref{sec:pseudo-data_generation}, 
 as
-%TODO once more complete uncertainty estimates are there, add them to the variation
-$\sigma_i^{\textrm{pd}} = \sigma_i^{\textrm{th}}(1 + r_i \delta_i^{\textrm{stat}})$, 
-with $r_i$ a univariate Gaussian random number.
+
+\begin{equation}
+\sigma_i^{\textrm{pd}}
+=
+\sigma_i^{\textrm{th}}
+\left( 1 + r_i \sqrt{     (\delta_i^{\textrm{stat}})^2
+                      + (f \delta_i^{\textrm{syst}})^2 }
+\right).
+\end{equation}
+Here, $r_i$ is a univariate Gaussian random number and $f = 0.5$ an effective correction factor 
+accounting for the improved constraining power of the same pseudodata set using correlated systematics, compared to solely adding all sources of uncertainty in quadrature.
 %
@@
 The decrease in the uncertainties of the shifted PDFs indicates the enhancement that including the FPF data in the global PDF fit could bring.
-Here, the profiling studies are performed using version 2.2.1 of the \textsc{xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}, extended to support the use of \textsc{PineAPPL} grids~\cite{christopher_schwan_2023_7499507, Carrazza:2020gss}.
+Here, the profiling studies are performed using version 2.2.1 of the \textsc{xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}.
 %
+
+\subsection{Modelling DIS structure functions}
+
+ %
+Theoretical predictions for neutrino DIS structure functions are evaluated with the {\sc\small EKO}~\cite{Candido:2022tld}
+and {\sc\small YADISM}~\cite{yadism,Candido:2023utz} programs interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss, christopher_schwan_2023_7995675}, with the latter providing the fast interpolation grids to be used in the fit.
+%
+To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed and is available with the open-source {\sc\small xFitter} code.

### 2023-06-27 paper/FPF-WG1.tex
Add plot with systematic errors from E-lepton

@@
   {\small
-Max Fieg$^{1}$, Tommaso Giani$^{2,3}$, Peter Krack$^{2,3}$  Giacomo Magni$^{2,3}$, Toni M\"akel\"a$^{4}$, \\[0.1cm]
+Max Fieg$^{1}$, Tommaso Giani$^{2,3}$, Peter Krack$^{2,3}$, Toni M\"akel\"a$^{4}$, Juan M. Cruz-Martinez$^{5}$, \\[0.1cm]
     Tanjona Rabemananjara$^{2,3}$, and Juan Rojo$^{2,3}$.
@@
     ~$^4$National Centre for Nuclear Research, Pasteura 7, Warsaw, PL-02-093, Poland \\[0.1cm]
+    ~$^5$CERN, Theoretical Physics Department, CH-1211 Geneva 23, Switzerland \\[0.1cm]
  }

### 2023-06-27 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

@@
 \midrule
-\multirow{2}{*}{FASER$\nu$}  &   &   Tungsten  & \multirow{2}{*}{muons}      &     &         \\
-  &   &   (1.1 ton)  &       &     &         \\
-\midrule
-\multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &       &       &       \\
-  &   &  (0.83 ton)   &       &       &       \\
-\midrule
-\midrule
-\multirow{3}{*}{FASER$\nu$2}  &   & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{only muons}     &   $E_\ell \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
-  &   &  \multirow{2}{*}{(20 ton)}   &       &  $\tan \theta_\ell \lsim 0.5$   &   $\delta \theta_\ell \sim 1$ mrad      \\
-  &   &     &       &  reconstructed $E_h$ \& charm ID   &  $\delta E_h \sim 30\%$        \\
-\midrule
-\multirow{3}{*}{AdvSND~(far)}  &   \multirow{3}{*}{ $7.2 \le \eta_\nu \le 8.4$}  &
-\multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{only muons}    &  $E_\mu \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
-  &   &   \multirow{2}{*}{(5 ton)}  &        & $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$     &           \\
-  &   &     &       &  reconstructed $E_h$   &           \\
-\midrule
-\multirow{3}{*}{FLArE}  & \multirow{3}{*}{Liquid Argon}  &  & \multirow{3}{*}{ maybe muons}  &  $E_\mu \lsim 2$ GeV, $E_e \lsim 1$ TeV    &    $\delta E_e \sim 5\% $ \\
-&   &     &   & $\theta_\mu \lsim 0.4$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $ mrad   \\
- &   &     &  & reconstructed $E_h$  &    $\delta E_h \sim 30\% $   \\
-  \bottomrule
 \end{tabularx}

### 2023-07-04 paper/sec-analysis.tex
sect 3

@@
 
-Once we have generated pseudo-data for the 
-neutrino DIS charged-current structure functions
-in bins of $(x,Q^2,y)$, and assuming that uncertainties
-are purely of statistical origin, we can assess their
-impact on proton PDFs.
+In this section, we describe the analysis settings adopted to quantify
+the impact of LHC neutrino measurements on the proton and nuclear PDFs.
 %
-At a first step we neglect nuclear effects
-and treat data as corresponding to a free isoscalar
-nucleon with $A=1$.
+First of all, we discuss the calculation of inclusive and charm structure functions
+and their interpolation in terms of fast grids. 
+%
+Second, we review the Hessian profiling framework and how it is applied
+in this work to proton and nuclear PDFs.
+%
+Third, we indicate the implementation of the LHC neutrino pseudo-data in the
+NNPDF framework and the settings of the subsequent global PDF analysis.
+
+\subsection{Structure function calculation}
+\label{subsec:dis_sf_calculations}
+
+The procedure described in Sect.~\ref{sec:dis_pseudodata} returns
+$N_{\rm bin}$ bins of LHC neutrino pseudo-data $\mathcal{O}_i^{{\rm (exp)}}$, Eq.~(\ref{eq:pseudo_data}), covering the $(x,Q^2,E_\nu)$ kinematic region accessible by the experiment,
+together with the associated statistical and systematic uncertainties.
+%
+The calculation of this pseudo-data relies on the corresponding set of
+theoretical predictions for the same observables $\mathcal{O}_i^{{\rm (th)}}$,
+Eq.~(\ref{eq:theory_dis_projections}).
+%
+Here we evaluate inclusive and charm DIS structure functions with the
+{\sc\small YADISM}~\cite{yadism,Candido:2023utz} program
+interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss, christopher_schwan_2023_7995675}
+to return a fast interpolation grid admitting a generic PDF input.
+%
+DGLAP evolution effects between the scale $Q_0$ at which PDFs are evaluated
+and the data scale $Q$ are provided by {\sc\small EKO}~\cite{Candido:2022tld}.
+
+The resulting {\sc\small PineAPPL} grids provide a fast evaluation
+of Eq.~(\ref{eq:theory_dis_projections}) for an arbitrary choice of the
+input PDFs at the initial scale $Q_0$, with the latter accessed via their
+{\sc\small LHAPDF} interface~\cite{Buckley:2014ana}.
+%
+Whenever pseudo-data is generated, it is crucial to adopt common inputs with
+the subsequent PDF analysis.
+%
+For instance, if one aims to include the LHC neutrino data into the NNPDF4.0
+NNLO determination, $\mathcal{O}_i^{{\rm (th)}}$ must be evaluated also at NNLO
+and also using
+NNPDF4.0 as input for consistency, else artificial tensions between theory
+and data would be introduced during the fit biasing the results.
+
+By means of this theoretical pipeline, predictions for
+DIS inclusive structure functions on an isoscalar target $N$ are computed
+using
+\be
+\label{eq:neutrino_DIS_xsec}
+\frac{d^2\sigma^{\nu N}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\nu N}_2(x,Q^2) - y^2F^{\nu N}_L(x,Q^2) +Y_- xF^{\nu N}_3(x,Q^2)\rc  \, ,
+\ee
+with an analogous formula for antineutrino scattering with the sign of $xF_3$ flipped.
+%
+A {\sc\small PineAPPL} interpolation grid for
+Eq.~(\ref{eq:neutrino_DIS_xsec}) is evaluated at the $(x,Q^2,E_\nu)$ bins
+for which pseudo-data is generated using DGLAP evolution and coefficient
+functions at $\mathcal{O}\lp \alpha_s^2\rp$ and accounting for target mass effects.
+%
+No higher-twists corrections to the structure functions are included, since we cut
+data with $W^2 \ge 12.5$ GeV in order to suppress them.
+%
+Deviations from isoscalarity and nuclear modifications with respect
+to a free isoscalar target are accounted for at the input PDF level,
+leaving the grid entering the evaluation of Eq.~(\ref{eq:neutrino_DIS_xsec}) unchanged.
+%
+No heavy quark mass effects are considered for at the level of these inclusive structure functions.
+
+Concerning charm structure functions, for experiments with charm tagging
+capabilities theoretical predictions are evaluated for
+\be
+\label{eq:neutrino_DIS_xsec}
+\frac{d^2\sigma^{\nu N}_c(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F_{2,c}^{\nu N}(x,Q^2) - y^2F^{\nu N}_{L,c}(x,Q^2) +Y_- xF^{\nu N}_{3,c}(x,Q^2)\rc  \, ,
+\ee
+with the DIS charm structure functions evaluated in the FONLL general-mass variable-flavour-number
+scheme~\cite{Forte:2010ta,Ball:2011mu,Faura:2020oom} in order to account for charm mass effects.
+%
+Eq.~(\ref{eq:neutrino_DIS_xsec}) is computed with $\mathcal{O}\lp \alpha_s^2\rp$ massless
+coefficient functions and $\mathcal{O}\lp \alpha_s\rp$ massive ones, given
+that the $\mathcal{O}\lp \alpha_s^2\rp$ massive calculation~\cite{Gao:2017kkx} is not publicly available.
+%
+Nevertheless, the $\mathcal{O}\lp \alpha_s\rp$ massive coefficient functions
+encapsulate the dominant charm mass dependence of the double differential
+cross-section.
+%
+We assume 100\% efficiency in charm tagging and do not impose acceptance cuts on the charm
+quark or $D$-meson kinematics (the only acceptance requirements are applied to the final-state
+charged lepton, as indicated in  Table~\ref{tab:FPF_experiments}).
+
+We note that experiments without charm-tagging capabilities can still identify charm production
+events by means of the dimuon final state,
+\be
+\nu + N \to \mu^+ + c~(\to D) + X \to \mu^+ + \mu^- +X \, ,
+\ee
+by profiting from the semileptonic decays of the $D$-meson leading
+to the characteristic signature of two opposite-sign muons.
+%
+In this case, the  differential charm production cross-section Eq.~(\ref{eq:neutrino_DIS_xsec})
+must be accompanied by the corresponding branching ratio
+\be
+\frac{d^2\sigma^{\nu N}_c(x,Q^2,y)}{dxdy}\mathcal{B}\lp c \to D \to \mu + X\rp \, ,
+\ee
+which given that $\mathcal{B}\sim 10\%$ suppresses the reconstructed charm
+production event yields by around an order of magnitude.
+%
+For experiments reconstructing the dimuon final state,
+we also apply the muon acceptance criteria to both muons.
+
+\subsection{Hessian profiling}
+\label{sec:profiling}
+
+In this work we consider two complementary approaches in order to assess the
+impact of LHC neutrino data on the proton and nuclear PDFs.
+%
+On the one hand, the Hessian profiling of a prior proton or
+nuclear PDF set, which here are taken to be PDF4LHC21~\cite{PDF4LHCWorkingGroup:2022cjn} and
+EPPS21~\cite{Eskola:2021nhw} respectively.
+%
+On the other hand, the inclusion of the LHC neutrino structure functions
+on the NNPDF global analysis framework~\cite{NNPDF:2021uiq,NNPDF:2021njg}.
+%
+Here we summarise the details of the Hessian profiling procedure and
+outline how it is applied in our work.
 
@@
 
-\subsection{Modelling DIS structure functions}
+To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed and is available with the open-source {\sc\small xFitter} code.
 
- %
-Theoretical predictions for neutrino DIS structure functions are evaluated with the {\sc\small EKO}~\cite{Candido:2022tld}
-and {\sc\small YADISM}~\cite{yadism,Candido:2023utz} programs interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss, christopher_schwan_2023_7995675}, with the latter providing the fast interpolation grids to be used in the fit.
-%
-To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed and is available with the open-source {\sc\small xFitter} code.
+\subsection{Implementation in NNPDF}

### 2023-07-04 paper/sec-analysis.tex
Update sec-analysis.tex

@@
 
-The expected impact of the FPF data on global PDF fits is assessed by a profiling procedure~\cite{Paukkunen:2014zia, Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre}, based on minimizing the function
-%TODO correlations are also included here, as we hopefully get there in the end -- if not, remove terms involving correlations+pseudodata
+The profiling method applied to Hessian PDF fits is described in~\cite{Paukkunen:2014zia, Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre} and is based
+on minimizing a goodness-of-fit error function defined as
 \begin{equation}
 \chi^2 = 
-\sum_{i=1}^{N_{\textrm{bins}}} 
-\frac{\left(  \sigma_i^{\textrm{pd}}
+\sum_{i=1}^{N_{\textrm{bin}}} 
+\frac{\left(  \mathcal{O}_i^{\rm (exp)}
             + \Gamma_i^{\alpha,\textrm{pd}}
-              b_\alpha^{\textrm{pd}}
-            - \sigma_i^{\textrm{th}}
+              b_\alpha^{\textrm{(pd)}}
+            - \mathcal{O}_i^{\textrm{th}}
             - \Gamma_i^{\beta,\textrm{th}}
-              b_\beta^{\textrm{th}}
+              b_\beta^{(\textrm{th})}
      \right)^2
-     }{\Delta_i^2}
-+ \sum_\alpha (b_\alpha^{\textrm{pd}})^2
-+ \sum_\beta  (b_\beta^{\textrm{th}})^2 \, .
+     }{\delta_{{\rm stat},i}^2}
++ \sum_\alpha \lp b_\alpha^{(\textrm{pd})}\rp^2
++ \sum_\beta  \lp b_\beta^{\textrm{(th)}}\rp ^2 \, .
 \label{eq:profilingchi2}
 \end{equation}
-Here the pseudodata 
-$\sigma_i^{\textrm{pd}}$ 
+The pseudodata 
+$\mathcal{O}_i^{\rm (exp)}$ 
 is obtained from the central theoretical prediction 
-$\sigma_i^{\textrm{th}}$ 
-for each bin $i$ out of $N_{\textrm{bins}}$ by varying it within bounds obtained from the statistical (systematic) uncertainties 
-$\delta_i^{\textrm{stat}}$ ($\delta_i^{\textrm{syst}}$), 
-obtained in the procedure described in Section~\ref{sec:pseudo-data_generation}, 
-as
+$\mathcal{O}_i^{(\textrm{th})}$
+for each bin $i$ out of $N_{\textrm{bin}}$ by fluctuating
+it within its uncertainties, following either
+Eq.~(\ref{eq:pseudo_data}), when accounting for the correlations
+between systematic uncertainties, or Eq.~(\ref{eq:pseudo_data_v2}),
+in the case in which errors are added in quadrature.
 
-\begin{equation}
-\sigma_i^{\textrm{pd}}
-=
-\sigma_i^{\textrm{th}}
-\left( 1 + r_i \sqrt{     (\delta_i^{\textrm{stat}})^2
-                      + (f \delta_i^{\textrm{syst}})^2 }
-\right).
-\end{equation}
-Here, $r_i$ is a univariate Gaussian random number and $f = 0.5$ an effective correction factor 
-accounting for the improved constraining power of the same pseudodata set using correlated systematics, compared to solely adding all sources of uncertainty in quadrature.
+The correlated uncertainties for the pseudodata and for the theoretical prediction 
+are contained in the nuisance parameter vectors $b^{(\textrm{pd})}$ and $b^{(\textrm{th})}$, respectively, and the total uncorrelated uncertainties are denoted by $\delta_{{\rm stat},i}$.
 %
-The correlated uncertainties for the pseudodata and the theoretical prediction 
-are contained in the nuisance parameter vectors $b^{\textrm{pd}}$ and $b^{\textrm{th}}$, respectively, and the uncorrelated uncertainties in $\Delta_i$.
+The effect of the nuisance parameters
+on the observables $\mathcal{O}_i^{\rm (exp)}$ and $\mathcal{O}_i^{\rm (th)}$
+is described by the matrices $\Gamma_i^{\textrm{pd}}$ and $\Gamma_i^{\textrm{th}}$.
 %
-Their effect on $\sigma^{\textrm{th}}$ and $\sigma^{\textrm{pd}}$
-is described by the matrices $\Gamma_i^{\textrm{pd}}$ and $\Gamma_i^{\textrm{th}}$.
 The indices $\alpha$ and $\beta$ then run over the uncertainty nuisance parameters for the pseudodata and the theoretical prediction, respectively.
 %
-The nuisance parameter values $b^{\textrm{th(min)}}$ that minimize Eq.~\eqref{eq:profilingchi2} give the central PDFs $f'_0$ optimized to the profiled dataset in the form
+The nuisance parameter values $b_\beta^{\textrm{(th,min)}}$ that minimize Eq.~\eqref{eq:profilingchi2} give the central PDFs $f'_0$ optimized to the profiled dataset in the form
 \begin{equation}
 f_0' = f_0
-      + \sum_\beta b_\beta^{\textrm{th(min)}} 
+      + \sum_\beta b_\beta^{\textrm{(th,min)}} 
         \left(  \frac{f_\beta^+   -  f_\beta^- }{2}
-              -    b_\beta^{\textrm{th(min)}}
+              -    b_\beta^{\textrm{(th,min)}}
                 \frac{f_\beta^+ + f_\beta^- - 2f_0}{2}
@@
 where $f_0$ is the original central PDF and the up and down variation eigenvectors are given by $f^+, f^-$.
-The decrease in the uncertainties of the shifted PDFs indicates the enhancement that including the FPF data in the global PDF fit could bring.
-Here, the profiling studies are performed using version 2.2.1 of the \textsc{xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}.
 %
+The reduction in the uncertainties of the profiled PDFs indicate the impact
+of the projected data with respect to the assumed prior PDF set.
 
-To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed and is available with the open-source {\sc\small xFitter} code.
+The profiling studies carried out in this work are performed using v2.2.1 of the \textsc{xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}.
+%
+To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed and is available in {\sc\small xFitter}.
+%
+All the experimental and theoretical data files used in the analysis, including
+the  {\sc\small PineAPPL}  grids, are available
+from the {\sc\small xFitter} repository.
 

### 2023-07-04 paper/sec-summary.tex
summary

@@
 
-In this work ....
+In this work, we have quantified the impact of ongoing and proposed
+experiments detecting the scattering of energetic neutrinos produced
+by LHC collisions in the forward direction.
+%
+By means of estimating the expected deep-inelastic scattering
+event rates differential
+in $x$, $Q^2$, and $E_\nu$ for these various experiments, and
+evaluating the associated theoretical predictions for
+both inclusive and charm production processes, we have
+assessed the expected reduction of PDF uncertainties with respect
+to modern fits of proton and nuclear structure.
+%
+To this end, we have studied the robustness of the results
+with respect the modelling of systematic uncertainties, the role of lepton
+charge separation, and the impact of the selection and acceptance cuts.
+
+We demonstrate that neutrino DIS measurements at the proposed FPF
+experiments would have a significant potential to improve our current
+knowledge of quark and antiquark flavour separation in protons
+and heavy nuclei, including strangeness,
+and that the FASER$\nu$ and SND@LHC
+experiments may provide the first-ever
+constraints on hadron structure from collider neutrinos.
+%
+Together with this paper, we also
+release the pseudodata and the corresponding theory
+calculations produced in this work.
+%
+These should be of relevance for colleagues interested in the physics
+of forward
+neutrino scattering at the LHC, not only for hadronic structure studies
+but also for neutrino (effective)
+interactions and BSM searches e.g. of sterile neutrino oscillations.
+
+Several avenues extending the results of this work may be foreseen.
+%
+First of all, as the design of the proposed FPF experiments
+becomes more advanced and concrete, it should be possible more reliable
+estimate of corrections, may become the limiting factor
+for this kind of analyses.
+%
+Improve event generation, based on {\sc\small Pythia}
+modern QCD generator with higher order QCD corrections,
+why improve estimates better modelling of final state acceptance.
+%
+Analysis also SIS region low $Q$, improve modelling of low-$Q$ cross-sections
+relevant for atmospheric and oscillation neutrino experiments.
+%
+Neglect flux uncertainties, joint determination
+
+All in all, Our analysis highlights how exploiting the potential
+ of this unique neutrino beam  effectively
+extends the LHC with a ``Neutrino-Ion Collider''.
+
+\subsection*{Acknowledgments}
+%
+We are grateful to many colleagues involved in the Forward
+Physics Facility initiative for many illuminating
+discussions and encouragement.

### 2023-07-04 paper/sec-summary.tex
Update sec-summary.tex

@@
 First of all, as the design of the proposed FPF experiments
-becomes more advanced and concrete, it should be possible more reliable
-estimate of corrections, may become the limiting factor
-for this kind of analyses.
+becomes more advanced and concrete, it should be possible
+to construct more accurate estimates of the systematic
+uncertainties and of their bin-by-bin correlations,
+which may eventually become the limiting factor
+for hadron structure analyses with LHC neutrinos.
 %
-Improve event generation, based on {\sc\small Pythia}
-modern QCD generator with higher order QCD corrections,
-why improve estimates better modelling of final state acceptance.
+Second, scattering analyses with LHC neutrinos would benefit from
+the use of Monte Carlo event generators accounting
+for higher-order QCD corrections.
 %
-Analysis also SIS region low $Q$, improve modelling of low-$Q$ cross-sections
-relevant for atmospheric and oscillation neutrino experiments.
+As compared to the currently used LO generators,
+these would improve the modelling of the final-state leptonic
+and hadronic kinematics, which in turn determine the acceptance rate
+of the reconstructed events.
 %
-Neglect flux uncertainties, joint determination
+Further, the predictions from such precise Monte Carlo generators
+should eventually be folded with a full-fledged detector simulation
+in order to robust determine selection efficiencies, e.g.
+such as those related to charm tagging.
 
-All in all, Our analysis highlights how exploiting the potential
- of this unique neutrino beam  effectively
-extends the LHC with a ``Neutrino-Ion Collider''.
+Third, while in this work we have focused on the deep-inelastic
+region, ongoing and future LHC experiments also provide
+important information on the shallow-inelastic scattering (SIS)
+region at low values of $Q$~\cite{Candido:2023utz}, relevant for inclusive cross-sections
+entering atmospheric and oscillation neutrino experiments.
+%
+By means of a similar approach, it should be possible to quantify
+the improvements that LHC neutrino data can provide on models
+of neutrino scattering in the poorly-understood SIS region.
+%
+Finally, in this work we have taken the incoming muon neutrino flux
+as a given and neglected any associated uncertainties.
+%
+However, ultimately one may need to constrain at the same time
+the incoming fluxes and the neutrino scattering cross-sections
+from the recorded event rates.
+%
+Such joint interpretation would require extending the present
+analysis with additional theory nuisance parameters modelling
+deviations of the neutrino flux with respect to the baseline predictions.
+
+All in all, our findings highlight how exploiting
+the LHC neutrino beam for hadron structure studies effectively
+extends the LHC with a ``Neutrino-Ion Collider'', a charged
+current-counterpart of the EIC, and that we are still
+scratching the surface of the uncharted
+scientific potential of such experiments.
 
@@
 discussions and encouragement.
+%
+We thank Akitaka Ariga and Tomoko Ariga for information
+concerning FASER$\nu$2,
+Wenjie Wu and Steven Linden concerning FLArE,
+and Antonia di Crescenzo concerning AdvSND.

### 2023-07-04 paper/sec-dis-pseudodata.tex
Revert "Update sec-dis-pseudodata.tex"
This reverts commit cbce81e997ce92974809e520a15f7827b6f3d2bc.
sect 4

--- 2023-06-22 paper/sec-dis-pseudodata.tex
@@
   See the description of each experiment in the text for more details.
+  %
+  For the projections in this work we assume that FASER$\nu$ and SND@LHC acquire data
+  for the full Run III period, while FASER$nu$2, AdvSND, and FLArE take data
+  for the complete HL-LHC period.
   \label{tab:FPF_experiments}
@@
 %-----------------------------------------------------------------------
-\begin{figure}[t]
+\begin{figure}[!ht]
     \centering
@@
     \label{fig:fasernu2_muon}
+\end{figure}
+%-----------------------------------------------------------------------
+
+%-----------------------------------------------------------------------
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=\textwidth]{plots/percentage_errors.pdf}
+	\caption{Estimate of the systematic uncertainties at FASER$\nu$2 coming from the final-state 
+		lepton energy $E_\ell$ for the inclusive and charm productions. The different markers
+		represent the charge of the incoming neutrino.
+	}
+	\label{fig:percentage_error_elepton}
 \end{figure}

### 2023-07-04 paper/sec-protonPDFs.tex
sect 4

@@
 \clearpage
-\section{Impact on the proton PDFs}
+\section{Constraints on proton structure}
 \label{sec:protonPDFs}
 
-Using the PDF4LHC21~\cite{PDF4LHCWorkingGroup:2022cjn} PDF set, the results are illustrated by comparing the fractional uncertainties of the original PDF set to those obtained after profiling. 
-This is shown for the valence quark, gluon and the singlet distributions in Fig.~\ref{FASERv2_profiling} for FASER$\nu$2 pseudodata, while Fig.~\ref{FASERv_profiling} indicates the impact of FASER$\nu$.
-FASER$\nu$2 is observed to provide tighter constraints on the PDFs, with the effects being the most prominent for the valence and sea quark distributions.
+By means of the strategy outlined in Sect.~\ref{sec:settings}, here we study the constraints that differential neutrino DIS
+cross-section measurements at the LHC have on the quark and gluon substructure of the proton.
+%
+In this section we assume an isoscalar free-nucleon target and neglect non-isoscalarity effects and nuclear modifications,
+which are instead considered in Sect.~\ref{sec:nuclearPDFs}.
+%
+We present results first for the Hessian profiling of the PDF4LHC21 combination of global PDF sets
+and second for the inclusion in the Monte Carlo fit NNPDF4.0.
+%
+We study the dependence on the result with respect to the choice of fitted dataset, the experiment considered,
+the modelling of experimental systematic uncertainties, and the availability or not of charged lepton separation.
 
-\begin{figure}[H]
+\subsection{Impact on PDF4LHC21}
+\label{sec:pdf4lhc21}
+
+For the Hessian profiling studies following the procedure of Sect.~\ref{sec:profiling}, the prior PDF set is taken to
+be PDF4LHC21 NNLO, a Monte Carlo combination~\cite{Watt:2012tq,Carrazza:2015hva} of three global PDF sets (CT18~\cite{Hou:2019efy},
+MSHT20~\cite{Bailey:2020ooq}, and NNPDF3.1~\cite{NNPDF:2017mvq}) for which Hessian
+representations~\cite{Gao:2013bia,Carrazza:2015aoa} are also provided.
+%
+PDF4LHC21, being based on the combination of three modern global fits, provides a reasonable representation
+of our current understanding of the proton PDFs.
+%
+We profile PDF4LHC21 with the various sets of LHC neutrino pseudo-data and assess the reduction
+of PDF uncertainties in each case.
+%
+In this analysis, a tolerance of $T = \sqrt{\Delta \chi^2}=3$ is adopted, which is the average tolerance
+used in the CT18 and MSHT20 Hessian determinations.
+%
+Note that we use a consistent perturbative accuracy in the prior PDF set and in the theoretical calculations.
+
+In the following, we first compare the impact on PDF4LHC21 of a baseline LHC neutrino dataset and subsequently
+we assess the stability of this result with respect to a range of variations of its input.
+
+\paragraph{Baseline results.}
+%
+The baseline dataset is defined as follows.
+%
+We consider the FASER$\nu$2 experiment integrated over the full duration of the HL-LHC data-taking period,
+we account both for inclusive and charm production structure functions, we consider the scenario
+in which systematic errors can be neglected, and we allow for charge separation of the outgoing lepton.
+%
+This baseline result therefore represents the best-case scenario and quantifies the maximum impact that can be expected
+on the PDFs: we then assess to which extent variations of these input choices degrade the reach of the pseudo-data.
+
+Fig.~\ref{fig:profiling_baseline} displays the fractional uncertainties at the 68\% confidence level
+for the up and down valence quarks, total quark singlet, strangeness, charm, and gluon PDFs
+in PDF4LHC21 compared to the results of its profiling with this baseline LHC neutrino dataset, namely
+FASER$\nu$2 with only statistical errors, both inclusive and charm structure functions,  and charge flavour
+separation.
+%
+The same style of PDF comparisons will be adopted through this section.
+%
+Results are shown at $Q^2 = 10^4 \, \textrm{GeV}^2$ and the residual shift in central values
+arising from the profiling is ignored.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\begin{figure}[t]
 \centering
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_g_ratio.pdf}
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\caption{The fractional uncertainties in the valence quark, gluon and singlet PDFs as a function of the momentum fraction $x$ at the scale $Q^2 = 10000 \, \textrm{GeV}^2$.
-The profiling is performed using the
-PDF4LHC21 set and the pseudodata for FASER$\nu$2. The original uncertainty of PDF4LHC21 is
-indicated by the red band, while the blue band demonstrates the profiled result.}
-\label{FASERv2_profiling}
+\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\caption{The fractional uncertainties (at the 68\% confidence level)
+for the up and down valence quarks, total quark singlet, strangeness, charm, and gluon PDFs
+in PDF4LHC21 compared to the results of its profiling with the baseline LHC neutrino dataset, namely
+FASER$\nu$2 with only statistical errors, both inclusive and charm structure functions,  and charge flavour
+separation.
+%
+Results are shown at the scale $Q^2 = 10^4 \, \textrm{GeV}^2$ and the shift in central values
+is not considered.}
+\label{fig:profiling_baseline}
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_dv_ratio.pdf}\\
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_g_ratio.pdf}
-\includegraphics[width=0.4\textwidth]{./figs_xFitter/FASERv_q2_10000_pdf_Sea_ratio.pdf}
-\caption{The fractional uncertainties in the valence quark, gluon and singlet PDFs as a function of the momentum fraction $x$ at the scale $Q^2 = 10000 \, \textrm{GeV}^2$.
-The profiling is performed using the
-PDF4LHC21 set and the pseudodata for FASER$\nu$. The original uncertainty of PDF4LHC21 is
-indicated by the red band, while the blue band demonstrates the profiled result.}
-\label{FASERv_profiling}
-\end{figure}
+In the following we consider the stability of the results in Fig.~\ref{fig:profiling_baseline}
+with respect to the chosen experiment and integrated luminosity, the modelling of systematic
+uncertainties, being able to identify or not charm production, and being able to tell part outgoing
+charged leptons from anti-leptons.
+
+\paragraph{Dependence with the experiments.}
+%
+Same as Fig.~\ref{fig:profiling_baseline} comparing FASER$\nu$2 with AdvSND and with FASER$\nu$.
+
+\paragraph{Impact of systematic uncertainties.}
+%
+Same as Fig.~\ref{fig:profiling_baseline} for different scenarios concerning the experimental
+systematic uncertainties.
+
+\paragraph{Impact of charm production.}
+%
+Same as Fig.~\ref{fig:profiling_baseline} comparing the baseline LHC neutrino dataset with the results
+of a profiling without the charm production structure functions.
+
+\paragraph{The role of lepton charge separation.}
+%
+Same as Fig.~\ref{fig:profiling_baseline} comparing the baseline LHC neutrino dataset with the results
+of a profiling without allowing for the possibility of outgoing lepton charge separation.
+
+\subsection{Impact on NNPDF4.0}
+\label{sec:nnpdf40}
+
+Selection of the {\sc\small xFitter} results for the NNPDF case.

### 2023-07-04 paper/sec-dis-pseudodata.tex
sect 2

@@
 
+Finally, we would like to compare the kinematic reach
+of the LHC neutrino measurements with respect to that of other experiments.
+%
+Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF} displays
+the kinematic coverage of the FASER$\nu$2 experiment in the $(x,Q^2)$ plane,
+same as  Fig.~\ref{fig:error_plot_FASERv2_14} now removing bins
+containing less than 30 reconstructed events.
+%
+It is compared to that of electron-ion collisions
+at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
+as well as to the kinematic coverage of other available hard-scattering datasets involving
+nuclear targets or projectiles.
+%
+Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
+fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
+production in proton-lead collisions at the LHC.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h]
+    \centering
+    \includegraphics[width = 0.8\textwidth]{plots/Kin_nNNPDF30_EIC_FPF.pdf}
+    \caption{The kinematic coverage of the FASER$\nu$2 experiment in the $(x,Q^2)$ plane,
+      same as  Fig.~\ref{fig:error_plot_FASERv2_14} now removing bins
+      containing less than 30 reconstructed events.
+      %
+      It is compared to that of electron-ion collisions
+      at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
+      as well as to the kinematic coverage of other available hard-scattering datasets involving
+      nuclear targets or projectiles.
+      %
+      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
+      fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
+      production in proton-lead collisions at the LHC.
+      }
+    \label{fig:Kin_nNNPDF30_EIC_FPF}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Systematic uncertainties}
+\label{sec:systematic_uncertainties}
 

### 2023-07-04 paper/sec-dis-pseudodata.tex
added discussion in Sect 2

@@
 \includegraphics[width=0.9\textwidth]{plots/Nevent_FASERv2_14.pdf}
-\caption{The event yields per bin $ N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}),
+\caption{\small The event yields per bin $ N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}),
   for muon neutrinos at FASER$\nu$2.
@@
 
+Fig.~\ref{fig:percentage_error_elepton}
+displays the estimated systematic uncertainties for the  measurements
+of the double-differential
+neutrino scattering cross-section at FASER$\nu$2.
+%
+We consider the leading sources of systematic errors,
+associated respectively to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$
+and to the hadronic energy $E_h$.
+%
+The size of each source of systematic error is plotted as a function
+of the average momentum fraction per bin $\la x\ra$
+in three different bins of $Q^2$.
+%
+We indicate separately the results for neutrino and antineutrino projectiles as well as
+those associated to inclusive and to charm production measurements.
+%
+Systematic uncertainties associated to the hadronic final state energy $E_h$ appear to be the largest.
+%
+The uncertainties associated to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$ range
+between a few percent up to 20\% in the nominal baseline scenario,
+and in the case of the latter they are the smallest in the large-$x$ region.
+%
+Similar overview plots have been produced for the other LHC neutrino experiments
+considered in this work.
+
 %-----------------------------------------------------------------------
@@
   \includegraphics[width=\textwidth]{plots/percentage_errors.pdf}
-	\caption{Estimate of the systematic uncertainties at FASER$\nu$2 coming from the final-state 
-		lepton energy $E_\ell$ for the inclusive and charm productions. The different markers
-		represent the charge of the incoming neutrino.
+  \caption{\small Estimated systematic uncertainties for the  measurements
+    of the double-differential
+    neutrino scattering cross-section at FASER$\nu$2.
+    %
+    We consider the leading sources of systematic errors,
+    associated respectively to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$
+    and to the hadronic energy $E_h$.
+    %
+    The size of each source of systematic error is plotted as a function
+    of the average momentum fraction per bin $\la x\ra$
+    in three different bins of $Q^2$.
+    %
+    We indicate separately the results for neutrino and antineutrino projectiles as well as
+    those associated to inclusive and to charm production measurements.
   }
-	\label{fig:percentage_error_elepton}
+  \label{fig:percentage_uncertainties_overview}
 \end{figure}

### 2023-07-04 paper/sec-nuclearPDFs.tex
more on sect 5

@@
 
-Here we study
+The study presented in Sect.~\ref{sec:protonPDFs} treated, from the point of view
+of PDF constraints, the neutrino scattering target
+as composed by isoscalar free-nucleons, and hence neglecting nuclear modifications
+and non-isoscalar effects.
+%
+We now revisit this analysis but accounting for the fact that the target materials in the FPF
+experiments actually
+composed by heavy nuclei, specifically by tungsten (the exception is FLArE with liquid argon, which
+is however not considered here).
+%
+Nuclear modifications associated to a tungsten target are not necessarily small as compared
+to a free isoscalar nucleon, and hence will affect the event rate predictions for
+the FPF experiments.
+%
+Turning the argument around, measurememnts of differential neutrino cross-sections
+on heavy nuclear targets provide direct constraints on these nuclear modifications
+without replying on assumptions on the $A$ dependence.
+
+For this exercise, the prior nuclear PDF set is taken to be EPPS21, a global determination
+that accounts for the constraints of existing datasets involving nuclei as target or projectiles.
+%
+In particular, EPPS21 already includes information from neutrino DIS on nuclear targets
+from the CHORUS and NuTeV experiments.
+%
+The application of Hessian profiling to EPPS21 follows the same strategy as that
+for PDF4LHC21, with the caveat that its Hessian error sets also include the contribution
+from the uncertainties  associated to their reference proton PDF set, in this case CT18.
+%
+Given that the measured event rates depend on both the proton PDFs and the nuclear modifications,
+when profiling EPPS21 we also account for the Hessian sets associated to the CT18 proton
+PDF dependence.
+
+Fig.~\ref{fig:profiling_baseline_nuclear} displays the same comparisons
+as in Fig.~\ref{fig:profiling_baseline},
+now for the profiling of the EPPS21 global determination of nuclear PDFs,
+specifically of the set with $A=184$ (tungsten target).
+%
+Also in this case we consider first the impact of the baseline LHC neutrino dataset, consisting
+on the FASER$\nu$2 experiment
+with statistical errors only, inclusive and charm structure functions,  and charge flavour
+separation.
+%
+The bands indicate the 68\% CL uncertainties.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/statOnly_FASERv2_q2_10000_pdf_uV_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/statOnly_FASERv2_q2_10000_pdf_dV_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\caption{Same as Fig.~\ref{fig:profiling_baseline},
+now for the profiling of the EPPS21 global determination of nuclear PDFs,
+specifically of the set with $A=184$ (tungsten target).
+%
+Also in this case we consider first the impact of the baseline LHC neutrino dataset, consisting
+on the FASER$\nu$2 experiment
+with statistical errors only, inclusive and charm structure functions,  and charge flavour
+separation.
+%
+The bands indicate the 68\% CL uncertainties.
+}
+\label{fig:profiling_baseline_nuclear}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Plots EPPS21 tungsten target? To quantify size of nuclear modifications?

### 2023-07-05 paper/sec-nuclearPDFs.tex
Updated stat-unc-only baseline plots

@@
 \centering
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/statOnly_FASERv2_q2_10000_pdf_uV_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/statOnly_FASERv2_q2_10000_pdf_dV_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
 \caption{Same as Fig.~\ref{fig:profiling_baseline},

### 2023-07-05 paper/sec-protonPDFs.tex
Updated stat-unc-only baseline plots

@@
 \centering
-\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_g_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{./figs_xFitter/FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
 \caption{The fractional uncertainties (at the 68\% confidence level)

### 2023-07-05 paper/sec-nuclearPDFs.tex
Added comparison to the inclusive+charm baseline into the no-charm case plots

@@
 %
-Turning the argument around, measurememnts of differential neutrino cross-sections
+Turning the argument around, measurements of differential neutrino cross-sections
 on heavy nuclear targets provide direct constraints on these nuclear modifications
@@
 
+{\color{red}
+The effect of including correlated systematic uncertainties is shown in 
+Fig.~\ref{fig:profiling_syst_nuclear}
+}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
@@
 \includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
 \includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\caption{Same as Fig.~\ref{fig:profiling_baseline_nuclear}, 
+but accounting for the statistical as well as correlated systematic uncertainties.
+}
+\label{fig:profiling_syst_nuclear}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\caption{Comparing Fig.~\ref{fig:profiling_baseline_nuclear}, 
+to the results obtained without charm production structure functions.
+}
+\label{fig:profiling_charm_nuclear}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2023-07-05 paper/sec-protonPDFs.tex
Added comparison to the inclusive+charm baseline into the no-charm case plots

@@
 %
-Same as Fig.~\ref{fig:profiling_baseline} for different scenarios concerning the experimental
-systematic uncertainties.
+The effect of including correlated systematic uncertainties is shown in 
+Fig.~\ref{fig:profiling_syst}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\caption{Same as Fig.~\ref{fig:profiling_baseline}, 
+but accounting for the statistical as well as correlated systematic uncertainties.
+}
+\label{fig:profiling_syst}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %
-Same as Fig.~\ref{fig:profiling_baseline} comparing the baseline LHC neutrino dataset with the results
-of a profiling without the charm production structure functions.
+Fig.~\ref{fig:profiling_charm} displays a comparison of the baseline LHC neutrino dataset with the results
+of profiling without the charm production structure functions. 
+Particularly, the constraints on the $s$ PDF are observed to become more stringent 
+by virtue of the contribution of the charm production structure functions.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\caption{Comparing the results shown in Fig.~\ref{fig:profiling_baseline} (red and blue), 
+to the results obtained without charm production structure functions (green).
+}
+\label{fig:profiling_charm}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2023-07-05 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/statOnly/FASERv2_inclusive/run.sh

@@ -22,7 +22,7 @@ xfitter
 
 # Visualize results:
 mv plots/plots.pdf plots/plots_OLD.pdf
-xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+xfitter-draw ${PLOTOPTS} output:"${DATATXT} (CD)" profile:../${DETSIMPLE}/output:"CD+${DETECTOR}" profile:output:"CD+${DETECTOR}, no charm"
 mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
 
 cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 

### 2023-07-05 xFitter/PDF_profiling/PDF4LHC21/statOnly/FASERv2_inclusive/run.sh

@@ -20,11 +20,11 @@ PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e
 ln -s ../../../../datafiles
 
 # Run xFitter:
-xfitter
+#xfitter
 
 # Visualize results:
 mv plots/plots.pdf plots/plots_OLD.pdf
-xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+xfitter-draw ${PLOTOPTS} output:"${DATATXT} (CD)" profile:../${DETSIMPLE}/output:"CD+${DETECTOR}" profile:output:"CD+${DETECTOR}, no charm"
 mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
 
 cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 

### 2023-07-05 paper/sec-nuclearPDFs.tex
Added stat-only baseline comparison to stat+syst and nochargediscrimination plots

@@
 \includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{Same as Fig.~\ref{fig:profiling_baseline_nuclear}, 
-but accounting for the statistical as well as correlated systematic uncertainties.
+\caption{The results of Fig.~\ref{fig:profiling_baseline_nuclear} (red and blue), 
+compared to profiling with the statistical as well as correlated systematic uncertainties accounted for.
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\caption{Comparing the results shown in Fig.~\ref{fig:profiling_baseline_nuclear} (red and blue), 
+to the results obtained without identifying the charge of the outgoing lepton (green).
+}
+\label{fig:profiling_nochargediscrimination_nuclear}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2023-07-05 paper/sec-protonPDFs.tex
Added stat-only baseline comparison to stat+syst and nochargediscrimination plots

@@
 %
-Same as Fig.~\ref{fig:profiling_baseline} comparing the baseline LHC neutrino dataset with the results
+Fig.~\ref{fig:profiling_nochargediscrimination} compares the baseline LHC neutrino dataset with the results
 of a profiling without allowing for the possibility of outgoing lepton charge separation.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\caption{Comparing the results shown in Fig.~\ref{fig:profiling_baseline} (red and blue), 
+to the results obtained without identifying the charge of the outgoing lepton (green).
+}
+\label{fig:profiling_nochargediscrimination}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2023-07-05 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/statOnly/FASERv2_nochargediscrimination/run.sh

@@ -22,7 +22,7 @@ xfitter
 
 # Visualize results:
 mv plots/plots.pdf plots/plots_OLD.pdf
-xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+xfitter-draw ${PLOTOPTS} output:"${DATATXT} (CD)" profile:../${DETSIMPLE}/output:"CD+${DETECTOR}" profile:output:"CD+${DETECTOR}, no charge id."
 mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
 
 cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 

### 2023-07-05 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/syst/FASERv2/run.sh

@@ -22,8 +22,7 @@ xfitter
 
 # Visualize results:
 mv plots/plots.pdf plots/plots_OLD.pdf
-xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
-mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT} (CD)" profile:../../statOnly/${DETSIMPLE}/output:"CD+${DETECTOR}, stat" profile:output:"CD+${DETECTOR}, stat+syst"
 
 cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
 cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 

### 2023-07-05 xFitter/PDF_profiling/PDF4LHC21/statOnly/FASERv2_inclusive/run.sh

@@ -20,7 +20,7 @@ PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e
 ln -s ../../../../datafiles
 
 # Run xFitter:
-#xfitter
+xfitter
 
 # Visualize results:
 mv plots/plots.pdf plots/plots_OLD.pdf

### 2023-07-05 xFitter/PDF_profiling/PDF4LHC21/statOnly/FASERv2_nochargediscrimination/run.sh

@@ -24,7 +24,7 @@ xfitter
 
 # Visualize results:
 mv plots/plots.pdf plots/plots_OLD.pdf
-xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+xfitter-draw ${PLOTOPTS} output:"${DATATXT} (CD)" profile:../${DETSIMPLE}/output:"CD+${DETECTOR}" profile:output:"CD+${DETECTOR}, no charge id."
 mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
 
 cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 

### 2023-07-05 xFitter/PDF_profiling/PDF4LHC21/syst/FASERv2/run.sh

@@ -24,7 +24,7 @@ xfitter
 
 # Visualize results:
 mv plots/plots.pdf plots/plots_OLD.pdf
-xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+xfitter-draw ${PLOTOPTS} output:"${DATATXT} (CD)" profile:../../statOnly/${DETSIMPLE}/output:"CD+${DETECTOR}, stat" profile:output:"CD+${DETECTOR}, stat+syst"
 mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
 
 cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 

### 2023-07-06 paper/sec-analysis.tex
summary
Removed mentions of reduction factor 0.5 which is now unnecessary, unified notation

@@
               b_\alpha^{\textrm{(pd)}}
-            - \mathcal{O}_i^{\textrm{th}}
+            - \mathcal{O}_i^{\rm (th)}
             - \Gamma_i^{\beta,\textrm{th}}
@@
      \right)^2
-     }{\delta_{{\rm stat},i}^2}
+     }{ \left(\delta_i^{\rm stat}\right)^2 }
 + \sum_\alpha \lp b_\alpha^{(\textrm{pd})}\rp^2
@@
 \subsection{Implementation in NNPDF}
+\label{subsec:NNPDF}

### 2023-07-06 paper/sec-dis-pseudodata.tex
Removed mentions of reduction factor 0.5 which is now unnecessary, unified notation

@@
  The central values for the LHC neutrino scattering pseudo-data, denoted
- by $\mathcal{O}_i^{{\rm exp}} $, are obtained
+ by $\mathcal{O}_i^{{\rm (exp)}} $, are obtained
  by fluctuating this reference theory prediction by the statistical and systematic
@@
   \label{eq:pseudo_data}
-  \mathcal{O}_i^{{\rm (exp)}}  =   \mathcal{O}_i^{{\rm (th)}}\left( 1+ r^{(i)}_{\rm stat}\delta_{i,{\rm stat}}
-  + \sum_{k=E_\ell, E_h,\theta_\ell} r_{{\rm sys},k} \,\delta_{i,{\rm sys}}^{(k)}\right) \, , \qquad i=1,\ldots,N_{\rm bin} \, ,
+  \mathcal{O}_i^{{\rm (exp)}}
+  =   \mathcal{O}_i^{{\rm (th)}}\left( 1+ r_{i} \delta_{i}^{\rm stat}
+  + \sum_{k=E_\ell, E_h,\theta_\ell}
+    r'_{k} \,\delta_{i,k}^{{\rm sys}}\right) \, , \qquad i=1,\ldots,N_{\rm bin} \, ,
  \end{equation}
- with $r^{(i)}_{\rm stat}$ and $r_{{\rm sys},k}$ being univariate Gaussian random numbers,
- and $\delta_{\rm stat}$ ($\delta_{\rm sys}^{(k)}$) indicate the relative statistical (systematic)
- uncertainties associated to the $i$-th bin.
+ with $r_{i}$ and $r'_{k}$ being univariate Gaussian random numbers,
+ and $\delta_i^{\rm stat}$ ($\delta_{i,k}^{\rm sys}$) indicate the relative statistical (systematic)
+ uncertainties associated to the $i$-th bin (and $k$-th source of systematic uncertainty).
  %
@@
  \be
- \delta_{{\rm tot},i}^{\rm exp} = \left( \left( \delta_i^{\rm stat}\right)^2 + \sum_{k=1}^{n_{\rm sys}}
-\left( f_{{\rm red},j}\delta_{i,j}^{\rm sys} \right)^2\right)^{1/2} \, ,
+ \delta_{i}^{\rm tot}
+ = \left( \left( \delta_i^{\rm stat}\right)^2 + \sum_{k=1}^{n_{\rm sys}}
+\left( \delta_{i,k}^{\rm sys} \right)^2\right)^{1/2} \, ,
  \ee
- with $f_{{\rm red},j} \le 1$ quantifies the possible reduction of systematic uncertainties, and
- then the pseudo-data is evaluated by means of
+ and the pseudo-data is evaluated by means of
  \begin{equation}
   \label{eq:pseudo_data_v2}
-  \mathcal{O}_i^{{\rm (exp)}}  =   \mathcal{O}_i^{{\rm (th)}}\left( 1+ r^{(i)}_{\rm stat}\delta_{i,{\rm tot}}
-  \right) \, , \qquad i=1,\ldots,N_{\rm bin} \, .
+  \mathcal{O}_i^{{\rm (exp)}}
+  = \mathcal{O}_i^{{\rm (th)}}
+    \left( 1+ r_i \delta_i^{\rm tot}
+    \right) \,
+    , \qquad i=1,\ldots,N_{\rm bin} \, .
  \end{equation}

### 2023-07-13 paper/sec-protonPDFs.tex
sect 4

@@
 %
-In this section we assume an isoscalar free-nucleon target and neglect non-isoscalarity effects and nuclear modifications,
+We assume an isoscalar free-nucleon target and neglect non-isoscalarity effects and nuclear modifications,
 which are instead considered in Sect.~\ref{sec:nuclearPDFs}.
-%
-We present results first for the Hessian profiling of the PDF4LHC21 combination of global PDF sets
+
+We present results first for the Hessian profiling of the PDF4LHC21 combination,
 and second for the inclusion in the Monte Carlo fit NNPDF4.0.
 %
-We study the dependence on the result with respect to the choice of fitted dataset, the experiment considered,
-the modelling of experimental systematic uncertainties, and the availability or not of charged lepton separation.
+We study the stability of the results with respect to the inclusion of systematic uncertainties
+and  charm-tagged events, as well to the availability of outgoing lepton-charge separation.
+%
+We compare the impact of four of the experiments considered in Sect.~\ref{sec:dis_pseudodata}:
+FASER$\nu$ and SND@LHC (LHC Run III) with FASER$\nu$2 and AdvSND (HL-LHC).
 
-\subsection{Impact on PDF4LHC21}
+\subsection{Hessian profiling of PDF4LHC21}
 \label{sec:pdf4lhc21}
 
-For the Hessian profiling studies following the procedure of Sect.~\ref{sec:profiling}, the prior PDF set is taken to
+For the Hessian profiling studies based on the procedure of Sect.~\ref{sec:profiling}, the prior PDF set is taken to
 be PDF4LHC21 NNLO, a Monte Carlo combination~\cite{Watt:2012tq,Carrazza:2015hva} of three global PDF sets (CT18~\cite{Hou:2019efy},
-MSHT20~\cite{Bailey:2020ooq}, and NNPDF3.1~\cite{NNPDF:2017mvq}) for which Hessian
-representations~\cite{Gao:2013bia,Carrazza:2015aoa} are also provided.
+MSHT20~\cite{Bailey:2020ooq}, and NNPDF3.1~\cite{NNPDF:2017mvq}).
 %
-PDF4LHC21, being based on the combination of three modern global fits, provides a reasonable representation
-of our current understanding of the proton PDFs.
+The Hessian representations of PDF4LHC21 are obtained by means of the methodology developed in~\cite{Gao:2013bia,Carrazza:2015aoa}.
 %
-We profile PDF4LHC21 with the various sets of LHC neutrino pseudo-data and assess the reduction
-of PDF uncertainties in each case.
+Being based on the combination of three modern global PDF fits, PDF4LHC21 provides a robust estimate
+of  current uncertainties associated to our understanding of proton PDFs.
 %
-In this analysis, a tolerance of $T = \sqrt{\Delta \chi^2}=3$ is adopted, which is the average tolerance
+We profile PDF4LHC21 with various sets of LHC neutrino DIS projections in order to assess the stability
+of the results with respect to its different inputs, such as charm-tagged structure functions.
+%
+A tolerance of $T = \sqrt{\Delta \chi^2}=3$ is adopted, corresponding to the average tolerance
 used in the CT18 and MSHT20 Hessian determinations.
 %
-Note that we use a consistent perturbative accuracy in the prior PDF set and in the theoretical calculations.
+The consistent perturbative accuracy of the prior PDF set and the theoretical calculations entering
+the pseudo-data generation is always accounted for.
 
-In the following, we first compare the impact on PDF4LHC21 of a baseline LHC neutrino dataset and subsequently
-we assess the stability of this result with respect to a range of variations of its input.
-
-\paragraph{Baseline results.}
 %
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%
+The effect of including correlated systematic uncertainties is shown in 
+Fig.~\ref{fig:profiling_syst}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[t]
 \centering
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{The fractional uncertainties (at the 68\% confidence level)
-for the up and down valence quarks, total quark singlet, strangeness, charm, and gluon PDFs
-in PDF4LHC21 compared to the results of its profiling with the baseline LHC neutrino dataset, namely
-FASER$\nu$2 with only statistical errors, both inclusive and charm structure functions, and charge flavour
-separation.
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\caption{
+The fractional uncertainties   (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
+for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
+in PDF4LHC21 compared to the results of its profiling with the FASER$\nu$2
+DIS projections.
 %
-Results are shown at the scale $Q^2 = 10^4 \, \textrm{GeV}^2$ and the shift in central values
-is not considered.}
-\label{fig:profiling_baseline}
+In the latter case, we consider both only statistical errors and statistical and systematic
+errors added in quadrature.
+%
+The FASER$\nu$2 dataset used here accounts for both  inclusive and charm-tagged structure functions
+as well as for outgoing lepton charge-separation.
+%
+}
+\label{fig:profiling_syst}
 \end{figure}
@@
 \paragraph{Impact of systematic uncertainties.}
-%
-The effect of including correlated systematic uncertainties is shown in 
-Fig.~\ref{fig:profiling_syst}.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{Same as Fig.~\ref{fig:profiling_baseline}, 
-but accounting for the statistical as well as correlated systematic uncertainties.
-}
-\label{fig:profiling_syst}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2023-07-13 paper/sec-protonPDFs.tex
Update sec-protonPDFs.tex

@@
 
+For the baseline results, we consider FASER$\nu$2 operative for the full duration
+of the HL-LHC data-taking period.
 %
-The baseline dataset is defined as follows.
+Both inclusive and charm-tagged structure functions enter the profiling,
+and outgoing lepton charge-separation is assumed.
 %
-We consider the FASER$\nu$2 experiment integrated over the full duration of the HL-LHC data-taking period,
-we account both for inclusive and charm production structure functions, we consider the scenario
-in which systematic errors can be neglected, and we allow for charge separation of the outgoing lepton.
+Fig.~\ref{fig:profiling_syst} displays the
+fractional uncertainties   (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
+for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
+in PDF4LHC21 compared to the results of its profiling with the FASER$\nu$2 projections.
 %
-This baseline result therefore represents the best-case scenario and quantifies the maximum impact that can be expected
-on the PDFs: we then assess to which extent variations of these input choices degrade the reach of the pseudo-data.
+For the latter, we consider two scenarios: first where the covariance matrix includes
+only statistical errors, and second with experimental systematic
+errors added in quadrature to the statistical ones.
+%
+Note that the residual shift in central values, which depends on the arbitrary fluctuations
+entering the pseudo-data generation, is not displayed.
 
-Fig.~\ref{fig:profiling_baseline} displays the fractional uncertainties at the 68\% confidence level
-for the up and down valence quarks, total quark singlet, strangeness, charm, and gluon PDFs
-in PDF4LHC21 compared to the results of its profiling with this baseline LHC neutrino dataset, namely
-FASER$\nu$2 with only statistical errors, both inclusive and charm structure functions,  and charge flavour
-separation.
-%
-The same style of PDF comparisons will be adopted through this section.
-%
-Results are shown at $Q^2 = 10^4 \, \textrm{GeV}^2$ and the residual shift in central values
-arising from the profiling is ignored.
-
-%
-The effect of including correlated systematic uncertainties is shown in 
-Fig.~\ref{fig:profiling_syst}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\paragraph{Dependence with the experiments.}
-%
-Same as Fig.~\ref{fig:profiling_baseline} comparing FASER$\nu$2 with AdvSND and with FASER$\nu$.
-
-\paragraph{Impact of systematic uncertainties.}
-
-\paragraph{Impact of charm production.}
 %
@@
 by virtue of the contribution of the charm production structure functions.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{Comparing the results shown in Fig.~\ref{fig:profiling_baseline} (red and blue), 
-to the results obtained without charm production structure functions (green).
+\caption{Same as Fig.~\ref{fig:profiling_syst}, now assessing the impact of FASER$\nu$2 structure functions
+once charm-tagged measurements are removed.
+%
+In both cases, the covariance matrix accounts for systematic uncertainties.
 }
@@
 \includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{Comparing the results shown in Fig.~\ref{fig:profiling_baseline} (red and blue), 
-to the results obtained without identifying the charge of the outgoing lepton (green).
+\caption{
+Same as Fig.~\ref{fig:profiling_syst}, now assessing the impact of that being unable to identify
+the charge of the outgoing lepton would have on the FASER$\nu$2 reach on the proton PDFs.
+%
+In both cases, the covariance matrix accounts for systematic uncertainties.
 }
@@
 
+{\bf add discussion of experiment sensitivity}
+
+%
+Same as Fig.~\ref{fig:profiling_baseline} comparing FASER$\nu$2 with AdvSND and with FASER$\nu$.
+
 \subsection{Impact on NNPDF4.0}

### 2023-07-13 paper/sec-protonPDFs.tex
sect 4

@@
 
+Inspection of Fig.~\ref{fig:profiling_syst} reveals that measurement of DIS structure
+functions at FASER$\nu$2 impose stringent constraints on the quark PDFs, while leaving
+the gluon PDF essentially unaffected.
+%
+As expected for a neutrino scattering experiment, its impact is most marked for
+those PDF combinations sensitive to quark flavour separation such as $u_V$, $d_V$, and
+$s^+$.
+%
+The reduction of PDF uncertainties is particularly significant for the total strangeness PDF,
+as  consequence of the inclusion of charm-tagged structure functions in the fit as we demonstrate below.
+%
+Crucially, one finds that for the assumptions on the systematic uncertainties
+discussed in Sect~\ref{sec:dis_pseudodata}, the PDF sensitivity is only marginally degraded
+as compared to the case in which systematic errors are neglected.
+%
+This result is consistent with Fig.~\ref{fig:percentage_uncertainties_overview}, showing
+how in most bins systematic and statistical errors are of similar magnitude.
+
 In the following we consider the stability of the results in Fig.~\ref{fig:profiling_baseline}
@@
 
-\paragraph{The role of lepton charge separation.}
 %
@@
 {\bf add discussion of experiment sensitivity}
-
 %
-Same as Fig.~\ref{fig:profiling_baseline} comparing FASER$\nu$2 with AdvSND and with FASER$\nu$.
+Same as Fig.~\ref{fig:profiling_syst} comparing FASER$\nu$2 with AdvSND and with FASER$\nu$.
 

### 2023-07-13 paper/sec-dis-pseudodata.tex
sect 2

@@
-\section{DIS pseudo-data generation}
+\section{DIS projections for LHC far-forward experiments}
 \label{sec:dis_pseudodata}
@@
 to generate projections for the kinematic coverage
-and experimental uncertainties associated to differential measurements
+and experimental uncertainties associated to  measurements
 of neutrino-nucleus scattering at the LHC far-forward experiments.
@@
 will be considered in the present study and indicate their
-key acceptance and performance parameters.
+main acceptance and performance parameters.
 %
@@
 of these detectors,
-we compute the foreseen event yields in bins of $x$, $Q^2$,
+we evaluate the foreseen event yields in bins of $x$, $Q^2$,
 and $E_\nu$ and therefore the associated statistical uncertainties.
 %
-Finally, we estimate how the dominant systematic
-uncertainties in each experiment translate into uncertainties in the predicted
-event rates and use this information to complete the calculation of the experimental
-covariance matrix.
+We also estimate how the systematic uncertainties in the measurement
+of final-state variables affects the experimental covariance matrix.
 
@@
 see~\cite{Candido:2023utz} and references therein,
-can be expressed in terms of 
+is expressed in terms of 
 independent structure functions $F_2^{\nu A}$, $xF_3^{\nu A}$
@@
 %
+Specifically, in this work we impose that $Q^2\ge 2$ GeV$^2$.
+%
 A similar expression holds for charm production~\cite{Faura:2020oom}, which requires
@@
 evaluate predictions for
-neutrino DIS structure functions, Eq.~(\ref{eq:sfs_pqcd}),
-and for differential cross-sections,
-Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}),
-in the kinematic range of relevance for LHC neutrinos.
+neutrino DIS structure functions
+and differential cross-sections,
+Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}),~(\ref{eq:antineutrino_DIS_xsec_FL}), and~(\ref{eq:sfs_pqcd}),
+in the kinematics covered by LHC neutrinos.
 
- Each neutrino structure function provides complementary sensitivity
+Different neutrino structure functions provide complementary sensitivity
  to the partonic flavour decompositions of nucleons.
@@
  \ee
- We note that even for isoscalar targets separate measurements
- for neutrinos and antineutrinos will not be equivalent, since in general neither $f_{s^-}$ nor
- $f_{c^-}$ are expected to vanish.
+ We note that, even for isoscalar targets, separate measurements
+ for neutrinos and antineutrinos will not be equivalent, since in general
+ the strange and charm sea asymmetries $f_{s^-}$ and
+ $f_{c^-}$ are not expected to vanish.
 
  In the projections presented in this work, when interpreting the LHC neutrino structure
- functions in terms of proton PDFs we will assume a isoscalar free-nucleon target and neglect
+ functions in terms of proton PDFs, we will assume a isoscalar free-nucleon target and neglect
  nuclear PDF modifications, along the lines of Eq.~(\ref{eq:neutrinoSFs_isoscalar}).
@@
  %
- We point out that accounting for nuclear target effects in a global proton
- PDF fit is straightforward by means of the procedure developed
+ We point out that accounting for nuclear modifications in a global proton
+ PDF fit is possible by means of the procedure developed
  in~\cite{Ball:2020xqw,Ball:2018twp}.
@@
  \eea
- with $xF_3$ being negligible in this region.
+ with $xF_3$ being negligible in this region below the $Z$-pole.
  %
@@
  neutrino and charged-lepton DIS in terms of sensitivity
- to the flavour PDF decomposition.
+ to the different flavour PDF decomposition.
 
@@
 \toprule
-Detector &  Rapidity &  Target & Lepton sign & Acceptance  & Performance \\
-\midrule
-\multirow{2}{*}{FASER$\nu$}  &   &   Tungsten  & \multirow{2}{*}{muons}      &     &         \\
-  &   &   (1.1 ton)  &       &     &         \\
-\midrule
-\multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &       &       &       \\
-  &   &  (0.83 ton)   &       &       &       \\
+Detector &  Rapidity &  Target & Charged Lepton ID & Acceptance  & Performance \\
 \midrule
 \midrule
-\multirow{3}{*}{FASER$\nu$2}  &   & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{only muons}     &   $E_\ell \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
+\multirow{2}{*}{FASER$\nu$}  &  \multirow{2}{*}{ $|\eta_\nu| \le 8.5$}  &   Tungsten  & \multirow{2}{*}{muons}      &   $E_\ell \gsim 100$ GeV   &    \multirow{2}{*}{n/a}       \\
+  &   &   (1.1 ton)  &       &  $\tan \theta_\ell \lsim 0.5$   &         \\
+\midrule
+\multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &   \multirow{2}{*}{n/a}    &  $E_\mu \gsim 20 $ GeV     &    \multirow{2}{*}{n/a}    \\
+  &    &  (0.83 ton)   &  &  $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$         &       \\
+\midrule
+\midrule
+\multirow{3}{*}{FASER$\nu$2}  & \multirow{3}{*}{ $|\eta_\nu| \le 8.5$}  & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{muons}     &   $E_\ell \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
   &   &  \multirow{2}{*}{(20 ton)}   &       &  $\tan \theta_\ell \lsim 0.5$   &   $\delta \theta_\ell \sim 1$ mrad      \\
@@
 \multirow{3}{*}{AdvSND~(far)}  &   \multirow{3}{*}{ $7.2 \le \eta_\nu \le 8.4$}  &
-\multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{only muons}    &  $E_\mu \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
+\multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{muons}    &  $E_\mu \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
   &   &   \multirow{2}{*}{(5 ton)}  &        & $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$     &           \\
@@
 \midrule
-\multirow{3}{*}{FLArE}  & \multirow{3}{*}{Liquid Argon}  &  & \multirow{3}{*}{ maybe muons}  &  $E_\mu \lsim 2$ GeV, $E_e \lsim 1$ TeV    &    $\delta E_e \sim 5\% $ \\
-&   &     &   & $\theta_\mu \lsim 0.4$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $ mrad   \\
+\multirow{3}{*}{FLArE}  & \multirow{3}{*}{tbd} & \multirow{2}{*}{Liquid Argon}  & \multirow{3}{*}{ maybe muons}  &  $E_\mu \lsim 2$ GeV, $E_e \lsim 1$ TeV    &    $\delta E_e \sim 5\% $ \\
+&   &  \multirow{2}{*}{(10 ton)}   &   & $\theta_\mu \lsim 0.4$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $ mrad   \\
  &   &     &  & reconstructed $E_h$  &    $\delta E_h \sim 30\% $   \\
@@
 \caption{\small For each of the far-forward LHC neutrino experiments considered
-  in this work, we indicate their rapidity coverage, target material, whether
+  in this work, we indicate their neutrino pseudo-rapidity coverage, target material, whether
   they can identify the sign of the outgoing charged lepton,
-  the detector acceptance for the charged lepton and hadronic final state,
+  the acceptance for the charged lepton and hadronic final state,
   and the expected reconstruction performance.
   %
-  We consider separately the acceptance and performance for electron and muon
-  neutrinos.
-  %
-  Tau neutrinos have much lower production rates and are not considered in this study.
+  We consider separately acceptance and performance for electron and muon
+  neutrinos, while tau neutrinos have lower production rates and are not considered in this study.
   %
@@
   For the projections in this work we assume that FASER$\nu$ and SND@LHC acquire data
-  for the full Run III period, while FASER$nu$2, AdvSND, and FLArE take data
+  for the full Run III period, while FASER$\nu$2, AdvSND, and FLArE take data
   for the complete HL-LHC period.
+  %
+  An estimate of the expected 
+  systematic uncertainties is not available for FASER$\nu$ and SND@LHC, experiments
+  which nevertheless are limited by statistics.
   \label{tab:FPF_experiments}

### 2023-07-13 paper/sec-dis-pseudodata.tex
sect 2 updated

@@
 
- As we discuss below, the calculation of differential neutrino scattering event rates
- at the LHC far-forward detectors requires two main ingredients: the energy
+ The calculation of differential neutrino scattering event rates
+ at the LHC far-forward detectors involves two main ingredients: the energy
  and flavour dependence of the incoming neutrino flux crossing
@@
  %
- In this section, we summarise the main features of each of the ongoing and future
+ In this section, we summarise the main features of each of the existing and future
  far-forward detectors considered in this study, in particular concerning
- their acceptance, geometry, and neutrino detection method.
+ their acceptance, performance, and detection method.
  %
- We also indicate the expected performance of the three FPF detectors
- and how this translates into the dominant experimental systematic
- uncertainties.
+ We focus on  muon
+ neutrino scattering, which benefits from the highest rates and is less
+ affected by uncertainties affecting $D$-meson production.
+
+ The kinematics of a charged-current neutrino DIS event $(x,Q^2, E_\nu)$,
+ or alternatively $(x,Q^2, y)$, are uniquely specified by the measurement of three independent
+ final-state variables,
+ such as $\lp E_\ell,\theta_\ell, W^2\rp$ or $\lp E_\ell,\theta_\ell, E_h \rp$,
+ with $E_\ell$ and $\theta_\ell$ being the energy and polar angle of the outgoing
+ charged lepton and $E_h$ the total energy of the hadronic final state.
  %
- Since for the projection studies considered in this work we focus on muon
- neutrino scattering, we will focus the subsequent discussion on the detection
- performance of this neutrino flavour.
+ Most neutrino detectors can only access $E_h$, given that $W^2$ requires
+ fully reconstructing this final state.
+ %
+ A measurement of  $\lp E_\ell,\theta_\ell, E_h \rp$ then fixed the DIS kinematics as:
+ \bea
+ E_\nu &=& E_h + E_\ell \, , \nonumber \\
+ Q^2 &=& 4 ( E_h + E_\ell) E_\ell \sin^2 \lp \theta_\ell/2\rp \, ,\\
+ x&=& \frac{4 ( E_h + E_\ell) E_\ell \sin^2 \lp \theta_\ell/2\rp}{2m_N E_h} \, .\nonumber
+ \eea
+ These relations also indicate how systematic uncertainties affecting the measurement
+ of $\lp E_\ell,\theta_\ell, E_h \rp$ translate into uncertainties in the
+ reconstructed values of  $(x,Q^2, E_\nu)$, which in turn modify the expected
+ event rates in a given bin.
 
- Table~\ref{tab:FPF_experiments} indicates
- the rapidity coverage, target material,
- muon neutrino acceptance, and the identification and reconstruction performance
+ Table~\ref{tab:FPF_experiments} indicates,
 for each of the far-forward LHC neutrino experiments considered
- in this work.
- %
- More details of the information listed in this table is provided
- in the following.
-
-  %-----------------------------------------------------------------
-\begin{table}[t]
-  \centering
-  \small
-  \renewcommand{\arraystretch}{1.50}
-\begin{tabularx}{\textwidth}{Xccccc}
-\toprule
-Detector &  Rapidity &  Target & Charged Lepton ID & Acceptance  & Performance \\
-\midrule
-\midrule
-\multirow{2}{*}{FASER$\nu$}  &  \multirow{2}{*}{ $|\eta_\nu| \le 8.5$}  &   Tungsten  & \multirow{2}{*}{muons}      &   $E_\ell \gsim 100$ GeV   &    \multirow{2}{*}{n/a}       \\
-  &   &   (1.1 ton)  &       &  $\tan \theta_\ell \lsim 0.5$   &         \\
-\midrule
-\multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &   \multirow{2}{*}{n/a}    &  $E_\mu \gsim 20 $ GeV     &    \multirow{2}{*}{n/a}    \\
-  &    &  (0.83 ton)   &  &  $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$         &       \\
-\midrule
-\midrule
-\multirow{3}{*}{FASER$\nu$2}  & \multirow{3}{*}{ $|\eta_\nu| \le 8.5$}  & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{muons}     &   $E_\ell \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
-  &   &  \multirow{2}{*}{(20 ton)}   &       &  $\tan \theta_\ell \lsim 0.5$   &   $\delta \theta_\ell \sim 1$ mrad      \\
-  &   &     &       &  reconstructed $E_h$ \& charm ID   &  $\delta E_h \sim 30\%$        \\
-\midrule
-\multirow{3}{*}{AdvSND~(far)}  &   \multirow{3}{*}{ $7.2 \le \eta_\nu \le 8.4$}  &
-\multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{muons}    &  $E_\mu \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
-  &   &   \multirow{2}{*}{(5 ton)}  &        & $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$     &           \\
-  &   &     &       &  reconstructed $E_h$   &           \\
-\midrule
-\multirow{3}{*}{FLArE}  & \multirow{3}{*}{tbd} & \multirow{2}{*}{Liquid Argon}  & \multirow{3}{*}{ maybe muons}  &  $E_\mu \lsim 2$ GeV, $E_e \lsim 1$ TeV    &    $\delta E_e \sim 5\% $ \\
-&   &  \multirow{2}{*}{(10 ton)}   &   & $\theta_\mu \lsim 0.4$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $ mrad   \\
- &   &     &  & reconstructed $E_h$  &    $\delta E_h \sim 30\% $   \\
-  \bottomrule
-\end{tabularx}
-\vspace{0.2cm}
-\caption{\small For each of the far-forward LHC neutrino experiments considered
-  in this work, we indicate their neutrino pseudo-rapidity coverage, target material, whether
+  in this work,  their neutrino pseudo-rapidity coverage, target material, whether
   they can identify the sign of the outgoing charged lepton,
@@
   We consider separately acceptance and performance for electron and muon
-  neutrinos, while tau neutrinos have lower production rates and are not considered in this study.
+  neutrinos, while tau neutrinos have lower production rates and are neglected in this study.
   %
-  See the description of each experiment in the text for more details.
-  %
-  For the projections in this work we assume that FASER$\nu$ and SND@LHC acquire data
+  For these projections we assume that FASER$\nu$ and SND@LHC acquire data
   for the full Run III period, while FASER$\nu$2, AdvSND, and FLArE take data
@@
   systematic uncertainties is not available for FASER$\nu$ and SND@LHC, experiments
-  which nevertheless are limited by statistics.
-  \label{tab:FPF_experiments}
-}
-\end{table}
-%-----------------------------------------------------------------
+  which are nevertheless limited by statistics.
+  %
+  In the following we provide more details about the information collected in
+  Table~\ref{tab:FPF_experiments}.
+
+%---------------------------------------------------
+  \input{tables/detectors.tex}
+%---------------------------------------------------
 
@@
 %
-The ForwArd Search ExpeRiment (FASER) detector and its companion FASER$\nu$
+The ForwArd Search ExpeRiment (FASER) detector and its companion FASER$\nu$~\cite{FASER:2019aik,FASER:2019dxq}
 are located at the TI12 tunnel of the CERN accelerator complex.
@@
 Both detectors are aligned
-with the collision axis LOS  and have been taking data since the begin of Run III.
+with the collision axis line-of-sight (LOS)
+and have been acquiring data since the begin of Run III.
 %
@@
 %
-The FASER/FASER$\nu$ apparatus is immersed in a magnetic field which enables charged lepton
-identification, provided by two 1 m-long dipole magnets with $B=0.57$ T
+The FASER apparatus is immersed in a magnetic field  providing charged lepton
+identification thanks to two 1 m-long dipole magnets with $B=0.57$ T
 and another 1.5 m-long magnet in front of the spectrometer. 
@@
 %
-A 20-ton neutrino experiment located on the line of sight (LOS)
-of the LHC neutrino beam.
+A proposed 20-ton neutrino experiment located on the LOS
+of the LHC neutrino beam to be installed in the FPF cavern.
 %
@@
  %
- The use of LAr as target is particularly beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimeter spatial resolution in all three dimensions.
+ The use of LAr as target is beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimeter spatial resolution in all three dimensions.
  %
@@
  With an expected fiducial (active) mass of 10 tons (30 tons), FLArE will
- detect muon neutrinos with energies  $E_\mu\lsim 1.5~\rm{TeV}$ and
- scattering angles up to 0.4 mrad.
+ detect final-state electrons with energies $E_{e}\lsim 1~\rm{TeV}$ and
+ scattering angles up to 0.5 mrad, while detecting final-state muons
+ is restricted to $E_{e}\lsim 2~\rm{GeV}$  and $\theta_\mu \lsim 0.4$.
  %
@@
  In terms of performance, the targets
- are $\delta E_\mu \sim$30\% of muon energy resolution and
- $\delta \theta_\mu \sim 5$ mrad of muon angular  resolution.
+ are $\delta E_\mu \sim$5\% of electron energy resolution,
+ $\delta \theta_e \sim 15$ mrad of electron angular  resolution,
+ and $\delta E_h \sim 30$\% for the hadronic energy.
 
@@
 %
-The goal is to quantify the number of reconstructed charged-current neutrino interaction
+The goal is to evaluate the number of reconstructed charged-current neutrino interaction
 events taking place in the fiducial volume of the detector in bins of Bjorken-$x$,
@@
 
-In this calculation we assume the neutrino fluxes provided by the calculation
-of~\cite{Kling:2021gos} and neglect the associated uncertainties.
+In this calculation, we assume the central values of the neutrino fluxes provided by the calculation
+of~\cite{Kling:2021gos}.
 %
@@
 %
-We consider the scattering of muon neutrinos, characterised by the highest rates, and in some cases
-we present results also for electron neutrinos.
+We consider only the scattering of muon neutrinos, characterised by the highest rates.
 %
-We have verified that the differential event yield calculation
+We verify that the differential event yield calculation
 implemented in Eq.~(\ref{eq:event_yields}), when extrapolated to a single bin
@@
 is consistent with the fiducial interaction rates presented in~\cite{Feng:2022inv}.
-%
+
 The triple integral in  Eq.~(\ref{eq:event_yields}) is evaluated numerically by means
@@
 and where $N_{\rm mc}$ is chosen to be large enough such that residual Monte Carlo integration
-uncertainties are negligible.
+uncertainties are negligible for all the bins considered.
 
-Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the five detectors considered
-  in the present analysis, separated into electron neutrinos and antineutrinos
+Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the five detectors
+considered, separated into electron neutrinos and antineutrinos
   and muon neutrinos and antineutrinos.
@@
   These event yields are computed from Eq.~(\ref{eq:event_yields}) with the only
-  restriction that the momentum transfer and the final-state invariant mass should be restricted
+  requirement that the momentum transfer and the final-state invariant mass are restricted
   to the DIS region,
@@
   \label{eq:DISconditions}
-Q^2 \ge 2~{\rm GeV}^2\quad{\rm and}\quad  W^2 \ge 12.5~{\rm GeV}^2 \, .
+Q^2 \ge 2~{\rm GeV}^2\quad{\rm and}\quad  W^2 \ge 4~{\rm GeV}^2 \, .
 \ee
   %
-  As discussed above, for FASER$\nu$ and SND@LHC we assume the integrated luminosity to
-  be that of Run III while for the FPF experiments we assume the full HL-LHC
-  luminosity (3 ab$^{-1}$).
-  %
    The numbers in parenthesis indicate the event rates corresponding to charm
-  production for those experiments with heavy flavour tagging capabilities.
+  production, for those experiments with heavy flavour tagging capabilities.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%-----------------------------------------------------------------
-\begin{table}[t]
-  \centering
-  \small
-  \renewcommand{\arraystretch}{1.60}
-\begin{tabularx}{\textwidth}{X|c|c|c|c|c|c}
-\toprule
-Detector & $\quad$ $N_{\nu_e}$ $\quad$ &$\quad$ $N_{\bar{\nu}_e}$$\quad$   &   $N_{\nu_e} + N_{\bar{\nu}_e}$ &
-$\quad$$N_{\nu_\mu}$ $\quad$ & $\quad$ $N_{\bar{\nu}_\mu}$ $\quad$  &   $N_{\nu_\mu} + N_{\bar{\nu}_\mu}$ \\
-\midrule
-FASER$\nu$  &    &    &   &   &    &    \\
-SND@LHC  &    &    &   &   &    &    \\
-\midrule
-FASER$\nu$2  &    &    &   &   &    &    \\
-AdvSND~(far)  &    &    &   &   &    &    \\
-FLArE &    &    &   &   &    &    \\
-  \bottomrule
-\end{tabularx}
-\vspace{0.2cm}
-\caption{\small The predicted integrated event yields for the five detectors considered
-  in the present analysis, separated into electron neutrinos and antineutrinos
-  and muon neutrinos and antineutrinos.
-  %
-  These event yields are computed from Eq.~(\ref{eq:event_yields}) with the only
-  restriction that the momentum transfer and the final-state invariant mass be restricted
-  to the DIS region, $Q^2 \ge 2$ GeV$^2$ and $W^2 \ge 12.5$ GeV$^2$.
-  %
-  The numbers in parenthesis indicate the event rates corresponding to charm
-  production.
-  \label{tab:integrated_rates}
-}
-\end{table}
-%-----------------------------------------------------------------
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%----------------------------------------------------
+\input{tables/integrated_yields.tex}
+%----------------------------------------------------
 
@@
   \ee
-  with the charm production cross-sections being discussed in~\cite{Faura:2020oom}
+  with the charm production cross-sections discussed in~\cite{Faura:2020oom}
   and references therein.
@@
  event yields per bin,  Eq.~(\ref{eq:event_yields}),
-  for muon neutrinos detected at FASER$\nu$2.
+  for muon neutrinos detected at FASER$\nu$2 restricted
+  to the DIS region defined by Eq.~(\ref{eq:DISconditions}).
   %
-  We present results binned in $x$ and $Q^2$ and integrated over the neutrino energies.
+  We present results binned in $x$ and $Q^2$ and integrated over all available neutrino energies.
   %
@@
   %
-  Adding up all bin entries results into $N_{\rm ev}(\nu_\mu)\sim 3\times 10^5 $ reconstructed muon
-  neutrinos as indicated in Table~\ref{tab:integrated_rates}.
+  Adding up all bin entries results into the $N_{\nu_\mu}$ value
+  for reconstructed muon
+  neutrinos listed in
+  Table~\ref{tab:integrated_rates}.
   %
-  Kinematic cuts are such that the DIS conditions in Eq.~(\ref{eq:DISconditions}) are satisfied.
+  Only bins with at least 30 events are retained, to ensure the validity of Gaussian
+  statistics.
   %
-  Only bins with at least 30 events are retained.
-  %
-  One can observe the large event rates for most of the region in $\lp x,Q^2\rp$ covered,
-  which result into very competitive statistical uncertainties.
-  %
-  From Fig.~\ref{fig:fasernu2_muon} we see that the kinematic coverage of FASER$\nu$2 is
-  $x_{\rm min}\sim 10^{-3}$ at small-$x$ and $Q^2_{\rm max}\sim 10^4$ at large-$Q^2$, which represent an extension
-  of around one order of magnitude in both directions as compared to available
-  DIS neutrino data.
+  One observes large event rates for most of the region in $\lp x,Q^2\rp$ covered,
+  leading to typical statistical uncertainties at the 1\% level or smaller.
 
 %-----------------------------------------------------------------------
-\begin{figure}[!ht]
+\begin{figure}[t]
     \centering
-\includegraphics[width=0.9\textwidth]{plots/Nevent_FASERv2_14.pdf}
-\caption{\small The event yields per bin $ N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}),
-  for muon neutrinos at FASER$\nu$2.
+\includegraphics[width=0.8\textwidth]{plots/Nevent_FASERv2_14.pdf}
+\caption{\small The event yields per bin $N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}),
+  for muon neutrinos at the FASER$\nu$2 detector, restricted
+  to the DIS region defined by Eq.~(\ref{eq:DISconditions}).
   %
-  We present results binned in $x$ and $Q^2$ and integrating over the neutrino energies.
+  We present results binned in $x$ and $Q^2$ integrated over neutrino energies.
   %
-  The red dot indicates the weighted center of each bin.
+  The red dots indicate the weighted bin center.
   %
-  Adding up all bin entries results into $N_{\rm ev}(\nu_\mu)\sim 3\times 10^5 $ reconstructed muon
-  neutrinos. }
+  Adding up all the bins in this plot results into the $N_{\nu_\mu}$ value listed in
+Table~\ref{tab:integrated_rates}.}
     \label{fig:fasernu2_muon}
@@
 %-----------------------------------------------------------------------
+
+Fig.~\ref{fig:fasernu2_muon} indicates
+how the kinematic coverage of FASER$\nu$2 reaches
+$x_{\rm min}\sim 3\times 10^{-3}$ at small-$x$ and $Q^2_{\rm max}\sim 2\times 10^3$
+at large-$Q^2$, representing an extension
+of around one order of magnitude in both directions as compared to available
+DIS neutrino data on nuclear targets.
+%
+Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF} compares
+the kinematic coverage of FASER$\nu$2 with that of electron-ion collisions
+at the upcoming EIC~\cite{Khalek:2021ulf,AbdulKhalek:2021gbh}
+and to other available hard-scattering datasets involving
+nuclear targets or projectiles.
+%
+Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
+fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
+production in proton-lead collisions at the LHC entering the  nNNPDF3.0
+determination~\cite{AbdulKhalek:2022fyi}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+    \centering
+    \includegraphics[width = 0.8\textwidth]{plots/Kin_nNNPDF30_EIC_FPF.pdf}
+    \caption{The kinematic coverage of FASER$\nu$2 in the $(x,Q^2)$ plane,
+      same as  Fig.~\ref{fig:fasernu2_muon},
+      compared to that of electron-ion collisions
+      at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
+      as well as to the coverage of other available hard-scattering datasets involving
+      nuclear targets or projectiles.
+      %
+      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
+      fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
+      production in proton-lead collisions at the LHC.
+      }
+    \label{fig:Kin_nNNPDF30_EIC_FPF}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Statistical and systematic uncertainties}
+\label{subsec:uncertainties}
+
+The event yields displayed in Fig.~\ref{fig:fasernu2_muon} determine the associated
+statistical uncertainty in each bin
+\be
+\label{eq:statistical_uncertainties}
+\delta_{\rm stat}  N_{\rm ev}^{(i)} = \sqrt{N_{\rm ev}^{(i)}} \, ,
+\ee
+such that the fractional statistical uncertainty per bin is $1/\sqrt{N_{\rm ev}^{(i)}}$.
+%
+Since here we discard bins with less than 30 events, this statistical uncertainty
+ranges between $\sim 1\%$ and $\sim 18\%$ for muon neutrinos in FASER$\nu$2 depending on the values of
+$x$ and $Q^2$ associated to this bin.
+%
+These statistical uncertainties are displayed in the left panel
+of Fig.~\ref{fig:error_plot_FASERv2_14}, which corresponds
+to the same event yields as in
+Fig.~\ref{fig:fasernu2_muon}
+now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$.
+%
+The error bar in the $y$-direction indicates the statistical uncertainties, while
+that in the $x$ direction corresponds to the width of the $x$-bins.
+{\color{red}[Suggestion (TM): let's refer to horizontal and vertical directions, since $x$ and $y$ are variables as well, not only directions]}
 
@@
 
-The event yields displayed in Fig.~\ref{fig:fasernu2_muon} determine the associated
-statistical uncertainty in each bin
-\be
-\label{eq:statistical_uncertainties}
-\delta_{\rm stat}  N_{\rm ev}^{(i)} = \sqrt{N_{\rm ev}^{(i)}} \, ,
-\ee
-such that the fractional statistical uncertainty per bin is $1/\sqrt{N_{\rm ev}^{(i)}}$.
-%
-Since here we discard bins with less than 30 events, this statistical uncertainty
-ranges between $\sim 1\%$ and $\sim 18\%$ for muon neutrinos in FASER$\nu$2 depending on the values of
-$x$ and $Q^2$ associated to this bin.
-%
-These statistical uncertainties are displayed in the left panel
-of Fig.~\ref{fig:error_plot_FASERv2_14}, which corresponds
-to the same event yields as in
-Fig.~\ref{fig:fasernu2_muon}
-now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$.
-%
-The error bar in the $y$-direction indicates the statistical uncertainties, while
-that in the $x$ direction corresponds to the width of the $x$-bins.
-{\color{red}[Suggestion (TM): let's refer to horizontal and vertical directions, since $x$ and $y$ are variables as well, not only directions]}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Finally, we would like to compare the kinematic reach
-of the LHC neutrino measurements with respect to that of other experiments.
-%
-Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF} displays
-the kinematic coverage of the FASER$\nu$2 experiment in the $(x,Q^2)$ plane,
-same as  Fig.~\ref{fig:error_plot_FASERv2_14} now removing bins
-containing less than 30 reconstructed events.
-%
-It is compared to that of electron-ion collisions
-at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
-as well as to the kinematic coverage of other available hard-scattering datasets involving
-nuclear targets or projectiles.
-%
-Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
-fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
-production in proton-lead collisions at the LHC.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h]
-    \centering
-    \includegraphics[width = 0.8\textwidth]{plots/Kin_nNNPDF30_EIC_FPF.pdf}
-    \caption{The kinematic coverage of the FASER$\nu$2 experiment in the $(x,Q^2)$ plane,
-      same as  Fig.~\ref{fig:error_plot_FASERv2_14} now removing bins
-      containing less than 30 reconstructed events.
-      %
-      It is compared to that of electron-ion collisions
-      at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
-      as well as to the kinematic coverage of other available hard-scattering datasets involving
-      nuclear targets or projectiles.
-      %
-      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
-      fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
-      production in proton-lead collisions at the LHC.
-      }
-    \label{fig:Kin_nNNPDF30_EIC_FPF}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Systematic uncertainties}
-\label{sec:systematic_uncertainties}
 

### 2023-07-13 paper/tables/detectors.tex
sect 2 updated

  %-----------------------------------------------------------------
\begin{table}[t]
  \centering
  \small
  \renewcommand{\arraystretch}{1.50}
\begin{tabularx}{\textwidth}{Xccccc}
\toprule
Detector &  Rapidity &  Target & Charged Lepton ID & Acceptance  & Performance \\
\midrule
\midrule
\multirow{2}{*}{FASER$\nu$}  &  \multirow{2}{*}{ $|\eta_\nu| \le 8.5$}  &   Tungsten  & \multirow{2}{*}{muons}      &   $E_\ell \gsim 100$ GeV   &    \multirow{2}{*}{n/a}       \\
  &   &   (1.1 ton)  &       &  $\tan \theta_\ell \lsim 0.5$   &         \\
\midrule
\multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &   \multirow{2}{*}{n/a}    &  $E_\mu \gsim 20 $ GeV     &    \multirow{2}{*}{n/a}    \\
  &    &  (0.83 ton)   &  &  $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$         &       \\
\midrule
\midrule
\multirow{3}{*}{FASER$\nu$2}  & \multirow{3}{*}{ $|\eta_\nu| \le 8.5$}  & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{muons}     &   $E_\ell \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
  &   &  \multirow{2}{*}{(20 ton)}   &       &  $\tan \theta_\ell \lsim 0.5$   &   $\delta \theta_\ell \sim 1$ mrad      \\
  &   &     &       &  reconstructed $E_h$ \& charm ID   &  $\delta E_h \sim 30\%$        \\
\midrule
\multirow{3}{*}{AdvSND~(far)}  &   \multirow{3}{*}{ $7.2 \le \eta_\nu \le 8.4$}  &
\multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{muons}    &  $E_\mu \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
  &   &   \multirow{2}{*}{(5 ton)}  &        & $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$     &           \\
  &   &     &       &  reconstructed $E_h$   &           \\
\midrule
\multirow{3}{*}{FLArE}  & \multirow{3}{*}{tbd} & \multirow{2}{*}{Liquid Argon}  & \multirow{3}{*}{ maybe muons}  &  $E_\mu \lsim 2$ GeV, $E_e \lsim 1$ TeV    &    $\delta E_e \sim 5\% $ \\
&   &  \multirow{2}{*}{(10 ton)}   &   & $\theta_\mu \lsim 0.4$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $ mrad   \\
 &   &     &  & reconstructed $E_h$  &    $\delta E_h \sim 30\% $   \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small For each of the far-forward LHC neutrino experiments considered
  in this work, we indicate their neutrino pseudo-rapidity coverage, target material, whether
  they can identify the sign of the outgoing charged lepton,
  the acceptance for the charged lepton and hadronic final state,
  and the expected reconstruction performance.
  %
  We consider separately acceptance and performance for electron and muon
  neutrinos, while tau neutrinos have lower production rates and are not considered in this study.
  %
  See the description of each experiment in the text for more details.
  %
  For the projections in this work we assume that FASER$\nu$ and SND@LHC acquire data
  for the full Run III period, while FASER$\nu$2, AdvSND, and FLArE take data
  for the complete HL-LHC period.
  %
  An estimate of the expected 
  systematic uncertainties is not available for FASER$\nu$ and SND@LHC, experiments
  which nevertheless are limited by statistics.
  \label{tab:FPF_experiments}
}
\end{table}
%-----------------------------------------------------------------

### 2023-07-13 paper/tables/integrated_yields.tex
sect 2 updated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-----------------------------------------------------------------
\begin{table}[t]
  \centering
  \small
  \renewcommand{\arraystretch}{1.70}
\begin{tabularx}{\textwidth}{X|c|c|c|c|c|c}
\toprule
Detector & $\quad$ $N_{\nu_e}$ $\quad$ &$\quad$ $N_{\bar{\nu}_e}$$\quad$   &   $N_{\nu_e} + N_{\bar{\nu}_e}$ &
$\quad$$N_{\nu_\mu}$ $\quad$ & $\quad$ $N_{\bar{\nu}_\mu}$ $\quad$  &   $N_{\nu_\mu} + N_{\bar{\nu}_\mu}$ \\
\midrule
\midrule
FASER$\nu$  &    &    &   &   &    &    \\
SND@LHC  &    &    &   &   &    &    \\
\midrule
\midrule
FASER$\nu$2  &    &    &   &   &    &    \\
AdvSND~(far)  &    &    &   &   &    &    \\
FLArE &    &    &   &   &    &    \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small Integrated event yields for the five detectors considered,
  separated into electron neutrinos and antineutrinos,
  muon neutrinos and antineutrinos, and their sum.
  %
  These event yields are computed from Eq.~(\ref{eq:event_yields})
  imposing DIS kinematics, $Q^2 \ge 2$ GeV$^2$ and $W^2 \ge 4$ GeV$^2$.
  %
  Whenever available, the
  numbers in parenthesis indicate the event rates corresponding to charm
  production.
  \label{tab:integrated_rates}
}
\end{table}
%-----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-07-13 paper/sec-analysis.tex
sect 2

--- 2023-07-04 paper/sec-analysis.tex
@@
 \label{sec:settings}
-
-In this section, we describe the analysis settings adopted to quantify
-the impact of LHC neutrino measurements on the proton and nuclear PDFs.
-%
-First of all, we discuss the calculation of inclusive and charm structure functions
-and their interpolation in terms of fast grids. 
-%
-Second, we review the Hessian profiling framework and how it is applied
-in this work to proton and nuclear PDFs.
-%
-Third, we indicate the implementation of the LHC neutrino pseudo-data in the
-NNPDF framework and the settings of the subsequent global PDF analysis.
-
-\subsection{Structure function calculation}
-\label{subsec:dis_sf_calculations}
-
-The procedure described in Sect.~\ref{sec:dis_pseudodata} returns
-$N_{\rm bin}$ bins of LHC neutrino pseudo-data $\mathcal{O}_i^{{\rm (exp)}}$, Eq.~(\ref{eq:pseudo_data}), covering the $(x,Q^2,E_\nu)$ kinematic region accessible by the experiment,
-together with the associated statistical and systematic uncertainties.
-%
-The calculation of this pseudo-data relies on the corresponding set of
-theoretical predictions for the same observables $\mathcal{O}_i^{{\rm (th)}}$,
-Eq.~(\ref{eq:theory_dis_projections}).
-%
-Here we evaluate inclusive and charm DIS structure functions with the
-{\sc\small YADISM}~\cite{yadism,Candido:2023utz} program
-interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss, christopher_schwan_2023_7995675}
-to return a fast interpolation grid admitting a generic PDF input.
-%
-DGLAP evolution effects between the scale $Q_0$ at which PDFs are evaluated
-and the data scale $Q$ are provided by {\sc\small EKO}~\cite{Candido:2022tld}.
-
-The resulting {\sc\small PineAPPL} grids provide a fast evaluation
-of Eq.~(\ref{eq:theory_dis_projections}) for an arbitrary choice of the
-input PDFs at the initial scale $Q_0$, with the latter accessed via their
-{\sc\small LHAPDF} interface~\cite{Buckley:2014ana}.
-%
-Whenever pseudo-data is generated, it is crucial to adopt common inputs with
-the subsequent PDF analysis.
-%
-For instance, if one aims to include the LHC neutrino data into the NNPDF4.0
-NNLO determination, $\mathcal{O}_i^{{\rm (th)}}$ must be evaluated also at NNLO
-and also using
-NNPDF4.0 as input for consistency, else artificial tensions between theory
-and data would be introduced during the fit biasing the results.
-
-By means of this theoretical pipeline, predictions for
-DIS inclusive structure functions on an isoscalar target $N$ are computed
-using
-\be
-\label{eq:neutrino_DIS_xsec}
-\frac{d^2\sigma^{\nu N}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\nu N}_2(x,Q^2) - y^2F^{\nu N}_L(x,Q^2) +Y_- xF^{\nu N}_3(x,Q^2)\rc  \, ,
-\ee
-with an analogous formula for antineutrino scattering with the sign of $xF_3$ flipped.
-%
-A {\sc\small PineAPPL} interpolation grid for
-Eq.~(\ref{eq:neutrino_DIS_xsec}) is evaluated at the $(x,Q^2,E_\nu)$ bins
-for which pseudo-data is generated using DGLAP evolution and coefficient
-functions at $\mathcal{O}\lp \alpha_s^2\rp$ and accounting for target mass effects.
-%
-No higher-twists corrections to the structure functions are included, since we cut
-data with $W^2 \ge 12.5$ GeV in order to suppress them.
-%
-Deviations from isoscalarity and nuclear modifications with respect
-to a free isoscalar target are accounted for at the input PDF level,
-leaving the grid entering the evaluation of Eq.~(\ref{eq:neutrino_DIS_xsec}) unchanged.
-%
-No heavy quark mass effects are considered for at the level of these inclusive structure functions.
-
-Concerning charm structure functions, for experiments with charm tagging
-capabilities theoretical predictions are evaluated for
-\be
-\label{eq:neutrino_DIS_xsec}
-\frac{d^2\sigma^{\nu N}_c(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F_{2,c}^{\nu N}(x,Q^2) - y^2F^{\nu N}_{L,c}(x,Q^2) +Y_- xF^{\nu N}_{3,c}(x,Q^2)\rc  \, ,
-\ee
-with the DIS charm structure functions evaluated in the FONLL general-mass variable-flavour-number
-scheme~\cite{Forte:2010ta,Ball:2011mu,Faura:2020oom} in order to account for charm mass effects.
-%
-Eq.~(\ref{eq:neutrino_DIS_xsec}) is computed with $\mathcal{O}\lp \alpha_s^2\rp$ massless
-coefficient functions and $\mathcal{O}\lp \alpha_s\rp$ massive ones, given
-that the $\mathcal{O}\lp \alpha_s^2\rp$ massive calculation~\cite{Gao:2017kkx} is not publicly available.
-%
-Nevertheless, the $\mathcal{O}\lp \alpha_s\rp$ massive coefficient functions
-encapsulate the dominant charm mass dependence of the double differential
-cross-section.
-%
-We assume 100\% efficiency in charm tagging and do not impose acceptance cuts on the charm
-quark or $D$-meson kinematics (the only acceptance requirements are applied to the final-state
-charged lepton, as indicated in  Table~\ref{tab:FPF_experiments}).
-
-We note that experiments without charm-tagging capabilities can still identify charm production
-events by means of the dimuon final state,
-\be
-\nu + N \to \mu^+ + c~(\to D) + X \to \mu^+ + \mu^- +X \, ,
-\ee
-by profiting from the semileptonic decays of the $D$-meson leading
-to the characteristic signature of two opposite-sign muons.
-%
-In this case, the  differential charm production cross-section Eq.~(\ref{eq:neutrino_DIS_xsec})
-must be accompanied by the corresponding branching ratio
-\be
-\frac{d^2\sigma^{\nu N}_c(x,Q^2,y)}{dxdy}\mathcal{B}\lp c \to D \to \mu + X\rp \, ,
-\ee
-which given that $\mathcal{B}\sim 10\%$ suppresses the reconstructed charm
-production event yields by around an order of magnitude.
-%
-For experiments reconstructing the dimuon final state,
-we also apply the muon acceptance criteria to both muons.
-
-\subsection{Hessian profiling}
-\label{sec:profiling}
-
-In this work we consider two complementary approaches in order to assess the
-impact of LHC neutrino data on the proton and nuclear PDFs.
-%
-On the one hand, the Hessian profiling of a prior proton or
-nuclear PDF set, which here are taken to be PDF4LHC21~\cite{PDF4LHCWorkingGroup:2022cjn} and
-EPPS21~\cite{Eskola:2021nhw} respectively.
-%
-On the other hand, the inclusion of the LHC neutrino structure functions
-on the NNPDF global analysis framework~\cite{NNPDF:2021uiq,NNPDF:2021njg}.
-%
-Here we summarise the details of the Hessian profiling procedure and
-outline how it is applied in our work.
-
-The profiling method applied to Hessian PDF fits is described in~\cite{Paukkunen:2014zia, Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre} and is based
-on minimizing a goodness-of-fit error function defined as
-\begin{equation}
-\chi^2 = 
-\sum_{i=1}^{N_{\textrm{bin}}} 
-\frac{\left(  \mathcal{O}_i^{\rm (exp)}
-            + \Gamma_i^{\alpha,\textrm{pd}}
-              b_\alpha^{\textrm{(pd)}}
-            - \mathcal{O}_i^{\textrm{th}}
-            - \Gamma_i^{\beta,\textrm{th}}
-              b_\beta^{(\textrm{th})}
-     \right)^2
-     }{\delta_{{\rm stat},i}^2}
-+ \sum_\alpha \lp b_\alpha^{(\textrm{pd})}\rp^2
-+ \sum_\beta  \lp b_\beta^{\textrm{(th)}}\rp ^2 \, .
-\label{eq:profilingchi2}
-\end{equation}
-The pseudodata 
-$\mathcal{O}_i^{\rm (exp)}$ 
-is obtained from the central theoretical prediction 
-$\mathcal{O}_i^{(\textrm{th})}$
-for each bin $i$ out of $N_{\textrm{bin}}$ by fluctuating
-it within its uncertainties, following either
-Eq.~(\ref{eq:pseudo_data}), when accounting for the correlations
-between systematic uncertainties, or Eq.~(\ref{eq:pseudo_data_v2}),
-in the case in which errors are added in quadrature.
-
-The correlated uncertainties for the pseudodata and for the theoretical prediction 
-are contained in the nuisance parameter vectors $b^{(\textrm{pd})}$ and $b^{(\textrm{th})}$, respectively, and the total uncorrelated uncertainties are denoted by $\delta_{{\rm stat},i}$.
-%
-The effect of the nuisance parameters
-on the observables $\mathcal{O}_i^{\rm (exp)}$ and $\mathcal{O}_i^{\rm (th)}$
-is described by the matrices $\Gamma_i^{\textrm{pd}}$ and $\Gamma_i^{\textrm{th}}$.
-%
-The indices $\alpha$ and $\beta$ then run over the uncertainty nuisance parameters for the pseudodata and the theoretical prediction, respectively.
-%
-The nuisance parameter values $b_\beta^{\textrm{(th,min)}}$ that minimize Eq.~\eqref{eq:profilingchi2} give the central PDFs $f'_0$ optimized to the profiled dataset in the form
-\begin{equation}
-f_0' = f_0
-      + \sum_\beta b_\beta^{\textrm{(th,min)}} 
-        \left(  \frac{f_\beta^+   -  f_\beta^- }{2}
-              -    b_\beta^{\textrm{(th,min)}}
-                \frac{f_\beta^+ + f_\beta^- - 2f_0}{2}
-        \right),
-\end{equation}
-where $f_0$ is the original central PDF and the up and down variation eigenvectors are given by $f^+, f^-$.
-%
-The reduction in the uncertainties of the profiled PDFs indicate the impact
-of the projected data with respect to the assumed prior PDF set.
-
-The profiling studies carried out in this work are performed using v2.2.1 of the \textsc{xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}.
-%
-To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed and is available in {\sc\small xFitter}.
-%
-All the experimental and theoretical data files used in the analysis, including
-the  {\sc\small PineAPPL}  grids, are available
-from the {\sc\small xFitter} repository.
-
-\subsection{Implementation in NNPDF}

### 2023-07-13 paper/sec-dis-pseudodata.tex
sect 2

@@
 
-The event yields displayed in Fig.~\ref{fig:fasernu2_muon} determine the associated
-statistical uncertainty in each bin
+The event yields displayed in Fig.~\ref{fig:fasernu2_muon} for FASER$\nu$2, and the corresponding
+calculations for the other experiments listed in Table~\ref{tab:FPF_experiments},
+determine the associated statistical uncertainty in each bin
 \be
 \label{eq:statistical_uncertainties}
-\delta_{\rm stat}  N_{\rm ev}^{(i)} = \sqrt{N_{\rm ev}^{(i)}} \, ,
+\delta^{\rm (stat)}  N_{\rm ev}^{(i)} = \sqrt{N_{\rm ev}^{(i)}} \, ,
 \ee
-such that the fractional statistical uncertainty per bin is $1/\sqrt{N_{\rm ev}^{(i)}}$.
+such that the fractional statistical uncertainty per bin is $\delta^{\rm (stat)}_i=1/\sqrt{N_{\rm ev}^{(i)}}$.
 %
-Since here we discard bins with less than 30 events, this statistical uncertainty
-ranges between $\sim 1\%$ and $\sim 18\%$ for muon neutrinos in FASER$\nu$2 depending on the values of
+Since we discard bins with less than 30 events, the fractional statistical uncertainty
+ranges between $\lsim 1\%$ and $\sim 18\%$ for muon neutrinos in
+the case of FASER$\nu$2 depending on the values of
 $x$ and $Q^2$ associated to this bin.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h]
+    \centering
+    \includegraphics[width = 0.95\textwidth]{plots/error_plot_FASERv2_14.pdf}
+    \caption{Same as Fig.~\ref{fig:fasernu2_muon} for FASER$\nu$2
+      now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$.
       %
+      In addition to the event yield values, we also show the error bars corresponding to
+      statistical errors only (left), systematic errors only (middle), and the
+      sum in quadrature of the two (right panel).
+      %
+      The error bars in the horizontal direction indicate the width of the adopted $x$-bins.
+      }
+    \label{fig:error_plot_FASERv2_14}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 These statistical uncertainties are displayed in the left panel
@@
 %
-The error bar in the $y$-direction indicates the statistical uncertainties, while
-that in the $x$ direction corresponds to the width of the $x$-bins.
-{\color{red}[Suggestion (TM): let's refer to horizontal and vertical directions, since $x$ and $y$ are variables as well, not only directions]}
-
-Fig.~\ref{fig:percentage_error_elepton}
-displays the estimated systematic uncertainties for the  measurements
-of the double-differential
-neutrino scattering cross-section at FASER$\nu$2.
+The error bar in the vertical direction indicates the statistical uncertainties, while
+that in the horizontal direction corresponds to the width of the $x$-bins.
 %
-We consider the leading sources of systematic errors,
-associated respectively to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$
-and to the hadronic energy $E_h$.
-%
-The size of each source of systematic error is plotted as a function
-of the average momentum fraction per bin $\la x\ra$
-in three different bins of $Q^2$.
-%
-We indicate separately the results for neutrino and antineutrino projectiles as well as
-those associated to inclusive and to charm production measurements.
-%
-Systematic uncertainties associated to the hadronic final state energy $E_h$ appear to be the largest.
-%
-The uncertainties associated to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$ range
-between a few percent up to 20\% in the nominal baseline scenario,
-and in the case of the latter they are the smallest in the large-$x$ region.
-%
-Similar overview plots have been produced for the other LHC neutrino experiments
-considered in this work.
-
-%-----------------------------------------------------------------------
-\begin{figure}[!ht]
-  \centering
-  \includegraphics[width=\textwidth]{plots/percentage_errors.pdf}
-  \caption{\small Estimated systematic uncertainties for the  measurements
-    of the double-differential
-    neutrino scattering cross-section at FASER$\nu$2.
-    %
-    We consider the leading sources of systematic errors,
-    associated respectively to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$
-    and to the hadronic energy $E_h$.
-    %
-    The size of each source of systematic error is plotted as a function
-    of the average momentum fraction per bin $\la x\ra$
-    in three different bins of $Q^2$.
-    %
-    We indicate separately the results for neutrino and antineutrino projectiles as well as
-    those associated to inclusive and to charm production measurements.
-  }
-  \label{fig:percentage_uncertainties_overview}
-\end{figure}
-%-----------------------------------------------------------------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h]
-    \centering
-    \includegraphics[width = 0.95\textwidth]{plots/error_plot_FASERv2_14.pdf}
-    \caption{Same as Fig.~\ref{fig:fasernu2_muon}
-      now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$.
-      %
-      In addition to the event yields we show the error bars corresponding to
-      statistical errors only (left), systematic errors only (middle), and the
-      sum in quadrature of the two (right panel).
-      %
-      The error bars in the $x$ direction indicate the width of the adopted $x$-bins.
-      }
-    \label{fig:error_plot_FASERv2_14}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Except for the bins with the smallest values of $x$, statistical uncertainties indeed
+are at the percent level for FASER$\nu$2.
 
 In addition to the statistical uncertainties given by Eq.~(\ref{eq:statistical_uncertainties}),
-one needs to estimate the systematic uncertainties associated to the reconstruction
-of the final state leptonic and hadronic variables as listed in Table~\ref{tab:FPF_experiments}.
+one needs to also estimate the systematic uncertainties associated to the reconstruction
+of the final state leptonic and hadronic variables listed in Table~\ref{tab:FPF_experiments}.
 %
-For instance, an event which would be classified in a given bin in the case
-of a perfect detector may end up in a different bin in the presence of systematic
+Event which would be classified in a given bin in the case
+of a perfect detector may end up being classified into a different bin in the presence of systematic
 shifts associated to the lepton energy $E_\ell$, lepton scattering angle $\theta_\ell$, and
@@
 
+Fig.~\ref{fig:percentage_error_elepton}
+displays the estimated systematic uncertainties for the  measurements
+of the double-differential
+neutrino scattering cross-section at FASER$\nu$2.
+%
+We consider the leading sources of systematic errors,
+associated respectively to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$
+and to the hadronic energy $E_h$.
+%
+The size of each source of systematic error is plotted as a function
+of the average momentum fraction per bin $\la x\ra$
+in three different bins of $Q^2$.
+%
+We indicate separately the results for neutrino and antineutrino projectiles as well as
+those associated to inclusive and to charm production measurements.
+%
+Systematic uncertainties associated to the hadronic final state energy $E_h$ appear to be the largest.
+%
+The uncertainties associated to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$ range
+between a few percent up to 20\% in the nominal baseline scenario,
+and in the case of the latter they are the smallest in the large-$x$ region.
+%
+Similar overview plots have been produced for the other LHC neutrino experiments
+considered in this work.
+
+%-----------------------------------------------------------------------
+\begin{figure}[!ht]
+  \centering
+  \includegraphics[width=\textwidth]{plots/percentage_errors.pdf}
+  \caption{\small Estimated systematic uncertainties for the  measurements
+    of the double-differential
+    neutrino scattering cross-section at FASER$\nu$2.
+    %
+    We consider the leading sources of systematic errors,
+    associated respectively to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$
+    and to the hadronic energy $E_h$.
+    %
+    The size of each source of systematic error is plotted as a function
+    of the average momentum fraction per bin $\la x\ra$
+    in three different bins of $Q^2$.
+    %
+    We indicate separately the results for neutrino and antineutrino projectiles as well as
+    those associated to inclusive and to charm production measurements.
+  }
+  \label{fig:percentage_uncertainties_overview}
+\end{figure}
+%-----------------------------------------------------------------------
+
 The end result of the procedure is the estimate of statistical and systematic uncertainties
@@
 
- \subsection{Pseudo-data generation}
+ \subsection{Pseudo-data generation and impact on PDFs}
 
@@
  on the PDFs and its dependence on the experimental correlation model.
+
+In this section, we describe the analysis settings adopted to quantify
+the impact of LHC neutrino measurements on the proton and nuclear PDFs.
+%
+First of all, we discuss the calculation of inclusive and charm structure functions
+and their interpolation in terms of fast grids. 
+%
+Second, we review the Hessian profiling framework and how it is applied
+in this work to proton and nuclear PDFs.
+%
+Third, we indicate the implementation of the LHC neutrino pseudo-data in the
+NNPDF framework and the settings of the subsequent global PDF analysis.
+
+The procedure described in Sect.~\ref{sec:dis_pseudodata} returns
+$N_{\rm bin}$ bins of LHC neutrino pseudo-data $\mathcal{O}_i^{{\rm (exp)}}$, Eq.~(\ref{eq:pseudo_data}), covering the $(x,Q^2,E_\nu)$ kinematic region accessible by the experiment,
+together with the associated statistical and systematic uncertainties.
+%
+The calculation of this pseudo-data relies on the corresponding set of
+theoretical predictions for the same observables $\mathcal{O}_i^{{\rm (th)}}$,
+Eq.~(\ref{eq:theory_dis_projections}).
+%
+Here we evaluate inclusive and charm DIS structure functions with the
+{\sc\small YADISM}~\cite{yadism,Candido:2023utz} program
+interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss, christopher_schwan_2023_7995675}
+to return a fast interpolation grid admitting a generic PDF input.
+%
+DGLAP evolution effects between the scale $Q_0$ at which PDFs are evaluated
+and the data scale $Q$ are provided by {\sc\small EKO}~\cite{Candido:2022tld}.
+
+The resulting {\sc\small PineAPPL} grids provide a fast evaluation
+of Eq.~(\ref{eq:theory_dis_projections}) for an arbitrary choice of the
+input PDFs at the initial scale $Q_0$, with the latter accessed via their
+{\sc\small LHAPDF} interface~\cite{Buckley:2014ana}.
+%
+Whenever pseudo-data is generated, it is crucial to adopt common inputs with
+the subsequent PDF analysis.
+%
+For instance, if one aims to include the LHC neutrino data into the NNPDF4.0
+NNLO determination, $\mathcal{O}_i^{{\rm (th)}}$ must be evaluated also at NNLO
+and also using
+NNPDF4.0 as input for consistency, else artificial tensions between theory
+and data would be introduced during the fit biasing the results.
+
+By means of this theoretical pipeline, predictions for
+DIS inclusive structure functions on an isoscalar target $N$ are computed
+using
+\be
+\label{eq:neutrino_DIS_xsec}
+\frac{d^2\sigma^{\nu N}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\nu N}_2(x,Q^2) - y^2F^{\nu N}_L(x,Q^2) +Y_- xF^{\nu N}_3(x,Q^2)\rc  \, ,
+\ee
+with an analogous formula for antineutrino scattering with the sign of $xF_3$ flipped.
+%
+A {\sc\small PineAPPL} interpolation grid for
+Eq.~(\ref{eq:neutrino_DIS_xsec}) is evaluated at the $(x,Q^2,E_\nu)$ bins
+for which pseudo-data is generated using DGLAP evolution and coefficient
+functions at $\mathcal{O}\lp \alpha_s^2\rp$ and accounting for target mass effects.
+%
+No higher-twists corrections to the structure functions are included, since we cut
+data with $W^2 \ge 12.5$ GeV in order to suppress them.
+%
+Deviations from isoscalarity and nuclear modifications with respect
+to a free isoscalar target are accounted for at the input PDF level,
+leaving the grid entering the evaluation of Eq.~(\ref{eq:neutrino_DIS_xsec}) unchanged.
+%
+No heavy quark mass effects are considered for at the level of these inclusive structure functions.
+
+Concerning charm structure functions, for experiments with charm tagging
+capabilities theoretical predictions are evaluated for
+\be
+\label{eq:neutrino_DIS_xsec}
+\frac{d^2\sigma^{\nu N}_c(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F_{2,c}^{\nu N}(x,Q^2) - y^2F^{\nu N}_{L,c}(x,Q^2) +Y_- xF^{\nu N}_{3,c}(x,Q^2)\rc  \, ,
+\ee
+with the DIS charm structure functions evaluated in the FONLL general-mass variable-flavour-number
+scheme~\cite{Forte:2010ta,Ball:2011mu,Faura:2020oom} in order to account for charm mass effects.
+%
+Eq.~(\ref{eq:neutrino_DIS_xsec}) is computed with $\mathcal{O}\lp \alpha_s^2\rp$ massless
+coefficient functions and $\mathcal{O}\lp \alpha_s\rp$ massive ones, given
+that the $\mathcal{O}\lp \alpha_s^2\rp$ massive calculation~\cite{Gao:2017kkx} is not publicly available.
+%
+Nevertheless, the $\mathcal{O}\lp \alpha_s\rp$ massive coefficient functions
+encapsulate the dominant charm mass dependence of the double differential
+cross-section.
+%
+We assume 100\% efficiency in charm tagging and do not impose acceptance cuts on the charm
+quark or $D$-meson kinematics (the only acceptance requirements are applied to the final-state
+charged lepton, as indicated in  Table~\ref{tab:FPF_experiments}).
+
+We note that experiments without charm-tagging capabilities can still identify charm production
+events by means of the dimuon final state,
+\be
+\nu + N \to \mu^+ + c~(\to D) + X \to \mu^+ + \mu^- +X \, ,
+\ee
+by profiting from the semileptonic decays of the $D$-meson leading
+to the characteristic signature of two opposite-sign muons.
+%
+In this case, the  differential charm production cross-section Eq.~(\ref{eq:neutrino_DIS_xsec})
+must be accompanied by the corresponding branching ratio
+\be
+\frac{d^2\sigma^{\nu N}_c(x,Q^2,y)}{dxdy}\mathcal{B}\lp c \to D \to \mu + X\rp \, ,
+\ee
+which given that $\mathcal{B}\sim 10\%$ suppresses the reconstructed charm
+production event yields by around an order of magnitude.
+%
+For experiments reconstructing the dimuon final state,
+we also apply the muon acceptance criteria to both muons.
+
+In this work we consider two complementary approaches in order to assess the
+impact of LHC neutrino data on the proton and nuclear PDFs.
+%
+On the one hand, the Hessian profiling of a prior proton or
+nuclear PDF set, which here are taken to be PDF4LHC21~\cite{PDF4LHCWorkingGroup:2022cjn} and
+EPPS21~\cite{Eskola:2021nhw} respectively.
+%
+On the other hand, the inclusion of the LHC neutrino structure functions
+on the NNPDF global analysis framework~\cite{NNPDF:2021uiq,NNPDF:2021njg}.
+%
+Here we summarise the details of the Hessian profiling procedure and
+outline how it is applied in our work.
+
+The profiling method applied to Hessian PDF fits is described in~\cite{Paukkunen:2014zia, Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre} and is based
+on minimizing a goodness-of-fit error function defined as
+\begin{equation}
+\chi^2 = 
+\sum_{i=1}^{N_{\textrm{bin}}} 
+\frac{\left(  \mathcal{O}_i^{\rm (exp)}
+            + \Gamma_i^{\alpha,\textrm{pd}}
+              b_\alpha^{\textrm{(pd)}}
+            - \mathcal{O}_i^{\rm (th)}
+            - \Gamma_i^{\beta,\textrm{th}}
+              b_\beta^{(\textrm{th})}
+     \right)^2
+     }{ \left(\delta_i^{\rm stat}\right)^2 }
++ \sum_\alpha \lp b_\alpha^{(\textrm{pd})}\rp^2
++ \sum_\beta  \lp b_\beta^{\textrm{(th)}}\rp ^2 \, .
+\label{eq:profilingchi2}
+\end{equation}
+The pseudodata 
+$\mathcal{O}_i^{\rm (exp)}$ 
+is obtained from the central theoretical prediction 
+$\mathcal{O}_i^{(\textrm{th})}$
+for each bin $i$ out of $N_{\textrm{bin}}$ by fluctuating
+it within its uncertainties, following either
+Eq.~(\ref{eq:pseudo_data}), when accounting for the correlations
+between systematic uncertainties, or Eq.~(\ref{eq:pseudo_data_v2}),
+in the case in which errors are added in quadrature.
+
+The correlated uncertainties for the pseudodata and for the theoretical prediction 
+are contained in the nuisance parameter vectors $b^{(\textrm{pd})}$ and $b^{(\textrm{th})}$, respectively, and the total uncorrelated uncertainties are denoted by $\delta_{{\rm stat},i}$.
+%
+The effect of the nuisance parameters
+on the observables $\mathcal{O}_i^{\rm (exp)}$ and $\mathcal{O}_i^{\rm (th)}$
+is described by the matrices $\Gamma_i^{\textrm{pd}}$ and $\Gamma_i^{\textrm{th}}$.
+%
+The indices $\alpha$ and $\beta$ then run over the uncertainty nuisance parameters for the pseudodata and the theoretical prediction, respectively.
+%
+The nuisance parameter values $b_\beta^{\textrm{(th,min)}}$ that minimize Eq.~\eqref{eq:profilingchi2} give the central PDFs $f'_0$ optimized to the profiled dataset in the form
+\begin{equation}
+f_0' = f_0
+      + \sum_\beta b_\beta^{\textrm{(th,min)}} 
+        \left(  \frac{f_\beta^+   -  f_\beta^- }{2}
+              -    b_\beta^{\textrm{(th,min)}}
+                \frac{f_\beta^+ + f_\beta^- - 2f_0}{2}
+        \right),
+\end{equation}
+where $f_0$ is the original central PDF and the up and down variation eigenvectors are given by $f^+, f^-$.
+%
+The reduction in the uncertainties of the profiled PDFs indicate the impact
+of the projected data with respect to the assumed prior PDF set.
+
+The profiling studies carried out in this work are performed using v2.2.1 of the \textsc{xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}.
+%
+To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed and is available in {\sc\small xFitter}.
+%
+All the experimental and theoretical data files used in the analysis, including
+the  {\sc\small PineAPPL}  grids, are available
+from the {\sc\small xFitter} repository.

### 2023-07-13 paper/sec-dis-pseudodata.tex
sect 2

@@
  E_\nu &=& E_h + E_\ell \, , \nonumber \\
- Q^2 &=& 4 ( E_h + E_\ell) E_\ell \sin^2 \lp \theta_\ell/2\rp \, ,\\
+ Q^2 &=& 4 ( E_h + E_\ell) E_\ell \sin^2 \lp \theta_\ell/2\rp \, ,  \label{eq:dis_kinematic_mapping}\\
  x&=& \frac{4 ( E_h + E_\ell) E_\ell \sin^2 \lp \theta_\ell/2\rp}{2m_N E_h} \, .\nonumber
@@
 In addition to the statistical uncertainties given by Eq.~(\ref{eq:statistical_uncertainties}),
-one needs to also estimate the systematic uncertainties associated to the reconstruction
+one needs to also estimate the systematic uncertainties associated to the
+finite precision in the reconstruction
 of the final state leptonic and hadronic variables listed in Table~\ref{tab:FPF_experiments}.
 %
-Event which would be classified in a given bin in the case
-of a perfect detector may end up being classified into a different bin in the presence of systematic
+For instance, an event which would be classified into a given bin in $(x,Q^2,E_\nu)$ in the case
+of a perfect detector may end up being
+mis-classified into a different bin in the presence of systematic
 shifts associated to the lepton energy $E_\ell$, lepton scattering angle $\theta_\ell$, and
-hadronic energy $E_h$.
+hadronic energy $E_h$, as indicated by  Eq.~(\ref{eq:dis_kinematic_mapping}).
+
+For each possible source of experimental systematic uncertainty, we therefore need to
+quantify its impact at the event yield level.
 %
-Hence, for each source of experimental systematic uncertainty we would like to estimate
-its impact at the level of event yields and eventually stablish also the associated
-correlation matrix.
-
-By means of tree-level DIS kinematics, one can relate the variables describing the neutrino-nucleon
-hard-scattering, $(x,Q^2,E_{\nu})$,
-with those describing the leptonic and hadronic final state, namely $\lp E_{\ell},\theta_\ell, E_{h} \rp$,
-and that correspond to experimentally measured quantities.
-%
-The mapping between the two sets of variables is 
-\bea
-E_{\nu} &=& E_\ell + E_h \, ,\nonumber \\
-Q^2 &=& 4E_\ell E_{\nu}\sin^2\lp {\theta_\ell/2}\rp  =  4E_\ell \lp E_\ell + E_h  \rp\sin^2\lp {\theta_\ell/2}\rp \, , \\
-x &=& \frac{Q^2}{2m_N(E_{\nu} - E_\ell)} = \frac{4E_\ell \lp E_\ell + E_h  \rp\sin^2\lp {\theta_\ell/2}\rp}{2m_NE_{h}} \, , \nonumber
-\eea
-highlighting how the measurement of $E_{\ell}$, $\theta_\ell$, and $E_{h}$ uniquely specify the hard-scattering
-kinematics $(x,Q^2,E_{\nu})$ of the event.
-%
-Therefore, systematic shifts in the measurement of these final-state variables will modify
-the assignment of each event to a given bin of $x$, $Q^2$, and $E_\mu$, introducing a systematic
-error in the event yields and hence in the measurement of the double-differential
-neutrino scattering cross-section.
-
 In order to determine these bin-by-bin systematic uncertainties,
@@
 %
-From Table~\ref{tab:FPF_experiments}, one reads that the corresponding acceptances
-and performance parameters for $E_{\ell}$, $\theta_\ell$, and $E_{h}$   are given by
+From Table~\ref{tab:FPF_experiments}, one reads that the detector
+acceptance and reconstruction performance is specified by:
 \bea
-E_\ell \ge 100~{\rm GeV} \, , \quad \delta E_\ell \sim 30\% \, ,\nonumber \\
-E_h \ge 100~{\rm GeV} \, , \quad \delta E_h \sim 30\% \, ,\\
- \theta_\ell \le \tan^{-1}(0.5) \, , \quad \delta\theta_\ell \sim 1~{\rm mrad} \, . \nonumber 
-\label{fasernu2systematic_errors}
+E_\ell \ge 100~{\rm GeV} \, , \quad \theta_\ell \le \tan^{-1}(0.5)\, , \qquad \nonumber\\
+\delta E_\ell \sim 30\% \, 
+ \quad \delta E_h \sim 30\% \, ,
+ \ \, , \quad \delta\theta_\ell \sim 1~{\rm mrad} \, . 
+\label{eq:fasernu2systematic_errors}
 \eea
-In order to translate the systematic uncertainties $\delta E_\ell$, $\delta E_h $,
-and $\delta\theta_\ell$ into systematic errors associated to the binned event yields, 
+To translate the uncertainties in $\delta E_\ell$, $\delta E_h $,
+and $\delta\theta_\ell$ into systematic errors associated to the event yields, 
 \be
@@
 of $\mathcal{D}_0$ which are then smeared with Gaussian distributions whose variances
-are given by Eq.~(\ref{fasernu2systematic_errors}).
+are given by Eq.~(\ref{eq:fasernu2systematic_errors}).
 %
@@
 by producing samples where only one source of error is varied at a time
-we can determine the values of Eq.~(\ref{eq:event_yields_systematic_error}) in each bin.
+we can determine the systematic errors Eq.~(\ref{eq:event_yields_systematic_error}) in each bin.
 
-Fig.~\ref{fig:percentage_error_elepton}
-displays the estimated systematic uncertainties for the  measurements
+Fig.~\ref{fig:percentage_uncertainties_overview}
+displays the systematic uncertainties associated
+to $E_\ell$, $\theta_\ell$, and $E_h$.
+in the  measurements
 of the double-differential
@@
 %
-We consider the leading sources of systematic errors,
-associated respectively to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$
-and to the hadronic energy $E_h$.
-%
-The size of each source of systematic error is plotted as a function
+The magnitude of each systematic error is plotted as a function
 of the average momentum fraction per bin $\la x\ra$
@@
 %
-Similar overview plots have been produced for the other LHC neutrino experiments
-considered in this work.
+The same procedure is adopted for all the experiments listed in Table~\ref{tab:FPF_experiments}.
 
@@
     %
-    We consider the leading sources of systematic errors,
-    associated respectively to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$
+    We consider the systematic errors
+    associated to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$
     and to the hadronic energy $E_h$.

### 2023-07-13 paper/sec-dis-pseudodata.tex
Start updaing plots

@@
     \centering
-\includegraphics[width=0.8\textwidth]{plots/Nevent_FASERv2_14.pdf}
-\caption{\small The event yields per bin $N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}),
-  for muon neutrinos at the FASER$\nu$2 detector, restricted
-  to the DIS region defined by Eq.~(\ref{eq:DISconditions}).
-  %
-  We present results binned in $x$ and $Q^2$ integrated over neutrino energies.
-  %
-  The red dots indicate the weighted bin center.
+	\includegraphics[width=0.495\textwidth]{plots/FPF-FASERv.pdf}
+	\includegraphics[width=0.495\textwidth]{plots/FPF-FASERv2.pdf}
+	\includegraphics[width=0.495\textwidth]{plots/FPF-FLArE100.pdf}
+	\includegraphics[width=0.495\textwidth]{plots/FPF-SND.pdf}
+	\caption{\small The event yields per bin $N_{\rm ev}^{(i)}$, for muon neutrinos at the FASER$\nu$(2)
+	and AdvSND detectors, and electron neutrinos the FLArE detector, restricted to the DIS region defined 
+	by Eq.~(\ref{eq:DISconditions}).
 	%
@@
     \centering
-    \includegraphics[width = 0.8\textwidth]{plots/Kin_nNNPDF30_EIC_FPF.pdf}
+    \includegraphics[width = 0.9\textwidth]{plots/Kin_nNNPDF30_EIC_FPF.pdf}
     \caption{The kinematic coverage of FASER$\nu$2 in the $(x,Q^2)$ plane,

### 2023-07-13 paper/sec-dis-pseudodata.tex
Fixed N_ev and systematic derivation

@@
   \label{eq:event_yields}
-   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) dQ^2 dx dE_{\nu} \, ,\quad i=1,\ldots, N_{\rm bins} \, ,
+   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, ,\quad i=1,\ldots, N_{\rm bins} \, ,
 \end{equation}
-with $n_T$ is the nuclear density of the target detector material and $L_T$ its length.
+with $n_T$ is the nuclear density of the target detector material, $L_T$ its length and ${\cal A}(x,Q^2,E_{\nu})$ is an acceptance factor which takes the form of a step function and accounts for the experimental thresholds from Table\ref{tab:FPF_experiments}.
 %
@@
 \begin{equation}
-    N_{\rm ev}^{(i)} \approx n_T L_T \frac{(Q^{2(i)}_{\rm max}-Q^{2(i)}_{\rm min})(x^{(i)}_{\rm max}-x^{(i)}_{\rm min})(E_{\rm max}^{(i)}-E_{\rm min}^{(i)})}{N_{\rm mc}}\times \sum_{j=1}^{N_{\rm mc}} \frac{dN_{\nu}(E^{(j)}_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x^{(j)},Q^{2(j)},E^{(j)}_{\nu})}{dxdQ^2}\right) \, ,
+    N_{\rm ev}^{(i)} \approx n_T L_T \frac{(Q^{2(i)}_{\rm max}-Q^{2(i)}_{\rm min})(x^{(i)}_{\rm max}-x^{(i)}_{\rm min})(E_{\rm max}^{(i)}-E_{\rm min}^{(i)})}{N_{\rm mc}}\times \sum_{j=1}^{N_{\rm mc}} \frac{dN_{\nu}(E^{(j)}_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x^{(j)},Q^{2(j)},E^{(j)}_{\nu})}{dxdQ^2}\right) {\cal A}(x^{(j)},Q^2^{(j)},E_{\nu}^{(j)}) \, ,
     \label{MCintegration}
@@
 %
-Provided the number of samples $M$ is large enough, the standard deviation over samples in this $ N_{\rm ev}^{(i)(k)}$
-distribution provides the sought-for estimate of the systematic uncertainties.
+Provided the number of samples $M$ is large enough,  {\color{red} the standard deviation over samples in this $ N_{\rm ev}^{(i)(k)}$
+distribution}{\color{blue} $\rightarrow$ the average difference of events in the smeared datasets and the original dataset,$ N_{\rm ev}^{(i)(k>0)} -  N_{\rm ev}^{(i)(0)}$,} provides the sought-for estimate of the systematic uncertainties.
 %

### 2023-07-14 paper/sec-dis-pseudodata.tex
Updated systematic uncertainty derivation

@@
 %
-Provided the number of samples $M$ is large enough,  {\color{red} the standard deviation over samples in this $ N_{\rm ev}^{(i)(k)}$
-distribution}{\color{blue} $\rightarrow$ the average difference of events in the smeared datasets and the original dataset,$ N_{\rm ev}^{(i)(k>0)} -  N_{\rm ev}^{(i)(0)}$,} provides the sought-for estimate of the systematic uncertainties.
+Provided the number of samples $M$ is large enough,the average difference of events in the smeared datasets and the original dataset, $\sum_{k=1}^{M} \frac{N_{\rm ev}^{(i)(k)}}{M-1} -  N_{\rm ev}^{(i)(0)}$, provides the sought-for estimate of the systematic uncertainties.
 %

### 2023-07-14 paper/sec-dis-pseudodata.tex
fixed compilation error

@@
 \begin{equation}
-    N_{\rm ev}^{(i)} \approx n_T L_T \frac{(Q^{2(i)}_{\rm max}-Q^{2(i)}_{\rm min})(x^{(i)}_{\rm max}-x^{(i)}_{\rm min})(E_{\rm max}^{(i)}-E_{\rm min}^{(i)})}{N_{\rm mc}}\times \sum_{j=1}^{N_{\rm mc}} \frac{dN_{\nu}(E^{(j)}_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x^{(j)},Q^{2(j)},E^{(j)}_{\nu})}{dxdQ^2}\right) {\cal A}(x^{(j)},Q^2^{(j)},E_{\nu}^{(j)}) \, ,
+    N_{\rm ev}^{(i)} \approx n_T L_T \frac{(Q^{2(i)}_{\rm max}-Q^{2(i)}_{\rm min})(x^{(i)}_{\rm max}-x^{(i)}_{\rm min})(E_{\rm max}^{(i)}-E_{\rm min}^{(i)})}{N_{\rm mc}}\times \sum_{j=1}^{N_{\rm mc}} \frac{dN_{\nu}(E^{(j)}_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x^{(j)},Q^{2(j)},E^{(j)}_{\nu})}{dxdQ^2}\right) {\cal A}(x^{(j)},Q^{2(j)},E_{\nu}^{(j)}) \, ,
     \label{MCintegration}

### 2023-07-17 paper/sec-dis-pseudodata.tex
updated some text on systematics

@@
 %
-Provided the number of samples $M$ is large enough,the average difference of events in the smeared datasets and the original dataset, $\sum_{k=1}^{M} \frac{N_{\rm ev}^{(i)(k)}}{M-1} -  N_{\rm ev}^{(i)(0)}$, provides the sought-for estimate of the systematic uncertainties.
+We take the uncertainty to be the absolute difference betweeen the mean number of events in the bin for the smeared samples samples, ${\overline{N}}^{(i)}~$ and$~ N_{\rm ev}^{(i)}$ as calculated from Eq.
+\ref{MCintegration}, {\it{i.e.}}  $\delta N^{(i)} = |{\overline{N}}^{(i)} -N_{\rm ev}^{(i)}|$ .
 %

### 2023-07-17 paper/sec-dis-pseudodata.tex
updated table experiments

@@
 %
-The ForwArd Search ExpeRiment (FASER) detector and its companion FASER$\nu$~\cite{FASER:2019aik,FASER:2019dxq}
+The ForwArd Search ExpeRiment (FASER) detector and its companion FASER$\nu$~\cite{FASER:2019aik,FASER:2019dxq,FASER:2023zcr,FASER:2022hcn}
 are located at the TI12 tunnel of the CERN accelerator complex.
@@
 %
-In the same manner as FASER, the SND@LHC experiment is located in a service tunnel (TI18)
+In the same manner as FASER, the SND@LHC experiment~\cite{SNDLHC:2022ihg}
+is located in a service tunnel (TI18)
 around 500 meters from the ATLAS interaction point and has been taking data
@@
  for muon charge and momentum measurements.
+ %
+  For the FLArE detector, we assume that muons would be measured in the FASER2 spectrometer
+  situated downstream in the FPF cavern.
  %

### 2023-07-17 paper/sec-summary.tex
updated table experiments

@@
 %
+We thank specially Felix Kling for may useful discussions in the course
+of the project.
+%
 We thank Akitaka Ariga and Tomoko Ariga for information
-concerning FASER$\nu$2,
+concerning FASER$\nu$2, Milind Diwan,
 Wenjie Wu and Steven Linden concerning FLArE,

### 2023-07-17 paper/tables/detectors.tex
updated table experiments

@@
 \midrule
-\multirow{2}{*}{FASER$\nu$}  &  \multirow{2}{*}{ $|\eta_\nu| \le 8.5$}  &   Tungsten  & \multirow{2}{*}{muons}      &   $E_\ell \gsim 100$ GeV   &    \multirow{2}{*}{n/a}       \\
-  &   &   (1.1 ton)  &       &  $\tan \theta_\ell \lsim 0.5$   &         \\
+\multirow{3}{*}{FASER$\nu$}  &  \multirow{3}{*}{ $\eta_\nu \ge 8.5$}  &   \multirow{2}{*}{Tungsten}  & \multirow{3}{*}{muons}      &   $E_\ell \gsim 100$ GeV   &      $\delta E_\ell \sim 30\% $    \\
+&   &   \multirow{2}{*}{(1.1 ton)}  &       &  $\tan \theta_\ell \lsim 0.025$   &
+$\delta \theta_\ell \sim 0.06$ mrad        \\
+&   &     &       &  reconstructed $E_h$ \& charm ID   &      $\delta E_h \sim 30\%$     \\
 \midrule
@@
 \midrule
-\multirow{3}{*}{FASER$\nu$2}  & \multirow{3}{*}{ $|\eta_\nu| \le 8.5$}  & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{muons}     &   $E_\ell \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
-  &   &  \multirow{2}{*}{(20 ton)}   &       &  $\tan \theta_\ell \lsim 0.5$   &   $\delta \theta_\ell \sim 1$ mrad      \\
+\multirow{3}{*}{FASER$\nu$2}  & \multirow{3}{*}{ $\eta_\nu \ge 8.5$}  & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{muons}     &   $E_\ell \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
+  &   &  \multirow{2}{*}{(20 ton)}   &       &  $\tan \theta_\ell \lsim 0.05$   &   $\delta \theta_\ell \sim 0.06$ mrad      \\
   &   &     &       &  reconstructed $E_h$ \& charm ID   &  $\delta E_h \sim 30\%$        \\
 \midrule
-\multirow{3}{*}{AdvSND~(far)}  &   \multirow{3}{*}{ $7.2 \le \eta_\nu \le 8.4$}  &
+\multirow{3}{*}{AdvSND-far}  &   \multirow{3}{*}{ $7.2 \le \eta_\nu \le 8.4$}  &
 \multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{muons}    &  $E_\mu \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
@@
 \midrule
-\multirow{3}{*}{FLArE}  & \multirow{3}{*}{tbd} & \multirow{2}{*}{Liquid Argon}  & \multirow{3}{*}{ maybe muons}  &  $E_\mu \lsim 2$ GeV, $E_e \lsim 1$ TeV    &    $\delta E_e \sim 5\% $ \\
-&   &  \multirow{2}{*}{(10 ton)}   &   & $\theta_\mu \lsim 0.4$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $ mrad   \\
+\multirow{3}{*}{FLArE ({\bf *})}  & \multirow{3}{*}{$\eta_\nu \ge 7.5$} & \multirow{2}{*}{LAr}  & \multirow{3}{*}{muons}  &  $E_\mu \gsim 2$ GeV, $E_e \lsim 2$ TeV    &    $\delta E_e \sim 5\% $ \\
+&   &  \multirow{2}{*}{(10 ton)}   &   & $\theta_\mu \lsim 0.025$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $ mrad   \\
  &   &     &  & reconstructed $E_h$  &    $\delta E_h \sim 30\% $   \\
@@
   %
+  For the FLArE detector, we assume that muons would be measured in the FASER2 spectrometer
+  situated downstream in the FPF cavern.
+  %
   See the description of each experiment in the text for more details.
   %
-  For the projections in this work we assume that FASER$\nu$ and SND@LHC acquire data
+  For the projections in this work, we assume that FASER$\nu$ and SND@LHC acquire data
   for the full Run III period, while FASER$\nu$2, AdvSND, and FLArE take data
   for the complete HL-LHC period.
-  %
-  An estimate of the expected 
-  systematic uncertainties is not available for FASER$\nu$ and SND@LHC, experiments
-  which nevertheless are limited by statistics.
   \label{tab:FPF_experiments}

### 2023-07-17 paper/sec-dis-pseudodata.tex
sect 2

@@
-\section{DIS projections for LHC far-forward experiments}
+\section{Deep-inelastic scattering with LHC neutrinos}
 \label{sec:dis_pseudodata}
@@
 to generate projections for the kinematic coverage
-and experimental uncertainties associated to  measurements
+and uncertainties associated to  measurements
 of neutrino-nucleus scattering at the LHC far-forward experiments.
@@
 will be considered in the present study and indicate their
-main acceptance and performance parameters.
+acceptance and performance parameters.
 %
-By convoluting the expected muon neutrino fluxes
+By convoluting the expected electron and muon neutrino fluxes
 with the acceptance and scattering rates of each
 of these detectors,
-we evaluate the foreseen event yields in bins of $x$, $Q^2$,
-and $E_\nu$ and therefore the associated statistical uncertainties.
+we evaluate the event yields in bins of $x$, $Q^2$,
+and $E_\nu$ and the associated statistical and systematic uncertainties.
 %
-We also estimate how the systematic uncertainties in the measurement
-of final-state variables affects the experimental covariance matrix.
+Finally, we discuss the procedure adopted to generate pseudo-data
+for LHC neutrino DIS and to their impact
+ into proton and nuclear PDF determinations.
 
@@
  %
- In this section, we summarise the main features of each of the existing and future
- far-forward detectors considered in this study, in particular concerning
- their acceptance, performance, and detection method.
+ Here we summarise the main features of each of the existing and future
+ far-forward detectors considered, in particular concerning
+ their acceptance and performance.
  %
- We focus on  muon
- neutrino scattering, which benefits from the highest rates and is less
- affected by uncertainties affecting $D$-meson production.
+ We focus on  muon neutrino scattering, which benefits from the highest rates and is less
+ affected by theoretical uncertainties in the production mechanism.
 
@@
  %
- A measurement of  $\lp E_\ell,\theta_\ell, E_h \rp$ then fixed the DIS kinematics as:
+ A measurement of  $\lp E_\ell,\theta_\ell, E_h \rp$ then fixes the DIS kinematics as:
  \bea
@@
  of $\lp E_\ell,\theta_\ell, E_h \rp$ translate into uncertainties in the
- reconstructed values of  $(x,Q^2, E_\nu)$, which in turn modify the expected
- event rates in a given bin.
+ reconstructed values of  $(x,Q^2, E_\nu)$ modifying the expected
+ binned event rates.
 
- Table~\ref{tab:FPF_experiments} indicates,
+ Table~\ref{tab:FPF_experiments} summarises,
 for each of the far-forward LHC neutrino experiments considered
@@
 %
-We take the uncertainty to be the absolute difference betweeen the mean number of events in the bin for the smeared samples samples, ${\overline{N}}^{(i)}~$ and$~ N_{\rm ev}^{(i)}$ as calculated from Eq.
+We take the uncertainty to be the absolute difference between the mean number of events in the bin for the smeared samples samples, ${\overline{N}}^{(i)}~$ and$~ N_{\rm ev}^{(i)}$ as calculated from Eq.
 \ref{MCintegration}, {\it{i.e.}}  $\delta N^{(i)} = |{\overline{N}}^{(i)} -N_{\rm ev}^{(i)}|$ .

### 2023-07-17 paper/tables/detectors.tex
sect 2

@@
 \caption{\small For each of the far-forward LHC neutrino experiments considered
-  in this work, we indicate their neutrino pseudo-rapidity coverage, target material, whether
+   we indicate their neutrino pseudo-rapidity coverage, target material, whether
   they can identify the sign of the outgoing charged lepton,
@@
   We consider separately acceptance and performance for electron and muon
-  neutrinos, while tau neutrinos have lower production rates and are not considered in this study.
+  neutrinos.
   %
-  For the FLArE detector, we assume that muons would be measured in the FASER2 spectrometer
+  For FLArE, we assume that muons would be measured in the FASER2 spectrometer
   situated downstream in the FPF cavern.
@@
   %
-  For the projections in this work, we assume that FASER$\nu$ and SND@LHC acquire data
-  for the full Run III period, while FASER$\nu$2, AdvSND, and FLArE take data
-  for the complete HL-LHC period.
+  For our projections we assume that FASER$\nu$ and SND@LHC acquire data
+  for the Run III period ($\mathcal{L}=150$ fb$^{-1}$), while FASER$\nu$2, AdvSND, and FLArE take data
+  for the complete HL-LHC period ($\mathcal{L}=3$ ab$^{-1}$).
   \label{tab:FPF_experiments}

### 2023-07-17 paper/sec-dis-pseudodata.tex
sect 2

@@
  Table~\ref{tab:FPF_experiments} summarises,
-for each of the far-forward LHC neutrino experiments considered
-  in this work,  their neutrino pseudo-rapidity coverage, target material, whether
+ for each of the far-forward LHC neutrino experiments considered,
+ their pseudo-rapidity coverage, target material, whether
   they can identify the sign of the outgoing charged lepton,
@@
   We consider separately acceptance and performance for electron and muon
-  neutrinos, while tau neutrinos have lower production rates and are neglected in this study.
+  neutrinos.
   %
   For these projections we assume that FASER$\nu$ and SND@LHC acquire data
-  for the full Run III period, while FASER$\nu$2, AdvSND, and FLArE take data
-  for the complete HL-LHC period.
-  %
-  An estimate of the expected 
-  systematic uncertainties is not available for FASER$\nu$ and SND@LHC, experiments
-  which are nevertheless limited by statistics.
+  for Run III ($\mathcal{L}=150$ fb$^{-1}$), while FASER$\nu$2,
+  AdvSND, and FLArE take data
+  for the complete HL-LHC period  ($\mathcal{L}=3$ ab$^{-1}$).
   %
@@
 %
-The ForwArd Search ExpeRiment (FASER) detector and its companion FASER$\nu$~\cite{FASER:2019aik,FASER:2019dxq,FASER:2023zcr,FASER:2022hcn}
+The ForwArd Search ExpeRiment (FASER) detector
+and its companion FASER$\nu$~\cite{FASER:2019aik,FASER:2019dxq,FASER:2023zcr,FASER:2022hcn}
 are located at the TI12 tunnel of the CERN accelerator complex.
@@
 with the collision axis line-of-sight (LOS)
-and have been acquiring data since the begin of Run III.
+and have been acquiring data since the begin of Run III in 2022.
 %
@@
 of the outgoing downstream energetic muons.
+%
+FASER$\nu$ is sensitive to neutrinos with pseudorapidity $\eta_\nu \ge 8.5$
+and can also identify charm-tagged events.
 
@@
 %
-It is based on an emulsion-based detector optimised to identify heavy flavor particles, including
+It is based on the same technology as FASER$\nu$, and hence
+relies on a emulsion-based detector optimised to identify heavy flavor particles, including
 tau leptons and charm and beauty particles, arising from neutrino interactions.
+%
+It would be sensitive to neutrinos with pseudorapidity $\eta_\nu \ge 8.5$.
 %
@@
  %
- This experiment consists on  two detectors, a far-detector to be installed
- at the FPF with a coverage in neutrino pseudorapidity $\eta_\nu$ of $7.2 \le \eta_\nu \le 8.4$
+ This proposed experiment consists actually on  two detectors, a far-detector to be installed
+ at the FPF with a coverage in neutrino pseudorapidity of $7.2 \le \eta_\nu \le 8.4$
  (hence off-LOS) and a near detector installed somewhere else in LHC
@@
  %
- In the following we focus on the AdvSND far-detector.
+ In the following we focus on the AdvSND-far detector.
  %
@@
  %
-  For the FLArE detector, we assume that muons would be measured in the FASER2 spectrometer
+ While muon neutrinos with energy $E_\nu \gsim 2$ GeV would not be fully
+ contained in the  FLArE detector,
+for the projections presented in this work
+ we assume that outgoing muons would be measured in the FASER2 spectrometer
   situated downstream in the FPF cavern.
@@
  With an expected fiducial (active) mass of 10 tons (30 tons), FLArE will
- detect final-state electrons with energies $E_{e}\lsim 1~\rm{TeV}$ and
- scattering angles up to 0.5 mrad, while detecting final-state muons
- is restricted to $E_{e}\lsim 2~\rm{GeV}$  and $\theta_\mu \lsim 0.4$.
+ detect final-state electrons with energies $E_{e}\lsim 2~\rm{TeV}$ and
+ scattering angles up to 0.5 mrad,  final-state muons
+ with $\theta_\mu \lsim 0.025$ will be recorded by FASER$\nu$2.
  %
@@
  and $\delta E_h \sim 30$\% for the hadronic energy.
+ %
+ Since muon neutrinos would be measured by FASER$\nu$2, the
+ performance parameters for $E_\mu$ and $\theta_\mu$ are  taken
+ to be the same as those of FASER$\nu$2.
 
@@
 \label{eq:event_yields}
-N_{\rm ev}^{(i)}\lp \nu_e ; E_{{\rm min}}^{(i)} \le E_\nu \le E_{{\rm max}}^{(i)} ,\,
+N_{\nu_e,{\rm ev}}^{(i)}\lp \nu_e ; E_{{\rm min}}^{(i)} \le E_\nu \le E_{{\rm max}}^{(i)} ,\,
 x_{{\rm min}}^{(i)} \le x \le x_{{\rm max}}^{(i)} ;\, Q_{{\rm min}}^{2(i)} \le Q^2 \le Q_{{\rm max}}^{2(i)}\rp
-\, ,\quad i=1,\ldots, N_{\rm bins} \, ,
+\, ,\quad i=1,\ldots, N_{\rm bin} \, ,
 \ee
 for electron neutrinos and for each of the bins composing the measurement, and with similar
-expressions applying for muon and tau neutrinos and antineutrinos.
+expressions applying for muon neutrinos and antineutrinos.
 %
@@
 %
-The choice of the binning is in principle arbitrary, and here we define them
-to ensure that Gaussian statistics hold for all the bins of the measurement.
+When choosing the binning of the measurement, the main criteria are
+simplicity and ensuring that Gaussian statistics holds in all bins.
 
-In this calculation, we assume the central values of the neutrino fluxes provided by the calculation
-of~\cite{Kling:2021gos}.
+In our calculation we assume the central values of the neutrino
+fluxes provided by~\cite{Kling:2021gos}.
 %
@@
 %
-As we further discuss in Sect.~\ref{sec:settings}, theoretical predictions
-for the latter are computed with {\sc\small YADISM} interfaced to {\sc\small PineAPPL}
-to produce fast precomputed interpolation grids.
-%
 Differential event yields are therefore evaluated using
 \begin{equation}
-  \label{eq:event_yields}
-   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, ,\quad i=1,\ldots, N_{\rm bins} \, ,
+  \label{eq:event_yields_calculation}
+   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, ,
 \end{equation}
-with $n_T$ is the nuclear density of the target detector material, $L_T$ its length and ${\cal A}(x,Q^2,E_{\nu})$ is an acceptance factor which takes the form of a step function and accounts for the experimental thresholds from Table\ref{tab:FPF_experiments}.
+with $n_T$ is the nuclear density of the target detector material, $L_T$ its
+length and ${\cal A}(x,Q^2,E_{\nu})$ is an acceptance factor which takes the form of a
+step function and accounts for the experimental acceptance thresholds
+in $E_\ell$, $\theta_\ell$, and $E_h$
+listed in Table~\ref{tab:FPF_experiments}.
 %
-The incoming neutrino fluxes, which include the geometric acceptance of the considered detector,
+The incoming neutrino fluxes, which account for the geometry
+and $\eta_\nu$ coverage of the considered detector,
 are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$.
 %
-We consider only the scattering of muon neutrinos, characterised by the highest rates.
-%
-We verify that the differential event yield calculation
-implemented in Eq.~(\ref{eq:event_yields}), when extrapolated to a single bin
+We have verified that the differential event yield calculation
+implemented in Eq.~(\ref{eq:event_yields_calculation}), when extrapolated to a single bin
 covering the full detector acceptance,
@@
 
-The triple integral in  Eq.~(\ref{eq:event_yields}) is evaluated numerically by means
-of Monte Carlo sampling, by generating sampling $N_{\rm mc}$ points in the $\lp x,Q^2,E_{\nu}\rp$ space
-with the constraint that $0 < y = Q^2/2m_N E_{\nu }x <1 $
+The triple integral in  Eq.~(\ref{eq:event_yields_calculation}) is evaluated numerically by means
+of Monte Carlo sampling, by generating  $N_{\rm mc}$
+sampling points in the $\lp x,Q^2,E_{\nu}\rp$ space
+with the constraint that
+\be 
+0 < y \lp = Q^2/2m_N E_{\nu }x\rp <1 \, ,
+\ee
 and then  integrating over the bin range:
-\begin{equation}
-    N_{\rm ev}^{(i)} \approx n_T L_T \frac{(Q^{2(i)}_{\rm max}-Q^{2(i)}_{\rm min})(x^{(i)}_{\rm max}-x^{(i)}_{\rm min})(E_{\rm max}^{(i)}-E_{\rm min}^{(i)})}{N_{\rm mc}}\times \sum_{j=1}^{N_{\rm mc}} \frac{dN_{\nu}(E^{(j)}_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x^{(j)},Q^{2(j)},E^{(j)}_{\nu})}{dxdQ^2}\right) {\cal A}(x^{(j)},Q^{2(j)},E_{\nu}^{(j)}) \, ,
+\bea
+   && N_{\rm ev}^{(i)} \approx n_T L_T \frac{(Q^{2(i)}_{\rm max}-Q^{2(i)}_{\rm min})(x^{(i)}_{\rm max}-x^{(i)}_{\rm min})(E_{\rm max}^{(i)}-E_{\rm min}^{(i)})}{N_{\rm mc}}\times \nonumber \\&& \sum_{j=1}^{N_{\rm mc}}\lc  \frac{dN_{\nu}(E^{(j)}_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x^{(j)},Q^{2(j)},E^{(j)}_{\nu})}{dxdQ^2}\right) {\cal A}(x^{(j)},Q^{2(j)},E_{\nu}^{(j)})\rc \, ,
     \label{MCintegration}
-\end{equation}
+\eea
 and where $N_{\rm mc}$ is chosen to be large enough such that residual Monte Carlo integration
@@
 %
-  These event yields are computed from Eq.~(\ref{eq:event_yields}) with the only
+As mentioned above, for FLArE we assume that muon neutrinos interacting
+in its fiducial volume will be measured
+by the FASER$\nu$2 spectrometer.
+  %
+These event yields are computed from Eq.~(\ref{eq:event_yields_calculation}) with the only
 requirement that the momentum transfer and the final-state invariant mass are restricted
@@
 production, for those experiments with heavy flavour tagging capabilities.
+%
+We note that, as opposed to the number of interacting neutrinos
+computed in~\cite{Feng:2022inv}, we now account for the 
+detector acceptance listed in  Table~\ref{tab:FPF_experiments}.
 
@@
 
-Eq.~(\ref{eq:event_yields}) can be generalised to charm-production events, with
+Eq.~(\ref{eq:event_yields_calculation}) can be generalised to charm-production events, with
 the only difference being that now the neutrino scattering cross-section is restricted
@@
 \label{eq:event_yields_charm}
-  N_{\rm ev,c}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma^{\nu N \to \ell + c+X}(x,Q^2,E_{\nu})}{dxdQ^2}\right) dQ^2 dx dE_{\nu} \,
+  N_{\rm ev,c}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma^{\nu N \to \ell + c+X}(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, ,
   \ee
-  with the charm production cross-sections discussed in~\cite{Faura:2020oom}
+  with charm production cross-sections discussed in~\cite{Faura:2020oom}
   and references therein.
   %
+   Here we neglect efficiency and acceptance effects associated to $D$-meson
+ tagging, which can only be properly estimated by means
+ of a full detector simulation.
+ %
+ The acceptance correction ${\cal A}(x,Q^2,E_{\nu})$ in Eq.~(\ref{eq:event_yields_charm})
+ applies only to the charged leptons and hence is the same as in
+ the inclusive case.
+
   Detectors without charm-tagging capabilities can still be sensitive to charm production via
@@
  of charm production events by a factor of 10 as compared to reconstructing the dimuon final state.
- %
- Here we neglect finite acceptance effects, which can only be properly estimated by means
- of a full detector simulation.
 
@@
     \includegraphics[width=0.495\textwidth]{plots/FPF-FASERv.pdf}
+    \includegraphics[width=0.495\textwidth]{plots/FPF-SND.pdf}
     \includegraphics[width=0.495\textwidth]{plots/FPF-FASERv2.pdf}
     \includegraphics[width=0.495\textwidth]{plots/FPF-FLArE100.pdf}
-	\includegraphics[width=0.495\textwidth]{plots/FPF-SND.pdf}
-	\caption{\small The event yields per bin $N_{\rm ev}^{(i)}$, for muon neutrinos at the FASER$\nu$(2)
-	and AdvSND detectors, and electron neutrinos the FLArE detector, restricted to the DIS region defined 
-	by Eq.~(\ref{eq:DISconditions}).
+    \caption{\small The event yields per bin, $N_{\rm ev}^{(i)}$, for muon neutrinos at the
+      FASER$\nu$, SND@LHC (upper panels), FASER$\nu$2, and FLArE (bottom panels) experiments.
       %
-	Adding up all the bins in this plot results into the $N_{\nu_\mu}$ value listed in
+      Selected events are restricted to the DIS region Eq.~(\ref{eq:DISconditions}).
+      %
+      Only bins with $\ge 30$ events are retained.
+	%
+	Adding up the bins in each of the panels results into the numbers listed in
 	Table~\ref{tab:integrated_rates}.}

### 2023-07-17 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

@@
  event yields per bin,  Eq.~(\ref{eq:event_yields}),
-  for muon neutrinos detected at FASER$\nu$2 restricted
-  to the DIS region defined by Eq.~(\ref{eq:DISconditions}).
+ for muon neutrinos detected at the
+ FASER$\nu$, SND@LHC, FASER$\nu$2, and FLArE  experiments,
+ restricted
+ to the DIS region defined by Eq.~(\ref{eq:DISconditions})
+ and where only bins with $\ge 30$ events are retained.
  %
-  We present results binned in $x$ and $Q^2$ and integrated over all available neutrino energies.
-  %
-  The red dot indicates the weighted center of each bin.
-  %
-  Adding up all bin entries results into the $N_{\nu_\mu}$ value
-  for reconstructed muon
-  neutrinos listed in
+ Adding up the bins in each of the panels results into the numbers listed in
  Table~\ref{tab:integrated_rates}.
  %
-  Only bins with at least 30 events are retained, to ensure the validity of Gaussian
-  statistics.
+ The clear improvement in going frm FASER$\nu$, SND@LHC
+ to the FPF experiments related not only to the number
+ of events but also to the kinematic coverage,
  %
+ For the FPF experiments,m 
  One observes large event rates for most of the region in $\lp x,Q^2\rp$ covered,
-  leading to typical statistical uncertainties at the 1\% level or smaller.
+ leading to typical statistical uncertainties at the 1\% level or smaller,
+ while for FASER$\nu$, SND@LHC statistical uncertainties are much larger.
 
@@
     \includegraphics[width = 0.9\textwidth]{plots/Kin_nNNPDF30_EIC_FPF.pdf}
-    \caption{The kinematic coverage of FASER$\nu$2 in the $(x,Q^2)$ plane,
-      same as  Fig.~\ref{fig:fasernu2_muon},
+    \caption{The kinematic coverage in the $(x,Q^2)$ plane
+      of muon neutrino scattering
+      at FASER$\nu$2, FLArE,
+      and AdvSND (see also Fig.~\ref{fig:fasernu2_muon})
       compared to that of electron-ion collisions

### 2023-07-17 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

@@
  %
- The clear improvement in going frm FASER$\nu$, SND@LHC
- to the FPF experiments related not only to the number
- of events but also to the kinematic coverage,
+ The clear improvement in going from the current FASER$\nu$ and SND@LHC
+ experiments to the FPF ones is visible both in terms
+ of the number
+ of events per bin as well as for the kinematic coverage.
  %
- For the FPF experiments,m 
- One observes large event rates for most of the region in $\lp x,Q^2\rp$ covered,
+ The FPF experiments benefit from large
+ event rates for most of the region in $\lp x,Q^2\rp$ covered,
  leading to typical statistical uncertainties at the 1\% level or smaller,
- while for FASER$\nu$, SND@LHC statistical uncertainties are much larger.
+ while for FASER$\nu$, SND@LHC statistical uncertainties are much larger due
+ to the reduced event rates.
 
@@
 Fig.~\ref{fig:fasernu2_muon} indicates
-how the kinematic coverage of FASER$\nu$2 reaches
-$x_{\rm min}\sim 3\times 10^{-3}$ at small-$x$ and $Q^2_{\rm max}\sim 2\times 10^3$
+how the kinematic coverage of the FPF far-forward experiments reaches
+$x_{\rm min}\sim \times 10^{-3}$ at small-$x$ and $Q^2_{\rm max}\sim 2\times 10^3$
 at large-$Q^2$, representing an extension
@@
 Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF} compares
-the kinematic coverage of FASER$\nu$2 with that of electron-ion collisions
+the kinematic coverage of FASER$\nu$2, FLArE, and AdvSND with that of electron-ion collisions
 at the upcoming EIC~\cite{Khalek:2021ulf,AbdulKhalek:2021gbh}
@@
 determination~\cite{AbdulKhalek:2022fyi}.
+%
+The LHC neutrino experiments cover the region $x\gsim 10^{-3}$ relevant
+for precision electroweak measurements at the LHC, such as the $W$-boson
+mass, and for new physics measurements sensitive to the large-$x$ quarks
+and antiquarks in the proton.
 
@@
 
-The event yields displayed in Fig.~\ref{fig:fasernu2_muon} for FASER$\nu$2, and the corresponding
-calculations for the other experiments listed in Table~\ref{tab:FPF_experiments},
-determine the associated statistical uncertainty in each bin
+The event yields displayed in Fig.~\ref{fig:fasernu2_muon} 
+determine the associated statistical uncertainty in each bin by means of
 \be
@@
 Since we discard bins with less than 30 events, the fractional statistical uncertainty
-ranges between $\lsim 1\%$ and $\sim 18\%$ for muon neutrinos in
-the case of FASER$\nu$2 depending on the values of
+ranges between $\lsim 1\%$ and $\sim 18\%$, depending on the values of
 $x$ and $Q^2$ associated to this bin.
@@
 to the same event yields as in
-Fig.~\ref{fig:fasernu2_muon}
-now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$.
+Fig.~\ref{fig:fasernu2_muon} for FASER$\nu$2
+now as a function of $x$ after having integrated the event
+yields in the range $Q^2 \in [10,100]$ GeV$^2$.
 %
@@
 Except for the bins with the smallest values of $x$, statistical uncertainties indeed
-are at the percent level for FASER$\nu$2.
+are at the percent level or smaller for FASER$\nu$2.
 
@@
 
-For each possible source of experimental systematic uncertainty, we therefore need to
+For each source of experimental systematic uncertainty we need to
 quantify its impact at the event yield level.
 %
-In order to determine these bin-by-bin systematic uncertainties,
+In order to determine these bin-by-bin systematic errors,
 we extend the calculation delineated in Eq.~(\ref{sec:pseudo-data_generation}) as follows.
 %
-Let us consider for illustrative purposes the FASER${\nu}$2 case.
+Let us consider for illustrative purposes the FASER${\nu}$2 detector.
 %
-From Table~\ref{tab:FPF_experiments}, one reads that the detector
-acceptance and reconstruction performance is specified by:
+From Table~\ref{tab:FPF_experiments} we know that its
+acceptance and reconstruction performance are specified by:
 \bea
-E_\ell \ge 100~{\rm GeV} \, , \quad \theta_\ell \le \tan^{-1}(0.5)\, , \qquad \nonumber\\
+E_\ell \ge 100~{\rm GeV} \, , \quad \theta_\ell \le \tan^{-1}(0.025)\, , \qquad\\
 \delta E_\ell \sim 30\% \, 
  \quad \delta E_h \sim 30\% \, ,
- \ \, , \quad \delta\theta_\ell \sim 1~{\rm mrad} \, . 
+ \quad \delta\theta_\ell \sim 0.06~{\rm mrad} \, . 
 \label{eq:fasernu2systematic_errors}
@@
 %
-By integrating over this sample by means of Eq.~(\ref{MCintegration}) we determine
+By integrating over this sample by means of Eq.~(\ref{MCintegration}), we determine
 the binned event yields for this reference $\mathcal{D}_0$ sample.
@@
 %
-We take the uncertainty to be the absolute difference between the mean number of events in the bin for the smeared samples samples, ${\overline{N}}^{(i)}~$ and$~ N_{\rm ev}^{(i)}$ as calculated from Eq.
-\ref{MCintegration}, {\it{i.e.}}  $\delta N^{(i)} = |{\overline{N}}^{(i)} -N_{\rm ev}^{(i)}|$ .
+We take the uncertainty associated
+to a given systematic source, say $\delta E_\ell$,
+to be the absolute difference between the mean number of events in this
+bin evaluated for the smeared samples samples and the
+central prediction for the number of events
+$ N_{\rm ev}^{(i)}$ as calculated from Eq.~(\ref{MCintegration}):
+\be
+\delta_{\rm sys}^{(E_\ell)} N^{(i)} = \Big| \la {N}^{(i)}\ra_{E_\ell-{\rm smeared}} -N_{\rm ev}^{(i)}\Big| \, .
+\ee
+Systematic errors are treated as uncorrelated among them and hence
+by producing samples where only one source of error is varied at a time
+we can determine the systematic errors, Eq.~(\ref{eq:event_yields_systematic_error}), in each bin.
 %
-Furthermore, 
-since the systematic errors are treated as uncorrelated among them,
-by producing samples where only one source of error is varied at a time
-we can determine the systematic errors Eq.~(\ref{eq:event_yields_systematic_error}) in each bin.
+This approach has the benefit that rescaling individual sources of systematic
+uncertainties, say to assess the impact of improved detector performance,
+are straightforward.
 

### 2023-07-17 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

@@
 uncertainties, say to assess the impact of improved detector performance,
-are straightforward.
+is straightforward.
 
@@
 displays the systematic uncertainties associated
-to $E_\ell$, $\theta_\ell$, and $E_h$.
-in the  measurements
+to $E_\ell$, $\theta_\ell$, and $E_h$ variations
+for the  measurements
 of the double-differential
@@
 %
-The same procedure is adopted for all the experiments listed in Table~\ref{tab:FPF_experiments}.
+Fig.~\ref{fig:error_plot_FASERv2_14} (central and right panels) display
+ the integrated event yields for FASER$\nu$2 as a function of $x$ for only
+ systematic errors and for the sum in quadrature of statistical and systematic errors.
+ %
+ For most of the bins, for the baseline performance assumptions the total systematic
+ uncertainty is at the $10\%$ and dominates over the statistical uncertainties.
 
 %-----------------------------------------------------------------------
-\begin{figure}[!ht]
+\begin{figure}[t]
   \centering
@@
 \be
-   {\rm cov}_{ij} = \delta_{ij} \lp \delta_{\rm stat}  N_{\rm ev}^{(i)}\rp^2
-   + \lp \delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} \rp \lp \delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(j)} \rp 
-   + \lp \delta_{\rm sys}^{(E_h)} N_{\rm ev}^{(i)} \rp \lp\delta_{\rm sys}^{(E_h)} N_{\rm ev}^{(j)}\rp 
-   + \lp \delta_{\rm sys}^{(\theta_\ell)} N_{\rm ev}^{(i)} \rp
-   \lp \delta_{\rm sys}^{(\theta_\ell)} N_{\rm ev}^{(j)} \rp
-   \, ,\qquad
- \nonumber
- \ee
- for $i,j=1,\ldots,N_{\rm bin}$, and the same for the associated correlation
+\label{eq:covmat_definition}
+   {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
+   + \sum_{k=1}^{n_{\rm sys}}\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp \lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(j)} \rp
+   \, ,\qquad i,j=1,\ldots,N_{\rm bin} \, ,
+ \ee
+  and the same for the associated correlation
  matrix of the measurement
@@
  independent of the considered observable and would also apply
- for the double-differential cross-sections Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) which are related to the event yields by a constant factor.
-
- One should emphasize that in a real experiment the actual covariance matrix will be
- composed by a much larger number of uncertainty sources, with typical
+ for the double-differential cross-sections Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) which are related to the event yields by a constant prefactor.
+ %
+
+ Eq.~(\ref{eq:covmat_definition}) assumes that each source of systematic
+ uncertainty is 100\% correlated across all the bins of the measurement.
+ %
+ In the real experiment, the actual covariance matrix will be
+ composed by a large number of uncertainty sources, with typical
   HERA and LHC precision measurements characterised by up to hundreds
@@
  In particular, the assumption that a single source of systematic error, say $\delta E_\ell$,
- is fully correlated among all the bins in $(x,Q^2)$ is likely not to be realistic.
- %
- For this reason, here we present impact results both for the nominal correlation model,
- for the case where systematic and statistical uncertainties are added in quadrature,
- and intermediate scenarios.
-
- Fig.~\ref{fig:error_plot_FASERv2_14} (central and right panels) display
- the integrated event yields for FASER$\nu$2 as a function of $x$ for only
- systematic errors and for the sum in quadrature of statistical and systematic errors.
- %
- For most of the bins, for the baseline performance assumptions the total systematic
- uncertainty is at the $10\%$ and dominates over the statistical uncertainties.
-
- \subsection{Pseudo-data generation and impact on PDFs}
+ is fully correlated among all the bins in $(x,Q^2)$ is unlikely to be accurate.
+ %
+ For this reason, here we neglect bin-by-bin correlations
+ and add in quadrature statistical and systematic errors
+ \be
+\label{eq:covmat_definition_v2}
+ {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
++ \delta_{ij}\sum_{k=1}^{n_{\rm sys}} \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp^2
+\, ,\qquad i,j=1,\ldots,N_{\rm bin} \, .
+\ee
+In Eq.~(\ref{eq:covmat_definition_v2}) we have introduced a parameter $f_{\rm red}^{(k)}\le 1$
+that gauges the impact of a possible reduction of the $k$-th systematic error
+as compared to the default experiment performance.
+%
+In Sect.~\ref{sec:protonPDFs} we present results for different scenarios
+for the systematic uncertainty reduction $f_{\rm red}^{(k)}$.
+
+ \subsection{Pseudo-data generation and inclusion on PDF fits}
 
  In order to generate pseudo-data for double-differential
- neutrino scattering cross-sections at the LHC, we follow the procedure
+ LHC neutrino scattering cross-sections, we follow the procedure
  used for the HL-LHC PDF projections of~\cite{AbdulKhalek:2018rok} which was

### 2023-07-17 paper/sec-dis-pseudodata.tex
sect 2 revised

@@
  LHC neutrino scattering cross-sections, we follow the procedure
- used for the HL-LHC PDF projections of~\cite{AbdulKhalek:2018rok} which was
+ used for the HL-LHC projections of~\cite{AbdulKhalek:2018rok} which was
  also adopted in~\cite{Ethier:2021ydt} and~\cite{Greljo:2021kvv} for SMEFT impact projections
@@
  %
- The starting point are the predictions for the differential neutrino scattering
- cross-section
+ The starting point are predictions for inclusive and charm-tagged
+ differential neutrino scattering cross-section, denoted generically by
  \be
@@
  \ee
- with $(x_i,Q^2_i,y_i)$ being the corresponding bin centers.
+ with $(x_i,Q^2_i,y_i)$ labeling the corresponding bin centers.
  %
- The observables $\mathcal{O}_i $ are evaluated using {\sc\small YADISM} and {\sc\small PineAPPL}
- as described in Sect.~\ref{sec:settings}.
+ The observables $\mathcal{O}_i $ in Eq.~(\ref{eq:theory_dis_projections})
+are evaluated with the
+{\sc\small YADISM}~\cite{yadism,Candido:2023utz} program
+interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss, christopher_schwan_2023_7995675}
+to return a fast interpolation grid admitting a generic PDF input,
+and with DGLAP evolution effects provided by {\sc\small EKO}~\cite{Candido:2022tld}.
 %
- An important point here is the choice of PDF set entering the evaluation of
- the observable in Eq.~(\ref{eq:theory_dis_projections}): it should be consistent
- with that of the fitting framework used to assess their impact on the (n)PDFs.
+PDF evolution and DIS structure functions account for NLO QCD corrections
+and target mass effects.
+%
+No higher-twists corrections are included.
+%
+Charm structure functions are evaluated in the FONLL general-mass variable-flavour-number
+scheme~\cite{Forte:2010ta,Ball:2011mu,Faura:2020oom} at $\mathcal{O}\lp \alpha_s\rp$
+accuracy.
+%
+For the proton PDF fits we assume a free isoscalar target $N$, while
+for the nuclear PDF one we allow for deviations from isoscalarity.
+
+The PDF set and other theory settings, such as the perturbative
+order and heavy quark scheme, adopted for the evaluation of
+Eq.~(\ref{eq:theory_dis_projections}) should be the same as those
+used in the fitting framework assessing their impact.
 %
@@
  %
- In order words, the generated pseudo-data should be fully consistent with the prior PDF
- set used as baseline, else one is introducing artificially inconsistencies which
- compromise the validity of the projection studies.
+This ensures that the generated pseudo-data is consistent with the prior PDF
+ set used as baseline and avoids introducing artificial inconsistencies 
+ compromising the validity of the projection studies.
 
- The central values for the LHC neutrino scattering pseudo-data, denoted
+ The central values for the pseudo-data, denoted
  by $\mathcal{O}_i^{{\rm (exp)}} $, are obtained
- by fluctuating this reference theory prediction by the statistical and systematic
- uncertainties, that is
- \begin{equation}
-  \label{eq:pseudo_data}
-  \mathcal{O}_i^{{\rm (exp)}}
-  =   \mathcal{O}_i^{{\rm (th)}}\left( 1+ r_{i} \delta_{i}^{\rm stat}
-  + \sum_{k=E_\ell, E_h,\theta_\ell}
-    r'_{k} \,\delta_{i,k}^{{\rm sys}}\right) \, , \qquad i=1,\ldots,N_{\rm bin} \, ,
- \end{equation}
- with $r_{i}$ and $r'_{k}$ being univariate Gaussian random numbers,
- and $\delta_i^{\rm stat}$ ($\delta_{i,k}^{\rm sys}$) indicate the relative statistical (systematic)
- uncertainties associated to the $i$-th bin (and $k$-th source of systematic uncertainty).
- %
- Note that a given systematic variation is assumed to be fully correlated among all the bins
- in the measurement.
-
- Alternatively, we can add all uncertainties in quadrature and account for a possible
- improvement in the systematic errors with respect to the current estimates,
- \be
- \delta_{i}^{\rm tot}
- = \left( \left( \delta_i^{\rm stat}\right)^2 + \sum_{k=1}^{n_{\rm sys}}
-\left( \delta_{i,k}^{\rm sys} \right)^2\right)^{1/2} \, ,
- \ee
- and the pseudo-data is evaluated by means of
+ by fluctuating the reference theory prediction Eq.~(\ref{eq:theory_dis_projections})
+ by the corresponding statistical and systematic
+ uncertainties,
  \begin{equation}
@@
     \right) \,
-    , \qquad i=1,\ldots,N_{\rm bin} \, .
+    , \qquad i=1,\ldots,N_{\rm bin} \, ,
  \end{equation}
- While the actual correlation model will lie somewhere between no correlation and full correlation,
- these two approaches to generate the pseudo-data bracket the projected impact
- on the PDFs and its dependence on the experimental correlation model.
+ where the total experimental uncertainty is the sum in quadrature of
+ statistical and systematic errors, accounting for a possible reduction
+ factor in the latter,
+  \be
+ \delta_{i}^{\rm tot}
+ = \left( \left( \delta_i^{\rm stat}\right)^2 + \sum_{k=1}^{n_{\rm sys}}
+ \left( f_{\rm red}^{(k)} \delta_{i,k}^{\rm sys} \right)^2\right)^{1/2} \, ,
+ \qquad i=1,\ldots,N_{\rm bin} \, ,
+ \ee
+ and with $r_{i}$ being univariate Gaussian random numbers.
+ %
+ The pseudo-data generated by means of Eq.~(\ref{eq:pseudo_data_v2}),
+ together with the corresponding covariance matrix
+  \be
+\label{eq:covmat_definition_v2}
+ {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)} \mathcal{O}_i^{\rm (th)} \rp^2
+ + \delta_{ij}\sum_{k=1}^{n_{\rm sys}}
+ \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} \mathcal{O}_i^{\rm (th)} \rp^2
+\, ,\qquad i,j=1,\ldots,N_{\rm bin} \, ,
+\ee
+define then the inputs of the subsequent proton and nuclear PDF determination.
 
-In this section, we describe the analysis settings adopted to quantify
-the impact of LHC neutrino measurements on the proton and nuclear PDFs.
-%
-First of all, we discuss the calculation of inclusive and charm structure functions
-and their interpolation in terms of fast grids. 
-%
-Second, we review the Hessian profiling framework and how it is applied
-in this work to proton and nuclear PDFs.
-%
-Third, we indicate the implementation of the LHC neutrino pseudo-data in the
-NNPDF framework and the settings of the subsequent global PDF analysis.
-
-The procedure described in Sect.~\ref{sec:dis_pseudodata} returns
-$N_{\rm bin}$ bins of LHC neutrino pseudo-data $\mathcal{O}_i^{{\rm (exp)}}$, Eq.~(\ref{eq:pseudo_data}), covering the $(x,Q^2,E_\nu)$ kinematic region accessible by the experiment,
-together with the associated statistical and systematic uncertainties.
-%
-The calculation of this pseudo-data relies on the corresponding set of
-theoretical predictions for the same observables $\mathcal{O}_i^{{\rm (th)}}$,
-Eq.~(\ref{eq:theory_dis_projections}).
-%
-Here we evaluate inclusive and charm DIS structure functions with the
-{\sc\small YADISM}~\cite{yadism,Candido:2023utz} program
-interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss, christopher_schwan_2023_7995675}
-to return a fast interpolation grid admitting a generic PDF input.
-%
-DGLAP evolution effects between the scale $Q_0$ at which PDFs are evaluated
-and the data scale $Q$ are provided by {\sc\small EKO}~\cite{Candido:2022tld}.
-
-The resulting {\sc\small PineAPPL} grids provide a fast evaluation
-of Eq.~(\ref{eq:theory_dis_projections}) for an arbitrary choice of the
-input PDFs at the initial scale $Q_0$, with the latter accessed via their
-{\sc\small LHAPDF} interface~\cite{Buckley:2014ana}.
-%
-Whenever pseudo-data is generated, it is crucial to adopt common inputs with
-the subsequent PDF analysis.
-%
-For instance, if one aims to include the LHC neutrino data into the NNPDF4.0
-NNLO determination, $\mathcal{O}_i^{{\rm (th)}}$ must be evaluated also at NNLO
-and also using
-NNPDF4.0 as input for consistency, else artificial tensions between theory
-and data would be introduced during the fit biasing the results.
-
-By means of this theoretical pipeline, predictions for
-DIS inclusive structure functions on an isoscalar target $N$ are computed
-using
-\be
-\label{eq:neutrino_DIS_xsec}
-\frac{d^2\sigma^{\nu N}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\nu N}_2(x,Q^2) - y^2F^{\nu N}_L(x,Q^2) +Y_- xF^{\nu N}_3(x,Q^2)\rc  \, ,
-\ee
-with an analogous formula for antineutrino scattering with the sign of $xF_3$ flipped.
-%
-A {\sc\small PineAPPL} interpolation grid for
-Eq.~(\ref{eq:neutrino_DIS_xsec}) is evaluated at the $(x,Q^2,E_\nu)$ bins
-for which pseudo-data is generated using DGLAP evolution and coefficient
-functions at $\mathcal{O}\lp \alpha_s^2\rp$ and accounting for target mass effects.
-%
-No higher-twists corrections to the structure functions are included, since we cut
-data with $W^2 \ge 12.5$ GeV in order to suppress them.
-%
-Deviations from isoscalarity and nuclear modifications with respect
-to a free isoscalar target are accounted for at the input PDF level,
-leaving the grid entering the evaluation of Eq.~(\ref{eq:neutrino_DIS_xsec}) unchanged.
-%
-No heavy quark mass effects are considered for at the level of these inclusive structure functions.
-
-Concerning charm structure functions, for experiments with charm tagging
-capabilities theoretical predictions are evaluated for
-\be
-\label{eq:neutrino_DIS_xsec}
-\frac{d^2\sigma^{\nu N}_c(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F_{2,c}^{\nu N}(x,Q^2) - y^2F^{\nu N}_{L,c}(x,Q^2) +Y_- xF^{\nu N}_{3,c}(x,Q^2)\rc  \, ,
-\ee
-with the DIS charm structure functions evaluated in the FONLL general-mass variable-flavour-number
-scheme~\cite{Forte:2010ta,Ball:2011mu,Faura:2020oom} in order to account for charm mass effects.
-%
-Eq.~(\ref{eq:neutrino_DIS_xsec}) is computed with $\mathcal{O}\lp \alpha_s^2\rp$ massless
-coefficient functions and $\mathcal{O}\lp \alpha_s\rp$ massive ones, given
-that the $\mathcal{O}\lp \alpha_s^2\rp$ massive calculation~\cite{Gao:2017kkx} is not publicly available.
-%
-Nevertheless, the $\mathcal{O}\lp \alpha_s\rp$ massive coefficient functions
-encapsulate the dominant charm mass dependence of the double differential
-cross-section.
-%
-We assume 100\% efficiency in charm tagging and do not impose acceptance cuts on the charm
-quark or $D$-meson kinematics (the only acceptance requirements are applied to the final-state
-charged lepton, as indicated in  Table~\ref{tab:FPF_experiments}).
-
-We note that experiments without charm-tagging capabilities can still identify charm production
-events by means of the dimuon final state,
-\be
-\nu + N \to \mu^+ + c~(\to D) + X \to \mu^+ + \mu^- +X \, ,
-\ee
-by profiting from the semileptonic decays of the $D$-meson leading
-to the characteristic signature of two opposite-sign muons.
-%
-In this case, the  differential charm production cross-section Eq.~(\ref{eq:neutrino_DIS_xsec})
-must be accompanied by the corresponding branching ratio
-\be
-\frac{d^2\sigma^{\nu N}_c(x,Q^2,y)}{dxdy}\mathcal{B}\lp c \to D \to \mu + X\rp \, ,
-\ee
-which given that $\mathcal{B}\sim 10\%$ suppresses the reconstructed charm
-production event yields by around an order of magnitude.
-%
-For experiments reconstructing the dimuon final state,
-we also apply the muon acceptance criteria to both muons.
-
-In this work we consider two complementary approaches in order to assess the
+We consider two complementary approaches to assess the
 impact of LHC neutrino data on the proton and nuclear PDFs.
 %
-On the one hand, the Hessian profiling of a prior proton or
-nuclear PDF set, which here are taken to be PDF4LHC21~\cite{PDF4LHCWorkingGroup:2022cjn} and
+First, the Hessian profiling\cite{Paukkunen:2014zia, Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre} of prior proton and
+nuclear PDF sets, taken to be PDF4LHC21~\cite{PDF4LHCWorkingGroup:2022cjn} and
 EPPS21~\cite{Eskola:2021nhw} respectively.
 %
-On the other hand, the inclusion of the LHC neutrino structure functions
-on the NNPDF global analysis framework~\cite{NNPDF:2021uiq,NNPDF:2021njg}.
+Second, the direct inclusion 
+in the NNPDF global analysis framework~\cite{NNPDF:2021uiq,NNPDF:2021njg}.
 %
-Here we summarise the details of the Hessian profiling procedure and
-outline how it is applied in our work.
-
-The profiling method applied to Hessian PDF fits is described in~\cite{Paukkunen:2014zia, Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre} and is based
+The profiling method applied to Hessian PDF fits is based
 on minimizing a goodness-of-fit error function defined as
@@
      \right)^2
-     }{ \left(\delta_i^{\rm stat}\right)^2 }
+     }{ \left(\delta^{{\rm (stat)}}\mathcal{O}_i^{\rm (th)}\rp^2 }
 + \sum_\alpha \lp b_\alpha^{(\textrm{pd})}\rp^2
-+ \sum_\beta  \lp b_\beta^{\textrm{(th)}}\rp ^2 \, .
++ \sum_\beta  \lp b_\beta^{\textrm{(th)}}\rp ^2 \, ,
 \label{eq:profilingchi2}
 \end{equation}
-The pseudodata 
-$\mathcal{O}_i^{\rm (exp)}$ 
-is obtained from the central theoretical prediction 
-$\mathcal{O}_i^{(\textrm{th})}$
-for each bin $i$ out of $N_{\textrm{bin}}$ by fluctuating
-it within its uncertainties, following either
-Eq.~(\ref{eq:pseudo_data}), when accounting for the correlations
-between systematic uncertainties, or Eq.~(\ref{eq:pseudo_data_v2}),
-in the case in which errors are added in quadrature.
+with the pseudodata 
+$\mathcal{O}_i^{\rm (exp)}$ defined in  Eq.~(\ref{eq:pseudo_data_v2}).
+%
+The correlated uncertainties for the pseudodata and for the theoretical prediction 
+are contained in the nuisance parameter vectors $b^{(\textrm{pd})}$ and $b^{(\textrm{th})}$, respectively, and the total uncorrelated uncertainty is $\delta^{{\rm (stat)}}\mathcal{O}_i^{\rm (th)}$.
 
-The correlated uncertainties for the pseudodata and for the theoretical prediction 
-are contained in the nuisance parameter vectors $b^{(\textrm{pd})}$ and $b^{(\textrm{th})}$, respectively, and the total uncorrelated uncertainties are denoted by $\delta_{{\rm stat},i}$.
-%
 The effect of the nuisance parameters
@@
 
-The profiling studies carried out in this work are performed using v2.2.1 of the \textsc{xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}.
+The profiling studies carried out in this work are performed using version 2.2.1
+of the 
+{\sc\small xFitter} open-source QCD analysis framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}.
 %
@@
 from the {\sc\small xFitter} repository.
+%
+A tolerance factor $T = \sqrt{\Delta \chi^2}=3$ is adopted for the proton
+PDF profiling, corresponding approximately to the average tolerance
+used in the CT18~\cite{Hou:2019efy} and MSHT20~\cite{Bailey:2020ooq} determinations,
+the two Hessian sets entering the PDF4LHC21 combination.
+%
+The same choice was adopted in the HL-LHC projections of~\cite{AbdulKhalek:2018rok},
+and a common value is used for the Hessian profiling of EPPS21.
+
+Concerning the inclusion of the LHC far-forward neutrino pseudo-data
+in the NNPDF proton analysis framework, we follow the procedure
+outlined in~\cite{NNPDF:2021uiq}.
+%
+Fast interpolation tables (FK-tables)~\cite{Ball:2010de} combining {\sc\small EKO}
+DGLAP evolution with {\sc\small YADISM} DIS coefficient functions
+are computed using {\sc\small PineAPPL}, see also~\cite{Barontini:2023vmr}.
+%
+Predictions for the observables Eq.~(\ref{eq:theory_dis_projections}) are evaluated
+with NNPDF4.0 NNLO for various choices of input datasets, and included
+directly in the same alongside all other DIS datasets.
+%
+We verify that in all cases $\chi^2/n_{\rm dat}\sim 1$ after the fit,
+as expected given the built-in consistency between the prior PDF fit
+and the generated pseudo-data.

### 2023-07-19 paper/sec-protonPDFs.tex
sect 2 revised
added nnpdf plot

@@
-\clearpage
 \section{Constraints on proton structure}
@@
 of the results with respect to its different inputs, such as charm-tagged structure functions.
-%
-A tolerance of $T = \sqrt{\Delta \chi^2}=3$ is adopted, corresponding to the average tolerance
-used in the CT18 and MSHT20 Hessian determinations.
 %
@@
 Selection of the {\sc\small xFitter} results for the NNPDF case.
+
+Fig.~\ref{fig:nnpdf40_fasernu2_baseline} presents the same comparison
+as in Fig.~\ref{fig:profiling_syst} now for
+ the fits
+ based on the NNPDF4.0 global analysis.
+ %
+ The impact on the PDFs found by direct inclusion of the FPF structure
+ functions on the NNPDF4.0 fit is qualitatively consistent with
+ that found from the Hessian profiling of PDF4LHC21.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.99\textwidth]{plots/FASERnu2-q100gev-ratios.pdf}
+\caption{
+  Same as Fig.~\ref{fig:profiling_syst} now for the fits
+  based on the NNPDF4.0 global analysis.
+%
+}
+\label{fig:nnpdf40_fasernu2_baseline}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-07-19 paper/scripts/PDFs.py

@@ -14,7 +14,7 @@ import scipy
 from scipy.integrate import dblquad
 
 print("\n *********************************************************")
-print("      Charm asymmetry                               ")
+print("      Impact of FPF data                               ")
 print(" ***********************************************************\n")
 
 q = 100 # GeV
@@ -37,7 +37,7 @@ nset=2
 nrep=np.zeros(nset, dtype='int')
 nrep_max = 1000
 
-pdfset=["210713-n3fit-001","NNPDF_FASERV2"]
+pdfset=["230309-ern-002","230718-jcmwfaser-001"]
 
 for iset in range(nset):
 
@@ -71,25 +71,25 @@ for iset in range(nset):
             for ifl in range(nfl):
 
                 if(ifl==0):
-                    # gluon
-                    if(iset==0):
-                        fit1[i-1][ifl][k] = p.xfxQ(0,x,q)
-                    if(iset==1):
-                        fit2[i-1][ifl][k] = p.xfxQ(0,x,q) 
-
-                elif(ifl==1):
                     # uV
                     if(iset==0):
                         fit1[i-1][ifl][k] = p.xfxQ(2,x,q) - p.xfxQ(-2,x,q)
                     if(iset==1):
                         fit2[i-1][ifl][k] = p.xfxQ(2,x,q) - p.xfxQ(-2,x,q)
 
-                elif(ifl==2):
+                elif(ifl==1):
                     # dV
                     if(iset==0):
                         fit1[i-1][ifl][k] = p.xfxQ(1,x,q) - p.xfxQ(-1,x,q)
                     if(iset==1):
                         fit2[i-1][ifl][k] = p.xfxQ(1,x,q) - p.xfxQ(-1,x,q)
+
+                elif(ifl==2):
+                    # gluon
+                    if(iset==0):
+                        fit1[i-1][ifl][k] = p.xfxQ(0,x,q)
+                    if(iset==1):
[…]

### 2023-07-28 paper/sec-dis-pseudodata.tex
Start improving kinematic plots
Update kinematic plots

@@
 	Adding up the bins in each of the panels results into the numbers listed in
-	Table~\ref{tab:integrated_rates}.}
+	Table~\ref{tab:integrated_rates}.
+	\textcolor{red}{(To be replaced with the results from the new fluxes, SND $\to$ AdvSND)}}
     \label{fig:fasernu2_muon}
@@
     \centering
-    \includegraphics[width = 0.9\textwidth]{plots/Kin_nNNPDF30_EIC_FPF.pdf}
+    \includegraphics[width = 0.6\textwidth]{plots/KIN_DIS_FPF.pdf}
     \caption{The kinematic coverage in the $(x,Q^2)$ plane

### 2023-07-28 xFitter/PDF_profiling/PDF4LHC21/statOnly/collectPlots.tex
Updating all xFitter files/directories

@@
 FASERv2\\
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}
 
@@
 \newcommand{\dataset}{_nochargediscrimination}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}
 
@@
 \renewcommand{\dataset}{_inclusive}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}
 
@@
 \renewcommand{\dataset}{_inclusive_nochargediscrimination}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}
 
@@
 \renewcommand{\dataset}{_charm}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}
 
@@
 \renewcommand{\dataset}{_charm_nochargediscrimination}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}
+
+\newpage
+
+FASERv\\
+\renewcommand{\experiment}{FASERv}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}
+
+\newpage
+
+SND\\
+\renewcommand{\experiment}{SND}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}
 

### 2023-07-28 xFitter/PDF_profiling/PDF4LHC21/systVar05/collectPlots.tex
Adding results corresponding to stat-only and all-syst-unc-uncorrelated cases
Updating all xFitter files/directories

--- 2023-06-04 xFitter/PDF_profiling/PDF4LHC21/statOnly/collectPlots.tex
@@
 \newcommand{\experiment}{FASERv2}
-\newcommand{\unctype}{statOnly}
+\newcommand{\unctype}{systVar05}
 
@@
 \renewcommand{\dataset}{_charm_nochargediscrimination}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}
+
+\newpage
+
+FASERv\\
+\renewcommand{\experiment}{FASERv}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}
 

### 2023-07-28 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/prel/FASERv_charm_nu/run.sh

@@ -1,0 +1,29 @@
+# The commands to perform Hessian PDF profiling w/ xFitter, do e.g.
+#    sh run.sh
+
+PDF="EPPS21"  #N.B. or plots only! Change also in parameters.yaml
+PSEUDODATA="charm"
+
+### OPTS w/o/ scaling 95% cl -> 68%, e.g. CT PDFs
+#PLOTOPTS="--asym --therr --bands --q2all --relative-errors"
+
+### OPTS w/ scaling 95% cl -> 68%, needed for EPPS PDFs (like CT)
+#PLOTOPTS="--splitplots-eps  --therr --bands --q2all --relative-errors --scale68 --xrange 1e-6:0.99"
+#scale68 no longer required, using scaling in profiling (parameters.yaml)
+PLOTOPTS="--therr --bands --q2all --relative-errors"
+
+ln -s ../../../../datafiles
+
+# Run xFitter:
+xfitter > log.txt
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:${PDF} profile:output:${PDF}-${PSEUDODATA}
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-07-28 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/statOnly/FASERv/plot.sh

@@ -1,0 +1,25 @@
+DETECTOR="FASER#nu"
+DETSIMPLE="FASERv"
+UNCLVL="statOnly"
+
+DATATXT="Current data"
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-07-28 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/statOnly/FASERv2_nochargediscrimination/plot.sh

@@ -1,0 +1,25 @@
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="statOnly"
+
+DATATXT="Current data"
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT} (CD)" profile:../${DETSIMPLE}/output:"CD+${DETECTOR}" profile:output:"CD+${DETECTOR}, no charge id."
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-07-28 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/syst/FASERv2/plot.sh

@@ -1,0 +1,24 @@
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="syst"
+
+DATATXT="Current data"
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT} (CD)" profile:../../statOnly/${DETSIMPLE}/output:"CD+${DETECTOR}, stat" profile:output:"CD+${DETECTOR}, stat+syst"
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-07-28 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/syst/FASERv2_charm/plot.sh

@@ -1,0 +1,25 @@
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="syst"
+
+DATATXT="Current data"
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-07-28 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/systVar05/FASERv2_inclusive_nochargediscrimination/plot.sh

@@ -1,0 +1,25 @@
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="systVar05"
+
+DATATXT="Current data"
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-07-28 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/systVar05El/FASERv2_nochargediscrimination/plot.sh

@@ -1,0 +1,25 @@
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="systVar05El"
+
+DATATXT="Current data"
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-07-28 xFitter/PDF_profiling/PDF4LHC21/runFinal.sh

@@ -1,0 +1,14 @@
+#!/bin/bash
+declare -a dirs=("statOnly" "syst" "systVar05" "systVar05El" "uncor")
+
+for dir in ${dirs[@]}; do
+    cd ${dir}
+    sh run.sh
+    cd ..
+done
+
+for dir in ${dirs[@]}; do
+    cd ${dir}
+    pdflatex collectPlots.tex
+    cd ..
+done

### 2023-07-28 xFitter/PDF_profiling/PDF4LHC21/statOnly/FASERv/plot.sh

@@ -1,0 +1,26 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter
+#    sh plot.sh
+
+DETECTOR="FASER#nu"
+DETSIMPLE="FASERv"
+UNCLVL="statOnly"
+
+DATATXT="Current data"
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-07-28 xFitter/PDF_profiling/PDF4LHC21/statOnly/FASERv2_charm_nochargediscrimination/plot.sh

@@ -1,0 +1,26 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter
+#    sh plot.sh
+
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="statOnly"
+
+DATATXT="Current data"
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-07-28 xFitter/PDF_profiling/PDF4LHC21/systVar05/FASERv2_nochargediscrimination/plot.sh

@@ -1,0 +1,28 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="systVar05"
+
+DATATXT="Current data"
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-07-28 xFitter/PDF_profiling/PDF4LHC21/systVar05El/FASERv2/plot.sh

@@ -1,0 +1,25 @@
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="systVar05El"
+
+DATATXT="Current data"
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT} (CD)" profile:../../statOnly/${DETSIMPLE}/output:"CD+${DETECTOR}, stat" profile:output:"CD+${DETECTOR}, stat+syst"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-07-28 xFitter/gitAdder.sh

@@ -1,0 +1,133 @@
+#!/bin/bash
+declare -a detectors=("FASERv" "FASERv2")
+declare -a datatypes=("charm" "inclusive")
+declare -a parts=("nu" "nub" "nochargediscrimination")
+declare -a unctypes=("statOnly" "syst" "systVar05" "systVar05El")
+declare -a pdfs=("PDF4LHC21" "EPPS21nlo_CT18Anlo_W184")
+
+datapath=xFitter/datafiles/lhc/fpf/neutrinoDIS/pseudodata
+
+#Navigate to git main directory
+cd ..
+
+for detector in ${detectors[@]}; do
+    for datatype in ${datatypes[@]}; do
+        for part in ${parts[@]}; do
+
+            #Add correlation tables
+            git add ${datapath}/${detector}_${datatype}_${part}.corr
+            git add ${datapath}/${detector}_${datatype}_${part}_onlyEl.corr
+
+            #Add datatables for preliminary runs
+            git add ${datapath}/prel/${detector}_${datatype}_${part}-thexp.dat
+
+            #Add datatables for final runs
+            for pdf in ${pdfs[@]}; do
+                for unctype in ${unctypes[@]}; do
+                    git add ${datapath}/${pdf}/${unctype}/${detector}_${datatype}_${part}-thexp.dat
+                done
+            done
+
+        done
+    done
+done
+
+#Add PDF_profiling files
+profilingpath=xFitter/PDF_profiling
+declare -a xFrunFiles=("constants.yaml" "parameters.yaml" "steering.txt" "plot.sh" "run.sh")
+declare -a xFprelFiles=("constants.yaml" "parameters.yaml" "steering.txt" "run.sh")
+for pdf in ${pdfs[@]}; do
+
+    if [[ ${pdf}=="PDF4LHC21" ]]; then
+        declare -a statOnlyDirs=("FASERv" "FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination")
+        declare -a systDirs=("FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination" )
[…]

### 2023-07-28 paper/sec-dis-pseudodata.tex
Updating paper: remaining xFitter plots (corresponding to pseudodata in main branch on 230728), including tolerance factor T in chi2, listing T values used for PDF4LHC21 and EPPS21 cases and including remarks about 68 vs 90 CL

@@
 + \sum_\alpha \lp b_\alpha^{(\textrm{pd})}\rp^2
-+ \sum_\beta  \lp b_\beta^{\textrm{(th)}}\rp ^2 \, ,
++ T^2 \sum_\beta  \lp b_\beta^{\textrm{(th)}}\rp ^2 \, ,
 \label{eq:profilingchi2}
@@
 The correlated uncertainties for the pseudodata and for the theoretical prediction 
-are contained in the nuisance parameter vectors $b^{(\textrm{pd})}$ and $b^{(\textrm{th})}$, respectively, and the total uncorrelated uncertainty is $\delta^{{\rm (stat)}}\mathcal{O}_i^{\rm (th)}$.
+are contained in the nuisance parameter vectors $b^{(\textrm{pd})}$ and $b^{(\textrm{th})}$, respectively, with $T$ the tolerance factor, and the total uncorrelated uncertainty is $\delta^{{\rm (stat)}}\mathcal{O}_i^{\rm (th)}$.
 
@@
 from the {\sc\small xFitter} repository.
+%%
+%A tolerance factor $T = \sqrt{\Delta \chi^2}=3$ is adopted for the proton
+%PDF profiling, corresponding approximately to the average tolerance
+%used in the CT18~\cite{Hou:2019efy} and MSHT20~\cite{Bailey:2020ooq} determinations,
+%the two Hessian sets entering the PDF4LHC21 combination.
+%The same choice was adopted in the HL-LHC projections of~\cite{AbdulKhalek:2018rok},
+%and a common value is used for the Hessian profiling of EPPS21.
+%%
+For the proton PDF profiling, a tolerance of $T^2 = 10$ is adopted, as in Ref.~\cite{PDF4LHCWorkingGroup:2022cjn}.
+For the Hessian profiling of EPPS21, a value of $T^2 = 33$ is used, following Ref.~\cite{Eskola:2021nhw}.
+Notably, the PDF uncertainties in the earlier (latter) case are given at 68\% (90\%) confidence level.
 %
-A tolerance factor $T = \sqrt{\Delta \chi^2}=3$ is adopted for the proton
-PDF profiling, corresponding approximately to the average tolerance
-used in the CT18~\cite{Hou:2019efy} and MSHT20~\cite{Bailey:2020ooq} determinations,
-the two Hessian sets entering the PDF4LHC21 combination.
-%
-The same choice was adopted in the HL-LHC projections of~\cite{AbdulKhalek:2018rok},
-and a common value is used for the Hessian profiling of EPPS21.
 

### 2023-07-28 paper/sec-nuclearPDFs.tex
Updating paper: remaining xFitter plots (corresponding to pseudodata in main branch on 230728), including tolerance factor T in chi2, listing T values used for PDF4LHC21 and EPPS21 cases and including remarks about 68 vs 90 CL

@@
 
-Fig.~\ref{fig:profiling_baseline_nuclear} displays the same comparisons
-as in Fig.~\ref{fig:profiling_baseline},
-now for the profiling of the EPPS21 global determination of nuclear PDFs,
+Fig.~\ref{fig:profiling_baseline_nuclear} displays the baseline result of the profiling using the EPPS21 global determination of nuclear PDFs,
 specifically of the set with $A=184$ (tungsten target).
@@
 \includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{Same as Fig.~\ref{fig:profiling_baseline},
-now for the profiling of the EPPS21 global determination of nuclear PDFs,
-specifically of the set with $A=184$ (tungsten target).
+\caption{The fractional uncertainties (90\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ of the EPPS21 global determination of nuclear PDFs,
+specifically of the set with $A=184$ (tungsten target), compared to the results of profiling with the FASER$\nu$2 DIS projections.
 %
@@
 %
-The bands indicate the 68\% CL uncertainties.
 }
@@
 \centering
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_s_ratio.pdf}
 \caption{The results of Fig.~\ref{fig:profiling_baseline_nuclear} (red and blue), 

### 2023-07-28 paper/sec-protonPDFs.tex
Updating paper: remaining xFitter plots (corresponding to pseudodata in main branch on 230728), including tolerance factor T in chi2, listing T values used for PDF4LHC21 and EPPS21 cases and including remarks about 68 vs 90 CL

@@
 \centering
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_s_ratio.pdf}
 \caption{
@@
 
-In the following we consider the stability of the results in Fig.~\ref{fig:profiling_baseline}
-with respect to the chosen experiment and integrated luminosity, the modelling of systematic
+In the following, we consider the results obtained using only statistical uncertainties as the baseline, 
+and examine stability of these results with respect to the chosen experiment and integrated luminosity, the modelling of systematic
 uncertainties, being able to identify or not charm production, and being able to tell part outgoing

### 2023-07-31 paper/sec-dis-pseudodata.tex
Update event rates plot
Updating all xFitter plots in paper

@@
     \centering
-    \includegraphics[width = 0.6\textwidth]{plots/KIN_DIS_FPF.pdf}
+    \includegraphics[width = 0.7\textwidth]{plots/KIN_DIS_FPF.pdf}
     \caption{The kinematic coverage in the $(x,Q^2)$ plane
@@
     \centering
-    \includegraphics[width = 0.95\textwidth]{plots/error_plot_FASERv2_14.pdf}
+    \includegraphics[width = \textwidth]{plots/Event_Rate_FASERv2_antineutrino.pdf}
     \caption{Same as Fig.~\ref{fig:fasernu2_muon} for FASER$\nu$2
@@
  \be
+\label{eq:corrmat_definition}
  \rho_{ij} =  \frac{{\rm cov}_{ij}}{\sqrt{ {\rm cov}_{ii} }\sqrt{ {\rm cov}_{jj} } } \, . 
@@
  The pseudo-data generated by means of Eq.~(\ref{eq:pseudo_data_v2}),
- together with the corresponding covariance matrix
-  \be
-\label{eq:covmat_definition_v2}
- {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)} \mathcal{O}_i^{\rm (th)} \rp^2
- + \delta_{ij}\sum_{k=1}^{n_{\rm sys}}
- \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} \mathcal{O}_i^{\rm (th)} \rp^2
-\, ,\qquad i,j=1,\ldots,N_{\rm bin} \, ,
-\ee
+ together with the corresponding correlations, computed according to Eq.s~\eqref{eq:corrmat_definition}--\eqref{eq:covmat_definition_v2},
+%  \be
+%\label{eq:covmat_definition_v2}
+% {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)} \mathcal{O}_i^{\rm (th)} \rp^2
+% + \delta_{ij}\sum_{k=1}^{n_{\rm sys}}
+% \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} \mathcal{O}_i^{\rm (th)} \rp^2
+%\, ,\qquad i,j=1,\ldots,N_{\rm bin} \, ,
+%\ee
 define then the inputs of the subsequent proton and nuclear PDF determination.

### 2023-07-31 paper/sec-protonPDFs.tex
Updating all xFitter plots in paper

@@
 once charm-tagged measurements are removed.
-%
-In both cases, the covariance matrix accounts for systematic uncertainties.
 }
@@
 \caption{
-Same as Fig.~\ref{fig:profiling_syst}, now assessing the impact of that being unable to identify
+Assessing the impact that being unable to identify
 the charge of the outgoing lepton would have on the FASER$\nu$2 reach on the proton PDFs.
-%
-In both cases, the covariance matrix accounts for systematic uncertainties.
 }
@@
 
-{\bf add discussion of experiment sensitivity}
 %
-Same as Fig.~\ref{fig:profiling_syst} comparing FASER$\nu$2 with AdvSND and with FASER$\nu$.
+Fig.~\ref{fig:profiling_experiment_comparison} shows a comparison of the impact 
+that FASER$\nu$2 and FASER$\nu$ pseudodata have in PDF profiling, illustrating 
+the improvement in precision obtainable with FASER$\nu$2.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/experiment_comparison/statOnly_FASERv_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/experiment_comparison/statOnly_FASERv_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/experiment_comparison/statOnly_FASERv_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/experiment_comparison/statOnly_FASERv_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/experiment_comparison/statOnly_FASERv_q2_10000_pdf_s_ratio.pdf}
+\caption{
+A comparison of the effect of FASER$\nu$ and FASER$\nu2$ pseudodata in profiling, 
+assuming only statistical uncertainties in the case of both experiments.
+}
+\label{fig:profiling_experiment_comparison}
+\end{figure}
 

### 2023-07-31 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/cleanFinal.sh

@@ -1,8 +1,9 @@
 #!/bin/bash
-declare -a dirs=("statOnly" "syst" "systVar05" "systVar05El" "uncor")
+declare -a dirs=("statOnly" "syst" "systVar05" "systVar05El")
 
 for dir in ${dirs[@]}; do
+    rm ${dir}/collectPlots.pdf
     cd ${dir}
-    sh clean.sh
+    ./clean.sh
     cd ..
 done

### 2023-07-31 xFitter/PDF_profiling/PDF4LHC21/statOnly/FASERv/plot.sh

@@ -5,12 +5,12 @@ DETECTOR="FASER#nu"
 DETSIMPLE="FASERv"
 UNCLVL="statOnly"
 
-DATATXT="Current data"
+DATATXT="Current data (CD)"
 PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
 
 PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
 mv plots/plots.pdf plots/plots_OLD.pdf
-xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:../FASERv2/output:"CD+FASER#nu2" profile:output:"CD+${DETECTOR}"
 mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
 
 cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 

### 2023-07-31 xFitter/PDF_profiling/PDF4LHC21/statOnly/FASERv2_nochargediscrimination/plot.sh

@@ -5,12 +5,12 @@ DETECTOR="FASER#nu2"
 DETSIMPLE="FASERv2"
 UNCLVL="statOnly"
 
-DATATXT="Current data"
+DATATXT="Current data (CD)"
 PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
 
 PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
 mv plots/plots.pdf plots/plots_OLD.pdf
-xfitter-draw ${PLOTOPTS} output:"Current data (CD)" profile:../FASERv2/output:"${DATATXT}+${DETECTOR}" profile:output:"${DATATXT}+${DETECTOR}, no charge id."
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:../FASERv2/output:"CD+${DETECTOR}" profile:output:"CD+${DETECTOR}, no charge id."
 mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
 
 cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 

### 2023-07-31 xFitter/gitAdder.sh

@@ -79,6 +79,7 @@ for pdf in ${pdfs[@]}; do
         unctype="statOnly"
         git add ${profilingpath}/${pdf}/${unctype}/collectPlots.tex                
         git add ${profilingpath}/${pdf}/${unctype}/run.sh
+        git add ${profilingpath}/${pdf}/${unctype}/clean.sh
         for xFrunFile in ${xFrunFiles[@]}; do
             git add ${profilingpath}/${pdf}/${unctype}/${subDir}/${xFrunFile}        
             git add ${profilingpath}/${pdf}/${unctype}/${subDir}/${unctype}_`echo ${subDir} | sed 's/_.*//'`_q2_10000_pdf_dv_ratio.pdf
@@ -94,6 +95,7 @@ for pdf in ${pdfs[@]}; do
         unctype="syst"
         git add ${profilingpath}/${pdf}/${unctype}/collectPlots.tex                
         git add ${profilingpath}/${pdf}/${unctype}/run.sh
+        git add ${profilingpath}/${pdf}/${unctype}/clean.sh
         for xFrunFile in ${xFrunFiles[@]}; do
             git add ${profilingpath}/${pdf}/${unctype}/${subDir}/${xFrunFile}        
             git add ${profilingpath}/${pdf}/${unctype}/${subDir}/${unctype}_`echo ${subDir} | sed 's/_.*//'`_q2_10000_pdf_dv_ratio.pdf
@@ -109,6 +111,7 @@ for pdf in ${pdfs[@]}; do
         unctype="systVar05"
         git add ${profilingpath}/${pdf}/${unctype}/collectPlots.tex                
         git add ${profilingpath}/${pdf}/${unctype}/run.sh
+        git add ${profilingpath}/${pdf}/${unctype}/clean.sh
         for xFrunFile in ${xFrunFiles[@]}; do
             git add ${profilingpath}/${pdf}/${unctype}/${subDir}/${xFrunFile}        
             git add ${profilingpath}/${pdf}/${unctype}/${subDir}/${unctype}_`echo ${subDir} | sed 's/_.*//'`_q2_10000_pdf_dv_ratio.pdf
@@ -124,6 +127,7 @@ for pdf in ${pdfs[@]}; do
         unctype="systVar05El"
         git add ${profilingpath}/${pdf}/${unctype}/collectPlots.tex                
         git add ${profilingpath}/${pdf}/${unctype}/run.sh
[…]

### 2023-07-31 paper/sec-protonPDFs.tex
Added reduction factor value 0.5

@@
 \includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{Same as Fig.~\ref{fig:profiling_syst}, now assessing the impact of FASER$\nu$2 structure functions
-once charm-tagged measurements are removed.
+\caption{Assessing the impact of FASER$\nu$2 structure functions
+once charm-tagged measurements are removed, assuming only statistical 
+uncertainties in both cases.
 }

### 2023-08-01 paper/sec-dis-pseudodata.tex
Added reduction factor value 0.5
Update event rate plots and kinematics

@@
     \includegraphics[width = 0.7\textwidth]{plots/KIN_DIS_FPF.pdf}
-    \caption{The kinematic coverage in the $(x,Q^2)$ plane
-      of muon neutrino scattering
-      at FASER$\nu$2, FLArE,
-      and AdvSND (see also Fig.~\ref{fig:fasernu2_muon})
-      compared to that of electron-ion collisions
-      at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
-      as well as to the coverage of other available hard-scattering datasets involving
-      nuclear targets or projectiles.
+    \caption{The kinematic coverage in the $(x,Q^2)$ plane of muon neutrino scattering
+      at FASER$\nu$(2), FLArE, and SND (see also Fig.~\ref{fig:fasernu2_muon})
+      compared to that of electron-ion collisions at the EIC for the highest center-of-mass 
+      energies $\sqrt{s}$ planned, as well as to the coverage of other available hard-scattering 
+      datasets involving nuclear targets or projectiles.
       %
-      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
-      fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
-      production in proton-lead collisions at the LHC.
+      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS.
+      Bins with less than $30$ events are represented by the grey dots.
+      %
+      \textcolor{red}{(To be replaced once AdvSND and new fluxes are available.)}
       }
@@
 
-The event yields displayed in Fig.~\ref{fig:fasernu2_muon} 
-determine the associated statistical uncertainty in each bin by means of
+The event yields displayed in Fig.~\ref{fig:fasernu2_muon} determine the associated statistical uncertainty 
+in each bin by means of the following equation:
 \be
@@
     \centering
-    \includegraphics[width = \textwidth]{plots/Event_Rate_FASERv2_antineutrino.pdf}
+    \includegraphics[width = \textwidth]{plots/Event_Rate_FASERv2.pdf}
     \caption{Same as Fig.~\ref{fig:fasernu2_muon} for FASER$\nu$2
-      now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$.
+      now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$
+      for both the neutrino and antineutrinos.
       %
@@
  and with $r_{i}$ being univariate Gaussian random numbers. 
+Similar to the factor $f_{\rm corr}$ in Ref.~\cite{AbdulKhalek:2018rok}, we take the factor $f_{\rm red}$ to be 0.5.
  %

### 2023-08-03 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/prel/FASERv2_inclusive_nub/run.sh
Added support for further experiments in pipeline, started work on adding support for sub i.e. electron pseudodata

@@ -9,12 +9,13 @@ PSEUDODATA="inclusive"
 
 ### OPTS w/ scaling 95% cl -> 68%, needed for EPPS PDFs (like CT)
 #PLOTOPTS="--splitplots-eps  --therr --bands --q2all --relative-errors --scale68 --xrange 1e-6:0.99"
-PLOTOPTS="--therr --bands --q2all --relative-errors --scale68"
+#scale68 no longer required, using scaling in profiling (parameters.yaml)
+PLOTOPTS="--therr --bands --q2all --relative-errors"
 
 ln -s ../../../../datafiles
 
 # Run xFitter:
-xfitter
+xfitter > log.txt
 
 # Visualize results:
 mv plots/plots.pdf plots/plots_OLD.pdf

### 2023-08-03 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/runFinal.sh

@@ -1,7 +1,15 @@
-for dir in "statOnly" "syst" "systVar05" "uncor"; do
-    for subdir in "FASERv2" "FASERv2_inclusive" "FASERv2_charm" "FASERv2_charm_nochargediscrimination" "FASERv2_inclusive_nochargediscrimination" "FASERv2_nochargediscrimination"; do
-        cd ${dir}/${subdir}
-        sh run.sh
-        cd ../..
-    done
+#!/bin/bash
+declare -a dirs=("statOnly" "syst" "systVar05" "systVar05El")
+
+for dir in ${dirs[@]}; do
+    cd ${dir}
+    ./run.sh
+    cd ..
+done
+
+for dir in ${dirs[@]}; do
+    cd ${dir} && pdflatex collectPlots.tex
+    cd ..
+    rm ${dir}/collectPlots.aux
+    rm ${dir}/collectPlots.log
 done

### 2023-08-03 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/statOnly/AdvSND/plot.sh

@@ -1,0 +1,25 @@
+DETECTOR="AdvSND"
+DETSIMPLE="AdvSND"
+UNCLVL="statOnly"
+
+DATATXT="Current data"
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-03 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/statOnly/FASERv2_charm_nochargediscrimination/run.sh

@@ -1,38 +1,7 @@
 # The commands to perform Hessian PDF profiling w/ xFitter, do e.g.
 #    sh run.sh
 
-DETECTOR="FASER#nu2"
-DETSIMPLE="FASERv2"
-UNCLVL="statOnly"
-
-DATATXT="Current data"
-PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
-
-
-### OPTS w/o/ scaling 95% cl -> 68%, e.g. CT PDFs
-#PLOTOPTS="--asym --therr --bands --q2all --relative-errors"
-
-### OPTS w/ scaling 95% cl -> 68%, needed for CT PDFs
-PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
-
 ln -s ../../../../datafiles
 
 # Run xFitter:
 xfitter
-
-# Visualize results:
-mv plots/plots.pdf plots/plots_OLD.pdf
-xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
-mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
-
-cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
-cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
-cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
-cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
-cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
-
-# Produce a new PDF in LHAPDF6 format:
-#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
-
-# Save the new PDF set into LHAPDF6 collection:
-#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-03 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/statOnly/FASERv2_inclusive_nochargediscrimination/plot.sh

@@ -1,0 +1,25 @@
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="statOnly"
+
+DATATXT="Current data"
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-03 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/statOnly/FLArE10/plot.sh

@@ -1,0 +1,25 @@
+DETECTOR="FLArE10"
+DETSIMPLE="FLArE10"
+UNCLVL="statOnly"
+
+DATATXT="Current data"
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-03 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/statOnly/FLArE100/plot.sh

@@ -1,0 +1,25 @@
+DETECTOR="FLArE100"
+DETSIMPLE="FLArE100"
+UNCLVL="statOnly"
+
+DATATXT="Current data"
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-03 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/systVar05/FASERv2_charm_nochargediscrimination/run.sh

@@ -1,38 +1,7 @@
 # The commands to perform Hessian PDF profiling w/ xFitter, do e.g.
 #    sh run.sh
 
-DETECTOR="FASER#nu2"
-DETSIMPLE="FASERv2"
-UNCLVL="systVar05"
-
-DATATXT="Current data"
-PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
-
-
-### OPTS w/o/ scaling 95% cl -> 68%, e.g. CT PDFs
-#PLOTOPTS="--asym --therr --bands --q2all --relative-errors"
-
-### OPTS w/ scaling 95% cl -> 68%, needed for CT PDFs
-PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
-
 ln -s ../../../../datafiles
 
 # Run xFitter:
 xfitter
-
-# Visualize results:
-mv plots/plots.pdf plots/plots_OLD.pdf
-xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
-mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
-
-cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
-cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
-cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
-cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
-cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
-
-# Produce a new PDF in LHAPDF6 format:
-#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
-
-# Save the new PDF set into LHAPDF6 collection:
-#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-03 xFitter/PDF_profiling/PDF4LHC21/cleanFinal.sh

@@ -1,8 +1,9 @@
-for dir in "statOnly" "syst" "systVar05" "uncor"; do
-    for subdir in "FASERv2" "FASERv2_inclusive" "FASERv2_charm" "FASERv2_charm_nochargediscrimination" "FASERv2_inclusive_nochargediscrimination" "FASERv2_nochargediscrimination"; do
-        rm -rf ${dir}/${subdir}/output
-        rm -rf ${dir}/${subdir}/plots
-        rm ${dir}/${subdir}/unpolarised.wgt
-        rm ${dir}/${subdir}/*.pdf
-    done
+#!/bin/bash
+declare -a dirs=("statOnly" "syst" "systVar05" "systVar05El")
+
+for dir in ${dirs[@]}; do
+    rm ${dir}/collectPlots.pdf
+    cd ${dir}
+    ./clean.sh
+    cd ..
 done

### 2023-08-03 xFitter/PDF_profiling/PDF4LHC21/prel/clean.sh

@@ -1,11 +1,7 @@
-for experiment in "FASERv2"; do
-    for origin in "inclusive" "charm"; do
-        for nuID in "nu" "nub" "nochargediscrimination"; do
-            dir="${experiment}_${origin}_${nuID}"
-            rm -rf ${dir}/output
-            rm -rf ${dir}/plots
-            rm ${dir}/unpolarised.wgt
-            rm ${dir}/*.pdf
-        done
-    done
+for dir in */; do
+    rm -rf ${dir}/output
+    rm -rf ${dir}/plots
+    rm ${dir}/unpolarised.wgt
+    rm ${dir}/*.pdf
+    rm ${dir}/log.txt
 done

### 2023-08-03 xFitter/PDF_profiling/PDF4LHC21/statOnly/AdvSND/plot.sh

@@ -1,0 +1,26 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter
+#    sh plot.sh
+
+DETECTOR="AdvSND"
+DETSIMPLE="AdvSND"
+UNCLVL="statOnly"
+
+DATATXT="Current data (CD)"
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:../FASERv2/output:"CD+FASER#nu2" profile:output:"CD+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-03 xFitter/PDF_profiling/PDF4LHC21/statOnly/FASERv/plot.sh

@@ -1,0 +1,26 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter
+#    sh plot.sh
+
+DETECTOR="FASER#nu"
+DETSIMPLE="FASERv"
+UNCLVL="statOnly"
+
+DATATXT="Current data (CD)"
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:../FASERv2/output:"CD+FASER#nu2" profile:output:"CD+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-03 xFitter/PDF_profiling/PDF4LHC21/statOnly/FASERv2_inclusive/plot.sh

@@ -1,0 +1,25 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter
+#    sh plot.sh
+
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="statOnly"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Current data (CD)" profile:../FASERv2/output:"CD+${DETECTOR}" profile:output:"CD+${DETECTOR}, no charm"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-03 xFitter/PDF_profiling/PDF4LHC21/statOnly/FASERv2_inclusive/run.sh

@@ -1,40 +1,7 @@
 # The commands to perform Hessian PDF profiling w/ xFitter, do e.g.
 #    sh run.sh
 
-DETECTOR="FASER#nu2"
-DETSIMPLE="FASERv2"
-UNCLVL="statOnly"
-
-DATATXT="Current data"
-PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
-
-
-### OPTS w/o/ scaling 95% cl -> 68%, e.g. CT PDFs
-#PLOTOPTS="--asym --therr --bands --q2all --relative-errors"
-
-### OPTS w/ scaling 95% cl -> 68%, needed for CT PDFs
-#PLOTOPTS="--splitplots-eps --therr --bands --q2all --relative-errors --scale68 --xrange 1e-6:0.7"
-#PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.7"
-PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
-
 ln -s ../../../../datafiles
 
 # Run xFitter:
 xfitter
-
-# Visualize results:
-mv plots/plots.pdf plots/plots_OLD.pdf
-xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
-mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
-
-cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
-cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
-cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
-cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
-cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
-
-# Produce a new PDF in LHAPDF6 format:
[…]

### 2023-08-03 xFitter/PDF_profiling/PDF4LHC21/statOnly/FASERv2_nochargediscrimination/plot.sh

@@ -1,0 +1,26 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter
+#    sh plot.sh
+
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="statOnly"
+
+DATATXT="Current data (CD)"
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:../FASERv2/output:"CD+${DETECTOR}" profile:output:"CD+${DETECTOR}, no charge id."
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-03 xFitter/PDF_profiling/PDF4LHC21/statOnly/FLArE10/plot.sh

@@ -1,0 +1,26 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter
+#    sh plot.sh
+
+DETECTOR="FLArE10"
+DETSIMPLE="FLArE10"
+UNCLVL="statOnly"
+
+DATATXT="Current data (CD)"
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:../FASERv2/output:"CD+FASER#nu2" profile:output:"CD+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-03 xFitter/PDF_profiling/PDF4LHC21/syst/FASERv2_inclusive/plot.sh

@@ -1,0 +1,28 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="syst"
+
+DATATXT="Current data"
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT} (CD)" profile:../../statOnly/${DETSIMPLE}/output:"CD+${DETECTOR}, stat" profile:output:"CD+${DETECTOR}, stat+syst"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-03 xFitter/PDF_profiling/PDF4LHC21/syst/FASERv2_nochargediscrimination/run.sh

@@ -1,40 +1,7 @@
 # The commands to perform Hessian PDF profiling w/ xFitter, do e.g.
 #    sh run.sh
 
-DETECTOR="FASER#nu2"
-DETSIMPLE="FASERv2"
-UNCLVL="syst"
-
-DATATXT="Current data"
-PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
-
-
-### OPTS w/o/ scaling 95% cl -> 68%, e.g. CT PDFs
-#PLOTOPTS="--asym --therr --bands --q2all --relative-errors"
-
-### OPTS w/ scaling 95% cl -> 68%, needed for CT PDFs
-#PLOTOPTS="--splitplots-eps --therr --bands --q2all --relative-errors --scale68 --xrange 1e-6:0.7"
-#PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.7"
-PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
-
 ln -s ../../../../datafiles
 
 # Run xFitter:
 xfitter
-
-# Visualize results:
-mv plots/plots.pdf plots/plots_OLD.pdf
-xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
-mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
-
-cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
-cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
-cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
-cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
-cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
-
-# Produce a new PDF in LHAPDF6 format:
[…]

### 2023-08-03 xFitter/PDF_profiling/PDF4LHC21/systVar05/FASERv2/plot.sh

@@ -1,0 +1,28 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="systVar05"
+
+DATATXT="Current data"
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT} (CD)" profile:../../statOnly/${DETSIMPLE}/output:"CD+${DETECTOR}, stat" profile:output:"CD+${DETECTOR}, stat+syst"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-03 xFitter/PDF_profiling/PDF4LHC21/systVar05/FASERv2_charm/plot.sh

@@ -1,0 +1,28 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="systVar05"
+
+DATATXT="Current data"
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"${DATATXT} (CD)" profile:output:"CD+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-03 xFitter/PDF_profiling/PDF4LHC21/systVar05/FASERv2_nochargediscrimination/run.sh

@@ -1,40 +1,7 @@
 # The commands to perform Hessian PDF profiling w/ xFitter, do e.g.
 #    sh run.sh
 
-DETECTOR="FASER#nu2"
-DETSIMPLE="FASERv2"
-UNCLVL="systVar05"
-
-DATATXT="Current data"
-PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
-
-
-### OPTS w/o/ scaling 95% cl -> 68%, e.g. CT PDFs
-#PLOTOPTS="--asym --therr --bands --q2all --relative-errors"
-
-### OPTS w/ scaling 95% cl -> 68%, needed for CT PDFs
-#PLOTOPTS="--splitplots-eps --therr --bands --q2all --relative-errors --scale68 --xrange 1e-6:0.7"
-#PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.7"
-PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
-
 ln -s ../../../../datafiles
 
 # Run xFitter:
 xfitter
-
-# Visualize results:
-mv plots/plots.pdf plots/plots_OLD.pdf
-xfitter-draw ${PLOTOPTS} output:"${DATATXT}" profile:output:"${DATATXT}+${DETECTOR}"
-mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
-
-cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
-cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
-cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
-cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
-cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
-
-# Produce a new PDF in LHAPDF6 format:
[…]

### 2023-08-03 xFitter/gitAdder.sh

@@ -1,0 +1,143 @@
+#!/bin/bash
+declare -a detectors=("FASERv" "FASERv2" "FLArE10" "FLArE100" "AdvSND")
+declare -a datatypes=("charm" "inclusive")
+declare -a parts=("nu" "nub" "nochargediscrimination")
+declare -a unctypes=("statOnly" "syst" "systVar05" "systVar05El")
+declare -a pdfs=("PDF4LHC21" "EPPS21nlo_CT18Anlo_W184")
+
+datapath=xFitter/datafiles/lhc/fpf/neutrinoDIS/pseudodata
+
+#Navigate to git main directory
+cd ..
+
+#Add general scripts
+git add xFitter/parser.cxx
+git add xFitter/gitAdder.sh
+
+for detector in ${detectors[@]}; do
+    for datatype in ${datatypes[@]}; do
+        for part in ${parts[@]}; do
+
+            #Add correlation tables
+            git add ${datapath}/${detector}_${datatype}_${part}.corr
+            git add ${datapath}/${detector}_${datatype}_${part}_onlyEl.corr
+            git add ${datapath}/${detector}_${datatype}_${part}_systVar05.corr
+            git add ${datapath}/${detector}_${datatype}_${part}_systVar05_onlyEl.corr
+
+            #Add datatables for preliminary runs
+            git add ${datapath}/prel/${detector}_${datatype}_${part}-thexp.dat
+
+            #Add datatables for final runs
+            for pdf in ${pdfs[@]}; do
+                for unctype in ${unctypes[@]}; do
+                    git add ${datapath}/${pdf}/${unctype}/${detector}_${datatype}_${part}-thexp.dat
+                done
+            done
+
+        done
+    done
+done
+
+#Add PDF_profiling files
+profilingpath=xFitter/PDF_profiling
+declare -a xFrunFiles=("constants.yaml" "parameters.yaml" "steering.txt" "plot.sh" "run.sh")
+declare -a xFprelFiles=("constants.yaml" "parameters.yaml" "steering.txt" "run.sh")
+for pdf in ${pdfs[@]}; do
+
+    if [[ ${pdf}=="PDF4LHC21" ]]; then
[…]

### 2023-08-16 paper/sec-dis-pseudodata.tex
sect 2

@@
 Finally, we discuss the procedure adopted to generate pseudo-data
-for LHC neutrino DIS and to their impact
+for LHC neutrino deep-inelastic scattering structure functions
+and to quantify their impact
  into proton and nuclear PDF determinations.

### 2023-08-16 paper/tables/integrated_yields.tex
Inlcuded dominant neutrino rate
Need to add subdominat rate for SND FASER (nu_e) and for FLARE(nu_mu)
sect 2
Included integrated yield rates
still waiting on advsnd and fasernu2
Updated event yields

@@
 \midrule
-FASER$\nu$  &    &    &   &   &    &    \\
-SND@LHC  &    &    &   &   &    &    \\
+FASER$\nu$  & 340 (56)    & 190 (36)  & 530 (92)  &  1100 (180)  &  440 (83)  &  1500 (260) \\
+SND@LHC  &  140 (15)  & 60 (9)    & 200 (24)   &  390 (54) & 150 (22)   &  550  (76)\\
 \midrule
 \midrule
-FASER$\nu$2  &    &    &   &   &    &    \\
-AdvSND~(far)  &    &    &   &   &    &    \\
-FLArE &    &    &   &   &    &    \\
+FASER$\nu$2  & 84k (11k)   & 42k (6.6k)   & 130k (19k)  & 274k (40k)  & 100k (17k)    & 370k (57k)   \\
+AdvSND-far  &  8.6k (0)  & 3500 (0)   & 13k (0.5k)  & 30k (2.7k)  & 12k (0.8k)   & 43k (4.5k)   \\
+FLArE-10 & 33k (3.3k) & 15k (1.4k)   &  50k (5.4k) &  53k (6.5k)&   28k (2.4k) &   81k (11k) \\
+FLArE-100 &   110k (13k)         &    58k (6.9k)         &       170k (21k)       &   302k (43k)      &  120k (15k)    &  420k (59k)  \\
   \bottomrule
@@
   %
-  These event yields are computed from Eq.~(\ref{eq:event_yields})
+  These event yields are computed from Eq.~(\ref{eq:event_yields_calculation})
   imposing DIS kinematics, $Q^2 \ge 2$ GeV$^2$ and $W^2 \ge 4$ GeV$^2$.
   %
-  Whenever available, the
-  numbers in parenthesis indicate the event rates corresponding to charm
+ The numbers in parenthesis indicate the event rates corresponding to charm
  production.
+ %
+ In the case of the FLArE detector, we display results for two proposed
+ options with fiducual masses of 10 and 100 tons respectively.
   \label{tab:integrated_rates}

### 2023-08-16 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

@@
 see~\cite{Candido:2023utz} and references therein,
-is expressed in terms of 
+is expressed in terms of three
 independent structure functions $F_2^{\nu A}$, $xF_3^{\nu A}$
@@
 %
-Structure functions depend only on $x$ and $Q^2$ while the differential
+In the case of tau-neutrino scattering, tau lepton mass effects
+cannot be neglected and Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) receive additional contributions
+from the $F_4$ and $F_5$ structure functions.
+%
+We neglect these effects since we focus on electron and muon neutrino scattering here.
+
+Structure functions depend only on $x$ and $Q^2$, while the differential
 cross-section depends also on the neutrino energy $E_\nu$, or alternatively
@@
 for the neutrino scattering through the nuclear modifications of the proton PDFs.
-
+%
 Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) are valid provided
 the hadronic 
-invariant mass $W$  is above the resonance threshold,
+invariant mass $W$  is above the resonance production threshold,
 \be
@@
 and in addition here we  restrict ourselves to the DIS region with perturbative momentum
-transfers $Q^2$, such that
+transfers $Q^2 \gsim 2$ GeV$^2$, such that
  structure functions are decomposed as

### 2023-08-16 paper/sec-dis-pseudodata.tex
sect 2

@@
 Further, structure functions $F^{\nu A}_i(x,Q^2)$ and $F^{\bar{\nu} A}_i(x,Q^2)$ depend on the nuclear target $A$ entering
-for the neutrino scattering through the nuclear modifications of the proton PDFs.
+for the neutrino scattering through the nuclear modifications of the free-nucleon PDFs.
 %
@@
 transfers $Q^2 \gsim 2$ GeV$^2$, such that
- structure functions are decomposed as
+ structure functions can be decomposed as
 \be
@@
 %
-Specifically, in this work we impose that $Q^2\ge 2$ GeV$^2$.
-%
 A similar expression holds for charm production~\cite{Faura:2020oom}, which requires
@@
  %
-We discuss in Sect.~\ref{sec:settings} the theoretical
-settings adopted~\cite{Candido:2022tld,yadism,Candido:2023utz,Carrazza:2020gss} to
+We discuss below the theoretical
+settings adopted here~\cite{Candido:2022tld,yadism,Candido:2023utz,Carrazza:2020gss} to
 evaluate predictions for
-neutrino DIS structure functions
-and differential cross-sections,
+neutrino differential cross-sections and DIS structure functions,
 Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}),~(\ref{eq:antineutrino_DIS_xsec_FL}), and~(\ref{eq:sfs_pqcd}),
@@
  %
- We point out that accounting for nuclear modifications in a global proton
+ Accounting for nuclear modifications in a global proton
  PDF fit is possible by means of the procedure developed
- in~\cite{Ball:2020xqw,Ball:2018twp}.
+ in~\cite{Ball:2020xqw,Ball:2018twp} based on
+ the theory covariance matrix approach~\cite{NNPDF:2019vjt,NNPDF:2019ubu}.
 
@@
  to the different flavour PDF decomposition.
+ %
+ This implies that the best sensitivity on the quark
+  flavour separation in the nucleon
+ would be provided by combining neutrino DIS at
+ LHC far-forward experiments with measurements on charged-lepton
+ DIS at the EIC.
 
- \subsection{Far-forward neutrino detectors at the LHC}
+ \subsection{LHC far-forward neutrino detectors}
  \label{sec:neutrinoDetectors}
@@
  far-forward detectors considered, in particular concerning
- their acceptance and performance.
+ their acceptance and (expected) performance.
  %
@@
  %
- A measurement of  $\lp E_\ell,\theta_\ell, E_h \rp$ then fixes the DIS kinematics as:
+ A measurement of the three kinematic variables $\lp E_\ell,\theta_\ell, E_h \rp$ then fixes the DIS kinematics as:
  \bea
@@
  Table~\ref{tab:FPF_experiments} summarises,
- for each of the far-forward LHC neutrino experiments considered,
+ for each of the far-forward LHC neutrino experiments considered in this
+ work,
  their pseudo-rapidity coverage, target material, whether
@@
   for the complete HL-LHC period  ($\mathcal{L}=3$ ab$^{-1}$).
+  %
+   In the case of FLArE, we consider projections for both
+  for 10 ton and 100 fiducial volume detectors.
   %
@@
 with the collision axis line-of-sight (LOS)
-and have been acquiring data since the begin of Run III in 2022.
+and have been acquiring data since the beginning of Run III in 2022.
 %
@@
 around 500 meters from the ATLAS interaction point and has been taking data
-since the  beginning of Run 3.
+since the  beginning of Run III.
 %
@@
 The combination of FASER$\nu$2  with the nearby FASER2 detector, equipped with a spectrometer, makes measurements of the outgoing muon charge possible.
+%
+Given that FASER$\nu$2 is based on the same detector technology
+as its predecessor, the same performance in terms of reconstruction
+of final-state kinematics is assumed.
 
@@
  at the FPF with a coverage in neutrino pseudorapidity of $7.2 \le \eta_\nu \le 8.4$
- (hence off-LOS) and a near detector installed somewhere else in LHC
+ (hence off-LOS, same as SND@LHC) and a near detector installed somewhere else in LHC
  complex and covering the range $4 \le \eta_\nu \le 5$.
@@
  in the hadronic calorimeter.
+ %
+ No information on the expected performance of the AdvSND-far detector
+ is available and hence to estimate of the systematic errors
+ is carried out.
 
@@
  %
- Building upon recent progress in liquid noble gas neutrino detectors over the last decade (ICARUS, MicroBooNE, SBND, ProtoDUNE, DUNE), this experiment relies on a modularized liquid argon (LAr) time projection detector.
+ Building upon recent progress in liquid noble gas neutrino detectors over the last decade (ICARUS, MicroBooNE, SBND, ProtoDUNE, DUNE), this experiment
+ would rely on a modularized liquid argon (LAr) time projection detector.
  %
- The use of LAr as target is beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimeter spatial resolution in all three dimensions.
+ The use of LAr as target is beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimeter spatial resolution in all dimensions.
  %
  FLArE is suitable to identify high-energy neutrinos ($E_\nu \gsim 100$ GeV)  from all three generations
- while  fully containing the events as required for kinematic reconstruction.
+ while containing the events as required for kinematic reconstruction.
  %
@@
 for the projections presented in this work
- we assume that outgoing muons would be measured in the FASER2 spectrometer
+we assume that outgoing high-energy
+muons would be measured in the FASER2 spectrometer
   situated downstream in the FPF cavern.
- %
+
  With an expected fiducial (active) mass of 10 tons (30 tons), FLArE will
  detect final-state electrons with energies $E_{e}\lsim 2~\rm{TeV}$ and
- scattering angles up to 0.5 mrad,  final-state muons
- with $\theta_\mu \lsim 0.025$ will be recorded by FASER$\nu$2.
+ scattering angles up to 0.5 mrad,  while final-state muons
+ with $\theta_\mu \lsim 0.025$ will be recorded by FASER$\nu$2
+ downstream in the FPF cavern.
+ %
+ We consider projections both for 10 ton (FLArE-10) and 100 ton (FLArE-100) fiducial volume detectors.
  %
@@
  performance parameters for $E_\mu$ and $\theta_\mu$ are  taken
- to be the same as those of FASER$\nu$2.
+ to be the same as those of FASER$\nu$2 as indicated
+ in Table~\ref{tab:FPF_experiments}.
 
-\subsection{Differential event rate calculation}
+\subsection{Differential scattering event rates}
 \label{sec:pseudo-data_generation}
@@
 %
-The goal is to evaluate the number of reconstructed charged-current neutrino interaction
+We want to evaluate the number of reconstructed charged-current neutrino interaction
 events taking place in the fiducial volume of the detector in bins of Bjorken-$x$,
@@
 In our calculation we assume the central values of the neutrino
-fluxes provided by~\cite{Kling:2021gos}.
+fluxes provided by~\cite{Kling:2021gos} and used
+for the FPF simulations in~\cite{Feng:2022inv}.
 %
@@
 %
-Differential event yields are therefore evaluated using
+Differential event yields are evaluated using
 \begin{equation}
@@
 The incoming neutrino fluxes, which account for the geometry
-and $\eta_\nu$ coverage of the considered detector,
+and neutrino pseudo-rapidity $\eta_\nu$ coverage of the considered detector,
 are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$.
@@
 covering the full detector acceptance,
-is consistent with the fiducial interaction rates presented in~\cite{Feng:2022inv}.
+is consistent with the fiducial interaction rates presented in~\cite{Feng:2022inv} once DIS cuts are imposed and detector acceptances are accounted for.
 
@@
 uncertainties are negligible for all the bins considered.
-
-Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the five detectors
-considered, separated into electron neutrinos and antineutrinos
-and muon neutrinos and antineutrinos.
-%
-As mentioned above, for FLArE we assume that muon neutrinos interacting
-in its fiducial volume will be measured
-by the FASER$\nu$2 spectrometer.
-  %
-These event yields are computed from Eq.~(\ref{eq:event_yields_calculation}) with the only
-requirement that the momentum transfer and the final-state invariant mass are restricted
-to the DIS region,
-\be
-\label{eq:DISconditions}
-Q^2 \ge 2~{\rm GeV}^2\quad{\rm and}\quad  W^2 \ge 4~{\rm GeV}^2 \, .
-\ee
-%
-The numbers in parenthesis indicate the event rates corresponding to charm
-production, for those experiments with heavy flavour tagging capabilities.
-%
-We note that, as opposed to the number of interacting neutrinos
-computed in~\cite{Feng:2022inv}, we now account for the 
-detector acceptance listed in  Table~\ref{tab:FPF_experiments}.
-
-%----------------------------------------------------
-\input{tables/integrated_yields.tex}
-%----------------------------------------------------
 
@@
 
- Fig.~\ref{fig:fasernu2_muon} displays the
+ Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the five detectors
+considered, separated into electron neutrinos and antineutrinos
+and muon neutrinos and antineutrinos.
+%
+As mentioned above, for FLArE we assume that muon neutrinos interacting
+in its fiducial volume will be measured
+by the FASER$\nu$2 spectrometer.
+  %
+These event yields are computed from Eq.~(\ref{eq:event_yields_calculation}) with the only
+requirement that the momentum transfer and the final-state invariant mass are restricted
+to the DIS region,
+\be
+\label{eq:DISconditions}
+Q^2 \ge 2~{\rm GeV}^2\quad{\rm and}\quad  W^2 \ge 4~{\rm GeV}^2 \, .
+\ee
+%
+The numbers in parenthesis indicate the event rates corresponding to charm
+production, for those experiments with heavy flavour tagging capabilities.
+%
+In the case of the FLArE detector, we display results for two proposed options with fiducual masses of 10 and 100 tons respectively.
+%
+We note that, as opposed to the number of interacting neutrinos
+ in~\cite{Feng:2022inv}, we now account for the 
+detector acceptance listed in  Table~\ref{tab:FPF_experiments}.
+
+%----------------------------------------------------
+\input{tables/integrated_yields.tex}
+%----------------------------------------------------
+
+Several observations can be derived from Table~\ref{tab:integrated_rates}.
+%
+First, one appreciates the large increase in statistics from
+the Run III experiments to the FPF ones, with for example a factor
+250 increase in the muon neutrino yield between FASER$\nu$ and
+FASER$\nu$2.
+%
+Second, muon neutrino scattering dominate over the electron ones by a factor
+between 2 and 3, though this ratio is affected by the large theory uncertainties
+affecting forward electron neutrino production.
+%
+Third, charm production  represents around 15\% of the inclusive
+yields, with both FASER$\nu$2 and FLArE-100 resulting in around
+60k recorded charm-production events.
+%
+Note that this result assumes charm ID is possible, and if only dimuon events can be recorded
+the yields would be reduced by a factor of 10.
+%
+Fourth, FASER$\nu$2 and FLArE-100 lead to the largest absolute
+yields of the FPF experiments, with around 500k and 600k (non-tau) neutrino DIS events respectively, with 56k and 131k
+events expected instead for AdvSND-far and FLArE-10.
+
+ Fig.~\ref{fig:fasernu2_muon} displays the differential
  event yields per bin,  Eq.~(\ref{eq:event_yields}),
  for muon neutrinos detected at the
- FASER$\nu$, SND@LHC, FASER$\nu$2, and FLArE  experiments,
+ FASER$\nu$ (Run III) and the AdvSND, FASER$\nu$2, and FLArE  (FPF) experiments,
  restricted
@@
     \includegraphics[width=0.495\textwidth]{plots/FPF-FLArE100.pdf}
-    \caption{\small The event yields per bin, $N_{\rm ev}^{(i)}$, for muon neutrinos at the
-      FASER$\nu$, SND@LHC (upper panels), FASER$\nu$2, and FLArE (bottom panels) experiments.
+    \caption{\small The event yields per bin $N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}), for muon neutrino
+      scattering at the
+      FASER$\nu$, AdvSND, FASER$\nu$2, and FLArE-100  experiments.
             %
-      Selected events are restricted to the DIS region Eq.~(\ref{eq:DISconditions}).
-      %
-      Only bins with $\ge 30$ events are retained.
+      Selected events are restricted to the DIS region Eq.~(\ref{eq:DISconditions})
+      and only bins with $\ge 30$ events are retained.
 	%

### 2023-08-16 paper/tables/detectors.tex
sect 2

@@
 \toprule
-Detector &  Rapidity &  Target & Charged Lepton ID & Acceptance  & Performance \\
+Detector &  Rapidity &  Target & Charge ID & Acceptance  & Performance \\
 \midrule
@@
 $\delta \theta_\ell \sim 0.06$ mrad        \\
-&   &     &       &  reconstructed $E_h$ \& charm ID   &      $\delta E_h \sim 30\%$     \\
+&   &     &       &  reco $E_h$ \& charm ID   &      $\delta E_h \sim 30\%$     \\
 \midrule
@@
   &   &  \multirow{2}{*}{(20 ton)}   &       &  $\tan \theta_\ell \lsim 0.05$   &   $\delta \theta_\ell \sim 0.06$ mrad      \\
-  &   &     &       &  reconstructed $E_h$ \& charm ID   &  $\delta E_h \sim 30\%$        \\
+  &   &     &       &  reco $E_h$ \& charm ID   &  $\delta E_h \sim 30\%$        \\
 \midrule
@@
   &   &   \multirow{2}{*}{(5 ton)}  &        & $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$     &           \\
-  &   &     &       &  reconstructed $E_h$   &           \\
+  &   &     &       &  reco $E_h$   &           \\
 \midrule
-\multirow{3}{*}{FLArE ({\bf *})}  & \multirow{3}{*}{$\eta_\nu \ge 7.5$} & \multirow{2}{*}{LAr}  & \multirow{3}{*}{muons}  &  $E_\mu \gsim 2$ GeV, $E_e \lsim 2$ TeV    &    $\delta E_e \sim 5\% $ \\
-&   &  \multirow{2}{*}{(10 ton)}   &   & $\theta_\mu \lsim 0.025$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $ mrad   \\
- &   &     &  & reconstructed $E_h$  &    $\delta E_h \sim 30\% $   \\
+\multirow{3}{*}{FLArE ({\bf *})}  & \multirow{3}{*}{$\eta_\nu \ge 7.5$} & \multirow{2}{*}{LAr}  & \multirow{3}{*}{muons}  &  $E_\mu \gsim 2$ GeV, $E_e \lsim 2$ TeV    &    $\delta E_e \sim 5\% $,  $\delta E_\mu \sim 30\% $ \\
+&   &  \multirow{2}{*}{(10 ton)}   &   & $\theta_\mu \lsim 0.025$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $,
+$\delta \theta_\mu \sim 0.06$ mrad\\
+ &   &     &  & reco $E_h$  &    $\delta E_h \sim 30\% $   \\
   \bottomrule
@@
 \vspace{0.2cm}
-\caption{\small For each of the far-forward LHC neutrino experiments considered
+\caption{\small For each of the far-forward LHC neutrino experiments considered,
    we indicate their neutrino pseudo-rapidity coverage, target material, whether
@@
   for the complete HL-LHC period ($\mathcal{L}=3$ ab$^{-1}$).
+  %
+  In the case of FLArE, we consider results both
+  for 10 ton and 100 ton fiducial volume detectors.
   \label{tab:FPF_experiments}

### 2023-08-16 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

@@
  %
- Adding up the bins in each of the panels results into the numbers listed in
+ Adding up the bins in each of the panels results into the inclusive yields listed in
  Table~\ref{tab:integrated_rates}.
  %
- The clear improvement in going from the current FASER$\nu$ and SND@LHC
- experiments to the FPF ones is visible both in terms
+ The clear improvement in going from the current FASER$\nu$ experiment
+ to the FPF ones is visible both in terms
  of the number
@@
  leading to typical statistical uncertainties at the 1\% level or smaller,
- while for FASER$\nu$, SND@LHC statistical uncertainties are much larger due
+ while for FASER$\nu$ the statistical uncertainties are much larger due
  to the reduced event rates.
@@
 how the kinematic coverage of the FPF far-forward experiments reaches
-$x_{\rm min}\sim \times 10^{-3}$ at small-$x$ and $Q^2_{\rm max}\sim 2\times 10^3$
+$x_{\rm min}\sim 3\times 10^{-3}$ at small-$x$ and $Q^2_{\rm max}\sim 10^4$ GeV$^2$
 at large-$Q^2$, representing an extension
@@
     \centering
-    \includegraphics[width = 0.7\textwidth]{plots/KIN_DIS_FPF.pdf}
-    \caption{The kinematic coverage in the $(x,Q^2)$ plane of muon neutrino scattering
-      at FASER$\nu$(2), FLArE, and SND (see also Fig.~\ref{fig:fasernu2_muon})
+    \includegraphics[width = 0.85\textwidth]{plots/KIN_DIS_FPF.pdf}
+    \caption{The kinematic coverage in the $(x,Q^2)$ plane of muon-neutrino scattering
+      at the FASER$\nu$, FASER$\nu$2, FLArE-100, and AdvSND experiments, see also Fig.~\ref{fig:fasernu2_muon},
       compared to that of electron-ion collisions at the EIC for the highest center-of-mass 
-      energies $\sqrt{s}$ planned, as well as to the coverage of other available hard-scattering 
-      datasets involving nuclear targets or projectiles.
+      energies $\sqrt{s}$ planned as well as to the coverage of existing nuclear neutral- and
+      charged-current DIS measurements.
       %
-      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS.
-      Bins with less than $30$ events are represented by the grey dots.
+      Bins with less than 30 events have been excluded.
       %

### 2023-08-16 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

@@
 Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF} compares
-the kinematic coverage of FASER$\nu$2, FLArE, and AdvSND with that of electron-ion collisions
-at the upcoming EIC~\cite{Khalek:2021ulf,AbdulKhalek:2021gbh}
-and to other available hard-scattering datasets involving
-nuclear targets or projectiles.
+the kinematic coverage of FASER$\nu$, FASER$\nu$2, FLArE, and AdvSND, same as in
+Fig.~\ref{fig:fasernu2_muon}, with that of electron-ion collisions
+at the upcoming EIC~\cite{Khalek:2021ulf,AbdulKhalek:2021gbh} at the highest
+center-of-mass energies planned, as well as to available fixed-target
+neutral- and charged-current DIS measurements.
 %
-Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
-fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
-production in proton-lead collisions at the LHC entering the  nNNPDF3.0
-determination~\cite{AbdulKhalek:2022fyi}.
-%
-The LHC neutrino experiments cover the region $x\gsim 10^{-3}$ relevant
+The LHC neutrino experiments cover the region $x\gsim 3\times 10^{-3}$, relevant
 for precision electroweak measurements at the LHC, such as the $W$-boson
@@
 and antiquarks in the proton.
+%
+FASER$\nu$2 and FLArE-100 mostly overlap with the EIC coverage, providing a complementary handle
+on the quark flavour decomposition in protons and heavy nuclei as compared
+to that provided by the EIC measurements.
 

### 2023-08-16 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

@@
 The event yields displayed in Fig.~\ref{fig:fasernu2_muon} determine the associated statistical uncertainty 
-in each bin by means of the following equation:
+in each bin,
 \be
@@
 ranges between $\lsim 1\%$ and $\sim 18\%$, depending on the values of
-$x$ and $Q^2$ associated to this bin.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+$x$ and $Q^2$ associated to each bin.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[h]
@@
       %
-      The error bars in the horizontal direction indicate the width of the adopted $x$-bins.
+      The bars in the horizontal direction indicate the width of the adopted $x$-bins.
       }
@@
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-These statistical uncertainties are displayed in the left panel
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The projected statistical uncertainties for muon-neutrino scattering
+in the case of FASER$\nu$2 are displayed in the left panel
 of Fig.~\ref{fig:error_plot_FASERv2_14}, which corresponds
 to the same event yields as in
-Fig.~\ref{fig:fasernu2_muon} for FASER$\nu$2
+Fig.~\ref{fig:fasernu2_muon} for 
 now as a function of $x$ after having integrated the event
@@
 Except for the bins with the smallest values of $x$, statistical uncertainties indeed
-are at the percent level or smaller for FASER$\nu$2.
-
-In addition to the statistical uncertainties given by Eq.~(\ref{eq:statistical_uncertainties}),
+are at the percent level or smaller for this experiment.
+
+In addition to the statistical uncertainties evaluated from Eq.~(\ref{eq:statistical_uncertainties}),
 one needs to also estimate the systematic uncertainties associated to the
@@
 
-For each source of experimental systematic uncertainty we need to
+For each independent source of experimental systematic uncertainty, we hence
 quantify its impact at the event yield level.
@@
 From Table~\ref{tab:FPF_experiments} we know that its
-acceptance and reconstruction performance are specified by:
+acceptance parameters and reconstruction performance are specified by:
 \bea
@@
 \eea
-To translate the uncertainties in $\delta E_\ell$, $\delta E_h $,
+To translate these uncertainties in $\delta E_\ell$, $\delta E_h $,
 and $\delta\theta_\ell$ into systematic errors associated to the event yields, 
@@
 to be the absolute difference between the mean number of events in this
-bin evaluated for the smeared samples samples and the
+bin evaluated for the smeared samples and the
 central prediction for the number of events
@@
 \ee
-Systematic errors are treated as uncorrelated among them and hence
+Individual sources of systematic errors are treated as uncorrelated among them and hence
 by producing samples where only one source of error is varied at a time
-we can determine the systematic errors, Eq.~(\ref{eq:event_yields_systematic_error}), in each bin.
+we can determine the systematic errors, Eq.~(\ref{eq:event_yields_systematic_error}), in each bin
+for each of the considered experiments.
 %
@@
 uncertainties, say to assess the impact of improved detector performance,
-is straightforward.
+becomes straightforward.
 
 Fig.~\ref{fig:percentage_uncertainties_overview}
-displays the systematic uncertainties associated
-to $E_\ell$, $\theta_\ell$, and $E_h$ variations
-for the  measurements
-of the double-differential
-neutrino scattering cross-section at FASER$\nu$2.
+displays the projected systematic uncertainties associated
+to $E_\ell$, $\theta_\ell$, and $E_h$ 
+for the  measurements of the double-differential
+muon-neutrino scattering  at FASER$\nu$2.
 %
@@
 of the average momentum fraction per bin $\la x\ra$
-in three different bins of $Q^2$.
+in two different bins of $Q^2$.
 %
@@
 %
-Systematic uncertainties associated to the hadronic final state energy $E_h$ appear to be the largest.
-%
-The uncertainties associated to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$ range
-between a few percent up to 20\% in the nominal baseline scenario,
-and in the case of the latter they are the smallest in the large-$x$ region.
-%
-Fig.~\ref{fig:error_plot_FASERv2_14} (central and right panels) display
- the integrated event yields for FASER$\nu$2 as a function of $x$ for only
- systematic errors and for the sum in quadrature of statistical and systematic errors.
- %
- For most of the bins, for the baseline performance assumptions the total systematic
- uncertainty is at the $10\%$ and dominates over the statistical uncertainties.
+For completeness, we also display in the bottom-right panel the corresponding
+statistical uncertainties in the same bins.
 
@@
     of the double-differential
-    neutrino scattering cross-section at FASER$\nu$2.
+    muon-neutrino scattering cross-section at FASER$\nu$2.
     %
@@
     of the average momentum fraction per bin $\la x\ra$
-    in three different bins of $Q^2$.
+    in two different bins of $Q^2$.
     %
@@
     those associated to inclusive and to charm production measurements.
+    %
+    For completeness, we display in the bottom-right panel the corresponding
+    statistical uncertainties in the same bins.
   }
@@
 
-The end result of the procedure is the estimate of statistical and systematic uncertainties
+In general, systematic uncertainties associated to the hadronic final state energy $E_h$ appear to be the largest,
+reaching up to $\sim 40\%$.
+%
+We recall that measurement of $E_h$ in addition to the leptonic variables is required to
+fix the incoming neutrino energy $E_\nu$, which is different in each event unlike
+the case of neutral-current scattering.
+%
+The uncertainties associated to the charged-lepton energy $E_\ell$ and scattering angle $\theta_\ell$ range
+between a few percent up to 20\% in the  baseline scenario listed in Table~\ref{tab:FPF_experiments}.
+%
+For the $\delta \theta_\ell$ variations, they are smallest in the large-$x$ region
+for $x\gsim 0.1$, where they are at the few-percent level typically.
+%
+Statistical uncertainties are subdominant in most of the bins and are below the 10\% level,
+specially at large-$x$ which is the kinematic region benefitting from the largest event rates.
+
+Fig.~\ref{fig:error_plot_FASERv2_14} also displays
+ the integrated event yields for FASER$\nu$2 as a function of $x$ for only
+ systematic errors and for the sum in quadrature of statistical and systematic errors
+ (central and right panels respectively).
+ %
+ For most of the bins, for the baseline performance assumptions the total systematic
+ uncertainty dominates over the statistical uncertainties, with the possible exception
+ of the small-$x$ region where statistical and systematic errors are comparable.
+
+The end result of the procedure is an estimate of statistical and systematic uncertainties
 for each bin of the measurement, from which a experimental covariance matrix can be constructed as
@@
  for the double-differential cross-sections Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) which are related to the event yields by a constant prefactor.
- %
-
+
+ The experimental covariance matrix constructed as per
  Eq.~(\ref{eq:covmat_definition}) assumes that each source of systematic
@@
  %
- For this reason, here we neglect bin-by-bin correlations
+ For this reason, following the HL-LHC projection strategy of~\cite{AbdulKhalek:2018rok}
+ here we neglect bin-by-bin correlations
  and add in quadrature statistical and systematic errors
@@
  {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
-+ \delta_{ij}\sum_{k=1}^{n_{\rm sys}} \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp^2
++ \lp f_{\rm corr}\rp^2\sum_{k=1}^{n_{\rm sys}} \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp^2
 \, ,\qquad i,j=1,\ldots,N_{\rm bin} \, .
@@
 %
+Furthermore, Here $f_{\rm corr}$ represents an effective correction factor that accounts for the fact that data with correlated
+systematics may be more constraining than the same data where each source of error is simply
+added in quadrature as we do here.
+%
+A value of $f_{\rm corr}=0.5$, obtained from the inspection of available measurements
+ for which the full information
+ on correlated systematics is available, was estimated in ~\cite{AbdulKhalek:2018rok}
+ and we adopt the same choice here.
+%
 In Sect.~\ref{sec:protonPDFs} we present results for different scenarios
-for the systematic uncertainty reduction $f_{\rm red}^{(k)}$.
+for the systematic uncertainty reduction $f_{\rm red}^{(k)}$ with respect to the baseline settings.
 
@@
 For the proton PDF fits we assume a free isoscalar target $N$, while
-for the nuclear PDF one we allow for deviations from isoscalarity.
+for the nuclear PDF one we allow for deviations from isoscalarity relevant
+for a tungsten nucleus.
 
@@
  by fluctuating the reference theory prediction Eq.~(\ref{eq:theory_dis_projections})
- by the corresponding statistical and systematic
+ by the corresponding fractional statistical and systematic
  uncertainties,
@@
  = \left( \left( \delta_i^{\rm stat}\right)^2 + \sum_{k=1}^{n_{\rm sys}}
- \left( f_{\rm red}^{(k)} \delta_{i,k}^{\rm sys} \right)^2\right)^{1/2} \, ,
+ \left( f_{\rm corr} \times f_{\rm red}^{(k)} \times \delta_{i,k}^{\rm sys} \right)^2\right)^{1/2} \, ,
  \qquad i=1,\ldots,N_{\rm bin} \, ,
@@
  and with $r_{i}$ being univariate Gaussian random numbers. 
-Similar to the factor $f_{\rm corr}$ in Ref.~\cite{AbdulKhalek:2018rok}, we take the factor $f_{\rm red}$ to be 0.5.
+ %
+ As mentioned above, $f_{\rm red}^{(k)}$ is a reduction factor that accounts possible
+ improvements in the experimental performance as compared to the baseline
+ settings summarised in Sect.~\ref{tab:FPF_experiments}.
+ %
+ Here we consider two scenarios for the systematic errors: conservative  $f_{\rm red}^{(k)}=1$, so
+ no improvement as compared to current projected performance, and  $f_{\rm red}^{(k)}=0.5$, a factor
+ two improvement for all relevant sources.
  %

### 2023-08-16 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

@@
  here we neglect bin-by-bin correlations
- and add in quadrature statistical and systematic errors
+ and add in quadrature statistical and systematic errors,
  \be
@@
  {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
-+ \lp f_{\rm corr}\rp^2\sum_{k=1}^{n_{\rm sys}} \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp^2
++ \delta_{ij}\lp f_{\rm corr}\rp^2\sum_{k=1}^{n_{\rm sys}} \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp^2
 \, ,\qquad i,j=1,\ldots,N_{\rm bin} \, .
@@
 %
-Furthermore, Here $f_{\rm corr}$ represents an effective correction factor that accounts for the fact that data with correlated
+Furthermore, $f_{\rm corr}$ represents an effective correction factor that accounts for the fact that data with correlated
 systematics may be more constraining than the same data where each source of error is simply
@@
 
- \subsection{Pseudo-data generation and inclusion on PDF fits}
+ \subsection{Pseudo-data generation}
 
@@
  %
- As mentioned above, $f_{\rm red}^{(k)}$ is a reduction factor that accounts possible
+ As mentioned above, $f_{\rm red}^{(k)}$ is a reduction factor modelling
  improvements in the experimental performance as compared to the baseline
@@
  %
- Here we consider two scenarios for the systematic errors: conservative  $f_{\rm red}^{(k)}=1$, so
- no improvement as compared to current projected performance, and  $f_{\rm red}^{(k)}=0.5$, a factor
- two improvement for all relevant sources.
+ Here we consider two scenarios for the systematic errors: conservative,  $f_{\rm red}=1$, where
+ no improvement as compared to current projected performance takes place, and  $f_{\rm red}=0.5$, a factor
+ two improvement for all relevant sources of systematics.
  %
  The pseudo-data generated by means of Eq.~(\ref{eq:pseudo_data_v2}),
- together with the corresponding correlations, computed according to Eq.s~\eqref{eq:corrmat_definition}--\eqref{eq:covmat_definition_v2},
-%  \be
-%\label{eq:covmat_definition_v2}
-% {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)} \mathcal{O}_i^{\rm (th)} \rp^2
-% + \delta_{ij}\sum_{k=1}^{n_{\rm sys}}
-% \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} \mathcal{O}_i^{\rm (th)} \rp^2
-%\, ,\qquad i,j=1,\ldots,N_{\rm bin} \, ,
-%\ee
+ together with the corresponding covariance matrix computed according to Eq.~\eqref{eq:covmat_definition_v2},
  define then the inputs of the subsequent proton and nuclear PDF determination.
 
+\subsection{PDF impact assessment}
+
 We consider two complementary approaches to assess the
-impact of LHC neutrino data on the proton and nuclear PDFs.
+impact of the projected LHC neutrino data on the proton and nuclear PDFs.
 %
@@
 \frac{\left(  \mathcal{O}_i^{\rm (exp)}
-            + \Gamma_i^{\alpha,\textrm{pd}}
-              b_\alpha^{\textrm{(pd)}}
+            + \Gamma_i^{\alpha,\textrm{exp}}
+              b_\alpha^{\textrm{(exp)}}
             - \mathcal{O}_i^{\rm (th)}
@@
      }{ \left(\delta^{{\rm (stat)}}\mathcal{O}_i^{\rm (th)}\rp^2 }
-+ \sum_\alpha \lp b_\alpha^{(\textrm{pd})}\rp^2
++ \sum_\alpha \lp b_\alpha^{(\textrm{exp})}\rp^2
 + T^2 \sum_\beta  \lp b_\beta^{\textrm{(th)}}\rp ^2 \, ,
@@
 The correlated uncertainties for the pseudodata and for the theoretical prediction 
-are contained in the nuisance parameter vectors $b^{(\textrm{pd})}$ and $b^{(\textrm{th})}$, respectively, with $T$ the tolerance factor, and the total uncorrelated uncertainty is $\delta^{{\rm (stat)}}\mathcal{O}_i^{\rm (th)}$.
+are contained in the nuisance parameter vectors $b^{(\textrm{exp})}$ and $b^{(\textrm{th})}$, respectively, with $T$ the tolerance factor, and the total uncorrelated uncertainty is $\delta^{{\rm (stat)}}\mathcal{O}_i^{\rm (th)}$.
 
@@
 on the observables $\mathcal{O}_i^{\rm (exp)}$ and $\mathcal{O}_i^{\rm (th)}$
-is described by the matrices $\Gamma_i^{\textrm{pd}}$ and $\Gamma_i^{\textrm{th}}$.
+is described by the matrices $\Gamma_i^{\textrm{exp}}$ and $\Gamma_i^{\textrm{th}}$.
 %
@@
 from the {\sc\small xFitter} repository.
-%%
-%A tolerance factor $T = \sqrt{\Delta \chi^2}=3$ is adopted for the proton
-%PDF profiling, corresponding approximately to the average tolerance
-%used in the CT18~\cite{Hou:2019efy} and MSHT20~\cite{Bailey:2020ooq} determinations,
-%the two Hessian sets entering the PDF4LHC21 combination.
-%The same choice was adopted in the HL-LHC projections of~\cite{AbdulKhalek:2018rok},
-%and a common value is used for the Hessian profiling of EPPS21.
-%%
-For the proton PDF profiling, a tolerance of $T^2 = 10$ is adopted, as in Ref.~\cite{PDF4LHCWorkingGroup:2022cjn}.
-For the Hessian profiling of EPPS21, a value of $T^2 = 33$ is used, following Ref.~\cite{Eskola:2021nhw}.
-Notably, the PDF uncertainties in the earlier (latter) case are given at 68\% (90\%) confidence level.
-%
+%
+For the proton PDF profiling, a tolerance of $T^2 = 10$ is adopted,
+which  corresponds approximately to the average tolerance
+used in the CT18~\cite{Hou:2019efy} and MSHT20~\cite{Bailey:2020ooq} determinations,
+the two Hessian sets entering the PDF4LHC21 combination~\cite{PDF4LHCWorkingGroup:2022cjn}, for
+one-sigma PDF uncertainties.
+%
+For the Hessian profiling of EPPS21, a value of $T^2 = 20$ is used consistently with~\cite{Eskola:2021nhw}
+for the definition of 68\%  confidence level intervals.
 
@@
 with NNPDF4.0 NNLO for various choices of input datasets, and included
-directly in the same alongside all other DIS datasets.
+directly in the same alongside all other datasets in the global fit.
 %
@@
 and the generated pseudo-data.
+%
+We assess the impact of the forward LHC neutrino data in the NNPDF fits both when added
+on top of the baseline dataset and when added to a dataset which excludes previous neutrino DIS
+cross-section measurements.

### 2023-08-16 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

@@
 that gauges the impact of a possible reduction of the $k$-th systematic error
-as compared to the default experiment performance.
+as compared to the default experiment performance (reproduced with $f_{\rm red}=1$).
 %
@@
 In Sect.~\ref{sec:protonPDFs} we present results for different scenarios
-for the systematic uncertainty reduction $f_{\rm red}^{(k)}$ with respect to the baseline settings.
+for the systematic uncertainty reduction factor $f_{\rm red}$ with respect to the baseline settings.
 
@@
  %
- Here we consider two scenarios for the systematic errors: conservative,  $f_{\rm red}=1$, where
- no improvement as compared to current projected performance takes place, and  $f_{\rm red}=0.5$, a factor
- two improvement for all relevant sources of systematics.
+ Here we consider two scenarios for the systematic errors: ``conservative'',  with $f_{\rm red}=1$, where
+ no improvement as compared to current projected performance takes place, and ``optimistic'', with  $f_{\rm red}=0.5$, a factor
+ two improvement for all sources of systematics.
  %

### 2023-08-17 paper/sec-dis-pseudodata.tex
added text and left comments

@@
 detector, composed by interleaved emulsion and tungsten plates and
-adding up to a mass of 1.1 tons with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 30~{\rm cm}$.
+adding up to a mass of 1.1 tons with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 30~{\rm cm}$ {\color{blue} [MF: Is 30 cm correct?
+The length I have is 100 cm.
+Looking at \cite{FASER:2023zcr}, I think that the final length of tungsten might be closer to 80cm = 730 layers * 1.1mm/layer]}.
 %
@@
 %
-With a total fiducial volume of 830 kg, it is composed by tungsten plates,
+With a total fiducial volume of 830 kg {\color{blue}[ MF: and length of 35 cm]}, it is composed by tungsten plates,
 where neutrino scattering takes place, interleaved with nuclear emulsions and electronic tracker
@@
  %
- The target region of the detector, where the neutrino interactions take place, is made of thin sensitive layers interleaved with tungsten plates, for a total mass of 5 tons.
+ The target region of the detector, where the neutrino interactions take place, is made of thin sensitive layers interleaved with tungsten plates, for a total mass of 5 tons {\color{blue} [MF: and fiducial length of 50 cm]}.
  %
@@
 
- With an expected fiducial (active) mass of 10 tons (30 tons), FLArE will
+ With an expected fiducial (active) mass of 10 tons (30 tons) {\color{blue} [MF: and length 3 m]}, FLArE will
  detect final-state electrons with energies $E_{e}\lsim 2~\rm{TeV}$ and
@@
 When choosing the binning of the measurement, the main criteria are
-simplicity and ensuring that Gaussian statistics holds in all bins.
+simplicity and ensuring that Gaussian statistics holds in all bins.{\color{blue} [MF: What does this mean exactly? Binning has not been chosen based on any criteria]}
 
@@
 We have verified that the differential event yield calculation
-implemented in Eq.~(\ref{eq:event_yields_calculation}), when extrapolated to a single bin
+implemented in Eq.~(\ref{eq:event_yields_calculation}) {\color{blue} [MF: There is a discrepancy beyond this.
+Our integrated cross sections come out a bit smaller.
+The total cross sections are very sensitive to kinematic cuts.
+TR and I have talked about this before and I will message] }, when extrapolated to a single bin
 covering the full detector acceptance,
@@
       %
-      Bins with less than 30 events have been excluded.
+      Bins with less than 30 events have been excluded.{\color{blue}[ MF: Currently, not 30 -  10 for Run3 expt's and 100 for HL-LHC expts]}
       %
@@
 %
-Since we discard bins with less than 30 events, the fractional statistical uncertainty
+Since we discard bins with less than 30 events{\color{blue} [MF: not 30. Currently 10 for Run3, 100 for HL-LHC]}, the fractional statistical uncertainty
 ranges between $\lsim 1\%$ and $\sim 18\%$, depending on the values of
@@
 we generate first a Monte Carlo set of events, denoted by $\mathcal{D}_0$,
-composed by $N_{\rm mc} = 10^7$ samples and determine the assignment of each event
+composed by $N_{\rm mc} \approx 10^7$ samples and determine the assignment of each event
 to a point in the $\lp x,Q^2,E_{\nu}\rp$ space.
 %
-By integrating over this sample by means of Eq.~(\ref{MCintegration}), we determine
-the binned event yields for this reference $\mathcal{D}_0$ sample.
+By comparing $\mathcal{D}_0$ with the total number of events as calculated by Eq.~(\ref{MCintegration}), we can normalize the distribution to produce the expected yield.{\color{blue} [MF:changed some wording here ]}
+%By integrating over this sample by means of Eq.~(\ref{MCintegration}), we determine
+%the binned event yields for this reference $\mathcal{D}_0$ sample.
 
@@
 to a given systematic source, say $\delta E_\ell$,
-to be the absolute difference between the mean number of events in this
-bin evaluated for the smeared samples and the
-central prediction for the number of events
+%to be the absolute difference between the mean number of events in this
+%bin evaluated for the smeared samples and the
+%central prediction for the number of events
+to be the mean of the absolute difference between the number of events in this bin for the smeared samples and the central prediction for the number of events
 $ N_{\rm ev}^{(i)}$ as calculated from Eq.~(\ref{MCintegration}):
 \be
-\delta_{\rm sys}^{(E_\ell)} N^{(i)} = \Big| \la {N}^{(i)}\ra_{E_\ell-{\rm smeared}} -N_{\rm ev}^{(i)}\Big| \, .
-\ee
+\delta_{\rm sys}^{(E_\ell)} N^{(i)} =\la \Big|  {N}^{(i)}_{E_\ell-{\rm smeared}} -N_{\rm ev}^{(i)}\Big|\ra \, .
+\ee
+{\color{blue} [MF:Changed some wording here and the equation slighlty to what we do]}
+
 Individual sources of systematic errors are treated as uncorrelated among them and hence
@@
 In general, systematic uncertainties associated to the hadronic final state energy $E_h$ appear to be the largest,
-reaching up to $\sim 40\%$.
+reaching up to $\sim 40\%$.{\color{blue} [MF: Sometimes uncertainties can be huge more than 100\%.
+We ignore these bins.
+Fig 2.4 will also be updated soon probably, and here we will see some larger uncerainties due to the updated cross sections.]}
 %

### 2023-08-17 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/fred05/FASERv2_inclusive/plot.sh
Updating xFitter directory structure

@@ -1,0 +1,24 @@
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="fred05"
+
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-17 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/syst/FASERv2_charm_nochargediscrimination/plot.sh

@@ -1,0 +1,24 @@
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="syst"
+
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-17 xFitter/PDF_profiling/PDF4LHC21/prel/FASERv2_charm_nu/run.sh

@@ -1,0 +1,28 @@
+# The commands to perform Hessian PDF profiling w/ xFitter, do e.g.
+#    sh run.sh
+
+PDF="PDF4LHC21"  #N.B. or plots only! Change also in parameters.yaml
+PSEUDODATA="charm"
+
+### OPTS w/o/ scaling 95% cl -> 68%, e.g. CT PDFs
+#PLOTOPTS="--asym --therr --bands --q2all --relative-errors"
+
+### OPTS w/ scaling 95% cl -> 68%, needed for CT PDFs
+#PLOTOPTS="--splitplots-eps  --therr --bands --q2all --relative-errors --scale68 --xrange 1e-6:0.99"
+PLOTOPTS="--therr --bands --q2all --relative-errors"
+
+ln -s ../../../../datafiles
+
+# Run xFitter:
+xfitter > log.txt
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:${PDF} profile:output:${PDF}-${PSEUDODATA}
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-17 xFitter/PDF_profiling/PDF4LHC21/runFinal.sh

@@ -1,0 +1,15 @@
+#!/bin/bash
+declare -a dirs=("statOnly" "syst" "fred05" "fcorr05" "fred05fcorr05")
+
+for dir in ${dirs[@]}; do
+    cd ${dir}
+    ./run.sh
+    cd ..
+done
+
+for dir in ${dirs[@]}; do
+    cd ${dir} && pdflatex collectPlots.tex
+    cd ..
+    rm ${dir}/collectPlots.aux
+    rm ${dir}/collectPlots.log
+done

### 2023-08-17 xFitter/gitAdder.sh

@@ -1,0 +1,123 @@
+#!/bin/bash
+declare -a detectors=("FASERv" "FASERv2")
+declare -a datatypes=("charm" "inclusive")
+declare -a parts=("nu" "nub" "nochargediscrimination")
+declare -a unctypes=("statOnly" "syst" "fred05" "fcorr05" "fred05fcorr05")
+declare -a pdfs=("PDF4LHC21" "EPPS21nlo_CT18Anlo_W184")
+
+datapath=xFitter/datafiles/lhc/fpf/neutrinoDIS/pseudodata
+
+#Navigate to git main directory
+cd ..
+
+#Add general scripts
+git add xFitter/parser.cxx
+git add xFitter/gitAdder.sh
+
+for detector in ${detectors[@]}; do
+    for datatype in ${datatypes[@]}; do
+        for part in ${parts[@]}; do
+
+            #Add correlation tables
+            git add ${datapath}/${detector}_${datatype}_${part}.corr
+            git add ${datapath}/${detector}_${datatype}_${part}_fred05.corr
+
+            #Add datatables for preliminary runs
+            git add ${datapath}/prel/${detector}_${datatype}_${part}-thexp.dat
+
+            #Add datatables for final runs
+            for pdf in ${pdfs[@]}; do
+                for unctype in ${unctypes[@]}; do
+                    git add ${datapath}/${pdf}/${unctype}/${detector}_${datatype}_${part}-thexp.dat
+                done
+            done
+
+        done
+    done
+done
+
+#Add PDF_profiling files
+profilingpath=xFitter/PDF_profiling
+declare -a xFrunFiles=("constants.yaml" "parameters.yaml" "steering.txt" "plot.sh" "run.sh")
+declare -a xFprelFiles=("constants.yaml" "parameters.yaml" "steering.txt" "run.sh")
+for pdf in ${pdfs[@]}; do
+
+    if [[ ${pdf}=="PDF4LHC21" ]]; then
+        declare -a statOnlyDirs=("FASERv" "FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination")
[…]

### 2023-08-17 paper/sec-dis-pseudodata.tex
Start updating plots

@@
     \includegraphics[width=0.495\textwidth]{plots/FPF-FASERv.pdf}
-    \includegraphics[width=0.495\textwidth]{plots/FPF-SND.pdf}
     \includegraphics[width=0.495\textwidth]{plots/FPF-FASERv2.pdf}
+    \includegraphics[width=0.495\textwidth]{plots/FPF-AdvSND.pdf}
     \includegraphics[width=0.495\textwidth]{plots/FPF-FLArE100.pdf}
@@
       scattering at the
-      FASER$\nu$, AdvSND, FASER$\nu$2, and FLArE-100  experiments.
+      FASER$\nu$, FASER$\nu$2, AdvSND, and FLArE-100  experiments.
             %
@@
 	Adding up the bins in each of the panels results into the numbers listed in
-	Table~\ref{tab:integrated_rates}.
-	\textcolor{red}{(To be replaced with the results from the new fluxes, SND $\to$ AdvSND)}}
+	Table~\ref{tab:integrated_rates}.}
     \label{fig:fasernu2_muon}
@@
   \centering
-  \includegraphics[width=\textwidth]{plots/percentage_errors.pdf}
+  \includegraphics[width=\textwidth]{plots/FASERv2_fractional_error.pdf}
   \caption{\small Estimated systematic uncertainties for the  measurements

### 2023-08-17 paper/sec-dis-pseudodata.tex
final plots w/ correct descriptions

@@
 We have verified that the differential event yield calculation
-implemented in Eq.~(\ref{eq:event_yields_calculation}) {\color{blue} [MF: There is a discrepancy beyond this.
-Our integrated cross sections come out a bit smaller.
-The total cross sections are very sensitive to kinematic cuts.
-TR and I have talked about this before and I will message] }, when extrapolated to a single bin
+implemented in Eq.~(\ref{eq:event_yields_calculation}), when extrapolated to a single bin
 covering the full detector acceptance,
@@
     \includegraphics[width=0.495\textwidth]{plots/FPF-FLArE100.pdf}
-    \caption{\small The event yields per bin $N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}), for muon neutrino
-      scattering at the
-      FASER$\nu$, FASER$\nu$2, AdvSND, and FLArE-100  experiments.
+    \caption{
+    	\small The event yields per bin $N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}), for 
+    	muon neutrino scattering at the FASER$\nu$, FASER$\nu$2, AdvSND, and FLArE-100  experiments.
         %
    		Selected events are restricted to the DIS region Eq.~(\ref{eq:DISconditions})
-      and only bins with $\ge 30$ events are retained.
+   		and only bins with $\ge 100$ events are retained except for FASER$\nu$ in which
+   		bins with $\ge 10$ events are kept.
 		%
@@
     \centering
-    \includegraphics[width = 0.85\textwidth]{plots/KIN_DIS_FPF.pdf}
-    \caption{The kinematic coverage in the $(x,Q^2)$ plane of muon-neutrino scattering
+    \includegraphics[width = 0.75\textwidth]{plots/KIN_DIS_FPF.pdf}
+    \caption{
+    	The kinematic coverage in the $(x,Q^2)$ plane of muon-neutrino scattering
 	    at the FASER$\nu$, FASER$\nu$2, FLArE-100, and AdvSND experiments, see also Fig.~\ref{fig:fasernu2_muon},
@@
       	%
-      Bins with less than 30 events have been excluded.{\color{blue}[ MF: Currently, not 30 -  10 for Run3 expt's and 100 for HL-LHC expts]}
-      %
-      \textcolor{red}{(To be replaced once AdvSND and new fluxes are available.)}
+      	Bins with less than 100 events have been excluded fo all the pseudodata except for FASER$\nu$ where we retain
+      	bins with $\ge 10$ events.
   	}

### 2023-08-18 paper/sec-dis-pseudodata.tex
Fix some of Max's comments

@@
 %
-With a total fiducial volume of 830 kg {\color{blue}[ MF: and length of 35 cm]}, it is composed by tungsten plates,
+With a total fiducial volume of 830 kg and length of 35 cm, it is composed by tungsten plates,
 where neutrino scattering takes place, interleaved with nuclear emulsions and electronic tracker
@@
  composed (from upstream to downstream) by a target region
- for  vertex reconstruction and electromagnetic energy measurement, followed  by a hadronic calorimeter, a  muon identification system, and finally  a magnet enabling muon charge and momentum measurements.
- %
- The target region of the detector, where the neutrino interactions take place, is made of thin sensitive layers interleaved with tungsten plates, for a total mass of 5 tons {\color{blue} [MF: and fiducial length of 50 cm]}.
+ for  vertex reconstruction and electromagnetic energy measurement, followed  by a hadronic calorimeter, a  muon 
+ identification system, and finally  a magnet enabling muon charge and momentum measurements.
+ %
+ The target region of the detector, where the neutrino interactions take place, is made of thin sensitive layers 
+ interleaved with tungsten plates, for a total mass of 5 tons and fiducial length of 50 cm.
  %
@@
 
- With an expected fiducial (active) mass of 10 tons (30 tons) {\color{blue} [MF: and length 3 m]}, FLArE will
+ With an expected fiducial (active) mass of 10 tons (30 tons) and length 3 m, FLArE will
  detect final-state electrons with energies $E_{e}\lsim 2~\rm{TeV}$ and
@@
 %
-Since we discard bins with less than 30 events{\color{blue} [MF: not 30. Currently 10 for Run3, 100 for HL-LHC]}, the fractional statistical uncertainty
+Since we discard bins with less than 100 events for HL-LHC experiments (FASER$\nu$2, FLArE100, AdvSND) and
+10 events for Run III experiments (FASER$\nu$, SND), the fractional statistical uncertainty
 ranges between $\lsim 1\%$ and $\sim 18\%$, depending on the values of
@@
 %
-By comparing $\mathcal{D}_0$ with the total number of events as calculated by Eq.~(\ref{MCintegration}), we can normalize the distribution to produce the expected yield.{\color{blue} [MF:changed some wording here ]}
-%By integrating over this sample by means of Eq.~(\ref{MCintegration}), we determine
-%the binned event yields for this reference $\mathcal{D}_0$ sample.
+By comparing $\mathcal{D}_0$ with the total number of events as calculated by Eq.~(\ref{MCintegration}), 
+we can normalize the distribution to produce the expected yield.
 
@@
 \ee
-{\color{blue} [MF:Changed some wording here and the equation slighlty to what we do]}
 
@@
 In general, systematic uncertainties associated to the hadronic final state energy $E_h$ appear to be the largest,
-reaching up to $\sim 40\%$.{\color{blue} [MF: Sometimes uncertainties can be huge more than 100\%.
-We ignore these bins.
-Fig 2.4 will also be updated soon probably, and here we will see some larger uncerainties due to the updated cross sections.]}
+reaching up to $\sim 90\%$ for some experiments.
 %

### 2023-08-18 paper/sec-dis-pseudodata.tex
faserv fiducial length

@@
 detector, composed by interleaved emulsion and tungsten plates and
-adding up to a mass of 1.1 tons with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 30~{\rm cm}$ {\color{blue} [MF: Is 30 cm correct?
-The length I have is 100 cm.
-Looking at \cite{FASER:2023zcr}, I think that the final length of tungsten might be closer to 80cm = 730 layers * 1.1mm/layer]}.
+adding up to a mass of 1.1 tons with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 80~{\rm cm}$.
 %

### 2023-08-21 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/syst/collectPlots.tex
Uploading xFitter results with the latest tables, including full FPF result FASERv2+FLArE10+AdvSND

--- 2023-06-04 xFitter/PDF_profiling/PDF4LHC21/statOnly/collectPlots.tex
@@
 \newcommand{\experiment}{FASERv2}
-\newcommand{\unctype}{statOnly}
+\newcommand{\unctype}{syst}
 
@@
 \renewcommand{\dataset}{_charm_nochargediscrimination}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}
+
+\newpage
+
+FASERv2+FLArE10+AdvSND\\
+\renewcommand{\experiment}{FPF}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}
 

### 2023-08-21 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/statOnly/FPF/plot.sh

@@ -1,0 +1,24 @@
+DETECTOR="FPF"
+DETSIMPLE="FPF"
+UNCLVL="statOnly"
+
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-21 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/syst/FPF/plot.sh

@@ -1,0 +1,23 @@
+DETECTOR="FPF"
+DETSIMPLE="FPF"
+UNCLVL="syst"
+
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:../../statOnly/${DETSIMPLE}/output:"BL+${DETECTOR}, stat" profile:output:"BL+${DETECTOR}, stat+syst"
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-21 xFitter/PDF_profiling/PDF4LHC21/statOnly/AdvSND/plot.sh

@@ -1,0 +1,25 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter
+#    sh plot.sh
+
+DETECTOR="AdvSND"
+DETSIMPLE="AdvSND"
+UNCLVL="statOnly"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-21 xFitter/PDF_profiling/PDF4LHC21/statOnly/FLArE100/plot.sh

@@ -1,0 +1,25 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter
+#    sh plot.sh
+
+DETECTOR="FLArE"
+DETSIMPLE="FLArE100"
+UNCLVL="statOnly"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-21 xFitter/PDF_profiling/PDF4LHC21/statOnly/FPF/plot.sh

@@ -1,0 +1,25 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter
+#    sh plot.sh
+
+DETECTOR="FPF"
+DETSIMPLE="FPF"
+UNCLVL="statOnly"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-21 xFitter/gitAdder.sh

@@ -43,13 +43,17 @@ declare -a xFprelFiles=("constants.yaml" "parameters.yaml" "steering.txt" "run.s
 for pdf in ${pdfs[@]}; do
 
     if [[ ${pdf}=="PDF4LHC21" ]]; then
-        declare -a statOnlyDirs=("FASERv" "FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination")
-        declare -a systDirs=("FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination" )
-        declare -a fred05Dirs=("FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination")
+        declare -a statOnlyDirs=("FASERv" "AdvSND" "FLArE100" "FLArE10" "FPF" "FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination")
+        declare -a systDirs=("FPF" "FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination" )
+        declare -a fred05Dirs=("FPF" "FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination")
+        declare -a fcorr05Dirs=("FPF" "FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination")
[…]

### 2023-08-21 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/fred05fcorr05/FPF/plot.sh
Including optimistic case with reduction and correlation factors

@@ -1,0 +1,24 @@
+DETECTOR="FPF"
+DETSIMPLE="FPF"
+UNCLVL="fred05fcorr05"
+
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-21 xFitter/PDF_profiling/PDF4LHC21/fred05fcorr05/FASERv2/plot.sh

@@ -1,0 +1,27 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="fred05fcorr05"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:../../statOnly/${DETSIMPLE}/output:"BL+${DETECTOR}, stat" profile:output:"BL+${DETECTOR}, stat+syst"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-21 xFitter/PDF_profiling/PDF4LHC21/fred05fcorr05/FLArE100/plot.sh

@@ -1,0 +1,27 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FLArE100"
+DETSIMPLE="FLArE100"
+UNCLVL="fred05fcorr05"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:../../statOnly/${DETSIMPLE}/output:"BL+${DETECTOR}, stat" profile:output:"BL+${DETECTOR}, stat+syst"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-21 xFitter/PDF_profiling/PDF4LHC21/fred05fcorr05/FPF/plot.sh

@@ -1,0 +1,27 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FPF"
+DETSIMPLE="FPF"
+UNCLVL="fred05fcorr05"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:../../statOnly/${DETSIMPLE}/output:"BL+${DETECTOR}, stat" profile:output:"BL+${DETECTOR}, stat+syst"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-08-21 xFitter/gitAdder.sh

@@ -139,7 +139,7 @@ for pdf in ${pdfs[@]}; do
     done
 
     #With statistical and systematic uncertainties (0.5 improvement & correlation factors)
-    for subDir in ${fred50fcorr05Dirs[@]}; do
+    for subDir in ${fred05fcorr05Dirs[@]}; do
         unctype="fred05fcorr05"
         git add ${profilingpath}/${pdf}/${unctype}/collectPlots.tex                
         git add ${profilingpath}/${pdf}/${unctype}/run.sh

### 2023-08-22 paper/sec-nuclearPDFs.tex
Updated xFitter plots, also including AdvSND, FLArE10 and FASERv2 results

--- 2023-07-05 paper/sec-nuclearPDFs.tex
@@
 
-Fig.~\ref{fig:profiling_baseline_nuclear} displays the same comparisons
-as in Fig.~\ref{fig:profiling_baseline},
-now for the profiling of the EPPS21 global determination of nuclear PDFs,
+Fig.~\ref{fig:profiling_syst_nuclear} displays the baseline result of the profiling using the EPPS21 global determination of nuclear PDFs,
 specifically of the set with $A=184$ (tungsten target).
@@
 Also in this case we consider first the impact of the baseline LHC neutrino dataset, consisting
-on the FASER$\nu$2 experiment
-with statistical errors only, inclusive and charm structure functions,  and charge flavour
+on the FASER$\nu$2 experiment inclusive and charm structure functions,  and charge flavour
 separation. 
+The bands indicate the 68\% CL uncertainties, 
+both for the case assuming statistical unertainties only, 
+as well as including an estimate for both statistical and systematic uncertainties.
+The result from using the full FPF set comprising of AdvSND, FASER$\nu$2 and FLArE pseudodata is shown in Fig.~\ref{fig:profiling_FPF_nuclear}.
 %
-The bands indicate the 68\% CL uncertainties.
 
-{\color{red}
-The effect of including correlated systematic uncertainties is shown in 
-Fig.~\ref{fig:profiling_syst_nuclear}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{Same as Fig.~\ref{fig:profiling_baseline},
-now for the profiling of the EPPS21 global determination of nuclear PDFs,
-specifically of the set with $A=184$ (tungsten target).
-%
-Also in this case we consider first the impact of the baseline LHC neutrino dataset, consisting
-on the FASER$\nu$2 experiment
-with statistical errors only, inclusive and charm structure functions,  and charge flavour
-separation.
-%
-The bands indicate the 68\% CL uncertainties.
-}
-\label{fig:profiling_baseline_nuclear}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{The results of Fig.~\ref{fig:profiling_baseline_nuclear} (red and blue), 
-compared to profiling with the statistical as well as correlated systematic uncertainties accounted for.
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\caption{The fractional uncertainties (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ of the EPPS21 global determination of nuclear PDFs (red),
+specifically of the set with $A=184$ (tungsten target), 
+compared to the results of profiling with the FASER$\nu$2 DIS projections.
+The impact of the baseline LHC neutrino dataset, 
+consisting of the FASER$\nu$2 experiment inclusive and charm structure functions and charge flavour separation,
+assuming statistical errors only (blue), 
+is compared to the case accounting for both statistical and systematic uncertainties (green).
 }
@@
 \includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{Comparing Fig.~\ref{fig:profiling_baseline_nuclear}, 
-to the results obtained without charm production structure functions.
+\caption{The effect of FASER$\nu$2 structure functions once charm-tagged measurements are removed, assuming only statistical uncertainties in both cases.
 }
@@
 \includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{Comparing the results shown in Fig.~\ref{fig:profiling_baseline_nuclear} (red and blue), 
-to the results obtained without identifying the charge of the outgoing lepton (green).
+\caption{The effect of being unable to identify the charge of the outgoing lepton in the FASER$\nu$2 pseudodata, assuming only statistical uncertainties.
 }
@@
 
-Plots EPPS21 tungsten target? To quantify size of nuclear modifications?
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_s_ratio.pdf}
+\caption{The impact of the full FPF pseudodataset in profiling using the EPPS21 global determination of nuclear PDFs (red), specifically for $A=184$.
+The 68\% CL uncertainty bands resulting from assuming only statistical (statistical and systematic) uncertainties are shown in blue (green).
+}
+\label{fig:profiling_FPF_nuclear}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-08-22 paper/sec-protonPDFs.tex
Updated xFitter plots, also including AdvSND, FLArE10 and FASERv2 results

--- 2023-07-28 paper/sec-protonPDFs.tex
@@
 \centering
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_s_ratio.pdf}
 \caption{
@@
 \includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{Same as Fig.~\ref{fig:profiling_syst}, now assessing the impact of FASER$\nu$2 structure functions
-once charm-tagged measurements are removed.
-%
-In both cases, the covariance matrix accounts for systematic uncertainties.
+\caption{Assessing the impact of FASER$\nu$2 structure functions
+once charm-tagged measurements are removed, assuming only statistical 
+uncertainties in both cases.
 }
@@
 \caption{
-Same as Fig.~\ref{fig:profiling_syst}, now assessing the impact of that being unable to identify
-the charge of the outgoing lepton would have on the FASER$\nu$2 reach on the proton PDFs.
-%
-In both cases, the covariance matrix accounts for systematic uncertainties.
+Assessing the impact that being unable to identify
+the charge of the outgoing lepton would have on the FASER$\nu$2 reach on the proton PDFs, assuming only statistical 
+uncertainties in both cases.
 }
@@
 
-{\bf add discussion of experiment sensitivity}
 %
-Same as Fig.~\ref{fig:profiling_syst} comparing FASER$\nu$2 with AdvSND and with FASER$\nu$.
+Fig.~\ref{fig:profiling_FASERv2_vs_FASERv} shows a comparison of the impact 
+that FASER$\nu$2 and FASER$\nu$ pseudodata have in PDF profiling, illustrating 
+the improvement in precision obtainable with FASER$\nu$2.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_s_ratio.pdf}
+\caption{
+A comparison of the effect of FASER$\nu$ and FASER$\nu2$ pseudodata in profiling, 
+assuming only statistical uncertainties in the case of both experiments.
+}
+\label{fig:profiling_FASERv2_vs_FASERv}
+\end{figure}
+
+Besides FASER$u$2, further FPF detectors may also be used for constraining the PDFs. 
+Fig.~\ref{fig:profiling_FASERv2_vs_AdvSND} illustrates the effect of using the AdvSND pseudodata alone, 
+shown together with the previous result of using only FASER$\nu$2 pseudodata. 
+Fig.~\ref{fig:profiling_FASERv2_vs_FLArE10} shows a similar comparison, 
+but using FLArE pseudodata instead of AdvSND. 
+Most importantly however, all these datasets can be included to obtain a complete FPF result, 
+shown in Fig.~\ref{fig:profiling_FPF}.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_AdvSND/statOnly_AdvSND_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_AdvSND/statOnly_AdvSND_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_AdvSND/statOnly_AdvSND_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_AdvSND/statOnly_AdvSND_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_AdvSND/statOnly_AdvSND_q2_10000_pdf_s_ratio.pdf}
+\caption{
+A comparison of the effect of FASER$\nu2$ and AdvSND pseudodata in profiling, 
+assuming only statistical uncertainties in the case of both experiments.
+}
+\label{fig:profiling_FASERv2_vs_AdvSND}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FLArE10/statOnly_FLArE10_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FLArE10/statOnly_FLArE10_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FLArE10/statOnly_FLArE10_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FLArE10/statOnly_FLArE10_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FLArE10/statOnly_FLArE10_q2_10000_pdf_s_ratio.pdf}
+\caption{
+A comparison of the effect of FASER$\nu2$ and FLArE pseudodata in profiling, 
+assuming only statistical uncertainties in the case of both experiments.
+}
+\label{fig:profiling_FASERv2_vs_FLArE10}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_s_ratio.pdf}
+\caption{
+A comparison of the effect of combined  AdvSND, FASER$\nu2$ and FLArE pseudodata in profiling. 
+The results obtained assuming only statistical (statistical+systematic) uncertainties are shown in blue (red).
+}
+\label{fig:profiling_FPF}
+\end{figure}
 

### 2023-08-22 paper/app-faser.tex
sect 3

--- 2023-07-31 paper/sec-protonPDFs.tex
@@
-\section{Constraints on proton structure}
-\label{sec:protonPDFs}
-
-By means of the strategy outlined in Sect.~\ref{sec:settings}, here we study the constraints that differential neutrino DIS
-cross-section measurements at the LHC have on the quark and gluon substructure of the proton.
-%
-We assume an isoscalar free-nucleon target and neglect non-isoscalarity effects and nuclear modifications,
-which are instead considered in Sect.~\ref{sec:nuclearPDFs}.
-
-We present results first for the Hessian profiling of the PDF4LHC21 combination,
-and second for the inclusion in the Monte Carlo fit NNPDF4.0.
-%
-We study the stability of the results with respect to the inclusion of systematic uncertainties
-and  charm-tagged events, as well to the availability of outgoing lepton-charge separation.
-%
-We compare the impact of four of the experiments considered in Sect.~\ref{sec:dis_pseudodata}:
-FASER$\nu$ and SND@LHC (LHC Run III) with FASER$\nu$2 and AdvSND (HL-LHC).
-
-\subsection{Hessian profiling of PDF4LHC21}
-\label{sec:pdf4lhc21}
-
-For the Hessian profiling studies based on the procedure of Sect.~\ref{sec:profiling}, the prior PDF set is taken to
-be PDF4LHC21 NNLO, a Monte Carlo combination~\cite{Watt:2012tq,Carrazza:2015hva} of three global PDF sets (CT18~\cite{Hou:2019efy},
-MSHT20~\cite{Bailey:2020ooq}, and NNPDF3.1~\cite{NNPDF:2017mvq}).
-%
-The Hessian representations of PDF4LHC21 are obtained by means of the methodology developed in~\cite{Gao:2013bia,Carrazza:2015aoa}.
-%
-Being based on the combination of three modern global PDF fits, PDF4LHC21 provides a robust estimate
-of  current uncertainties associated to our understanding of proton PDFs.
-%
-We profile PDF4LHC21 with various sets of LHC neutrino DIS projections in order to assess the stability
-of the results with respect to its different inputs, such as charm-tagged structure functions.
-%
-The consistent perturbative accuracy of the prior PDF set and the theoretical calculations entering
-the pseudo-data generation is always accounted for.
-
-For the baseline results, we consider FASER$\nu$2 operative for the full duration
-of the HL-LHC data-taking period.
-%
-Both inclusive and charm-tagged structure functions enter the profiling,
-and outgoing lepton charge-separation is assumed.
-%
-Fig.~\ref{fig:profiling_syst} displays the
-fractional uncertainties   (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
-for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
-in PDF4LHC21 compared to the results of its profiling with the FASER$\nu$2 projections.
-%
-For the latter, we consider two scenarios: first where the covariance matrix includes
-only statistical errors, and second with experimental systematic
-errors added in quadrature to the statistical ones.
-%
-Note that the residual shift in central values, which depends on the arbitrary fluctuations
-entering the pseudo-data generation, is not displayed.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/systVar05_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{
-The fractional uncertainties   (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
-for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
-in PDF4LHC21 compared to the results of its profiling with the FASER$\nu$2
-DIS projections.
-%
-In the latter case, we consider both only statistical errors and statistical and systematic
-errors added in quadrature.
-%
-The FASER$\nu$2 dataset used here accounts for both  inclusive and charm-tagged structure functions
-as well as for outgoing lepton charge-separation.
-%
-}
-\label{fig:profiling_syst}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Inspection of Fig.~\ref{fig:profiling_syst} reveals that measurement of DIS structure
-functions at FASER$\nu$2 impose stringent constraints on the quark PDFs, while leaving
-the gluon PDF essentially unaffected.
-%
-As expected for a neutrino scattering experiment, its impact is most marked for
-those PDF combinations sensitive to quark flavour separation such as $u_V$, $d_V$, and
-$s^+$.
-%
-The reduction of PDF uncertainties is particularly significant for the total strangeness PDF,
-as  consequence of the inclusion of charm-tagged structure functions in the fit as we demonstrate below.
-%
-Crucially, one finds that for the assumptions on the systematic uncertainties
-discussed in Sect~\ref{sec:dis_pseudodata}, the PDF sensitivity is only marginally degraded
-as compared to the case in which systematic errors are neglected.
-%
-This result is consistent with Fig.~\ref{fig:percentage_uncertainties_overview}, showing
-how in most bins systematic and statistical errors are of similar magnitude.
-
-In the following, we consider the results obtained using only statistical uncertainties as the baseline, 
-and examine stability of these results with respect to the chosen experiment and integrated luminosity, the modelling of systematic
-uncertainties, being able to identify or not charm production, and being able to tell part outgoing
-charged leptons from anti-leptons.
+\section{Impact of FASER$\nu$ Run III measurements}
+\label{app:fasernu_runIII_impact}
 
 %
-Fig.~\ref{fig:profiling_charm} displays a comparison of the baseline LHC neutrino dataset with the results
-of profiling without the charm production structure functions. 
-Particularly, the constraints on the $s$ PDF are observed to become more stringent 
-by virtue of the contribution of the charm production structure functions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{Same as Fig.~\ref{fig:profiling_syst}, now assessing the impact of FASER$\nu$2 structure functions
-once charm-tagged measurements are removed.
-}
-\label{fig:profiling_charm}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%
-Fig.~\ref{fig:profiling_nochargediscrimination} compares the baseline LHC neutrino dataset with the results
-of a profiling without allowing for the possibility of outgoing lepton charge separation.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{
-Assessing the impact that being unable to identify
-the charge of the outgoing lepton would have on the FASER$\nu$2 reach on the proton PDFs.
-}
-\label{fig:profiling_nochargediscrimination}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%
-Fig.~\ref{fig:profiling_experiment_comparison} shows a comparison of the impact 
+Fig.~\ref{fig:profiling_FASERv2_vs_FASERv} shows a comparison of the impact 
 that FASER$\nu$2 and FASER$\nu$ pseudodata have in PDF profiling, illustrating 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[t]
 \centering
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/experiment_comparison/statOnly_FASERv_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/experiment_comparison/statOnly_FASERv_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/experiment_comparison/statOnly_FASERv_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/experiment_comparison/statOnly_FASERv_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/experiment_comparison/statOnly_FASERv_q2_10000_pdf_s_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_s_ratio.pdf}
 \caption{
@@
 }
-\label{fig:profiling_experiment_comparison}
+\label{fig:profiling_FASERv2_vs_FASERv}
 \end{figure}
-
-\subsection{Impact on NNPDF4.0}
-\label{sec:nnpdf40}
-
-Selection of the {\sc\small xFitter} results for the NNPDF case.
-
-Fig.~\ref{fig:nnpdf40_fasernu2_baseline} presents the same comparison
-as in Fig.~\ref{fig:profiling_syst} now for
- the fits
- based on the NNPDF4.0 global analysis.
- %
- The impact on the PDFs found by direct inclusion of the FPF structure
- functions on the NNPDF4.0 fit is qualitatively consistent with
- that found from the Hessian profiling of PDF4LHC21.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.99\textwidth]{plots/FASERnu2-q100gev-ratios.pdf}
-\caption{
-  Same as Fig.~\ref{fig:profiling_syst} now for the fits
-  based on the NNPDF4.0 global analysis.
-%
-}
-\label{fig:nnpdf40_fasernu2_baseline}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-08-22 paper/app-nuclearPDFs.tex
sect 3

--- 2023-08-22 paper/sec-nuclearPDFs.tex
@@
 \clearpage
-\section{Impact on nuclear PDFs}
-\label{sec:nuclearPDFs}
-
-The study presented in Sect.~\ref{sec:protonPDFs} treated, from the point of view
-of PDF constraints, the neutrino scattering target
-as composed by isoscalar free-nucleons, and hence neglecting nuclear modifications
-and non-isoscalar effects.
-%
-We now revisit this analysis but accounting for the fact that the target materials in the FPF
-experiments actually
-composed by heavy nuclei, specifically by tungsten (the exception is FLArE with liquid argon, which
-is however not considered here).
-%
-Nuclear modifications associated to a tungsten target are not necessarily small as compared
-to a free isoscalar nucleon, and hence will affect the event rate predictions for
-the FPF experiments.
-%
-Turning the argument around, measurements of differential neutrino cross-sections
-on heavy nuclear targets provide direct constraints on these nuclear modifications
-without replying on assumptions on the $A$ dependence.
-
-For this exercise, the prior nuclear PDF set is taken to be EPPS21, a global determination
-that accounts for the constraints of existing datasets involving nuclei as target or projectiles.
-%
-In particular, EPPS21 already includes information from neutrino DIS on nuclear targets
-from the CHORUS and NuTeV experiments.
-%
-The application of Hessian profiling to EPPS21 follows the same strategy as that
-for PDF4LHC21, with the caveat that its Hessian error sets also include the contribution
-from the uncertainties  associated to their reference proton PDF set, in this case CT18.
-%
-Given that the measured event rates depend on both the proton PDFs and the nuclear modifications,
-when profiling EPPS21 we also account for the Hessian sets associated to the CT18 proton
-PDF dependence.
-
-Fig.~\ref{fig:profiling_syst_nuclear} displays the baseline result of the profiling using the EPPS21 global determination of nuclear PDFs,
-specifically of the set with $A=184$ (tungsten target).
-%
-Also in this case we consider first the impact of the baseline LHC neutrino dataset, consisting
-on the FASER$\nu$2 experiment inclusive and charm structure functions,  and charge flavour
-separation. 
-The bands indicate the 68\% CL uncertainties, 
-both for the case assuming statistical unertainties only, 
-as well as including an estimate for both statistical and systematic uncertainties.
-The result from using the full FPF set comprising of AdvSND, FASER$\nu$2 and FLArE pseudodata is shown in Fig.~\ref{fig:profiling_FPF_nuclear}.
-%
+\section{Impact of FPF DIS data on nuclear PDFs}
+\label{app:nPDF_impact_appendix}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_s_ratio.pdf}
-\caption{The impact of the full FPF pseudodataset in profiling using the EPPS21 global determination of nuclear PDFs (red), specifically for $A=184$.
-The 68\% CL uncertainty bands resulting from assuming only statistical (statistical and systematic) uncertainties are shown in blue (green).
-}
-\label{fig:profiling_FPF_nuclear}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-08-22 paper/sec-protonPDFs.tex
sect 3

@@
-\section{Constraints on proton structure}
+\section{Constraints on proton and nuclear structure}
 \label{sec:protonPDFs}
 
-By means of the strategy outlined in Sect.~\ref{sec:settings}, here we study the constraints that differential neutrino DIS
-cross-section measurements at the LHC have on the quark and gluon substructure of the proton.
+By means of the strategy outlined in Sect.~\ref{sec:dis_pseudodata}, here
+we quantify the impact on the proton PDFs
+of differential  DIS
+cross-section measurements exploiting the  LHC
+neutrino beam. 
 %
@@
 which are instead considered in Sect.~\ref{sec:nuclearPDFs}.
+%
+We present results first for the Hessian profiling of the PDF4LHC21,
+and second for the Monte Carlo fit NNPDF4.0.
+%
+We study the stability of the results with respect to the inclusion of systematic uncertainties,
+charm-tagged data, and lepton-charge separation.
+%
+We compare the impact of the different FPF experiments separately and also provide
+results for their combination.
 
-We present results first for the Hessian profiling of the PDF4LHC21 combination,
-and second for the inclusion in the Monte Carlo fit NNPDF4.0.
-%
-We study the stability of the results with respect to the inclusion of systematic uncertainties
-and  charm-tagged events, as well to the availability of outgoing lepton-charge separation.
-%
-We compare the impact of four of the experiments considered in Sect.~\ref{sec:dis_pseudodata}:
-FASER$\nu$ and SND@LHC (LHC Run III) with FASER$\nu$2 and AdvSND (HL-LHC).
-
-\subsection{Hessian profiling of PDF4LHC21}
+\subsection{Impact on PDF4LHC21}
 \label{sec:pdf4lhc21}
@@
 for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
-in PDF4LHC21 compared to the results of its profiling with the FASER$\nu$2
-DIS projections.
+in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 pseudo-data is included.
 %
-In the latter case, we consider both only statistical errors and statistical and systematic
-errors added in quadrature.
+The FASER$\nu$2 impact projections are provided both without and with systematic
+uncertainties accounted for.
 %
-The FASER$\nu$2 dataset used here accounts for both  inclusive and charm-tagged structure functions
-as well as for outgoing lepton charge-separation.
+We include both  both  inclusive and charm-tagged structure functions
+and assume outgoing lepton charge-separation.
 %
 }
-\label{fig:profiling_syst}
+\label{fig:FASERnu2_baseline}
 \end{figure}
@@
 \includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{Assessing the impact of FASER$\nu$2 structure functions
-once charm-tagged measurements are removed, assuming only statistical 
-uncertainties in both cases.
+\caption{Same as Fig.~\ref{fig:FASERnu2_baseline} (statistical uncertainties only),
+  now showing results in the scenario where charm-tagged structure function measurements
+  are excluded from the analysis.
 }
-\label{fig:profiling_charm}
+\label{fig:FASERnu2_nocharm}
 \end{figure}
@@
 of a profiling without allowing for the possibility of outgoing lepton charge separation.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{
-Assessing the impact that being unable to identify
-the charge of the outgoing lepton would have on the FASER$\nu$2 reach on the proton PDFs, assuming only statistical 
-uncertainties in both cases.
+\caption{Same as Fig.~\ref{fig:FASERnu2_baseline} (statistical uncertainties only),
+  now showing results in the scenario where the charge of the final-state charged lepton
+  cannot be identified.
  }
-\label{fig:profiling_nochargediscrimination}
+\label{fig:FASERnu2_nochargeID}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%
-Fig.~\ref{fig:profiling_FASERv2_vs_FASERv} shows a comparison of the impact 
-that FASER$\nu$2 and FASER$\nu$ pseudodata have in PDF profiling, illustrating 
-the improvement in precision obtainable with FASER$\nu$2.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_s_ratio.pdf}
-\caption{
-A comparison of the effect of FASER$\nu$ and FASER$\nu2$ pseudodata in profiling, 
-assuming only statistical uncertainties in the case of both experiments.
-}
-\label{fig:profiling_FASERv2_vs_FASERv}
-\end{figure}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[t]
@@
 \caption{
-A comparison of the effect of FASER$\nu2$ and AdvSND pseudodata in profiling, 
-assuming only statistical uncertainties in the case of both experiments.
+  Same as  Fig.~\ref{fig:FASERnu2_baseline} (statistical uncertainties only), comparing
+  the projected PDF impact of FASER$\nu$2 with that of AdvSND.
 }
-\label{fig:profiling_FASERv2_vs_AdvSND}
+\label{fig:FASERnu2_advsnd}
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[t]
@@
 \caption{
-A comparison of the effect of FASER$\nu2$ and FLArE pseudodata in profiling, 
-assuming only statistical uncertainties in the case of both experiments.
+  Same as Fig.~\ref{fig:FASERnu2_advsnd},
+  comparing
+  the projected PDF impact of FASER$\nu$2 with that of FLArE10. 
 }
-\label{fig:profiling_FASERv2_vs_FLArE10}
+\label{fig:FASERnu2_FLAre10}
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[t]
@@
 \caption{
-A comparison of the effect of combined  AdvSND, FASER$\nu2$ and FLArE pseudodata in profiling. 
-The results obtained assuming only statistical (statistical+systematic) uncertainties are shown in blue (red).
+  Same as Fig.~\ref{fig:FASERnu2_baseline} now quantifying the
+  projected PDF impact of the three FPF experiments added simultaneously to
+  the analysis: FASER$\nu$2, AdvSND, and FLArE10. 
 }
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage
+
+\subsection{Impact on EPPS21}
+\label{sec:nuclearPDFs}
+
+The study presented in Sect.~\ref{sec:protonPDFs} treated, from the point of view
+of PDF constraints, the neutrino scattering target
+as composed by isoscalar free-nucleons, and hence neglecting nuclear modifications
+and non-isoscalar effects.
+%
+We now revisit this analysis but accounting for the fact that the target materials in the FPF
+experiments actually
+composed by heavy nuclei, specifically by tungsten (the exception is FLArE with liquid argon, which
+is however not considered here).
+%
+Nuclear modifications associated to a tungsten target are not necessarily small as compared
+to a free isoscalar nucleon, and hence will affect the event rate predictions for
+the FPF experiments.
+%
+Turning the argument around, measurements of differential neutrino cross-sections
+on heavy nuclear targets provide direct constraints on these nuclear modifications
+without replying on assumptions on the $A$ dependence.
+
+For this exercise, the prior nuclear PDF set is taken to be EPPS21, a global determination
+that accounts for the constraints of existing datasets involving nuclei as target or projectiles.
+%
+In particular, EPPS21 already includes information from neutrino DIS on nuclear targets
+from the CHORUS and NuTeV experiments.
+%
+The application of Hessian profiling to EPPS21 follows the same strategy as that
+for PDF4LHC21, with the caveat that its Hessian error sets also include the contribution
+from the uncertainties  associated to their reference proton PDF set, in this case CT18.
+%
+Given that the measured event rates depend on both the proton PDFs and the nuclear modifications,
+when profiling EPPS21 we also account for the Hessian sets associated to the CT18 proton
+PDF dependence.
+
+Fig.~\ref{fig:profiling_syst_nuclear} displays the baseline result of the profiling using the EPPS21 global determination of nuclear PDFs,
+specifically of the set with $A=184$ (tungsten target).
+%
+Also in this case we consider first the impact of the baseline LHC neutrino dataset, consisting
+on the FASER$\nu$2 experiment inclusive and charm structure functions,  and charge flavour
+separation. 
+The bands indicate the 68\% CL uncertainties, 
+both for the case assuming statistical unertainties only, 
+as well as including an estimate for both statistical and systematic uncertainties.
+The result from using the full FPF set comprising of AdvSND, FASER$\nu$2 and FLArE pseudodata is shown in Fig.~\ref{fig:profiling_FPF_nuclear}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_s_ratio.pdf}
+\caption{The impact of the full FPF pseudodataset in profiling using the EPPS21 global determination of nuclear PDFs (red), specifically for $A=184$.
+The 68\% CL uncertainty bands resulting from assuming only statistical (statistical and systematic) uncertainties are shown in blue (green).
+}
+\label{fig:profiling_FPF_nuclear}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-08-22 paper/app-faser.tex
app A

@@
+\clearpage
 \section{Impact of FASER$\nu$ Run III measurements}
@@
 
+The same procedure applied to the FPF experiments in Sect.~\ref{sec:pdf4lhc21}
+can also be used in the case of the FASER$\nu$ pseudo-data, generated under the
+assumption a Run III integrated
+luminosity of $\mathcal{L}=150$ fb$^{-1}$.
 %
-Fig.~\ref{fig:profiling_FASERv2_vs_FASERv} shows a comparison of the impact 
-that FASER$\nu$2 and FASER$\nu$ pseudodata have in PDF profiling, illustrating 
-the improvement in precision obtainable with FASER$\nu$2.
+As indicated by Table~\ref{tab:integrated_rates}, by the end of Run III, one expects
+that FASER$\nu$ will have recorded around 500 and 1500 electron- and muon-neutrinos
+respectively corresponding to deep-inelastic scattering events, of which around 100
+and 250 respectively are associated to charm-tagged events.
+%
+These projected event rates can be compared with the expectations
+for FASER$\nu$2, which predicts an increase in statistics of up to two orders
+of magnitude.
+
+Fig.~\ref{fig:FASERnu2_vs_FASERnu} presents a similar comparison as that of
+Fig.~\ref{fig:FASERnu2_baseline} now between that projected PDF impact of FASER$\nu$2 and that of
+FASER$\nu$, in the latter
+case for an integrated luminosity of $\mathcal{L}=150$ fb$^{-1}$.
+%
+One finds that neutrino DIS measurements at FASER$\nu$ are unable to improve
+PDF uncertainties as compared to the baseline scenario encapsulated by PDF4LHC21.
+%
+The reason is two-fold: the smaller event rates as compared to FASER$\nu$2,
+and the reduced coverage of the $(x,Q^2)$ phase space shown in Fig.~\ref{fig:fasernu2_muon}.
+%
+The striking differences in PDF sensitivity between FASER$\nu$ and FASER$\nu$2 in
+Fig.~\ref{fig:FASERnu2_vs_FASERnu} illustrate
+the key importance of realising the FPF in order to exploit the full physics potential enabled 
+by LHC neutrinos for QCD and hadron structure studies.
 
@@
 \includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_s_ratio.pdf}
-\caption{
-A comparison of the effect of FASER$\nu$ and FASER$\nu2$ pseudodata in profiling, 
-assuming only statistical uncertainties in the case of both experiments.
+\caption{Same as  Fig.~\ref{fig:FASERnu2_baseline} (statistical uncertainties only), comparing
+  the projected PDF impact of FASER$\nu$2 with that of FASER$\nu$, in the latter
+  case assuming the Run III integrated
+luminosity of $\mathcal{L}=150$ fb$^{-1}$.
 }
-\label{fig:profiling_FASERv2_vs_FASERv}
+\label{fig:FASERnu2_vs_FASERnu}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+It should be emphasized that the lack of PDF sensitivity displayed in Fig.~\ref{fig:FASERnu2_vs_FASERnu}
+does not imply that measuring DIS structure functions at FASER$\nu$ will not provide new information.
+%
+First of all, our procedure assumes perfect compatibility between current data and the projected DIS
+neutrino measurements at the LHC, something which remains to be demonstrated experimentally.
+%
+Second, FASER$\nu$ still covers a region of neutrino energies unexplored by previous experiments, hence providing
+a new validation of our QCD calculations and of neutrino interactions at the TeV scale.
+%
+Third, it would represent a non-trivial proof-of-concept that LHC neutrino differential measurements can be
+unfolded to the cross-section level such that they can be used in  theoretical
+interpretations, paving the way and demonstrating the feasibility of subsequent neutrino DIS
+measurements at the FPF experiments.

### 2023-08-22 paper/sec-introduction.tex
app A

@@
 directions for follow-up research.
+%
+Additional impact results are collected in two appendices:
+App.~\ref{app:fasernu_runIII_impact} studies the possible PDF impact
+of FASER$\nu$ Run III measurements, and App.~\ref{app:nPDF_impact_appendix}
+quantifies the stability of the nuclear PDF projections with respect
+of variations of its inputs.

### 2023-08-22 paper/sec-summary.tex
app A

@@
 Physics Facility initiative for many illuminating
-discussions and encouragement.
+discussions and encouragement along the course of this project.
 %
@@
 %
-We thank Akitaka Ariga and Tomoko Ariga for information
+We thank Akitaka Ariga and Tomoko Ariga for discussion
 concerning FASER$\nu$2, Milind Diwan,

### 2023-08-22 paper/FPF-WG1.tex
sect 2
Update FPF-WG1.tex
sect 3
app A
new abstract

@@
 
-Proton-proton collisions at the LHC produce an intense collimated beam of high-energy neutrinos
+Proton-proton collisions at the LHC produce an intense collimated beam of high-energy (TeV) neutrinos
 in the forward direction.
 %
-Their recent  observation by the FASER$\nu$ and SND@LHC experiments
-indicates that this hitherto discarded beam becomes now available for scientific studies.
+The recent  observation of LHC neutrinos by the FASER$\nu$ and SND@LHC experiments
+indicates that this hitherto ignored beam becomes available for scientific investigations.
 %
@@
 to provide a sensitive probe of the quark flavour separation in nucleons
-and nuclei, in particular strangeness.
+and nuclei.
 %
-Here we assess the expected impact of DIS neutrino structure functions at the LHC
+Here we quantify the projected impact of DIS neutrino structure functions at the LHC
 on the parton distribution functions (PDFs) of protons and heavy nuclei.
 %
-We consider projections for  FASER$\nu$ and SND@LHC based on the Run III luminosity
-and for the  experiments hosted by the
- Forward Physics Facility (FPF) operating concurrently with the HL-LHC.
+We generate differential structure function DIS pseudo-data 
+for  FASER$\nu$ and SND@LHC based on the Run III luminosity,
+as well as for the FASER$\nu$2, AdvSND, and FLArE experiments
+to be  hosted at the proposed
+ Forward Physics Facility (FPF) operating concurrently with the High Luminosity LHC.
  %
- By means of both Hessian profiling within {\sc\small xFitter} and
- of the  NNPDF open-source framework,
- we demonstrate the significant PDF impact of the high-statistics FPF data
- on the region $10^{-3}\lsim x \lsim 0.7$, comparable to that covered by the
- Electron-Ion Collider (EIC) with neutral-current scattering.
+ By using both the Hessian profiling of PDF4LHC21 with {\sc\small xFitter} and
+ the  NNPDF open-source framework,
+ we highlight the impact on the proton and nuclear PDFs of the FPF
+ experiments in a kinematic region in $x$ and $Q^2$ which is comparable to that
+ to be covered at the upcoming
+ Electron-Ion Collider (EIC).
  %
- Our analysis highlights how exploiting the potential
- of this unique neutrino beam  effectively
-extends the LHC with a ``Neutrino-Ion Collider''.
+ This sensitivity is found to be the largest for  strangeness as well as for
+ the up and down valence quark PDFs.
+%
+ Our analysis demonstrates how exploiting the potential
+ of this unique LHC neutrino beam  effectively
+extends the CERN infrastructure with a ``Neutrino-Ion Collider''.
 
@@
 
-% Analysis settings, theory calculations, xfitter vs NNPDFs, yadism/eko/pineappl
-% Fitting vs profiling
-\input{sec-analysis}
-
 % REsults for the proton PDFs, using NNPDF and PDF4LHC21/xfitter
 \input{sec-protonPDFs}
-
-% REsults for the nuclear PDFs, using NNPDF and EPPS21/xfitter
-\input{sec-nuclearPDFs}
 
@@
 
-%\section{Description of the $\nu$FPF codes}
+% Appendices
+\appendix
 
-%The part that computes the differential cross sections is taken care by the python
-%package $\nu$FPF. By default, it computes the HERA cross section defined as
-%\begin{equation}
-%    \frac{d^2\tilde{\sigma}^{A}}{dxdy} \lp x,Q^2,y \rp =  \frac{1}{2}\lc (1-y)F^{\nu A}_2(x,Q^2) + y^2xF^{\nu A}_1(x,Q^2)
-%    + (-1)^\ell  y\lp 1-\frac{y}{2}\rp xF^{\nu A}_3(x,Q^2)\rc ,
-%\end{equation}
-%where $\ell = 0$ for leptons and $\ell = 1$ for anti-leptons. Thus, in order to compare with 
-%Eq.~\ref{eq:neutrino_DIS_xsec} one needs to multiply the above equation with $G_F^2s/2 \pi (1 + Q^2/m^2_W)^2$.
+% Impact of FASERnu
+\input{app-faser.tex}
 
-% Bibliography
+% Impact in nuclear PDFs
+\input{app-nuclearPDFs.tex}
+
+\clearpage
+
 \bibliographystyle{utphys}

### 2023-08-22 paper/sec-introduction.tex
new intro

--- 2023-06-19 paper/sec-introduction.tex
@@
 Proton-proton collisions at energy-frontier hadron colliders
-such as the LHC produce an intense collimated flux of neutrinos~\cite{Kling:2021gos}.
+such as the LHC produce an intense collimated flux of neutrinos.
 %
-These neutrinos are characterised by the largest energies ever achieved in laboratory experiments,
-reaching up to several TeV.
+These neutrinos are characterised by the largest energies ever achieved in laboratory experiments and
+reaching up to several TeV~\cite{Kling:2021gos}.
 %
 Due to the lack of dedicated instrumentation in the LHC far-forward region,
-until recently these neutrinos escaped detection.
+until very recently these neutrinos escaped detection.
 %
@@
 %
-LHC neutrinos enable
+Current and future 
+LHC neutrinos experiments enable
 unprecedented scientific opportunities
@@
 (DIS) provide sensitive information on the parton distribution functions (PDFs)
-of nucleons and nuclei~\cite{Ethier:2020way,Gao:2017yyd,Kovarik:2019xvh}, in particular
+of nucleons and nuclei~\cite{Ethier:2020way,Gao:2017yyd,Kovarik:2019xvh}, and in particular
 they probe the quark/antiquark  flavour separation including
@@
 These constraints, arising from charged-current DIS, are fully complementary to those
-provided by neutral-current charged-lepton DIS given that they reveal independent
-flavour combinations.
+provided by neutral-current charged-lepton DIS, given that they reveal independent
+quark flavour combinations.
 %
@@
 
-As compared to these previous experiments,
+As compared to  previous neutrino DIS experiments,
 the unique benefit of LHC neutrinos is their energy spectrum, reaching
-energies up to a factor 10 higher (several TeV).
+energies up to an order of magnitude higher.
 %
-This feature, together with the large statistics (up to $10^6$ muon neutrinos detected at the FPF~\cite{Kling:2021gos}),  strongly suggest that the LHC  neutrino beam should be
-deployed as a precise probe of hadron structure, complementing
-and extending available results by an order of magnitude both at small-$x$
+This feature, together with the large statistics (with up to one million muon neutrinos to be
+detected at the FPF~\cite{Kling:2021gos}),  indicates that the LHC  neutrino beam should be
+deployed as a precise probe of hadron structure in order to complement
+and extend available results by a factor 10 both at small-$x$
 and large-$Q^2$~\cite{Feng:2022inv}.
@@
 However, we currently lack  dedicated projections for the kinematic coverage
-and accuracy expected for LHC neutrino structure functions,
+and experimental accuracy expected for LHC neutrino structure functions,
 including bin-by-bin statistical and systematic uncertainties and their
@@
 the expected impact of  DIS structure functions from the LHC
-neutrino beam on the proton and nuclear PDFs.
+neutrino experiments on the proton and nuclear PDFs.
 %
@@
 structure functions, 
-and estimate the main systematic uncertainties and their correlation pattern.
+and estimate the main systematic uncertainties.
 %
-Subsequently, we study their impact on the proton PDFs by means of the Hessian profiling~\cite{Paukkunen:2014zia}
+Subsequently, we study their impact on the proton PDFs by means of both the Hessian profiling~\cite{Paukkunen:2014zia,  Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre}
 of the PDF4LHC21 combination~\cite{PDF4LHCWorkingGroup:2022cjn}
-within the  {\sc\small xFitter} framework~\cite{Alekhin:2014irh}, cross-checked
-with their direct inclusion in the open-source NNPDF fitting framework~\cite{NNPDF:2021uiq}.
+within the  {\sc\small xFitter} framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}
+as well as the direct inclusion in the open-source NNPDF4.0 fitting framework~\cite{NNPDF:2021uiq}.
 %
-We also assess their impact on the PDFs of tungsten (target of FASER$\nu$ and SND@LHC)
+We also assess their impact on the PDFs of tungsten, the target material of FASER$\nu$ and SND@LHC,
 using the EPPS21 global nuclear PDF fit~\cite{Eskola:2021nhw}
@@
 
-Our analysis reveals that  neutrino structure function measurements at the LHC, specially
-for the high-statistics  experiments of the FPF, provides  stringent constraints
-on the quark and antiquark (nuclear) PDFs, specially on the up and down
-antiquarks and on strangeness, as compared to state-of-the-art (n)PDF determinations.
+Our analysis reveals that  LHC neutrino structure function measurements at the FPF
+would  provide  stringent constraints
+on the quark and antiquark PDFs, specially on the up and down
+valence quarks and on strangeness, as compared to state-of-the-art determinations.
 %
-The best-case scenario when only statistical errors are considered is not
-significantly distorted upon the inclusion of realistic systematic errors.
+We find that accounting for systematic uncertainties does not significantly
+degrade the sensitivity achieved by the statistics-only baseline.
 %
-We make the resulting (n)PDF sets publicly available, as well as the DIS pseudo-data projections
-for the various scenarios for the systematic uncertainties considered.
+We also quantify the impact of charm-tagged structure functions, study the relevance
+of final-state lepton charge identification, and compare the relative sensitivity
+provided by each of the FPF experiments.
+
+Together with this paper, we release the generated  DIS pseudo-data projections for the various scenarios
+considered, as well as the resulting PDF sets, for which one can foresee
+many other applications beyond hadronic structure studies.
 %
-Our work demonstrates that detection of LHC far-forward neutrinos  effectively
-extends the LHC with a charged-current counterpart of the EIC,
-with similar kinematic reach and complementary charged-current reactions,
-therefore realising (upon Lorentz-boosting) the analog of a ``Neutrino-Ion Collider'' at CERN
-without the need of additional accelerator infrastructure.
+Our work demonstrates that the availability of far-forward neutrino detection
+at the LHC effectively
+extends CERN with a charged-current counterpart of the EIC,
+with a similar kinematic reach and complementing
+the information provided by its neutral-current scattering data.
+%
+Therefore, LHC neutrino experiments realise, upon Lorentz-boosting, the analog of
+a ``Neutrino-Ion Collider'' at CERN
+without the need of additional accelerator infrastructure or energy consumption.
 
@@
 %
-First, in Sect.~\ref{sec:dis_pseudodata} we describe the procedure
-adopted to generate projections for DIS structure functions associated to
-LHC neutrino scattering, including the modelling of experimental systematic
-uncertainties.
-%
-Then in Sect.~\ref{sec:settings} we discuss the theoretical settings used
-for the calculation of DIS structure functions and the methodology adopted
-to account for the constraints of LHC neutrino DIS data on proton and nuclear PDFs.
+Sect.~\ref{sec:dis_pseudodata} discusses the procedure
+adopted to generate projections for neutrino DIS structure functions at the LHC,
+as well as the methodology used
+to include them in proton and nuclear PDF fits.
 %
 The projected impact of these structure functions on proton and nuclear
-PDFs is quantified in Sects.~\ref{sec:protonPDFs} and~\ref{sec:nuclearPDFs} respectively.
+PDFs is quantified in Sect.~\ref{sec:protonPDFs}.
 %
-Finally we summarise in Sect.~\ref{sec:summary} and consider some possible
+We summarise in Sect.~\ref{sec:summary} and also consider some possible
 directions for follow-up research.
+%
+Additional impact results are collected in two appendices:
+App.~\ref{app:fasernu_runIII_impact} studies the possible PDF impact
+of FASER$\nu$ Run III measurements, and App.~\ref{app:nPDF_impact_appendix}
+quantifies the stability of the nuclear PDF projections with respect
+to variations of its inputs.

### 2023-08-22 paper/sec-results.tex
Update sec-results.tex

--- 2023-08-22 paper/sec-protonPDFs.tex
@@
 
-\subsection{Impact on PDF4LHC21}
+\subsection{Proton PDFs: impact on PDF4LHC21}
 \label{sec:pdf4lhc21}
 
-For the Hessian profiling studies based on the procedure of Sect.~\ref{sec:profiling}, the prior PDF set is taken to
-be PDF4LHC21 NNLO, a Monte Carlo combination~\cite{Watt:2012tq,Carrazza:2015hva} of three global PDF sets (CT18~\cite{Hou:2019efy},
-MSHT20~\cite{Bailey:2020ooq}, and NNPDF3.1~\cite{NNPDF:2017mvq}).
+We begin by presenting results for the Hessian profiling of
+the PDF4LHC21 NNLO set.
 %
-The Hessian representations of PDF4LHC21 are obtained by means of the methodology developed in~\cite{Gao:2013bia,Carrazza:2015aoa}.
+This proton PDF set is a Monte Carlo combination~\cite{Watt:2012tq,Carrazza:2015hva} of three global PDF sets, CT18~\cite{Hou:2019efy},
+MSHT20~\cite{Bailey:2020ooq}, and NNPDF3.1~\cite{NNPDF:2017mvq}.
+%
+Its Hessian representations are obtained by means of the reduction methodologies developed in~\cite{Gao:2013bia,Carrazza:2015aoa}.
 %
@@
 %
-We profile PDF4LHC21 with various sets of LHC neutrino DIS projections in order to assess the stability
-of the results with respect to its different inputs, such as charm-tagged structure functions.
+We profile PDF4LHC21 with pseudodata from various LHC neutrino experiments,
+and study the stability of the results with respect to variations in the data
+and methodology inputs.
+
+Fig.~\ref{fig:FASERnu2_baseline} shows the
+fractional uncertainties (at the 68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
+for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
+in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 pseudo-data is added
+by means of Hessian profiling.
 %
-The consistent perturbative accuracy of the prior PDF set and the theoretical calculations entering
-the pseudo-data generation is always accounted for.
-
-For the baseline results, we consider FASER$\nu$2 operative for the full duration
-of the HL-LHC data-taking period.
+The FASER$\nu$2 pseudo-data accounts for  both  inclusive and charm-tagged structure functions
+and assumes outgoing lepton- charge identification.
 %
-Both inclusive and charm-tagged structure functions enter the profiling,
-and outgoing lepton charge-separation is assumed.
+We display results for the profiling in which the experimental covariance matrix
+considers only statistical uncertainties, as well as for the scenario where
+statistical and systematic errors are added in quadrature following
+the procedure spelled out in Sect.~\ref{subsec:uncertainties}.
 %
-Fig.~\ref{fig:profiling_syst} displays the
-fractional uncertainties   (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
-for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
-in PDF4LHC21 compared to the results of its profiling with the FASER$\nu$2 projections.
+Note that in addition of a reduction of PDF uncertainties, the Hessian profiling
+also results in general in a shift in the PDF central values.
 %
-For the latter, we consider two scenarios: first where the covariance matrix includes
-only statistical errors, and second with experimental systematic
-errors added in quadrature to the statistical ones.
-%
-Note that the residual shift in central values, which depends on the arbitrary fluctuations
-entering the pseudo-data generation, is not displayed.
+This shift is however arbitrary since it 
+depends on the fluctuations
+entering the pseudo-data generation, and is hence ignored in the following.
 
@@
 %
-We include both  both  inclusive and charm-tagged structure functions
+We include  both  inclusive and charm-tagged structure functions
 and assume outgoing lepton charge-separation.
@@
 
-Inspection of Fig.~\ref{fig:profiling_syst} reveals that measurement of DIS structure
+Inspection of Fig.~\ref{fig:FASERnu2_baseline} reveals that measurement of DIS structure
 functions at FASER$\nu$2 impose stringent constraints on the quark PDFs, while leaving
@@
 
-\subsection{Impact on NNPDF4.0}
+\subsection{Proton PDFs: impact on NNPDF4.0}
 \label{sec:nnpdf40}
@@
 
-\subsection{Impact on EPPS21}
+\subsection{Nuclear PDFs: impact on EPPS21}
 \label{sec:nuclearPDFs}
@@
 The bands indicate the 68\% CL uncertainties, 
-both for the case assuming statistical unertainties only, 
+both for the case assuming statistical uncertainties only, 
 as well as including an estimate for both statistical and systematic uncertainties.

### 2023-08-22 paper/sec-results.tex
Update sec-results.tex

@@
 
-Fig.~\ref{fig:FASERnu2_baseline} shows the
-fractional uncertainties (at the 68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
-for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
-in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 pseudo-data is added
-by means of Hessian profiling.
-%
-The FASER$\nu$2 pseudo-data accounts for  both  inclusive and charm-tagged structure functions
-and assumes outgoing lepton- charge identification.
-%
-We display results for the profiling in which the experimental covariance matrix
-considers only statistical uncertainties, as well as for the scenario where
-statistical and systematic errors are added in quadrature following
-the procedure spelled out in Sect.~\ref{subsec:uncertainties}.
-%
-Note that in addition of a reduction of PDF uncertainties, the Hessian profiling
-also results in general in a shift in the PDF central values.
-%
-This shift is however arbitrary since it 
-depends on the fluctuations
-entering the pseudo-data generation, and is hence ignored in the following.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Inspection of Fig.~\ref{fig:FASERnu2_baseline} reveals that measurement of DIS structure
-functions at FASER$\nu$2 impose stringent constraints on the quark PDFs, while leaving
+Fig.~\ref{fig:FASERnu2_baseline} shows the
+fractional uncertainties (at the 68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
+for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
+in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 pseudo-data is added
+by means of Hessian profiling.
+%
+The FASER$\nu$2 pseudo-data accounts for  both  inclusive and charm-tagged structure functions
+and assumes outgoing lepton- charge identification.
+%
+We display results for the profiling in which the experimental covariance matrix
+considers only statistical uncertainties, as well as for the scenario where
+statistical and systematic errors are added in quadrature following
+the procedure spelled out in Sect.~\ref{subsec:uncertainties}.
+%
+We restrict the comparisons to the region $10^{-3}\lsim x \lsim 0.7$ covered
+by the LHC neutrino experiments as shown in Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF}.
+%
+Note that in addition of a reduction of PDF uncertainties, the Hessian profiling
+also results in general in a shift in the PDF central values.
+%
+This shift is however arbitrary since it 
+depends on the fluctuations
+entering the pseudo-data generation, and is hence ignored in the following.
+
+Inspection of Fig.~\ref{fig:FASERnu2_baseline} reveals that measurements of DIS structure
+functions at FASER$\nu$2 improve PDF uncertainties on the quark PDFs, while leaving
 the gluon PDF essentially unaffected.
@@
 As expected for a neutrino scattering experiment, its impact is most marked for
-those PDF combinations sensitive to quark flavour separation such as $u_V$, $d_V$, and
-$s^+$.
+those PDF combinations sensitive to quark flavour separation such as
+the up and down valence PDF as well as the total strangeness.
 %
-The reduction of PDF uncertainties is particularly significant for the total strangeness PDF,
-as  consequence of the inclusion of charm-tagged structure functions in the fit as we demonstrate below.
+Indeed, the reduction of PDF uncertainties is particularly significant for the latter,
+a consequence of the inclusion of charm-tagged structure functions in the fit.
 %
-Crucially, one finds that for the assumptions on the systematic uncertainties
+Given that all PDF determinations entering PDF4LHC21 already include existing neutrino
+DIS measurements, the fact that FASER$\nu$2 pseudo-data still manages to reduce PDF
+uncertainties highlights the new information provided by the LHC neutrino experiments.
+
+The  analysis of Fig.~\ref{fig:FASERnu2_baseline} also indicates that 
+ for the assumptions on the systematic uncertainties
 discussed in Sect~\ref{sec:dis_pseudodata}, the PDF sensitivity is only marginally degraded
 as compared to the case in which systematic errors are neglected.
-%
-This result is consistent with Fig.~\ref{fig:percentage_uncertainties_overview}, showing
-how in most bins systematic and statistical errors are of similar magnitude.
+
+%%
+%% Here
 

### 2023-08-22 paper/sec-results.tex
Update sec-results.tex

@@
 
+\paragraph{Statistic versus systematic uncertainties.}
+%
 Fig.~\ref{fig:FASERnu2_baseline} shows the
@@
 
-The  analysis of Fig.~\ref{fig:FASERnu2_baseline} also indicates that 
- for the assumptions on the systematic uncertainties
-discussed in Sect~\ref{sec:dis_pseudodata}, the PDF sensitivity is only marginally degraded
-as compared to the case in which systematic errors are neglected.
+By comparing the impact of the FASER$\nu$2 structure functions
+in the case where only statistical errors are considered with that
+where also systematic uncertainties are accounted for,
+one finds that the latter eventually become a limiting factor,
+but also that they not modify the qualitative findings of the statistics-only scenario.
+%
+Indeed, while systematic uncertainties somewhat degrade the PDF sensitivity,
+they don't eliminate it for none of the quark PDFs.
+%
+Furthermore, in the projections presented in this work,
+we assume the performance parameters of  Table~\ref{tab:FPF_experiments}, which
+however could be very well enhanced in the actual realisation of the experiments,
+using for instance detector improvements or different kinematic reconstruction techniques.
+%
+We also note that the availability of different experiments accessing the same neutrino
+beam should allow their mutual cross-calibration, such that the combination of their
+data brings in more information than just the trivial statistics scaling.
 
-%%
-%% Here
-
-In the following, we consider the results obtained using only statistical uncertainties as the baseline, 
-and examine stability of these results with respect to the chosen experiment and integrated luminosity, the modelling of systematic
-uncertainties, being able to identify or not charm production, and being able to tell part outgoing
-charged leptons from anti-leptons.
-
+\paragraph{Importance of charm-tagged measurements.}
 %
-Fig.~\ref{fig:profiling_charm} displays a comparison of the baseline LHC neutrino dataset with the results
-of profiling without the charm production structure functions. 
-Particularly, the constraints on the $s$ PDF are observed to become more stringent 
-by virtue of the contribution of the charm production structure functions.
+The analysis of Fig.~\ref{fig:FASERnu2_baseline} shows that LHC neutrino data is particularly
+constraining for the poorly-known strange PDF, which is one of the quark flavour combinations
+for which proton PDF fits differ the most~\cite{Faura:2020oom}.
+%
+To further investigate this point, Fig.~\ref{fig:FASERnu2_nocharm} compares the impact of the FASER$\nu$2 data shown in
+Fig.~\ref{fig:FASERnu2_baseline}, for the case in which only statistical
+uncertainties are considered, with the results of the same profiling once the charm-tagged
+structure function data is excluded from the fit.
+%
+While differences are moderate for the up and down quark PDFs, the significant loss
+of information resulting from this exclusion of charm-tagged data is clearly
+visible for the strange PDF.
+%
+Specially in the region $x\gsim 0.01$, the constraints on strangeness shown in
+Fig.~\ref{fig:FASERnu2_nocharm} are washed out in the absence of charm-tagged data.
+%
+We can hence establish that inclusive neutrino DIS measurements constrain mostly
+the up and down quark and antiquark PDFs (and thus also the total quark singlet), while the charm-tagged
+structure functions are responsible for most of the constraints provided on the total strangeness.
+%
+The PDF reach of the LHC neutrino experiments would thus be  markedly limited for experiments without
+charm-identification capabilities.
 
@@
 
+\paragraph{Lepton-charge identification.}
 %
-Fig.~\ref{fig:profiling_nochargediscrimination} compares the baseline LHC neutrino dataset with the results
-of a profiling without allowing for the possibility of outgoing lepton charge separation.
+Being able to identify the charge of the produced final-state lepton in charged-current
+neutrino scattering demands equipping an experiment with a powerful enough magnet suitable to
+deflect this lepton within the detector fiducial volume.
+%
+Our baseline results for FASER$\nu$2 in Fig.~\ref{fig:FASERnu2_baseline} assume that this charge-identification
+is possible, and therefore include separate structure function datasets for neutrino and anti-neutrino projectiles.
+%
+In order to ascertain to which extent the constraints provided by FASER$\nu$2 structure functions
+depend on the availability of such a magnet,
+Fig.~\ref{fig:FASERnu2_nochargeID} compares the reduction of the PDF uncertainties using
+the FASER$\nu$2 data with and without charged-lepton identification capabilities.
 
@@
 
-Besides FASER$u$2, further FPF detectors may also be used for constraining the PDFs. 
-Fig.~\ref{fig:profiling_FASERv2_vs_AdvSND} illustrates the effect of using the AdvSND pseudodata alone, 
-shown together with the previous result of using only FASER$\nu$2 pseudodata. 
-Fig.~\ref{fig:profiling_FASERv2_vs_FLArE10} shows a similar comparison, 
-but using FLArE pseudodata instead of AdvSND. 
-Most importantly however, all these datasets can be included to obtain a complete FPF result, 
-shown in Fig.~\ref{fig:profiling_FPF}.
+One finds that the lack of charged-lepton identification actually does not degrade significantly the PDF
+sensitivity of FASER$\nu$2.
+%
+Having access of the lepton charge information improves a bit the constraints for the down and (to a lesser
+extent) the up valence quark PDFs,  while there are no differences for the total quark
+singlet and for strangeness.
+%
+This behaviour can be understood by inspecting the leading-order decomposition of neutrino DIS
+structure functions in terms of PDFs for different targets, Eqns.~(\ref{eq:neutrinoSFs_proton})--(\ref{eq:neutrinoSFs_isoscalar}).
+%
+For an isoscalar target, as assumed here, structure functions are very similar for neutrino
+and anti-neutrino projectiles, with differences restricted to the strangeness asymmetry.
+%
+Given that this strangeness asymmetry is quite small, this also explains why the impact
+on strangeness, which is driven by the charm-tagged data, is the same irrespective of whether one identifies
+the outgoing lepton charge.
+%
+We conclude that LHC neutrino DIS data exhibits good PDF sensitivity even for an experiment which cannot tell
+apart incoming neutrinos from antineutrinos.
+
+\paragraph{FASER$\nu$2 compared to AdvSND and FLArE.}
+%
+In addition to FASER$\nu$2, we have also produced PDF impact projections for
+other proposed FPF experiments, specifically for AdvSND and FLArE.
+%
+In the latter case, we consider both the 10 ton and 100 ton variants.
+%
+Figs.~\ref{fig:FASERnu2_advsnd} and~\ref{fig:FASERnu2_FLAre10} compare the PDF sensitivity
+of FASER$\nu$2, in the scenario where systematic uncertainties are neglected, with the corresponding
+results for AdvSND and FLArE100 respectively.
+%
+As summarised by Table~\ref{tab:integrated_rates}, each of these experiments
+has associated different expected numbers of DIS events, namely 370k, 43k, and 81k (420K)
+inclusive muon-neutrino events for FASER$\nu$2, AdvSND and FLArE10~(100) respectively,
+with 57k, 4.5k, and 11k (59k) in the charm-tagged case.
+%
+In this comparison, one would expect that experiments with the largest event rates best PDF sensitivity.
 
@@
 
+From Figs.~\ref{fig:FASERnu2_advsnd} and~\ref{fig:FASERnu2_FLAre10} one can see that the three
+FPF experiments studied lead to a reduction of the  uncertainties in the quark PDFs.
+%
+By comparing their relative impact, we find that the constraints
+achieved by FASER$\nu$2 are somewhat better than for the other two experiments,
+as could have been expected by the larger event yields obtained in the former.
+%
+In the case of AdvSND, the  smaller sample of charm-tagged events lead to reduction
+of the constraints on strangeness.
+%
+Another consequence of the smaller event rates in AdvSND and FLArE10 as compared
+to FASER$\nu$2 is the milder impact for the $x\lsim 10^{-2}$ region,
+which can only be properly covered once the integrated statistics become large
+enough,  as indicated by the differential bin-by-bin yields displayed in Fig.~\ref{fig:fasernu2_muon}.
+
+We note that a proper comparison between the PDF reach of
+the various FPF experiments requires accounting for the systematic uncertainties
+associated to their kinematic reconstruction performance, which ultimately becomes
+one of the limiting factors.
+%
+Also, as mentioned above, cross-calibration between experiments should provide
+valuable input to enhance the PDF sensitivity.
+
+\paragraph{Combined impact of the FPF experiments.}
+%
+Finally, we have carried out a further PDF analysis including simultaneously the three FPF experiments
+considered so far: FASER$\nu$2, AdvSND, and FLArE100.
+%
+Fig.~\ref{fig:FPF_combined} displays the combined impact of the FPF experiments when added
+on top of the  PDF4LHC21 baseline by means of Hessian profiling, both in the statistics-only case and
+when systematic and statistical uncertainties are added in quadrature.
+%
+Possible correlations between the individual experiments are neglected in this exercise, though they
+will become important when interpreting the actual measurements.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 }
-\label{fig:profiling_FPF}
+\label{fig:FPF_combined}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The combined impact of the three FPF experiments on PDF4LHC21 shown in Fig.~\ref{fig:FPF_combined}
+is only slightly improved as compared to the results of the FASER$\nu$2-only profiling
+in Fig.~\ref{fig:FASERnu2_baseline}.
+%
+This shows that in this naive combination of experiments the one with the largest individual
+sensitivity dominates, in this case FASER$\nu$2.
+%
+Again, this exercise is somewhat simplistic since within the real experiments the consistency (or lack thereof) between
+individual measurements, which here is assumed by construction, provides useful information, and also
+because the FPF experiments will cross-calibrate each other and cover somewhat different kinematic regions.
+
+All in all, Fig.~\ref{fig:FPF_combined}, and in particular the statistics-only case, represents
+a best-case scenario for the reduction of PDF uncertainties which can be expected from
+the analysis of neutrino DIS structure function data at the FPF, in the assumption that PDF4LHC21 accurately represents
+our current knowledge about the quark and gluon structure of the proton.
 

### 2023-08-22 paper/sec-results.tex
some work on Sect 3.2

@@
 
+Add also statistical estimators, and plots of PDF uncertainty only.
+%
+Maybe also reduction of PDF luminosities, as relevant for phenomenology.
+
+Fig.~\ref{fig:nnpdf40_fpf_lumis} displays a comparison of the PDF luminosities at $\sqrt{s}=13$ TeV
+  as a function of the final-state invariant mass $m_X$ between
+  the baseline NNPDF4.0 NNLO determination and its variant which includes
+  the FPF pseudo-data from the FASER$\nu$2, FLArE100, and AdvSND experiments.
+  %
+  Results are shown normalised to the central value of the NNPDF4.0 baseline.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.45\textwidth]{plots/qqlumi_nnpdf40_allfpf.pdf}
+\includegraphics[width=0.45\textwidth]{plots/qqbarlumi_nnpdf40_allfpf.pdf}
+\includegraphics[width=0.45\textwidth]{plots/udbarlumi_nnpdf40_allfpf.pdf}
+\includegraphics[width=0.45\textwidth]{plots/dubarlumi_nnpdf40_allfpf.pdf}
+\caption{Comparison of the PDF luminosities at $\sqrt{s}=13$ TeV
+  as a function of the final-state invariant mass $m_X$ between
+  the baseline NNPDF4.0 NNLO determination and its variant which includes
+  the FPF pseudo-data from the FASER$\nu$2, FLArE100, and AdvSND experiments.
+  %
+  Results are shown normalised to the central value of the NNPDF4.0 baseline.
+%
+}
+\label{fig:nnpdf40_fpf_lumis}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \clearpage

### 2023-08-23 paper/sec-pheno.tex
new nnpdf40 plots

\section{Implications for HL-LHC processes}
\label{sec:pheno}

The reduction of PDF uncertainties enabled by the neutrino DIS measurements
at the FPF presented in Sect.~\ref{sec:protonPDFs}
makes possible more precise theoretical predictions for key processes at the
HL-LHC.
%
Here we present an initial study of the phenomenological implications
of PDFs enhanced with LHC neutrino data.
%
We adopt the same settings as in the LHC phenomenology analysis presented
in the PDF4LHC21 combination paper~\cite{PDF4LHCWorkingGroup:2022cjn} and provide predictions
both for inclusive fiducial cross-sections and for differential distributions.
%
Specifically, we present results for 
single and double gauge boson production, inclusive top quark pair production,
and Higgs production in gluon
fusion and in association with a vector boson.
%
We evaluate these cross-sections using NLO matric elements
which include  both in the
QCD and electroweak corrections using
{\sc\small mg5\_amc@nlo}~\cite{Frederix:2018nkq}
interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss}.
%
For all processes, realistic selection and acceptance cuts on the final state particles
have been applied, and PDF uncertainty bands correspond to 90\% CL
uncertainties.
%
No further theory uncertainties are considered in this
analysis.

### 2023-08-23 paper/sec-results.tex
new nnpdf40 plots

@@
 \centering
-\includegraphics[width=0.99\textwidth]{plots/FASERnu2-q100gev-ratios.pdf}
+\includegraphics[width=0.99\textwidth]{plots/NNPDF40-FPFall-q100gev.pdf}
 \caption{
-  Same as Fig.~\ref{fig:profiling_syst} now for the fits
-  based on the NNPDF4.0 global analysis.
+The fractional uncertainties (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
+for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
+in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 pseudo-data is included.
+%
+The FASER$\nu$2 impact projections are provided both without and with systematic
+uncertainties accounted for.
+%
+We include  both  inclusive and charm-tagged structure functions
+and assume outgoing lepton charge-separation.
 %
 }
-\label{fig:nnpdf40_fasernu2_baseline}
+\label{fig:NNPDF40_baseline}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.99\textwidth]{plots/NNPDF40-FPFall-q1p65gev-abs.pdf}
+\caption{
+The fractional uncertainties (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
+for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
+in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 pseudo-data is included.
+%
+The FASER$\nu$2 impact projections are provided both without and with systematic
+uncertainties accounted for.
+%
+We include  both  inclusive and charm-tagged structure functions
+and assume outgoing lepton charge-separation.
+%
+}
+\label{fig:NNPDF40_lowQ_abs}
 \end{figure}

### 2023-08-23 paper/sec-results.tex
sect 3.2

@@
 
-Selection of the {\sc\small xFitter} results for the NNPDF case.
+As discussed in Sect.~\ref{subsec:pdf_impact_assessment}, the PDF sensitivity
+studies of the FPF neutrino data based on the {\sc\small xFitter} profiling
+of PDF4LHC21 are complemented by those based on their direct inclusion
+in the NNPDF4.0 global analysis.
+%
+Here we present results for the impact of the combined FPF neutrino
+measurements on NNPDF4.0, namely the analogous study of that shown
+in Fig.~\ref{fig:FPF_combined} for PDF4LHC21.
+%
+While we have produced results also the variations studied in
+Sect.~\ref{sec:pdf4lhc21} with the NNPDF fitting methodology, the qualitative
+findings are compatible with those obtained with {\sc\small xFitter} and
+hence it is not necessary to duplicate them here.
 
-Fig.~\ref{fig:nnpdf40_fasernu2_baseline} presents the same comparison
-as in Fig.~\ref{fig:profiling_syst} now for
- the fits
- based on the NNPDF4.0 global analysis.
+Fig.~\ref{fig:NNPDF40_baseline} displays the
+same results as Fig.~\ref{fig:FPF_combined} now in the case of the
+fits obtained with the NNPDF4.0 fitting methodology.
 %
- The impact on the PDFs found by direct inclusion of the FPF structure
+The baseline NNPDF4.0 NNLO analysis is compared
+with the results of the fits which include the combined FPF dataset,
+in both the statistics-only scenario and for the case
+where systematic uncertainties are also accounted for.
+%
+As in the PDF4LHC21 analysis, the bands indicate the one-sigma PDF uncertainties.
+%
+Note that we also show results for the charm PDF (bottom right panel), which
+in the NNPDF4.0 fit is also determined directly from the data entering
+the fit~\cite{Ball:2016neh}.
+%
+In this way we can determine the possible constraints that neutrino
+DIS measurements at the LHC may impose on the intrinsic charm
+content of the proton~\cite{Ball:2022qks}.
+
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.99\textwidth]{plots/NNPDF40-FPFall-q100gev.pdf}
+\caption{
+  Same as Fig.~\ref{fig:FPF_combined} for the results obtained
+  using the NNPDF4.0 fitting methodology.
+  %
+  The baseline NNPDF4.0 NNLO analysis is compared
+  with the results of the fits which include the combined FPF dataset
+  in both the statistics-only scenario and for the case
+  where systematic uncertainties are also accounted for.
+  %
+  As in the PDF4LHC21 case, the bands indicate the one-sigma PDF uncertainties.
+  %
+  We now also show results for the charm PDF (bottom right panel), which
+  in the NNPDF4.0 fit is also determined directly from the data entering the fit.
+%
+}
+\label{fig:NNPDF40_baseline}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+From  Fig.~\ref{fig:NNPDF40_baseline} one finds that
+the impact on the PDFs found by direct inclusion of the FPF structure
 functions on the NNPDF4.0 fit is qualitatively consistent with
@@
 \centering
-\includegraphics[width=0.99\textwidth]{plots/NNPDF40-FPFall-q100gev.pdf}
-\caption{
-The fractional uncertainties (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
-for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
-in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 pseudo-data is included.
-%
-The FASER$\nu$2 impact projections are provided both without and with systematic
-uncertainties accounted for.
-%
-We include  both  inclusive and charm-tagged structure functions
-and assume outgoing lepton charge-separation.
-%
-}
-\label{fig:NNPDF40_baseline}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\centering
 \includegraphics[width=0.99\textwidth]{plots/NNPDF40-FPFall-q1p65gev-abs.pdf}
 \caption{
-The fractional uncertainties (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
-for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
-in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 pseudo-data is included.
-%
-The FASER$\nu$2 impact projections are provided both without and with systematic
-uncertainties accounted for.
-%
-We include  both  inclusive and charm-tagged structure functions
-and assume outgoing lepton charge-separation.
+  Same as Fig.~\ref{fig:NNPDF40_baseline} now for the absolute PDFs
+  at the initial parametrisation scale, $Q=1.65$ GeV, focusing
+  on the large-$x$ region.
 %
@@
 
-Add also statistical estimators, and plots of PDF uncertainty only.
+The statistical estimators for the NNPDF4.0 NNLO
+baseline fit, compared to those in the variations including
+the combined FPF dataset shown in Figs.~\ref{fig:NNPDF40_baseline}
+and~\ref{fig:NNPDF40_lowQ_abs}, are reported in Table~\ref{tab:chi2_nnpdf40_baseline}.
 %
-Maybe also reduction of PDF luminosities, as relevant for phenomenology.
+From top to bottom we indicate total $\chi^2$, average
+over replicas of the training and validation figures of merit
+$\la E_{\rm tr}\ra_{\rm rep}$ and $\la E_{\rm val}\ra_{\rm rep}$,
+average $\chi^2$ over replicas $\la \chi^2\ra_{\rm rep}$,
+$\chi^2$ for datasets grouped by process.
+%
+Note that the last row displays the $\chi^2$ obtained for the combined FPF dataset.
+
+%-----------------------------------------------------------------------
+\begin{table}[!t]
+  \centering
+  \footnotesize
+  \renewcommand{\arraystretch}{1.30}
+  \begin{tabularx}{\textwidth}{X|l|l|l|l}
+  \toprule
+  & \multirow{3}{*}{Dataset}
+  & \multicolumn{3}{c}{\bf NNPDF4.0 NNLO} \\
+  &
+  & Baseline
+  & \multicolumn{2}{c}{with combined FPF data}  \\
+  &
+  &
+  & Statistical-only  & Statistical + systematics  \\
+  \midrule
+  $\chi^2$ &  \multirow{4}{*}{Global}      &  &    &  \\
+  $\la E_{\rm tr}\ra_{\rm rep}$
+  & &    &     &   \\
+  $\la E_{\rm val}\ra_{\rm rep}$
+  & &     &     & \\
+  $\la \chi^2\ra_{\rm rep}$
+  & &      &        &   \\
+  \midrule
+  \multirow{8}{*}{$\chi^2$}
+  & DIS neutral-current                     &      &       &      \\
+  & DIS charged-current                     &     &       &      \\
+  & Drell--Yan (inclusive and one-jet) &     &       &      \\
+  & Top-quark pair production               &     &       &      \\
+  & Single-top production                   &     &       &      \\
+  & Inclusive jet production                &     &       &      \\
+  & Dijet production                        &     &       &      \\
+  & Direct photon production                 &    &       &      \\
+  & FPF (total)                 &  -  &       &      \\
+  \bottomrule
+\end{tabularx}
+\vspace{0.2cm}
+\caption{\small Statistical estimators for the NNPDF4.0 NNLO
+  baseline fit, compared to those in the variations including
+  the combined FPF dataset shown in Figs.~\ref{fig:NNPDF40_baseline}
+  and~\ref{fig:NNPDF40_lowQ_abs}.
+  %
+  From top to bottom: total $\chi^2$, average
+  over replicas of the training and validation figures of merit
+  $\la E_{\rm tr}\ra_{\rm rep}$ and $\la E_{\rm val}\ra_{\rm rep}$,
+  average $\chi^2$ over replicas $\la \chi^2\ra_{\rm rep}$,
+  $\chi^2$ for datasets grouped by process.
+  %
+  The last row displays the $\chi^2$ obtained for the combined FPF dataset.
+  \label{tab:chi2_nnpdf40_baseline}
+}
+\end{table}
+%--------------------------------------------------------------------------
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{plots/qqlumi_nnpdf40_allfpf.pdf}
-\includegraphics[width=0.45\textwidth]{plots/qqbarlumi_nnpdf40_allfpf.pdf}
-\includegraphics[width=0.45\textwidth]{plots/udbarlumi_nnpdf40_allfpf.pdf}
-\includegraphics[width=0.45\textwidth]{plots/dubarlumi_nnpdf40_allfpf.pdf}
-\caption{Comparison of the PDF luminosities at $\sqrt{s}=13$ TeV
+\includegraphics[width=0.49\textwidth]{plots/qqlumi_nnpdf40_allfpf.pdf}
+\includegraphics[width=0.49\textwidth]{plots/qqbarlumi_nnpdf40_allfpf.pdf}
+\includegraphics[width=0.49\textwidth]{plots/udbarlumi_nnpdf40_allfpf.pdf}
+\includegraphics[width=0.49\textwidth]{plots/dubarlumi_nnpdf40_allfpf.pdf}
+\caption{Comparison of the PDF luminosities at $\sqrt{s}=14$ TeV
   as a function of the final-state invariant mass $m_X$ between
   the baseline NNPDF4.0 NNLO determination and its variant which includes
-  the FPF pseudo-data from the FASER$\nu$2, FLArE100, and AdvSND experiments.
+  the full set of FPF pseudo-data.
   %

### 2023-08-24 paper/sec-results.tex
pap

@@
 measurements on NNPDF4.0, namely the analogous study of that shown
-in Fig.~\ref{fig:FPF_combined} for PDF4LHC21.
+in Fig.~\ref{fig:FPF_combined} in the case of PDF4LHC21.
 %
-While we have produced results also the variations studied in
-Sect.~\ref{sec:pdf4lhc21} with the NNPDF fitting methodology, the qualitative
-findings are compatible with those obtained with {\sc\small xFitter} and
-hence it is not necessary to duplicate them here.
+We emphasize that we have produced results for the variations studied in
+Sect.~\ref{sec:pdf4lhc21} also with the NNPDF fitting methodology.
+%
+Given that the qualitative obtained with the NNPDF fits
+are compatible with those obtained with {\sc\small xFitter}, it is not necessary to duplicate them here,
+and hence we only show results for the impact of the combined FPF pseudo-data.
 
@@
 %
-In this way we can determine the possible constraints that neutrino
+In this way, we can determine the possible constraints that neutrino
 DIS measurements at the LHC may impose on the intrinsic charm
@@
 functions on the NNPDF4.0 fit is qualitatively consistent with
-that found from the Hessian profiling of PDF4LHC21.
+that found in the the Hessian profiling of PDF4LHC21.
+%
+In particular, the constraints are more significant for the up and down
+quark valence PDFs as well as for the total strangeness.
+%
+As was the case with the PDF4LHC21 baseline, the uncertainty reduction
+in the case of the strangeness PDF is particularly
+striking.
+%
+Also consistently with Sect.~\ref{sec:pdf4lhc21}, the gluon
+PDF is unchanged, and the impact on the total quark PDF
+is restricted to the large-$x$ region.
+%
+While one can also identify differences related to analysis choices
+such as the PDF parametrisation and the method used to assess the PDF
+error reduction (for example for the small-$x$ behaviour of $xu_V$ and $xd_V$)
+we conclude that by and large the projected impact of the FPF structure function
+measurements us robust against the specific fitting methodology adopted.
 

### 2023-08-24 paper/sec-results.tex
Update sec-results.tex

@@
 As was the case with the PDF4LHC21 baseline, the uncertainty reduction
-in the case of the strangeness PDF is particularly
+for the strangeness PDF is particularly
 striking.
 %
-Also consistently with Sect.~\ref{sec:pdf4lhc21}, the gluon
+Also consistently with the results of Sect.~\ref{sec:pdf4lhc21}, the gluon
 PDF is unchanged, and the impact on the total quark PDF
@@
 such as the PDF parametrisation and the method used to assess the PDF
-error reduction (for example for the small-$x$ behaviour of $xu_V$ and $xd_V$)
+error reduction (for example, concerning the small-$x$ behaviour of $xu_V$ and $xd_V$)
 we conclude that by and large the projected impact of the FPF structure function
-measurements us robust against the specific fitting methodology adopted.
+measurements is independent of the specific fitting methodology adopted.
 
@@
 
-The statistical estimators for the NNPDF4.0 NNLO
-baseline fit, compared to those in the variations including
-the combined FPF dataset shown in Figs.~\ref{fig:NNPDF40_baseline}
-and~\ref{fig:NNPDF40_lowQ_abs}, are reported in Table~\ref{tab:chi2_nnpdf40_baseline}.
+As indicated by Fig.~\ref{fig:NNPDF40_baseline}, the FPF data is also expected
+to reduce the uncertainties associated to the fitted charm PDF in the region $x\simeq 0.2$
+dominated by the non-perturbative component.
 %
-From top to bottom we indicate total $\chi^2$, average
-over replicas of the training and validation figures of merit
-$\la E_{\rm tr}\ra_{\rm rep}$ and $\la E_{\rm val}\ra_{\rm rep}$,
-average $\chi^2$ over replicas $\la \chi^2\ra_{\rm rep}$,
-$\chi^2$ for datasets grouped by process.
+In order to highlight this impact on the large-$x$ region of the PDFs,
+Fig.~\ref{fig:NNPDF40_lowQ_abs} presents the same comparison as
+in  Fig.~\ref{fig:NNPDF40_baseline} now for the absolute PDFs
+at the initial parametrisation scale, $Q=1.65$ GeV, using a linear scale.
 %
-Note that the last row displays the $\chi^2$ obtained for the combined FPF dataset.
+One can observe the improved constraints on the charm PDF in the large-$x$ region,
+further confirming previous studies~\cite{Anchordoqui:2021ghd,Feng:2022inv} that indicate the
+sensitivity of the FPF to the intrinsic charm content of the proton.
+%
+This comparison also illustrates the excellent constraining power on the proton
+strangeness enabled by the FPF charm-tagged structure function data.
 
@@
   \renewcommand{\arraystretch}{1.30}
-  \begin{tabularx}{\textwidth}{X|l|l|l|l}
+  \begin{tabularx}{\textwidth}{X|l|c|c|c}
   \toprule
@@
 \caption{\small Statistical estimators for the NNPDF4.0 NNLO
-  baseline fit, compared to those in the variations including
+  baseline fit, compared to the variants including
   the combined FPF dataset shown in Figs.~\ref{fig:NNPDF40_baseline}
@@
 
-Fig.~\ref{fig:nnpdf40_fpf_lumis} displays a comparison of the PDF luminosities at $\sqrt{s}=13$ TeV
+The statistical estimators for the NNPDF4.0 NNLO
+baseline fit, compared to the variants including
+the combined FPF dataset shown in Figs.~\ref{fig:NNPDF40_baseline}
+and~\ref{fig:NNPDF40_lowQ_abs}, are reported in Table~\ref{tab:chi2_nnpdf40_baseline}.
+%
+From top to bottom we indicate the total $\chi^2$, average
+over replicas of the training and validation figures of merit
+$\la E_{\rm tr}\ra_{\rm rep}$ and $\la E_{\rm val}\ra_{\rm rep}$,
+average $\chi^2$ over replicas $\la \chi^2\ra_{\rm rep}$,
+$\chi^2$ for datasets grouped by process.
+%
+Note that the last row displays the $\chi^2$ obtained for the combined FPF dataset.
+%
+For the latter, one finds that as expected $\chi^2 \sim 1$, given that the FPF pseudo-data
+is produced by construction to be fully compatible with the NNPDF4.0 baseline.
+%
+For the same reason, the description of all other experiments entering
+the NNPDF4.0 global fit is not distorted by the inclusion of the FPF data.
+
+Fig.~\ref{fig:nnpdf40_fpf_lumis} displays a comparison of the PDF luminosities at $\sqrt{s}=14$ TeV
 as a function of the final-state invariant mass $m_X$ between
 the baseline NNPDF4.0 NNLO determination and its variant which includes
-  the FPF pseudo-data from the FASER$\nu$2, FLArE100, and AdvSND experiments.
+the combined FPF pseudo-data from the FASER$\nu$2, FLArE100, and AdvSND experiments.
+%
+We display the optimistic scenario where only statistical uncertainties
+  are included. 
 %
   Results are shown normalised to the central value of the NNPDF4.0 baseline.
+  %
+  Specifically, we show the quark-quark, quark-antiquark, $u\bar{d}$, and $d\bar{u}$
+  luminosities, where the latter two combinations are those dominating $W^+$ and $W^-$ production
+  at the LHC.
+  %
+These luminosities are useful to interpret the phenomenological studies with the FPF-improved
+PDFs for the HL-LHC that will be presented in Sect.~\ref{sec:pheno}.
 
@@
   the baseline NNPDF4.0 NNLO determination and its variant which includes
-  the full set of FPF pseudo-data.
+  the full set of FPF pseudo-data, in the scenario where only statistical uncertainties
+  are included. 
   %

### 2023-08-24 paper/sec-results.tex
sect 3 completed

@@
 
+The reduction of PDF uncertainties found in  Figs.~\ref{fig:NNPDF40_baseline}
+and~\ref{fig:NNPDF40_lowQ_abs} is also visible
+for the partonic luminosities.
+%
+The improvement for the $u\bar{d}$ and $d\bar{u}$ luminosities at $Q\sim 100$ GeV
+benefits theoretical predictions for $W$ and $Z$ production at the LHC.
+%
+It is also worth noting the PDF error reduction for the quark-quark luminosity at high invariant masses,
+which will feed into searches for new heavy particles at the TeV scale.
+
 \clearpage
@@
 
-The study presented in Sect.~\ref{sec:protonPDFs} treated, from the point of view
+The studies presented in Sects.~\ref{sec:pdf4lhc21} (for PDF4LHC21)
+and~\ref{sec:nnpdf40} (for NNPDF4.0) treated, from the point of view
 of PDF constraints, the neutrino scattering target
-as composed by isoscalar free-nucleons, and hence neglecting nuclear modifications
+as composed by isoscalar free-nucleons.
+%
+They hence neglected both nuclear modifications
 and non-isoscalar effects.
 %
-We now revisit this analysis but accounting for the fact that the target materials in the FPF
-experiments actually
-composed by heavy nuclei, specifically by tungsten (the exception is FLArE with liquid argon, which
-is however not considered here).
+We now revisit these analyses but accounting for the fact that the target materials
+in the FASER$\nu$2 and AdvSND experiments is tungsten, with $A=184$.
 %
-Nuclear modifications associated to a tungsten target are not necessarily small as compared
-to a free isoscalar nucleon, and hence will affect the event rate predictions for
+In this exercise we do not include the FLArE structure function data,
+corresponding to a different target material (liquid argon, with $A=40$), although
+in an actual nuclear PDF fit all FPF datasets would be included simultaneously.
+%
+Nuclear modifications associated to a tungsten target, when compared
+to a free isoscalar nucleon, are not necessarily small, and  will affect the event rate predictions for
 the FPF experiments.
 %
-Turning the argument around, measurements of differential neutrino cross-sections
+This fact also implies that  measurements of differential neutrino cross-sections
 on heavy nuclear targets provide direct constraints on these nuclear modifications
-without replying on assumptions on the $A$ dependence.
+without relying on assumptions on their $A$ dependence.
 
-For this exercise, the prior nuclear PDF set is taken to be EPPS21, a global determination
+We quantify the impact of the FPF structure function measurements
+on the nuclear PDFs of tungsten by applying the same Hessian profiling
+of Sects.~\ref{sec:pdf4lhc21} to EPPS1, a global determination of nuclear PDFs
 that accounts for the constraints of existing datasets involving nuclei as target or projectiles.
 %
-In particular, EPPS21 already includes information from neutrino DIS on nuclear targets
+We note that EPPS21 already includes information from neutrino DIS on nuclear targets
 from the CHORUS and NuTeV experiments.
 %
-The application of Hessian profiling to EPPS21 follows the same strategy as that
+EPPS21 is generally in good agreement with other recent nPDF fits such as nNNPDF3.0~\cite{AbdulKhalek:2022fyi}
+and nCTEQ15HQ~\cite{Duwentaster:2022kpv}.
+%
+The application of profiling to EPPS21 follows the same strategy as that
 for PDF4LHC21, with the caveat that its Hessian error sets also include the contribution
@@
 PDF dependence.
-
-Fig.~\ref{fig:profiling_syst_nuclear} displays the baseline result of the profiling using the EPPS21 global determination of nuclear PDFs,
-specifically of the set with $A=184$ (tungsten target).
 %
-Also in this case we consider first the impact of the baseline LHC neutrino dataset, consisting
-on the FASER$\nu$2 experiment inclusive and charm structure functions,  and charge flavour
-separation. 
-The bands indicate the 68\% CL uncertainties, 
-both for the case assuming statistical uncertainties only, 
-as well as including an estimate for both statistical and systematic uncertainties.
-The result from using the full FPF set comprising of AdvSND, FASER$\nu$2 and FLArE pseudodata is shown in Fig.~\ref{fig:profiling_FPF_nuclear}.
+Also relevant for the subsequent discussion, EPPS21 adopts a tolerance
+factor of $T^2 = 20$ when defining their  68\%  confidence level uncertainties,
+to be contrasted with  $T^2 = 10$ used in PDF4LHC21.
 
@@
 \includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_s_ratio.pdf}
-\caption{The impact of the full FPF pseudodataset in profiling using the EPPS21 global determination of nuclear PDFs (red), specifically for $A=184$.
-The 68\% CL uncertainty bands resulting from assuming only statistical (statistical and systematic) uncertainties are shown in blue (green).
+\caption{Same as Fig.~\ref{fig:FPF_combined} now corresponding to the Hessian
+ profiling of EPPS21 for a tungsten nucleus.
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Fig.~\ref{fig:profiling_FPF_nuclear} displays a similar comparison as that of
+ Fig.~\ref{fig:FPF_combined}, now corresponding to the Hessian
+ profiling of EPPS21 for a tungsten nucleus.
+ %
+ The FPF dataset is in this case composed by FASER$\nu$2 and AdvSND, given that FLArE
+ adopts a different target material.
+ %
+ Also in this case of nuclear PDFs one finds that the impact of FPF structure function measurements
+ is most important for the strange PDF, and to a lesser extent for the up and down
+ valence quark PDFs.
+ %
+ For the latter, the projected impact of FPF measurements appears to be somewhat milder
+ as in the case of PDF4LHC21, specially once systematic uncertainties are taken into account.
+
+ While the main qualitative features of the nPDF profiling are consistent with the free-proton
+ case, one reason explaining the observed differences is the choice of a larger tolerance factor $T$ in EPPS21
+ as compared to PDF4HC21, which effectively reduces the impact of new data.
+ %
+ Another reason is the more restrictive functional form adopted in EPPS21 as compared
+ to the PDF sets entering PDF4LHC21, a consequence of the smaller dataset available
+ for hard scattering on nuclear targets.
+ %
+ Given that these  functional forms are fixed when applying Hessian profiling,
+ assessing the impact on a nuclear PDFs by a direct refit, as was done for NNPDF4.0,
+ may provide a more  robust estimate of the impact of FPF structure function data
+ on nuclear PDFs.
+ %
+ Additional results for the Hessian profiling of EPPS21 are presented in App.~\ref{app:nPDF_impact_appendix}.

### 2023-08-24 paper/app-nuclearPDFs.tex
appendix B

@@
 \clearpage
-\section{Impact of FPF DIS data on nuclear PDFs}
+\section{Additional nPDF impact studies}
 \label{app:nPDF_impact_appendix}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{The fractional uncertainties (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ of the EPPS21 global determination of nuclear PDFs (red),
-specifically of the set with $A=184$ (tungsten target), 
-compared to the results of profiling with the FASER$\nu$2 DIS projections.
-The impact of the baseline LHC neutrino dataset, 
-consisting of the FASER$\nu$2 experiment inclusive and charm structure functions and charge flavour separation,
-assuming statistical errors only (blue), 
-is compared to the case accounting for both statistical and systematic uncertainties (green).
-}
-\label{fig:profiling_syst_nuclear}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The impact of the FPF structure function measurements on the
+EPPS21 nuclear PDF determination has been studied in Sect.~\ref{sec:nuclearPDFs}.
+%
+Here we provide additional results from this study, and specifically quantify the impact
+that removing charm-tagged structure functions and flavour-charge
+identification capabilities would have on the projected results.
+%
+Figs.~\ref{fig:EPPS21_nocharm} and~\ref{fig:EPPS21_nochargeID} display
+the analogous comparisons as in Figs.~\ref{fig:FASERnu2_nocharm}
+and~\ref{fig:EPPS21_nochargeID} in the case of EPPS21.
+%
+In both cases, results are consistent with the proton PDF profiling analysis.
+
+First of all, charm-tagged events are essential to achieve the best
+sensitivity to the strange PDF, while they have a vanishing impact on the
+other PDF combinations.
+%
+Second, not being able to identify the charge of the outgoing final-state lepton
+does not affect sizable the baseline results, with the possible exception
+of the down valence quark PDF.
+%
+As discussed in Sect.~\ref{sec:nudis_revisited}, for a non-isoscalar target
+such as tungsten, with $Z=74$ and $A-Z=110$, event rates with neutrino projectiles
+will differ from those arising from antineutrino scattering, introducing
+hence some additional information as compared to an isoscalar target in terms
+of PDF sensitivity.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{The effect of FASER$\nu$2 structure functions once charm-tagged measurements are removed, assuming only statistical uncertainties in both cases.
+\caption{Same as Fig.~\ref{fig:FASERnu2_nocharm} in the case of EPPS21.
 }
-\label{fig:profiling_charm_nuclear}
+\label{fig:EPPS21_nocharm}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{The effect of being unable to identify the charge of the outgoing lepton in the FASER$\nu$2 pseudodata, assuming only statistical uncertainties.
+\caption{Same as Fig.~\ref{fig:FASERnu2_nochargeID} in the case of EPPS21.
 }
-\label{fig:profiling_nochargediscrimination_nuclear}
+\label{fig:EPPS21_nochargeID}
 \end{figure}

### 2023-08-28 paper/sec-pheno.tex
sect 3 completed
pheno plots

@@
+\clearpage
 \section{Implications for HL-LHC processes}
@@
 %
-We evaluate these cross-sections using NLO matric elements
+We evaluate these cross-sections using NLO matrix elements
 which include  both in the
@@
 analysis.
+
+Fig.~\ref{fig:NNPDF40_pheno_integrated} displays
+fiducial cross-section for representative LHC processes at $\sqrt{s}=14$ TeV
+evaluated with NNPDF4.0 NNLO, compared with the fits including the FPF structure function projections.
+%
+For the latter, we display the variants based only on statistical uncertainties and that
+which includes also systematic errors.
+%
+The central values are set to be the same as in the original NNPDF4.0 calculation in all cases.
+%
+See~\cite{NNPDF:2021njg} for the calculational settings.
+%
+From top to bottom, we show inclusive Drell-Yan production ($Z, W^+, W^-$), Higgs production
+in vector-boson fusion, Higgs associated
+production, and diboson production ($W^+W^-$, $W^+Z$, $W^-Z$).
+%
+We focus on processes dominated by quark-quark and quark-antiquark scattering, given
+that the FPF structure functions would not have any impact on gluon-initiated
+processes such as top quark pair production or Higgs production in gluon fusion.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-integrated.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-integrated.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-integrated.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-integrated.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-integrated.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-integrated.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-integrated.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-integrated.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-integrated.pdf}
+\caption{Fiducial cross-section for representative LHC processes at $\sqrt{s}=14$ TeV
+evaluated with NNPDF4.0 NNLO, compared with the fits including the FPF structure function projections.
+%
+For the latter, we display the variants based only on statistical uncertainties and that
+which includes also systematic errors.
+%
+The central values are set to be the same as in the original NNPDF4.0 calculation in all cases.
+%
+See~\cite{NNPDF:2021njg} for the calculational settings.
+%
+From top to bottom, we show inclusive Drell-Yan production ($Z, W^+, W^-$), Higgs production
+in vector-boson fusion, Higgs associated
+production, and diboson production ($W^+W^-$, $W^+Z$, $W^-Z$).
+%
+}
+\label{fig:NNPDF40_pheno_integrated}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The corresponding comparison at the level of differential distributions
+are shown in Fig.~\ref{fig:NNPDF40_pheno_differential}.
+%
+As done for the fiducial cross-sections of Fig.~\ref{fig:NNPDF40_pheno_integrated},
+we only indicate the relative PDF uncertainty in each fit, with central values
+assumed to be the same by construction.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-global.pdf}
+\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-global.pdf}
+\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-global.pdf}
+\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-global.pdf}
+\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-global.pdf}
+\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-global.pdf}
+\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-global.pdf}
+\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-global.pdf}
+%\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-global.pdf}
+\caption{Same as Fig.~\ref{fig:NNPDF40_pheno_integrated}
+for the corresponding differential distributions.
+%
+}
+\label{fig:NNPDF40_pheno_differential}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-08-28 paper/scripts/PDFs-lowQ-abs.py
work on Sect 3

@@ -37,7 +37,7 @@ nset=2
 nrep=np.zeros(nset, dtype='int')
 nrep_max = 1000
 
-pdfset=["230309-ern-002","230812-tr-fpf-001"]
+pdfset=["230309-ern-002","230824-tr-fpf-002"]
 
 for iset in range(nset):
 

### 2023-08-28 paper/scripts/PDFs.py

@@ -32,12 +32,12 @@ nfl=6
 # Set x grid
 X = np.logspace(log(xmin),log(xmax),nx)
 # number of pdf sets
-nset=2
+nset=3
 
 nrep=np.zeros(nset, dtype='int')
 nrep_max = 1000
 
-pdfset=["230309-ern-002","230812-tr-fpf-001"]
+pdfset=["230309-ern-002","230824-tr-fpf-002","230824-jcm-fpf-001_iterated"]
 
 for iset in range(nset):
 
@@ -76,6 +76,8 @@ for iset in range(nset):
                         fit1[i-1][ifl][k] = p.xfxQ(2,x,q) - p.xfxQ(-2,x,q)
                     if(iset==1):
                         fit2[i-1][ifl][k] = p.xfxQ(2,x,q) - p.xfxQ(-2,x,q)
+                    if(iset==2):
+                        fit3[i-1][ifl][k] = p.xfxQ(2,x,q) - p.xfxQ(-2,x,q)
 
                 elif(ifl==1):
                     # dV
@@ -83,13 +85,17 @@ for iset in range(nset):
                         fit1[i-1][ifl][k] = p.xfxQ(1,x,q) - p.xfxQ(-1,x,q)
                     if(iset==1):
                         fit2[i-1][ifl][k] = p.xfxQ(1,x,q) - p.xfxQ(-1,x,q)
+                    if(iset==2):
+                        fit3[i-1][ifl][k] = p.xfxQ(1,x,q) - p.xfxQ(-1,x,q)
 
                 elif(ifl==2):
                     # gluon
                     if(iset==0):
                         fit1[i-1][ifl][k] = p.xfxQ(0,x,q)
                     if(iset==1):
-                        fit2[i-1][ifl][k] = p.xfxQ(0,x,q) 
+                        fit2[i-1][ifl][k] = p.xfxQ(0,x,q)
+                    if(iset==2):
+                        fit3[i-1][ifl][k] = p.xfxQ(0,x,q) 
 
                 elif(ifl==3):
                     # singlet
@@ -101,20 +107,28 @@ for iset in range(nset):
                         fit2[i-1][ifl][k] = p.xfxQ(2,x,q) + p.xfxQ(-2,x,q) +\
                             p.xfxQ(1,x,q) + p.xfxQ(-1,x,q) +\
[…]

### 2023-08-28 paper/scripts/lumis.py

@@ -27,12 +27,14 @@ epsrel=5e-3
 #------------------------------------------------------------------------------------
 #------------------------------------------------------------------------------------
 
-nset=2
-pdfset=["210713-n3fit-001","NNPDF_FASERV2"]
-pdfsetlab=[r"${\rm Current~Data~(NNPDF4.0)}$",\
-           r"${\rm Current~Data+FASER}\nu 2$"]
-error_option=["mc_68cl","mc_68cl"]
-filelabel="-fasernu2"
+nset=3
+pdfset=["230309-ern-002","230824-tr-fpf-002","230824-jcm-fpf-001_iterated"]
+
+pdfsetlab=[r"${\rm NNPDF4.0}$",\
+                   r"${\rm NNPDF4.0}+{\rm FPF~(stat\,only)}$",\
+                   r"${\rm NNPDF4.0}+{\rm FPF~(stat+sys)}$"]
+error_option=["mc_1sigma","mc_1sigma","mc_1sigma"]
+filelabel="-FPFall"
 
 #------------------------------------------------------------------------------------
 #------------------------------------------------------------------------------------
@@ -395,102 +397,40 @@ for ilumi in range(nlumi):
     norm = abs(lumi1_mid[ilumi]+eps) # avoid crossing zero
     # print(norm)
 
+    # Only interested in relative reduction of uncertainties
+
     ax = py.subplot(gs[ilumi])
-    p1=ax.plot(mx,norm/norm,lumi1_mid[ilumi],ls="solid",color=rescolors[0])
+    p1=ax.plot(mx,norm/norm,lumi1_mid[ilumi],ls="solid",color=rescolors[0],lw=2)
     ax.fill_between(mx,lumi1_high[ilumi]/norm,lumi1_low[ilumi]/norm,color=rescolors[0],alpha=0.2)
     p2=ax.fill(np.NaN,np.NaN,color=rescolors[0],alpha=0.2)
-    p3=ax.plot(mx,lumi2_mid[ilumi]/norm,ls="dashed",color=rescolors[1])
-    ax.fill_between(mx,lumi2_high[ilumi]/norm,lumi2_low[ilumi]/norm,color=rescolors[1],alpha=0.2)
[…]

### 2023-08-28 paper/sec-results.tex
work on Sect 3
sect 3 done

@@
 in  Fig.~\ref{fig:NNPDF40_baseline} now for the absolute PDFs
-at the initial parametrisation scale, $Q=1.65$ GeV, using a linear scale.
+at the initial parametrisation scale, $Q=1.65$ GeV, using a linear scale, for the statistics-only
+scenario.
 %
@@
 the baseline NNPDF4.0 NNLO determination and its variant which includes
-the combined FPF pseudo-data from the FASER$\nu$2, FLArE100, and AdvSND experiments.
+the combined FPF pseudo-data from the FASER$\nu$2, FLArE100, and AdvSND experiments,
+see Figs.~\ref{fig:NNPDF40_baseline} or the corresponding PDF comparison.
 %
-We display the optimistic scenario where only statistical uncertainties
-  are included. 
 %
@@
   %
-  Specifically, we show the quark-quark, quark-antiquark, $u\bar{d}$, and $d\bar{u}$
-  luminosities, where the latter two combinations are those dominating $W^+$ and $W^-$ production
-  at the LHC.
+  Specifically, we show the gluon-gluon, quark-antiquark, and
+  quark-quark luminosities.
   %
@@
 \centering
-\includegraphics[width=0.49\textwidth]{plots/qqlumi_nnpdf40_allfpf.pdf}
-\includegraphics[width=0.49\textwidth]{plots/qqbarlumi_nnpdf40_allfpf.pdf}
-\includegraphics[width=0.49\textwidth]{plots/udbarlumi_nnpdf40_allfpf.pdf}
-\includegraphics[width=0.49\textwidth]{plots/dubarlumi_nnpdf40_allfpf.pdf}
+\includegraphics[width=0.99\textwidth]{plots/lumi-FPFall.pdf}
 \caption{Comparison of the PDF luminosities at $\sqrt{s}=14$ TeV
   as a function of the final-state invariant mass $m_X$ between
-  the baseline NNPDF4.0 NNLO determination and its variant which includes
-  the full set of FPF pseudo-data, in the scenario where only statistical uncertainties
-  are included. 
+  the baseline NNPDF4.0 NNLO determination and its variants which include
+  the full set of FPF pseudo-data, see Figs.~\ref{fig:NNPDF40_baseline}
+  for the corresponding PDF comparison.
   %
   Results are shown normalised to the central value of the NNPDF4.0 baseline.
+  %
+  From left to right we show the gluon-gluon, quark-antiquark, and
+  quark-quark luminosities.
 %
@@
 and~\ref{fig:NNPDF40_lowQ_abs} is also visible
-for the partonic luminosities.
+for the partonic luminosities, specially on the scenario where only statistical
+uncertainties in the FPF pseudo-data are considered.
 %
-The improvement for the $u\bar{d}$ and $d\bar{u}$ luminosities at $Q\sim 100$ GeV
+The improvement quark-antiquark luminosities at $Q\sim 100$ GeV
 benefits theoretical predictions for $W$ and $Z$ production at the LHC.
@@
 It is also worth noting the PDF error reduction for the quark-quark luminosity at high invariant masses,
-which will feed into searches for new heavy particles at the TeV scale.
-
-\clearpage
+which will feed into searches for new heavy particles at the TeV scale driven by quark-initiated scattering.
 

### 2023-08-28 paper/FPF-WG1.tex
small typo
new nnpdf40 plots
paper abstract

@@
  we highlight the impact on the proton and nuclear PDFs of the FPF
- experiments in a kinematic region in $x$ and $Q^2$ which is comparable to that
- to be covered at the upcoming
+ experiments in a kinematic region in $x$ and $Q^2$ comparable to that
+ covered by the upcoming
  Electron-Ion Collider (EIC).
@@
  This sensitivity is found to be the largest for  strangeness as well as for
- the up and down valence quark PDFs.
+ the up and down valence quark PDFs, and lead to improved theoretical
+ predictions for key scattering processes at the HL-LHC.
 %
@@
 
-% REsults for the proton PDFs, using NNPDF and PDF4LHC21/xfitter
-\input{sec-protonPDFs}
+% REsults 
+\input{sec-results}
+
+% Pheno
+\input{sec-pheno}
 

### 2023-08-29 paper/sec-results.tex
Update pheno plots and Chi2 tables

@@
   \midrule
-  $\chi^2$ &  \multirow{4}{*}{Global}      &  &    &  \\
+  $\chi^2$ &  \multirow{4}{*}{Global}  & 1.170 &  1.161  & 1.145  \\
   $\la E_{\rm tr}\ra_{\rm rep}$
-  & &    &     &   \\
+  &  &  2.256  &  2.242   & 2.215   \\
   $\la E_{\rm val}\ra_{\rm rep}$
-  & &     &     & \\
+  & & 2.360    &   2.332  & 2.311  \\
   $\la \chi^2\ra_{\rm rep}$
-  & &      &        &   \\
+  & &   1.194   &    1.187    & 1.169  \\
   \midrule
   \multirow{8}{*}{$\chi^2$}
-  & DIS neutral-current                     &      &       &      \\
-  & DIS charged-current                     &     &       &      \\
-  & Drell--Yan (inclusive and one-jet) &     &       &      \\
-  & Top-quark pair production               &     &       &      \\
-  & Single-top production                   &     &       &      \\
-  & Inclusive jet production                &     &       &      \\
-  & Dijet production                        &     &       &      \\
-  & Direct photon production                 &    &       &      \\
+  & DIS neutral-current                     &  1.220    &  1.230    &   1.220   \\
+  & DIS charged-current                     &   0.904  &   0.942    &  0.913    \\
+  & Drell--Yan (inclusive and one-jet) &  1.76   &   1.830    &   1.830   \\
+  & Top-quark pair production               &  1.230   &   1.220    &  1.250    \\
+  & Single-top production                   &  0.362   &   0.364    &   0.361   \\
+  & Inclusive jet production                &  0.957   &  0.963     &   0.942   \\
+  & Dijet production                        &  2.030    &    2.010   &   2.010   \\
+  & Direct photon production                 &  0.740  &   0.729    &    0.744  \\
   & FPF (total)                 &  -  &       &      \\

### 2023-08-29 paper/sec-pheno.tex
pheno

@@
 processes such as top quark pair production or Higgs production in gluon fusion.
+%
+The corresponding comparison at the level of differential distributions
+are shown in Fig.~\ref{fig:NNPDF40_pheno_differential}.
+%
+As done for the fiducial cross-sections of Fig.~\ref{fig:NNPDF40_pheno_integrated},
+we only indicate the relative PDF uncertainty in each fit, with central values
+assumed to be the same by construction.
 
@@
 \includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-integrated.pdf}
-\caption{Fiducial cross-section for representative LHC processes at $\sqrt{s}=14$ TeV
+\caption{Fiducial cross-sections for representative LHC processes at $\sqrt{s}=14$ TeV
 evaluated with NNPDF4.0 NNLO, compared with the fits including the FPF structure function projections.
 %
-For the latter, we display the variants based only on statistical uncertainties and that
-which includes also systematic errors.
+For the NNPDF4.0 baseline
+prediction, the dark (light) bands indicate the 68\% (95\%) CL uncertainties.
+%
+The fit labelled as ``\_FPF'' is the one  based on statistical uncertainties,
+while that labelled as ``\_FPF$^*$'' also includes systematic errors.
 %
@@
 %
-See~\cite{NNPDF:2021njg} for the calculational settings.
+See~\cite{NNPDF:2021njg,PDF4LHCWorkingGroup:2022cjn} for the calculational settings.
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The corresponding comparison at the level of differential distributions
-are shown in Fig.~\ref{fig:NNPDF40_pheno_differential}.
-%
-As done for the fiducial cross-sections of Fig.~\ref{fig:NNPDF40_pheno_integrated},
-we only indicate the relative PDF uncertainty in each fit, with central values
-assumed to be the same by construction.
 
@@
 \includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-global.pdf}
-%\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-global.pdf}
+\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-global.pdf}
 \caption{Same as Fig.~\ref{fig:NNPDF40_pheno_integrated}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Inspection of Figs.~\ref{fig:NNPDF40_pheno_integrated} and~\ref{fig:NNPDF40_pheno_differential}
+quantifies the potential of neutrino structure function measurements at the LHC
+to improve theoretical predictions for electroweak and high-scale processes at the HL-LHC.
+%
+Concerning first the fiducial integrated cross-sections, a reduction of PDF
+uncertainties is observed for all processes,
+including for $W^+$ production relevant for $m_W$ measurements, and its specific  magnitude depends
+on the underlying scattering reaction.
+%
+This finding also applies for Higgs associated production with vector bosons and in vector-boson-scattering,
+with for example
+PDF uncertainties in $hW^+$ reduced by up to a factor two thanks to the FPF measurements.
+%
+Similar remarks apply to the diboson cross-sections, with in this case the largest
+improvement observed for $ZW^+$ channel.
+%
+Reassuringly, LHC predictions based on the fits with FPF pseudo-data are stable
+upon the inclusion of the experimental systematic uncertainties in the fit.
+
+In the case of the differential cross-sections shown in Fig.~\ref{fig:NNPDF40_pheno_differential},
+we observe how the impact of the FPF structure functions on LHC observables depends
+on the hard-scattering scale.
+%
+For instance, searches for heavy-resonances in the high-mass tail of the Drell-Yan
+distributions are going to be improved by FPF data.
+%
+The same applies for diboson prediction, and in the case of the $ZW^+$ channel we observe
+an improvement spatially in the low $p_{T,\ell\bar{\ell}}$ region.
+%
+For the Higgs production processes, the PDF uncertainty in the theory predictions is relatively
+stable as a function of the rapidity.
+%
+The effects of accounting for systematic uncertainties in the fit are somewhat more visible
+here as compared to the inclusive cross-sections, indicating that they affect mostly
+the tails, rather than the bulk, of the distributions, and in particular the large-$x$
+behaviour of the PDFs.
+
+The studies presented in this section provide only a first glimpse of the potential
+of neutrino DIS measurements at the LHC to inform predictions for high-$p_T$ processes.

### 2023-08-29 paper/sec-results.tex
pheno

@@
   &
-  & Baseline
+  & \multirow{2}{*}{Baseline}
   & \multicolumn{2}{c}{with combined FPF data}  \\
@@
 the NNPDF4.0 global fit is not distorted by the inclusion of the FPF data.
+%
+In particular, the $\chi^2$ of the available (non-FPF) DIS neutral-current and charged-current
+datasets changes from 1.220 and 0.904 in NNPDF4.0 to 1.220 and 0.913 in the fit
+with FPF pseudo-data.
+%
+A moderate increase is found to the $\chi^2$ of Drell-Yan processes, from 1.76 to 1.83, possibly
+because of the enhanced weight that DIS data carries in this fit variant.
 

### 2023-08-30 paper/sec-dis-pseudodata.tex
sect 3.2
appendix B
minor typos, addressed some comments

@@
  \subsection{Neutrino DIS revisited}
+ \label{sec:nudis_revisited}
 
@@
 Neutrino detection and identification can be carried out either using the emulsion
-films of FASER$\nu$2, which have the key benefit of excellent position and angular resolution,
+films, which have the key benefit of excellent position and angular resolution,
 or instead using the electronic detector components of FASER, which enable the tagging
@@
  No information on the expected performance of the AdvSND-far detector
- is available and hence to estimate of the systematic errors
+ is available and hence no estimate of the systematic errors
  is carried out.
@@
  %
- The use of LAr as target is beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimeter spatial resolution in all dimensions.
- %
- FLArE is suitable to identify high-energy neutrinos ($E_\nu \gsim 100$ GeV)  from all three generations
- while containing the events as required for kinematic reconstruction.
+ The use of LAr as a target is beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimeter spatial resolution in all dimensions.
+ %
+% FLArE is suitable to identify high-energy neutrinos ($E_\nu \gsim 100$ GeV)  from all three generations while containing the events as required for kinematic reconstruction.
  %
@@
 
- With an expected fiducial (active) mass of 10 tons (30 tons) and length 3 m, FLArE will
+ With an expected fiducial (active) mass of 10 tons (30 tons) and length 7 m, FLArE will
  detect final-state electrons with energies $E_{e}\lsim 2~\rm{TeV}$ and
@@
 %
-When choosing the binning of the measurement, the main criteria are
-simplicity and ensuring that Gaussian statistics holds in all bins.{\color{blue} [MF: What does this mean exactly? Binning has not been chosen based on any criteria]}
+When choosing the binning of the measurement, we simply choose log-spaced bins in $x$ and $Q^2$.
 
@@
 \end{equation}
-with $n_T$ is the nuclear density of the target detector material, $L_T$ its
+with $n_T$ is the nucleon density of the target detector material, $L_T$ its
 length and ${\cal A}(x,Q^2,E_{\nu})$ is an acceptance factor which takes the form of a
@@
  \subsection{PDF impact assessment}
+ \label{subsec:pdf_impact_assessment}
 

### 2023-08-30 paper/tables/detectors.tex
E_hadron_min

@@
 \midrule
-\multirow{3}{*}{FASER$\nu$}  &  \multirow{3}{*}{ $\eta_\nu \ge 8.5$}  &   \multirow{2}{*}{Tungsten}  & \multirow{3}{*}{muons}      &   $E_\ell \gsim 100$ GeV   &      $\delta E_\ell \sim 30\% $    \\
+\multirow{3}{*}{FASER$\nu$}  &  \multirow{3}{*}{ $\eta_\nu \ge 8.5$}  &   \multirow{2}{*}{Tungsten}  & \multirow{3}{*}{muons}      &   $E_\ell,E_h \gsim 100$ GeV   &      $\delta E_\ell \sim 30\% $    \\
 &   &   \multirow{2}{*}{(1.1 ton)}  &       &  $\tan \theta_\ell \lsim 0.025$   &
@@
 \midrule
-\multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &   \multirow{2}{*}{n/a}    &  $E_\mu \gsim 20 $ GeV     &    \multirow{2}{*}{n/a}    \\
+\multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &   \multirow{2}{*}{n/a}    &  $E_\mu,E_h \gsim 20 $ GeV     &    \multirow{2}{*}{n/a}    \\
   &    &  (0.83 ton)   &  &  $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$         &       \\
@@
 \midrule
-\multirow{3}{*}{FASER$\nu$2}  & \multirow{3}{*}{ $\eta_\nu \ge 8.5$}  & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{muons}     &   $E_\ell \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
+\multirow{3}{*}{FASER$\nu$2}  & \multirow{3}{*}{ $\eta_\nu \ge 8.5$}  & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{muons}     &   $E_\ell,E_h \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
   &   &  \multirow{2}{*}{(20 ton)}   &       &  $\tan \theta_\ell \lsim 0.05$   &   $\delta \theta_\ell \sim 0.06$ mrad      \\
@@
 \multirow{3}{*}{AdvSND-far}  &   \multirow{3}{*}{ $7.2 \le \eta_\nu \le 8.4$}  &
-\multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{muons}    &  $E_\mu \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
+\multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{muons}    &  $E_\mu,E_h \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
   &   &   \multirow{2}{*}{(5 ton)}  &        & $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$     &           \\
@@
 \midrule
-\multirow{3}{*}{FLArE ({\bf *})}  & \multirow{3}{*}{$\eta_\nu \ge 7.5$} & \multirow{2}{*}{LAr}  & \multirow{3}{*}{muons}  &  $E_\mu \gsim 2$ GeV, $E_e \lsim 2$ TeV    &    $\delta E_e \sim 5\% $,  $\delta E_\mu \sim 30\% $ \\
+\multirow{3}{*}{FLArE ({\bf *})}  & \multirow{3}{*}{$\eta_\nu \ge 7.5$} & \multirow{2}{*}{LAr}  & \multirow{3}{*}{muons}  &  $E_\mu,E_h \gsim 2$ GeV, $E_e \lsim 2$ TeV    &    $\delta E_e \sim 5\% $,  $\delta E_\mu \sim 30\% $ \\
 &   &  \multirow{2}{*}{(10 ton)}   &   & $\theta_\mu \lsim 0.025$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $,

### 2023-08-30 paper/tables/detectors.tex
updated to include electron acceptance

@@
 \midrule
-\multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &   \multirow{2}{*}{n/a}    &  $E_\mu,E_h \gsim 20 $ GeV     &    \multirow{2}{*}{n/a}    \\
+\multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &   \multirow{2}{*}{n/a}    &  $E_\ell,E_h \gsim 20 $ GeV     &    \multirow{2}{*}{n/a}    \\
   &    &  (0.83 ton)   &  &  $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$         &       \\
@@
 \multirow{3}{*}{AdvSND-far}  &   \multirow{3}{*}{ $7.2 \le \eta_\nu \le 8.4$}  &
-\multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{muons}    &  $E_\mu,E_h \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
+\multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{muons}    &  $E_\ell,E_h \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
   &   &   \multirow{2}{*}{(5 ton)}  &        & $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$     &           \\
@@
 \midrule
-\multirow{3}{*}{FLArE ({\bf *})}  & \multirow{3}{*}{$\eta_\nu \ge 7.5$} & \multirow{2}{*}{LAr}  & \multirow{3}{*}{muons}  &  $E_\mu,E_h \gsim 2$ GeV, $E_e \lsim 2$ TeV    &    $\delta E_e \sim 5\% $,  $\delta E_\mu \sim 30\% $ \\
+\multirow{3}{*}{FLArE ({\bf *})}  & \multirow{3}{*}{$\eta_\nu \ge 7.5$} & \multirow{2}{*}{LAr}  & \multirow{3}{*}{muons}  &  $E_\ell,E_h \gsim 2$ GeV, $E_e \lsim 2$ TeV    &    $\delta E_e \sim 5\% $,  $\delta E_\mu \sim 30\% $ \\
 &   &  \multirow{2}{*}{(10 ton)}   &   & $\theta_\mu \lsim 0.025$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $,

### 2023-08-30 paper/sec-dis-pseudodata.tex
removed comparison with whitepaper's yield
Integrating over the diff-xsec we use, we get a smaller total-xsec. A part of this is due to NLO vs LO

@@
 %
-We have verified that the differential event yield calculation
-implemented in Eq.~(\ref{eq:event_yields_calculation}), when extrapolated to a single bin
-covering the full detector acceptance,
-is consistent with the fiducial interaction rates presented in~\cite{Feng:2022inv} once DIS cuts are imposed and detector acceptances are accounted for.
+%We have verified that the differential event yield calculation
+%implemented in Eq.~(\ref{eq:event_yields_calculation}), when extrapolated to a single bin
+%covering the full detector acceptance,
+%is consistent with the fiducial interaction rates presented in~\cite{Feng:2022inv} once DIS cuts are imposed and detector acceptances are accounted for.
+%
 

### 2023-08-31 paper/tables/detectors.tex
Minor corrections

@@
 \multirow{3}{*}{FLArE ({\bf *})}  & \multirow{3}{*}{$\eta_\nu \ge 7.5$} & \multirow{2}{*}{LAr}  & \multirow{3}{*}{muons}  &  $E_\ell,E_h \gsim 2$ GeV, $E_e \lsim 2$ TeV    &    $\delta E_e \sim 5\% $,  $\delta E_\mu \sim 30\% $ \\
-&   &  \multirow{2}{*}{(10 ton)}   &   & $\theta_\mu \lsim 0.025$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $,
-$\delta \theta_\mu \sim 0.06$ mrad\\
+&   &  \multirow{2}{*}{(10 ton)}   &   & $\theta_\mu \lsim 0.025$, $\theta_e \lsim 0.5$ &    $\delta \theta_\ell \sim 15 $ mrad\\
  &   &     &  & reco $E_h$  &    $\delta E_h \sim 30\% $   \\

### 2023-08-31 paper/sec-dis-pseudodata.tex
Fixed details, cleaned up text

@@
 \be
+\label{eq:W2_invmass}
 W^2 = \lp m_N^2 + Q^2 \frac{(1-x)}{x} \rp \gsim \lp 2\,{\rm GeV} \rp^2\, ,
@@
  %
- Since muon neutrinos would be measured by FASER$\nu$2, the
- performance parameters for $E_\mu$ and $\theta_\mu$ are  taken
+ Since the muon energy from a charged-current interaction would be measured by FASER2, the
+ performance parameters for $E_\mu$ are  taken
  to be the same as those of FASER$\nu$2 as indicated
@@
 The bin-by-bin integrated event yields in Eq.~(\ref{eq:event_yields}) are
-obtained by convoluting the incoming neutrino fluxes, for a given geometric acceptance
+obtained by convoluting the incoming neutrino fluxes, for a given acceptance
 of the target detector, with the corresponding neutrino differential cross-sections
@@
 %
-Differential event yields are evaluated using
+Binned event yields are evaluated using
 \begin{equation}
@@
 length and ${\cal A}(x,Q^2,E_{\nu})$ is an acceptance factor which takes the form of a
-step function and accounts for the experimental acceptance thresholds
+step function and accounts for the experimental acceptances
 in $E_\ell$, $\theta_\ell$, and $E_h$
@@
 \ee
-and then  integrating over the bin range:
-\bea
-   && N_{\rm ev}^{(i)} \approx n_T L_T \frac{(Q^{2(i)}_{\rm max}-Q^{2(i)}_{\rm min})(x^{(i)}_{\rm max}-x^{(i)}_{\rm min})(E_{\rm max}^{(i)}-E_{\rm min}^{(i)})}{N_{\rm mc}}\times \nonumber \\&& \sum_{j=1}^{N_{\rm mc}}\lc  \frac{dN_{\nu}(E^{(j)}_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x^{(j)},Q^{2(j)},E^{(j)}_{\nu})}{dxdQ^2}\right) {\cal A}(x^{(j)},Q^{2(j)},E_{\nu}^{(j)})\rc \, ,
-    \label{MCintegration}
-\eea
 and where $N_{\rm mc}$ is chosen to be large enough such that residual Monte Carlo integration
@@
 The numbers in parenthesis indicate the event rates corresponding to charm
-production, for those experiments with heavy flavour tagging capabilities.
+production, assuming heavy flavour tagging capabilities.
 %
@@
 First, one appreciates the large increase in statistics from
-the Run III experiments to the FPF ones, with for example a factor
-250 increase in the muon neutrino yield between FASER$\nu$ and
+the Run III experiments to the FPF ones, with for example a factor of
+$\sim$ 250 increase in the muon neutrino yield between FASER$\nu$ and
 FASER$\nu$2.
 %
-Second, muon neutrino scattering dominate over the electron ones by a factor
+Second, the muon neutrino scattering yield dominates over electron neutrino scattering by a factor
 between 2 and 3, though this ratio is affected by the large theory uncertainties
@@
 yields, with both FASER$\nu$2 and FLArE-100 resulting in around
-60k recorded charm-production events.
+40k recorded charm-production events.
 %
@@
 Fourth, FASER$\nu$2 and FLArE-100 lead to the largest absolute
-yields of the FPF experiments, with around 500k and 600k (non-tau) neutrino DIS events respectively, with 56k and 131k
+yields of the FPF experiments, with around 260k and 340k (non-tau) neutrino DIS events respectively, with 28k and 57k
 events expected instead for AdvSND-far and FLArE-10.
@@
  for muon neutrinos detected at the
- FASER$\nu$ (Run III) and the AdvSND, FASER$\nu$2, and FLArE  (FPF) experiments,
+ FASER$\nu$ (Run III) and the AdvSND, FASER$\nu$2, and FLArE-100  (FPF) experiments,
  restricted
  to the DIS region defined by Eq.~(\ref{eq:DISconditions})
- and where only bins with $\ge 30$ events are retained.
+ and where only bins with $\ge 100$ events are retained, except for FASER$\nu$ in which bins with $\ge 10$ events are shown.
  %
@@
 10 events for Run III experiments (FASER$\nu$, SND), the fractional statistical uncertainty
-ranges between $\lsim 1\%$ and $\sim 18\%$, depending on the values of
+ranges between $\lsim 1\%$ and $\sim 30\%$, depending on the values of
 $x$ and $Q^2$ associated to each bin.
@@
 In order to determine these bin-by-bin systematic errors,
-we extend the calculation delineated in Eq.~(\ref{sec:pseudo-data_generation}) as follows.
-%
-Let us consider for illustrative purposes the FASER${\nu}$2 detector.
-%
-From Table~\ref{tab:FPF_experiments} we know that its
-acceptance parameters and reconstruction performance are specified by:
-\bea
-E_\ell \ge 100~{\rm GeV} \, , \quad \theta_\ell \le \tan^{-1}(0.025)\, , \qquad\\
-\delta E_\ell \sim 30\% \, 
- \quad \delta E_h \sim 30\% \, ,
- \quad \delta\theta_\ell \sim 0.06~{\rm mrad} \, . 
-\label{eq:fasernu2systematic_errors}
-\eea
-To translate these uncertainties in $\delta E_\ell$, $\delta E_h $,
+we extend the calculation delineated in Sec.~(\ref{sec:pseudo-data_generation}) as follows.
+%{\color{blue} [MF: I don't think this faser example is necessary]}
+%Let us consider for illustrative purposes the FASER${\nu}$2 detector.
+%
+%From Table~\ref{tab:FPF_experiments} we know that its
+%acceptance parameters and reconstruction performance are specified by:
+%\bea
+%E_\ell \ge 100~{\rm GeV} \, , \quad \theta_\ell \le \tan^{-1}(0.025)\, , \qquad\\
+%\delta E_\ell \sim 30\% \, 
+ %\quad \delta E_h \sim 30\% \, ,
+ %\quad \delta\theta_\ell \sim 0.06~{\rm mrad} \, . 
+%\label{eq:fasernu2systematic_errors}
+%\eea
+%To translate these uncertainties in $\delta E_\ell$, $\delta E_h $,
+To translate uncertainties in $\delta E_\ell$, $\delta E_h $
 and $\delta\theta_\ell$ into systematic errors associated to the event yields, 
@@
 \ee
-we generate first a Monte Carlo set of events, denoted by $\mathcal{D}_0$,
+we first generate a Monte Carlo set of events, denoted by $\mathcal{D}_0$,
 composed by $N_{\rm mc} \approx 10^7$ samples and determine the assignment of each event
@@
 %
-By comparing $\mathcal{D}_0$ with the total number of events as calculated by Eq.~(\ref{MCintegration}), 
-we can normalize the distribution to produce the expected yield.
-
-We then produce a second Monte Carlo sample $\mathcal{D}_1$ starting from the events
-of $\mathcal{D}_0$ which are then smeared with Gaussian distributions whose variances
-are given by Eq.~(\ref{eq:fasernu2systematic_errors}).
-%
-The bin assignment of the events in the smeared sample $\mathcal{D}_1$ will
-in general be different from those of the baseline sample.
-%
-The procedure is repeated $M$ times, leading to
-$\mathcal{D}_k$ (with $k=1,\ldots,M$) smeared
-samples each one leading to a different binned event yields
-$ N_{\rm ev}^{(i)(k)}$.
+By comparing $\mathcal{D}_0$ with the number of events as calculated by Eq.~(\ref{eq:event_yields_calculation}), 
+we can normalize the sampled distribution with a factor $\hat{n}$ to reproduce the expected yield.
+
+We then take each event in $\mathcal{D}_0$ and smear it with Gaussian distributions whose variances are given by Table~\ref{tab:FPF_experiments} to produce new samples $\mathcal{D}_k$.
+The smeared samples are subjected to the same DIS cuts from Eq.~(\ref{eq:DISconditions}) and acceptances from Table~\ref{tab:FPF_experiments}.
+The bin assignment of the events in the smeared samples $\mathcal{D}_k$ will in general be different from those of the baseline sample.
+
 %
@@
 to a given systematic source, say $\delta E_\ell$,
-%to be the absolute difference between the mean number of events in this
-%bin evaluated for the smeared samples and the
-%central prediction for the number of events
-to be the mean of the absolute difference between the number of events in this bin for the smeared samples and the central prediction for the number of events
-$ N_{\rm ev}^{(i)}$ as calculated from Eq.~(\ref{MCintegration}):
-\be
-\delta_{\rm sys}^{(E_\ell)} N^{(i)} =\la \Big|  {N}^{(i)}_{E_\ell-{\rm smeared}} -N_{\rm ev}^{(i)}\Big|\ra \, .
+to be the mean of the absolute difference between the number of events in this bin for the smeared samples, normalized by $\hat{n}$, and the central prediction for the number of events
+$ N_{\rm ev}^{(i)}$ as calculated from Eq.~(\ref{eq:event_yields_calculation}):
+\be
+\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} =\la \Big|  \hat{n}\times{N}^{(i)}_{E_\ell-{\rm smeared}} -N_{\rm ev}^{(i)}\Big|\ra \, .
 \ee

### 2023-09-01 paper/sec-dis-pseudodata.tex
minor wording changes. nu-flux description

@@
 and neutrino pseudo-rapidity $\eta_\nu$ coverage of the considered detector,
-are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$.
-%
-%We have verified that the differential event yield calculation
-%implemented in Eq.~(\ref{eq:event_yields_calculation}), when extrapolated to a single bin
-%covering the full detector acceptance,
-%is consistent with the fiducial interaction rates presented in~\cite{Feng:2022inv} once DIS cuts are imposed and detector acceptances are accounted for.
-%
+are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$~\cite{Kling:2021gos}.
+The neutrino flux takes into account both the prompt component associated with neutrinos from charmed hadron decay as well as a displaced component from light hadron decays.
+The prompt component was simulated at NLO using \textsc{POWHEG}~\cite{Nason:2004r,Frixione:2007vwx,Alioli:2010xd} and \textsc{Pythia}~\cite{Sjostrand:2014zea, Bierlich:2022pfr} for the parton shower and hadronization, and the displaced component was simulated with \textsc{Epos-Lhc}~\cite{Pierog:2013ria}.
+In addition to the updated charmed hadron production, the neutrino flux from Ref.~\cite{Kling:2021gos} was also updated for $\sqrt{s} = 13.6~{\rm TeV}$.
 
@@
 By comparing $\mathcal{D}_0$ with the number of events as calculated by Eq.~(\ref{eq:event_yields_calculation}), 
-we can normalize the sampled distribution with a factor $\hat{n}$ to reproduce the expected yield.
-
-We then take each event in $\mathcal{D}_0$ and smear it with Gaussian distributions whose variances are given by Table~\ref{tab:FPF_experiments} to produce new samples $\mathcal{D}_k$.
-The smeared samples are subjected to the same DIS cuts from Eq.~(\ref{eq:DISconditions}) and acceptances from Table~\ref{tab:FPF_experiments}.
-The bin assignment of the events in the smeared samples $\mathcal{D}_k$ will in general be different from those of the baseline sample.
+we can normalize the sampled $\mathcal{D}_0$ distribution with a factor $\hat{n}$ to reproduce the expected yield.
+
+We then take each event in $\mathcal{D}_0$ and smear it with Gaussian distributions whose variances are given by Table~\ref{tab:FPF_experiments} to produce a set of new samples $\{\mathcal{D}_k\}$.
+The smeared events are subjected to the same DIS cuts from Eq.~(\ref{eq:DISconditions}) and acceptances from Table~\ref{tab:FPF_experiments}.
+The bin assignment of the events in the smeared samples $\mathcal{D}_k$ will in general be different from those of the baseline sample $\mathcal{D}_0$.
 
@@
 to a given systematic source, say $\delta E_\ell$,
-to be the mean of the absolute difference between the number of events in this bin for the smeared samples, normalized by $\hat{n}$, and the central prediction for the number of events
+to be the mean of the absolute difference between the number of events in this bin for the smeared samples $\{\mathcal{D}_k\}$ normalized by $\hat{n}$, and the central prediction for the number of events
 $ N_{\rm ev}^{(i)}$ as calculated from Eq.~(\ref{eq:event_yields_calculation}):
@@
 
-In general, systematic uncertainties associated to the hadronic final state energy $E_h$ appear to be the largest,
-reaching up to $\sim 90\%$ for some experiments.
-%
-We recall that measurement of $E_h$ in addition to the leptonic variables is required to
-fix the incoming neutrino energy $E_\nu$, which is different in each event unlike
-the case of neutral-current scattering.
-%
-The uncertainties associated to the charged-lepton energy $E_\ell$ and scattering angle $\theta_\ell$ range
-between a few percent up to 20\% in the  baseline scenario listed in Table~\ref{tab:FPF_experiments}.
-%
-For the $\delta \theta_\ell$ variations, they are smallest in the large-$x$ region
-for $x\gsim 0.1$, where they are at the few-percent level typically.
-%
-Statistical uncertainties are subdominant in most of the bins and are below the 10\% level,
-specially at large-$x$ which is the kinematic region benefitting from the largest event rates.
+For the experiments which use a Tungsten target, the systematic uncertainties associated to the final state energies $E_\ell$, $E_h$ are comparable and are typically $\sim 10\%$ and range from $1\%$ to  ${\cal O}(1)$ across bins.
+The uncertainties associated with $\theta_\ell$ are typically at or well below $1\%$ for these experiments, which can be attributed to the high spatial resolution.
+%
+On the other hand, for the FLArE-10(0) experiment, uncertainties associated with the scattering angle $\theta_\ell$ dominate at $\sim 40\%$ ranging from a few percent to ${\cal O}(1)$.
+Whereas the uncertainties associated with final state energy resconstruction are $\sim 10\%$ and range from $\lesssim 1\%$ to $\sim 80\%$.
+%
+For all experiments, statistical uncertainties are subdominant in most of the bins and are below the 10\% level,
+especially at large-$x$ which is the kinematic region benefitting from the largest event rates.
 
@@
 The end result of the procedure is an estimate of statistical and systematic uncertainties
-for each bin of the measurement, from which a experimental covariance matrix can be constructed as
+for each bin of the measurement, from which an experimental covariance matrix can be constructed as
 \be

### 2023-09-01 paper/sec-results.tex
updated event rate to table

@@
 As summarised by Table~\ref{tab:integrated_rates}, each of these experiments
-has associated different expected numbers of DIS events, namely 370k, 43k, and 81k (420K)
+has associated different expected numbers of DIS events, namely 260k, 28k, and 57k (340K)
 inclusive muon-neutrino events for FASER$\nu$2, AdvSND and FLArE10~(100) respectively,
-with 57k, 4.5k, and 11k (59k) in the charm-tagged case.
+with 39k, 3.5k, and 7.7k (45k) in the charm-tagged case.
 %

### 2023-09-01 paper/sec-summary.tex
added funding and acknowledgements

@@
 We thank specially Felix Kling for may useful discussions in the course
-of the project.
+of the project and for providing the neutrino fluxes.
 %
@@
 Wenjie Wu and Steven Linden concerning FLArE,
-and Antonia di Crescenzo concerning AdvSND.
+and Antonia di Crescenzo concerning AdvSND. The work of M.F. was supported by NSF Grant PHY-2210283 and was also supported by NSF Graduate Research Fellowship Award No. DGE-1839285.

### 2023-09-01 paper/sec-results.tex
some polishing

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
+\begin{figure}[htbp]
 \centering
@@
 \includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_AdvSND/statOnly_AdvSND_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_AdvSND/statOnly_AdvSND_q2_10000_pdf_s_ratio.pdf}
-\caption{
-  Same as  Fig.~\ref{fig:FASERnu2_baseline} (statistical uncertainties only), comparing
-  the projected PDF impact of FASER$\nu$2 with that of AdvSND.
-}
-\label{fig:FASERnu2_advsnd}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\centering
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_AdvSND/statOnly_AdvSND_q2_10000_pdf_s_ratio.pdf}\\
 \includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FLArE10/statOnly_FLArE10_q2_10000_pdf_uv_ratio.pdf}
@@
   comparing
-  the projected PDF impact of FASER$\nu$2 with that of FLArE10. 
+  the projected PDF impact of FASER$\nu$2 with that of  AdvSND (top) and FLArE10 (bottom). 
 }
@@
 our current knowledge about the quark and gluon structure of the proton.
-
-\clearpage
 

### 2023-09-01 paper/FPF-WG1.tex
some polishing
Update FPF-WG1.tex

@@
 
-\vspace{0.7cm}
+\vspace{-2.0cm}
+\begin{flushright}
+Nikhef-2023-aaa\\
+\end{flushright}
+\vspace{0.6cm}
 
@@
 
-Proton-proton collisions at the LHC produce an intense collimated beam of high-energy (TeV) neutrinos
-in the forward direction.
+Proton-proton collisions at the LHC generate a high-intensity collimated beam of neutrinos
+in the forward (beam) direction, characterised by energies of up to several TeV.
 %
-The recent  observation of LHC neutrinos by the FASER$\nu$ and SND@LHC experiments
-indicates that this hitherto ignored beam becomes available for scientific investigations.
+The recent  observation of LHC neutrinos by FASER$\nu$ and SND@LHC
+signals that this hitherto ignored particle beam is now available for scientific inquiry.
 %
-Neutrino deep-inelastic scattering (DIS) is known
-to provide a sensitive probe of the quark flavour separation in nucleons
-and nuclei.
+Here we quantify the impact that neutrino deep-inelastic scattering (DIS) structure function
+measurements at the LHC would have
+on the parton distributions (PDFs) of protons and heavy nuclei.
 %
-Here we quantify the projected impact of DIS neutrino structure functions at the LHC
-on the parton distribution functions (PDFs) of protons and heavy nuclei.
+We generate projections for DIS structure functions
+at FASER$\nu$ and SND@LHC,
+as well as at the FASER$\nu$2, AdvSND, and FLArE experiments
+to be  hosted at the proposed
+Forward Physics Facility (FPF) operating concurrently with the High-Luminosity LHC.
 %
-We generate differential structure function DIS pseudo-data 
-for  FASER$\nu$ and SND@LHC based on the Run III luminosity,
-as well as for the FASER$\nu$2, AdvSND, and FLArE experiments
-to be  hosted at the proposed
- Forward Physics Facility (FPF) operating concurrently with the High Luminosity LHC.
+These measurements are found to cover a kinematic region in $x$ and $Q^2$ comparable to that
+of the upcoming Electron-Ion Collider, with sub-percent statistical uncertainties
+in the FPF case.
 %
- By using both the Hessian profiling of PDF4LHC21 with {\sc\small xFitter} and
- the  NNPDF open-source framework,
- we highlight the impact on the proton and nuclear PDFs of the FPF
- experiments in a kinematic region in $x$ and $Q^2$ comparable to that
- covered by the upcoming
- Electron-Ion Collider (EIC).
+Including these DIS projections into global (n)PDF analyses, specifically PDF4LHC21, NNPDF4.0,
+ and EPPS21,  reveals a significant reduction of PDF uncertainties, in particular
+ for strangeness and the up and down valence PDFs.
  %
- This sensitivity is found to be the largest for  strangeness as well as for
- the up and down valence quark PDFs, and lead to improved theoretical
- predictions for key scattering processes at the HL-LHC.
+ We demonstrate that LHC neutrino data enables improved theoretical
+ predictions for core processes at the HL-LHC, such as Higgs and weak gauge (di)boson production.
 %
- Our analysis demonstrates how exploiting the potential
- of this unique LHC neutrino beam  effectively
-extends the CERN infrastructure with a ``Neutrino-Ion Collider''.
+ Our analysis highlights how exploiting the LHC neutrino beam effectively
+provides CERN with a new ``Neutrino-Ion Collider''.
 
@@
 
-% Introduction and motivation
 \input{sec-introduction}
-
-% Generation of FPF DIS structure functions pseudo-data
 \input{sec-dis-pseudodata}
-
-% REsults 
 \input{sec-results}
-
-% Pheno
 \input{sec-pheno}
-
-% Summary and outlook
 \input{sec-summary}
 
-% Appendices
 \appendix
-
-% Impact of FASERnu
 \input{app-faser.tex}
-
-% Impact in nuclear PDFs
 \input{app-nuclearPDFs.tex}
-
-\clearpage
 

### 2023-09-01 paper/sec-introduction.tex
paper abstract
intro revised

@@
 Proton-proton collisions at energy-frontier hadron colliders
-such as the LHC produce an intense collimated flux of neutrinos.
+such as the LHC produce a high-intensity collimated flux of neutrinos.
 %
-These neutrinos are characterised by the largest energies ever achieved in laboratory experiments and
+These neutrinos are characterised by the largest energies ever achieved in laboratory experiments,
 reaching up to several TeV~\cite{Kling:2021gos}.
@@
 Due to the lack of dedicated instrumentation in the LHC far-forward region,
-until very recently these neutrinos escaped detection.
+until recently these neutrinos avoided detection.
 %
-The reported observation of LHC neutrinos~\cite{FASER:2023zcr,SNDLHC:2023pun} by the
-far-forward  FASER$\nu$~\cite{FASER:2019dxq} and SND@LHC~\cite{SHiP:2020sos,SNDLHC:2022ihg} experiments
+The recent observation of LHC neutrinos~\cite{FASER:2023zcr,SNDLHC:2023pun} by the
+  FASER$\nu$~\cite{FASER:2019dxq} and SND@LHC~\cite{SHiP:2020sos,SNDLHC:2022ihg} far-forward experiments
 demonstrates that this hitherto discarded beam can now be deployed for physics studies.
@@
 Beyond the ongoing Run III, a dedicated suite of upgraded far-forward
-neutrino experiments hosted by a
-Forward Physics Facility (FPF)~\cite{Anchordoqui:2021ghd,Feng:2022inv} has been
-proposed to operate concurrently with the High-Luminosity LHC~\cite{Azzi:2019yne,Cepeda:2019klc}.
+neutrino experiments would be hosted by the proposed
+Forward Physics Facility (FPF)~\cite{Anchordoqui:2021ghd,Feng:2022inv} operating
+concurrently with the High-Luminosity LHC~\cite{Azzi:2019yne,Cepeda:2019klc}.
 %
-Current and future 
-LHC neutrinos experiments enable
-unprecedented scientific opportunities
+Current and future LHC neutrinos experiments enable unprecedented scientific opportunities
 for particle and astroparticle physics both within the Standard Model and beyond it,
@@
 measurements of neutrino structure functions~\cite{Candido:2023utz} in deep-inelastic scattering
-(DIS) provide sensitive information on the parton distribution functions (PDFs)
-of nucleons and nuclei~\cite{Ethier:2020way,Gao:2017yyd,Kovarik:2019xvh}, and in particular
-they probe the quark/antiquark  flavour separation including
-strangeness~\cite{NuTeV:2007uwm,CCFR:1994ikl,Faura:2020oom,NOMAD:2013hbk}.
+(DIS) are sensitive probes of the parton distributions (PDFs)
+of nucleons and nuclei~\cite{Ethier:2020way,Gao:2017yyd,Kovarik:2019xvh},  in particular
+of quark/antiquark  flavour separation and
+strangeness~\cite{NuTeV:2007uwm,CCFR:1994ikl,Faura:2020oom,Alekhin:2014sya}.
 %
-These constraints, arising from charged-current DIS, are fully complementary to those
-provided by neutral-current charged-lepton DIS, given that they reveal independent
-quark flavour combinations.
+Constraints arising from charged-current neutrino scattering provide information on
+different flavour combinations as compared to neutral-current charged-lepton DIS,
+being hence fully complementary.
 %
-Several  experiments have measured neutrino-nucleus
+Several  experiments have measured neutrino
 DIS structure functions over a wide range of energies, and neutrino data
-from the CHORUS~\cite{CHORUS:2005cpn}, NuTeV~\cite{NuTeV:2001dfo},
-CCFR~\cite{Yang:2000ju}, and CDHS~\cite{Berge:1989hr}
+from CHORUS~\cite{CHORUS:2005cpn}, NuTeV~\cite{NuTeV:2001dfo},
+CCFR~\cite{Yang:2000ju}, NOMAD~\cite{NOMAD:2013hbk}, and CDHS~\cite{Berge:1989hr}
 and other experiments is routinely  included in global
@@
 
-As compared to  previous neutrino DIS experiments,
-the unique benefit of LHC neutrinos is their energy spectrum, reaching
-energies up to an order of magnitude higher.
+As compared to  previous experiments,  neutrino
+scattering at the LHC involves energies of up to a factor 10  higher.
 %
-This feature, together with the large statistics (with up to one million muon neutrinos to be
-detected at the FPF~\cite{Kling:2021gos}),  indicates that the LHC  neutrino beam should be
-deployed as a precise probe of hadron structure in order to complement
-and extend available results by a factor 10 both at small-$x$
-and large-$Q^2$~\cite{Feng:2022inv}.
+This key feature, together with the large event rates,
+up to one million muon neutrinos at the FPF~\cite{Kling:2021gos},
+suggests that the LHC  neutrino beam may be utilized
+as a precise probe of hadron structure.
 %
-However, we currently lack  dedicated projections for the kinematic coverage
-and experimental accuracy expected for LHC neutrino structure functions,
-including bin-by-bin statistical and systematic uncertainties and their
-correlations, for the various operating and proposed detectors.
+Initial estimates~\cite{Feng:2022inv} indicate that an extension of the coverage of
+available neutrino data by an order of magnitude both at small-$x$
+and large-$Q^2$ may be possible.
 %
-The lack of these projections
-has so far prevented quantitative studies assessing the impact
-of LHC neutrinos in global fits of proton and nuclear PDFs along the lines
-of those performed for the HL-LHC~\cite{AbdulKhalek:2018rok}, the Electron-Ion Collider (EIC)~\cite{AbdulKhalek:2021gbh,Khalek:2021ulf}, and the
-Large Hadron electron Collider (LHeC)~\cite{AbdulKhalek:2019mps,LHeC:2020van}.
+However, projections for the kinematic coverage
+and experimental accuracy expected at current
+and future LHC neutrino experiments are not available.
+%
+The lack of these projections has prevented quantitative studies assessing the impact
+of LHC neutrinos in global analyses of proton and nuclear PDFs, comparable to
+those performed for the HL-LHC~\cite{AbdulKhalek:2018rok,Azzi:2019yne}, the Electron-Ion Collider (EIC)~\cite{AbdulKhalek:2021gbh,Khalek:2021ulf,AbdulKhalek:2019mzd}, and the
+Large Hadron-electron Collider (LHeC)~\cite{AbdulKhalek:2019mps,LHeC:2020van,LHeCStudyGroup:2012zhm}.
 
-The goal of this work is to bridge this gap and quantify
-the expected impact of  DIS structure functions from the LHC
-neutrino experiments on the proton and nuclear PDFs.
+Here we bridge this gap by quantifying
+the expected impact of  neutrino DIS structure functions at the LHC on proton and nuclear PDFs.
 %
-To this end, we carry out projections for  FASER$\nu$ and SND@LHC based on the full Run III luminosity
-as well as for  three of the proposed experiments to be hosted
-at the FPF~\cite{Anchordoqui:2021ghd,Feng:2022inv}: FLArE, AdvSND, and FASER$\nu$2.
+To this end, we produce simulations for  FASER$\nu$ and SND@LHC at Run III 
+as well as for the proposed FPF experiments~\cite{Anchordoqui:2021ghd,Feng:2022inv,Batell:2021blf,Batell:2021aja}, FLArE, AdvSND, and FASER$\nu$2.
 %
-For each experiment, we determine the expected event yields in bins in $x$, $Q^2$,
-and neutrino energy $E_\nu$,
+For each experiment, we determine the expected event yields in bins of $(x,Q^2,E_\nu)$
+satisfying acceptance and selection cuts,
 generate pseudo-data for  inclusive and charm 
 structure functions, 
-and estimate the main systematic uncertainties.
+and estimate their dominant systematic uncertainties.
 %
-Subsequently, we study their impact on the proton PDFs by means of both the Hessian profiling~\cite{Paukkunen:2014zia,  Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre}
-of the PDF4LHC21 combination~\cite{PDF4LHCWorkingGroup:2022cjn}
-within the  {\sc\small xFitter} framework~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web}
-as well as the direct inclusion in the open-source NNPDF4.0 fitting framework~\cite{NNPDF:2021uiq}.
+Subsequently, we study their impact on the proton and nuclear PDFs by means of both the Hessian profiling~\cite{Paukkunen:2014zia,  Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre}
+of  PDF4LHC21~\cite{PDF4LHCWorkingGroup:2022cjn} (for protons) and EPPS21~\cite{Eskola:2021nhw}
+(for tungsten nuclei)
+within {\sc\small xFitter}~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web},
+as well as with the direct inclusion in the open-source NNPDF4.0 fitting framework~\cite{NNPDF:2021uiq}.
+
+Our analysis reveals that  LHC neutrino structure functions can provide  stringent constraints
+on the light quark and antiquark PDFs, specially on the up and down
+valence quarks and on strangeness, as compared to state-of-the-art global analyses.
 %
-We also assess their impact on the PDFs of tungsten, the target material of FASER$\nu$ and SND@LHC,
-using the EPPS21 global nuclear PDF fit~\cite{Eskola:2021nhw}
-profiled with {\sc\small xFitter}.
+We also  find that accounting for the main systematic uncertainties does not significantly
+degrade the sensitivity achieved by baseline fits considering only statistical errors.
+%
+We quantify the impact in our results of charm-tagged structure functions (large), study the relevance
+of final-state lepton charge identification capabilities (moderate), and compare the constraints
+provided by different experiments (finding that the overall sensitivity is dominated by FASER$\nu$2).
+%
+We also study the implications of the resulting improvement in PDF precision
+on core processes at the HL-LHC, finding a theory error reduction
+of up to a factor two for selected  Higgs and  single and pair gauge boson production
+cross-sections.
 
-Our analysis reveals that  LHC neutrino structure function measurements at the FPF
-would  provide  stringent constraints
-on the quark and antiquark PDFs, specially on the up and down
-valence quarks and on strangeness, as compared to state-of-the-art determinations.
-%
-We find that accounting for systematic uncertainties does not significantly
-degrade the sensitivity achieved by the statistics-only baseline.
-%
-We also quantify the impact of charm-tagged structure functions, study the relevance
-of final-state lepton charge identification, and compare the relative sensitivity
-provided by each of the FPF experiments.
-
-Together with this paper, we release the generated  DIS pseudo-data projections for the various scenarios
-considered, as well as the resulting PDF sets, for which one can foresee
-many other applications beyond hadronic structure studies.
-%
-Our work demonstrates that the availability of far-forward neutrino detection
+These results demonstrate that the availability of far-forward neutrino detection
 at the LHC effectively
@@
 a ``Neutrino-Ion Collider'' at CERN
-without the need of additional accelerator infrastructure or energy consumption.
+without the need of new accelerator infrastructure or additional energy consumption.
 
@@
 Sect.~\ref{sec:dis_pseudodata} discusses the procedure
-adopted to generate projections for neutrino DIS structure functions at the LHC,
-as well as the methodology used
-to include them in proton and nuclear PDF fits.
+adopted to generate projections for neutrino DIS structure functions at the LHC
+and the methodology used to include these in PDF fits.
 %
-The projected impact of these structure functions on proton and nuclear
+The impact of such LHC structure function measurements on proton and nuclear
 PDFs is quantified in Sect.~\ref{sec:protonPDFs}.
+%
+The implications of neutrino DIS at the FPF on precision observables
+at the HL-LHC are studied in Sect.~\ref{sec:pheno}.
 %
@@
 to variations of its inputs.
+
+Together with this paper, we release the generated  DIS pseudo-data projections for the various scenarios
+considered, as well as the resulting PDF sets, for which one can foresee
+many other applications beyond hadronic structure studies.

### 2023-09-01 paper/sec-introduction.tex
Update sec-introduction.tex

@@
 
-Proton-proton collisions at energy-frontier hadron colliders
-such as the LHC produce a high-intensity collimated flux of neutrinos.
+Proton-proton collisions at the LHC produce a high-intensity collimated flux of neutrinos.
 %
@@
 of nucleons and nuclei~\cite{Ethier:2020way,Gao:2017yyd,Kovarik:2019xvh},  in particular
-of quark/antiquark  flavour separation and
+concerning quark/antiquark  flavour separation and
 strangeness~\cite{NuTeV:2007uwm,CCFR:1994ikl,Faura:2020oom,Alekhin:2014sya}.
@@
 %
-However, projections for the kinematic coverage
+However, quantitative projections for the kinematic coverage
 and experimental accuracy expected at current
@@
 %
-The lack of these projections has prevented quantitative studies assessing the impact
-of LHC neutrinos in global analyses of proton and nuclear PDFs, comparable to
+The lack of these projections has prevented detailed studies assessing the impact
+of LHC neutrino data in global analyses of proton and nuclear PDFs, comparable to
 those performed for the HL-LHC~\cite{AbdulKhalek:2018rok,Azzi:2019yne}, the Electron-Ion Collider (EIC)~\cite{AbdulKhalek:2021gbh,Khalek:2021ulf,AbdulKhalek:2019mzd}, and the
@@
 We quantify the impact in our results of charm-tagged structure functions (large), study the relevance
-of final-state lepton charge identification capabilities (moderate), and compare the constraints
+of final-state lepton-charge identification capabilities (moderate), and compare the constraints
 provided by different experiments (finding that the overall sensitivity is dominated by FASER$\nu$2).
@@
 on core processes at the HL-LHC, finding a theory error reduction
-of up to a factor two for selected  Higgs and  single and pair gauge boson production
+of up to a factor two for selected  Higgs and gauge boson production
 cross-sections.
@@
 at the LHC effectively
-extends CERN with a charged-current counterpart of the EIC,
-with a similar kinematic reach and complementing
-the information provided by its neutral-current scattering data.
+provides CERN with a charged-current counterpart of the EIC,
+with similar kinematic reach and complementary sensitivity on hadronic
+structure.
 %
@@
 adopted to generate projections for neutrino DIS structure functions at the LHC
-and the methodology used to include these in PDF fits.
+and the methodology used to include these into PDF fits.
 %
 The impact of such LHC structure function measurements on proton and nuclear
-PDFs is quantified in Sect.~\ref{sec:protonPDFs}.
+PDFs is quantified in Sect.~\ref{sec:protonPDFs}, with the
+associated implications for precision phenomenology
+at the HL-LHC assessed in Sect.~\ref{sec:pheno}.
 %
-The implications of neutrino DIS at the FPF on precision observables
-at the HL-LHC are studied in Sect.~\ref{sec:pheno}.
-%
-We summarise in Sect.~\ref{sec:summary} and also consider some possible
+We summarise in Sect.~\ref{sec:summary}, where we also consider possible
 directions for follow-up research.
 %
-Additional impact results are collected in two appendices:
-App.~\ref{app:fasernu_runIII_impact} studies the possible PDF impact
-of FASER$\nu$ Run III measurements, and App.~\ref{app:nPDF_impact_appendix}
-quantifies the stability of the nuclear PDF projections with respect
-to variations of its inputs.
+Additional results are collected in two appendices:
+App.~\ref{app:fasernu_runIII_impact} studies the constraints provided by
+FASER$\nu$ measurements at Run III, and App.~\ref{app:nPDF_impact_appendix}
+quantifies the stability of the nPDF impact projections with respect
+to input variations.
 
-Together with this paper, we release the generated  DIS pseudo-data projections for the various scenarios
-considered, as well as the resulting PDF sets, for which one can foresee
-many other applications beyond hadronic structure studies.
+We note that, together with this paper,
+we release the generated  DIS structure functions for the LHC
+neutrino experiments as well as the resulting PDF sets, which may be helpful
+to inform related studies of high-energy
+neutrino production and scattering at the LHC.

### 2023-09-01 paper/sec-dis-pseudodata.tex
working on sect 2

@@
 
-Here we describe the procedure adopted in order 
+We begin by describing the procedure adopted in order 
 to generate projections for the kinematic coverage
@@
 First, we summarise the theoretical description of differential
-neutrino scattering in terms of DIS structure functions and highlight
-their PDF sensitivity.
-%
-Second, we present an  overview of the operative and proposed
+neutrino scattering in terms of DIS structure functions.
+%
+Then, we present an  overview of the operative and proposed
 LHC far-forward neutrino detectors that
@@
 Finally, we discuss the procedure adopted to generate pseudo-data
-for LHC neutrino deep-inelastic scattering structure functions
-and to quantify their impact
+for LHC neutrino structure functions
+and quantify their impact
  into proton and nuclear PDF determinations.
@@
 see~\cite{Candido:2023utz} and references therein,
-is expressed in terms of three
+can be expressed in terms of three
 independent structure functions $F_2^{\nu A}$, $xF_3^{\nu A}$
@@
 \ee
-where $s=2m_N E_\nu$ being the neutrino-nucleon center of mass energy squared, $m_N$ is the nucleon mass,
-$E_\nu$ is the incoming neutrino energy,
+with $s=2m_N E_\nu$ being the neutrino-nucleon center of mass energy squared, $m_N$ the nucleon mass,
+$E_\nu$ the incoming neutrino energy,
 and the inelasticity is $y=Q^2/(2x m_n E_{\nu})$.
 %
-In the case of tau-neutrino scattering, tau lepton mass effects
-cannot be neglected and Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) receive additional contributions
+In the case of tau-neutrino scattering, tau-lepton mass effects
+may be relevant and Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) receive additional contributions
 from the $F_4$ and $F_5$ structure functions.
 %
-We neglect these effects since we focus on electron and muon neutrino scattering here.
-
-Structure functions depend only on $x$ and $Q^2$, while the differential
+We neglect these effects, since here we focus on electron and muon neutrino scattering.
+
+Structure functions depend on both $x$ and $Q^2$, while the differential
 cross-section depends also on the neutrino energy $E_\nu$, or alternatively
@@
 %
-Further, structure functions $F^{\nu A}_i(x,Q^2)$ and $F^{\bar{\nu} A}_i(x,Q^2)$ depend on the nuclear target $A$ entering
-for the neutrino scattering through the nuclear modifications of the free-nucleon PDFs.
+Further, structure functions $F^{\nu A}_i(x,Q^2)$ and $F^{\bar{\nu} A}_i(x,Q^2)$ depend on the nuclear target $A$ entering neutrino scattering through the
+nuclear modifications of the free-nucleon PDFs.
 %
@@
 %
-We discuss below the theoretical
-settings adopted here~\cite{Candido:2022tld,yadism,Candido:2023utz,Carrazza:2020gss} to
-evaluate predictions for
-neutrino differential cross-sections and DIS structure functions,
-Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}),~(\ref{eq:antineutrino_DIS_xsec_FL}), and~(\ref{eq:sfs_pqcd}),
-in the kinematics covered by LHC neutrinos.
+Here the theory pipeline adopted
+to evaluate neutrino structure functions using Eq.~(\ref{eq:sfs_pqcd}) is provided by 
+{\sc\small EKO}~\cite{Candido:2022tld}
+and {\sc\small YADISM}~\cite{yadism,Candido:2023utz}
+interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss}
+for the generation of fast interpolation grids.
 
@@
  %
- To illustrate this sensitivity, consider a leading order  calculation
+ To illustrate this feature, consider a leading order  calculation
  for a proton target with $n_f=4$ active quark flavours,
-a diagonal CKM matrix and no heavy quark mass effects.
+a diagonal CKM matrix, and no heavy quark mass effects.
  %
@@
 
- It is illustrative to compare the PDF dependence of neutrino structure functions
+ It is also illustrative to compare the PDF dependence of neutrino structure functions
  at LO with that of their counterparts for neutral-current
@@
  the $Z$-boson mass, $Q^2 \ll m_Z^2$, the corresponding
- partonic decomposition is
- the 
- \bea
+decomposition is \bea
  F_2^{\ell p}(x,Q^2) &=& x\lp \frac{4}{9}\lc f_{u^+} + f_{c^+}\rc
@@
  \eea
- with $xF_3$ being negligible in this region below the $Z$-pole.
+ with $xF_3$ being negligible in this region.
  %
@@
   flavour separation in the nucleon
- would be provided by combining neutrino DIS at
+ would be provided by combining neutrino DIS from the
  LHC far-forward experiments with measurements on charged-lepton
@@
 
- \subsection{LHC far-forward neutrino detectors}
+ \subsection{LHC far-forward neutrino experiments}
  \label{sec:neutrinoDetectors}
@@
  far-forward detectors considered, in particular concerning
- their acceptance and (expected) performance.
- %
- We focus on  muon neutrino scattering, which benefits from the highest rates and is less
- affected by theoretical uncertainties in the production mechanism.
+ their acceptance and expected performance.
+ %
+ We focus on  muon-neutrino scattering, which benefits from the highest rates and is less
+ affected by theoretical uncertainties in the production mechanism, but
+ provide also predictions for electron-neutrino scattering.
 
@@
  %
- Most neutrino detectors can only access $E_h$, given that $W^2$ requires
- fully reconstructing this final state.
+ Most neutrino detectors can only access $E_h$, given that measuring the invariant mass $W^2$ requires
+ fully reconstructing the final state.
  %
@@
  \eea
- These relations also indicate how systematic uncertainties affecting the measurement
+ These relations also reflect how systematic uncertainties affecting the measurement
  of $\lp E_\ell,\theta_\ell, E_h \rp$ translate into uncertainties in the
@@
 
+ \paragraph{Detector overview.}
+ %
  Table~\ref{tab:FPF_experiments} summarises,
@@
   %
-  We consider separately acceptance and performance for electron and muon
-  neutrinos.
-  %
-  For these projections we assume that FASER$\nu$ and SND@LHC acquire data
+  We consider separately acceptance and performance for electron-neutrinos and
+  muon-neutrinos.
+  %
+  In these projections we assume that FASER$\nu$ and SND@LHC acquire data
   for Run III ($\mathcal{L}=150$ fb$^{-1}$), while FASER$\nu$2,
@@
   %
-  In the following we provide more details about the information collected in
+  In the following, we provide details about the information collected in
   Table~\ref{tab:FPF_experiments}.
@@
 %
-The FASER apparatus is immersed in a magnetic field  providing charged lepton
+The FASER apparatus is immersed in a magnetic field,  providing charged-lepton
 identification thanks to two 1 m-long dipole magnets with $B=0.57$ T
@@
 %
-A proposed 20-ton neutrino experiment located on the LOS
+This is proposed 20-ton neutrino experiment located on the LOS
 of the LHC neutrino beam to be installed in the FPF cavern.
@@
 as its predecessor, the same performance in terms of reconstruction
-of final-state kinematics is assumed.
+of final-state kinematics can be assumed.
 
@@
  at the FPF with a coverage in neutrino pseudorapidity of $7.2 \le \eta_\nu \le 8.4$
- (hence off-LOS, same as SND@LHC) and a near detector installed somewhere else in LHC
+ (hence off-LOS, same as SND@LHC) and a near detector installed somewhere else in the LHC
  complex and covering the range $4 \le \eta_\nu \le 5$.
  %
- In the following we focus on the AdvSND-far detector.
+Here we focus on the former.
  %
@@
  %
- Building upon recent progress in liquid noble gas neutrino detectors over the last decade (ICARUS, MicroBooNE, SBND, ProtoDUNE, DUNE), this experiment
+ Building upon recent progress in liquid noble gas neutrino detectors over the last decade (ICARUS, MicroBooNE, SBND, DUNE), this experiment
  would rely on a modularized liquid argon (LAr) time projection detector.
@@
  The use of LAr as a target is beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimeter spatial resolution in all dimensions.
- %
-% FLArE is suitable to identify high-energy neutrinos ($E_\nu \gsim 100$ GeV)  from all three generations while containing the events as required for kinematic reconstruction.
  %
@@
  contained in the  FLArE detector,
-for the projections presented in this work
+for our projections
 we assume that outgoing high-energy
@@
 
- With an expected fiducial (active) mass of 10 tons (30 tons) and length 7 m, FLArE will
+ With an expected fiducial (active) mass of 10 tons (30 tons) and a length of 7 m, FLArE will
  detect final-state electrons with energies $E_{e}\lsim 2~\rm{TeV}$ and
@@
  %
- We consider projections both for 10 ton (FLArE-10) and 100 ton (FLArE-100) fiducial volume detectors.
+ Here we present  projections for this baseline design of the experiment, FLArE10,
+ as well as for a potential larger variant based on a fiducial mass of 100 ton, which
+ is known as FLArE100.
  %
@@
  In terms of performance, the targets
- are $\delta E_\mu \sim$5\% of electron energy resolution,
+ are $\delta E_\mu \sim5\%$ of electron energy resolution,
  $\delta \theta_e \sim 15$ mrad of electron angular  resolution,
@@
  %
- Since the muon energy from a charged-current interaction would be measured by FASER2, the
- performance parameters for $E_\mu$ are  taken
- to be the same as those of FASER$\nu$2 as indicated
- in Table~\ref{tab:FPF_experiments}.
+ Since the muon energy from a charged-current interaction would be measured by FASER$\nu$2, the
+ performance parameters for $E_\mu$ are taken to be the same.
 
@@
 are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$~\cite{Kling:2021gos}.
+%
 The neutrino flux takes into account both the prompt component associated with neutrinos from charmed hadron decay as well as a displaced component from light hadron decays.
-The prompt component was simulated at NLO using \textsc{POWHEG}~\cite{Nason:2004r,Frixione:2007vwx,Alioli:2010xd} and \textsc{Pythia}~\cite{Sjostrand:2014zea, Bierlich:2022pfr} for the parton shower and hadronization, and the displaced component was simulated with \textsc{Epos-Lhc}~\cite{Pierog:2013ria}.
-In addition to the updated charmed hadron production, the neutrino flux from Ref.~\cite{Kling:2021gos} was also updated for $\sqrt{s} = 13.6~{\rm TeV}$.
+%
+The prompt component was simulated at NLO using {\sc\small POWHEG}~\cite{Nason:2004r,Frixione:2007vwx,Alioli:2010xd} and {\sc\small Pythia8}~\cite{Sjostrand:2014zea, Bierlich:2022pfr} for the parton shower and hadronization, and the displaced component was simulated with {\sc\small EPOS-LHC}~\cite{Pierog:2013ria}.
+%
+In addition to the updated charmed hadron production,
+the neutrino flux from Ref.~\cite{Kling:2021gos} was also updated for $\sqrt{s} = 13.6~{\rm TeV}$.
 
@@
 we extend the calculation delineated in Sec.~(\ref{sec:pseudo-data_generation}) as follows.
-%{\color{blue} [MF: I don't think this faser example is necessary]}
-%Let us consider for illustrative purposes the FASER${\nu}$2 detector.
-%
-%From Table~\ref{tab:FPF_experiments} we know that its
-%acceptance parameters and reconstruction performance are specified by:
-%\bea
-%E_\ell \ge 100~{\rm GeV} \, , \quad \theta_\ell \le \tan^{-1}(0.025)\, , \qquad\\
-%\delta E_\ell \sim 30\% \, 
- %\quad \delta E_h \sim 30\% \, ,
- %\quad \delta\theta_\ell \sim 0.06~{\rm mrad} \, . 
-%\label{eq:fasernu2systematic_errors}
-%\eea
-%To translate these uncertainties in $\delta E_\ell$, $\delta E_h $,
+%
 To translate uncertainties in $\delta E_\ell$, $\delta E_h $
@@
 We then take each event in $\mathcal{D}_0$ and smear it with Gaussian distributions whose variances are given by Table~\ref{tab:FPF_experiments} to produce a set of new samples $\{\mathcal{D}_k\}$.
+%
 The smeared events are subjected to the same DIS cuts from Eq.~(\ref{eq:DISconditions}) and acceptances from Table~\ref{tab:FPF_experiments}.
+%
 The bin assignment of the events in the smeared samples $\mathcal{D}_k$ will in general be different from those of the baseline sample $\mathcal{D}_0$.
@@
     We consider the systematic errors
-    associated to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$
+    associated to the charged-lepton energy $E_\ell$ and scattering angle $\theta_\ell$
     and to the hadronic energy $E_h$.
@@
 On the other hand, for the FLArE-10(0) experiment, uncertainties associated with the scattering angle $\theta_\ell$ dominate at $\sim 40\%$ ranging from a few percent to ${\cal O}(1)$.
-Whereas the uncertainties associated with final state energy resconstruction are $\sim 10\%$ and range from $\lesssim 1\%$ to $\sim 80\%$.
+Whereas the uncertainties associated with final state energy reconstruction are $\sim 10\%$ and range from $\lesssim 1\%$ to $\sim 80\%$.
 %

### 2023-09-01 paper/tables/detectors.tex
working on sect 2

@@
 \multirow{3}{*}{FLArE ({\bf *})}  & \multirow{3}{*}{$\eta_\nu \ge 7.5$} & \multirow{2}{*}{LAr}  & \multirow{3}{*}{muons}  &  $E_\ell,E_h \gsim 2$ GeV, $E_e \lsim 2$ TeV    &    $\delta E_e \sim 5\% $,  $\delta E_\mu \sim 30\% $ \\
-&   &  \multirow{2}{*}{(10 ton)}   &   & $\theta_\mu \lsim 0.025$, $\theta_e \lsim 0.5$ &    $\delta \theta_\ell \sim 15 $ mrad\\
+&   &  \multirow{2}{*}{(10,~100~ton)}   &   & $\theta_\mu \lsim 0.025$, $\theta_e \lsim 0.5$ &    $\delta \theta_\ell \sim 15 $ mrad\\
  &   &     &  & reco $E_h$  &    $\delta E_h \sim 30\% $   \\

### 2023-09-01 paper/sec-dis-pseudodata.tex
sec 2

@@
 described in Table~\ref{tab:FPF_experiments}, we generate
-projections for the expected precision of DIS structure function
+projections for the expected DIS structure function
 measurements as follows.
@@
 We want to evaluate the number of reconstructed charged-current neutrino interaction
-events taking place in the fiducial volume of the detector in bins of Bjorken-$x$,
+events taking place in the fiducial volume of the detector when divided into bins of Bjorken-$x$,
 momentum transfer $Q^2$, and neutrino energy $E_\nu$, that is,
@@
 %
-When choosing the binning of the measurement, we simply choose log-spaced bins in $x$ and $Q^2$.
-
-In our calculation we assume the central values of the neutrino
-fluxes provided by~\cite{Kling:2021gos} and used
-for the FPF simulations in~\cite{Feng:2022inv}.
+For simplicity, in this initial study we consider a single bin in energy
+and choose log-spaced bins in $x$ and $Q^2$; the eventual optimisation
+of the binning selection is left for future work.
+
+In this calculation, we adopt the neutrino fluxes evaluated in~\cite{Kling:2021gos} and used
+for the FPF simulations presented in~\cite{Feng:2022inv}.
 %
@@
 with $n_T$ is the nucleon density of the target detector material, $L_T$ its
-length and ${\cal A}(x,Q^2,E_{\nu})$ is an acceptance factor which takes the form of a
+length, and ${\cal A}(x,Q^2,E_{\nu})$ is an global acceptance factor which takes the form of a
 step function and accounts for the experimental acceptances
@@
 listed in Table~\ref{tab:FPF_experiments}.
-%
-The incoming neutrino fluxes, which account for the geometry
-and neutrino pseudo-rapidity $\eta_\nu$ coverage of the considered detector,
-are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$~\cite{Kling:2021gos}.
-%
-The neutrino flux takes into account both the prompt component associated with neutrinos from charmed hadron decay as well as a displaced component from light hadron decays.
-%
-The prompt component was simulated at NLO using {\sc\small POWHEG}~\cite{Nason:2004r,Frixione:2007vwx,Alioli:2010xd} and {\sc\small Pythia8}~\cite{Sjostrand:2014zea, Bierlich:2022pfr} for the parton shower and hadronization, and the displaced component was simulated with {\sc\small EPOS-LHC}~\cite{Pierog:2013ria}.
-%
-In addition to the updated charmed hadron production,
-the neutrino flux from Ref.~\cite{Kling:2021gos} was also updated for $\sqrt{s} = 13.6~{\rm TeV}$.
+
+The incoming neutrino fluxes of~\cite{Kling:2021gos} account for the geometry
+and neutrino pseudo-rapidity $\eta_\nu$ coverage of the considered detector and
+are encoded in Eq.~(\ref{eq:event_yields_calculation}) as $dN_{\nu}(E_\nu)/dE_{\nu}$.
+%
+This neutrino flux takes into account both the prompt component associated with neutrinos from charmed hadron decay as well as a displaced component from light hadron decays.
+%
+The prompt component used in this work was simulated at NLO using {\sc\small POWHEG}~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd} matched to {\sc\small Pythia8}~\cite{Sjostrand:2014zea, Bierlich:2022pfr} for the parton shower and hadronization, and the displaced component was simulated with {\sc\small EPOS-LHC}~\cite{Pierog:2013ria}.
+%
+In comparison with~\cite{Kling:2021gos}, in addition to the updated charmed hadron production,
+the neutrino flux has been updated to $\sqrt{s} = 13.6~{\rm TeV}$.
 
@@
 
- Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the five detectors
+ Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the six
+ detectors
 considered, separated into electron neutrinos and antineutrinos
@@
   %
-These event yields are computed from Eq.~(\ref{eq:event_yields_calculation}) with the only
+These event yields are computed from Eq.~(\ref{eq:event_yields_calculation}) with the
 requirement that the momentum transfer and the final-state invariant mass are restricted
@@
 %
-In the case of the FLArE detector, we display results for two proposed options with fiducual masses of 10 and 100 tons respectively.
-%
-We note that, as opposed to the number of interacting neutrinos
+In the case of the FLArE detector, we display results for two proposed options with fiducial
+masses of 10 and 100 tons.
+%
+As opposed to the number of interacting neutrinos presented
 in~\cite{Feng:2022inv}, we now account for the
-detector acceptance listed in  Table~\ref{tab:FPF_experiments}.
+detector acceptances listed in  Table~\ref{tab:FPF_experiments}.
 
@@
 %
-Second, the muon neutrino scattering yield dominates over electron neutrino scattering by a factor
-between 2 and 3, though this ratio is affected by the large theory uncertainties
+Second, the muon-neutrino scattering yield dominates over electron neutrino scattering by a factor
+between 2 and 3, though the precise value of this ratio is affected by the large theory uncertainties
 affecting forward electron neutrino production.
@@
 Third, charm production  represents around 15\% of the inclusive
-yields, with both FASER$\nu$2 and FLArE-100 resulting in around
+yields, with both FASER$\nu$2 and FLArE100 resulting in around
 40k recorded charm-production events.
 %
-Note that this result assumes charm ID is possible, and if only dimuon events can be recorded
+Note that this result assumes $D$-meson tagging capabilities,
+and if only dimuon events can be recorded
 the yields would be reduced by a factor of 10.
 %
-Fourth, FASER$\nu$2 and FLArE-100 lead to the largest absolute
-yields of the FPF experiments, with around 260k and 340k (non-tau) neutrino DIS events respectively, with 28k and 57k
-events expected instead for AdvSND-far and FLArE-10.
+Fourth, FASER$\nu$2 and FLArE100 lead to the largest absolute
+yields of the FPF experiments, with a total of around 370k and 550k (non-tau) neutrino DIS events respectively, with 37k and 90k
+events expected instead for AdvSND-far and for FLArE10.
 
@@
  for muon neutrinos detected at the
- FASER$\nu$ (Run III) and the AdvSND, FASER$\nu$2, and FLArE-100  (FPF) experiments,
+ FASER$\nu$ (Run III) and the AdvSND, FASER$\nu$2, and FLArE100  (FPF) experiments,
  restricted
@@
  leading to typical statistical uncertainties at the 1\% level or smaller,
- while for FASER$\nu$ the statistical uncertainties are much larger due
+ while for FASER$\nu$ the statistical uncertainties are larger due
  to the reduced event rates.
@@
     	\small The event yields per bin $N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}), for 
-    	muon neutrino scattering at the FASER$\nu$, FASER$\nu$2, AdvSND, and FLArE-100  experiments.
+    	muon-neutrino scattering at the FASER$\nu$, FASER$\nu$2, AdvSND, and FLArE100  experiments.
         %
@@
 
-Fig.~\ref{fig:fasernu2_muon} indicates
-how the kinematic coverage of the FPF far-forward experiments reaches
-$x_{\rm min}\sim 3\times 10^{-3}$ at small-$x$ and $Q^2_{\rm max}\sim 10^4$ GeV$^2$
+From Fig.~\ref{fig:fasernu2_muon} one observes
+how the kinematic coverage of the FPF far-forward experiments reaches down to
+$x_{\rm min}\sim 3\times 10^{-3}$ at small-$x$ and up to $Q^2_{\rm max}\sim 10^4$ GeV$^2$
 at large-$Q^2$, representing an extension
 of around one order of magnitude in both directions as compared to available
-DIS neutrino data on nuclear targets.
-%
+DIS neutrino data.
+%
+To illustrate this,
 Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF} compares
@@
 %
-The LHC neutrino experiments cover the region $x\gsim 3\times 10^{-3}$, relevant
-for precision electroweak measurements at the LHC, such as the $W$-boson
-mass, and for new physics measurements sensitive to the large-$x$ quarks
-and antiquarks in the proton.
-%
-FASER$\nu$2 and FLArE-100 mostly overlap with the EIC coverage, providing a complementary handle
+The LHC neutrino experiments cover an $x$ region relevant
+at hadron colliders for Higgs boson analyses,
+precision electroweak measurements  such as the $W$-boson
+mass~\cite{Amoroso:2023pey}, and new physics measurements sensitive
+to the large-$x$ PDFs~\cite{Ball:2022qtp}.
+%
+FASER$\nu$2 and FLArE100 mostly overlap with the EIC coverage, providing a complementary handle
 on the quark flavour decomposition in protons and heavy nuclei as compared
-to that provided by the EIC measurements.
+to the one provided by the EIC measurements.
 
@@
     \centering
-    \includegraphics[width = 0.75\textwidth]{plots/KIN_DIS_FPF.pdf}
+    \includegraphics[width = 0.80\textwidth]{plots/KIN_DIS_FPF.pdf}
     \caption{
       The kinematic coverage in the $(x,Q^2)$ plane of muon-neutrino scattering
-	    at the FASER$\nu$, FASER$\nu$2, FLArE-100, and AdvSND experiments, see also Fig.~\ref{fig:fasernu2_muon},
+      at the FASER$\nu$, FASER$\nu$2, FLArE10(100), and AdvSND experiments, see also Fig.~\ref{fig:fasernu2_muon},
       compared to that of electron-ion collisions at the EIC for the highest center-of-mass 
-	    energies $\sqrt{s}$ planned as well as to the coverage of existing nuclear neutral- and
-	    charged-current DIS measurements.
+      energies $\sqrt{s}$ planned as well as to the coverage of existing neutrino
+      (fixed-target) DIS measurements.
       %
       Bins with less than 100 events have been excluded fo all the pseudodata except for FASER$\nu$ where we retain
-      	bins with $\ge 10$ events.
+      bins with at least 10 events.
     }
@@
 %
-Since we discard bins with less than 100 events for HL-LHC experiments (FASER$\nu$2, FLArE100, AdvSND) and
-10 events for Run III experiments (FASER$\nu$, SND), the fractional statistical uncertainty
+Since we discard bins with less than 100 events for FPF experiments (FASER$\nu$2, FLArE, AdvSND) and
+10 events for FASER$\nu$ and SND@LHC, the fractional statistical uncertainty
 ranges between $\lsim 1\%$ and $\sim 30\%$, depending on the values of
@@
 
-For each independent source of experimental systematic uncertainty, we hence
+For each independent source of experimental systematic uncertainty, we 
 quantify its impact at the event yield level.
 %
-In order to determine these bin-by-bin systematic errors,
+In order to determine these systematic errors,
 we extend the calculation delineated in Sec.~(\ref{sec:pseudo-data_generation}) as follows.
@@
 %
-On the other hand, for the FLArE-10(0) experiment, uncertainties associated with the scattering angle $\theta_\ell$ dominate at $\sim 40\%$ ranging from a few percent to ${\cal O}(1)$.
+On the other hand, for the FLArE10(0) experiment, uncertainties associated with the scattering angle $\theta_\ell$ dominate at $\sim 40\%$ ranging from a few percent to ${\cal O}(1)$.
 Whereas the uncertainties associated with final state energy reconstruction are $\sim 10\%$ and range from $\lesssim 1\%$ to $\sim 80\%$.

### 2023-09-01 paper/tables/integrated_yields.tex
updated table for final xsecs and fluxes
Minor corrections
sec 2

@@
   \renewcommand{\arraystretch}{1.70}
-\begin{tabularx}{\textwidth}{X|c|c|c|c|c|c}
+\begin{tabularx}{\textwidth}{X||c|c|c||c|c|c}
 \toprule
@@
 \midrule
-FASER$\nu$  & 340 (56)    & 190 (36)  & 530 (92)  &  1100 (180)  &  440 (83)  &  1500 (260) \\
-SND@LHC  &  140 (15)  & 60 (9)    & 200 (24)   &  390 (54) & 150 (22)   &  550  (76)\\
+FASER$\nu$  & 0.2k (31)    & 110 (19)  & 0.3k (50)  &  0.6k (98)  &  0.3k (45)  &  0.9k (140) \\
+SND@LHC  &  88 (11)  & 38 (5.4)    & 130 (16)   &  0.3k (54) & 96 (22)   &  0.4k  (76)\\
 \midrule
 \midrule
-FASER$\nu$2  & 84k (11k)   & 42k (6.6k)   & 130k (19k)  & 274k (40k)  & 100k (17k)    & 370k (57k)   \\
-AdvSND-far  &  8.6k (0)  & 3500 (0)   & 13k (0.5k)  & 30k (2.7k)  & 12k (0.8k)   & 43k (4.5k)   \\
-FLArE-10 & 33k (3.3k) & 15k (1.4k)   &  50k (5.4k) &  53k (6.5k)&   28k (2.4k) &   81k (11k) \\
-FLArE-100 &   110k (13k)         &    58k (6.9k)         &       170k (21k)       &   302k (43k)      &  120k (15k)    &  420k (59k)  \\
+FASER$\nu$2  & 58k (8.3k)   & 28k (5.0k)   & 86k (13.3k)  & 190k (27k)  & 67k (12k)    & 260k (39k)   \\
+AdvSND-far  &  5.9k (0.7k)  & 2.8k (0.4k)   & 8.7k (1.1k)  & 20k (2.4k)  & 8k (1.1k)   & 28k (3.5k)   \\
+FLArE10 & 22k (2.7k) & 10k (1.5k)   &  32k (4.2k) &  38k (5.2k)&   19k (2.5k) &   57k (7.7k) \\
+FLArE100 &   140k (18k)         &    66k (9.5k)         &       210k (27k)       &   220k (30k)      &  120k (15k)    &  340k (45k)  \\
   \bottomrule
@@
 \vspace{0.2cm}
-\caption{\small Integrated event yields for the five detectors considered,
+\caption{\small Integrated event yields for the six detectors considered,
   separated into electron neutrinos and antineutrinos,

### 2023-09-01 paper/sec-dis-pseudodata.tex
sect 3

@@
 
-For each independent source of experimental systematic uncertainty, we 
-quantify its impact at the event yield level.
-%
-In order to determine these systematic errors,
-we extend the calculation delineated in Sec.~(\ref{sec:pseudo-data_generation}) as follows.
-%
-To translate uncertainties in $\delta E_\ell$, $\delta E_h $
-and $\delta\theta_\ell$ into systematic errors associated to the event yields, 
+For each independent source of systematic uncertainty, which in this analysis
+consists of  $\delta E_\ell$, $\delta E_h $,
+and $\delta\theta_\ell$, we 
+quantify its impact at the event yield level
 \be
@@
 \ee
-we first generate a Monte Carlo set of events, denoted by $\mathcal{D}_0$,
+by extending the calculation delineated in Sect.~(\ref{sec:pseudo-data_generation}).
+%
+First, we generate a Monte Carlo set of events, denoted by $\mathcal{D}_0$,
 composed by $N_{\rm mc} \approx 10^7$ samples and determine the assignment of each event
@@
 By comparing $\mathcal{D}_0$ with the number of events as calculated by Eq.~(\ref{eq:event_yields_calculation}), 
-we can normalize the sampled $\mathcal{D}_0$ distribution with a factor $\hat{n}$ to reproduce the expected yield.
-
+we can normalize the sampled $\mathcal{D}_0$ distribution with a factor $\hat{f}$ to reproduce the expected yield.
+%
 We then take each event in $\mathcal{D}_0$ and smear it with Gaussian distributions whose variances are given by Table~\ref{tab:FPF_experiments} to produce a set of new samples $\{\mathcal{D}_k\}$.
@@
 
-%
-We take the uncertainty associated
+We define the uncertainty associated
 to a given systematic source, say $\delta E_\ell$,
-to be the mean of the absolute difference between the number of events in this bin for the smeared samples $\{\mathcal{D}_k\}$ normalized by $\hat{n}$, and the central prediction for the number of events
-$ N_{\rm ev}^{(i)}$ as calculated from Eq.~(\ref{eq:event_yields_calculation}):
-\be
-\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} =\la \Big|  \hat{n}\times{N}^{(i)}_{E_\ell-{\rm smeared}} -N_{\rm ev}^{(i)}\Big|\ra \, .
-\ee
-
-Individual sources of systematic errors are treated as uncorrelated among them and hence
+to be the mean of the absolute difference between the number of events in this bin for the smeared samples $\{\mathcal{D}_k\}$ normalized to $\hat{f}$  and the central prediction for the number of events
+$N_{\rm ev}^{(i)}$ as calculated from Eq.~(\ref{eq:event_yields_calculation}):
+\be
+\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} =\la \Big|  \hat{f} {N}^{(i)}_{E_\ell-{\rm smeared}} -N_{\rm ev}^{(i)}\Big|\ra \, .
+\ee
+Individual sources of systematic errors are treated as uncorrelated among them, and hence
 by producing samples where only one source of error is varied at a time
@@
 
-For the experiments which use a Tungsten target, the systematic uncertainties associated to the final state energies $E_\ell$, $E_h$ are comparable and are typically $\sim 10\%$ and range from $1\%$ to  ${\cal O}(1)$ across bins.
-The uncertainties associated with $\theta_\ell$ are typically at or well below $1\%$ for these experiments, which can be attributed to the high spatial resolution.
-%
-On the other hand, for the FLArE10(0) experiment, uncertainties associated with the scattering angle $\theta_\ell$ dominate at $\sim 40\%$ ranging from a few percent to ${\cal O}(1)$.
-Whereas the uncertainties associated with final state energy reconstruction are $\sim 10\%$ and range from $\lesssim 1\%$ to $\sim 80\%$.
+In the case of FASER$\nu$2, the systematic uncertainties associated to the final state energies $E_\ell$ and $E_h$ are comparable and are typically at the $10\%$ level, ranging
+from $1\%$ to  ${\cal O}(1)$ across bins. The uncertainties associated with $\theta_\ell$ are typically at or well below $1\%$ for these experiments, which can be attributed to their good spatial
+resolution. 
+%
+On the other hand, for the FLArE10(100) experiment, uncertainties associated with the scattering angle $\theta_\ell$ dominate, being at the $ 40\%$ level and ranging from a few percent to ${\cal O}(1)$,
+whereas the uncertainties associated with final-state energy reconstruction
+are smaller, around the $10\%$ level, and range from $\lesssim 1\%$ to up to around $80\%$
+depending on the bin.
 %
@@
  uncertainty dominates over the statistical uncertainties, with the possible exception
- of the small-$x$ region where statistical and systematic errors are comparable.
-
-The end result of the procedure is an estimate of statistical and systematic uncertainties
+ of the small-$x$ region where statistical and systematic errors are of comparable size.
+
+The end result of the procedure is an estimate of the statistical and systematic uncertainties
 for each bin of the measurement, from which an experimental covariance matrix can be constructed as
@@
  is fully correlated among all the bins in $(x,Q^2)$ is unlikely to be accurate.
- %
- For this reason, following the HL-LHC projection strategy of~\cite{AbdulKhalek:2018rok}
+
+ For this reason, following the HL-LHC projection strategy of~\cite{AbdulKhalek:2018rok},
  here we neglect bin-by-bin correlations
@@
 %
-A value of $f_{\rm corr}=0.5$, obtained from the inspection of available measurements
+A value of $f_{\rm corr} \sim 0.5$, obtained from the inspection of available measurements
  for which the full information
@@
 %
-In Sect.~\ref{sec:protonPDFs} we present results for different scenarios
-for the systematic uncertainty reduction factor $f_{\rm red}$ with respect to the baseline settings.
+ In Sect.~\ref{sec:protonPDFs} we present results for the conservative scenario with
+ $f_{\rm red}=1$, but it is
+ straightforward to revisit the projections for a more optimistic
+ detector performance with $f_{\rm red}< 1$.
 
@@
 %
-PDF evolution and DIS structure functions account for NLO QCD corrections
-and target mass effects.
+DIS structure functions are evaluated at NLO in the QCD expansion
+and account both for heavy quark and target mass effects.
 %
@@
 %
-Charm structure functions are evaluated in the FONLL general-mass variable-flavour-number
+In particular,
+charm structure functions are evaluated in the FONLL general-mass variable-flavour-number
 scheme~\cite{Forte:2010ta,Ball:2011mu,Faura:2020oom} at $\mathcal{O}\lp \alpha_s\rp$
@@
 %
-For the proton PDF fits we assume a free isoscalar target $N$, while
+For the proton PDF fits, we assume a free isoscalar target $N$, while
 for the nuclear PDF one we allow for deviations from isoscalarity relevant
@@
 
-The PDF set and other theory settings, such as the perturbative
+For ensure consistency, the PDF set and other theory settings, such as the perturbative
 order and heavy quark scheme, adopted for the evaluation of
@@
 For instance, when using the {\sc\small xFitter} profiling of PDF4LHC21, one needs
- to generate LHC neutrino pseudo-data also using PDF4LHC21 as input.
- %
-This ensures that the generated pseudo-data is consistent with the prior PDF
+ to generate  neutrino structure functions also using PDF4LHC21 as input.
+ %
+This ensures that the generated pseudo-data is coherent with the prior PDF
  set used as baseline and avoids introducing artificial inconsistencies 
@@
 
- The central values for the pseudo-data, denoted
- by $\mathcal{O}_i^{{\rm (exp)}} $, are obtained
+ The central values for the pseudo-data, denoted by $\mathcal{O}_i^{{\rm (exp)}} $, are obtained
  by fluctuating the reference theory prediction Eq.~(\ref{eq:theory_dis_projections})
@@
  %
- Here we consider two scenarios for the systematic errors: ``conservative'',  with $f_{\rm red}=1$, where
- no improvement as compared to current projected performance takes place, and ``optimistic'', with  $f_{\rm red}=0.5$, a factor
- two improvement for all sources of systematics.
- %
  The pseudo-data generated by means of Eq.~(\ref{eq:pseudo_data_v2}),
  together with the corresponding covariance matrix computed according to Eq.~\eqref{eq:covmat_definition_v2},
- define then the inputs of the subsequent proton and nuclear PDF determination.
+ define then the inputs of the subsequent proton and nuclear PDF determinations.
 
@@
 %
-To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed and is available in {\sc\small xFitter}.
+To this end, a new interface between  {\sc\small PineAPPL} and {\sc\small xFitter} has been developed and is made available in {\sc\small xFitter}.
 %
@@
 the  {\sc\small PineAPPL}  grids, are available
-from the {\sc\small xFitter} repository.
+from the public {\sc\small xFitter} repository.
 %
@@
 %
-Predictions for the observables Eq.~(\ref{eq:theory_dis_projections}) are evaluated
-with NNPDF4.0 NNLO for various choices of input datasets, and included
+Predictions for the fitted observables Eq.~(\ref{eq:theory_dis_projections}) are evaluated
+with NNPDF4.0 NNLO and included
 directly in the same alongside all other datasets in the global fit.
@@
 and the generated pseudo-data.
-%
-We assess the impact of the forward LHC neutrino data in the NNPDF fits both when added
-on top of the baseline dataset and when added to a dataset which excludes previous neutrino DIS
-cross-section measurements.

### 2023-09-01 paper/sec-results.tex
sect 3

@@
 
-By means of the strategy outlined in Sect.~\ref{sec:dis_pseudodata}, here
-we quantify the impact on the proton PDFs
-of differential  DIS
-cross-section measurements exploiting the  LHC
-neutrino beam. 
-%
-We assume an isoscalar free-nucleon target and neglect non-isoscalarity effects and nuclear modifications,
-which are instead considered in Sect.~\ref{sec:nuclearPDFs}.
+By following the strategy outlined in Sect.~\ref{sec:dis_pseudodata}, one can
+quantify the impact on the proton and nuclear PDFs of differential  DIS
+cross-section measurements exploiting the  LHC neutrino beam. 
 %
 We present results first for the Hessian profiling of the PDF4LHC21,
-and second for the Monte Carlo fit NNPDF4.0.
+then for the Monte Carlo fit NNPDF4.0, and finally for the nuclear PDFs of EPPS21, also
+by means of profiling.
 %
@@
 %
-We compare the impact of the different FPF experiments separately and also provide
+We also compare the impact of the different FPF experiments separately and provide
 results for their combination.
@@
 We begin by presenting results for the Hessian profiling of
-the PDF4LHC21 NNLO set.
+the PDF4LHC21 set.
 %
@@
 We profile PDF4LHC21 with pseudodata from various LHC neutrino experiments,
-and study the stability of the results with respect to variations in the data
-and methodology inputs.
+and study the stability of the results with respect to variations in the profiling inputs.
 
@@
 \caption{
-The fractional uncertainties (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
+The fractional PDF uncertainties (at the 68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
 for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
-in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 pseudo-data is included.
+in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 structure
+functions are included.
 %
-The FASER$\nu$2 impact projections are provided both without and with systematic
-uncertainties accounted for.
-%
-We include  both  inclusive and charm-tagged structure functions
-and assume outgoing lepton charge-separation.
+The FASER$\nu$2 impact projections are presented both without and with systematic
+uncertainties accounted for, and include charm-tagged structure functions
+as well as final-state lepton-charge separation.
 %
@@
 
-\paragraph{Statistic versus systematic uncertainties.}
+\paragraph{Constraints from FASER$\nu$2.}
 %
@@
 for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
-in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 pseudo-data is added
-by means of Hessian profiling.
+in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 structure functions are
+added by means of Hessian profiling.
 %
@@
 We restrict the comparisons to the region $10^{-3}\lsim x \lsim 0.7$ covered
-by the LHC neutrino experiments as shown in Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF}.
+by the LHC neutrino experiments (see Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF}).
 %
-Note that in addition of a reduction of PDF uncertainties, the Hessian profiling
+In addition of a reduction of PDF uncertainties, the Hessian profiling
 also results in general in a shift in the PDF central values.
@@
 functions at FASER$\nu$2 improve PDF uncertainties on the quark PDFs, while leaving
-the gluon PDF essentially unaffected.
+the gluon essentially unaffected.
 %
@@
 %
-The analysis of Fig.~\ref{fig:FASERnu2_baseline} shows that LHC neutrino data is particularly
+The analysis of Fig.~\ref{fig:FASERnu2_baseline} highlights that LHC neutrino data is particularly
 constraining for the poorly-known strange PDF, which is one of the quark flavour combinations
@@
 %
-We can hence establish that inclusive neutrino DIS measurements constrain mostly
-the up and down quark and antiquark PDFs (and thus also the total quark singlet), while the charm-tagged
+We thus establish that inclusive neutrino DIS measurements constrain mostly
+the up and down quark and antiquark PDFs (and thus also the quark singlet), while the charm-tagged
 structure functions are responsible for most of the constraints provided on the total strangeness.
 %
-The PDF reach of the LHC neutrino experiments would thus be  markedly limited for experiments without
+The PDF reach of the LHC neutrino experiments would thus be  markedly limited in experiments without
 charm-identification capabilities.
@@
 
-One finds that the lack of charged-lepton identification actually does not degrade significantly the PDF
+This analysis finds that the lack of charged-lepton identification actually does not degrade significantly the PDF
 sensitivity of FASER$\nu$2.
@@
 %
-We conclude that LHC neutrino DIS data exhibits good PDF sensitivity even for an experiment which cannot tell
-apart incoming neutrinos from antineutrinos.
+We conclude that LHC neutrino DIS data exhibits good PDF sensitivity even for detectors which cannot
+separate incoming neutrinos from antineutrinos.
 

### 2023-09-01 paper/sec-results.tex
Update sec-results.tex

@@
 
-\paragraph{FASER$\nu$2 compared to AdvSND and FLArE.}
+\paragraph{Experiment dependence.}
 %
@@
 %
-Figs.~\ref{fig:FASERnu2_advsnd} and~\ref{fig:FASERnu2_FLAre10} compare the PDF sensitivity
+Fig.~\ref{fig:FASERnu2_FLAre10} compares the PDF sensitivity
 of FASER$\nu$2, in the scenario where systematic uncertainties are neglected, with the corresponding
-results for AdvSND and FLArE100 respectively.
+results for AdvSND and FLArE10 respectively.
 %
 As summarised by Table~\ref{tab:integrated_rates}, each of these experiments
-has associated different expected numbers of DIS events, namely 260k, 28k, and 57k (340K)
+has associated different expected numbers of DIS events, namely 260k, 28k, and 57k (340k)
 inclusive muon-neutrino events for FASER$\nu$2, AdvSND and FLArE10~(100) respectively,
@@
 %
-In this comparison, one would expect that experiments with the largest event rates best PDF sensitivity.
+As shown below, experiments with the largest event rates are those exhibiting the
+best PDF sensitivity.
 
@@
 \caption{
-  Same as Fig.~\ref{fig:FASERnu2_advsnd},
+  Same as Fig.~\ref{fig:FASERnu2_baseline} (statistical uncertainties only),
   comparing
-  the projected PDF impact of FASER$\nu$2 with that of  AdvSND (top) and FLArE10 (bottom). 
+  the projected PDF impact of FASER$\nu$2 with that of  AdvSND (top panels) and FLArE10 (bottom panels). 
 }
@@
 
-From Figs.~\ref{fig:FASERnu2_advsnd} and~\ref{fig:FASERnu2_FLAre10} one can see that the three
+From Fig.~\ref{fig:FASERnu2_FLAre10} one can see that the three
 FPF experiments studied lead to a reduction of the  uncertainties in the quark PDFs.
@@
 %
-In the case of AdvSND, the  smaller sample of charm-tagged events lead to reduction
-of the constraints on strangeness.
+In the case of AdvSND, the  smaller sample of charm-tagged events is responsible for the reduction
+in the constraints on strangeness.
 %
@@
 
-We note that a proper comparison between the PDF reach of
-the various FPF experiments requires accounting for the systematic uncertainties
-associated to their kinematic reconstruction performance, which ultimately becomes
+We note here that Fig.~\ref{fig:FASERnu2_FLAre10} compares fits based on FPF pseudo-data
+with only statistical uncertainties, and that a more refined comparison between the PDF reach of
+the various FPF experiments requires accounting also for the systematic uncertainties, which ultimately become
 one of the limiting factors.
@@
 valuable input to enhance the PDF sensitivity.
+
+To conclude this discussion, applying the same procedure to FASER$\nu$ and SND@LHC structure
+functions leaves the baseline PDF4LHC21 results unaffected, as demonstrated in App.~\ref{app:fasernu_runIII_impact},
+showing that for the current generation of LHC neutrino detectors
+it will be difficult to provide competitive constraints on the proton structure.
 

### 2023-09-01 paper/sec-dis-pseudodata.tex
systematic wording and Eq.

@@
 %
-By comparing $\mathcal{D}_0$ with the number of events as calculated by Eq.~(\ref{eq:event_yields_calculation}), 
-we can normalize the sampled $\mathcal{D}_0$ distribution with a factor $\hat{f}$ to reproduce the expected yield.
-%
 We then take each event in $\mathcal{D}_0$ and smear it with Gaussian distributions whose variances are given by Table~\ref{tab:FPF_experiments} to produce a set of new samples $\{\mathcal{D}_k\}$.
@@
 
-We define the uncertainty associated
-to a given systematic source, say $\delta E_\ell$,
-to be the mean of the absolute difference between the number of events in this bin for the smeared samples $\{\mathcal{D}_k\}$ normalized to $\hat{f}$  and the central prediction for the number of events
-$N_{\rm ev}^{(i)}$ as calculated from Eq.~(\ref{eq:event_yields_calculation}):
+We define the fractional uncertainty associated
+to a given systematic source, say $\delta E_\ell$, for bin $i$
+to be the mean of the absolute difference between the number of events in this bin for the smeared samples $\{\mathcal{D}_k\}$  and the number of events in this bin for ${\mathcal{D}_0}$:
 \be
-\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} =\la \Big|  \hat{f} {N}^{(i)}_{E_\ell-{\rm smeared}} -N_{\rm ev}^{(i)}\Big|\ra \, .
+\delta_{\rm sys}^{(E_\ell)} =\la \left|  \frac{{N}^{(i)}_{E_\ell-{\rm smeared},k} -N_0^{(i)}}{N_0^{(i)}}\right|\ra \, .
 \ee

### 2023-09-01 paper/sec-dis-pseudodata.tex
missed a piece in sys unc.

@@
 to a given systematic source, say $\delta E_\ell$, for bin $i$
-to be the mean of the absolute difference between the number of events in this bin for the smeared samples $\{\mathcal{D}_k\}$  and the number of events in this bin for ${\mathcal{D}_0}$:
+to be the mean of the absolute difference between the number of events in this bin for the smeared samples $\{\mathcal{D}_k\}$  and the number of events in this bin for ${\mathcal{D}_0}$ which also serves as a normalization to produce a fractional uncertainty:
 \be

### 2023-09-01 paper/sec-dis-pseudodata.tex
event yield uncertainty

@@
 \ee
+The systematic uncertainty in event yield caused by $\delta E_\ell$ is then $\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)}$.
+%
 Individual sources of systematic errors are treated as uncorrelated among them, and hence

### 2023-09-02 paper/FPF-WG1.tex
Minor corrections

@@
 to be  hosted at the proposed
-Forward Physics Facility (FPF) operating concurrently with the High-Luminosity LHC.
+Forward Physics Facility (FPF) operating concurrently with the High-Luminosity LHC (HL-LHC).
 %

### 2023-09-02 paper/sec-pheno.tex
some polishing
Minor corrections

@@
-\clearpage
 \section{Implications for HL-LHC processes}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+	\caption{
+		Same as Fig.~\ref{fig:NNPDF40_pheno_integrated} but with PDF4LHC21.
+		}
+	\label{fig:PDF4LHC21_pheno_integrated}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\caption{
+		Same as Fig.~\ref{fig:NNPDF40_pheno_differential} but with PDF4LHC21.
+	}
+	\label{fig:PDF4LHC21_pheno_differential}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The studies presented in this section provide only a first glimpse of the potential

### 2023-09-03 paper/sec-results.tex
Add FPF chi2 for stat only to table

@@
   & Direct photon production                 &  0.740  &   0.729    &    0.744  \\
-  & FPF (total)                 &  -  &       &      \\
+  & FPF (total)                 &  -  &   1.192    &      \\
   \bottomrule

### 2023-09-04 paper/sec-summary.tex
some polishing
summary

@@
 
-In this work, we have quantified the impact of ongoing and proposed
-experiments detecting the scattering of energetic neutrinos produced
-by LHC collisions in the forward direction.
+In this work we have, for the first time,
+quantified the impact that measurements of high-energy
+neutrino DIS structure functions at the LHC would have on the quark
+and gluon structure of the nucleon.
 %
-By means of estimating the expected deep-inelastic scattering
-event rates differential
-in $x$, $Q^2$, and $E_\nu$ for these various experiments, and
-evaluating the associated theoretical predictions for
-both inclusive and charm production processes, we have
-assessed the expected reduction of PDF uncertainties with respect
-to modern fits of proton and nuclear structure.
+Our analysis has required the generation of
+DIS pseudo-data fully differential in $x$, $Q^2$, and $E_\nu$
+for the various ongoing and proposed far-forward
+neutrino LHC experiments, including an initial estimate
+of their associated systematic uncertainties.
 %
-To this end, we have studied the robustness of the results
-with respect the modelling of systematic uncertainties, the role of lepton
-charge separation, and the impact of the selection and acceptance cuts.
+Consistent results are obtained from both the Hessian profiling
+of PDF4LHC21 and from the direct inclusion of LHC neutrino
+structure functions in the NNPDF4.0 global
+fit, revealing a reduction of PDF uncertainties in the
+light quark sector, in particular concerning strangeness, as well
+as for the large-$x$ charm PDF in the case of NNPDF4.0.
+%
+We have then assessed the  robustness of the results upon
+removing charm-tagged data and final-state lepton-charge
+identification, as well as upon the combination
+of all FPF experiments within a single analysis.
 
-We demonstrate that neutrino DIS measurements at the proposed FPF
-experiments would have a significant potential to improve our current
-knowledge of quark and antiquark flavour separation in protons
-and heavy nuclei, including strangeness,
-and that the FASER$\nu$ and SND@LHC
-experiments may provide the first-ever
-constraints on hadron structure from collider neutrinos.
+We have also demonstrated the rich interplay between
+far-forward and central measurements
+at the HL-LHC by providing predictions
+for a range of Higgs and gauge boson production processes,
+both for integrated cross-sections in the fiducial region and for
+single-differential distributions.
+%
+This HL-LHC phenomenological analysis suggests that a reduction
+of the  PDF uncertainty by up to a factor two
+may be within reach for some of these cross-sections,
+in the most optimistic scenario.
+%
+As was the case at the PDF level, also for 
+the HL-LHC projections results based on  PDF4LHC21 and NNPDF4.0
+are in qualitative agreement.
 %
 Together with this paper, we also
-release the pseudodata and the corresponding theory
-calculations produced in this work.
+release the corresponding {\sc\small LHAPDF} grids~\cite{Buckley:2014ana}
+for PDF4LHC21 and NNPDF4.0 including FPF data,
+as well as the LHC neutrino DIS structure function pseudo-data
+and the corresponding theory
+calculations for all scenarios considered in this work.
 %
-These should be of relevance for colleagues interested in the physics
+The latter should be of relevance for colleagues interested in the physics
 of forward
@@
 for hadron structure analyses with LHC neutrinos.
+%
+In particular, improved experiment design novel reconstruction techniques i.e. based
+on deep learning or combination of information from different
+experiments may be key to further reduce systematic
+uncertainties as required to maximise the impact
+of neutrino DIS measurements at the LHC.
 %
@@
 important information on the shallow-inelastic scattering (SIS)
-region at low values of $Q$~\cite{Candido:2023utz}, relevant for inclusive cross-sections
+region at low values of $Q$~\cite{Jeong:2023hwe,Candido:2023utz}, relevant for inclusive cross-sections
 entering atmospheric and oscillation neutrino experiments.
@@
 as a given and neglected any associated uncertainties.
+%
+small-x QCD, gluon PDF
 %
@@
 We are grateful to many colleagues involved in the Forward
-Physics Facility initiative for many illuminating
-discussions and encouragement along the course of this project.
+Physics Facility initiative for illuminating
+discussions and encouragement along the course of this project,
+in particular Jamie Boyd, Jonathan Feng, and Albert de Roeck.
 %
-We thank specially Felix Kling for may useful discussions in the course
-of the project and for providing the neutrino fluxes.
+We thank specially Felix Kling for many useful discussions
+and for providing updated predictions for the neutrino fluxes.
 %
@@
 concerning FASER$\nu$2, Milind Diwan,
-Wenjie Wu and Steven Linden concerning FLArE,
-and Antonia di Crescenzo concerning AdvSND. The work of M.F. was supported by NSF Grant PHY-2210283 and was also supported by NSF Graduate Research Fellowship Award No. DGE-1839285.
+Wenjie Wu, and Steven Linden concerning FLArE,
+and Antonia di Crescenzo for information concerning AdvSND.
+
+The work of M.~F. was supported by NSF Grant PHY-2210283 and was also supported by NSF Graduate Research Fellowship Award No. DGE-1839285.
+%
+The work of T.~G., G.~M., and J.~R. is partially supported by NWO, the Dutch Research Council.
+%
+The work of T.~R. and J.~R. is partially supported by an ASDI2020
+Fellowship from the Netherlands eScience Center.

### 2023-09-04 paper/sec-summary.tex
Update sec-summary.tex

@@
 %
-Our analysis has required the generation of
+Our analysis has involved the generation of
 DIS pseudo-data fully differential in $x$, $Q^2$, and $E_\nu$
@@
 far-forward and central measurements
-at the HL-LHC by providing predictions
+at the HL-LHC, by providing predictions
 for a range of Higgs and gauge boson production processes,
@@
 are in qualitative agreement.
-%
-Together with this paper, we also
-release the corresponding {\sc\small LHAPDF} grids~\cite{Buckley:2014ana}
-for PDF4LHC21 and NNPDF4.0 including FPF data,
-as well as the LHC neutrino DIS structure function pseudo-data
-and the corresponding theory
-calculations for all scenarios considered in this work.
-%
-The latter should be of relevance for colleagues interested in the physics
-of forward
-neutrino scattering at the LHC, not only for hadronic structure studies
-but also for neutrino (effective)
-interactions and BSM searches e.g. of sterile neutrino oscillations.
 
@@
 First of all, as the design of the proposed FPF experiments
-becomes more advanced and concrete, it should be possible
-to construct more accurate estimates of the systematic
-uncertainties and of their bin-by-bin correlations,
-which may eventually become the limiting factor
-for hadron structure analyses with LHC neutrinos.
+ advances, it will be possible to derive
+ more accurate estimates of the systematic
+uncertainties (and of their correlations) 
+which eventually become the limiting factor.
 %
-In particular, improved experiment design novel reconstruction techniques i.e. based
-on deep learning or combination of information from different
-experiments may be key to further reduce systematic
-uncertainties as required to maximise the impact
-of neutrino DIS measurements at the LHC.
+This will allow studying whether  improved detection methods,
+novel reconstruction techniques i.e. based
+on deep learning, or combining information from different
+experiments can  push down the systematic uncertainties
+affecting the measurements.
 %
-Second, scattering analyses with LHC neutrinos would benefit from
+Second, the modelling of neutrino scattering at the LHC would benefit from
 the use of Monte Carlo event generators accounting
@@
 As compared to the currently used LO generators,
-these would improve the modelling of the final-state leptonic
-and hadronic kinematics, which in turn determine the acceptance rate
+these would improve the description of the final-state
+kinematics, which in turn determine the acceptance rate
 of the reconstructed events.
 %
-Further, the predictions from such precise Monte Carlo generators
+Furthermore, the predictions from such precise Monte Carlo generators
 should eventually be folded with a full-fledged detector simulation
-in order to robust determine selection efficiencies, e.g.
-such as those related to charm tagging.
+in order to robustly determine selection efficiencies, e.g.
+such as those related to charm and $D$-meson tagging.
 
-Third, while in this work we have focused on the deep-inelastic
-region, ongoing and future LHC experiments also provide
-important information on the shallow-inelastic scattering (SIS)
-region at low values of $Q$~\cite{Jeong:2023hwe,Candido:2023utz}, relevant for inclusive cross-sections
+Third, while here we focus on the DIS
+region, ongoing and future LHC neutrino experiments also provide
+important information on shallow-inelastic scattering (SIS)
+ at lower values of $Q$~\cite{Jeong:2023hwe,Candido:2023utz},
+ which in turn are relevant for inclusive cross-sections
 entering atmospheric and oscillation neutrino experiments.
 %
-By means of a similar approach, it should be possible to quantify
-the improvements that LHC neutrino data can provide on models
-of neutrino scattering in the poorly-understood SIS region.
+By following the approach presented in this work, it should be possible to quantify
+the improvements that LHC data provides on models
+of neutrino scattering in this poorly-understood SIS region.
 %
-Finally, in this work we have taken the incoming muon neutrino flux
-as a given and neglected any associated uncertainties.
+Finally, in this work we have taken the incoming neutrino fluxes
+as an external input and neglected any associated uncertainties.
 %
-small-x QCD, gluon PDF
+However, measurements of these fluxes provides
+unique information on light and heavy forward hadron
+production in QCD, and in particular open
+a new window to the small-$x$ gluon PDF.
 %
-However, ultimately one may need to constrain at the same time
+For this reason, ultimately one needs to simultaneously constrain 
 the incoming fluxes and the neutrino scattering cross-sections
-from the recorded event rates.
+from the measured event rates.
 %
 Such joint interpretation would require extending the present
-analysis with additional theory nuisance parameters modelling
-deviations of the neutrino flux with respect to the baseline predictions.
+analysis with a data-driven parametrisation of the neutrino fluxes,
+which could subsequently be compared with different theoretical predictions.
 
-All in all, our findings highlight how exploiting
-the LHC neutrino beam for hadron structure studies effectively
-extends the LHC with a ``Neutrino-Ion Collider'', a charged
-current-counterpart of the EIC, and that we are still
-scratching the surface of the uncharted
-scientific potential of such experiments.
+Our findings highlight how exploiting the LHC neutrino beam for hadron structure
+studies effectively provides CERN with a ``Neutrino-Ion Collider'', a charged
+current-counterpart of the EIC, without  changes in
+its accelerator infrastructure or additional energy costs.
+%
+In addition for their intrinsic interest for hadronic science,
+measurements of neutrino structure function at the LHC
+provide a novel, and until now ignored, handle to inform theoretical
+predictions of hard-scattering cross-sections  at the HL-LHC.
+
+\begin{center}
+\rule{5cm}{.1pt}
+\end{center}
+\bigskip
+
+Together with this paper, we 
+make public in Zenodo
+the corresponding {\sc\small LHAPDF} grids~\cite{Buckley:2014ana}
+for the PDF4LHC21 and NNPDF4.0 fits including FPF data.
+%
+We also release
+the generated LHC neutrino DIS structure function pseudo-data
+and the corresponding theory
+calculations, for all scenarios considered in this work.
+%
+These projections for neutrino structure functions
+should be of relevance for a broad range of
+applications related to forward
+neutrino scattering at the LHC, from tests
+of lepton flavour university at the TeV scale
+in the neutrino sector to probes of anomalous neutrino
+interactions and searches for sterile neutrinos
+distorting  oscillation patterns.
 

### 2023-09-04 paper/sec-pheno.tex
Update sec-pheno.tex

@@
-\section{Implications for HL-LHC processes}
+\section{Implications for Higgs and weak boson production}
 \label{sec:pheno}
 
-The reduction of PDF uncertainties enabled by the neutrino DIS measurements
-at the FPF presented in Sect.~\ref{sec:protonPDFs}
-makes possible more precise theoretical predictions for key processes at the
+The reduction of PDF uncertainties made possible by neutrino DIS measurements
+at the FPF, discussed in Sect.~\ref{sec:protonPDFs},
+enables more precise theoretical predictions for core processes at the
 HL-LHC.
@@
 Here we present an initial study of the phenomenological implications
-of PDFs enhanced with LHC neutrino data.
-%
-We adopt the same settings as in the LHC phenomenology analysis presented
-in the PDF4LHC21 combination paper~\cite{PDF4LHCWorkingGroup:2022cjn} and provide predictions
-both for inclusive fiducial cross-sections and for differential distributions.
+of the PDFs enhanced with LHC neutrino data
+for hard-scattering processes at proton colliders.
 %
 Specifically, we present results for 
-single and double gauge boson production, inclusive top quark pair production,
-and Higgs production in gluon
-fusion and in association with a vector boson.
+single and double gauge boson production,  Higgs production in
+vector-boson fusion, and Higgs production and in association with a vector boson.
 %
-We evaluate these cross-sections using NLO matrix elements
-which include  both in the
-QCD and electroweak corrections using
+We focus on processes sensitive to the quark-quark and quark-antiquark initial
+states, given that LHC neutrinos do not provide information on the gluon
+PDF and hence they cannot inform  gluon-initiated
+processes, such as top quark pair production or Higgs production in gluon fusion.
+
+We adopt the same calculational settings as in the LHC phenomenology analysis considered
+in the PDF4LHC21 combination study~\cite{PDF4LHCWorkingGroup:2022cjn} and provide predictions
+both for inclusive cross-sections, integrated in the fiducial
+region, and for differential distributions.
+%
+We evaluate these cross-sections using matrix elements
+which include NLO corrections both in the
+QCD and electroweak coupling using
 {\sc\small mg5\_amc@nlo}~\cite{Frederix:2018nkq}
@@
 For all processes, realistic selection and acceptance cuts on the final state particles
-have been applied, and PDF uncertainty bands correspond to 90\% CL
-uncertainties.
+have been applied.
 %
 No further theory uncertainties are considered in this
-analysis.
+analysis, given that we don't aim to compare with experimental data.
 
@@
 fiducial cross-section for representative LHC processes at $\sqrt{s}=14$ TeV
-evaluated with NNPDF4.0 NNLO, compared with the fits including the FPF structure function projections.
+evaluated with NNPDF4.0 (top panels)
+and with PDF4LHC21 (bottom panels),
+compared with the results obtained from
+the fits including the FPF structure function projections.
 %
@@
 %
-We focus on processes dominated by quark-quark and quark-antiquark scattering, given
-that the FPF structure functions would not have any impact on gluon-initiated
-processes such as top quark pair production or Higgs production in gluon fusion.
-%
 The corresponding comparison at the level of differential distributions
@@
 \includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-integrated.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
+\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
 \caption{Fiducial cross-sections for representative LHC processes at $\sqrt{s}=14$ TeV
-evaluated with NNPDF4.0 NNLO, compared with the fits including the FPF structure function projections.
+  evaluated with NNPDF4.0 (upper panels) and PDF4LHC21 (bottom panels),
+  compared with the fits including the FPF structure function projections.
   %
-For the NNPDF4.0 baseline
-prediction, the dark (light) bands indicate the 68\% (95\%) CL uncertainties.
+  See~\cite{NNPDF:2021njg,PDF4LHCWorkingGroup:2022cjn} for the calculational settings
+  used to evaluate these cross-sections.
 %
-The fit labelled as ``\_FPF'' is the one  based on statistical uncertainties,
-while that labelled as ``\_FPF$^*$'' also includes systematic errors.
+For the baseline
+predictions, the dark (light) bands indicate the 68\% (95\%) CL uncertainties.
 %
-The central values are set to be the same as in the original NNPDF4.0 calculation in all cases.
+The fits labelled as ``\_FPF'' are the ones considering statistical uncertainties,
+while those labelled as ``\_FPF$^*$'' also include systematic errors.
 %
-See~\cite{NNPDF:2021njg,PDF4LHCWorkingGroup:2022cjn} for the calculational settings.
+In the fits with FPF data, the central values are set to be the same as
+in the corresponding baseline.
 %
-From top to bottom, we show inclusive Drell-Yan production ($Z, W^+, W^-$), Higgs production
+We provide predictions for inclusive Drell-Yan production ($Z, W^+, W^-$), Higgs production
 in vector-boson fusion, Higgs associated
@@
 \caption{Same as Fig.~\ref{fig:NNPDF40_pheno_integrated}
-for the corresponding differential distributions.
+for the corresponding differential distributions in the case of NNPDF4.0
 %
@@
 \label{fig:NNPDF40_pheno_differential}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-global-pdf4lhc21.pdf}
+	\caption{
+		Same as Fig.~\ref{fig:NNPDF40_pheno_differential} but with PDF4LHC21.
+	}
+	\label{fig:PDF4LHC21_pheno_differential}
 \end{figure}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
-	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
-	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
-	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
-	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
-	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
-	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
-	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
-	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-integrated-pdf4lhc21.pdf}
-	\caption{
-		Same as Fig.~\ref{fig:NNPDF40_pheno_integrated} but with PDF4LHC21.
-		}
-	\label{fig:PDF4LHC21_pheno_integrated}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-global-pdf4lhc21.pdf}
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-global-pdf4lhc21.pdf}
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-global-pdf4lhc21.pdf}
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-global-pdf4lhc21.pdf}
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-global-pdf4lhc21.pdf}
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-global-pdf4lhc21.pdf}
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-global-pdf4lhc21.pdf}
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-global-pdf4lhc21.pdf}
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-global-pdf4lhc21.pdf}
-	\caption{
-		Same as Fig.~\ref{fig:NNPDF40_pheno_differential} but with PDF4LHC21.
-	}
-	\label{fig:PDF4LHC21_pheno_differential}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 The studies presented in this section provide only a first glimpse of the potential

### 2023-09-04 paper/sec-pheno.tex
results section

@@
 compared with the results obtained from
-the fits including the FPF structure function projections.
+the corresponding fits including the FPF structure function projections.
 %
-For the latter, we display the variants based only on statistical uncertainties and that
-which includes also systematic errors.
+For the fits with FPF data we display the variants where the covariance matrix
+consists only of statistical errors (``\_FPF'') and where also
+systematic errors are accounted for (``\_FPF$^*$'').
 %
-The central values are set to be the same as in the original NNPDF4.0 calculation in all cases.
+For the baseline
+predictions, the dark (light) bands indicate the 68\% (95\%) CL uncertainties.
 %
-See~\cite{NNPDF:2021njg} for the calculational settings.
+The central values are set to be the same as in the baseline calculation in all cases.
 %
-From top to bottom, we show inclusive Drell-Yan production ($Z, W^+, W^-$), Higgs production
+From top to bottom, we show inclusive Drell-Yan production in the $Z$, $W^+$, and $W^-$
+channels, Higgs production
 in vector-boson fusion, Higgs associated
-production, and diboson production ($W^+W^-$, $W^+Z$, $W^-Z$).
+production, and diboson production in the $W^+W^-$, $W^+Z$, and $W^-Z$ final-states.
 %
-The corresponding comparison at the level of differential distributions
-are shown in Fig.~\ref{fig:NNPDF40_pheno_differential}.
+The corresponding comparisons at the level of differential distributions
+are shown in Figs.~\ref{fig:NNPDF40_pheno_differential} and~\ref{fig:PDF4LHC21_pheno_differential}
+for NNPDF4.0 and PDF4LHC21 respectively.
 %
@@
 we only indicate the relative PDF uncertainty in each fit, with central values
-assumed to be the same by construction.
+assumed to be unchanged.
 
@@
 
-Inspection of Figs.~\ref{fig:NNPDF40_pheno_integrated} and~\ref{fig:NNPDF40_pheno_differential}
-quantifies the potential of neutrino structure function measurements at the LHC
-to improve theoretical predictions for electroweak and high-scale processes at the HL-LHC.
+Inspection of Figs.~\ref{fig:NNPDF40_pheno_integrated}--\ref{fig:PDF4LHC21_pheno_differential}
+confirms the potential of LHC neutrino structure function measurements
+to improve theoretical predictions for Higgs, electroweak and high-mass
+processes at the HL-LHC.
 %
-Concerning first the fiducial integrated cross-sections, a reduction of PDF
+In general, qualitative consistency between the results based on NNPDF4.0
+and on PDF4LHC21 is found, as was already the case at the PDF level.
+%
+As  compared to the limiting scenario where only statistical uncertainties
+are taken into account, the reduction of PDF errors in the LHC cross-sections
+obtained thanks for the FPF structure functions becomes less marked,
+but still visible for most of the processes under consideration,
+upon the inclusion of systematic uncertainties in the fit covariance matrix.
+
+Concerning the fiducial integrated cross-sections, a decrease in PDF
 uncertainties is observed for all processes,
-including for $W^+$ production relevant for $m_W$ measurements, and its specific  magnitude depends
-on the underlying scattering reaction.
+including for single gauge boson production relevant for core
+HL-LHC analyses such as the $m_W$ and $\sin^2\theta_W$ measurements.
 %
-This finding also applies for Higgs associated production with vector bosons and in vector-boson-scattering,
-with for example
-PDF uncertainties in $hW^+$ reduced by up to a factor two thanks to the FPF measurements.
+The specific improvement in precision depends
+on the underlying scattering reaction as well as on the range
+of $x$ and $Q^2$ covered by each process.
 %
-Similar remarks apply to the diboson cross-sections, with in this case the largest
-improvement observed for $ZW^+$ channel.
+In the case of  Higgs associated production with vector bosons and in vector-boson
+scattering,
+driven by the quark-antiquark and quark-quark initial states respectively,
+one observes that PDF uncertainties can  be reduced
+by up to a factor two thanks to the FPF measurements, for instance
+in the case of the $hW^+$ and $hW^-$ cross-sections,
+in the most optimistic scenario in which systematic uncertainties
+are neglected.
 %
-Reassuringly, LHC predictions based on the fits with FPF pseudo-data are stable
-upon the inclusion of the experimental systematic uncertainties in the fit.
+Likewise for the diboson cross-sections, with in this case the largest
+improvement observed for the $ZW^+$  and  $ZW^-$ final states, with a reduction
+of up to $\sim 40\%$ in the PDF uncertainties.
 
-In the case of the differential cross-sections shown in Fig.~\ref{fig:NNPDF40_pheno_differential},
+In the case of the differential cross-sections displayed in Figs.~\ref{fig:NNPDF40_pheno_differential}
+and~\ref{fig:PDF4LHC21_pheno_differential},
 we observe how the impact of the FPF structure functions on LHC observables depends
@@
 %
-For instance, searches for heavy-resonances in the high-mass tail of the Drell-Yan
-distributions are going to be improved by FPF data.
+For instance, searches for heavy resonances in the high-mass tail of the Drell-Yan
+distributions could be improved by the addition of the FPF data.
 %
-The same applies for diboson prediction, and in the case of the $ZW^+$ channel we observe
-an improvement spatially in the low $p_{T,\ell\bar{\ell}}$ region.
+Similar considerations apply for diboson prediction, and in the case of the $ZW^{\pm}$ channel we observe
+an improvement specially in the low $p_{T,\ell\bar{\ell}}$ region which
+represents the bulk of the fiducial cross-sections.
 %
@@
 %
-The effects of accounting for systematic uncertainties in the fit are somewhat more visible
-here as compared to the inclusive cross-sections, indicating that they affect mostly
+The effects of accounting for systematic uncertainties in the fit covariance
+matrix are somewhat more visible here as compared to the inclusive cross-sections,
+indicating that they affect mostly
 the tails, rather than the bulk, of the distributions, and in particular the large-$x$
 behaviour of the PDFs.
-
-The studies presented in this section provide only a first glimpse of the potential
-of neutrino DIS measurements at the LHC to inform predictions for high-$p_T$ processes.
+%
+This observation emphasizes the importance of reducing systematic errors
+in the FPF measurements in order to enhance the cross-talk with HL-LHC analyses.

### 2023-09-04 paper/sec-results.tex
results section

--- 2023-09-01 paper/sec-results.tex
@@
   & Direct photon production                 &  0.740  &   0.729    &    0.744  \\
-  & FPF (total)                 &  -  &       &      \\
+  & FPF (total)                 &  -  &   1.192    &   0.919   \\
   \bottomrule
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
+\begin{figure}[htbp]
 \centering
 \includegraphics[width=0.99\textwidth]{plots/lumi-FPFall.pdf}
-\caption{Comparison of the PDF luminosities at $\sqrt{s}=14$ TeV
+\caption{Comparison of the PDF luminosities evaluated at $\sqrt{s}=14$ TeV
   as a function of the final-state invariant mass $m_X$ between
@@
   %
-  From left to right we show the gluon-gluon, quark-antiquark, and
-  quark-quark luminosities.
+  From left to right and top to bottom we show the gluon-gluon, quark-antiquark,
+  quark-quark, down-antiup, up-antistrange, and strange-antistrange luminosities.
+  %
+  The bands in the NNPDF4.0 baseline indicate the one-sigma PDF uncertainties.
 %

### 2023-09-04 paper/scripts/lumis.py

@@ -90,6 +90,20 @@ def lumi_wrap(y):
         xpdf1 = p.xfxQ(3,x1,q)+p.xfxQ(-3,x1,q)
         xpdf2 = p.xfxQ(0,x2,q) 
         integrand = (1.0/x1)*(xpdf1/x1)*(xpdf2/x2)
+    elif(lumitype=="dubar"): # strange-antistrange
+        xpdf1 = p.xfxQ(1,x1,q)
+        xpdf2 = p.xfxQ(-2,x2,q) 
+        integrand = (1.0/x1)*(xpdf1/x1)*(xpdf2/x2)
+        xpdf1 = p.xfxQ(-2,x1,q)
+        xpdf2 = p.xfxQ(1,x2,q) 
+        integrand = integrand + (1.0/x1)*(xpdf1/x1)*(xpdf2/x2)
+    elif(lumitype=="usbar"): # strange-antistrange
+        xpdf1 = p.xfxQ(2,x1,q)
+        xpdf2 = p.xfxQ(-3,x2,q) 
+        integrand = (1.0/x1)*(xpdf1/x1)*(xpdf2/x2)
+        xpdf1 = p.xfxQ(-3,x1,q)
+        xpdf2 = p.xfxQ(2,x2,q) 
+        integrand = integrand + (1.0/x1)*(xpdf1/x1)*(xpdf2/x2)
     else:
         print("invalid type of lumi = ",lumitype)
         exit()
@@ -105,8 +119,8 @@ def lumi_wrap(y):
 # Reduce verbosity of LHAPDF
 lhapdf.setVerbosity(0)
 # number of lumi combinations
-nlumi=3
-lumichannel=["gg","qq","q2"]
+nlumi=6
+lumichannel=["gg","qq","q2","dubar","usbar","ss"]
 # Set mx grid (log spaced)
 mx = np.logspace(np.log10(mxmin),np.log10(mxmax),nmx)
 
@@ -379,18 +393,23 @@ for iset in range(nset):
 #---------------------------------------------------------------------
 print("\n ****** Plotting relative luminosities ******* \n")
 
-ncols,nrows=3,1
+ncols,nrows=2,3
 py.figure(figsize=(ncols*5,nrows*3.5))
 gs = gridspec.GridSpec(nrows,ncols)
[…]

### 2023-09-04 paper/sec-results.tex
sect 3

@@
 quantify the impact on the proton and nuclear PDFs of differential  DIS
-cross-section measurements exploiting the  LHC neutrino beam. 
+cross-section measurements obtained with the  LHC neutrino beam. 
 %
-We present results first for the Hessian profiling of the PDF4LHC21,
+Here we present results first for the Hessian profiling of the PDF4LHC21,
 then for the Monte Carlo fit NNPDF4.0, and finally for the nuclear PDFs of EPPS21, also
@@
 results for their combination.
-
-\subsection{Proton PDFs: impact on PDF4LHC21}
-\label{sec:pdf4lhc21}
-
-We begin by presenting results for the Hessian profiling of
-the PDF4LHC21 set.
-%
-This proton PDF set is a Monte Carlo combination~\cite{Watt:2012tq,Carrazza:2015hva} of three global PDF sets, CT18~\cite{Hou:2019efy},
-MSHT20~\cite{Bailey:2020ooq}, and NNPDF3.1~\cite{NNPDF:2017mvq}.
-%
-Its Hessian representations are obtained by means of the reduction methodologies developed in~\cite{Gao:2013bia,Carrazza:2015aoa}.
-%
-Being based on the combination of three modern global PDF fits, PDF4LHC21 provides a robust estimate
-of  current uncertainties associated to our understanding of proton PDFs.
-%
-We profile PDF4LHC21 with pseudodata from various LHC neutrino experiments,
-and study the stability of the results with respect to variations in the profiling inputs.
 
@@
 
+\subsection{Proton PDFs: impact on PDF4LHC21}
+\label{sec:pdf4lhc21}
+
+We begin by presenting results for the Hessian profiling of
+the PDF4LHC21 set.
+%
+This proton PDF set is a Monte Carlo combination~\cite{Watt:2012tq,Carrazza:2015hva} of three global PDF sets, CT18~\cite{Hou:2019efy},
+MSHT20~\cite{Bailey:2020ooq}, and NNPDF3.1~\cite{NNPDF:2017mvq}.
+%
+Its Hessian representations are obtained by means of the reduction methodologies developed in~\cite{Gao:2013bia,Carrazza:2015aoa}.
+%
+Being based on the combination of three modern global PDF fits, PDF4LHC21 provides a conservative estimate
+of  current uncertainties associated to our understanding of proton PDFs.
+%
+We profile PDF4LHC21 with pseudodata from various LHC neutrino experiments,
+and study the stability of the results with respect to variations in the profiling inputs.
+
 \paragraph{Constraints from FASER$\nu$2.}
@@
 We restrict the comparisons to the region $10^{-3}\lsim x \lsim 0.7$ covered
-by the LHC neutrino experiments (see Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF}).
+by the LHC neutrino experiments (see also Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF}).
 %
@@
 %
-This shift is however arbitrary since it 
+This shift is however arbitrary, since it 
 depends on the fluctuations
@@
 Inspection of Fig.~\ref{fig:FASERnu2_baseline} reveals that measurements of DIS structure
-functions at FASER$\nu$2 improve PDF uncertainties on the quark PDFs, while leaving
+functions at FASER$\nu$2 would reduce PDF uncertainties on the quark and antiquark
+PDFs, while leaving
 the gluon essentially unaffected.
@@
 Given that all PDF determinations entering PDF4LHC21 already include existing neutrino
-DIS measurements, the fact that FASER$\nu$2 pseudo-data still manages to reduce PDF
+DIS measurements, the fact that FASER$\nu$2 pseudo-data still manages to improve
 uncertainties highlights the new information provided by the LHC neutrino experiments.
@@
 Indeed, while systematic uncertainties somewhat degrade the PDF sensitivity,
-they don't eliminate it for none of the quark PDFs.
+they do not wash it out for none of the quark PDFs.
 %
@@
 %
-We also note that the availability of different experiments accessing the same neutrino
+We also note that the availability of complementary experiments accessing the same neutrino
 beam should allow their mutual cross-calibration, such that the combination of their
 data brings in more information than just the trivial statistics scaling.
-
-\paragraph{Importance of charm-tagged measurements.}
-%
-The analysis of Fig.~\ref{fig:FASERnu2_baseline} highlights that LHC neutrino data is particularly
-constraining for the poorly-known strange PDF, which is one of the quark flavour combinations
-for which proton PDF fits differ the most~\cite{Faura:2020oom}.
-%
-To further investigate this point, Fig.~\ref{fig:FASERnu2_nocharm} compares the impact of the FASER$\nu$2 data shown in
-Fig.~\ref{fig:FASERnu2_baseline}, for the case in which only statistical
-uncertainties are considered, with the results of the same profiling once the charm-tagged
-structure function data is excluded from the fit.
-%
-While differences are moderate for the up and down quark PDFs, the significant loss
-of information resulting from this exclusion of charm-tagged data is clearly
-visible for the strange PDF.
-%
-Specially in the region $x\gsim 0.01$, the constraints on strangeness shown in
-Fig.~\ref{fig:FASERnu2_nocharm} are washed out in the absence of charm-tagged data.
-%
-We thus establish that inclusive neutrino DIS measurements constrain mostly
-the up and down quark and antiquark PDFs (and thus also the quark singlet), while the charm-tagged
-structure functions are responsible for most of the constraints provided on the total strangeness.
-%
-The PDF reach of the LHC neutrino experiments would thus be  markedly limited in experiments without
-charm-identification capabilities.
 
@@
 
+\paragraph{Relevance of charm-tagged measurements.}
+%
+The analysis of Fig.~\ref{fig:FASERnu2_baseline} highlights that LHC neutrino data is particularly
+constraining for the poorly-known strange PDF, which is one of the quark flavour combinations
+for which proton PDF fits differ the most~\cite{Faura:2020oom}.
+%
+To further investigate this point, Fig.~\ref{fig:FASERnu2_nocharm} compares the impact of the FASER$\nu$2 data shown in
+Fig.~\ref{fig:FASERnu2_baseline}, for the case in which only statistical
+uncertainties are considered, with the results of the same profiling once the charm-tagged
+structure function data is excluded from the fit.
+%
+While differences are moderate for the up and down quark PDFs, the significant loss
+of information resulting from this exclusion of charm-tagged data is clearly
+visible for the strange PDF.
+%
+Specially in the region $x\gsim 0.01$, the constraints on strangeness shown in
+Fig.~\ref{fig:FASERnu2_nocharm} are mostly washed out in the absence of charm-tagged data.
+%
+We thus establish that inclusive neutrino DIS measurements constrain predominantly
+the up and down quark and antiquark PDFs (and thus also the quark singlet), while the charm-tagged
+structure functions are responsible for most of the constraints provided on the total strangeness.
+%
+The PDF reach of the LHC neutrino experiments would thus be  markedly limited in experiments without
+charm-identification capabilities.
+
 \paragraph{Lepton-charge identification.}
@@
 Fig.~\ref{fig:FASERnu2_nochargeID} compares the reduction of the PDF uncertainties using
-the FASER$\nu$2 data with and without charged-lepton identification capabilities.
+the FASER$\nu$2 data with and without assuming charged-lepton identification capabilities.
 
@@
 %
-We conclude that LHC neutrino DIS data exhibits good PDF sensitivity even for detectors which cannot
+We conclude that LHC neutrino DIS data exhibits competitive PDF sensitivity even for detectors which cannot
 separate incoming neutrinos from antineutrinos.
@@
 %
-In addition to FASER$\nu$2, we have also produced PDF impact projections for
+Together with those for FASER$\nu$2, we have also produced PDF impact projections for
 other proposed FPF experiments, specifically for AdvSND and FLArE.
@@
 with 39k, 3.5k, and 7.7k (45k) in the charm-tagged case.
-%
-As shown below, experiments with the largest event rates are those exhibiting the
-best PDF sensitivity.
 
@@
 
+In agreement with expectations, 
+detectors with the largest event rates are those exhibiting the
+best PDF sensitivity.
+%
 From Fig.~\ref{fig:FASERnu2_FLAre10} one can see that the three
@@
 achieved by FASER$\nu$2 are somewhat better than for the other two experiments,
-as could have been expected by the larger event yields obtained in the former.
+consistent with the larger event yields obtained in the former.
 %
@@
 
-We note here that Fig.~\ref{fig:FASERnu2_FLAre10} compares fits based on FPF pseudo-data
+We emphasize
+that Fig.~\ref{fig:FASERnu2_FLAre10} compares fits based on FPF pseudo-data
 with only statistical uncertainties, and that a more refined comparison between the PDF reach of
@@
 
-To conclude this discussion, applying the same procedure to FASER$\nu$ and SND@LHC structure
-functions leaves the baseline PDF4LHC21 results unaffected, as demonstrated in App.~\ref{app:fasernu_runIII_impact},
-showing that for the current generation of LHC neutrino detectors
-it will be difficult to provide competitive constraints on the proton structure.
+Applying the same procedure to FASER$\nu$ and SND@LHC structure
+functions leaves the baseline  results from PDF4LHC21 essentially
+unaffected, as demonstrated in App.~\ref{app:fasernu_runIII_impact},
+and showing that for the current generation of LHC neutrino detectors
+it will be difficult to provide competitive constraints on the proton structure due
+to the (relatively) low event rates.
 
@@
 %
-Finally, we have carried out a further PDF analysis including simultaneously the three FPF experiments
+We have also carried out a further PDF analysis including simultaneously the three FPF experiments
 considered so far: FASER$\nu$2, AdvSND, and FLArE100.
@@
 
-All in all, Fig.~\ref{fig:FPF_combined}, and in particular the statistics-only case, represents
+The projections displayed in
+Fig.~\ref{fig:FPF_combined}, and in particular the statistics-only case, represents
 a best-case scenario for the reduction of PDF uncertainties which can be expected from
-the analysis of neutrino DIS structure function data at the FPF, in the assumption that PDF4LHC21 accurately represents
+the analysis of neutrino DIS structure function data at the FPF,
+under the assumption that PDF4LHC21 accurately represents
 our current knowledge about the quark and gluon structure of the proton.
@@
 %
-We emphasize that we have produced results for the variations studied in
-Sect.~\ref{sec:pdf4lhc21} also with the NNPDF fitting methodology.
+We have also produced results for the different variations studied in
+Sect.~\ref{sec:pdf4lhc21} with the NNPDF fitting methodology.
 %
 Given that the qualitative obtained with the NNPDF fits
-are compatible with those obtained with {\sc\small xFitter}, it is not necessary to duplicate them here,
-and hence we only show results for the impact of the combined FPF pseudo-data.
+are compatible with those obtained with {\sc\small xFitter}, it is not necessary to duplicate them here
+and we only show results for the impact of the combined FPF pseudo-data.
 
@@
   We now also show results for the charm PDF (bottom right panel), which
-  in the NNPDF4.0 fit is also determined directly from the data entering the fit.
+  in the NNPDF4.0 fit is determined from the data entering the fit.
 %
@@
 %
-From top to bottom we indicate the total $\chi^2$, average
-over replicas of the training and validation figures of merit
-$\la E_{\rm tr}\ra_{\rm rep}$ and $\la E_{\rm val}\ra_{\rm rep}$,
-average $\chi^2$ over replicas $\la \chi^2\ra_{\rm rep}$,
-$\chi^2$ for datasets grouped by process.
+The last row displays the $\chi^2$ obtained for the combined FPF dataset,
+for which one finds $\chi^2 \sim 1$ up to fluctuations, consistent
+with the fact that the FPF pseudo-data
+is produced by construction to be compatible with the NNPDF4.0 baseline.
 %
-Note that the last row displays the $\chi^2$ obtained for the combined FPF dataset.
-%
-For the latter, one finds that as expected $\chi^2 \sim 1$, given that the FPF pseudo-data
-is produced by construction to be fully compatible with the NNPDF4.0 baseline.
-%
-For the same reason, the description of all other experiments entering
+For the same reason, the description of the other experiments entering
 the NNPDF4.0 global fit is not distorted by the inclusion of the FPF data.
@@
 as a function of the final-state invariant mass $m_X$ between
-the baseline NNPDF4.0 NNLO determination and its variant which includes
-the combined FPF pseudo-data from the FASER$\nu$2, FLArE100, and AdvSND experiments,
+the baseline NNPDF4.0 determination and its variants which includes
+the combined FPF pseudo-data from the FASER$\nu$2, FLArE, and AdvSND experiments,
 see Figs.~\ref{fig:NNPDF40_baseline} or the corresponding PDF comparison.
-%
 %
@@
 %
-  Specifically, we show the gluon-gluon, quark-antiquark, and
-  quark-quark luminosities.
+Specifically, we show the gluon-gluon, quark-antiquark, 
+quark-quark, down-antiup, up-antistrange, and strange-antistrange  luminosities.
 %
@@
 %
-It is also worth noting the PDF error reduction for the quark-quark luminosity at high invariant masses,
-which will feed into searches for new heavy particles at the TeV scale driven by quark-initiated scattering.
+It is also worth noting the PDF error reduction for the quark-quark luminosity at
+high invariant masses,
+which will feed into searches for new heavy particles at the TeV scale
+driven by quark-initiated scattering.
+%
+Luminosities related to the strange PDF are those mostly
+improved, such as the $u\bar{s}$ channel which provides a significant
+contribution to inclusive $W^+$ production at the LHC.
 
@@
 The studies presented in Sects.~\ref{sec:pdf4lhc21} (for PDF4LHC21)
-and~\ref{sec:nnpdf40} (for NNPDF4.0) treated, from the point of view
+and~\ref{sec:nnpdf40} (for NNPDF4.0) treat, from the point of view
 of PDF constraints, the neutrino scattering target
@@
 %
-They hence neglected both nuclear modifications
-and non-isoscalar effects.
+They hence neglect both nuclear modifications and non-isoscalar effects.
 %
-We now revisit these analyses but accounting for the fact that the target materials
+We now revisit these analyses but accounting for the fact that the target material
 in the FASER$\nu$2 and AdvSND experiments is tungsten, with $A=184$.
@@
 of Sects.~\ref{sec:pdf4lhc21} to EPPS1, a global determination of nuclear PDFs
-that accounts for the constraints of existing datasets involving nuclei as target or projectiles.
+that accounts for the constraints of existing datasets involving nuclei as target or projectiles,
+and based on the CT18 set as proton boundary condition.
 %
@@
 and nCTEQ15HQ~\cite{Duwentaster:2022kpv}.
-%
+
 The application of profiling to EPPS21 follows the same strategy as that
@@
 Given that the measured event rates depend on both the proton PDFs and the nuclear modifications,
-when profiling EPPS21 we also account for the Hessian sets associated to the CT18 proton
+when profiling EPPS21 we also account for the Hessian sets associated to the proton
 PDF dependence.
@@
  %
- The FPF dataset is in this case composed by FASER$\nu$2 and AdvSND, given that FLArE
- adopts a different target material.
+ The FPF dataset is in this case composed by FASER$\nu$2 and AdvSND.
  %
- Also in this case of nuclear PDFs one finds that the impact of FPF structure function measurements
+ One finds that the impact of FPF structure function measurements
  is most important for the strange PDF, and to a lesser extent for the up and down
@@
  case, one reason explaining the observed differences is the choice of a larger tolerance factor $T$ in EPPS21
- as compared to PDF4HC21, which effectively reduces the impact of new data.
+ as compared to PDF4HC21, which effectively reduces the impact of new data in the fit.
  %
- Another reason is the more restrictive functional form adopted in EPPS21 as compared
+ Another potential reason is the more restrictive functional form adopted in EPPS21 as compared
  to the PDF sets entering PDF4LHC21, a consequence of the smaller dataset available
@@
  may provide a more  robust estimate of the impact of FPF structure function data
- on nuclear PDFs.
+ on nPDFs.
  %
- Additional results for the Hessian profiling of EPPS21 are presented in App.~\ref{app:nPDF_impact_appendix}.
+ Additional results for the profiling of EPPS21 are presented in App.~\ref{app:nPDF_impact_appendix}.

### 2023-09-04 paper/scripts/lumis.py

@@ -16,13 +16,13 @@ import scipy.special as special
 #---------------------------------------------------------
 #---------------------------------------------------------
 # General plot settings
-nmx = 30
+nmx = 20
 mxmin = 9 # GeV
 mxmax = 7000 # GeV
 sqrts = 14000 # GeV, center of mass energy
 s = math.pow(sqrts,2.0)
 # Integration settings
-epsrel=5e-3
+epsrel=1e-3
 
 #------------------------------------------------------------------------------------
 #------------------------------------------------------------------------------------
@@ -408,8 +408,8 @@ ylabel=[r"$\mathcal{L}_{gg}/\mathcal{L}_{gg}^{(\rm ref)}$",\
         r"$\mathcal{L}_{s\bar{s}}/\mathcal{L}_{s\bar{s}}^{(\rm ref)}$"]
 
 # y axis ranges
-yranges=[[0.90,1.15],[0.95,1.06],[0.90,1.15],\
-         [0.90,1.15],[0.95,1.06],[0.90,1.15]]
+yranges=[[0.90,1.10],[0.95,1.06],[0.90,1.10],\
+         [0.90,1.10],[0.95,1.06],[0.90,1.12]]
 
 for ilumi in range(nlumi):
 

### 2023-09-04 paper/FPF-WG1.tex
paper revision almost complete

@@
 
-%%%%% raquel: color marks %%%%%
-%\usepackage{color} 
-\newcommand{\raq}[1]{{\bf\color{orange} #1}}  
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%% jaco: wider spacing in tables %%%%%
-\renewcommand{\arraystretch}{1.7}
-\def\lra#1{\overset{\text{\scriptsize$\leftrightarrow$}}{#1}}
-
 \begin{document}
@@
 Max Fieg$^{1}$, Tommaso Giani$^{2,3}$, Peter Krack$^{2,3}$, Toni M\"akel\"a$^{4}$, Juan M. Cruz-Martinez$^{5}$, \\[0.1cm]
-    Tanjona Rabemananjara$^{2,3}$, and Juan Rojo$^{2,3}$.
+    Tanjona Rabemananjara$^{2,3}$, and Juan Rojo$^{2,3}$
   }\\
@@
  %
- We demonstrate that LHC neutrino data enables improved theoretical
- predictions for core processes at the HL-LHC, such as Higgs and weak gauge (di)boson production.
+ We show that LHC neutrino data enables improved theoretical
+ predictions for core processes at the HL-LHC, such as Higgs and weak gauge
+ boson production.
 %
- Our analysis highlights how exploiting the LHC neutrino beam effectively
-provides CERN with a new ``Neutrino-Ion Collider''.
+ Our analysis demonstrates that exploiting the LHC neutrino beam effectively
+ provides CERN with a ``Neutrino-Ion Collider''
+ without  requiring modifications in its accelerator infrastructure
 
@@
 \tableofcontents
-
 \input{sec-introduction}
@@
 \input{sec-summary}
-
 \appendix

### 2023-09-04 paper/app-faser.tex
some polishing
paper revision almost complete

--- 2023-08-22 paper/app-faser.tex
@@
 
+The same procedure applied to the FPF experiments in Sect.~\ref{sec:pdf4lhc21}
+can also be used in the case of FASER$\nu$, for which pseudo-data is generated
+for a Run III integrated
+luminosity of $\mathcal{L}=150$ fb$^{-1}$.
 %
-Fig.~\ref{fig:profiling_FASERv2_vs_FASERv} shows a comparison of the impact 
-that FASER$\nu$2 and FASER$\nu$ pseudodata have in PDF profiling, illustrating 
-the improvement in precision obtainable with FASER$\nu$2.
+As indicated by Table~\ref{tab:integrated_rates}, by the end of Run III, one expects
+that FASER$\nu$ will have recorded around 300 and 900 electron- and muon-neutrinos
+respectively corresponding to deep-inelastic scattering events, of which around 50
+and 140 respectively are associated to charm-tagged events.
+%
+These projected event rates can be compared with the expectations for FASER$\nu$2, which predict
+an increase in statistics of more than two orders of magnitude.
+
+Fig.~\ref{fig:FASERnu2_vs_FASERnu} presents a similar comparison as that of
+Fig.~\ref{fig:FASERnu2_baseline} now between the projected PDF impact of FASER$\nu$2 and that of
+FASER$\nu$.
+%
+One finds that neutrino DIS measurements at FASER$\nu$ are unable to improve
+PDF uncertainties as compared to the baseline scenario encapsulated by PDF4LHC21.
+%
+The reason is two-fold: the much smaller event rates as compared to FASER$\nu$2,
+and the reduced coverage of the $(x,Q^2)$ phase space shown in Fig.~\ref{fig:fasernu2_muon}.
+%
+The differences in PDF sensitivity between FASER$\nu$ and FASER$\nu$2 in
+Fig.~\ref{fig:FASERnu2_vs_FASERnu} illustrate
+the  importance of realising the FPF in order to exploit the full physics potential enabled 
+by LHC neutrinos for QCD and hadron structure studies.
 
@@
 \includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_s_ratio.pdf}
-\caption{
-A comparison of the effect of FASER$\nu$ and FASER$\nu2$ pseudodata in profiling, 
-assuming only statistical uncertainties in the case of both experiments.
+\caption{Same as  Fig.~\ref{fig:FASERnu2_baseline} (statistical uncertainties only), comparing
+  the projected PDF impact of FASER$\nu$2 with that of FASER$\nu$, in the latter
+  case assuming the Run III integrated
+luminosity of $\mathcal{L}=150$ fb$^{-1}$.
 }
-\label{fig:profiling_FASERv2_vs_FASERv}
+\label{fig:FASERnu2_vs_FASERnu}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+It should be emphasized that the lack of PDF sensitivity displayed in Fig.~\ref{fig:FASERnu2_vs_FASERnu}
+does not imply that measuring DIS structure functions at FASER$\nu$ will not provide useful information.
+%
+First of all, our procedure assumes perfect compatibility between current data and the projected DIS
+neutrino measurements at the LHC, something which remains to be demonstrated experimentally.
+%
+Second, FASER$\nu$ still covers a region of neutrino energies unexplored by previous experiments, hence providing
+a new validation of our QCD calculations and of neutrino interactions at the TeV scale.
+%
+Third, it would represent a non-trivial proof-of-concept that LHC neutrino differential measurements can be
+unfolded to the cross-section level to be used in  theoretical
+interpretations, paving the way and demonstrating the feasibility of subsequent neutrino DIS
+measurements at the FPF experiments.

### 2023-09-04 paper/app-nuclearPDFs.tex
some polishing
paper revision almost complete

@@
-\clearpage
 \section{Additional nPDF impact studies}
@@
 
-The impact of the FPF structure function measurements on the
+The impact of FPF structure function measurements on the
 EPPS21 nuclear PDF determination has been studied in Sect.~\ref{sec:nuclearPDFs}.
@@
 %
-Figs.~\ref{fig:EPPS21_nocharm} and~\ref{fig:EPPS21_nochargeID} display
+Fig.~\ref{fig:EPPS21_nochargeID} displays
 the analogous comparisons as in Figs.~\ref{fig:FASERnu2_nocharm}
-and~\ref{fig:EPPS21_nochargeID} in the case of EPPS21.
+and~\ref{fig:FASERnu2_nochargeID} in the case of EPPS21.
 %
@@
 Second, not being able to identify the charge of the outgoing final-state lepton
-does not affect sizable the baseline results, with the possible exception
+does not markedly affect  the baseline results, with the possible exception
 of the down valence quark PDF.
@@
 \includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{Same as Fig.~\ref{fig:FASERnu2_nocharm} in the case of EPPS21.
-}
-\label{fig:EPPS21_nocharm}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\centering
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}\\
 \includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
@@
 \includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{Same as Fig.~\ref{fig:FASERnu2_nochargeID} in the case of EPPS21.
+\caption{Same as Fig.~\ref{fig:FASERnu2_nocharm} (upper panels)
+  and  Fig.~\ref{fig:FASERnu2_nochargeID} (bottom panels) in the case of EPPS21.
 }

### 2023-09-04 paper/sec-introduction.tex
paper revision almost complete

@@
 of nucleons and nuclei~\cite{Ethier:2020way,Gao:2017yyd,Kovarik:2019xvh},  in particular
-concerning quark/antiquark  flavour separation and
+concerning (anti)quark  flavour separation and
 strangeness~\cite{NuTeV:2007uwm,CCFR:1994ikl,Faura:2020oom,Alekhin:2014sya}.
@@
 
-These results demonstrate that the availability of far-forward neutrino detection
+Our results demonstrate that the availability of far-forward neutrino detection
 at the LHC effectively
@@
 
-We note that, together with this paper,
-we release the generated  DIS structure functions for the LHC
-neutrino experiments as well as the resulting PDF sets, which may be helpful
+Together with this paper,
+we release the generated  DIS structure function pseudo-data for the LHC
+neutrino experiments, which may be helpful
 to inform related studies of high-energy

### 2023-09-04 paper/sec-dis-pseudodata.tex
Minor corrections
revision completed

@@
 %
+ expressed
  in terms of a convolution of partonic scattering cross-sections  $C_{i,j}^{\nu N}(x,\alpha_s)$ and
@@
  affected by theoretical uncertainties in the production mechanism, but
- provide also predictions for electron-neutrino scattering.
+ provide also predictions for the subdominant electron-neutrino structure functions.
 
@@
 \ee
-The systematic uncertainty in event yield caused by $\delta E_\ell$ is then $\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)}$.
+The absolute systematic uncertainty in event yield caused by $\delta E_\ell$ is then $\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)}$.
 %

### 2023-09-04 paper/sec-introduction.tex
Added mention that xFitter is also open-source + small typo fix

@@
 (for tungsten nuclei)
-within {\sc\small xFitter}~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web},
+within the {\sc\small xFitter}~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web} open-source QCD analysis framework,
 as well as with the direct inclusion in the open-source NNPDF4.0 fitting framework~\cite{NNPDF:2021uiq}.
@@
 Our analysis reveals that  LHC neutrino structure functions can provide  stringent constraints
-on the light quark and antiquark PDFs, specially on the up and down
+on the light quark and antiquark PDFs, especially on the up and down
 valence quarks and on strangeness, as compared to state-of-the-art global analyses.

### 2023-09-04 paper/sec-dis-pseudodata.tex
Fixed a few sentences where fiducial volume was given units of mass, used forms like 'fiducial volume corresponding to a X kg detector'

@@
   %
-   In the case of FLArE, we consider projections for both
-  for 10 ton and 100 fiducial volume detectors.
+   In the case of FLArE, we consider projections for fiducial volumes corresponding to both 10 and 100 tonne detectors.
   %
@@
 %
-With a total fiducial volume of 830 kg and length of 35 cm, it is composed by tungsten plates,
+With a total fiducial volume corresponding to a 830 kg detector with a length of 35 cm, it is composed by tungsten plates,
 where neutrino scattering takes place, interleaved with nuclear emulsions and electronic tracker

### 2023-09-04 paper/sec-dis-pseudodata.tex
Ton -> tonne (metric unit)

@@
 detector, composed by interleaved emulsion and tungsten plates and
-adding up to a mass of 1.1 tons with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 80~{\rm cm}$.
+adding up to a mass of 1.1 tonnes with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 80~{\rm cm}$.
 %
@@
 %
-This is proposed 20-ton neutrino experiment located on the LOS
+This is proposed 20-tonne neutrino experiment located on the LOS
 of the LHC neutrino beam to be installed in the FPF cavern.
@@
  The target region of the detector, where the neutrino interactions take place, is made of thin sensitive layers 
- interleaved with tungsten plates, for a total mass of 5 tons and fiducial length of 50 cm.
+ interleaved with tungsten plates, for a total mass of 5 tonnes and fiducial length of 50 cm.
  %
@@
 
- With an expected fiducial (active) mass of 10 tons (30 tons) and a length of 7 m, FLArE will
+ With an expected fiducial (active) mass of 10 tonnes (30 tonnes) and a length of 7 m, FLArE will
  detect final-state electrons with energies $E_{e}\lsim 2~\rm{TeV}$ and
@@
  Here we present  projections for this baseline design of the experiment, FLArE10,
- as well as for a potential larger variant based on a fiducial mass of 100 ton, which
+ as well as for a potential larger variant based on a fiducial mass of 100 tonnes, which
  is known as FLArE100.
@@
 In the case of the FLArE detector, we display results for two proposed options with fiducial
-masses of 10 and 100 tons.
+masses of 10 and 100 tonnes.
 %

### 2023-09-04 paper/sec-results.tex
revision completed
Ton -> tonne (metric unit)

@@
 %
-Its Hessian representations are obtained by means of the reduction methodologies developed in~\cite{Gao:2013bia,Carrazza:2015aoa}.
+Its Hessian representations are obtained by means of the reduction methodologies developed in~\cite{Gao:2013bia,Carrazza:2015aoa,Carrazza:2016htc}.
 %
@@
 %
-In the latter case, we consider both the 10 ton and 100 ton variants.
+In the latter case, we consider both the 10 tonne and 100 tonne variants.
 %

### 2023-09-04 paper/tables/detectors.tex
Fixed a few sentences where fiducial volume was given units of mass, used forms like 'fiducial volume corresponding to a X kg detector'
Ton -> tonne (metric unit)

--- 2023-08-31 paper/tables/detectors.tex
@@
 \multirow{3}{*}{FASER$\nu$}  &  \multirow{3}{*}{ $\eta_\nu \ge 8.5$}  &   \multirow{2}{*}{Tungsten}  & \multirow{3}{*}{muons}      &   $E_\ell,E_h \gsim 100$ GeV   &      $\delta E_\ell \sim 30\% $    \\
-&   &   \multirow{2}{*}{(1.1 ton)}  &       &  $\tan \theta_\ell \lsim 0.025$   &
+&   &   \multirow{2}{*}{(1.1 tonnes)}  &       &  $\tan \theta_\ell \lsim 0.025$   &
 $\delta \theta_\ell \sim 0.06$ mrad        \\
@@
 \multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &   \multirow{2}{*}{n/a}    &  $E_\ell,E_h \gsim 20 $ GeV     &    \multirow{2}{*}{n/a}    \\
-  &    &  (0.83 ton)   &  &  $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$         &       \\
+  &    &  (0.83 tonnes)   &  &  $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$         &       \\
 \midrule
@@
 \multirow{3}{*}{FASER$\nu$2}  & \multirow{3}{*}{ $\eta_\nu \ge 8.5$}  & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{muons}     &   $E_\ell,E_h \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
-  &   &  \multirow{2}{*}{(20 ton)}   &       &  $\tan \theta_\ell \lsim 0.05$   &   $\delta \theta_\ell \sim 0.06$ mrad      \\
+  &   &  \multirow{2}{*}{(20 tonnes)}   &       &  $\tan \theta_\ell \lsim 0.05$   &   $\delta \theta_\ell \sim 0.06$ mrad      \\
   &   &     &       &  reco $E_h$ \& charm ID   &  $\delta E_h \sim 30\%$        \\
@@
 \multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{muons}    &  $E_\ell,E_h \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
-  &   &   \multirow{2}{*}{(5 ton)}  &        & $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$     &           \\
+  &   &   \multirow{2}{*}{(5 tonnes)}  &        & $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$     &           \\
   &   &     &       &  reco $E_h$   &           \\
@@
 \multirow{3}{*}{FLArE ({\bf *})}  & \multirow{3}{*}{$\eta_\nu \ge 7.5$} & \multirow{2}{*}{LAr}  & \multirow{3}{*}{muons}  &  $E_\ell,E_h \gsim 2$ GeV, $E_e \lsim 2$ TeV    &    $\delta E_e \sim 5\% $,  $\delta E_\mu \sim 30\% $ \\
-&   &  \multirow{2}{*}{(10 ton)}   &   & $\theta_\mu \lsim 0.025$, $\theta_e \lsim 0.5$ &    $\delta \theta_\ell \sim 15 $ mrad\\
+&   &  \multirow{2}{*}{(10,~100~tonnes)}   &   & $\theta_\mu \lsim 0.025$, $\theta_e \lsim 0.5$ &    $\delta \theta_\ell \sim 15 $ mrad\\
  &   &     &  & reco $E_h$  &    $\delta E_h \sim 30\% $   \\
@@
   %
-  In the case of FLArE, we consider results both
-  for 10 ton and 100 ton fiducial volume detectors.
+  In the case of FLArE, we consider projections for fiducial volumes corresponding to both 10 and 100 tonne detectors.
   \label{tab:FPF_experiments}

### 2023-09-04 paper/sec-dis-pseudodata.tex
British english conventions: Meter for devices, metre for length

@@
 is located in a service tunnel (TI18)
-around 500 meters from the ATLAS interaction point and has been taking data
+around 500 metres from the ATLAS interaction point and has been taking data
 since the  beginning of Run III.
@@
 It is based on the same technology as FASER$\nu$, and hence
-relies on a emulsion-based detector optimised to identify heavy flavor particles, including
+relies on a emulsion-based detector optimised to identify heavy flavour particles, including
 tau leptons and charm and beauty particles, arising from neutrino interactions.
@@
  %
- The use of LAr as a target is beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimeter spatial resolution in all dimensions.
+ The use of LAr as a target is beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimetre spatial resolution in all dimensions.
  %
@@
 %
-The prompt component used in this work was simulated at NLO using {\sc\small POWHEG}~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd} matched to {\sc\small Pythia8}~\cite{Sjostrand:2014zea, Bierlich:2022pfr} for the parton shower and hadronization, and the displaced component was simulated with {\sc\small EPOS-LHC}~\cite{Pierog:2013ria}.
+The prompt component used in this work was simulated at NLO using {\sc\small POWHEG}~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd} matched to {\sc\small Pythia8}~\cite{Sjostrand:2014zea, Bierlich:2022pfr} for the parton shower and hadronisation, and the displaced component was simulated with {\sc\small EPOS-LHC}~\cite{Pierog:2013ria}.
 %
@@
 to a given systematic source, say $\delta E_\ell$, for bin $i$
-to be the mean of the absolute difference between the number of events in this bin for the smeared samples $\{\mathcal{D}_k\}$  and the number of events in this bin for ${\mathcal{D}_0}$ which also serves as a normalization to produce a fractional uncertainty:
+to be the mean of the absolute difference between the number of events in this bin for the smeared samples $\{\mathcal{D}_k\}$  and the number of events in this bin for ${\mathcal{D}_0}$ which also serves as a normalisation to produce a fractional uncertainty:
 \be
@@
 The profiling method applied to Hessian PDF fits is based
-on minimizing a goodness-of-fit error function defined as
+on minimising a goodness-of-fit error function defined as
 \begin{equation}

### 2023-09-04 paper/sec-dis-pseudodata.tex
Changed remaining US->UK english conventions of which I'm aware of

@@
 \ee
-with $s=2m_N E_\nu$ being the neutrino-nucleon center of mass energy squared, $m_N$ the nucleon mass,
+with $s=2m_N E_\nu$ being the neutrino-nucleon centre-of-mass energy squared, $m_N$ the nucleon mass,
 $E_\nu$ the incoming neutrino energy,
@@
 at the upcoming EIC~\cite{Khalek:2021ulf,AbdulKhalek:2021gbh} at the highest
-center-of-mass energies planned, as well as to available fixed-target
+centre-of-mass energies planned, as well as to available fixed-target
 neutral- and charged-current DIS measurements.
@@
       at the FASER$\nu$, FASER$\nu$2, FLArE10(100), and AdvSND experiments, see also Fig.~\ref{fig:fasernu2_muon},
-      compared to that of electron-ion collisions at the EIC for the highest center-of-mass 
+      compared to that of electron-ion collisions at the EIC for the highest centre-of-mass 
       energies $\sqrt{s}$ planned as well as to the coverage of existing neutrino
@@
  \ee
- with $(x_i,Q^2_i,y_i)$ labeling the corresponding bin centers.
+ with $(x_i,Q^2_i,y_i)$ labeling the corresponding bin centres.
  %

### 2023-09-04 paper/sec-dis-pseudodata.tex
Mentioned fred=0.5 in xFitter results with stat+syst uncertainties, and that for EPPS21 we first obtain uncertainties at 90% CL and scale them down to 68% CL afterwards

@@
 % 
- In Sect.~\ref{sec:protonPDFs} we present results for the conservative scenario with
- $f_{\rm red}=1$, but it is
- straightforward to revisit the projections for a more optimistic
- detector performance with $f_{\rm red}< 1$.
+In Sect.~\ref{sec:pdf4lhc21} and Sect.~\ref{sec:nuclearPDFs} we present results with $f_{\rm red}=0.5$, 
+ while the remainder of Sect.~\ref{sec:protonPDFs} assumes the conservative scenario $f_{\rm red}=1$, 
+ but it is straightforward to revisit the projections for a more optimistic detector performance with $f_{\rm red}< 1$.
 
@@
 
-For ensure consistency, the PDF set and other theory settings, such as the perturbative
+To ensure consistency, the PDF set and other theory settings, such as the perturbative
 order and heavy quark scheme, adopted for the evaluation of
@@
 %
-For the Hessian profiling of EPPS21, a value of $T^2 = 20$ is used consistently with~\cite{Eskola:2021nhw}
-for the definition of 68\%  confidence level intervals.
+For the Hessian profiling of EPPS21, a value of $T^2 = 33$ is used consistently with~\cite{Eskola:2021nhw}, and the resulting uncertainties are scaled down by a factor of 1.645 to obtain 68\% confidence level intervals.
 

### 2023-09-04 paper/sec-results.tex
Specified that we use FLArE10 for xFitter results
All TM corrections from proofreading are now there

@@
 %
-In the latter case, we consider both the 10 tonne and 100 tonne variants.
+In the latter case, we consider the 10 tonne variant.
 %
@@
 \centering
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_s_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fpf/fred05fcorr05_FPF_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fpf/fred05fcorr05_FPF_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fpf/fred05fcorr05_FPF_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fpf/fred05fcorr05_FPF_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fpf/fred05fcorr05_FPF_q2_10000_pdf_s_ratio.pdf}
 \caption{
@@
 \centering
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/nuclear_fasernu2/FPF/fred05fcorr05_FPF_q2_10000_pdf_s_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fpf/fred05fcorr05_FPF_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fpf/fred05fcorr05_FPF_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fpf/fred05fcorr05_FPF_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fpf/fred05fcorr05_FPF_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/nuclear_fpf/fred05fcorr05_FPF_q2_10000_pdf_s_ratio.pdf}
 \caption{Same as Fig.~\ref{fig:FPF_combined} now corresponding to the Hessian
- profiling of EPPS21 for a tungsten nucleus.
+ profiling of EPPS21 for a tungsten nucleus, and excluding FLArE contributions.
 }
@@
  For the latter, the projected impact of FPF measurements appears to be somewhat milder
- as in the case of PDF4LHC21, specially once systematic uncertainties are taken into account.
+ as in the case of PDF4LHC21, especially once systematic uncertainties are taken into account.
 

### 2023-09-05 paper/FPF-WG1.tex
revision completed
some minor updates ; added NNPDF40 baseline chi2 ; added cern preprint number

@@
 \begin{flushright}
-Nikhef-2023-aaa\\
+Nikhef-2023-009, CERN-TH-2023-165\\
 \end{flushright}
@@
   {\small
-Max Fieg$^{1}$, Tommaso Giani$^{2,3}$, Peter Krack$^{2,3}$, Toni M\"akel\"a$^{4}$, Juan M. Cruz-Martinez$^{5}$, \\[0.1cm]
-    Tanjona Rabemananjara$^{2,3}$, and Juan Rojo$^{2,3}$
+    Juan M. Cruz-Martinez$^{1}$, Max Fieg$^{2}$, Tommaso Giani$^{3,4}$, Peter Krack$^{3,4}$, Toni M\"akel\"a$^{5}$,  \\[0.1cm]
+    Tanjona Rabemananjara$^{3,4}$, and Juan Rojo$^{3,4}$
   }\\
@@
 {\it \small
-    ~$^1$ Department of Physics and Astronomy, University of California, Irvine, CA 92697 USA  \\[0.1cm]
-    ~$^2$Department of Physics and Astronomy, Vrije Universiteit, NL-1081 HV Amsterdam\\[0.1cm]
-    ~$^3$Nikhef Theory Group, Science Park 105, 1098 XG Amsterdam, The Netherlands\\[0.1cm]
-    ~$^4$National Centre for Nuclear Research, Pasteura 7, Warsaw, PL-02-093, Poland \\[0.1cm]
-    ~$^5$CERN, Theoretical Physics Department, CH-1211 Geneva 23, Switzerland \\[0.1cm]
+    ~$^1$CERN, Theoretical Physics Department, CH-1211 Geneva 23, Switzerland \\[0.1cm]
+    ~$^2$ Department of Physics and Astronomy, University of California, Irvine, CA 92697 USA  \\[0.1cm]
+    ~$^3$Department of Physics and Astronomy, Vrije Universiteit, NL-1081 HV Amsterdam\\[0.1cm]
+    ~$^4$Nikhef Theory Group, Science Park 105, 1098 XG Amsterdam, The Netherlands\\[0.1cm]
+    ~$^5$National Centre for Nuclear Research, Pasteura 7, Warsaw, PL-02-093, Poland \\[0.1cm]
  }

### 2023-09-05 paper/sec-dis-pseudodata.tex
some minor updates ; added NNPDF40 baseline chi2 ; added cern preprint number

@@
 $E_\nu$ the incoming neutrino energy,
-and the inelasticity is $y=Q^2/(2x m_n E_{\nu})$.
+and $y=Q^2/(2x m_n E_{\nu})$ the inelasticity.
 %
@@
 \label{eq:W2_invmass}
-W^2 = \lp m_N^2 + Q^2 \frac{(1-x)}{x} \rp \gsim \lp 2\,{\rm GeV} \rp^2\, ,
+W^2 = \lp m_N^2 + Q^2 \frac{(1-x)}{x} \rp \gsim \lp 2\,{\rm GeV} \rp^2\, .
 \ee
-and in addition here we  restrict ourselves to the DIS region with perturbative momentum
-transfers $Q^2 \gsim 2$ GeV$^2$, such that
- structure functions can be decomposed as
+In addition, here we  restrict ourselves to the DIS region with perturbative momentum
+transfers $Q^2 \gsim 2$ GeV$^2$, such that the structure functions can be decomposed as
 \be
@@
 %
-This is proposed 20-tonne neutrino experiment located on the LOS
+This is a proposed 20-tonne neutrino experiment located on the LOS
 of the LHC neutrino beam to be installed in the FPF cavern.
@@
  at the FPF with a coverage in neutrino pseudorapidity of $7.2 \le \eta_\nu \le 8.4$
- (hence off-LOS, same as SND@LHC) and a near detector installed somewhere else in the LHC
+ (i.e., off-LOS, same as SND@LHC) and a near detector installed somewhere else in the LHC
  complex and covering the range $4 \le \eta_\nu \le 5$.
@@
   \ee
-  with charm production cross-sections discussed in~\cite{Faura:2020oom}
+  with the charm production cross-sections discussed in~\cite{Faura:2020oom}
   and references therein.
@@
 Predictions for the fitted observables Eq.~(\ref{eq:theory_dis_projections}) are evaluated
-with NNPDF4.0 NNLO and included
-directly in the same alongside all other datasets in the global fit.
+with NNPDF4.0 NNLO and included in the corresponding PDF determination
+alongside all other datasets already present in the global fit.
 %

### 2023-09-05 paper/sec-introduction.tex
some minor updates ; added NNPDF40 baseline chi2 ; added cern preprint number

@@
 
-As well known~\cite{Conrad:1997ne,Mangano:2001mj},
+As is well known~\cite{Conrad:1997ne,Mangano:2001mj},
 measurements of neutrino structure functions~\cite{Candido:2023utz} in deep-inelastic scattering
@@
 different flavour combinations as compared to neutral-current charged-lepton DIS,
-being hence fully complementary.
+hence being fully complementary.
 %
@@
 suggests that the LHC  neutrino beam may be utilized
-as a precise probe of hadron structure.
+as a precise probe of the hadron structure.
 %

### 2023-09-05 paper/sec-results.tex
some minor updates ; added NNPDF40 baseline chi2 ; added cern preprint number

@@
 Indeed, while systematic uncertainties somewhat degrade the PDF sensitivity,
-they do not wash it out for none of the quark PDFs.
+they do not wash it out for any of the quark PDFs.
 %
@@
   \midrule
-  $\chi^2$ &  \multirow{4}{*}{Global}  & 1.170 &  1.161  & 1.145  \\
+  $\chi^2/n_{\rm dat}$ &  \multirow{4}{*}{Global}  & 1.170 &  1.161  & 1.145  \\
   $\la E_{\rm tr}\ra_{\rm rep}$
@@
   & & 2.360    &   2.332  & 2.311  \\
-  $\la \chi^2\ra_{\rm rep}$
+  $\la \chi^2/n_{\rm dat}\ra_{\rm rep}$
   & &   1.194   &    1.187    & 1.169  \\
   \midrule
-  \multirow{8}{*}{$\chi^2$}
+  \multirow{8}{*}{$\chi^2/n_{\rm dat}$}
   & DIS neutral-current                     &  1.220    &  1.230    &   1.220   \\
@@
   & Direct photon production                 &  0.740  &   0.729    &    0.744  \\
-  & FPF (total)                 &  -  &   1.192    &   0.919   \\
+  & FPF (total)                 &  1.301 / 0.958 &   1.192    &   0.919   \\
   \bottomrule
@@
   %
-  From top to bottom: total $\chi^2$, average
+  From top to bottom: total $\chi^2/n_{\rm dat}$, average
   over replicas of the training and validation figures of merit
   $\la E_{\rm tr}\ra_{\rm rep}$ and $\la E_{\rm val}\ra_{\rm rep}$,
-  average $\chi^2$ over replicas $\la \chi^2\ra_{\rm rep}$,
-  $\chi^2$ for datasets grouped by process.
+  average $\chi^2/n_{\rm dat}$ over replicas $\la \chi^2/n_{\rm dat}\ra_{\rm rep}$,
+  $\chi^2/n_{\rm dat}$ for datasets grouped by process.
   %
-  The last row displays the $\chi^2$ obtained for the combined FPF dataset.
+  The last row displays the $\chi^2/n_{\rm dat}$ obtained for the combined FPF dataset.
+  For the baseline fit we present both the value computed with only statistical error
+  and also adding the systematics so that it can be compared with both fits. 
   \label{tab:chi2_nnpdf40_baseline}
@@
 %
-The last row displays the $\chi^2$ obtained for the combined FPF dataset,
-for which one finds $\chi^2 \sim 1$ up to fluctuations, consistent
+The last row displays the $\chi^2/n_{\rm dat}$ obtained for the combined FPF dataset,
+for which one finds $\chi^2/n_{\rm dat} \sim 1$ up to fluctuations, consistent
 with the fact that the FPF pseudo-data
@@
 %
-In particular, the $\chi^2$ of the available (non-FPF) DIS neutral-current and charged-current
+In particular, the $\chi^2/n_{\rm dat}$ of the available (non-FPF) DIS neutral-current and charged-current
 datasets changes from 1.220 and 0.904 in NNPDF4.0 to 1.220 and 0.913 in the fit
@@
 %
-A moderate increase is found to the $\chi^2$ of Drell-Yan processes, from 1.76 to 1.83, possibly
+A moderate increase is found to the $\chi^2/n_{\rm dat}$ of Drell-Yan processes, from 1.76 to 1.83, possibly
 because of the enhanced weight that DIS data carries in this fit variant.
@@
 %
-The improvement quark-antiquark luminosities at $Q\sim 100$ GeV
-benefits theoretical predictions for $W$ and $Z$ production at the LHC.
+The improved quark-antiquark luminosities at $Q\sim 100$ GeV
+benefit theoretical predictions for $W$ and $Z$ production at the LHC.
 %
@@
 %
-Luminosities related to the strange PDF are those mostly
-improved, such as the $u\bar{s}$ channel which provides a significant
+Unsurprisingly, luminosities related to the strange PDF are those
+which improve the most, such as the $u\bar{s}$ channel which provides a significant
 contribution to inclusive $W^+$ production at the LHC.

### 2023-09-12 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/fcorr05/FASERv2_inclusive/plot.sh
Updating all xFitter results after pseudodata and grid update

@@ -1,0 +1,24 @@
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="fcorr05"
+
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/fcorr05/FPF/plot.sh

@@ -1,0 +1,24 @@
+DETECTOR="FPF"
+DETSIMPLE="FPF"
+UNCLVL="fcorr05"
+
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/fred05/FPF/plot.sh

@@ -1,0 +1,24 @@
+DETECTOR="FPF"
+DETSIMPLE="FPF"
+UNCLVL="fred05"
+
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/fred05fcorr05/FASERv2_charm/plot.sh

@@ -1,0 +1,24 @@
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="fred05fcorr05"
+
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/fred05fcorr05/FLArE10/plot.sh

@@ -1,0 +1,24 @@
+DETECTOR="FLArE10"
+DETSIMPLE="FLArE10"
+UNCLVL="fred05fcorr05"
+
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/statOnly/FASERv/plot.sh

@@ -1,0 +1,24 @@
+DETECTOR="FASER#nu"
+DETSIMPLE="FASERv"
+UNCLVL="statOnly"
+
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/statOnly/FPF/plot.sh

@@ -1,0 +1,25 @@
+DETECTOR="FPF"
+DETSIMPLE="FPF"
+UNCLVL="statOnly"
+
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+PDFLONG="EPPS21nlo_CT18Anlo_W184"
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDFLONG}/ ${PDF}-${DETECTOR}-${UNCLVL}
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/PDF4LHC21/fcorr05/FASERv2/plot.sh

@@ -1,0 +1,27 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="fcorr05"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:../../statOnly/${DETSIMPLE}/output:"BL+${DETECTOR}, stat" profile:output:"BL+${DETECTOR}, stat+syst"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/PDF4LHC21/fred05/FPF/plot.sh

@@ -1,0 +1,27 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FPF"
+DETSIMPLE="FPF"
+UNCLVL="fred05"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:../../statOnly/${DETSIMPLE}/output:"BL+${DETECTOR}, stat" profile:output:"BL+${DETECTOR}, stat+syst"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/PDF4LHC21/fred05fcorr05/AdvSND/plot.sh

@@ -1,0 +1,27 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="AdvSND"
+DETSIMPLE="AdvSND"
+UNCLVL="fred05fcorr05"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:../../statOnly/${DETSIMPLE}/output:"BL+${DETECTOR}, stat" profile:output:"BL+${DETECTOR}, stat+syst"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/PDF4LHC21/statOnly/AdvSND/plot.sh

@@ -1,0 +1,25 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter
+#    sh plot.sh
+
+DETECTOR="AdvSND"
+DETSIMPLE="AdvSND"
+UNCLVL="statOnly"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:../FASERv2/output:"BL+FASER#nu2" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/PDF4LHC21/statOnly/FLArE10/plot.sh

@@ -1,0 +1,25 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter
+#    sh plot.sh
+
+DETECTOR="FLArE"
+DETSIMPLE="FLArE10"
+UNCLVL="statOnly"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:../FASERv2/output:"BL+FASER#nu2" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/PDF4LHC21/syst/FPF/plot.sh

@@ -1,0 +1,27 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FPF"
+DETSIMPLE="FPF"
+UNCLVL="syst"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:../../statOnly/${DETSIMPLE}/output:"BL+${DETECTOR}, stat" profile:output:"BL+${DETECTOR}, stat+syst"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/gitAdder.sh

@@ -50,9 +50,9 @@ for pdf in ${pdfs[@]}; do
         declare -a fred05fcorr05Dirs=("AdvSND" "FLArE100" "FLArE10" "FPF" "FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination")
     else
         declare -a statOnlyDirs=("AdvSND" "FLArE100" "FLArE10" "FPF" "FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination")
-        declare -a systDirs=("FPF" "FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination")
-        declare -a fred05Dirs=("FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination")
-        declare -a fcorr05Dirs=("FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination")
+        declare -a systDirs=("FASERv2" "FPF")
+        declare -a fred05Dirs=("FASERv2" "FPF")
+        declare -a fcorr05Dirs=("FASERv2" "FPF")
         declare -a fred05fcorr05Dirs=("AdvSND" "FLArE100" "FLArE10" "FPF" "FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination")
     fi
 

### 2023-09-12 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/fred05fcorr05/FLArE100/plot.sh
Updating all xFitter results

@@ -1,0 +1,24 @@
+DETECTOR="FLArE100"
+DETSIMPLE="FLArE100"
+UNCLVL="fred05fcorr05"
+
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/statOnly/AdvSND/plot.sh

@@ -1,0 +1,24 @@
+DETECTOR="AdvSND"
+DETSIMPLE="AdvSND"
+UNCLVL="statOnly"
+
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/statOnly/FLArE10/plot.sh

@@ -1,0 +1,24 @@
+DETECTOR="FLArE"
+DETSIMPLE="FLArE10"
+UNCLVL="statOnly"
+
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/PDF4LHC21/fcorr05/FASERv2_inclusive/plot.sh

@@ -1,0 +1,27 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="fcorr05"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/PDF4LHC21/fcorr05/FPF/plot.sh

@@ -1,0 +1,27 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FPF"
+DETSIMPLE="FPF"
+UNCLVL="fcorr05"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:../../statOnly/${DETSIMPLE}/output:"BL+${DETECTOR}, stat" profile:output:"BL+${DETECTOR}, stat+syst"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/PDF4LHC21/fred05/FASERv2/plot.sh

@@ -1,0 +1,27 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="fred05"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:../../statOnly/${DETSIMPLE}/output:"BL+${DETECTOR}, stat" profile:output:"BL+${DETECTOR}, stat+syst"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/PDF_profiling/PDF4LHC21/fred05fcorr05/FASERv2_inclusive/plot.sh

@@ -1,0 +1,27 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="fred05fcorr05"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-12 xFitter/gitAdder.sh

@@ -42,7 +42,7 @@ declare -a xFrunFiles=("constants.yaml" "parameters.yaml" "steering.txt" "plot.s
 declare -a xFprelFiles=("constants.yaml" "parameters.yaml" "steering.txt" "run.sh")
 for pdf in ${pdfs[@]}; do
 
-    if [[ ${pdf}=="PDF4LHC21" ]]; then
+    if [[ "${pdf}" == "PDF4LHC21" ]]; then
         declare -a statOnlyDirs=("FASERv" "AdvSND" "FLArE100" "FLArE10" "FPF" "FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination")
         declare -a systDirs=("FPF" "FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination" )
         declare -a fred05Dirs=("FPF" "FASERv2" "FASERv2_nochargediscrimination" "FASERv2_inclusive" "FASERv2_inclusive_nochargediscrimination" "FASERv2_charm" "FASERv2_charm_nochargediscrimination")
@@ -82,13 +82,13 @@ for pdf in ${pdfs[@]}; do
         git add ${profilingpath}/${pdf}/${unctype}/clean.sh
         for xFrunFile in ${xFrunFiles[@]}; do
             git add ${profilingpath}/${pdf}/${unctype}/${subDir}/${xFrunFile}        
-            git add ${profilingpath}/${pdf}/${unctype}/${subDir}/${unctype}_`echo ${subDir} | sed 's/_.*//'`_q2_10000_pdf_dv_ratio.pdf
-            git add ${profilingpath}/${pdf}/${unctype}/${subDir}/${unctype}_`echo ${subDir} | sed 's/_.*//'`_q2_10000_pdf_g_ratio.pdf
-            git add ${profilingpath}/${pdf}/${unctype}/${subDir}/${unctype}_`echo ${subDir} | sed 's/_.*//'`_q2_10000_pdf_Sea_ratio.pdf
[…]

### 2023-09-13 paper/tables/acceptance.tex
added cut table

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-----------------------------------------------------------------
\begin{table}[t]
  \centering
  \small
  \renewcommand{\arraystretch}{1.70}
  \begin{tabularx}{0.8\textwidth}{p{0.3\textwidth}|c|c|c}
    \toprule
    Detector & Before Cuts & DIS Cut & Acceptance Cut \\
    \midrule
    \midrule
    FASER$\nu$ & 1.2k , 4.1k & 1.2k , 4.1k & 0.61k , 1.8k \\
    SND@LHC & 0.28k , 0.86k & 0.28k , 0.86k & 0.25k , 0.70k \\
    \midrule
    \midrule
    FASER$\nu$2 & 270k , 980k & 270k , 980k  & 172k , 510k \\
    AdvSND-far & 19k , 66k & 19k , 66k & 17k , 56k\\
    FLArE10 & 65k , 202k & 65k , 202k  & 64k , 114k \\
    FLArE100 & 427k , 1.3M &427k , 1.3M  & 420k , 680k \\
    \bottomrule
  \end{tabularx}
  \vspace{0.2cm}
\caption{Cut table showing the impact on the event yield after employing DIS cuts, $W^2 > 4{\rm GeV}^2$ and $Q^2 > 2{\rm GeV}^2$, and experimental acceptances from Table~\ref{tab:FPF_experiments}. The first number for each entry is the numer of $\nu_e + \bar{\nu}_e$ events and the second is for $\nu_{\mu} + \bar{\nu}_{\mu}$.  For the region of parameter space that we study, DIS cuts remove very few events ($\lesssim 1\%$), while acceptance cuts depend on the detector but can remove as many as 50$\%$.}
\label{tab:acceptance}
\end{table}
%-----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-09-13 paper/sec-dis-pseudodata.tex
added cut table
felix comments, event yields

@@
 and can also identify charm-tagged events.
+To identify the charge of the lepton from a neutrino interaction, the lepton is required to pass through the FASER spectrometer.
+This imposes an angular requirement on the outgoing charged lepton, which we show in Table~\ref{tab:FPF_experiments}.
+Also, to identify a DIS interaction the emulsion detector requires at least 5 charged tracks to emerge from the interaction vertex.
+We implement this in our simulations by requiring a minimum hadronic energy when calculating the yield.
 
@@
  as well as for a potential larger variant based on a fiducial mass of 100 tonnes, which
- is known as FLArE100.
+ is known as FLArE100. While FLArE100 is not one of the currently proposed FPF experiments, we include it for illustration purposes.
  %
@@
 
-The incoming neutrino fluxes of~\cite{Kling:2021gos} account for the geometry
+The incoming neutrino fluxes of Ref.~\cite{Kling:2021gos} account for the geometry
 and neutrino pseudo-rapidity $\eta_\nu$ coverage of the considered detector and
@@
 %
-In comparison with~\cite{Kling:2021gos}, in addition to the updated charmed hadron production,
+In comparison with Ref.~\cite{Kling:2021gos}, in addition to the updated charmed hadron production~\cite{Sominka:2023},
 the neutrino flux has been updated to $\sqrt{s} = 13.6~{\rm TeV}$.
@@
 \input{tables/integrated_yields.tex}
+%----------------------------------------------------
+
+%----------------------------------------------------
+\input{tables/acceptance.tex}
 %----------------------------------------------------
@@
 for the  measurements of the double-differential
-muon-neutrino scattering  at FASER$\nu$2.
+muon-neutrino scattering  at FASER$\nu$2. We note that there is a further systematic uncertainty associated to the overall neutrino flux, but we do not include this uncertainty in our estimation.
 %

### 2023-09-13 paper/sec-introduction.tex
felix comments, event yields

@@
 %
-The recent observation of LHC neutrinos~\cite{FASER:2023zcr,SNDLHC:2023pun} by the
-  FASER$\nu$~\cite{FASER:2019dxq} and SND@LHC~\cite{SHiP:2020sos,SNDLHC:2022ihg} far-forward experiments
+The recent observation of LHC neutrinos~\cite{FASER:2023zcr,SNDLHC:2023pun,CERN-FASER-CONF-2023-002} by the
+  FASER~\cite{FASER:2019dxq,FASER:2022hcn} and SND@LHC~\cite{SHiP:2020sos,SNDLHC:2022ihg} far-forward experiments
 demonstrates that this hitherto discarded beam can now be deployed for physics studies.
@@
 This key feature, together with the large event rates,
-up to one million muon neutrinos at the FPF~\cite{Kling:2021gos},
+up to one million muon neutrinos at the FPF~\cite{Anchordoqui:2021ghd,Feng:2022inv},
 suggests that the LHC  neutrino beam may be utilized

### 2023-09-13 paper/tables/detectors.tex
felix comments, event yields

@@
 \multirow{3}{*}{FASER$\nu$}  &  \multirow{3}{*}{ $\eta_\nu \ge 8.5$}  &   \multirow{2}{*}{Tungsten}  & \multirow{3}{*}{muons}      &   $E_\ell,E_h \gsim 100$ GeV   &      $\delta E_\ell \sim 30\% $    \\
-&   &   \multirow{2}{*}{(1.1 tonnes)}  &       &  $\tan \theta_\ell \lsim 0.025$   &
+&   &   \multirow{2}{*}{(1.1 tonnes)}  &       &  $\tan \theta_\ell \lsim 0.025 $ (charge ID)   &
 $\delta \theta_\ell \sim 0.06$ mrad        \\
@@
 \multirow{3}{*}{FASER$\nu$2}  & \multirow{3}{*}{ $\eta_\nu \ge 8.5$}  & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{muons}     &   $E_\ell,E_h \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
-  &   &  \multirow{2}{*}{(20 tonnes)}   &       &  $\tan \theta_\ell \lsim 0.05$   &   $\delta \theta_\ell \sim 0.06$ mrad      \\
+  &   &  \multirow{2}{*}{(20 tonnes)}   &       &  $\tan \theta_\ell \lsim 0.05$ (charge ID)  &   $\delta \theta_\ell \sim 0.06$ mrad      \\
   &   &     &       &  reco $E_h$ \& charm ID   &  $\delta E_h \sim 30\%$        \\

### 2023-09-13 paper/sec-dis-pseudodata.tex
sec 2

@@
 is located in a service tunnel (TI18)
-around 500 metres from the ATLAS interaction point and has been taking data
+around 500 meters from the ATLAS interaction point and has been taking data
 since the  beginning of Run III.
@@
  %
- The use of LAr as a target is beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimetre spatial resolution in all dimensions.
+ The use of LAr as a target is beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimeter spatial resolution in all dimensions.
  %
@@
 
-The incoming neutrino fluxes of Ref.~\cite{Kling:2021gos} account for the geometry
+The incoming neutrino fluxes of~\cite{Kling:2021gos} account for the geometry
 and neutrino pseudo-rapidity $\eta_\nu$ coverage of the considered detector and
@@
 %
-In comparison with Ref.~\cite{Kling:2021gos}, in addition to the updated charmed hadron production~\cite{Sominka:2023},
+In comparison with the calculation from~\cite{Kling:2021gos}, in addition to the updated charmed hadron production~\cite{Sominka:2023},
 the neutrino flux has been updated to $\sqrt{s} = 13.6~{\rm TeV}$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The inclusive yields listed in Table~\ref{tab:integrated_rates}
+differ from the total number of neutrinos interacting within the
+detector volume~\cite{Feng:2022inv,Kling:2021gos} due to both the
+DIS requirements  ($W^2 > 4\,{\rm GeV}^2$ and $Q^2 > 2\,{\rm GeV}^2$)
+and the detector fiducial acceptances summarised in Table~\ref{tab:FPF_experiments}.
+%
+The former is found to be negligible, with DIS cuts removing
+only  $\lesssim 1\%$ of the events, a consequence of the high energy of
+LHC neutrinos.
+%
+The latter is quantified in Table~\ref{tab:acceptance}, displaying
+the number of electron and muon neutrinos before and after applying
+acceptance cuts.
+%
+The acceptance efficiency, defined as the ratio between pre- and post-acceptance
+integrated event yields, depends on the detector and can be up to 50\%.
+%
+For instance, FASER$\nu$2 loses 63\% and 52\% of the interacting electron and muon
+neutrinos respectively due to the acceptance requirements.
+%
+From Table~\ref{tab:FPF_experiments}, is it also worth noting how FLArE has virtually
+perfect acceptance for electron neutrinos.
+%
+One also observes that SND@LHC and AdvSND exhibit relatively
+large acceptance efficiencies, which however are not sufficient to compensate
+the lower number of initial interacting neutrinos due to their off-axis location
+as compared to FASER$\nu$(2) and FLArE.
 

### 2023-09-13 paper/tables/acceptance.tex
felix comments, event yields
sec 2

@@
   \renewcommand{\arraystretch}{1.70}
-  \begin{tabularx}{0.8\textwidth}{p{0.3\textwidth}|c|c|c}
+  \begin{tabularx}{0.99\textwidth}{p{0.26\textwidth}|c|c|c}
     \toprule
-    Detector & Before Cuts & DIS Cut & Acceptance Cut \\
+    \multirow{2}{*}{Detector} & before cuts & after DIS and acceptance cuts  & acceptance efficiency \\
+    & $N_{\nu_e} + N_{\bar{\nu}_e},~N_{\nu_\mu} + N_{\bar{\nu}_\mu}$ &  $N_{\nu_e} + N_{\bar{\nu}_e},~N_{\nu_\mu} + N_{\bar{\nu}_\mu}$ &
+    $N_{\nu_e} + N_{\bar{\nu}_e},~N_{\nu_\mu} + N_{\bar{\nu}_\mu}$\\
     \midrule
     \midrule
-    FASER$\nu$ & 1.2k , 4.1k & 1.2k , 4.1k & 0.61k , 1.8k \\
-    SND@LHC & 0.28k , 0.86k & 0.28k , 0.86k & 0.25k , 0.70k \\
+    FASER$\nu$ & 1.2k, 4.1k  & 610, 1.8k  & 51\%, 44\% \\
+    SND@LHC & 280, 860 & 260, 700 & 92\%, 81\% \\
     \midrule
     \midrule
-    FASER$\nu$2 & 270k , 980k & 270k , 980k  & 172k , 510k \\
-    AdvSND-far & 19k , 66k & 19k , 66k & 17k , 56k\\
-    FLArE10 & 65k , 202k & 65k , 202k  & 64k , 114k \\
-    FLArE100 & 427k , 1.3M &427k , 1.3M  & 420k , 680k \\
+    FASER$\nu$2 & 270k, 980k   & 170k, 510k  & 63\%, 52\%\\
+    AdvSND-far & 19k, 66k &  18k, 56k & 95\%, 85\%\\
+    FLArE10 & 65k, 202k  & 64k, 110k & 98\%, 55\%\\
+    FLArE100 & 427k, 1.3M   & 420k, 670k &98\%, 52\%  \\
     \bottomrule
@@
   \vspace{0.2cm}
-\caption{Cut table showing the impact on the event yield after employing DIS cuts, $W^2 > 4{\rm GeV}^2$ and $Q^2 > 2{\rm GeV}^2$, and experimental acceptances from Table~\ref{tab:FPF_experiments}.
-The first number for each entry is the numer of $\nu_e + \bar{\nu}_e$ events and the second is for $\nu_{\mu} + \bar{\nu}_{\mu}$.
-For the region of parameter space that we study, DIS cuts remove very few events ($\lesssim 1\%$), while acceptance cuts depend on the detector but can remove as many as 50$\%$.}
+  \caption{The number of electron and muon neutrinos interacting within the detector volume,
+    compared with the results after applying the DIS requirements  ($W^2 > 4\,{\rm GeV}^2$ and $Q^2 > 2\,{\rm GeV}^2$)
+    and the experimental acceptances from Table~\ref{tab:FPF_experiments}.
+    %
+    The DIS requirement removes only  $\lesssim 1\%$ of the events, a consequence of the high energy of
+    LHC neutrinos.
+    %
+    The last column displays the acceptance efficiency, defined as the ratio between pre- and post-acceptance
+    integrated event yields.
+    %
+    While the specific efficiencies depend on the experiment, up to 50\% of the neutrinos
+  interacting in the detector volume may fall outside detector acceptance. }
 \label{tab:acceptance}

### 2023-09-14 paper/sec-results.tex
Added sentence about nPDF quark shadowing, added discussions about xFitter+PineAPPL interface to acknowledgements
update chi2 numbers for stats+syst nnpdf fit

@@
   & Direct photon production                 &  0.740  &   0.729    &    0.744  \\
-  & FPF (total)                 &  1.301 / 0.958 &   1.192    &   0.919   \\
+  & FPF (total)                 &  1.301 / 0.923 &   1.192    &   0.888   \\
   \bottomrule

### 2023-09-14 paper/sec-dis-pseudodata.tex
updated yields

@@
 yields, with both FASER$\nu$2 and FLArE100 resulting in around
-40k recorded charm-production events.
+80k recorded charm-production events.
 %
@@
 Fourth, FASER$\nu$2 and FLArE100 lead to the largest absolute
-yields of the FPF experiments, with a total of around 370k and 550k (non-tau) neutrino DIS events respectively, with 37k and 90k
+yields of the FPF experiments, with a total of around 680k and 1.1M (non-tau) neutrino DIS events respectively, with 74k and 170k
 events expected instead for AdvSND-far and for FLArE10.

### 2023-09-15 paper/FPF-WG1.tex
bib
Update FPF-WG1.tex

@@
 \begin{flushright}
-Nikhef-2023-009, CERN-TH-2023-165\\
+Nikhef-2023-009 \\ CERN-TH-2023-165\\
 \end{flushright}
@@
 %
-Here we quantify the impact that neutrino deep-inelastic scattering (DIS) structure function
+Here we quantify the impact that neutrino deep-inelastic scattering (DIS)
 measurements at the LHC would have
@@
 We generate projections for DIS structure functions
-at FASER$\nu$ and SND@LHC,
-as well as at the FASER$\nu$2, AdvSND, and FLArE experiments
+for FASER$\nu$ and SND@LHC at Run III,
+as well as for the FASER$\nu$2, AdvSND, and FLArE experiments
 to be  hosted at the proposed
@@
 %
-These measurements are found to cover a kinematic region in $x$ and $Q^2$ comparable to that
-of the upcoming Electron-Ion Collider, with sub-percent statistical uncertainties
-in the FPF case.
+We determine that up to one million electron- and muon-neutrino DIS interactions
+within detector acceptance can be expected by the end of the HL-LHC,
+covering a kinematic region in $x$ and $Q^2$ overlapping with that
+of the Electron-Ion Collider.
 %
-Including these DIS projections into global (n)PDF analyses, specifically PDF4LHC21, NNPDF4.0,
+Including these DIS projections into
+global (n)PDF analyses, specifically PDF4LHC21, NNPDF4.0,
 and EPPS21,  reveals a significant reduction of PDF uncertainties, in particular
@@
 provides CERN with a ``Neutrino-Ion Collider''
- without  requiring modifications in its accelerator infrastructure
+without  requiring modifications in its accelerator infrastructure.
 
@@
 \bibliographystyle{utphys}
-\bibliography{FPF-WG1}
+%\bibliography{FPF-WG1}
+\input{FPF-WG1.bbl}
 

### 2023-09-15 paper/sec-introduction.tex
intro

@@
 
-As is well known~\cite{Conrad:1997ne,Mangano:2001mj},
-measurements of neutrino structure functions~\cite{Candido:2023utz} in deep-inelastic scattering
+Measurements of neutrino structure functions~\cite{Conrad:1997ne,Mangano:2001mj,Candido:2023utz} in deep-inelastic scattering
 (DIS) are sensitive probes of the parton distributions (PDFs)
@@
 Constraints arising from charged-current neutrino scattering provide information on
-different flavour combinations as compared to neutral-current charged-lepton DIS,
-hence being fully complementary.
+complementary flavour combinations as compared to neutral-current charged-lepton DIS.
 %
@@
 from CHORUS~\cite{CHORUS:2005cpn}, NuTeV~\cite{NuTeV:2001dfo},
-CCFR~\cite{Yang:2000ju}, NOMAD~\cite{NOMAD:2013hbk}, and CDHS~\cite{Berge:1989hr}
+CCFR~\cite{Yang:2000ju}, NOMAD~\cite{NOMAD:2013hbk}, CDHS~\cite{Berge:1989hr},
 and other experiments is routinely  included in global
@@
 
-As compared to  previous experiments,  neutrino
+As compared to  previous neutrino DIS experiments,  neutrino
 scattering at the LHC involves energies of up to a factor 10  higher.
 %
-This key feature, together with the large event rates,
-up to one million muon neutrinos at the FPF~\cite{Anchordoqui:2021ghd,Feng:2022inv},
-suggests that the LHC  neutrino beam may be utilized
-as a precise probe of the hadron structure.
+Furthermore, large event rates are expected, with
+up to one million muon neutrinos interacting at the
+FPF detectors~\cite{Anchordoqui:2021ghd,Feng:2022inv}.
 %
@@
 available neutrino data by an order of magnitude both at small-$x$
-and large-$Q^2$ may be possible.
+and large-$Q^2$ is within reach.
 %
@@
 Here we bridge this gap by quantifying
-the expected impact of  neutrino DIS structure functions at the LHC on proton and nuclear PDFs.
+the expected impact of  LHC neutrino DIS structure functions on proton and nuclear PDFs.
 %
@@
 within the {\sc\small xFitter}~\cite{Alekhin:2014irh, Bertone:2017tig, xFitter:2022zjb, xFitter:web} open-source QCD analysis framework,
-as well as with the direct inclusion in the open-source NNPDF4.0 fitting framework~\cite{NNPDF:2021uiq}.
+as well as with the direct inclusion in the open-source NNPDF4.0 fitting code~\cite{NNPDF:2021uiq}.
 
@@
 We also  find that accounting for the main systematic uncertainties does not significantly
-degrade the sensitivity achieved by baseline fits considering only statistical errors.
+degrade the sensitivity achieved in the baseline fits considering only statistical errors.
 %
@@
 on core processes at the HL-LHC, finding a theory error reduction
-of up to a factor two for selected  Higgs and gauge boson production
-cross-sections.
+of up to a factor two in the most optimistic scenario
+for selected  Higgs and gauge boson production cross-sections.
 
-Our results demonstrate that the availability of far-forward neutrino detection
+Our results demonstrate that the availability of far-forward neutrino detectors
 at the LHC effectively
@@
 we release the generated  DIS structure function pseudo-data for the LHC
-neutrino experiments, which may be helpful
+neutrino experiments, which should be helpful
 to inform related studies of high-energy

### 2023-09-15 paper/sec-introduction.tex
Update sec-introduction.tex

@@
 %
-Due to the lack of dedicated instrumentation in the LHC far-forward region,
+Due to the lack of dedicated instrumentation in the far-forward region,
 until recently these neutrinos avoided detection.
@@
 %
-Current and future LHC neutrinos experiments enable unprecedented scientific opportunities
+Current and future LHC neutrino experiments enable unprecedented scientific opportunities
 for particle and astroparticle physics both within the Standard Model and beyond it,
@@
 available neutrino data by an order of magnitude both at small-$x$
-and large-$Q^2$ is within reach.
+and large-$Q^2$ should be possible.
 %
-However, quantitative projections for the kinematic coverage
+However, quantitative projections for the kinematic reach
 and experimental accuracy expected at current
@@
 Here we bridge this gap by quantifying
-the expected impact of  LHC neutrino DIS structure functions on proton and nuclear PDFs.
+the expected impact of  LHC neutrino structure functions on proton and nuclear PDFs.
 %
@@
 
-Our analysis reveals that  LHC neutrino structure functions can provide  stringent constraints
+Our analysis reveals that  LHC neutrino structure functions provide  stringent constraints
 on the light quark and antiquark PDFs, especially on the up and down
@@
 %
-Sect.~\ref{sec:dis_pseudodata} discusses the procedure
+Sect.~\ref{sec:dis_pseudodata} describes the procedure
 adopted to generate projections for neutrino DIS structure functions at the LHC
@@
 to input variations.
-
-Together with this paper,
-we release the generated  DIS structure function pseudo-data for the LHC
-neutrino experiments, which should be helpful
-to inform related studies of high-energy
-neutrino production and scattering at the LHC.

### 2023-09-15 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

@@
 
-We begin by describing the procedure adopted in order 
+Here we describe the procedure adopted 
 to generate projections for the kinematic coverage
@@
 LHC far-forward neutrino detectors that
-will be considered in the present study and indicate their
+are considered in the present study and indicate their
 acceptance and performance parameters.
@@
 for LHC neutrino structure functions
-and quantify their impact
+and to quantify their impact
  into proton and nuclear PDF determinations.
@@
  the detector fiducial volume, on the one hand,
- and the scattering rates within the same fiducial volume, on the other hand.
+ and the scattering rates within the detector acceptance, on the other hand.
  %
@@
 and can also identify charm-tagged events.
+%
 To identify the charge of the lepton from a neutrino interaction, the lepton is required to pass through the FASER spectrometer.
-This imposes an angular requirement on the outgoing charged lepton, which we show in Table~\ref{tab:FPF_experiments}.
-Also, to identify a DIS interaction the emulsion detector requires at least 5 charged tracks to emerge from the interaction vertex.
-We implement this in our simulations by requiring a minimum hadronic energy when calculating the yield.
+%
+This imposes an angular requirement on the outgoing charged lepton, indicated
+in Table~\ref{tab:FPF_experiments}.
+%
+Also, to identify a DIS interaction the emulsion detector requires at least 5 charged tracks
+to emerge from the interaction vertex.
+%
+We implement this last constraint
+in our simulations by requiring a minimum hadronic energy when calculating the event yields.
 
@@
  scattering angles up to 0.5 mrad,  while final-state muons
- with $\theta_\mu \lsim 0.025$ will be recorded by FASER$\nu$2
- downstream in the FPF cavern.
+ with $\theta_\mu \lsim 0.025$ will be recorded by FASER2.
  %
  Here we present  projections for this baseline design of the experiment, FLArE10,
- as well as for a potential larger variant based on a fiducial mass of 100 tonnes, which
- is known as FLArE100. While FLArE100 is not one of the currently proposed FPF experiments, we include it for illustration purposes.
- %
- Reconstruction of the total energy of the hadronic final state will also
+ as well as for a potential larger variant based on a fiducial mass of 100 tonnes,
+ denoted FLArE100.
+ %
+ While FLArE100 is not one of the currently proposed FPF experiments, we nevertheless
+ include it for illustration purposes.
+ %
+ Reconstruction of the total energy of the hadronic final state will be
  possible. 
@@
  %
- Since the muon energy from a charged-current interaction would be measured by FASER$\nu$2, the
+ Since the muon energy from a charged-current interaction would be measured by FASER2, the
  performance parameters for $E_\mu$ are taken to be the same.

### 2023-09-15 paper/sec-results.tex
update chi2 numbers

@@
   \midrule
-  $\chi^2/n_{\rm dat}$ &  \multirow{4}{*}{Global}  & 1.170 &  1.161  & 1.145  \\
+  $\chi^2/n_{\rm dat}$ &  \multirow{4}{*}{Global}  & 1.17  &  1.16   & 1.15   \\
   $\la E_{\rm tr}\ra_{\rm rep}$
-  &  &  2.256  &  2.242   & 2.215   \\
+  &  &  2.26  &  2.24   & 2.21   \\
   $\la E_{\rm val}\ra_{\rm rep}$
-  & & 2.360    &   2.332  & 2.311  \\
+  & & 2.36    &   2.33  & 2.30  \\
   $\la \chi^2/n_{\rm dat}\ra_{\rm rep}$
-  & &   1.194   &    1.187    & 1.169  \\
+  & &   1.19   &    1.19    & 1.16  \\
   \midrule
   \multirow{8}{*}{$\chi^2/n_{\rm dat}$}
-  & DIS neutral-current                     &  1.220    &  1.230    &   1.220   \\
-  & DIS charged-current                     &   0.904  &   0.942    &  0.913    \\
-  & Drell--Yan (inclusive and one-jet) &  1.76   &   1.830    &   1.830   \\
-  & Top-quark pair production               &  1.230   &   1.220    &  1.250    \\
-  & Single-top production                   &  0.362   &   0.364    &   0.361   \\
-  & Inclusive jet production                &  0.957   &  0.963     &   0.942   \\
-  & Dijet production                        &  2.030    &    2.010   &   2.010   \\
-  & Direct photon production                 &  0.740  &   0.729    &    0.744  \\
-  & FPF (total)                 &  1.301 / 0.923 &   1.192    &   0.888   \\
+  & DIS neutral-current                     &  1.22    &  1.23    &   1.22   \\
+  & DIS charged-current                     &   0.90  &   0.94    &  0.90    \\
+  & Drell--Yan (inclusive and one-jet)      &  1.76   &   1.83    &   1.83   \\
+  & Top-quark pair production               &  1.23   &   1.22    &  1.25     \\
+  & Single-top production                   &  0.36    &   0.36   &   0.37    \\
+  & Inclusive jet production                &  0.96    &  0.96      &   0.94    \\
+  & Dijet production                        &  2.03     &    2.01    &   2.00    \\
+  & Direct photon production                 &  0.74   &   0.73     &    0.73   \\
+  & FPF (total)                 &  1.30  / 0.92  &   1.19     &   0.89    \\
   \bottomrule
@@
 In particular, the $\chi^2/n_{\rm dat}$ of the available (non-FPF) DIS neutral-current and charged-current
-datasets changes from 1.220 and 0.904 in NNPDF4.0 to 1.220 and 0.913 in the fit
-with FPF pseudo-data.
+datasets is unchanged (1.22 and 0.90, respectively) from the baseline to the fit with FPF pseudo-data.
 %

### 2023-09-15 paper/sec-results.tex
Complete numbers on chi2 table

@@
   \midrule
-  $\chi^2/n_{\rm dat}$ &  \multirow{4}{*}{Global}  & 1.17  &  1.16   & 1.15   \\
+  $\chi^2/n_{\rm dat}$ &  \multirow{4}{*}{Global}  & 1.17  &  1.15   & 1.14   \\
   $\la E_{\rm tr}\ra_{\rm rep}$
@@
   $\la \chi^2/n_{\rm dat}\ra_{\rm rep}$
-  & &   1.19   &    1.19    & 1.16  \\
+  & &   1.19   &    1.18    & 1.16  \\
   \midrule
@@
   & DIS neutral-current                     &  1.22    &  1.23    &   1.22   \\
-  & DIS charged-current                     &   0.90  &   0.94    &  0.90    \\
-  & Drell--Yan (inclusive and one-jet)      &  1.76   &   1.83    &   1.83   \\
-  & Top-quark pair production               &  1.23   &   1.22    &  1.25     \\
-  & Single-top production                   &  0.36    &   0.36   &   0.37    \\
+  & DIS charged-current                     &   0.90  &   0.91    &  0.90    \\
+  & Drell--Yan (inclusive and one-jet)      &  1.76   &   1.84    &   1.83   \\
+  & Top-quark pair production               &  1.23   &   1.19    &  1.25     \\
+  & Single-top production                   &  0.36    &   0.37   &   0.37    \\
   & Inclusive jet production                &  0.96    &  0.96      &   0.94    \\
-  & Dijet production                        &  2.03     &    2.01    &   2.00    \\
-  & Direct photon production                 &  0.74   &   0.73     &    0.73   \\
-  & FPF (total)                 &  1.30  / 0.92  &   1.19     &   0.89    \\
+  & Dijet production                        &  2.03     &    2.03    &   2.00    \\
+  & Direct photon production                 &  0.74   &   0.74     &    0.73   \\
+  & FPF (total)                 &  1.29  / 0.92  &   1.10     &   0.89    \\
   \bottomrule

### 2023-09-16 paper/sec-summary.tex
results section
Added TM acknowledgements
Added sentence about nPDF quark shadowing, added discussions about xFitter+PineAPPL interface to acknowledgements
Acknowledge ERN

@@
-\clearpage
 \section{Summary and outlook}
@@
 and Antonia di Crescenzo for information concerning AdvSND.
+%
+We thank Christopher Schwan, Simone Amoroso and Xiaomin Shen for useful 
+discussions regarding the implementation and testing of the 
+{\sc\small PineAPPL} interface to {\sc\small xFitter}.
+%
+We also thank Emanuele R. Nocera for providing the EIC pseudodata.
 
@@
 Fellowship from the Netherlands eScience Center.
+%
+The work of T.~M is supported by the National Science Centre, Poland, research grant No. 2021/42/E/ST2/00031.

### 2023-09-18 paper/sec-introduction.tex
small fixes

@@
 Forward Physics Facility (FPF)~\cite{Anchordoqui:2021ghd,Feng:2022inv} operating
-concurrently with the High-Luminosity LHC~\cite{Azzi:2019yne,Cepeda:2019klc}.
+concurrently with the High-Luminosity LHC (HL-LHC)~\cite{Azzi:2019yne,Cepeda:2019klc}.
 %
@@
 Initial estimates~\cite{Feng:2022inv} indicate that an extension of the coverage of
-available neutrino data by an order of magnitude both at small-$x$
+available neutrino DIS data by an order of magnitude both at small-$x$
 and large-$Q^2$ should be possible.
@@
 
-Our analysis reveals that  LHC neutrino structure functions provide  stringent constraints
+Our analysis reveals that  LHC neutrino structure functions can provide  stringent constraints
 on the light quark and antiquark PDFs, especially on the up and down

### 2023-09-18 paper/sec-summary.tex
small fixes

@@
 %
-Our analysis has involved the generation of
+Our analysis requires the generation of
 DIS pseudo-data fully differential in $x$, $Q^2$, and $E_\nu$
 for the various ongoing and proposed far-forward
-neutrino LHC experiments, including an initial estimate
+neutrino LHC experiments, including the estimate
 of their associated systematic uncertainties.
@@
 %
-We have then assessed the  robustness of the results upon
+We have assessed the  robustness of these results upon
 removing charm-tagged data and final-state lepton-charge
@@
 far-forward and central measurements
-at the HL-LHC, by providing predictions
+at the HL-LHC by providing predictions
 for a range of Higgs and gauge boson production processes,
@@
 %
-This HL-LHC phenomenological analysis suggests that a reduction
+This phenomenological analysis suggests that a reduction
 of the  PDF uncertainty by up to a factor two
-may be within reach for some of these cross-sections,
+may be within reach for some of these cross-sections
 in the most optimistic scenario.
@@
 Furthermore, the predictions from such precise Monte Carlo generators
-should eventually be folded with a full-fledged detector simulation
+should be folded with a full-fledged detector simulation
 in order to robustly determine selection efficiencies, e.g.
@@
 %
-Finally, in this work we have taken the incoming neutrino fluxes
+Finally, here we have taken the incoming neutrino fluxes
 as an external input and neglected any associated uncertainties.
 %
-However, measurements of these fluxes provides
+However, measurements of these fluxes provide
 unique information on light and heavy forward hadron
@@
 We also release
-the generated LHC neutrino DIS structure function pseudo-data
+the generated neutrino structure function pseudo-data
 and the corresponding theory
-calculations, for all scenarios considered in this work.
+calculations, for the different scenarios considered in this work.
 %
@@
 %
-We also thank Emanuele R. Nocera for providing the EIC pseudodata.
+We also thank Emanuele R. Nocera for providing us with the EIC pseudodata.
 

### 2023-09-18 paper/sec-dis-pseudodata.tex
sect 2 revised

@@
 
- In the projections presented in this work, when interpreting the LHC neutrino structure
+ In the projections presented here, when interpreting the LHC neutrino structure
  functions in terms of proton PDFs, we will assume a isoscalar free-nucleon target and neglect
@@
  %
- Eq.~(\ref{eq:NC_chargedlepton}) showcases the complementarity between
+ Comparing Eqns.~(\ref{eq:neutrinoSFs_proton})--(\ref{eq:neutrinoSFs_isoscalar})
+ with Eq.~(\ref{eq:NC_chargedlepton}) showcases the complementarity between
  neutrino and charged-lepton DIS in terms of sensitivity
- to the different flavour PDF decomposition.
+ to different flavour PDF combinations.
  %
@@
  %
- Here we summarise the main features of each of the existing and future
+ Here we summarise the main features of the existing and future
  far-forward detectors considered, in particular concerning
@@
 \label{eq:event_yields}
-N_{\nu_e,{\rm ev}}^{(i)}\lp \nu_e ; E_{{\rm min}}^{(i)} \le E_\nu \le E_{{\rm max}}^{(i)} ,\,
+N_{\nu_e,{\rm ev}}^{(i)}\lp \nu_e ; E_{{\rm min}}^{(i)} \le E_\nu \le E_{{\rm max}}^{(i)} ;\,
 x_{{\rm min}}^{(i)} \le x \le x_{{\rm max}}^{(i)} ;\, Q_{{\rm min}}^{2(i)} \le Q^2 \le Q_{{\rm max}}^{2(i)}\rp
@@
 %
-In comparison with the calculation from~\cite{Kling:2021gos}, in addition to the updated charmed hadron production~\cite{Sominka:2023},
+In comparison with the calculation from~\cite{Kling:2021gos}, in addition to the improved charmed hadron production presented in~\cite{Sominka:2023},
 the neutrino flux has been updated to $\sqrt{s} = 13.6~{\rm TeV}$.
@@
 
- Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the six
+ Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the
  detectors
@@
 in~\cite{Feng:2022inv}, we now account for the
-detector acceptances listed in  Table~\ref{tab:FPF_experiments}.
+detector acceptances listed in  Table~\ref{tab:FPF_experiments}, which reduce
+the event yields by up to a factor 2.
 
@@
       at the FASER$\nu$, FASER$\nu$2, FLArE10(100), and AdvSND experiments, see also Fig.~\ref{fig:fasernu2_muon},
-      compared to that of electron-ion collisions at the EIC for the highest centre-of-mass 
-      energies $\sqrt{s}$ planned as well as to the coverage of existing neutrino
-      (fixed-target) DIS measurements.
-      %
-      Bins with less than 100 events have been excluded fo all the pseudodata except for FASER$\nu$ where we retain
-      bins with at least 10 events.
+      compared to that of electron-ion collisions at the EIC
+      as well as to the coverage of existing neutrino
+      fixed-target DIS measurements.
     }
@@
 The latter is quantified in Table~\ref{tab:acceptance}, displaying
-the number of electron and muon neutrinos before and after applying
+the total number of electron and muon neutrinos before and after applying
 acceptance cuts.
@@
 One also observes that SND@LHC and AdvSND exhibit relatively
-large acceptance efficiencies, which however are not sufficient to compensate
+large acceptance efficiencies, which however are not sufficient to compensate for
 the lower number of initial interacting neutrinos due to their off-axis location
@@
 
-The event yields displayed in Fig.~\ref{fig:fasernu2_muon} determine the associated statistical uncertainty 
-in each bin,
+The event yields displayed in Fig.~\ref{fig:fasernu2_muon} determine the associated
+statistical uncertainty in each bin,
 \be
@@
 to a given systematic source, say $\delta E_\ell$, for bin $i$
-to be the mean of the absolute difference between the number of events in this bin for the smeared samples $\{\mathcal{D}_k\}$  and the number of events in this bin for ${\mathcal{D}_0}$ which also serves as a normalisation to produce a fractional uncertainty:
+to be the mean of the absolute difference between the number of events in this bin for the smeared samples $\{\mathcal{D}_k\}$  and the number of events in this bin for ${\mathcal{D}_0}$:
 \be
@@
 
-In the case of FASER$\nu$2, the systematic uncertainties associated to the final state energies $E_\ell$ and $E_h$ are comparable and are typically at the $10\%$ level, ranging
-from $1\%$ to  ${\cal O}(1)$ across bins. The uncertainties associated with $\theta_\ell$ are typically at or well below $1\%$ for these experiments, which can be attributed to their good spatial
+In the case of FASER$\nu$2, the systematic uncertainties associated to the final state energies $E_\ell$ and $E_h$ are comparable and are in general at the $10\%$ level, ranging
+from $1\%$ to  $30\%$ across bins.
+%
+The uncertainties associated with $\theta_\ell$ are typically at or well below the $1\%$ level
+for these experiments, which can be attributed to their good spatial
 resolution. 
 %
-On the other hand, for the FLArE10(100) experiment, uncertainties associated with the scattering angle $\theta_\ell$ dominate, being at the $ 40\%$ level and ranging from a few percent to ${\cal O}(1)$,
+On the other hand, for the FLArE experiment, uncertainties associated with the scattering angle $\theta_\ell$ dominate, being at the $ 40\%$ level and ranging from a few percent to ${\cal O}(1)$,
 whereas the uncertainties associated with final-state energy reconstruction
@@
 % 
-In Sect.~\ref{sec:pdf4lhc21} and Sect.~\ref{sec:nuclearPDFs} we present results with $f_{\rm red}=0.5$, 
- while the remainder of Sect.~\ref{sec:protonPDFs} assumes the conservative scenario $f_{\rm red}=1$, 
- but it is straightforward to revisit the projections for a more optimistic detector performance with $f_{\rm red}< 1$.
+ In  Sect.~\ref{sec:protonPDFs} we present results both for $f_{\rm red}=1$ (conservative)
+ and $f_{\rm red}=0.5$ (optimistic scenario), though we note that it would be straightforward to revisit
+ the projections for other assumptions of the detector performance.
 
@@
  The observables $\mathcal{O}_i $ in Eq.~(\ref{eq:theory_dis_projections})
-are evaluated with the
-{\sc\small YADISM}~\cite{yadism,Candido:2023utz} program
+are evaluated with 
+{\sc\small YADISM}~\cite{yadism,Candido:2023utz}
 interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss, christopher_schwan_2023_7995675}
@@
 in the NNPDF global analysis framework~\cite{NNPDF:2021uiq,NNPDF:2021njg}.
-%
+
 The profiling method applied to Hessian PDF fits is based
@@
 
-Concerning the inclusion of the LHC far-forward neutrino pseudo-data
+Concerning the inclusion of the LHC neutrino pseudo-data
 in the NNPDF proton analysis framework, we follow the procedure

### 2023-09-18 paper/tables/integrated_yields.tex
Ton -> tonne (metric unit)
felix comments, event yields
sect 2 revised

@@
 \midrule
-FASER$\nu$  & 0.2k (31)    & 110 (19)  & 0.3k (50)  &  0.6k (98)  &  0.3k (45)  &  0.9k (140) \\
-SND@LHC  &  88 (11)  & 38 (5.4)    & 130 (16)   &  0.3k (54) & 96 (22)   &  0.4k  (76)\\
+FASER$\nu$  & 400 (62)    & 210 (38)  & 610 (100)  &  1.3k (200)  &  500 (90)  &  1.8k (290) \\
+SND@LHC  &  180 (22)  & 76 (11)    & 260 (32)   &  510 (59) & 190 (25)   &  700  (83)\\
 \midrule
 \midrule
-FASER$\nu$2  & 58k (8.3k)   & 28k (5.0k)   & 86k (13.3k)  & 190k (27k)  & 67k (12k)    & 260k (39k)   \\
-AdvSND-far  &  5.9k (0.7k)  & 2.8k (0.4k)   & 8.7k (1.1k)  & 20k (2.4k)  & 8k (1.1k)   & 28k (3.5k)   \\
-FLArE10 & 22k (2.7k) & 10k (1.5k)   &  32k (4.2k) &  38k (5.2k)&   19k (2.5k) &   57k (7.7k) \\
-FLArE100 &   140k (18k)         &    66k (9.5k)         &       210k (27k)       &   220k (30k)      &  120k (15k)    &  340k (45k)  \\
+FASER$\nu$2  & 116k (17k)   & 56k (9.9k)   & 170k (27k)  & 380k (53k)  & 133k (23k)    & 510k (76k)   \\
+AdvSND-far  &  12k (1.5k)  & 5.5k (0.82k)   & 18k (2.3k)  & 40k (4.8k)  & 16k (2.2k)   & 56k (7k)   \\
+FLArE10 & 44k (5.5k) & 20k (3.0k)   &  64k (8.5k) &  76k (10k)&   38k (5.0k) &   110k (15k) \\
+FLArE100 &   290k (35k)         &    130k (19k)         &       420k (54k)       &   440k (60k)      &  232k (30k)    &  670k (90k)  \\
   \bottomrule
@@
  The numbers in parenthesis indicate the event rates corresponding to charm
- production.
+ production, Eq.~(\ref{eq:event_yields_charm}).
  %
  In the case of the FLArE detector, we display results for two proposed
- options with fiducual masses of 10 and 100 tons respectively.
+ options with fiducual masses of 10 and 100 tonnes respectively.
   \label{tab:integrated_rates}

### 2023-09-18 paper/sec-results.tex
sect 3

@@
 
-By following the strategy outlined in Sect.~\ref{sec:dis_pseudodata}, one can
+By following the strategy outlined in Sect.~\ref{sec:dis_pseudodata}, we 
 quantify the impact on the proton and nuclear PDFs of differential  DIS
@@
 
-We begin by presenting results for the Hessian profiling of
+We begin with the Hessian profiling of
 the PDF4LHC21 set.
@@
 we assume the performance parameters of  Table~\ref{tab:FPF_experiments}, which
-however could be very well enhanced in the actual realisation of the experiments,
+however could be improved in the actual realisation of the experiments,
 using for instance detector improvements or different kinematic reconstruction techniques.
@@
 beam should allow their mutual cross-calibration, such that the combination of their
-data brings in more information than just the trivial statistics scaling.
+data brings in more information than just the naive statistics scaling.
 
@@
 %
-In the latter case, we consider the 10 tonne variant.
+In the latter case, we consider the 10 tonne variant FLArE10.
 %
@@
 As summarised by Table~\ref{tab:integrated_rates}, each of these experiments
-has associated different expected numbers of DIS events, namely 260k, 28k, and 57k (340k)
+has associated different expected numbers of DIS events, namely 510k, 56k, and 110k (670k)
 inclusive muon-neutrino events for FASER$\nu$2, AdvSND and FLArE10~(100) respectively,
-with 39k, 3.5k, and 7.7k (45k) in the charm-tagged case.
+with 76k, 7k, and 15k (90k) in the charm-tagged case.
 
@@
 to FASER$\nu$2 is the milder impact for the $x\lsim 10^{-2}$ region,
-which can only be properly covered once the integrated statistics become large
+which can only be covered once the integrated statistics become large
 enough,  as indicated by the differential bin-by-bin yields displayed in Fig.~\ref{fig:fasernu2_muon}.
 
-We emphasize
-that Fig.~\ref{fig:FASERnu2_FLAre10} compares fits based on FPF pseudo-data
-with only statistical uncertainties, and that a more refined comparison between the PDF reach of
+While Fig.~\ref{fig:FASERnu2_FLAre10} compares fits based on FPF pseudo-data
+with only statistical uncertainties, a more robust comparison between the PDF reach of
 the various FPF experiments requires accounting also for the systematic uncertainties, which ultimately become
@@
 it will be difficult to provide competitive constraints on the proton structure due
-to the (relatively) low event rates.
+to the (relatively) low DIS event rates.
 
@@
 We have also carried out a further PDF analysis including simultaneously the three FPF experiments
-considered so far: FASER$\nu$2, AdvSND, and FLArE100.
+considered here: FASER$\nu$2, AdvSND, and FLArE10.
 %
@@
 %
-Possible correlations between the individual experiments are neglected in this exercise, though they
-will become important when interpreting the actual measurements.
+Potential correlations between individual experiments are neglected in this exercise.
+%
+The combined impact of the three FPF experiments on PDF4LHC21 shown in Fig.~\ref{fig:FPF_combined}
+is only moderately improved as compared to the results of the FASER$\nu$2-only profiling
+in Fig.~\ref{fig:FASERnu2_baseline}.
+%
+This shows that in this combination of experiments the one with the largest individual
+sensitivity dominates, in this case FASER$\nu$2.
+%
+Again, here we assume perfect consistency between theory and data, while
+within the actual experiments the consistency (or lack thereof) between
+individual measurements cannot be guaranteed.
 
@@
 
-The combined impact of the three FPF experiments on PDF4LHC21 shown in Fig.~\ref{fig:FPF_combined}
-is only slightly improved as compared to the results of the FASER$\nu$2-only profiling
-in Fig.~\ref{fig:FASERnu2_baseline}.
-%
-This shows that in this naive combination of experiments the one with the largest individual
-sensitivity dominates, in this case FASER$\nu$2.
-%
-Again, this exercise is somewhat simplistic since within the real experiments the consistency (or lack thereof) between
-individual measurements, which here is assumed by construction, provides useful information, and also
-because the FPF experiments will cross-calibrate each other and cover somewhat different kinematic regions.
-
 The projections displayed in
@@
 the analysis of neutrino DIS structure function data at the FPF,
-under the assumption that PDF4LHC21 accurately represents
+under the assumption that PDF4LHC21 represents
 our current knowledge about the quark and gluon structure of the proton.
@@
 
-As discussed in Sect.~\ref{subsec:pdf_impact_assessment}, the PDF sensitivity
+The PDF sensitivity
 studies of the FPF neutrino data based on the {\sc\small xFitter} profiling

### 2023-09-18 paper/sec-results.tex
Update sec-results.tex

@@
 
-The PDF sensitivity
-studies of the FPF neutrino data based on the {\sc\small xFitter} profiling
+The PDF sensitivity studies based on the {\sc\small xFitter} profiling
 of PDF4LHC21 are complemented by those based on their direct inclusion
-in the NNPDF4.0 global analysis.
+in the NNPDF4.0 analysis.
 %
@@
 %
-Given that the qualitative obtained with the NNPDF fits
+Given that the findings obtained with the NNPDF fits
 are compatible with those obtained with {\sc\small xFitter}, it is not necessary to duplicate them here
@@
 %
-As was the case with the PDF4LHC21 baseline, the uncertainty reduction
-for the strangeness PDF is particularly
-striking.
+As was the case with PDF4LHC21, the uncertainty reduction
+for the strangeness is particularly striking.
 %
@@
 such as the PDF parametrisation and the method used to assess the PDF
-error reduction (for example, concerning the small-$x$ behaviour of $xu_V$ and $xd_V$)
+error reduction, for example, concerning the small-$x$ behaviour of $xu_V$ and $xd_V$,
 we conclude that by and large the projected impact of the FPF structure function
@@
 As indicated by Fig.~\ref{fig:NNPDF40_baseline}, the FPF data is also expected
-to reduce the uncertainties associated to the fitted charm PDF in the region $x\simeq 0.2$
+to reduce the uncertainties associated to the fitted charm PDF in the large-$x$ region 
 dominated by the non-perturbative component.
@@
   & Direct photon production                 &  0.74   &   0.74     &    0.73   \\
-  & FPF (total)                 &  1.29  / 0.92  &   1.10     &   0.89    \\
+  & FPF (total)                 &  {\it 1.29  / 0.92}  &   1.10     &   0.89    \\
   \bottomrule
@@
   The last row displays the $\chi^2/n_{\rm dat}$ obtained for the combined FPF dataset.
-  For the baseline fit we present both the value computed with only statistical error
-  and also adding the systematics so that it can be compared with both fits. 
+  %
+  For the baseline, we indicate the pre-fit values of $\chi^2/n_{\rm dat}$  for the  FPF dataset (in italics)
+  computed without
+  and with systematic errors in the covariance matrix.
   \label{tab:chi2_nnpdf40_baseline}
@@
 as a function of the final-state invariant mass $m_X$ between
-the baseline NNPDF4.0 determination and its variants which includes
-the combined FPF pseudo-data from the FASER$\nu$2, FLArE, and AdvSND experiments,
-see Figs.~\ref{fig:NNPDF40_baseline} or the corresponding PDF comparison.
+the baseline NNPDF4.0 fit and its variants including the combined FPF dataset,
+see Fig.~\ref{fig:NNPDF40_baseline} for the corresponding PDF comparison.
 %
@@
 %
-These luminosities are useful to interpret the phenomenological studies with the FPF-improved
-PDFs for the HL-LHC that will be presented in Sect.~\ref{sec:pheno}.
+The reduction of PDF uncertainties found in  Figs.~\ref{fig:NNPDF40_baseline}
+and~\ref{fig:NNPDF40_lowQ_abs} is also visible
+for the partonic luminosities, specially in the best-case scenario where only statistical
+uncertainties in the FPF pseudo-data are considered.
+%
+The improved quark-antiquark luminosities at $Q\sim 100$ GeV
+benefit theoretical predictions for gauge-boson production at the LHC.
+%
+It is also worth noting the PDF error reduction for the quark-quark luminosity at
+high invariant masses,
+which will feed into searches for new heavy particles at the TeV scale
+driven by quark-initiated scattering.
+%
+Unsurprisingly, luminosities related to the strange PDF are those
+which improve the most, such as the $u\bar{s}$ channel which provides a significant
+contribution to inclusive $W^+$ production.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The reduction of PDF uncertainties found in  Figs.~\ref{fig:NNPDF40_baseline}
-and~\ref{fig:NNPDF40_lowQ_abs} is also visible
-for the partonic luminosities, specially on the scenario where only statistical
-uncertainties in the FPF pseudo-data are considered.
-%
-The improved quark-antiquark luminosities at $Q\sim 100$ GeV
-benefit theoretical predictions for $W$ and $Z$ production at the LHC.
-%
-It is also worth noting the PDF error reduction for the quark-quark luminosity at
-high invariant masses,
-which will feed into searches for new heavy particles at the TeV scale
-driven by quark-initiated scattering.
-%
-Unsurprisingly, luminosities related to the strange PDF are those
-which improve the most, such as the $u\bar{s}$ channel which provides a significant
-contribution to inclusive $W^+$ production at the LHC.
 
@@
 While the main qualitative features of the nPDF profiling are consistent with the free-proton
- case, one reason explaining the observed differences is the choice of a larger tolerance factor $T$ in EPPS21
+case, one reason explaining the observed differences may be the usage of a larger tolerance factor $T$ in EPPS21
 as compared to PDF4HC21, which effectively reduces the impact of new data in the fit.
@@
 assessing the impact on a nuclear PDFs by a direct refit, as was done for NNPDF4.0,
- may provide a more  robust estimate of the impact of FPF structure function data
+may be required to establish the impact of FPF structure function data
 on nPDFs.

### 2023-09-18 paper/app-faser.tex
revision completed

@@
 As indicated by Table~\ref{tab:integrated_rates}, by the end of Run III, one expects
-that FASER$\nu$ will have recorded around 300 and 900 electron- and muon-neutrinos
-respectively corresponding to deep-inelastic scattering events, of which around 50
-and 140 respectively are associated to charm-tagged events.
+that FASER$\nu$ will have recorded around 600 and 1800 electron- and muon-neutrinos
+respectively corresponding to deep-inelastic scattering events, of which around 100
+and 300 respectively are associated to charm-tagged events.
 %
@@
 %
-The reason is two-fold: the much smaller event rates as compared to FASER$\nu$2,
+The reason is two-fold: the smaller event rates as compared to FASER$\nu$2,
 and the reduced coverage of the $(x,Q^2)$ phase space shown in Fig.~\ref{fig:fasernu2_muon}.

### 2023-09-18 paper/app-nuclearPDFs.tex
revision completed

@@
 will differ from those arising from antineutrino scattering, introducing
-hence some additional information as compared to an isoscalar target in terms
-of PDF sensitivity.
+additional information as compared to an isoscalar target in terms of PDF sensitivity.
 

### 2023-09-18 paper/sec-pheno.tex
revision completed

@@
 analysis, given that we don't aim to compare with experimental data.
-
-Fig.~\ref{fig:NNPDF40_pheno_integrated} displays
-fiducial cross-section for representative LHC processes at $\sqrt{s}=14$ TeV
-evaluated with NNPDF4.0 (top panels)
-and with PDF4LHC21 (bottom panels),
-compared with the results obtained from
-the corresponding fits including the FPF structure function projections.
-%
-For the fits with FPF data we display the variants where the covariance matrix
-consists only of statistical errors (``\_FPF'') and where also
-systematic errors are accounted for (``\_FPF$^*$'').
-%
-For the baseline
-predictions, the dark (light) bands indicate the 68\% (95\%) CL uncertainties.
-%
-The central values are set to be the same as in the baseline calculation in all cases.
-%
-From top to bottom, we show inclusive Drell-Yan production in the $Z$, $W^+$, and $W^-$
-channels, Higgs production
-in vector-boson fusion, Higgs associated
-production, and diboson production in the $W^+W^-$, $W^+Z$, and $W^-Z$ final-states.
-%
-The corresponding comparisons at the level of differential distributions
-are shown in Figs.~\ref{fig:NNPDF40_pheno_differential} and~\ref{fig:PDF4LHC21_pheno_differential}
-for NNPDF4.0 and PDF4LHC21 respectively.
-%
-As done for the fiducial cross-sections of Fig.~\ref{fig:NNPDF40_pheno_integrated},
-we only indicate the relative PDF uncertainty in each fit, with central values
-assumed to be unchanged.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Fig.~\ref{fig:NNPDF40_pheno_integrated} displays
+fiducial cross-section for representative LHC processes at $\sqrt{s}=14$ TeV
+evaluated with NNPDF4.0 (top panels)
+and with PDF4LHC21 (bottom panels),
+compared with the results obtained from
+the corresponding fits including the FPF structure function projections.
+%
+For the fits with FPF data we display the variants where the covariance matrix
+consists only of statistical errors (``\_FPF'') and where also
+systematic errors are accounted for (``\_FPF$^*$'').
+%
+For the baseline
+predictions, the dark (light) bands indicate the 68\% (95\%) CL uncertainties.
+%
+The central values are set to be the same as in the baseline calculation in all cases.
+%
+From top to bottom, we show inclusive Drell-Yan production in the $Z$, $W^+$, and $W^-$
+channels, Higgs production
+in vector-boson fusion, Higgs associated
+production, and diboson production in the $W^+W^-$, $W^+Z$, and $W^-Z$ final-states.
+%
+The corresponding comparisons at the level of differential distributions
+are shown in Figs.~\ref{fig:NNPDF40_pheno_differential} and~\ref{fig:PDF4LHC21_pheno_differential}
+for NNPDF4.0 and PDF4LHC21 respectively.
+%
+As done for the fiducial cross-sections of Fig.~\ref{fig:NNPDF40_pheno_integrated},
+we only indicate the relative PDF uncertainty in each fit.
 
@@
 %
-As  compared to the limiting scenario where only statistical uncertainties
+As  compared to the best-case scenario where only statistical uncertainties
 are taken into account, the reduction of PDF errors in the LHC cross-sections
@@
 and~\ref{fig:PDF4LHC21_pheno_differential},
-we observe how the impact of the FPF structure functions on LHC observables depends
+one observes
+how the impact of the FPF structure functions on LHC observables depends
 on the hard-scattering scale.

### 2023-09-18 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/fred05fcorr05/AdvSND/plot.sh
Importing all xFitter files from PDF4LHC21 branch

@@ -1,0 +1,24 @@
+DETECTOR="AdvSND"
+DETSIMPLE="AdvSND"
+UNCLVL="fred05fcorr05"
+
+PDF="EPPS21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --scale68 --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-18 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/prel/FASERv2_inclusive_nu/run.sh

@@ -1,0 +1,28 @@
+# The commands to perform Hessian PDF profiling w/ xFitter, do e.g.
+#    sh run.sh
+
+PDF="EPPS21"  #N.B. or plots only! Change also in parameters.yaml
+PSEUDODATA="inclusive"
+
+### OPTS w/o/ scaling 95% cl -> 68%, e.g. CT PDFs
+#PLOTOPTS="--asym --therr --bands --q2all --relative-errors"
+
+### OPTS w/ scaling 95% cl -> 68%, needed for EPPS PDFs (like CT)
+#PLOTOPTS="--splitplots-eps  --therr --bands --q2all --relative-errors --scale68 --xrange 1e-6:0.99"
+PLOTOPTS="--therr --bands --q2all --scale68 --relative-errors"
+
+ln -s ../../../../datafiles
+
+# Run xFitter:
+xfitter > log.txt
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:${PDF} profile:output:${PDF}-${PSEUDODATA}
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-18 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/syst/clean.sh

@@ -1,0 +1,7 @@
+#Some plots depend on results in many dirs, depending on the plot.sh scripts
+for dir in */; do
+    rm -rf ${dir}/output
+    rm -rf ${dir}/plots
+    rm ${dir}/*.pdf
+    rm ${dir}/unpolarised.wgt
+done

### 2023-09-18 xFitter/PDF_profiling/PDF4LHC21/fred05fcorr05/FLArE10/plot.sh

@@ -1,0 +1,27 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FLArE10"
+DETSIMPLE="FLArE10"
+UNCLVL="fred05fcorr05"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:../../statOnly/${DETSIMPLE}/output:"BL+${DETECTOR}, stat" profile:output:"BL+${DETECTOR}, stat+syst"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-18 xFitter/PDF_profiling/PDF4LHC21/fred05fcorr05/FPF/plot.sh

@@ -1,0 +1,28 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FPF"
+DETSIMPLE="FPF"
+UNCLVL="fred05fcorr05"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+PDFLONG="PDF4LHC21_40"
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:../../statOnly/${DETSIMPLE}/output:"BL+${DETECTOR}, stat" profile:output:"BL+${DETECTOR}, stat+syst"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDFLONG}/ ${PDF}-${DETECTOR}
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-18 xFitter/PDF_profiling/PDF4LHC21/prel/FASERv_inclusive_nub/run.sh

@@ -1,0 +1,28 @@
+# The commands to perform Hessian PDF profiling w/ xFitter, do e.g.
+#    sh run.sh
+
+PDF="PDF4LHC21"  #N.B. or plots only! Change also in parameters.yaml
+PSEUDODATA="inclusive"
+
+### OPTS w/o/ scaling 95% cl -> 68%, e.g. CT PDFs
+#PLOTOPTS="--asym --therr --bands --q2all --relative-errors"
+
+### OPTS w/ scaling 95% cl -> 68%, needed for CT PDFs
+#PLOTOPTS="--splitplots-eps  --therr --bands --q2all --relative-errors --scale68 --xrange 1e-6:0.99"
+PLOTOPTS="--therr --bands --q2all --relative-errors"
+
+ln -s ../../../../datafiles
+
+# Run xFitter:
+xfitter > log.txt
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:${PDF} profile:output:${PDF}-${PSEUDODATA}
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-18 xFitter/PDF_profiling/PDF4LHC21/statOnly/FASERv/plot.sh

@@ -1,0 +1,25 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter
+#    sh plot.sh
+
+DETECTOR="FASER#nu"
+DETSIMPLE="FASERv"
+UNCLVL="statOnly"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:../FASERv2/output:"BL+FASER#nu2" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-18 xFitter/PDF_profiling/PDF4LHC21/statOnly/FPF/plot.sh

@@ -1,0 +1,26 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter
+#    sh plot.sh
+
+DETECTOR="FPF"
+DETSIMPLE="FPF"
+UNCLVL="statOnly"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+PDFLONG="PDF4LHC21_40"
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:output:"BL+${DETECTOR}"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDFLONG}/ ${PDF}-${DETECTOR}-${UNCLVL}
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-18 xFitter/PDF_profiling/PDF4LHC21/syst/FASERv2_charm/plot.sh

@@ -1,0 +1,27 @@
+# The commands to visualize results of Hessian PDF profiling w/ xFitter, do e.g.
+#    sh plot.sh
+
+DETECTOR="FASER#nu2"
+DETSIMPLE="FASERv2"
+UNCLVL="syst"
+
+PDF="PDF4LHC21"  #N.B. filenames only! Change also in parameters.yaml
+
+PLOTOPTS="--splitplots-pdf --therr --bands --q2all --relative-errors --xrange 1e-3:0.6"
+
+# Visualize results:
+mv plots/plots.pdf plots/plots_OLD.pdf
+xfitter-draw ${PLOTOPTS} output:"Baseline (BL)" profile:../../statOnly/${DETSIMPLE}/output:"BL+${DETECTOR}, stat" profile:output:"BL+${DETECTOR}, stat+syst"
+mv plots/plots.pdf plots/${PDF}_vs_profiled.pdf
+
+cp plots/q2_10000_pdf_uv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_uv_ratio.pdf 
+cp plots/q2_10000_pdf_dv_ratio.pdf  ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_dv_ratio.pdf 
+cp plots/q2_10000_pdf_g_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_g_ratio.pdf
+cp plots/q2_10000_pdf_Sea_ratio.pdf ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_Sea_ratio.pdf
+cp plots/q2_10000_pdf_s_ratio.pdf   ${UNCLVL}_${DETSIMPLE}_q2_10000_pdf_s_ratio.pdf
+
+# Produce a new PDF in LHAPDF6 format:
+#xfitter-process profile output/pdf_shifts.dat output/pdf_rotate.dat `lhapdf-config --datadir`/${PDF}/ ${PDF}-profiled
+
+# Save the new PDF set into LHAPDF6 collection:
+#cp -r ${PDF}-profiled/ `lhapdf-config --datadir`

### 2023-09-27 journal_sub/main.tex
Add epjc typeset version

--- 2023-09-15 paper/FPF-WG1.tex
@@
-\documentclass[11pt,a4paper]{article}
-\pdfoutput=1
+%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% This is a template file for The European Physical Journal
+%
+% Copy it to a new file with a new name and use it as the basis
+% for your article
+%
+%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+\begin{filecontents}{leer.eps}
+	%!PS-Adobe-2.0 EPSF-2.0
+	%%CreationDate: Mon Jul 13 16:51:17 1992
+	%%DocumentFonts: (atend)
+	%%Pages: 0 1
+	%%BoundingBox: 72 31 601 342
+	%%EndComments
+
+	gsave
+	72 31 moveto
+	72 342 lineto
+	601 342 lineto
+	601 31 lineto
+	72 31 lineto
+	showpage
+	grestore
+	%%Trailer
+	%%DocumentFonts: Helvetica
+\end{filecontents}
+%
+\documentclass[epj]{svjour}
 
@@
 \usepackage[font=small,labelfont=bf,margin=0mm,labelsep=period,tableposition=top]{caption}
-\usepackage[a4paper,top=1.5cm,bottom=2cm,left=1.5cm,right=1.5cm,bindingoffset=0mm]{geometry}
+%\usepackage[a4paper,top=1.5cm,bottom=2cm,left=1.5cm,right=1.5cm,bindingoffset=0mm]{geometry}
 
+% Various Packages
 \usepackage{placeins,cite}
@@
 \usepackage{float}
+\usepackage{microtype}
 \usepackage{afterpage}
@@
 \usepackage{url}
-\usepackage{booktabs,multirow}
+\usepackage{booktabs,multirow,longtable}
 \usepackage{textcomp}
 \graphicspath{{../}{./figures/}}
-
-\makeatletter
-\def\thickhline{%
-             \noalign{\ifnum0 =`}\fi\hrule \@height \thickarrayrulewidth \futurelet
-             \reserved@a\@xthickhline}
-\def\@xthickhline{\ifx\reserved@a\thickhline
-                \vskip\doublerulesep
-                \vskip -\thickarrayrulewidth
-                \fi
-                \ifnum0 =`{\fi}}
-\makeatother
-\newlength{\thickarrayrulewidth}
-\setlength{\thickarrayrulewidth}{3\arrayrulewidth}
 
@@
 \begin{document}
-\newgeometry{top=1.5cm,bottom=1.5cm,left=1.5cm,right=1.5cm,bindingoffset=0mm}
-
-\vspace{-2.0cm}
-\begin{flushright}
-Nikhef-2023-009 \\ CERN-TH-2023-165\\
-\end{flushright}
-\vspace{0.6cm}
-
-\begin{center}
-  {\Large \bf The LHC as a Neutrino-Ion Collider }\\
-  \vspace{1.1cm}
-  {\small
-    Juan M. Cruz-Martinez$^{1}$, Max Fieg$^{2}$, Tommaso Giani$^{3,4}$, Peter Krack$^{3,4}$, Toni M\"akel\"a$^{5}$,  \\[0.1cm]
-    Tanjona Rabemananjara$^{3,4}$, and Juan Rojo$^{3,4}$
-  }\\
-
-\vspace{0.7cm}
-
-{\it \small
-    ~$^1$CERN, Theoretical Physics Department, CH-1211 Geneva 23, Switzerland \\[0.1cm]
-    ~$^2$ Department of Physics and Astronomy, University of California, Irvine, CA 92697 USA  \\[0.1cm]
-    ~$^3$Department of Physics and Astronomy, Vrije Universiteit, NL-1081 HV Amsterdam\\[0.1cm]
-    ~$^4$Nikhef Theory Group, Science Park 105, 1098 XG Amsterdam, The Netherlands\\[0.1cm]
-    ~$^5$National Centre for Nuclear Research, Pasteura 7, Warsaw, PL-02-093, Poland \\[0.1cm]
+	%
+	\title{The LHC as a Neutrino-Ion Collider}
+%	\subtitle{Do you have a subtitle?\\ If so, write it here}
+	\author{
+		Juan M. Cruz-Martinez\inst{1},
+		Max Fieg\inst{2},
+		Tommaso Giani\inst{3,4},
+		Peter Krack\inst{3,4},
+		Toni M\"akel\"a\inst{5},
+		Tanjona R. Rabemananjara\inst{3,4},
+		Juan Rojo\inst{3,4}
 	}
-
-\vspace{1.0cm}
-
-{\bf \large Abstract}
-
-\end{center}
-
+	\titlerunning{The LHC as a Neutrino-Ion Collider}
+	\authorrunning{Juan M. Cruz-Martinez et al.}
+	\institute{
+		CERN, Theoretical Physics Department, CH-1211 Geneva 23, Switzerland  \and
+		Department of Physics and Astronomy, University of California, Irvine, CA 92697 USA \and
+		Department of Physics and Astronomy, Vrije Universiteit, NL-1081 HV Amsterdam \and
+		Nikhef Theory Group, Science Park 105, 1098 XG Amsterdam, The Netherlands \and
+		National Centre for Nuclear Research, Pasteura 7, Warsaw, PL-02-093, Poland
+	}
+	%
+	\date{Received: date / Revised version: date}
+	\abstract{
 		Proton-proton collisions at the LHC generate a high-intensity collimated beam of neutrinos
@@
 		without  requiring modifications in its accelerator infrastructure.
+		%
+		\PACS{
+			{12.38.-t}{Quantum chromodynamics}   \and
+			{24.85.+p}{Quarks, gluons, and QCD in nuclear reactions}
+		} % end of PACS codes
+	}
 
-\clearpage
+	\maketitle
+	\setcounter{tocdepth}{3}
+	\tableofcontents
 
-\tableofcontents
 	\input{sec-introduction}
@@
 	\bibliographystyle{utphys}
-%\bibliography{FPF-WG1}
-\input{FPF-WG1.bbl}
+	\bibliography{main.bib}
 

### 2023-09-27 journal_sub/sec-dis-pseudodata.tex
Add epjc typeset version

--- 2023-09-18 paper/sec-dis-pseudodata.tex
@@
 and $F_L^{\nu A}$:
-\be
+\begin{align}
 	\label{eq:neutrino_DIS_xsec_FL}
-\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\nu A}_2(x,Q^2) - y^2F^{\nu A}_L(x,Q^2) +Y_- xF^{\nu A}_3(x,Q^2)\rc  \, ,
-\ee
+	&\frac{d^2\sigma^{\nu A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\\ 
+	& \lc Y_+F^{\nu A}_2(x,Q^2) - y^2F^{\nu A}_L(x,Q^2) +Y_- xF^{\nu A}_3(x,Q^2)\rc, \nonumber
+\end{align}
 where $Y_\pm = 1 \pm (1-y)^2$ and with a counterpart expression for anti-neutrino scattering,
-\be
+\begin{align}
 	\label{eq:antineutrino_DIS_xsec_FL}
-\frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2}\lc Y_+F^{\bar{\nu} A}_2(x,Q^2) - y^2F^{\bar{\nu} A}_L(x,Q^2) -Y_- xF^{\bar{\nu} A}_3(x,Q^2)\rc  \, ,
-\ee
+	&\frac{d^2\sigma^{\bar{\nu} A}(x,Q^2,y)}{dxdy} =  \frac{G_F^2s/4\pi}{\lp 1+Q^2/m_W^2\rp^2} \\
+	& \lc Y_+F^{\bar{\nu} A}_2(x,Q^2) - y^2F^{\bar{\nu} A}_L(x,Q^2) -Y_- xF^{\bar{\nu} A}_3(x,Q^2)\rc,
+	\nonumber
+\end{align}
 with $s=2m_N E_\nu$ being the neutrino-nucleon centre-of-mass energy squared, $m_N$ the nucleon mass,
@@
 transfers $Q^2 \gsim 2$ GeV$^2$, such that the structure functions can be decomposed as
-\be
+\begin{align}
 	\label{eq:sfs_pqcd}
- F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g}\int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \quad i = 2,3,L \, .
- \ee
+	F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g} & \int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}
+	(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \nonumber \\
+	& \text{ with } \quad i = 2,3,L \, ,
+\end{align}
 %
@@
  The resulting $F_2^{\nu p}$ and $xF_3^{\nu p}$ structure functions read
- \bea
- F_2^{\nu p}(x,Q^2) &=& 2x\lp f_{\bar{u}} + f_{d} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
- F_2^{\bar{\nu} p}(x,Q^2) &=& 2x\lp f_u + f_{\bar{d}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:neutrinoSFs_proton} \\
- xF_3^{\nu p}(x,Q^2) &=& 2x\lp -f_{\bar{u}} + f_d +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
- xF_3^{\bar{\nu} p}(x,Q^2) &=& 2x\lp f_u - f_{\bar{d}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, . \nonumber
- \eea
+\begin{align}
+	 F_2^{\nu p}(x,Q^2) &= 2x\lp f_{\bar{u}} + f_{d} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
+	F_2^{\bar{\nu} p}(x,Q^2) &= 2x\lp f_u + f_{\bar{d}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:neutrinoSFs_proton} \\
+	xF_3^{\nu p}(x,Q^2) &= 2x\lp -f_{\bar{u}} + f_d +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
+	xF_3^{\bar{\nu} p}(x,Q^2) &= 2x\lp f_u - f_{\bar{d}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, . \nonumber
+\end{align}
  The corresponding expressions for a neutron target are obtained from isospin symmetry
- \bea
- F_2^{\nu n}(x,Q^2) &=& 2x\lp f_{\bar{d}} + f_{u} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
- F_2^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d + f_{\bar{u}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:antineutrinoSFs_neutron} \\
- xF_3^{\nu n}(x,Q^2) &=& 2x\lp -f_{\bar{d}} + f_u +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
- xF_3^{\bar{\nu} n}(x,Q^2) &=& 2x\lp f_d - f_{\bar{u}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, , \nonumber
- \eea
+ \begin{align}
+ 	 F_2^{\nu n}(x,Q^2) &= 2x\lp f_{\bar{d}} + f_{u} + f_{s} + f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
+ 	F_2^{\bar{\nu} n}(x,Q^2) &= 2x\lp f_d + f_{\bar{u}} + f_{\bar{s}} + f_c \rp(x,Q^2) \, , \label{eq:antineutrinoSFs_neutron} \\
+ 	xF_3^{\nu n}(x,Q^2) &= 2x\lp -f_{\bar{d}} + f_u +f_s - f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
+ 	xF_3^{\bar{\nu} n}(x,Q^2) &= 2x\lp f_d - f_{\bar{u}} -f_{\bar{s}} + f_{c}\rp(x,Q^2) \, , \nonumber
+ \end{align}
  while for an isoscalar, free-nucleon target denoted by $N$ one has
- \bea
- F_2^{\nu N}(x,Q^2) &=& 2x\lp f_{u^+} + f_{d^+} + 2f_s + 2f_{\bar{c}} \rp(x,Q^2) \, , \nonumber  \\
- F_2^{\bar{\nu} N}(x,Q^2) &=& 2x\lp f_{u^+} + f_{d^+} + 2f_{\bar{s}} + 2f_c \rp(x,Q^2) \, , \label{eq:neutrinoSFs_isoscalar} \\
- xF_3^{\nu N}(x,Q^2) &=& 2x\lp f_{u^-} + f_{d^-} +2f_s - 2f_{\bar{c}}\rp(x,Q^2)  \, , \nonumber\\
- xF_3^{\bar{\nu} N}(x,Q^2) &=& 2x\lp   f_{u^-} + f_{d^-}-2f_{\bar{s}} +2 f_{c}\rp(x,Q^2) \, , \nonumber
- \eea
- in terms of the valence and sea PDF combinations defined by
- \be
- f_{q^+} (x,Q^2)\equiv \lp f_{q}+f_{\bar{q}}\rp(x,Q^2) \, , \qquad
- f_{q^-} (x,Q^2)\equiv \lp f_{q}- f_{\bar{q}}\rp(x,Q^2) \, .
- \ee
+ \begin{align}
+ 	\noindent
+ 	&F_2^{\nu N}(x,Q^2)= 2x\lp f_{u^+} + f_{d^+} + 2f_s + 2f_{\bar{c}} \rp(x,Q^2), \nonumber  \\
+ 	&F_2^{\bar{\nu} N}(x,Q^2)= 2x\lp f_{u^+} + f_{d^+} + 2f_{\bar{s}} + 2f_c \rp(x,Q^2), \label{eq:neutrinoSFs_isoscalar} \\
+ 	&xF_3^{\nu N}(x,Q^2)= 2x\lp f_{u^-} + f_{d^-} +2f_s - 2f_{\bar{c}}\rp(x,Q^2), \nonumber\\
+ 	&xF_3^{\bar{\nu} N}(x,Q^2)= 2x\lp   f_{u^-} + f_{d^-}-2f_{\bar{s}} +2 f_{c}\rp(x,Q^2), \nonumber \qquad
+ \end{align}
+ in terms of the valence and sea PDF combinations defined by the following relations
+\begin{align}
+	 f_{q^+} (x,Q^2) &\equiv \lp f_{q}+f_{\bar{q}}\rp(x,Q^2) \, , \nonumber \\
+	f_{q^-} (x,Q^2) &\equiv \lp f_{q}- f_{\bar{q}}\rp(x,Q^2) \, .
+\end{align}
  We note that, even for isoscalar targets, separate measurements
@@
  the $Z$-boson mass, $Q^2 \ll m_Z^2$, the corresponding
-decomposition is \bea
- F_2^{\ell p}(x,Q^2) &=& x\lp \frac{4}{9}\lc f_{u^+} + f_{c^+}\rc
+decomposition is
+\begin{align}
+	 F_2^{\ell p}(x,Q^2) &= x\lp \frac{4}{9}\lc f_{u^+} + f_{c^+}\rc
 	+ \frac{1}{9}\lc f_{d^+} + f_{s^+}\rc\rp(x,Q^2) \, , \nonumber  \\
- F_2^{\ell n}(x,Q^2) &=& x\lp \frac{4}{9}\lc f_{d^+} + f_{c^+}\rc
- + \frac{1}{9}\lc f_{u^+} + f_{s^+}\rc\rp(x,Q^2) \, ,\label{eq:NC_chargedlepton}   \\
- F_2^{\ell N}(x,Q^2) &=& x\lp \frac{5}{18}\lc f_{u^+} + f_{d^+}\rc
- + \frac{1}{9} f_{s^+} + \frac{4}{9} f_{c^+} \rp(x,Q^2) \, , \nonumber  
- \eea
+	F_2^{\ell n}(x,Q^2) &= x\lp \frac{4}{9}\lc f_{d^+} + f_{c^+}\rc
+	+ \frac{1}{9}\lc f_{u^+} + f_{s^+}\rc\rp(x,Q^2) \, , \nonumber   \\
+	F_2^{\ell N}(x,Q^2) &= x\lp \frac{5}{18}\lc f_{u^+} + f_{d^+}\rc
+	+ \frac{1}{9} f_{s^+} + \frac{4}{9} f_{c^+} \rp(x,Q^2) \, , \label{eq:NC_chargedlepton} 
+\end{align}
  with $xF_3$ being negligible in this region.
  %
- Comparing Eqns.~(\ref{eq:neutrinoSFs_proton})--(\ref{eq:neutrinoSFs_isoscalar})
+ Comparing Eqns. (\ref{eq:neutrinoSFs_proton})--(\ref{eq:neutrinoSFs_isoscalar})
  with Eq.~(\ref{eq:NC_chargedlepton}) showcases the complementarity between
@@
 momentum transfer $Q^2$, and neutrino energy $E_\nu$, that is,
-\be
+\begin{align}
 	\label{eq:event_yields}
-N_{\nu_e,{\rm ev}}^{(i)}\lp \nu_e ; E_{{\rm min}}^{(i)} \le E_\nu \le E_{{\rm max}}^{(i)} ;\,
-x_{{\rm min}}^{(i)} \le x \le x_{{\rm max}}^{(i)} ;\, Q_{{\rm min}}^{2(i)} \le Q^2 \le Q_{{\rm max}}^{2(i)}\rp
-\, ,\quad i=1,\ldots, N_{\rm bin} \, ,
-\ee
+	N_{\nu_e,{\rm ev}}^{(i)}\lp \nu_e ;  E_\nu; x; Q^2\rp
+	\, ,\quad i=1,\ldots, N_{\rm bin},
+\end{align}
+with
+\allowdisplaybreaks
+\begin{align}
+	E_{{\rm min}}^{(i)} &\le E_\nu \le E_{{\rm max}}^{(i)}, \nonumber \\
+	x_{{\rm min}}^{(i)} &\le x \le x_{{\rm max}}^{(i)} , \nonumber \\
+	Q_{{\rm min}}^{2(i)} & \le Q^2 \le Q_{{\rm max}}^{2(i)}, \nonumber
+\end{align}
+\allowdisplaybreaks
 for electron neutrinos and for each of the bins composing the measurement, and with similar
@@
 Binned event yields are evaluated using
-\begin{equation}
+\begin{align}
   \label{eq:event_yields_calculation}
-   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, ,
-\end{equation}
+   N_{\rm ev}^{(i)} =& n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}} \\
+   &\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, , \nonumber
+\end{align}
 with $n_T$ is the nucleon density of the target detector material, $L_T$ its
@@
 Assuming that charm quarks can be directly tagged by the detector one has
-\be
+\begin{align}
 	\label{eq:event_yields_charm}
-  N_{\rm ev,c}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma^{\nu N \to \ell + c+X}(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, ,
-  \ee
+	&N_{\rm ev,c}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}
+	\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}} \\
+	&\left(\frac{d^2\sigma^{\nu N \to \ell + c+X}(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, , 
+	\nonumber
+\end{align}
 with the charm production cross-sections discussed in~\cite{Faura:2020oom}
@@
 %-----------------------------------------------------------------------
-\begin{figure}[t]
+\begin{figure*}[t]
     \centering
@@
     \label{fig:fasernu2_muon}
-\end{figure}
+\end{figure*}
 %-----------------------------------------------------------------------
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
+\begin{figure*}[t]
     \centering
@@
     \label{fig:Kin_nNNPDF30_EIC_FPF}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h]
+\begin{figure*}[h]
     \centering
@@
     \label{fig:error_plot_FASERv2_14}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %-----------------------------------------------------------------------
-\begin{figure}[t]
+\begin{figure*}[t]
   \centering
@@
   \label{fig:percentage_uncertainties_overview}
-\end{figure}
+\end{figure*}
 %-----------------------------------------------------------------------
@@
 for each bin of the measurement, from which an experimental covariance matrix can be constructed as
-\be
+\begin{align}
 	\label{eq:covmat_definition}
-   {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
-   + \sum_{k=1}^{n_{\rm sys}}\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp \lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(j)} \rp
-   \, ,\qquad i,j=1,\ldots,N_{\rm bin} \, ,
- \ee
+	{\rm cov}_{ij} =\delta_{ij} & \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
+	+ \sum_{k=1}^{n_{\rm sys}}\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp \lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(j)} \rp,
+	\nonumber\\ 
+	& \text{ for } i,j=1,\ldots,N_{\rm bin} \, ,
+\end{align}
 and the same for the associated correlation
@@
 and add in quadrature statistical and systematic errors,
- \be
+\begin{align}
 	\label{eq:covmat_definition_v2}
- {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
-+ \delta_{ij}\lp f_{\rm corr}\rp^2\sum_{k=1}^{n_{\rm sys}} \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp^2
-\, ,\qquad i,j=1,\ldots,N_{\rm bin} \, .
-\ee
+	{\rm cov}_{ij} &= \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
+	+ \delta_{ij}\lp f_{\rm corr}\rp^2\sum_{k=1}^{n_{\rm sys}} \lp f_{\rm red}^{(k)}\rp^2 \times
+	\nonumber \\
+	& \lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp^2 \text{ for } i,j=1,\ldots,N_{\rm bin} \, .
+\end{align}
 In Eq.~(\ref{eq:covmat_definition_v2}) we have introduced a parameter $f_{\rm red}^{(k)}\le 1$
@@
  and we adopt the same choice here.
-% 
+
  In  Sect.~\ref{sec:protonPDFs} we present results both for $f_{\rm red}=1$ (conservative)
@@
  the projections for other assumptions of the detector performance.
+ %
+ Specifically, $f_{\rm red}=0.5$ is assumed for the Hessian profiling
+ of PDF4LHC21 and EPPS21 while $f_{\rm red}=1$ for the NNPDF4.0-based fits.
 
@@
 factor in the latter,
-  \be
+\begin{align}
 	\delta_{i}^{\rm tot}
- = \left( \left( \delta_i^{\rm stat}\right)^2 + \sum_{k=1}^{n_{\rm sys}}
- \left( f_{\rm corr} \times f_{\rm red}^{(k)} \times \delta_{i,k}^{\rm sys} \right)^2\right)^{1/2} \, ,
- \qquad i=1,\ldots,N_{\rm bin} \, ,
- \ee
+	= & \left( \left( \delta_i^{\rm stat}\right)^2 + \sum_{k=1}^{n_{\rm sys}}
+	\left( f_{\rm corr} \times f_{\rm red}^{(k)} \times \delta_{i,k}^{\rm sys} \right)^2\right)^{1/2} \, , \nonumber\\
+	& \text{ for } i=1,\ldots,N_{\rm bin} \, ,
+\end{align}
 and with $r_{i}$ being univariate Gaussian random numbers. 
@@
 on minimising a goodness-of-fit error function defined as
-\begin{equation}
+\begin{align}
 \chi^2 = 
-\sum_{i=1}^{N_{\textrm{bin}}} 
+\sum_{i=1}^{N_{\textrm{bin}}} &
 \frac{\left(  \mathcal{O}_i^{\rm (exp)}
@@
      \right)^2
-     }{ \left(\delta^{{\rm (stat)}}\mathcal{O}_i^{\rm (th)}\rp^2 }
-+ \sum_\alpha \lp b_\alpha^{(\textrm{exp})}\rp^2
+     }{ \left(\delta^{{\rm (stat)}}\mathcal{O}_i^{\rm (th)}\rp^2 } \nonumber\\
++ &\sum_\alpha \lp b_\alpha^{(\textrm{exp})}\rp^2
 + T^2 \sum_\beta  \lp b_\beta^{\textrm{(th)}}\rp ^2 \, ,
 \label{eq:profilingchi2}
-\end{equation}
+\end{align}
 with the pseudodata 

### 2023-09-27 journal_sub/sec-summary.tex
Add epjc typeset version

--- 2023-09-18 paper/sec-summary.tex
@@
 Together with this paper, we 
-make public in Zenodo
+make public in Zenodo~\cite{cruz_martinez_juan_2023_8355209}
 the corresponding {\sc\small LHAPDF} grids~\cite{Buckley:2014ana}

### 2023-11-09 journal_sub/sec-dis-pseudodata.tex
some referee updates
https://docs.google.com/document/d/1Uaoc4B43W9kNWLhwCEfg5po59jjxrRj-qubZol22BsY/edit?usp=sharing

@@
  the strange and charm sea asymmetries $f_{s^-}$ and
- $f_{c^-}$ are not expected to vanish.
+ $f_{c^-}$ are not expected to vanish~\cite{Sufian:2018cpj,Sufian:2020coz}.
 
@@
 We implement this last constraint
-in our simulations by requiring a minimum hadronic energy when calculating the event yields.
+in our simulations by requiring a minimum hadronic energy when calculating the event yields, as the charged track multiplicity is expected to grow with $W$~\cite{Aachen-Bonn-CERN-Munich-Oxford:1981lfk,FASER:2019dxq}.
 
@@
  %
- This proposed experiment consists actually on  two detectors, a far-detector to be installed
+ This proposed experiment~\cite{Feng:2022inv} consists actually on  two detectors, a far-detector to be installed
  at the FPF with a coverage in neutrino pseudorapidity of $7.2 \le \eta_\nu \le 8.4$
@@
  %
- Building upon recent progress in liquid noble gas neutrino detectors over the last decade (ICARUS, MicroBooNE, SBND, DUNE), this experiment
+ Building upon recent progress in liquid noble gas neutrino detectors over the last decade (ICARUS, MicroBooNE, SBND, DUNE), this experiment~\cite{Batell:2021blf,Feng:2022inv}
  would rely on a modularized liquid argon (LAr) time projection detector.

### 2023-11-14 journal_sub/sec-pheno.tex
Add epjc typeset version
Add star in pheno to stat only

--- 2023-09-18 paper/sec-pheno.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htbp]
+\begin{figure*}[htbp]
 \centering
@@
 %
-The fits labelled as ``\_FPF'' are the ones considering statistical uncertainties,
-while those labelled as ``\_FPF$^*$'' also include systematic errors.
+The fits labelled as ``\_FPF$^*$'' are the ones considering statistical uncertainties,
+while those labelled as ``\_FPF'' also include systematic errors.
 %
@@
 \label{fig:NNPDF40_pheno_integrated}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 For the fits with FPF data we display the variants where the covariance matrix
-consists only of statistical errors (``\_FPF'') and where also
-systematic errors are accounted for (``\_FPF$^*$'').
+consists only of statistical errors (``\_FPF$^*$'') and where also
+systematic errors are accounted for (``\_FPF'').
 %
@@
 \label{fig:NNPDF40_pheno_differential}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htbp]
+\begin{figure*}[htbp]
 	\centering
@@
 	\label{fig:PDF4LHC21_pheno_differential}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-11-14 referee/referee-reply.tex
Init. referee also for Max

\documentclass[11pt,a4paper]{article}
\usepackage{placeins}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{float}
\usepackage{afterpage}
\usepackage{amssymb,amsmath}
\usepackage{multirow,booktabs,multirow}
\usepackage{cite}
\usepackage[colorlinks=true, linkcolor=black!50!blue, urlcolor=blue, citecolor=blue, anchorcolor=blue]{hyperref}
\usepackage[font=small,labelfont=bf,margin=0mm,labelsep=period,tableposition=top]{caption}
\usepackage[a4paper,top=3cm,bottom=2.5cm,left=2.5cm,right=2.5cm,bindingoffset=0mm]{geometry}
\setlength{\unitlength}{1mm}

\usepackage{tabularx}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\smallfrac#1#2{\hbox{$\frac{#1}{#2}$}}
\newcommand{\be}{\begin{equation}}
	\newcommand{\ee}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
	\newcommand{\eea}{\end{eqnarray}}
\newcommand{\bi}{\begin{itemize}}
	\newcommand{\ei}{\end{itemize}}
\newcommand{\ben}{\begin{enumerate}}
	\newcommand{\een}{\end{enumerate}}
\newcommand{\la}{\left\langle}
\newcommand{\ra}{\right\rangle}
\newcommand{\lc}{\left[}
\newcommand{\rc}{\right]}
\newcommand{\lp}{\left(}
\newcommand{\rp}{\right)}
\newcommand{\as}{\alpha_s}
\newcommand{\aq}{\alpha_s\left( Q^2 \right)}
\newcommand{\amz}{\alpha_s\left( M_Z^2 \right)}
\newcommand{\aqq}{\alpha_s \left( Q^2_0 \right)}
\newcommand{\aqz}{\alpha_s \left( Q^2_0 \right)}
\newcommand{\Ord}{\mathcal{O}}
\newcommand{\MSbar}{\overline{\text{MS}}}
\def\toinf#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
			{#1\rightarrow\infty }}}}
\def\tozero#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
			{#1\rightarrow0 }}}}
\def\toone#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
			{#1\rightarrow1 }}}}
\def\frac#1#2{{{#1}\over {#2}}}
\def\gsim{\gtrsim}
\def\lsim{\lesssim}
\newcommand{\mrexp}{\mathrm{exp}}
\newcommand{\dat}{\mathrm{dat}}
\newcommand{\one}{\mathrm{(1)}}
\newcommand{\two}{\mathrm{(2)}}
\newcommand{\art}{\mathrm{art}} 
\newcommand{\rep}{\mathrm{rep}}
\newcommand{\net}{\mathrm{net}}
\newcommand{\stopp}{\mathrm{stop}}
\newcommand{\sys}{\mathrm{sys}}
\newcommand{\stat}{\mathrm{stat}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\pdf}{\mathrm{pdf}}
\newcommand{\tot}{\mathrm{tot}}
\newcommand{\minn}{\mathrm{min}}
\newcommand{\mut}{\mathrm{mut}}
\newcommand{\partt}{\mathrm{part}}
\newcommand{\dof}{\mathrm{dof}}
\newcommand{\NS}{\mathrm{NS}}
\newcommand{\cov}{\mathrm{cov}}
\newcommand{\gen}{\mathrm{gen}}
\newcommand{\cut}{\mathrm{cut}}
\newcommand{\parr}{\mathrm{par}}
\newcommand{\val}{\mathrm{val}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\checkk}{\mathrm{check}}
\newcommand{\reff}{\mathrm{ref}}
\newcommand{\Mll}{M_{ll}}
\newcommand{\extra}{\mathrm{extra}}
\newcommand{\draft}[1]{}
\newcommand{\comment}[1]{{\bf \it  #1}}
\newcommand{\muf}{\mu_\text{F}}
\newcommand{\mur}{\mu_\text{R}}

\def\beq{\begin{equation}}
	\def\eeq{\end{equation}}

\def\({\left(}
\def\){\right)}
\def\[{\left[}
\def\]{\right]}
\let\originalleft\left
\let\originalright\right
\renewcommand{\left}{\mathopen{}\mathclose\bgroup\originalleft}
\renewcommand{\right}{\aftergroup\egroup\originalright}

%\let\sectionold\section
%\renewcommand\section[2][]{%
	%\sectionold{\boldmath #2}}

\let\oldsubsection\subsection
\renewcommand\subsection[2][\subsectiontoc]{%
	\def\subsectiontoc{#2}%
	\oldsubsection[#1]{\boldmath #2}%
}

\let\oldsubsubsection\subsubsection
\renewcommand\subsubsection[2][\subsubsectiontoc]{%
	\def\subsubsectiontoc{#2}%
	\oldsubsubsection[#1]{\boldmath #2}%
}

\newcommand{\tmop}[1]{\ensuremath{\operatorname{#1}}}
\newcommand{\tmtextit}[1]{{\itshape{#1}}}
\newcommand{\tmtextrm}[1]{{\rmfamily{#1}}}
\newcommand{\tmtexttt}[1]{{\ttfamily{#1}}}

\usepackage{xcolor}
\definecolor{tpurple}{RGB}{128,0,128}
\definecolor{darkgreen}{RGB}{0,180,0}
\newcommand{\SM}[1]{\textbf{\textcolor{blue}  {SM: #1}}}
\newcommand{\MB}[1]{\textbf{\textcolor{red}   {MB: #1}}}
\newcommand{\MBn}[2]{\textcolor{red}{OLD: #1 NEW: #2}}
\newcommand{\LR}[1]{{\bf\color{orange}LR: #1}}
\newcommand{\todo}[1]{{\bf\color{red}TODO: #1}}
\newcommand{\JR}[1]{{\bf\color{purple}JR: #1}}
\newcommand{\SF}[1]{{\bf\color{darkgreen}SF: #1}}
\newcommand{\RDB}[1]{{\bf\color{cyan}RDB: #1}}

\begin{document}

\noindent
We would like to express our gratitude to the referee for the appreciation
of our work and for providing constructive
comments on our manuscript. The valuable feedback has been used to
improve the quality and clarity of our work.
%
In response to the suggestions, we address below each of the points raised by 
the referee and describe the actions that have been taken
in the revised version of the manuscript.

\noindent

\begin{enumerate}
	\item {\it Page 3, below (2.8). It is noted that nuclear corrections are not included when 
		interpreting the neutrino structure function data in terms of proton PDFs. It would be good
		to provide some brief discussion of the size of these and the associated uncertainties.
	}

	$\cdots$

	\item {\it able 2.2. It is not clear to me at the point where these numbers are produced exactly
		how the cross section inputs corresponding to these numbers are calculated. So I
		think a reference forward to Section 2.5, where the theory settings are described, is
		needed. Although even then, for completeness giving the PDF set that is used and
		some uncertain
		ty on the event rates here would be useful.
	}

	$\cdots$

	\item {\it Page 11. The discussion about consistency between the PDF set and theory settings
		used to produce the pseudodata and those entering the fit/profiling is in my view not
		correct or at least too strong. In particular, while it is perfectly reasonable to keep
		these the same there is definitely no requirement to, as is currently strongly implied in
		the discussion. In real PDF fits we often see that the fit quality for a given dataset does
		not follow textbook expectations, with $\chi^2/N \sim 1$. So some inconsistency between data
		and theory is often observed, rather than being artificial. Indeed, it is precisely because
		of this effect that tolerances (which are included in e.g. the PDF4LHC profiling) are
		included. In other words, one could perfectly reasonably generate pseudodata with a
		different PDF set, or different theory settings in order to emulate this inconsistency.
		One is free not to, but it should not be suggested that complete consistency is the only
		option here. It is a choice that is made, and not the only possible one.
	}

	$\cdots$

	\item {\it Page 15, and Fig. 3.3. Perhaps some explanation of why dV and to a lesser extend uV
		benefits from charge-lepton identification could be provided?
	}

	$\cdots$

	\item {\it Page 16, and Appendix A. The fact that the FASER$\nu$ (and SNDLHC) projections lead
		to a very limited improvement on the PDF uncertainties is rather hidden in a paragraph
		here, and then in the appendix. In my view, this ‘negative’ result should be given more
		prominence. It after all motivates the improvements that might come with the FPF. I
		would suggest moving this to the main body of the text and starting with this as the
		first study.
	}

	$\cdots$

	\item {\it Page 22. I am rather unsure about the approach for presenting results here, and in
		particular in showing numbers without including systematic errors, which are described
		as being ‘optimistic’. Having zero systematic uncertainties is surely unrealistic, rather
		than optimistic, so I feel as though a clearer justification for this needs to be given.
		Even more importantly, the labelling of the result without systematic uncertainties as
		‘FPF’ and those with as ‘FPF*’ is surely the wrong way round, given it implies that
		the case where the systematic uncertainties are not included is the default in some
		sense. So these should be swapped, and the rationale behind showing numbers without
		systematic uncertainties accounted for more clearly presented.
	}

	The referee is surely correct in that zero-systematic uncertainties is unrealistic. However,
	the reason to also show results with statistical uncertainties only is twofold. First, it
	substantiates the claim that FPF measurements will be statistically dominated. Second, in the
	ideal scenario (most optimistic) in which all the sources of systematic uncertainties are 
	under control, the statistic-only case would be the limit in terms of effects. It is also 
	worth noting that the estimation of the systematic uncertainties in our analysis is very 
	much conservative.

	According to the referee's suggestion, the results which only includes the statistical errors
	are labelled "FPF$\star$" while the one that also account for the systematics are labelled "FPF".

	\item {\it Section 4 and elsewhere. Given these are HL-LHC projections, somewhere these should
		be compared with the HL-LHC PDFs of Ref [34]. This would surely be the fairer
		comparison, or in any case will give a clearer picture of where things may stand.
	}

	$\cdots$

\end{enumerate}

\end{document}

### 2023-11-14 referee/referee-reply.tex
Push previous address to the referee

@@
 
-	$\cdots$
+	In order to address the need for a comment regarding the sizes of the nuclear corrections
+	in proton PDF fits, we have swapped the order of the last two sentences in that paragraph.
+	The cited references, and the references therein, provide ample discussion regarding the
+	the procedure to include nuclear corrections and their effects.
 
-	\item {\it able 2.2. It is not clear to me at the point where these numbers are produced exactly
+	\item {\it Table 2.2. It is not clear to me at the point where these numbers are produced exactly
 		how the cross section inputs corresponding to these numbers are calculated. So I
@@
 
-	$\cdots$
+	The numbers in Table 2.2 are computed by integrating the event yields shown in Eq.~2.12 in
+	which the differential cross sections are computed using the central value of the PDF4LHC21
+	set. For completeness, we have added a sentence above Eq. (2.16) that mention the exact
+	PDF set used to compute these numbers.
 
@@
 
-	$\cdots$
+	We have slightly rephrased the subsequent sentences to make it clear that the improvements
+	seen in $d_v$ and to a lesser extend $u_v$ can be fully understood by looking at LO expressions
+	of the structure functions in terms of the PDFs for $\nu$ and $\bar{\nu}$.
 
@@
 
-	$\cdots$
+	The main reason the study of the constraints provided by FASER$\nu$ in the Appendix is because
+	the study in Section 3 is mainly dedicated to the FPF experiments. We nevertheless agree with the
+	referee such findings should be highlighted and used as a motivation for the FPF. In this regard, we
+	have added two sentences in the introductory paragraph of Section to describe this.
 
@@
 
-	According to the referee's suggestion, the results which only includes the statistical errors
+	Following the referee's suggestion, the results which only includes the statistical errors
 	are labelled "FPF$\star$" while the one that also account for the systematics are labelled "FPF".
@@
 
-	$\cdots$
+	The reason why we did not provide comparisons with the HL-LHC PDFs of ref. [34] is because
+	the pseudodata used to determine these PDFs were produced with the PDF4LHC15 set which
+	does not account for the recent LHC measurements. The most consistent comparisons would
+	be to re-do the analysis done in ref. [34] and then compare the resulting PDFs with our 
+	determination.
 

### 2023-11-14 journal_sub/sec-dis-pseudodata.tex
Push previous address to the referee

@@
  In the projections presented here, when interpreting the LHC neutrino structure
- functions in terms of proton PDFs, we will assume a isoscalar free-nucleon target and neglect
+ functions in terms of proton PDFs, we will assume an isoscalar free-nucleon target and neglect
  nuclear PDF modifications, along the lines of Eq.~(\ref{eq:neutrinoSFs_isoscalar}).
+  %
+ Accounting for nuclear modifications in a global proton
+ PDF fit is possible by means of the procedure developed
+ in~\cite{Ball:2020xqw,Ball:2018twp} based on
+ the theory covariance matrix approach~\cite{NNPDF:2019vjt,NNPDF:2019ubu}.
  %
@@
  the target is not isoscalar when evaluating the physical observables.
- %
- Accounting for nuclear modifications in a global proton
- PDF fit is possible by means of the procedure developed
- in~\cite{Ball:2020xqw,Ball:2018twp} based on
- the theory covariance matrix approach~\cite{NNPDF:2019vjt,NNPDF:2019ubu}.
 
@@
 and muon neutrinos and antineutrinos.
+%
+We used the PDF4LHC21 set to compute the differential cross sections that enter in Eq.~\ref{eq:event_yields_calculation}.
 %

### 2023-11-14 journal_sub/sec-results.tex
Add epjc typeset version
Push previous address to the referee

--- 2023-09-18 paper/sec-results.tex
@@
 results for their combination.
+%
+For completeness, we study in App.~\ref{app:fasernu_runIII_impact} the constraints on PDFs 
+provided by the forward experiments, namely FASER$\nu$. The results show that measurements
+at FASERV$\nu$ are unable to improve the determination of PDFs therefore strengthening the
+need for the FPF experiments.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
+\begin{figure*}[t]
 \centering
@@
 \label{fig:FASERnu2_baseline}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
+\begin{figure*}[t]
 \centering
@@
 \label{fig:FASERnu2_nocharm}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{fig:FASERnu2_nochargeID}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %
-This behaviour can be understood by inspecting the leading-order decomposition of neutrino DIS
-structure functions in terms of PDFs for different targets, Eqns.~(\ref{eq:neutrinoSFs_proton})--(\ref{eq:neutrinoSFs_isoscalar}).
+Such an improvement can be understood by inspecting the leading-order decomposition of neutrino DIS
+structure functions in terms of the different PDF flavours for different targets, Eqns.~(\ref{eq:neutrinoSFs_proton})--(\ref{eq:neutrinoSFs_isoscalar}).
 %
@@
 \label{fig:FASERnu2_FLAre10}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
+\begin{figure*}[t]
 \centering
@@
 \label{fig:FPF_combined}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
+\begin{figure*}[t]
 \centering
@@
 \label{fig:NNPDF40_baseline}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{fig:NNPDF40_lowQ_abs}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %-----------------------------------------------------------------------
-\begin{table}[!t]
+\begin{table*}[!t]
   \centering
@@
 }
-\end{table}
+\end{table*}
 %--------------------------------------------------------------------------
@@
 \label{fig:nnpdf40_fpf_lumis}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{fig:profiling_FPF_nuclear}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-11-14 referee/referee-reply.tex
more ref comments

@@
 
+\noindent
+We now address the comments of referee B
+
+\begin{enumerate}
+\item{\it Page 3, lines 34-36 column 2 “since in general the strange and charm … not expected to vanish”. I agree but I suggest adding a reference or a comment supporting this statement. }
+
+We have added the following references which explore strange and charm PDF asymmetries Sufian:2018cpj, Sufian:2020coz
+
+\item{\it p. 4 l. 30-35 col.2 “Also, to identify… event yields.” Why a cut on the hadronic energy should properly simulate a cut on the number of charged tracks emerging from the interaction vertex?}
+
+The charged track multiplicity is expected to grow with the hadronic system’s invariant mass.
+We make this clear and cite a neutrino-Hydrogen interaction multiplicity study (Aachen-Bonn-CERN-Munich-Oxford:1981lfk) as well as a FASER paper (FASER:2019dxq) which also point this out.
+We also append this sentence:
+
+"…, as the charged track multiplicity is expected to grow with $W$~\cite{Aachen-Bonn-CERN-Munich-Oxford:1981lfk,FASER:2019dxq}."
+
+\item{\it Table 2.1 What is the meaning of the asterisk in “FLArE (*)”? I cannot see it referred to in the caption}
+
+The meaning of the asterisk was to be clear that this row represents 2 proposed detectors, as opposed to the remaining rows which are each one detector.
+We make this clear by appending the end of the caption:
+
+"…, which we denote for the two detectors as as FLArE(*)."
+
+\item{\it  p.5 l. 38 col.2 “is made of thin sensitive layers” What is the material/detector the layers are made of?}
+
+{\color{red} [MF: Not clear, Whitepaper says the same thing. Need to look closer or say that we don't know]}
+
+\item{\it  p.5 l.49 col 1 and col 2 (“AdvSND” and “FLArE”) Can you put a reference about these experiments? Did you take the info from ref [10]?}
+
+We have added the original flare proposal paper as well as the whitepaper (ref[10]) to the FLArE section. For AdvSND, we have added included the whitepaper
+
+\item{\it p.6 l.
+50-53 col.2 “Here we neglect efficiency ..
+simulation.” I am aware that this might be difficult to simulate at this stage but I think this effect is non-negligible due to misidentification ( a large background could enter this sample).
+Can you comment further on it?
+In addition, some guesses on misidentification capabilities can be drawn by the current FASER and SND@CERN capabilities.}
+
+Indeed, misidentification is not expected to be negligible.
+While there are no detailed studies on efficiencies, as we point out in the paper charm tagging can be done by through multiple methods, including reconstructing the topology of D-meson decays, and through dimuon events.
+With multiple techniques, one can draw the conclusion that that charm-tagging efficiency is not small.
+{\color {red} [MF: looking for quantitative perofrmances/efficiencies, can't find anything. Is there more we can say?}
+
+\item{\it p.9 l.
+41-43 col.2 “We note that … in our estimation.” (see also the conclusions p.
+27 l.
+52-55 col.1) I am puzzled by this statement.
+It is well known that flux systematics in Faser and SND@CERN play a prominent role and set the normalization (and shape?) of eqn 2.12.
+How can you ignore such an important effect in your analyses?
+Even if the PDF constraints are marginally affected by the normalization of the neutrino flux, some of your considerations about the on-axis (faser and faser2) versus the off-axis experiments (SND@CERN and its upgrades) may be affected by flux uncertainties.
+Can you comment on it in the paper?}
+
+Indeed, neutrino flux uncertainties are well established, and the shape and normalization of the flux can vary widely between different models.
+It is important to note that neutrino measurements actually constrain the product of flux and cross-section - each of these components brings an uncertainty with it, and a full analysis with real data would constrain them simultaneously.
+We wish to motivate this joint analysis by calculating the  impact that FPF data can bring to a PDF fit.
+In this sense, by taking the flux to be known we can understand the full reach of FPF data on cross-section measurements, analogous to what was done in 2309.10417.
+Moreover, projections of FPF data on flux measurements has shown that HL-LHC data can bring flux uncertainties to a sub-percent level.
+We thank the referee for this important point and add the following paragraph after we introduce the flux model in the middle of section 2.3.
+
+"As pointed out in Ref.~\cite{Kling:2021gos} there are notable neutrino flux uncertainties, as various event generators do not agree on the forward parent hadron spectra.
+The spread of the generators' predictions can be taken as a means of flux uncertainty, in which case there is a $\lesssim 50\%$ uncertainty on the interacting muon neutrino spectrum --- if left unresolved this would be a significant systematic.
+Indeed, there are already projections of FPF measurements which would reduce this uncertainty~\cite{Kling:2023tgr} as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}.
+However, it is important to note that forward neutrino experiments actually constrain the product of flux and cross-section, and one must be assumed to measure the other.
+In a full analysis, they would be constrained simultaneously in a joint measurement.
+In our study, we aim to understand the full impact of FPF data on the PDF fit, thus motivating this future joint measurement.
+To this aim, we take the neutrino flux to be known and focus on the irreducible systematics associated with event reconstruction."
+
+\item{\it p.11 l.
+33-37 col.1 Are you sure that an assumption of $f_{corr}$ = 0.5 is realistic?
+The estimates made in ref.[34] are for LHC experiments, not for fixed-target experiments like those of the FPF.}
+
+\item{\it  Fig. 2.4 In the bottom-left plot, I see a sharp increase in the fractional error at about x= 4 e-2. Why?}
+{\color{red} [MF: Probably a binning effect, will think about it.]}
+
+\item{\it p.19 l.50-53 col 1 and in general along the paper: I cannot see a discussion of the impact of neutral-current events at the FPF. Can you further comment on it?}
+
+There are expected to be roughly as many neutral current neutrino scattering events as charged current events.
+However, due to the lack of information on both the incoming and outgoing neutrino, the full event cannot be reconstructed, only the total hadronic energy can be measured.
+One could try to use the total NC event rate as a means of constraining the integrated PDF, however we expect that this would negligibly improve the impact on the PDF constraints as compared to fully reconstructed CC events.
+{\color{red} [MF: Does this agree with others' understanding?]}
+
+\end{enumerate}
+
 \end{document}

### 2023-11-14 journal_sub/sec-dis-pseudodata.tex
more ref comments

@@
 the neutrino flux has been updated to $\sqrt{s} = 13.6~{\rm TeV}$.
+
+%
+As pointed out in Ref.~\cite{Kling:2021gos} there are notable neutrino flux uncertainties, as various event generators do not agree on the forward parent hadron spectra. 
+%
+The spread of the generators' predictions can be taken as a means of flux uncertainty, in which case there is a $\lesssim 50\%$ uncertainty on the interacting muon neutrino spectrum --- if left unresolved this would be a significant systematic.
+Indeed, there are already projections of FPF measurements which would reduce this uncertainty~\cite{Kling:2023tgr} as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}.
+%
+However, it is important to note that forward neutrino experiments actually constrain the product of flux and cross-section, and one must be assumed to measure the other.
+In a full analysis,  they would be constrained simultaneously in a joint measurement.
+%
+In our study, we aim to understand the full impact of FPF data on the PDF fit, thus motivating this future joint measurement.
+%
+To this aim, we take the neutrino flux to be known and focus on the irreducible systematics associated with event reconstruction.
 

### 2023-11-15 referee/referee-reply.tex
minor updates

@@
 	in proton PDF fits, we have swapped the order of the last two sentences in that paragraph.
-	The cited references, and the references therein, provide ample discussion regarding the
+	The cited references, and the references therein, provide extensive discussions regarding
 	the procedure to include nuclear corrections and their effects.
@@
 	set. For completeness, we have added a sentence above Eq. (2.16) that mention the exact
-	PDF set used to compute these numbers.
+	PDF set used to compute these numbers. Although
+	Section 2.5 indeed provides some descriptions regarding the computation of the differential cross sections
+	(which were also described in Section 2.1), it mainly focuses on the construction of the pseudodata
+	needed for the fit/re-weighting.
 
@@
 
-	$\cdots$
+	\textcolor{blue}{(TR) I was not sure how to best address this. We might indeed need to tone this down
+	a bit but I was not sure how to properly do so.}
 
@@
 	We have slightly rephrased the subsequent sentences to make it clear that the improvements
-	seen in $d_v$ and to a lesser extend $u_v$ can be fully understood by looking at LO expressions
-	of the structure functions in terms of the PDFs for $\nu$ and $\bar{\nu}$.
+	seen in $d_v$ and to a lesser extend in $u_v$ can be fully understood by looking at analytical 
+	LO expressions of the structure functions in terms of the PDFs for $\nu$ and $\bar{\nu}$.
 
@@
 
-	The main reason the study of the constraints provided by FASER$\nu$ in the Appendix is because
-	the study in Section 3 is mainly dedicated to the FPF experiments. We nevertheless agree with the
-	referee such findings should be highlighted and used as a motivation for the FPF. In this regard, we
+	The main reason to put the study of the constraints provided by FASER$\nu$ in the Appendix is because
+	the analysis in Section 3 is mainly dedicated to the FPF experiments. We nevertheless agree with the
+	referee that such findings should be highlighted and used as a motivation for the FPF. In this regard, we
 	have added two sentences in the introductory paragraph of Section to describe this.
@@
 	ideal scenario (most optimistic) in which all the sources of systematic uncertainties are 
-	under control, the statistic-only case would be the limit in terms of effects. It is also 
-	worth noting that the estimation of the systematic uncertainties in our analysis is very 
-	much conservative.
+	under control, the statistic-only case would be the limit in terms of constraints on PDF
+	determination.  It is also worth noting that the estimation of the systematic uncertainties in our 
+	analysis is very  much conservative.
 
@@
 	does not account for the recent LHC measurements. The most consistent comparisons would
-	be to re-do the analysis done in ref. [34] and then compare the resulting PDFs with our 
-	determination.
+	be to re-do the analysis done in ref. [34] using PDF4LHC21 and then compare the resulting PDFs 
+	with our determination.
 
@@
 With multiple techniques, one can draw the conclusion that that charm-tagging efficiency is not small.
-{\color {red} [MF: looking for quantitative perofrmances/efficiencies, can't find anything. Is there more we can say?}
+{\color {red} [MF: looking for quantitative perofrmances/efficiencies, can't find anything. Is there more we can say?]}
 

### 2023-11-16 referee/referee-reply.tex
some further updates

@@
 
-{\color{red} [MF: Not clear, Whitepaper says the same thing. Need to look closer or say that we don't know]}
+The target layers are interleaved with tungsten and emulsion. We make this clear by ammending this sentence:
+
+"...sensitive layers of emulsion..."
 
@@
 Indeed, misidentification is not expected to be negligible.
-While there are no detailed studies on efficiencies, as we point out in the paper charm tagging can be done by through multiple methods, including reconstructing the topology of D-meson decays, and through dimuon events.
+While there are no detailed studies of charm tagging efficiencies at the FPF, as we point out in the paper charm tagging can be done by through multiple methods, including reconstructing the topology of D-meson decays, and through dimuon events.
 With multiple techniques, one can draw the conclusion that that charm-tagging efficiency is not small.
-{\color {red} [MF: looking for quantitative perofrmances/efficiencies, can't find anything. Is there more we can say?]}
+{\color {red} [MF: looking for quantitative perofrmances/efficiencies, can't find anything. Is there more we can say? We could look at older experiments]}
 
@@
 
+{\color{red} [MF: can someone comment here?]}
+
 \item{\it  Fig. 2.4 In the bottom-left plot, I see a sharp increase in the fractional error at about x= 4 e-2. Why?}
-{\color{red} [MF: Probably a binning effect, will think about it.]}
+
+The points near $x$=4e-2 with large uncertainties have small $E_h$, and are approaching the $E_h>100~ {\rm GeV}$ threshold that we set in Table 2.1.
+When we fluctuate the data according to our definition of uncertainty (Eq.
+2.19 with $E_h$ instead of $E_{\ell}$), these points drop below the acceptance and thus contribute to a fluctuation in this bin.
 
@@
 One could try to use the total NC event rate as a means of constraining the integrated PDF, however we expect that this would negligibly improve the impact on the PDF constraints as compared to fully reconstructed CC events.
-{\color{red} [MF: Does this agree with others' understanding?]}
+{\color{red} [MF: Does this agree with others' understanding, should we add something to the paper?
+There is the possibility of using muons with NC for PDF constraints, which we could comment on.]}
 

### 2023-11-16 journal_sub/sec-dis-pseudodata.tex
minor updates
some further updates

@@
  %
- The target region of the detector, where the neutrino interactions take place, is made of thin sensitive layers 
- interleaved with tungsten plates, for a total mass of 5 tonnes and fiducial length of 50 cm.
+ The target region of the detector, where the neutrino interactions take place, is made of thin sensitive layers of emulsion interleaved with tungsten plates, for a total mass of 5 tonnes and fiducial length of 50 cm.
  %
@@
 %
-DIS structure functions are evaluated at NLO in the QCD expansion
+DIS structure functions are evaluated at NNLO in the QCD expansion
 and account both for heavy quark and target mass effects.

### 2023-11-16 referee/referee-reply.tex
small corrections

@@
 While there are no detailed studies of charm tagging efficiencies at the FPF, as we point out in the paper charm tagging can be done by through multiple methods, including reconstructing the topology of D-meson decays, and through dimuon events.
-With multiple techniques, one can draw the conclusion that that charm-tagging efficiency is not small.
+With multiple techniques, one can draw the conclusion that charm-tagging efficiency is not small.
 {\color {red} [MF: looking for quantitative perofrmances/efficiencies, can't find anything. Is there more we can say? We could look at older experiments]}
@@
 The spread of the generators' predictions can be taken as a means of flux uncertainty, in which case there is a $\lesssim 50\%$ uncertainty on the interacting muon neutrino spectrum --- if left unresolved this would be a significant systematic.
-Indeed, there are already projections of FPF measurements which would reduce this uncertainty~\cite{Kling:2023tgr} as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}.
+Indeed, there are already projections of FPF measurements which would reduce this uncertainty to the sub-percent level~\cite{Kling:2023tgr} as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}.
 However, it is important to note that forward neutrino experiments actually constrain the product of flux and cross-section, and one must be assumed to measure the other.

### 2023-11-16 journal_sub/sec-dis-pseudodata.tex
small corrections

@@
 The spread of the generators' predictions can be taken as a means of flux uncertainty, in which case there is a $\lesssim 50\%$ uncertainty on the interacting muon neutrino spectrum --- if left unresolved this would be a significant systematic.
-Indeed, there are already projections of FPF measurements which would reduce this uncertainty~\cite{Kling:2023tgr} as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}.
+Indeed, there are already projections of FPF measurements which would reduce this uncertainty to the sub-percent level~\cite{Kling:2023tgr} as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}.
 %

### 2023-11-21 referee/referee-reply.tex
reply to referee

@@
 in the revised version of the manuscript.
+%
+To facilitate the review process, in the revised version of the manuscript
+we have highlighted all the changes that have been made with respect to the original
+submission.
 
@@
 	which the differential cross sections are computed using the central value of the PDF4LHC21
-	set. For completeness, we have added a sentence above Eq. (2.16) that mention the exact
-	PDF set used to compute these numbers. Although
+	set. For completeness, we have added a sentence above Eq. (2.16) that mention the specific
+	PDF set used to compute these numbers, and where we also indicate that the calculation
+        is performed at NLO in the QCD expansion.
+        %
+        Although
 	Section 2.5 indeed provides some descriptions regarding the computation of the differential cross sections
 	(which were also described in Section 2.1), it mainly focuses on the construction of the pseudodata
-	needed for the fit/re-weighting.
+	needed for the fit/profiling.
+
+        This said, we would like to emphasize that the predicted event rates in Table 2.2 depend
+        only mildly on the specific settings of the DIS cross-section entering the calculation.
+        %
+        Furthermore, these event rates are only used to determine the expected bib-by-bin
+        statistical uncertainty.
+        %
+        Hence our results are relatively independent on the theoretical settings
+        entering the calculation of the event yields in Table 2.2.
 
@@
 
-	\textcolor{blue}{(TR) I was not sure how to best address this. We might indeed need to tone this down
-	a bit but I was not sure how to properly do so.}
+          We agree with the referee that, when generating pseudo-data, one may or may not want to
+          assume the same underlying truth as in the prior of the corresponding PDF fit.
+          %
+          Indeed, data inconsistencies are present in real data.
+
+          Our motivation to keep these settings consistent is that we would like to investigate
+          what is the PDF constraining power of the FPF measurements
+          assuming that there are no inconsistencies,
+          which is the best-case scenario.
+          %
+          In the presence of inconsistencies one finds two effects: a shift in the central value
+          of the PDF and a reduction of the PDF error whose magnitude depends on the assumed
+          inconsistencies.
+          %
+          For example, if we generate the FPF pseudo-data far from the PDF4LHC21 prior,
+          the main impact of the data will be to shift the central prediction, rather than
+          to reduce the uncertainty.
+
+          Another reason to assume this consistency  is that when carrying out Hessian profiling,
+          one keeps the PDF parametrisation fixed. In the presence of inconsistencies, it may be
+          that the best fit with FPF data requires a different parametrisation and hence
+          a different PDF error analysis.
+          %
+          So Hessian profiling is most reliable in the absence of data inconsistencies.
+
+          In the revised version of the paper, we have emphasized our two-fold region
+          to assume full consistency between the prior PDF and the FPF pseudo-data: to
+          quantify the PDF reach of the FPF pseudo-data in the most advantageous scenario,
+          and to ensure the procedural validity of the Hessian profiling procedure.
+
+          This said, the suggestion from the referee to generate data with an ``inconsistent'' PDF
+          set is valuable and it would be interesting to carry out this exercise in the future.
 
@@
 With multiple techniques, one can draw the conclusion that charm-tagging efficiency is not small.
-{\color {red} [MF: looking for quantitative perofrmances/efficiencies, can't find anything. Is there more we can say? We could look at older experiments]}
+{\color {red} [MF: looking for quantitative performances/efficiencies, can't find anything. Is there more we can say? We could look at older experiments]}
 

### 2023-11-21 referee/referee-reply.tex
referee reply

@@
 
-          Our motivation to keep these settings consistent is that we would like to investigate
+          Our motivation to keep these settings consistent is that in this work we aim to investigate
           what is the PDF constraining power of the FPF measurements
@@
           %
-          In the presence of inconsistencies one finds two effects: a shift in the central value
+          In the presence of inconsistencies, one finds two competing effects: a shift in the central value
           of the PDF and a reduction of the PDF error whose magnitude depends on the assumed
@@
           set is valuable and it would be interesting to carry out this exercise in the future.
+          %
+          To emphasize this, we have added a sentence stating that generating pseudo-data with a different
+          PDF set from the prior would test the capabilities of the FPF to disentangle between
+          different PDF sets among them.
 
@@
 	We have slightly rephrased the subsequent sentences to make it clear that the improvements
-	seen in $d_v$ and to a lesser extend in $u_v$ can be fully understood by looking at analytical 
-	LO expressions of the structure functions in terms of the PDFs for $\nu$ and $\bar{\nu}$.
+	seen in $d_V$ and to a lesser extend in $u_V$ can be understood by looking at analytical 
+	LO expressions of the structure functions in terms of the PDFs for $\nu$ and $\bar{\nu}$
+        provided in Sect.~2.
 
-	\item {\it Page 16, and Appendix A. The fact that the FASER$\nu$ (and SNDLHC) projections lead
+	\item {\it Page 16, and Appendix A. The fact that the FASER$\nu$ (and SND@LHC) projections lead
 		to a very limited improvement on the PDF uncertainties is rather hidden in a paragraph
@@
 
-	The main reason to put the study of the constraints provided by FASER$\nu$ in the Appendix is because
+	The main reason to put the study of the constraints provided by FASER$\nu$ in the Appendix was because
 	the analysis in Section 3 is mainly dedicated to the FPF experiments. We nevertheless agree with the
-	referee that such findings should be highlighted and used as a motivation for the FPF. In this regard, we
-	have added two sentences in the introductory paragraph of Section to describe this.
+	referee that such findings should be highlighted and used as a motivation for the FPF.
+        %
+        We have moved App. A to the first subsection of Sect 3, to highlight that the ultimate
+        constraining power of LHC neutrino experiments can only be realised with the FPF.
+
+        Actually, this result is also relevant concerning another points raised by the referee below:
+        the fact that the FASER$\nu$ and SND@LHC data not not impact the PDFs indicates that the
+        interpretation of their event rate measurements depends only loosely on the modelling
+        of the deep-inelastic scattering interaction.
+        %
+        Hence, the FASER$\nu$ and SND@LHC data can be safely used to tune the incoming neutrino fluxes
+        and learn for example about PDFs at very small-$x$, without compromising
+        the validity of the interpretation.
+        %
+        So this ``null result'' is also relevant in this context, and motivates the use of the current
+        FASER$\nu$ and SND@LHC data to validate models of charm production, forward light hadron
+        production, and small-$x$ QCD.
 
@@
 
-	The referee is surely correct in that zero-systematic uncertainties is unrealistic. However,
+	  The referee is surely correct in that zero-systematic uncertainties is not realistic.
+          %
+          However,
 	the reason to also show results with statistical uncertainties only is twofold. First, it
-	substantiates the claim that FPF measurements will be statistically dominated. Second, in the
-	ideal scenario (most optimistic) in which all the sources of systematic uncertainties are 
-	under control, the statistic-only case would be the limit in terms of constraints on PDF
-	determination.  It is also worth noting that the estimation of the systematic uncertainties in our 
-	analysis is very  much conservative.
+	substantiates the claim that FPF measurements will be dominated by systematics, rather
+        than statistical uncertainties, which is a very important and non-trivial consideration
+        informing detector design. The FPF detectors have not been designed with ``precision physics'' as main
+        goal, and showing that improving systematics has strong physics benefits is important
+        in the context of these studies.
+        %
+        Note that this is not the case in FASER$\nu$ and SND@LHC, where the physics reach
+        (at least concerning proton structure studies via neutrino DIS) is completely
+        limited by the low statistics available.
 
-	Following the referee's suggestion, the results which only includes the statistical errors
-	are labelled "FPF$\star$" while the one that also account for the systematics are labelled "FPF".
+        Second, and perhaps most importantly, we cannot claim to have a fully realistic modelling
+        of systematic errors, and in particular we miss a detailed estimate of their correlation, which
+        is known to be decisive in stablishing the PDF sensitivity.
+        %
+        Such analysis can only be carried by the experimental collaborations themselves and
+        be based on a complete detector simulation, and indeed our study provides
+        a strong motivation for this.
+        %
+        In this respect,  it is also worth noting that the estimation of the systematic uncertainties in our 
+	analysis is very  much conservative, and already the insights provided by our paper
+        are helping the experimentalists to improve designs to reduce systematics.
+        %
+        So there is a clear added value in separating the two scenarios.
+
+	Following the referee's suggestion, the results which only include the statistical errors
+	are now labelled "FPF$\star$" while the one that also account for the systematics are labelled "FPF".
+        %
+        We have also extended the rationale for showing results in the statistics-only scenario, alongside the
+        considerations described above.
 
@@
 	with our determination.
+
+        This said, to answer the point of the referee, we have repeated the phenomenological study of Sect 4
+        comparing PDF4LHC15 with PDF4LHC15+HLHC PDFs for the same processes.
+        %
+        We show below the results for the same inclusive cross-sections as in Sect 4.
+        %
+        As it can be seen from this comparison.
+        %
+        We have added to the paper an Appendix where the pheno study of Sect 4 is repeated
+        now for the PDF4LHC15 with PDF4LHC15+HLHC PDFs.
+
+        Further, as mentioned in the paper, the PDF constraints from the FPF and from the HL-LHC are
+        fully orthogonal and complementary, and the former have the very important property that
+        possible contamination from new physics on the PDF fits can be completely ignored, since
+        this process is driven by $Q^2$ values where we know QCD holds.
 

### 2023-11-21 referee/referee-reply.tex
done revised referee reply

@@
 
-	The reason why we did not provide comparisons with the HL-LHC PDFs of ref. [34] is because
+	The reason why we did not provide comparisons with the HL-LHC PDFs of Ref. [34] is because
 	the pseudodata used to determine these PDFs were produced with the PDF4LHC15 set which
@@
 	be to re-do the analysis done in ref. [34] using PDF4LHC21 and then compare the resulting PDFs 
-	with our determination.
+	with our determination, something which is clearly outside the scope of this paper.
 
-        This said, to answer the point of the referee, we have repeated the phenomenological study of Sect 4
+        This said, to answer the question from the referee, we have repeated the phenomenological study of Sect 4
         comparing PDF4LHC15 with PDF4LHC15+HLHC PDFs for the same processes.
         %
-        We show below the results for the same inclusive cross-sections as in Sect 4.
+        Specifically, we have added to the paper an Appendix where the phenomenology study of Sect 4 is repeated
+        now for the PDF4LHC15 with PDF4LHC15+HLHC PDFs.
         %
-        As it can be seen from this comparison.
-        %
-        We have added to the paper an Appendix where the pheno study of Sect 4 is repeated
-        now for the PDF4LHC15 with PDF4LHC15+HLHC PDFs.
+        From this comparison, one can observe that .... ADD
 
-        Further, as mentioned in the paper, the PDF constraints from the FPF and from the HL-LHC are
+        Furthermore, as mentioned in the paper, the PDF constraints from the FPF and from the HL-LHC are
         fully orthogonal and complementary, and the former have the very important property that
         possible contamination from new physics on the PDF fits can be completely ignored, since
-        this process is driven by $Q^2$ values where we know QCD holds.
+        this process is driven by $Q^2$ values outside the possible presence of BSM physics.
+        %
+        Specially should a large-mass anomaly be revealed at the HL-LHC, having the fully independent
+        validation of the large-$x$ PDFs provided by the FPF would be extremely valuable for its
+        interpretation.
 
@@
 
-We have added the following references which explore strange and charm PDF asymmetries Sufian:2018cpj, Sufian:2020coz
+  We have added the following references which explore strange and charm PDF asymmetries Sufian:2018cpj, Sufian:2020coz.
+  %
+  We have also added a reference to the recent NNPDF study of the intrinsic charm asymmetry in the proton,
+  showing that these effects are potentially sizable and could hence be relevant for the interpretation
+  of the FPF measurements.
 
@@
 
-"…, as the charged track multiplicity is expected to grow with $W$~\cite{Aachen-Bonn-CERN-Munich-Oxford:1981lfk,FASER:2019dxq}."
+"…, as the charged track multiplicity is expected to grow with the invariant mass of the hadronic
+final state $W$~\cite{Aachen-Bonn-CERN-Munich-Oxford:1981lfk,FASER:2019dxq}."
 
@@
 
-We have added the original flare proposal paper as well as the whitepaper (ref[10]) to the FLArE section. For AdvSND, we have added included the whitepaper
+  We have added the original FLArE experiment proposal paper as well as the FPF whitepaper (ref[10]) to the FLArE section.
+For AdvSND, we have added included the reference to the FPF whitepaper, which is currently the most detailed
+  description of this proposed experiment.
 
@@
 
-Indeed, misidentification is not expected to be negligible.
-While there are no detailed studies of charm tagging efficiencies at the FPF, as we point out in the paper charm tagging can be done by through multiple methods, including reconstructing the topology of D-meson decays, and through dimuon events.
-With multiple techniques, one can draw the conclusion that charm-tagging efficiency is not small.
-{\color {red} [MF: looking for quantitative performances/efficiencies, can't find anything. Is there more we can say? We could look at older experiments]}
+  Indeed, uncertainties due to misidentification are in general not expected to be negligible.
+%
+  While there are no detailed studies of charm tagging efficiencies at the FPF, as we point out in the paper, charm tagging can be done by through multiple methods, including reconstructing the topology of $D$-meson decays, and through dimuon events.
+With multiple techniques at hand, one should be able to determine in-situ quite well the $D$-meson tagging efficiencies, for example comparing the dimuon selection method with the charm tagging via the emulsion detector.
+Furthermore, the availability of different experiments based on complementary techniques will help to cross-calibrate these effects.
+
+It is worth pointing out that our framework is flexible enough to accomodate variations in the modelling of systematic uncertainties, and in particular there is no conceptual issue preventing anyone to repeat our analysis for different treatments of efficiencies and other related experimental parameters.
 
@@
 
-Indeed, neutrino flux uncertainties are well established, and the shape and normalization of the flux can vary widely between different models.
+  Indeed, the large neutrino flux uncertainties are well established, and the shape and normalization of the flux can vary widely between different models, although the neutrino muon component which is mostly relevant for neutrino DIS experiments is the one which is known the best.
+
   It is important to note that neutrino measurements actually constrain the product of flux and cross-section - each of these components brings an uncertainty with it, and a full analysis with real data would constrain them simultaneously.
@@
 
+  We would like to raise two more considerations which justify, in this work, to assume that the incoming neutrino
+  fluxes are known:
+  \begin{itemize}
+  \item As shown in appendix A, now moved to Sect 3, FASER$\nu$ and SND@LHC data from run III do not have sensitivity on the modelling of the neutrino-nucleus interaction cross-section.
+    %
+    This means that these measurements can be safely used, before the start of the FPF, to cross-calibrate
+    incoming neutrino fluxes and markedly improve their predictions for subsequent analysis.
+    %
+    Just due to this, by the time the FPF starts data taking the neutrino fluxes will be known
+    more precisely than now.
+
+  \item The flux and the neutrino DIS cross-section have very different kinematic dependences.
+    %
+    The incoming nuetrino flux is mostly fixed from the $(E_\nu, y_\nu)$ dependence of the event rates,
+    while the PDFs in the DIS cross-section are fixed by the $(x,Q^2)$ dependence.
+    %
+    By measuring event rates differentially in the three kinematic variables $(E_\nu, x,Q^2)$, and also
+    accessing the $y_\nu$ dependence of the incoming neutrinos, one can efficiency disentangle the
+    fluxes from the DIS cross-section.
+    %
+    Of course, one needs to explicitely demonstrate this via a dedicated analysis, but there
+    is no conceptual reason preventing us from this goal.
+
+   \end{itemize}
+
 \item{\it p.11 l.
@@
 
-{\color{red} [MF: can someone comment here?]}
+  In the absence of full detector simulation and detailed correlation model, it is not possible to answer
+  this point conclusively.
+  %
+  What we can say is that we have repeated our analysis for $f_{corr}=1$ and find that our main
+  qualitative conclusions remain unchanged.
 
@@
 2.19 with $E_h$ instead of $E_{\ell}$), these points drop below the acceptance and thus contribute to a fluctuation in this bin.
+  %
+  We have added to the revised version of the paper a short discussion to explain this observation.
 
@@
 One could try to use the total NC event rate as a means of constraining the integrated PDF, however we expect that this would negligibly improve the impact on the PDF constraints as compared to fully reconstructed CC events.
-{\color{red} [MF: Does this agree with others' understanding, should we add something to the paper?
-There is the possibility of using muons with NC for PDF constraints, which we could comment on.]}
+Indeed, if anything, NC scattering brings in less sensitivity to PDFs than CC events, as can be seen from the LO decomposition of the corresponding structure functions.
+
+  We have added to Sect 2 a short discussion on why it is very likely that NC events do not provide useful PDF information: first of all, event kinematics cannot be reconstructed on an event by event basis as in the CC case, second, that systematics will be large since are dominated by the hadronic final state, and third, that NC scattering in general provides less complete information on the PDF flavour decomposition as compared to CC scattering.
 

### 2023-11-21 referee/referee-reply.tex
Extra Flux points from Juan

@@
 Moreover, projections of FPF data on flux measurements has shown that HL-LHC data can bring flux uncertainties to a sub-percent level.
-We thank the referee for this important point and add the following paragraph after we introduce the flux model in the middle of section 2.3.
-
-  "As pointed out in Ref.~\cite{Kling:2021gos} there are notable neutrino flux uncertainties, as various event generators do not agree on the forward parent hadron spectra.
-The spread of the generators' predictions can be taken as a means of flux uncertainty, in which case there is a $\lesssim 50\%$ uncertainty on the interacting muon neutrino spectrum --- if left unresolved this would be a significant systematic.
-Indeed, there are already projections of FPF measurements which would reduce this uncertainty to the sub-percent level~\cite{Kling:2023tgr} as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}.
-However, it is important to note that forward neutrino experiments actually constrain the product of flux and cross-section, and one must be assumed to measure the other.
-In a full analysis, they would be constrained simultaneously in a joint measurement.
-In our study, we aim to understand the full impact of FPF data on the PDF fit, thus motivating this future joint measurement.
-To this aim, we take the neutrino flux to be known and focus on the irreducible systematics associated with event reconstruction."
 
@@
    \end{itemize}
+
+We thank the referee for this important point and add the following paragraph after we introduce the flux model in the middle of section 2.3.
+
+  "%
+As pointed out in Ref.~\cite{Kling:2021gos} there are notable neutrino flux uncertainties, as various event generators do not agree on the forward parent hadron spectra. 
+%
+The spread of the generators' predictions can be taken as a means of flux uncertainty, in which case there is a $\lesssim 50\%$ uncertainty on the interacting muon neutrino spectrum --- if left unresolved this would be a significant systematic.
+Indeed, there are already projections of FPF measurements which would reduce this uncertainty to the sub-percent level~\cite{Kling:2023tgr} as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}.
+%
+However, it is important to note that forward neutrino experiments actually constrain the product of flux and cross-section, and one must be assumed to measure the other.
+In a full analysis,  the flux and cross-section would be constrained simultaneously in a joint measurement, utilizing their different kinematic dependences on $ x,Q^2,E_{\nu}$ and neutrino rapidity $\eta_{\nu}$.
+%
+In our study, we aim to understand the full impact of FPF data on the PDF fit, thus motivating this future joint measurement.
+%
+To this aim, we take the neutrino flux to be known and focus on the irreducible systematics associated with event reconstruction. 
+%
+With this assumption, we will show that Run 3 measruements will not be sufficient to impact PDF fits.
+Instead, Run 3 measurements could be used to calibrate incoming neutrino fluxes, effectively reducing the large uncertainties by the time FPF data is collected in the future.
+The expected reduction of FPF neutrino flux uncertainties further justifies our choice to take the neutrino flux as known.
+%"
 

### 2023-11-21 journal_sub/sec-dis-pseudodata.tex
Extra Flux points from Juan

@@
 However, it is important to note that forward neutrino experiments actually constrain the product of flux and cross-section, and one must be assumed to measure the other.
-In a full analysis,  they would be constrained simultaneously in a joint measurement.
+In a full analysis,  the flux and cross-section would be constrained simultaneously in a joint measurement, utilizing their different kinematic dependences on $ x,Q^2,E_{\nu}$ and neutrino rapidity $\eta_{\nu}$.
 %
@@
 To this aim, we take the neutrino flux to be known and focus on the irreducible systematics associated with event reconstruction. 
+%
+With this assumption, we will show that Run 3 measruements will not be sufficient to impact PDF fits.
+Instead, Run 3 measurements could be used to calibrate incoming neutrino fluxes, effectively reducing the large uncertainties by the time FPF data is collected in the future.
+The expected reduction of FPF neutrino flux uncertainties further justifies our choice to take the neutrino flux as known.
+%
 

### 2023-11-23 referee/referee-reply.tex
Modifying statement about flux uncertainties in referee reply and journal sub

@@
 %
-The spread of the generators' predictions can be taken as a means of flux uncertainty, in which case there is a $\lesssim 50\%$ uncertainty on the interacting muon neutrino spectrum --- if left unresolved this would be a significant systematic.
-Indeed, there are already projections of FPF measurements which would reduce this uncertainty to the sub-percent level~\cite{Kling:2023tgr} as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}.
+If the spread of various generators' predictions was taken as a means of flux uncertainty, corresponding to a $\lesssim 50\%$ uncertainty on the interacting muon neutrino spectrum, this would be a significant systematic if left unresolved.
+However, it is noteworthy that many existing predictions are yet to be tuned for the purposes of experiments such as those planned for the FPF.
+Nevertheless, there are projections of FPF measurements which would reduce this uncertainty to the sub-percent level already in the context of the contemporary predictions, based on parametrizing their expected correlations~\cite{Kling:2023tgr}, as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}.
 %

### 2023-11-23 journal_sub/sec-dis-pseudodata.tex
minor typo
Modifying statement about flux uncertainties in referee reply and journal sub

@@
 %
-With this assumption, we will show that Run 3 measruements will not be sufficient to impact PDF fits.
+With this assumption, we will show that Run 3 measurements will not be sufficient to impact PDF fits.
 Instead, Run 3 measurements could be used to calibrate incoming neutrino fluxes, effectively reducing the large uncertainties by the time FPF data is collected in the future.

### 2023-11-27 referee/referee-reply.tex
added bib
references typo

@@
 
-  We have added the following references which explore strange and charm PDF asymmetries Sufian:2018cpj, Sufian:2020coz.
+  We have added the following references which explore strange and charm PDF asymmetries ~\cite{Sufian:2018cpj, Sufian:2020coz}.
   %
@@
 The charged track multiplicity is expected to grow with the hadronic system’s invariant mass.
-We make this clear and cite a neutrino-Hydrogen interaction multiplicity study (Aachen-Bonn-CERN-Munich-Oxford:1981lfk) as well as a FASER paper (FASER:2019dxq) which also point this out.
+We make this clear and cite a neutrino-Hydrogen interaction multiplicity study ~\cite{Aachen-Bonn-CERN-Munich-Oxford:1981lfk} as well as a FASER paper ~\cite{FASER:2019dxq} which also point this out.
 We also append this sentence:
@@
 \end{enumerate}
-
+\bibliographystyle{utphys}
+\bibliography{main.bib}
 \end{document}

### 2023-11-27 referee/referee-reply.tex
Add HL-LHC phenos and move FASERv results to Sec. 3

@@
         %
-        From this comparison, one can observe that .... ADD
+        From this comparison, one can observe a significant reduction in the PDF uncertainties, especially for
+        processes that involve single gauge boson productions. The decrease in PDF uncertainties, for most of
+        the processes and most of the kinematic regions, are greater than the decrease observed in FPF with only
+        statistical uncertianties.
 

### 2023-11-27 journal_sub/app-faser.tex
Add epjc typeset version
Add HL-LHC phenos and move FASERv results to Sec. 3

--- 2023-09-18 paper/app-faser.tex
@@
-\section{Impact of FASER$\nu$ Run III measurements}
-\label{app:fasernu_runIII_impact}
+\section{Phenomenology of HL-LHC}
+\label{app:comparisons_with_HLLHC}
 
-The same procedure applied to the FPF experiments in Sect.~\ref{sec:pdf4lhc21}
-can also be used in the case of FASER$\nu$, for which pseudo-data is generated
-for a Run III integrated
-luminosity of $\mathcal{L}=150$ fb$^{-1}$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!h]
+	\centering
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-integrated-HLLHC.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-integrated-HLLHC.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-integrated-HLLHC.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-integrated-HLLHC.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-integrated-HLLHC.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-integrated-HLLHC.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-integrated-HLLHC.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-integrated-HLLHC.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-integrated-HLLHC.pdf}
+	\caption{Same as}
+	\label{fig:HLLHC_pheno_integrated}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In the following section, we repeat the same phenomenology studies as in
+Sec.~\ref{sec:pheno} but using the High-Luminosity LHC (HL-LHC) PDF 
+from~\cite{AbdulKhalek:2018rok}.
 %
-As indicated by Table~\ref{tab:integrated_rates}, by the end of Run III, one expects
-that FASER$\nu$ will have recorded around 600 and 1800 electron- and muon-neutrinos
-respectively corresponding to deep-inelastic scattering events, of which around 100
-and 300 respectively are associated to charm-tagged events.
+Such comparisons present a complementary study to the impact seen both at the PDF 
+and prediction level shown in Sec.~\ref{sec:pheno}. The PDF constraints from the 
+FPF and HL-LHC experiments are fully orthogonal in that the former have the very 
+important property that possible contamination from new physics on the PDF fits 
+can be completely ignored, since this process is driven by $Q^2$ values outside 
+the possible presence of BSM physics.
 %
-These projected event rates can be compared with the expectations for FASER$\nu$2, which predict
-an increase in statistics of more than two orders of magnitude.
+Specially, should anomalies be revealed at the HL-LHC, having the fully independent
+validation of the large-$x$ PDFs provided by the FPF would be extremely valuable 
+for its interpretation.
 
-Fig.~\ref{fig:FASERnu2_vs_FASERnu} presents a similar comparison as that of
-Fig.~\ref{fig:FASERnu2_baseline} now between the projected PDF impact of FASER$\nu$2 and that of
-FASER$\nu$.
+In Fig.~\ref{fig:HLLHC_pheno_integrated} are displayed the fiducial cross-sections for 
+representative LHC processes, similar to the ones shown in Fig.~\ref{fig:NNPDF40_pheno_integrated},
+but evaluated with PDF4LHC15 and its variant that includes HL-LHC projections (``\_HLLHC'').
+The corresponding differential cross-sections are shown in Fig.~\ref{fig:HLLHC_pheno_differential}.
 %
-One finds that neutrino DIS measurements at FASER$\nu$ are unable to improve
-PDF uncertainties as compared to the baseline scenario encapsulated by PDF4LHC21.
+Concerning the fiducial cross-sections, a significant reduction in PDF uncertainties
+is seen, reaching up to a factor of four for processes involving single boson productions. 
+Such a significant decrease in the PDF uncertainties is also observed at the differential
+level.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[htbp]
+	\centering
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-global-HLLHC.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-global-HLLHC.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-global-HLLHC.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-global-HLLHC.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-global-HLLHC.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-global-HLLHC.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-global-HLLHC.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-global-HLLHC.pdf}
+	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-global-HLLHC.pdf}
+	\caption{Same as Fig.~\ref{fig:NNPDF40_pheno_integrated}
+		for the corresponding differential distributions in the case of NNPDF4.0
 		%
-The reason is two-fold: the smaller event rates as compared to FASER$\nu$2,
-and the reduced coverage of the $(x,Q^2)$ phase space shown in Fig.~\ref{fig:fasernu2_muon}.
-%
-The differences in PDF sensitivity between FASER$\nu$ and FASER$\nu$2 in
-Fig.~\ref{fig:FASERnu2_vs_FASERnu} illustrate
-the  importance of realising the FPF in order to exploit the full physics potential enabled 
-by LHC neutrinos for QCD and hadron structure studies.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_s_ratio.pdf}
-\caption{Same as  Fig.~\ref{fig:FASERnu2_baseline} (statistical uncertainties only), comparing
-  the projected PDF impact of FASER$\nu$2 with that of FASER$\nu$, in the latter
-  case assuming the Run III integrated
-luminosity of $\mathcal{L}=150$ fb$^{-1}$.
 	}
-\label{fig:FASERnu2_vs_FASERnu}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-It should be emphasized that the lack of PDF sensitivity displayed in Fig.~\ref{fig:FASERnu2_vs_FASERnu}
-does not imply that measuring DIS structure functions at FASER$\nu$ will not provide useful information.
-%
-First of all, our procedure assumes perfect compatibility between current data and the projected DIS
-neutrino measurements at the LHC, something which remains to be demonstrated experimentally.
-%
-Second, FASER$\nu$ still covers a region of neutrino energies unexplored by previous experiments, hence providing
-a new validation of our QCD calculations and of neutrino interactions at the TeV scale.
-%
-Third, it would represent a non-trivial proof-of-concept that LHC neutrino differential measurements can be
-unfolded to the cross-section level to be used in  theoretical
-interpretations, paving the way and demonstrating the feasibility of subsequent neutrino DIS
-measurements at the FPF experiments.
+	\label{fig:HLLHC_pheno_differential}
+\end{figure*}

### 2023-11-27 journal_sub/sec-results.tex
Add HL-LHC phenos and move FASERv results to Sec. 3

@@
 %
-For completeness, we study in App.~\ref{app:fasernu_runIII_impact} the constraints on PDFs 
+For completeness, we study the constraints on PDFs 
 provided by the forward experiments, namely FASER$\nu$. The results show that measurements
-at FASERV$\nu$ are unable to improve the determination of PDFs therefore strengthening the
+at FASER$\nu$ are unable to further improve the determination of PDFs therefore strengthening the
 need for the FPF experiments.
@@
 our current knowledge about the quark and gluon structure of the proton.
+
+\paragraph{Impact of FASER$\nu$ Run III measurements}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[htbp]
+	\centering
+	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_uv_ratio.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_dv_ratio.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_g_ratio.pdf}\\
+	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_Sea_ratio.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_s_ratio.pdf}
+	\caption{Same as  Fig.~\ref{fig:FASERnu2_baseline} (statistical uncertainties only), comparing
+		the projected PDF impact of FASER$\nu$2 with that of FASER$\nu$, in the latter
+		case assuming the Run III integrated
+		luminosity of $\mathcal{L}=150$ fb$^{-1}$.
+	}
+	\label{fig:FASERnu2_vs_FASERnu}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The same procedure applied to the FPF experiments in earlier
+can also be used in the case of FASER$\nu$, for which pseudo-data is generated
+for a Run III integrated
+luminosity of $\mathcal{L}=150$ fb$^{-1}$.
+%
+As indicated by Table~\ref{tab:integrated_rates}, by the end of Run III, one expects
+that FASER$\nu$ will have recorded around 600 and 1800 electron- and muon-neutrinos
+respectively corresponding to deep-inelastic scattering events, of which around 100
+and 300 respectively are associated to charm-tagged events.
+%
+These projected event rates can be compared with the expectations for FASER$\nu$2, which predict
+an increase in statistics of more than two orders of magnitude.
+
+Fig.~\ref{fig:FASERnu2_vs_FASERnu} presents a similar comparison as that of
+Fig.~\ref{fig:FASERnu2_baseline} now between the projected PDF impact of FASER$\nu$2 and that of
+FASER$\nu$.
+%
+One finds that neutrino DIS measurements at FASER$\nu$ are unable to improve
+PDF uncertainties as compared to the baseline scenario encapsulated by PDF4LHC21.
+%
+The reason is two-fold: the smaller event rates as compared to FASER$\nu$2,
+and the reduced coverage of the $(x,Q^2)$ phase space shown in Fig.~\ref{fig:fasernu2_muon}.
+%
+The differences in PDF sensitivity between FASER$\nu$ and FASER$\nu$2 in
+Fig.~\ref{fig:FASERnu2_vs_FASERnu} illustrate
+the  importance of realising the FPF in order to exploit the full physics potential enabled 
+by LHC neutrinos for QCD and hadron structure studies.
+
+It should be emphasized that the lack of PDF sensitivity displayed in Fig.~\ref{fig:FASERnu2_vs_FASERnu}
+does not imply that measuring DIS structure functions at FASER$\nu$ will not provide useful information.
+%
+First of all, our procedure assumes perfect compatibility between current data and the projected DIS
+neutrino measurements at the LHC, something which remains to be demonstrated experimentally.
+%
+Second, FASER$\nu$ still covers a region of neutrino energies unexplored by previous experiments, hence providing
+a new validation of our QCD calculations and of neutrino interactions at the TeV scale.
+%
+Third, it would represent a non-trivial proof-of-concept that LHC neutrino differential measurements can be
+unfolded to the cross-section level to be used in  theoretical
+interpretations, paving the way and demonstrating the feasibility of subsequent neutrino DIS
+measurements at the FPF experiments.
 

### 2023-12-05 journal_sub/app-hllhc.tex
working on paper revision

--- 2023-11-27 journal_sub/app-faser.tex
@@
-\section{Phenomenology of HL-LHC}
+\section{Comparison with HL-LHC PDF projections}
 \label{app:comparisons_with_HLLHC}
@@
 	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-integrated-HLLHC.pdf}
-	\caption{Same as}
+	\caption{The same LHC fiducial cross-sections as in Fig.~\ref{fig:NNPDF40_pheno_integrated},
+          now comparing the PDF4LHC15 baseline predictions with those based
+          on the PDFs including HL-LHC pseudo-data from~\cite{AbdulKhalek:2018rok}.
+          %
+          Specifically, we consider the HL-LHC PDF projections
+          from ``Scenario B'', corresponding to an intermediate scenario for the expected reduction
+          of systematic uncertainties. }
 	\label{fig:HLLHC_pheno_integrated}
@@
 
-In the following section, we repeat the same phenomenology studies as in
+Here we revisit the phenomenology studies as in
 Sec.~\ref{sec:pheno} but using the High-Luminosity LHC (HL-LHC) PDF 
@@
 
-In Fig.~\ref{fig:HLLHC_pheno_integrated} are displayed the fiducial cross-sections for 
-representative LHC processes, similar to the ones shown in Fig.~\ref{fig:NNPDF40_pheno_integrated},
-but evaluated with PDF4LHC15 and its variant that includes HL-LHC projections (``\_HLLHC'').
-The corresponding differential cross-sections are shown in Fig.~\ref{fig:HLLHC_pheno_differential}.
+In Fig.~\ref{fig:HLLHC_pheno_integrated} The same LHC fiducial cross-sections as in Fig.~\ref{fig:NNPDF40_pheno_integrated},
+now comparing the PDF4LHC15 baseline predictions with those based
+on the PDFs including HL-LHC pseudo-data from~\cite{AbdulKhalek:2018rok}.
+%
+Specifically, we consider the HL-LHC PDF projections
+from ``Scenario B'', corresponding to an intermediate scenario for the expected reduction
+of systematic uncertainties.
  %
@@
 level.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[htbp]
-	\centering
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-global-HLLHC.pdf}
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-global-HLLHC.pdf}
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-global-HLLHC.pdf}
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-global-HLLHC.pdf}
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-global-HLLHC.pdf}
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-global-HLLHC.pdf}
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-global-HLLHC.pdf}
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-global-HLLHC.pdf}
-	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-global-HLLHC.pdf}
-	\caption{Same as Fig.~\ref{fig:NNPDF40_pheno_integrated}
-		for the corresponding differential distributions in the case of NNPDF4.0
-		%
-	}
-	\label{fig:HLLHC_pheno_differential}
-\end{figure*}

### 2023-12-05 journal_sub/sec-results.tex
working on paper revision

@@
 by means of profiling.
+
+First of all, we study the constraints on the PDFs 
+provided by FASER$\nu$ during the LHC Run III data taking period,
+showing that they are not able to improve the determination of PDFs.
+%
+We then move to study the impact of the FPF experiments, focusing
+on FASER$\nu$2.
 %
@@
 results for their combination.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[htbp]
+	\centering
+	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_uv_ratio.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_dv_ratio.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_g_ratio.pdf}\\
+	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_Sea_ratio.pdf}
+	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_s_ratio.pdf}
+	\caption{
+The fractional PDF uncertainties (at the 68\% CL) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
+for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
+in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$
+and FASER$\nu$2 structure functions are included in the fit.
 %
-For completeness, we study the constraints on PDFs 
-provided by the forward experiments, namely FASER$\nu$. The results show that measurements
-at FASER$\nu$ are unable to further improve the determination of PDFs therefore strengthening the
-need for the FPF experiments.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[t]
-\centering
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_uv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_dv_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
-\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_s_ratio.pdf}
-\caption{
-The fractional PDF uncertainties (at the 68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
-for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
-in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 structure
-functions are included.
+In both cases we include charm-tagged structure functions
+and assume final-state lepton-charge separation.
 %
-The FASER$\nu$2 impact projections are presented both without and with systematic
-uncertainties accounted for, and include charm-tagged structure functions
-as well as final-state lepton-charge separation.
-%
+The FASER$\nu$ projections are based on a Run III integrated
+luminosity of $\mathcal{L}=150$ fb$^{-1}$.
 	}
-\label{fig:FASERnu2_baseline}
+	\label{fig:FASERnu2_vs_FASERnu}
 \end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\paragraph{Impact of the FASER$\nu$ Run III measurements.}
+%
+Fig.~\ref{fig:FASERnu2_vs_FASERnu} shows the
+fractional uncertainties (at the 68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
+for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
+in the PDF4LHC21 baseline, compared to the results obtained once the  FASER$\nu$
+and FASER$\nu$2 structure functions are
+added by means of Hessian profiling.
+%
+In both cases we include charm-tagged structure functions
+and assume final-state lepton-charge separation.
+%
+The FASER$\nu$ projections are based on a Run III integrated
+luminosity of $\mathcal{L}=150$ fb$^{-1}$.
+%
+As indicated by Table~\ref{tab:integrated_rates}, by the end of Run III, one expects
+that FASER$\nu$ will have recorded around 600 and 1800 electron- and muon-neutrinos
+respectively corresponding to deep-inelastic scattering events, of which around 100
+and 300 respectively are associated to charm-tagged events.
+%
+We display results for the profiling in which the experimental covariance matrix
+considers only statistical uncertainties.
+%
+We restrict the comparisons to the region $10^{-3}\lsim x \lsim 0.7$ covered
+by the LHC neutrino experiments (see also Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF}).
+
+From Fig.~\ref{fig:FASERnu2_vs_FASERnu}
+we find that neutrino DIS measurements at FASER$\nu$ are unable to improve
+PDF uncertainties as compared to the baseline scenario encapsulated by PDF4LHC21.
+%
+The reason is two-fold: the smaller event rates as compared to FASER$\nu$2,
+and the reduced coverage of the $(x,Q^2)$ phase space shown in Fig.~\ref{fig:fasernu2_muon}.
+%
+The differences in PDF sensitivity between FASER$\nu$ and FASER$\nu$2 in
+Fig.~\ref{fig:FASERnu2_vs_FASERnu} illustrate
+the  importance of realising the FPF in order to exploit the full physics potential enabled 
+by LHC neutrinos for QCD and hadron structure studies.
+
+It should be emphasized that the lack of PDF sensitivity displayed in Fig.~\ref{fig:FASERnu2_vs_FASERnu}
+does not imply that measuring DIS structure functions at FASER$\nu$ will not provide useful information.
+%
+First of all, our procedure assumes perfect compatibility between current data and the projected DIS
+neutrino measurements at the LHC, something which remains to be demonstrated experimentally.
+%
+Second, FASER$\nu$ still covers a region of neutrino energies unexplored by previous experiments, hence providing
+a new validation of our QCD calculations and of neutrino interactions at the TeV scale.
+%
+Third, it would represent a non-trivial proof-of-concept that LHC neutrino differential measurements can be
+unfolded to the cross-section level to be used in  theoretical
+interpretations, paving the way and demonstrating the feasibility of subsequent neutrino DIS
+measurements at the FPF experiments.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\caption{Same as in Fig.~\ref{fig:FASERnu2_vs_FASERnu} comparing
+  the FASER$\nu$2 impact projections without and with systematic
+uncertainties accounted for in the experimental covariance matrix.
+}
+\label{fig:FASERnu2_baseline}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \paragraph{Constraints from FASER$\nu$2.}
@@
 Fig.~\ref{fig:FASERnu2_baseline} shows the
-fractional uncertainties (at the 68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
-for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
-in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 structure functions are
-added by means of Hessian profiling.
+same comparison as in as in Fig.~\ref{fig:FASERnu2_vs_FASERnu}, now for the
+  the FASER$\nu$2 impact projections without and with systematic
+  uncertainties accounted for in the experimental covariance matrix,
+  following
+the procedure spelled out in Sect.~\ref{subsec:uncertainties}.
 %
@@
 considers only statistical uncertainties, as well as for the scenario where
-statistical and systematic errors are added in quadrature following
-the procedure spelled out in Sect.~\ref{subsec:uncertainties}.
-%
-We restrict the comparisons to the region $10^{-3}\lsim x \lsim 0.7$ covered
-by the LHC neutrino experiments (see also Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF}).
+statistical and systematic errors are added in quadrature.
 %
@@
 
-Inspection of Fig.~\ref{fig:FASERnu2_baseline} reveals that measurements of DIS structure
+Inspection of Fig.~\ref{fig:FASERnu2_baseline} reveals that, as opposed
+to the FASER$\nu$ impact projections, measurements of DIS structure
 functions at FASER$\nu$2 would reduce PDF uncertainties on the quark and antiquark
@@
 %
-Together with those for FASER$\nu$2, we have also produced PDF impact projections for
+Together with the impact projections for FASER$\nu$2, we have also produced analogous results for
 other proposed FPF experiments, specifically for AdvSND and FLArE.
 %
-In the latter case, we consider the 10 tonne variant FLArE10.
+In the latter case, we consider the 10 tonne variant, FLArE10.
 %
@@
 
-Applying the same procedure to FASER$\nu$ and SND@LHC structure
-functions leaves the baseline  results from PDF4LHC21 essentially
-unaffected, as demonstrated in App.~\ref{app:fasernu_runIII_impact},
-and showing that for the current generation of LHC neutrino detectors
-it will be difficult to provide competitive constraints on the proton structure due
-to the (relatively) low DIS event rates.
-
 \paragraph{Combined impact of the FPF experiments.}
@@
 our current knowledge about the quark and gluon structure of the proton.
-
-\paragraph{Impact of FASER$\nu$ Run III measurements}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[htbp]
-	\centering
-	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_uv_ratio.pdf}
-	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_dv_ratio.pdf}
-	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_g_ratio.pdf}\\
-	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_Sea_ratio.pdf}
-	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_s_ratio.pdf}
-	\caption{Same as  Fig.~\ref{fig:FASERnu2_baseline} (statistical uncertainties only), comparing
-		the projected PDF impact of FASER$\nu$2 with that of FASER$\nu$, in the latter
-		case assuming the Run III integrated
-		luminosity of $\mathcal{L}=150$ fb$^{-1}$.
-	}
-	\label{fig:FASERnu2_vs_FASERnu}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The same procedure applied to the FPF experiments in earlier
-can also be used in the case of FASER$\nu$, for which pseudo-data is generated
-for a Run III integrated
-luminosity of $\mathcal{L}=150$ fb$^{-1}$.
-%
-As indicated by Table~\ref{tab:integrated_rates}, by the end of Run III, one expects
-that FASER$\nu$ will have recorded around 600 and 1800 electron- and muon-neutrinos
-respectively corresponding to deep-inelastic scattering events, of which around 100
-and 300 respectively are associated to charm-tagged events.
-%
-These projected event rates can be compared with the expectations for FASER$\nu$2, which predict
-an increase in statistics of more than two orders of magnitude.
-
-Fig.~\ref{fig:FASERnu2_vs_FASERnu} presents a similar comparison as that of
-Fig.~\ref{fig:FASERnu2_baseline} now between the projected PDF impact of FASER$\nu$2 and that of
-FASER$\nu$.
-%
-One finds that neutrino DIS measurements at FASER$\nu$ are unable to improve
-PDF uncertainties as compared to the baseline scenario encapsulated by PDF4LHC21.
-%
-The reason is two-fold: the smaller event rates as compared to FASER$\nu$2,
-and the reduced coverage of the $(x,Q^2)$ phase space shown in Fig.~\ref{fig:fasernu2_muon}.
-%
-The differences in PDF sensitivity between FASER$\nu$ and FASER$\nu$2 in
-Fig.~\ref{fig:FASERnu2_vs_FASERnu} illustrate
-the  importance of realising the FPF in order to exploit the full physics potential enabled 
-by LHC neutrinos for QCD and hadron structure studies.
-
-It should be emphasized that the lack of PDF sensitivity displayed in Fig.~\ref{fig:FASERnu2_vs_FASERnu}
-does not imply that measuring DIS structure functions at FASER$\nu$ will not provide useful information.
-%
-First of all, our procedure assumes perfect compatibility between current data and the projected DIS
-neutrino measurements at the LHC, something which remains to be demonstrated experimentally.
-%
-Second, FASER$\nu$ still covers a region of neutrino energies unexplored by previous experiments, hence providing
-a new validation of our QCD calculations and of neutrino interactions at the TeV scale.
-%
-Third, it would represent a non-trivial proof-of-concept that LHC neutrino differential measurements can be
-unfolded to the cross-section level to be used in  theoretical
-interpretations, paving the way and demonstrating the feasibility of subsequent neutrino DIS
-measurements at the FPF experiments.
 

### 2023-12-05 referee/referee-reply.tex
done revision

--- 2023-11-27 referee/referee-reply.tex
@@
         now for the PDF4LHC15 with PDF4LHC15+HLHC PDFs.
+
+        This comparison highlights the complementarity between the two experiments
+in terms of PDF constraints, being fully orthogonal and arising from different
+scattering process.
 %
-        From this comparison, one can observe that .... ADD
-
-        Furthermore, as mentioned in the paper, the PDF constraints from the FPF and from the HL-LHC are
-        fully orthogonal and complementary, and the former have the very important property that
-        possible contamination from new physics on the PDF fits can be completely ignored, since
-        this process is driven by $Q^2$ values outside the possible presence of BSM physics.
+Furthermore, the FPF constraints benefit from the valuable property
+that an eventual contamination from new physics on the PDF fits 
+can be neglected, since this process is driven by $Q^2$ values outside 
+the possible presence of BSM physics, at least concerning new heavy states.
 %
-        Specially should a large-mass anomaly be revealed at the HL-LHC, having the fully independent
-        validation of the large-$x$ PDFs provided by the FPF would be extremely valuable for its
-        interpretation.
+Therefore, the ultimate sensitivity on high-precision observables being
+obtained by integrating the constraints both from the HL-LHC and from the FPF
+in the same global determination of PDFs.
 
@@
   \begin{itemize}
-  \item As shown in appendix A, now moved to Sect 3, FASER$\nu$ and SND@LHC data from run III do not have sensitivity on the modelling of the neutrino-nucleus interaction cross-section.
+  \item As shown in appendix A in the original version of the paper (now moved to Sect 3), FASER$\nu$ and SND@LHC data from run III do not have sensitivity on the modelling of the neutrino-nucleus interaction cross-section.
     %

### 2023-12-05 journal_sub/app-hllhc.tex
done revision

@@
 
-Here we revisit the phenomenology studies as in
-Sec.~\ref{sec:pheno} but using the High-Luminosity LHC (HL-LHC) PDF 
-from~\cite{AbdulKhalek:2018rok}.
+Here we revisit the phenomenology studies of
+Sect.~\ref{sec:pheno} using the HL-LHC PDF impact projections
+presented in~\cite{AbdulKhalek:2018rok}.
 %
-Such comparisons present a complementary study to the impact seen both at the PDF 
-and prediction level shown in Sec.~\ref{sec:pheno}. The PDF constraints from the 
-FPF and HL-LHC experiments are fully orthogonal in that the former have the very 
-important property that possible contamination from new physics on the PDF fits 
-can be completely ignored, since this process is driven by $Q^2$ values outside 
-the possible presence of BSM physics.
+These projections were obtained with the same Hessian profiling strategy
+as discussed in Sect.~\ref{sec:dis_pseudodata}, with the important
+difference that the prior PDF set was PDf4LHC15 rather than
+PDF4LHC21.
 %
-Specially, should anomalies be revealed at the HL-LHC, having the fully independent
+Therefore, while a direct comparison with the results presented in
+Sect.~\ref{sec:pheno} is not possible due to the use of a different prior,
+we can assess the relative reduction of PDF uncertainties in both cases,
+and hence compare the reach on the PDFs of the FPF neutrino structure functions
+and that of the HL-LHC measurements considered in the analysis of~\cite{AbdulKhalek:2018rok}.
+
+This comparison of the relative PDF sensitivity of the FPF and
+the HL-LHC data is interesting given that the  constraints from the 
+two experiments are fully orthogonal and arise from completely different
+scattering process.
+%
+Furthermore, the FPF constraints benefit from the valuable property
+that an eventual contamination from new physics on the PDF fits 
+can be neglected, since this process is driven by $Q^2$ values outside 
+the possible presence of BSM physics (at least concerning new heavy particles).
+%
+Specially, should anomalies be revealed at the HL-LHC, having the independent
 validation of the large-$x$ PDFs provided by the FPF would be extremely valuable 
@@
 
-In Fig.~\ref{fig:HLLHC_pheno_integrated} The same LHC fiducial cross-sections as in Fig.~\ref{fig:NNPDF40_pheno_integrated},
+Fig.~\ref{fig:HLLHC_pheno_integrated} displays the
+same LHC fiducial cross-sections as in Fig.~\ref{fig:NNPDF40_pheno_integrated},
 now comparing the PDF4LHC15 baseline predictions with those based
@@
 %
-Concerning the fiducial cross-sections, a significant reduction in PDF uncertainties
-is seen, reaching up to a factor of four for processes involving single boson productions. 
-Such a significant decrease in the PDF uncertainties is also observed at the differential
-level.
+In general, the relative reduction on PDF uncertainties provided by the HL-LHC experiments
+is more marked as in the case of the FPF pseudo-data, with the important caveat that
+PDF4LHC21 already includes much more LHC data in comparison with its predecessor,
+PDF4LHC15.
+%
+Another possible limiting assumption used in~\cite{AbdulKhalek:2018rok} is that
+correlated uncertainties can be reliable estimated at the few-permille level
+relevant for the intepretation of the HL-LHC data, something that is proving quite challenging
+even for Run I and II measurements.
+
+Nevertheless, the message obtained by comparing Fig.~\ref{fig:HLLHC_pheno_integrated} 
+ with Fig.~\ref{fig:NNPDF40_pheno_integrated} is that of complementarity,
+with the ultimate sensitivity on high-precision observables being
+obtained by integrating the constraints both from the HL-LHC and from the FPF
+in the same global determination of PDFs.

### 2023-12-05 journal_sub/sec-introduction.tex
done revision

--- 2023-09-18 paper/sec-introduction.tex
@@
 Additional results are collected in two appendices:
-App.~\ref{app:fasernu_runIII_impact} studies the constraints provided by
-FASER$\nu$ measurements at Run III, and App.~\ref{app:nPDF_impact_appendix}
+App.~\ref{app:comparisons_with_HLLHC} revisits
+the phenomenological studies of
+Sect.~\ref{sec:pheno} using the HL-LHC PDF impact projections
+presented in~\cite{AbdulKhalek:2018rok}, while App.~\ref{app:nPDF_impact_appendix}
 quantifies the stability of the nPDF impact projections with respect

### 2023-12-05 journal_sub/sec-pheno.tex
done revision

@@
 in the FPF measurements in order to enhance the cross-talk with HL-LHC analyses.
+
+For completeness, App.~\ref{app:comparisons_with_HLLHC} revisits
+the phenomenological studies  presented in this section for the fiducial cross-sections
+in terms of the  HL-LHC PDF impact projections of~\cite{AbdulKhalek:2018rok}.
+%
+This comparison highlights the complementarity between the two experiments
+in terms of PDF constraints, being fully orthogonal and arising from different
+scattering process.
+%
+Furthermore, the FPF constraints benefit from the valuable property
+that an eventual contamination from new physics on the PDF fits 
+can be neglected, since this process is driven by $Q^2$ values outside 
+the possible presence of BSM physics, at least concerning new heavy states.
+%
+Therefore, the ultimate sensitivity on high-precision observables being
+obtained by integrating the constraints both from the HL-LHC and from the FPF
+in the same global determination of PDFs.

### 2024-01-26 paper/sec-results.tex
Paragraph discussing the effect of flux normalization uncertainties

@@
 our current knowledge about the quark and gluon structure of the proton.
+
+\paragraph{The effect of neutrino flux uncertainties.}
+%
+The estimation of the effect of neutrino flux uncertainties in the determination of PDFs is done by extending the procedure of Ref.~\cite{Kling:2023tgr}, using the predictions provided by Ref.s~\cite{Ahn:2009wx, Ahn:2011wt, Riehn:2015oba, Fedynitch:2018cbl, Pierog:2013ria, Buonocore:2023kna, Roesler:2000he, Fedynitch:2015kcn, Bai:2020ukz, Bai:2021ira, Bai:2022xad, Ostapchenko:2010vb, Bhattacharya:2023zei, Fieg:2023kld, Maciula:2022lzk}, by introducing an additional fit parameter to account for the normalisation of the neutrino flux.
+The constraint for the normalisation parameter is found considering two scenarios: by using all the expected run III data from FASER$\nu$, and 50\% of the data expected at FASER$\nu$2 during the high-luminosity LHC run.
+In the latter case, only the remaining 50\% of FASER$\nu$2 data is then considered available for PDF determination.
+The flux normalisation parameter can be constrained approximately to 6\% using FASER$\nu$ run III data, and to 0.4\% using 50\% of FASER$\nu$2 data, as illustrated in Fig.~\ref{fig:flux_constraints}.
+The constraints are passed to the profiling studies as additional fully correlated uncertainties, also accounting for an increase in statistical uncertainty in the case where only 50\% of data is used.
+The PDFs resulting from using the run III constraint are shown in Fig.~\ref{fig:FASERv2_flux_unc_run3}, and those obtained with the high-lumi LHC constraints in Fig.~\ref{fig:FASERv2_flux_unc_HL-LHC}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.42\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/normalization_constraint_run3.pdf}
+\includegraphics[width=0.42\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/normalization_constraint_HL-LHC.pdf}
+\caption{
+  An illustration of the difference of the obtained flux normalisation constraints to the baseline uncertainty of the amount of muon neutrino interactions, using FASER$\nu$ data (left) and 50\% of the expected FASER$\nu$2 data (right).
+The baseline uncertainty is obtained following Ref.~\cite{Kling:2023tgr}.
+}
+\label{fig:flux_constraints}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\caption{
+  Same as Fig.~\ref{fig:FASERnu2_baseline} now quantifying the
+  effect of neutrino flux uncertainties in the analysis of FASER$\nu$2 pseudodata, assuming that the neutrino flux normalisation is constrained using FASER$\nu$ run III data. 
+}
+\label{fig:FASERv2_flux_unc_run3}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\caption{
+  Same as Fig.~\ref{fig:FASERnu2_baseline} now quantifying the
+  effect of neutrino flux uncertainties in the analysis of FASER$\nu$2 pseudodata, assuming that the neutrino flux normalisation is constrained using 50\% of FASER$\nu$2 data to constrain the flux and the remainder for PDF determination.
+}
+\label{fig:FASERv2_flux_unc_HL-LHC}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2024-01-26 journal_sub/sec-results.tex
Paragraph on estimating effects of flux uncertainties

@@
 
+\paragraph{The effect of neutrino flux uncertainties.}
+%
+The estimation of the effect of neutrino flux uncertainties in the determination of PDFs is done by extending the procedure of Ref.~\cite{Kling:2023tgr}, 
+using the predictions provided by Ref.s~\cite{Ahn:2009wx, Ahn:2011wt, Riehn:2015oba, Fedynitch:2018cbl, Pierog:2013ria, Buonocore:2023kna, Roesler:2000he, Fedynitch:2015kcn, Bai:2020ukz, Bai:2021ira, Bai:2022xad, Ostapchenko:2010vb, Bhattacharya:2023zei, Fieg:2023kld, Maciula:2022lzk},
+by introducing an additional fit parameter to account for the normalisation of the neutrino flux. 
+The constraint for the normalisation parameter is found considering two scenarios: by using all the expected run III data from FASER$\nu$, and 50\% of the data expected at FASER$\nu$2 during the high-luminosity LHC run.
+In the latter case, only the remaining 50\% of FASER$\nu$2 data is then considered available for PDF determination. 
+The flux normalisation parameter can be constrained approximately to 6\% using FASER$\nu$ run III data, and to 0.4\% using 50\% of FASER$\nu$2 data, as illustrated in Fig.~\ref{fig:flux_constraints}. 
+The constraints are passed to the profiling studies as additional fully correlated uncertainties, also accounting for an increase in statistical uncertainty in the case where only 50\% of data is used.
+The PDFs resulting from using the run III constraint are shown in Fig.~\ref{fig:FASERv2_flux_unc_run3}, and those obtained with the high-lumi LHC constraints in Fig.~\ref{fig:FASERv2_flux_unc_HL-LHC}.
+In either case, the results indicate only a minor increase in the resulting PDF uncertainties.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.4\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/normalization_constraint_run3.pdf}
+\hspace{1cm}
+\includegraphics[width=0.4\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/normalization_constraint_HL-LHC.pdf}
+\caption{
+  An illustration of the difference of the obtained flux normalisation constraints to the baseline uncertainty of the amount of muon neutrino interactions, using FASER$\nu$ data (left) and 50\% of the expected FASER$\nu$2 data (right).
+The baseline uncertainty is obtained following Ref.~\cite{Kling:2023tgr}.
+}
+\label{fig:flux_constraints}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\caption{
+  Same as Fig.~\ref{fig:FASERnu2_baseline} now quantifying the
+  effect of neutrino flux uncertainties in the analysis of FASER$\nu$2 pseudodata, assuming that the neutrino flux normalisation is constrained using FASER$\nu$ run III data. 
+}
+\label{fig:FASERv2_flux_unc_run3}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\caption{
+  Same as Fig.~\ref{fig:FASERnu2_baseline} now quantifying the
+  effect of neutrino flux uncertainties in the analysis of FASER$\nu$2 pseudodata, assuming that the neutrino flux normalisation is constrained using 50\% of FASER$\nu$2 data to constrain the flux and the remainder for PDF determination.
+}
+\label{fig:FASERv2_flux_unc_HL-LHC}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Proton PDFs: impact on NNPDF4.0}

### 2024-01-29 journal_sub/sec-results.tex
revised flux uncertainty discussion

--- 2023-12-05 journal_sub/sec-results.tex
@@
 
+\paragraph{The effect of neutrino flux uncertainties.}
+%
+The results presented so far assume the incoming far-forward neutrino flux as input, with vanishing uncertainties.
+%
+One can estimate the impact that uncertainties associated to this neutrino flux input have
+on the PDF constraints by extending the procedure of~\cite{Kling:2023tgr}, 
+based on the predictions provided in~\cite{Ahn:2009wx, Ahn:2011wt, Riehn:2015oba, Fedynitch:2018cbl, Pierog:2013ria, Buonocore:2023kna, Roesler:2000he, Fedynitch:2015kcn, Bai:2020ukz, Bai:2021ira, Bai:2022xad, Ostapchenko:2010vb, Bhattacharya:2023zei, Fieg:2023kld, Maciula:2022lzk},
+by introducing an additional fit parameter to account for the overall normalisation of the neutrino flux (while assuming the shape is unchanged with respect to the baseline predictions).
+%
+The constraint for this flux normalisation parameter is obtained considering two scenarios: first, by using the expected Run 3 data from FASER$\nu$, and second, by using 50\% of the data expected at FASER$\nu$2 during the HL-LHC run.
+%
+In the latter case, only the remaining 50\% of FASER$\nu$2 data is then considered available for PDF determination, to avoid double counting.
+
+The resulting flux normalisation parameter can be constrained approximately to a precision of
+6\% using FASER$\nu$
+Run 3 data, and to
+0.4\% using 50\% of FASER$\nu$2 data, as illustrated in Fig.~\ref{fig:flux_constraints}.
+%
+These constraints are then incorporated into
+the profiling studies as additional fully correlated (across bins) uncertainties, also accounting for an increase in statistical uncertainty in the case where only 50\% of data is used.
+%
+The impact on the FASER$\nu$2 projections of the neutrino flux uncertainties, in the case of the 
+PDFs resulting from using the Run 3 constraint are shown in Fig.~\ref{fig:FASERv2_flux_unc_run3}, and those obtained with the HL-LHC constraints in Fig.~\ref{fig:FASERv2_flux_unc_HL-LHC}.
+%
+In either case, the results indicate only a very small increase in the resulting PDF uncertainties.
+%
+One may conclude that neutrino flux uncertainties do not significantly degrade the PDF constraining potential of the FPF experiments presented in this work.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.4\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/normalization_constraint_run3.pdf}
+\hspace{1cm}
+\includegraphics[width=0.4\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/normalization_constraint_HL-LHC.pdf}
+\caption{The baseline uncertainty associated to the theoretical modelling of the far-forward muon neutrino fluxes~\cite{Kling:2023tgr} at FASER$\nu$ (left) and FASER$\nu$2 (right panel), compared to the results of constraining the overall normalisation of this flux from  FASER$\nu$ data and from 50\% of the expected FASER$\nu$2 data, respectively.
+}
+\label{fig:flux_constraints}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_run3/fred05fcorr05_fluxR3_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\caption{
+  Same as Fig.~\ref{fig:FASERnu2_baseline}, now quantifying the
+  impact on the FASER$\nu$2 results of accounting for the muon neutrino flux uncertainties, assuming its
+  overall normalisation has been constrained with FASER$\nu$ Run 3 data.
+  %
+  See text for more details.
+}
+\label{fig:FASERv2_flux_unc_run3}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_uv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_dv_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
+\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_flux_HL-LHC/fred05fcorr05_fluxR4_FASERv2_q2_10000_pdf_s_ratio.pdf}
+\caption{
+  Same as Fig.~\ref{fig:FASERnu2_baseline} now quantifying the
+  effect of neutrino flux uncertainties in the analysis of FASER$\nu$2 pseudodata, assuming that the neutrino flux normalisation is constrained using 50\% of FASER$\nu$2 data to constrain the flux and the remainder for PDF determination.
+}
+\label{fig:FASERv2_flux_unc_HL-LHC}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Proton PDFs: impact on NNPDF4.0}

### 2024-01-29 referee/referee-reply-rev2.tex
added referee reply

--- 2023-11-27 referee/referee-reply.tex
@@
 
-\noindent
-We would like to express our gratitude to the referee for the appreciation
-of our work and for providing constructive
-comments on our manuscript. The valuable feedback has been used to
-improve the quality and clarity of our work.
+We thank the referee for their additional observations.
 %
-In response to the suggestions, we address below each of the points raised by 
-the referee and describe the actions that have been taken
-in the revised version of the manuscript.
+The referee suggests that we should provide a more quantitative answer to the objections concerning
+the possible degradation of our results once one accounts for the uncertainties associated to the incoming neutrino fluxes:\\
+
+{\it So, the authors essentially appear to be arguing that as the flux uncertainties will be smaller in the future than the current (very large) ones then they are justified in ignoring them entirely.
+But this has not been quantitively justified anywhere.
+In the text and their response to referee B the authors in particular mention two points, namely the possibility for Run 3 data to reduce the flux uncertainty, and the potential for a combined analysis, given the different kinematic dependencies of the flux and DIS cross sections.
+
+  These are both perfectly reasonable points to make, but as thing stand, and in particular without further quantitative analysis, there is no way to tell to what extent these will really allow the flux uncertainty to be disentangled from the PDF impact.
+And without that one simply cannot say whether the projections presented here are reasonable or not.
+The authors point to 2309.1047, but of course this omits the PDF uncertainty on the DIS cross section, so the issue remains.
+Any PDF impact study of this sort therefore has to account for all known sources of uncertainty, including the flux, and determine to what extent these points will be true.
+To do otherwise, and describe this as the ‘full’ impact of FPF data on the PDF fit, as the authors do, seems to me to be very problematic.
+Moreover, as I pointed out in my earlier report, at the moment they still talk in the abstract, introduction and elsewhere as if the projected PDF impact is fully assessed here, i.e.
+as if the flux uncertainty were actually zero.
+
+  So, all I can (again) say is that the machinery is there to account for this issue in the analysis, by simply accounting for a reasonable flux uncertainty (as per e.g.
+2309.1047) and seeing to what extent this impacts on the PDF projections.
+The authors could consider a range of possible uncertainty sizes (e.g.
+to demonstrate that so long as the flux uncertainty is constrained to a given degree the PDF impact will not be washed out), and presumably would in any case be able to demonstrate this point about kinematic separation between the flux and DIS cross sections, which should come out in the analysis.
+I regret to say that unless the issue of the flux uncertainty is quantitatively accounted for in this way in the analysis for at least one projection study then I cannot recommend the paper for publication, as was made clear in my original report.}\\
+
+To address this point, we have extended our analysis with a dedicated quantitative discussion on the impact of neutrino flux uncertainties in our PDF projection results.
 %
-To facilitate the review process, in the revised version of the manuscript
-we have highlighted all the changes that have been made with respect to the original
-submission.
+The procedure we have adopted is described in the paragraph ``The effect of neutrino flux uncertainties'' towards the end of Sect 3.1, and the main results are presented in the new figures 3.7, 3.8, and 3.9.
 
-\noindent
+First, we demonstrate that Run 3 data from FASERnu can constrain the overall normalisation of the muon neutrino flux by 6\%, while 50\% of the HL-LHC data would constrain it down to the permille level.
+%
+We then repeat the PDF profiling analysis by adding an extra fully correlated (across bins) systematic uncertainty in the fitted DIS cross-sections, associated to this overall normalisation of the incoming muon neutrino flux.
+%
+As shown by Fig. 3.8, already once the muon neutrino fluxes have been constrained by FASER$\nu$ Run 3 data, the remaining residual uncertainties would have a very small effect in the PDF profiling.
+%
+The key observation, as mentioned in our first rebuttal, is the fact that constraints on the overall normalisation of the fluxes and on the PDFs have more or less an orthogonal kinematic sensitivity.
+%
+One may conclude that neutrino flux uncertainties do not significantly degrade the PDF constraining potential of the FPF experiments presented in this work.
 
-\begin{enumerate}
-	\item {\it Page 3, below (2.8). It is noted that nuclear corrections are not included when 
-		interpreting the neutrino structure function data in terms of proton PDFs. It would be good
-		to provide some brief discussion of the size of these and the associated uncertainties.
-	}
+We point out that the overall normalisation is the main source of theory uncertainty in the modelling of far-forward neutrino flux at the LHC, and hence our choice to focus on it.
+%
+This analysis could be further refined by adding more nuisance parameters accounting for instance for a $E_\nu$ and $y_\nu$ variation of the fluxes as compared to the baseline, or different normalizations for each of the flux components, but it is unlikely that the conclusions that we find would be qualitatively modified.
+%
 
-	In order to address the need for a comment regarding the sizes of the nuclear corrections
-	in proton PDF fits, we have swapped the order of the last two sentences in that paragraph.
-	The cited references, and the references therein, provide extensive discussions regarding
-	the procedure to include nuclear corrections and their effects.
+We hope that, having addressed the objection of the referee with a dedicated quantitative discussion as requested, our paper will now be considered suitable for publication.
 
-	\item {\it Table 2.2. It is not clear to me at the point where these numbers are produced exactly
-		how the cross section inputs corresponding to these numbers are calculated. So I
-		think a reference forward to Section 2.5, where the theory settings are described, is
-		needed. Although even then, for completeness giving the PDF set that is used and
-		some uncertain
-		ty on the event rates here would be useful.
-	}
-
-	The numbers in Table 2.2 are computed by integrating the event yields shown in Eq.~2.12 in
-	which the differential cross sections are computed using the central value of the PDF4LHC21
-	set. For completeness, we have added a sentence above Eq. (2.16) that mention the specific
-	PDF set used to compute these numbers, and where we also indicate that the calculation
-        is performed at NLO in the QCD expansion.
-        %
-        Although
-	Section 2.5 indeed provides some descriptions regarding the computation of the differential cross sections
-	(which were also described in Section 2.1), it mainly focuses on the construction of the pseudodata
-	needed for the fit/profiling.
-
-        This said, we would like to emphasize that the predicted event rates in Table 2.2 depend
-        only mildly on the specific settings of the DIS cross-section entering the calculation.
-        %
-        Furthermore, these event rates are only used to determine the expected bib-by-bin
-        statistical uncertainty.
-        %
-        Hence our results are relatively independent on the theoretical settings
-        entering the calculation of the event yields in Table 2.2.
-
-	\item {\it Page 11. The discussion about consistency between the PDF set and theory settings
-		used to produce the pseudodata and those entering the fit/profiling is in my view not
-		correct or at least too strong. In particular, while it is perfectly reasonable to keep
-		these the same there is definitely no requirement to, as is currently strongly implied in
-		the discussion. In real PDF fits we often see that the fit quality for a given dataset does
-		not follow textbook expectations, with $\chi^2/N \sim 1$. So some inconsistency between data
-		and theory is often observed, rather than being artificial. Indeed, it is precisely because
-		of this effect that tolerances (which are included in e.g. the PDF4LHC profiling) are
-		included. In other words, one could perfectly reasonably generate pseudodata with a
-		different PDF set, or different theory settings in order to emulate this inconsistency.
-		One is free not to, but it should not be suggested that complete consistency is the only
-		option here. It is a choice that is made, and not the only possible one.
-	}
-
-          We agree with the referee that, when generating pseudo-data, one may or may not want to
-          assume the same underlying truth as in the prior of the corresponding PDF fit.
-          %
-          Indeed, data inconsistencies are present in real data.
-
-          Our motivation to keep these settings consistent is that in this work we aim to investigate
-          what is the PDF constraining power of the FPF measurements
-          assuming that there are no inconsistencies,
-          which is the best-case scenario.
-          %
-          In the presence of inconsistencies, one finds two competing effects: a shift in the central value
-          of the PDF and a reduction of the PDF error whose magnitude depends on the assumed
-          inconsistencies.
-          %
-          For example, if we generate the FPF pseudo-data far from the PDF4LHC21 prior,
-          the main impact of the data will be to shift the central prediction, rather than
-          to reduce the uncertainty.
-
-          Another reason to assume this consistency  is that when carrying out Hessian profiling,
-          one keeps the PDF parametrisation fixed. In the presence of inconsistencies, it may be
-          that the best fit with FPF data requires a different parametrisation and hence
-          a different PDF error analysis.
-          %
-          So Hessian profiling is most reliable in the absence of data inconsistencies.
-
-          In the revised version of the paper, we have emphasized our two-fold region
-          to assume full consistency between the prior PDF and the FPF pseudo-data: to
-          quantify the PDF reach of the FPF pseudo-data in the most advantageous scenario,
-          and to ensure the procedural validity of the Hessian profiling procedure.
-
-          This said, the suggestion from the referee to generate data with an ``inconsistent'' PDF
-          set is valuable and it would be interesting to carry out this exercise in the future.
-          %
-          To emphasize this, we have added a sentence stating that generating pseudo-data with a different
-          PDF set from the prior would test the capabilities of the FPF to disentangle between
-          different PDF sets among them.
-
-	\item {\it Page 15, and Fig. 3.3. Perhaps some explanation of why dV and to a lesser extend uV
-		benefits from charge-lepton identification could be provided?
-	}
-
-	We have slightly rephrased the subsequent sentences to make it clear that the improvements
-	seen in $d_V$ and to a lesser extend in $u_V$ can be understood by looking at analytical 
-	LO expressions of the structure functions in terms of the PDFs for $\nu$ and $\bar{\nu}$
-        provided in Sect.~2.
-
-	\item {\it Page 16, and Appendix A. The fact that the FASER$\nu$ (and SND@LHC) projections lead
-		to a very limited improvement on the PDF uncertainties is rather hidden in a paragraph
-		here, and then in the appendix. In my view, this ‘negative’ result should be given more
-		prominence. It after all motivates the improvements that might come with the FPF. I
-		would suggest moving this to the main body of the text and starting with this as the
-		first study.
-	}
-
-	The main reason to put the study of the constraints provided by FASER$\nu$ in the Appendix was because
-	the analysis in Section 3 is mainly dedicated to the FPF experiments. We nevertheless agree with the
-	referee that such findings should be highlighted and used as a motivation for the FPF.
-        %
-        We have moved App. A to the first subsection of Sect 3, to highlight that the ultimate
-        constraining power of LHC neutrino experiments can only be realised with the FPF.
-
-        Actually, this result is also relevant concerning another points raised by the referee below:
-        the fact that the FASER$\nu$ and SND@LHC data not not impact the PDFs indicates that the
-        interpretation of their event rate measurements depends only loosely on the modelling
-        of the deep-inelastic scattering interaction.
-        %
-        Hence, the FASER$\nu$ and SND@LHC data can be safely used to tune the incoming neutrino fluxes
-        and learn for example about PDFs at very small-$x$, without compromising
-        the validity of the interpretation.
-        %
-        So this ``null result'' is also relevant in this context, and motivates the use of the current
-        FASER$\nu$ and SND@LHC data to validate models of charm production, forward light hadron
-        production, and small-$x$ QCD.
-
-	\item {\it Page 22. I am rather unsure about the approach for presenting results here, and in
-		particular in showing numbers without including systematic errors, which are described
-		as being ‘optimistic’. Having zero systematic uncertainties is surely unrealistic, rather
-		than optimistic, so I feel as though a clearer justification for this needs to be given.
-		Even more importantly, the labelling of the result without systematic uncertainties as
-		‘FPF’ and those with as ‘FPF*’ is surely the wrong way round, given it implies that
-		the case where the systematic uncertainties are not included is the default in some
-		sense. So these should be swapped, and the rationale behind showing numbers without
-		systematic uncertainties accounted for more clearly presented.
-	}
-
-	  The referee is surely correct in that zero-systematic uncertainties is not realistic.
-          %
-          However,
-	the reason to also show results with statistical uncertainties only is twofold. First, it
-	substantiates the claim that FPF measurements will be dominated by systematics, rather
-        than statistical uncertainties, which is a very important and non-trivial consideration
-        informing detector design. The FPF detectors have not been designed with ``precision physics'' as main
-        goal, and showing that improving systematics has strong physics benefits is important
-        in the context of these studies.
-        %
-        Note that this is not the case in FASER$\nu$ and SND@LHC, where the physics reach
-        (at least concerning proton structure studies via neutrino DIS) is completely
-        limited by the low statistics available.
-
-        Second, and perhaps most importantly, we cannot claim to have a fully realistic modelling
-        of systematic errors, and in particular we miss a detailed estimate of their correlation, which
-        is known to be decisive in stablishing the PDF sensitivity.
-        %
-        Such analysis can only be carried by the experimental collaborations themselves and
-        be based on a complete detector simulation, and indeed our study provides
-        a strong motivation for this.
-        %
-        In this respect,  it is also worth noting that the estimation of the systematic uncertainties in our 
-	analysis is very  much conservative, and already the insights provided by our paper
-        are helping the experimentalists to improve designs to reduce systematics.
-        %
-        So there is a clear added value in separating the two scenarios.
-
-	Following the referee's suggestion, the results which only include the statistical errors
-	are now labelled "FPF$\star$" while the one that also account for the systematics are labelled "FPF".
-        %
-        We have also extended the rationale for showing results in the statistics-only scenario, alongside the
-        considerations described above.
-
-	\item {\it Section 4 and elsewhere. Given these are HL-LHC projections, somewhere these should
-		be compared with the HL-LHC PDFs of Ref [34]. This would surely be the fairer
-		comparison, or in any case will give a clearer picture of where things may stand.
-	}
-
-	The reason why we did not provide comparisons with the HL-LHC PDFs of Ref. [34] is because
-	the pseudodata used to determine these PDFs were produced with the PDF4LHC15 set which
-	does not account for the recent LHC measurements. The most consistent comparisons would
-	be to re-do the analysis done in ref. [34] using PDF4LHC21 and then compare the resulting PDFs 
-	with our determination, something which is clearly outside the scope of this paper.
-
-        This said, to answer the question from the referee, we have repeated the phenomenological study of Sect 4
-        comparing PDF4LHC15 with PDF4LHC15+HLHC PDFs for the same processes.
-        %
-        Specifically, we have added to the paper an Appendix where the phenomenology study of Sect 4 is repeated
-        now for the PDF4LHC15 with PDF4LHC15+HLHC PDFs.
-        %
-        From this comparison, one can observe that .... ADD
-
-        Furthermore, as mentioned in the paper, the PDF constraints from the FPF and from the HL-LHC are
-        fully orthogonal and complementary, and the former have the very important property that
-        possible contamination from new physics on the PDF fits can be completely ignored, since
-        this process is driven by $Q^2$ values outside the possible presence of BSM physics.
-        %
-        Specially should a large-mass anomaly be revealed at the HL-LHC, having the fully independent
-        validation of the large-$x$ PDFs provided by the FPF would be extremely valuable for its
-        interpretation.
-
-\end{enumerate}
-
-\noindent
-We now address the comments of referee B
-
-\begin{enumerate}
-\item{\it Page 3, lines 34-36 column 2 “since in general the strange and charm … not expected to vanish”. I agree but I suggest adding a reference or a comment supporting this statement. }
-
-  We have added the following references which explore strange and charm PDF asymmetries ~\cite{Sufian:2018cpj, Sufian:2020coz}.
-  %
-  We have also added a reference to the recent NNPDF study of the intrinsic charm asymmetry in the proton,
-  showing that these effects are potentially sizable and could hence be relevant for the interpretation
-  of the FPF measurements.
-
-\item{\it p. 4 l. 30-35 col.2 “Also, to identify… event yields.” Why a cut on the hadronic energy should properly simulate a cut on the number of charged tracks emerging from the interaction vertex?}
-
-The charged track multiplicity is expected to grow with the hadronic system’s invariant mass.
-We make this clear and cite a neutrino-Hydrogen interaction multiplicity study ~\cite{Aachen-Bonn-CERN-Munich-Oxford:1981lfk} as well as a FASER paper ~\cite{FASER:2019dxq} which also point this out.
-We also append this sentence:
-
-"…, as the charged track multiplicity is expected to grow with the invariant mass of the hadronic
-final state $W$~\cite{Aachen-Bonn-CERN-Munich-Oxford:1981lfk,FASER:2019dxq}."
-
-\item{\it Table 2.1 What is the meaning of the asterisk in “FLArE (*)”? I cannot see it referred to in the caption}
-
-The meaning of the asterisk was to be clear that this row represents 2 proposed detectors, as opposed to the remaining rows which are each one detector.
-We make this clear by appending the end of the caption:
-
-"…, which we denote for the two detectors as as FLArE(*)."
-
-\item{\it  p.5 l. 38 col.2 “is made of thin sensitive layers” What is the material/detector the layers are made of?}
-
-The target layers are interleaved with tungsten and emulsion. We make this clear by ammending this sentence:
-
-"...sensitive layers of emulsion..."
-
-\item{\it  p.5 l.49 col 1 and col 2 (“AdvSND” and “FLArE”) Can you put a reference about these experiments? Did you take the info from ref [10]?}
-
-  We have added the original FLArE experiment proposal paper as well as the FPF whitepaper (ref[10]) to the FLArE section.
-For AdvSND, we have added included the reference to the FPF whitepaper, which is currently the most detailed
-  description of this proposed experiment.
-
-\item{\it p.6 l.
-50-53 col.2 “Here we neglect efficiency ..
-simulation.” I am aware that this might be difficult to simulate at this stage but I think this effect is non-negligible due to misidentification ( a large background could enter this sample).
-Can you comment further on it?
-In addition, some guesses on misidentification capabilities can be drawn by the current FASER and SND@CERN capabilities.}
-
-  Indeed, uncertainties due to misidentification are in general not expected to be negligible.
-%
-  While there are no detailed studies of charm tagging efficiencies at the FPF, as we point out in the paper, charm tagging can be done by through multiple methods, including reconstructing the topology of $D$-meson decays, and through dimuon events.
-With multiple techniques at hand, one should be able to determine in-situ quite well the $D$-meson tagging efficiencies, for example comparing the dimuon selection method with the charm tagging via the emulsion detector.
-Furthermore, the availability of different experiments based on complementary techniques will help to cross-calibrate these effects.
-
-It is worth pointing out that our framework is flexible enough to accomodate variations in the modelling of systematic uncertainties, and in particular there is no conceptual issue preventing anyone to repeat our analysis for different treatments of efficiencies and other related experimental parameters.
-
-\item{\it p.9 l.
-41-43 col.2 “We note that … in our estimation.” (see also the conclusions p.
-27 l.
-52-55 col.1) I am puzzled by this statement.
-It is well known that flux systematics in Faser and SND@CERN play a prominent role and set the normalization (and shape?) of eqn 2.12.
-How can you ignore such an important effect in your analyses?
-Even if the PDF constraints are marginally affected by the normalization of the neutrino flux, some of your considerations about the on-axis (faser and faser2) versus the off-axis experiments (SND@CERN and its upgrades) may be affected by flux uncertainties.
-Can you comment on it in the paper?}
-
-  Indeed, the large neutrino flux uncertainties are well established, and the shape and normalization of the flux can vary widely between different models, although the neutrino muon component which is mostly relevant for neutrino DIS experiments is the one which is known the best.
-
-  It is important to note that neutrino measurements actually constrain the product of flux and cross-section - each of these components brings an uncertainty with it, and a full analysis with real data would constrain them simultaneously.
-We wish to motivate this joint analysis by calculating the  impact that FPF data can bring to a PDF fit.
-In this sense, by taking the flux to be known we can understand the full reach of FPF data on cross-section measurements, analogous to what was done in 2309.10417.
-Moreover, projections of FPF data on flux measurements has shown that HL-LHC data can bring flux uncertainties to a sub-percent level.
-
-  We would like to raise two more considerations which justify, in this work, to assume that the incoming neutrino
-  fluxes are known:
-  \begin{itemize}
-  \item As shown in appendix A, now moved to Sect 3, FASER$\nu$ and SND@LHC data from run III do not have sensitivity on the modelling of the neutrino-nucleus interaction cross-section.
-    %
-    This means that these measurements can be safely used, before the start of the FPF, to cross-calibrate
-    incoming neutrino fluxes and markedly improve their predictions for subsequent analysis.
-    %
-    Just due to this, by the time the FPF starts data taking the neutrino fluxes will be known
-    more precisely than now.
-
-  \item The flux and the neutrino DIS cross-section have very different kinematic dependences.
-    %
-    The incoming nuetrino flux is mostly fixed from the $(E_\nu, y_\nu)$ dependence of the event rates,
-    while the PDFs in the DIS cross-section are fixed by the $(x,Q^2)$ dependence.
-    %
-    By measuring event rates differentially in the three kinematic variables $(E_\nu, x,Q^2)$, and also
-    accessing the $y_\nu$ dependence of the incoming neutrinos, one can efficiency disentangle the
-    fluxes from the DIS cross-section.
-    %
-    Of course, one needs to explicitely demonstrate this via a dedicated analysis, but there
-    is no conceptual reason preventing us from this goal.
-
-   \end{itemize}
-
-We thank the referee for this important point and add the following paragraph after we introduce the flux model in the middle of section 2.3.
-
-  "%
-As pointed out in Ref.~\cite{Kling:2021gos} there are notable neutrino flux uncertainties, as various event generators do not agree on the forward parent hadron spectra. 
-%
-If the spread of various generators' predictions was taken as a means of flux uncertainty, corresponding to a $\lesssim 50\%$ uncertainty on the interacting muon neutrino spectrum, this would be a significant systematic if left unresolved.
-However, it is noteworthy that many existing predictions are yet to be tuned for the purposes of experiments such as those planned for the FPF.
-Nevertheless, there are projections of FPF measurements which would reduce this uncertainty to the sub-percent level already in the context of the contemporary predictions, based on parametrizing their expected correlations~\cite{Kling:2023tgr}, as well as efforts to describe the uncertainty in a data-driven way while improving the modelling of forward hadronization~\cite{Fieg:2023kld}.
-%
-However, it is important to note that forward neutrino experiments actually constrain the product of flux and cross-section, and one must be assumed to measure the other.
-In a full analysis,  the flux and cross-section would be constrained simultaneously in a joint measurement, utilizing their different kinematic dependences on $ x,Q^2,E_{\nu}$ and neutrino rapidity $\eta_{\nu}$.
-%
-In our study, we aim to understand the full impact of FPF data on the PDF fit, thus motivating this future joint measurement.
-%
-To this aim, we take the neutrino flux to be known and focus on the irreducible systematics associated with event reconstruction. 
-%
-With this assumption, we will show that Run 3 measruements will not be sufficient to impact PDF fits.
-Instead, Run 3 measurements could be used to calibrate incoming neutrino fluxes, effectively reducing the large uncertainties by the time FPF data is collected in the future.
-The expected reduction of FPF neutrino flux uncertainties further justifies our choice to take the neutrino flux as known.
-%"
-
-\item{\it p.11 l.
-33-37 col.1 Are you sure that an assumption of $f_{corr}$ = 0.5 is realistic?
-The estimates made in ref.[34] are for LHC experiments, not for fixed-target experiments like those of the FPF.}
-
-  In the absence of full detector simulation and detailed correlation model, it is not possible to answer
-  this point conclusively.
-  %
-  What we can say is that we have repeated our analysis for $f_{corr}=1$ and find that our main
-  qualitative conclusions remain unchanged.
-
-\item{\it  Fig. 2.4 In the bottom-left plot, I see a sharp increase in the fractional error at about x= 4 e-2. Why?}
-
-  The points near $x$=4e-2 with large uncertainties have small $E_h$, and are approaching the $E_h>100~ {\rm GeV}$ threshold that we set in Table 2.1.
-When we fluctuate the data according to our definition of uncertainty (Eq.
-2.19 with $E_h$ instead of $E_{\ell}$), these points drop below the acceptance and thus contribute to a fluctuation in this bin.
-  %
-  We have added to the revised version of the paper a short discussion to explain this observation.
-
-\item{\it p.19 l.50-53 col 1 and in general along the paper: I cannot see a discussion of the impact of neutral-current events at the FPF. Can you further comment on it?}
-
-  There are expected to be roughly as many neutral current neutrino scattering events as charged current events.
-However, due to the lack of information on both the incoming and outgoing neutrino, the full event cannot be reconstructed, only the total hadronic energy can be measured.
-One could try to use the total NC event rate as a means of constraining the integrated PDF, however we expect that this would negligibly improve the impact on the PDF constraints as compared to fully reconstructed CC events.
-Indeed, if anything, NC scattering brings in less sensitivity to PDFs than CC events, as can be seen from the LO decomposition of the corresponding structure functions.
-
-  We have added to Sect 2 a short discussion on why it is very likely that NC events do not provide useful PDF information: first of all, event kinematics cannot be reconstructed on an event by event basis as in the CC case, second, that systematics will be large since are dominated by the hadronic final state, and third, that NC scattering in general provides less complete information on the PDF flavour decomposition as compared to CC scattering.
-
-\end{enumerate}
-\bibliographystyle{utphys}
 \bibliography{main.bib}

### 2024-01-29 referee/referee-reply-rev2.tex
FASERnu -> FASER$\nu$

@@
 
-First, we demonstrate that Run 3 data from FASERnu can constrain the overall normalisation of the muon neutrino flux by 6\%, while 50\% of the HL-LHC data would constrain it down to the permille level.
+First, we demonstrate that Run 3 data from FASER$\nu$ can constrain the overall normalisation of the muon neutrino flux by 6\%, while 50\% of the HL-LHC data would constrain it down to the permille level.
 %
